### 2017-10-11 EUCBV/Conclusion.tex
Latest on 11/10/2017

In this paper, we studied the EUCBV algorithm which takes into account the empirical variance of the arms and  employs aggressive exploration parameters in conjunction with non-uniform arm selection (as opposed to UCB-Improved) to eliminate sub-optimal arms. Our theoretical analysis conclusively established that EUCBV exhibits an order-optimal gap-independent regret bound of $O\left(\sqrt{KT}\right)$. Empirically, we show that EUCBV performs superbly across diverse experimental settings and outperforms most of the bandit algorithms in a  stochastic MAB setup. Our experiments show that EUCBV is extremely stable for larger horizons and performs consistently well across different types of distributions. One avenue for future work is to remove the constraint of $T\geq K^{2.4}$ required for EUCBV to reach the order optimal regret bound. Another future direction is to come up with an anytime version of EUCBV. An anytime algorithm does not need the horizon $T$ as an input parameter.

%\section*{Acknowledgement} This work was supported by a funding from IIT Madras under project CSE/14-15/831/ RFTP/BRAV.

### 2017-10-11 EUCBV/EUCBV.tex
Latest on 11/10/2017

\def\year{2018}\relax
%File: formatting-instruction.tex
\documentclass[letterpaper]{article} %DO NOT CHANGE THIS
\usepackage{aaai18}  %Required
\usepackage{times}  %Required
\usepackage{helvet}  %Required
\usepackage{courier}  %Required
\usepackage{url}  %Required
\usepackage{graphicx}  %Required

\usepackage{macros}

\frenchspacing  %Required
\setlength{\pdfpagewidth}{8.5in}  %Required
\setlength{\pdfpageheight}{11in}  %Required
%PDF Info Is Required:
  \pdfinfo{
/Title (2018 Formatting Instructions for Authors Using LaTeX)
/Author (AAAI Press Staff)}
\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Efficient-UCBV: An Almost Optimal Algorithm using Variance Estimates}
\author{Author names withheld}

\maketitle

\begin{abstract}
We propose a novel variant of the UCB algorithm (referred to as Efficient-UCB-Variance (EUCBV)) for minimizing cumulative regret in the stochastic multi-armed bandit (MAB) setting. EUCBV incorporates the arm elimination strategy proposed in UCB-Improved \citep{auer2010ucb}, while taking into account the variance estimates to compute the arms' confidence bounds, similar to UCBV \citep{audibert2009exploration}. Through a theoretical analysis we establish that EUCBV incurs a \emph{gap-dependent} regret bound of {\scriptsize $O\left( \dfrac{K\sigma^2_{\max} \log (T\Delta^2 /K)}{\Delta}\right)$} after $T$ trials, where $\Delta$ is the minimal gap between optimal and sub-optimal arms; the above bound is an improvement over that of existing state-of-the-art UCB algorithms (such as UCB1, UCB-Improved, UCBV,  MOSS). Further, EUCBV incurs a \emph{gap-independent} regret bound of {\scriptsize $O\left(\sqrt{KT}\right)$}  which is an improvement over that of UCB1, UCBV and UCB-Improved, while being comparable with that of MOSS and OCUCB. Through an extensive numerical study we show that EUCBV significantly outperforms the popular UCB variants (like MOSS, OCUCB, etc.) as well as Thompson sampling and Bayes-UCB algorithms.

%\Keywords{Stochastic multi-armed bandits, cumulative regret, UCB-Improved, UCBV.}
\end{abstract}

\section{Introduction}
\label{sec:intro}
\input{intro}

\subsection{Related Work}
\label{sec:related}
\input{related}

\subsection{Our Contributions}
\label{sec:contri}
\input{contribution}

\section{Algorithm: Efficient UCB Variance}
\label{sec:eucbv}
\input{ealgo}

\section{Main Results} 
\label{sec:results}
\input{results}

\section{Proofs}
\label{sec:proofTheorem}
\input{proofTheorem}

\section{Experiments}
\label{sec:expt}
\input{expts}

\section{Conclusion and Future Works}
\label{sec:conc}
\input{Conclusion}

\clearpage
\newpage

\bibliography{biblio}
\bibliographystyle{aaai}

\clearpage
\newpage

\section{Appendix}
\label{sec:app}
\input{Appendix}

\end{document}

### 2017-10-11 EUCBV/contribution.tex
Latest on 11/10/2017

In this paper we propose the Efficient-UCB-Variance (henceforth referred to as EUCBV) algorithm for the stochastic MAB setting. EUCBV combines the approach of UCB-Improved, CCB \citep{liu2016modification} and UCBV algorithms. EUCBV, by virtue of taking into account the empirical variance of the arms, exploration parameters  and non-uniform arm selection (as opposed to UCB-Improved), performs significantly better than the existing algorithms in the stochastic MAB setting. EUCBV outperforms UCBV \citep{audibert2009exploration} which also takes into account empirical variance but is less powerful than EUCBV because of the usage of exploration regulatory factor by EUCBV. Also, we carefully design the confidence interval term with the variance estimates along with the pulls allocated to each arm to balance the risk of eliminating the optimal arm against excessive optimism. Theoretically we refine the analysis of \citet{auer2010ucb} and prove that for $T\geq K^{2.4}$ our algorithm is order optimal and achieves a worst case gap-independent regret bound of $O\left( \sqrt{KT} \right)$ which is same as that of MOSS and OCUCB but better than that of UCBV, UCB1 and UCB-Improved. Also, the gap-dependent regret bound of EUCBV is better than UCB1, UCB-Improved and MOSS but is poorer than OCUCB. However, EUCBV's gap-dependent bound matches OCUCB in the worst case scenario when all the gaps are equal. Through our theoretical analysis we establish the exact values of the exploration parameters for the best performance of EUCBV. Our proof technique is highly generic and can be easily extended to other MAB settings. An illustrative table containing the bounds is provided in Table \ref{tab:comp-bds}.

\begin{table}[t]
\caption{Regret upper bound of different algorithms}
\label{tab:comp-bds}
\begin{center}
\begin{tabular}{|p{5em}|p{12em}|p{7em}|}
\hline
Algorithm  &   \hspace*{1mm}Gap-Dependent & Gap-Independent \\
\hline
\hline
EUCBV		& $O\left( \dfrac{K\sigma_{\max}^{2}\log (\frac{T\Delta^2}{K})}{\Delta}\right)$ & $O\left(\sqrt{KT}\right)$\\
\hline
\hline
UCB1        & $O\left( \dfrac{K\log T}{\Delta} \right)$ & $O\left(\sqrt{KT\log T}\right)$ \\%\midrule
\hline
\hline
UCBV        & $O\left( \dfrac{K\sigma_{\max}^{2}\log T}{\Delta} \right)$ & $O\left(\sqrt{KT\log T}\right)$ \\
\hline
\hline
UCB-Imp 		& $O\left( \dfrac{K\log (T\Delta^2)}{\Delta} \right)$ & $O\left(\sqrt{KT\log K}\right)$ \\%\midrule
\hline
\hline
MOSS	     	& $O\left( \dfrac{K^2\log (T\Delta^2 /K)}{\Delta}\right)$ & $O\left(\sqrt{KT}\right)$\\%\midrule
\hline
\hline
OCUCB     	& $O\left( \dfrac{K\log (T/ H_{i})}{\Delta}\right)$ & $O\left(\sqrt{KT}\right)$\\\midrule
\end{tabular}
\end{center}
%\vspace*{-2em}
\end{table}

Empirically, we show that EUCBV, owing to its estimating the variance of the arms, exploration parameters and non-uniform arm pull, performs significantly better than MOSS, OCUCB, UCB-Improved, UCB1, UCBV, TS, BU, DMED, KLUCB and Median Elimination algorithms. Note that except UCBV, TS, KLUCB and BU (the last three with Gaussian priors) all the aforementioned algorithms do not take into account the empirical variance estimates of the arms. Also, for the optimal performance of TS, KLUCB and BU one has to have the prior knowledge of the type of distribution, but EUCBV requires no such prior knowledge. EUCBV is the first arm-elimination algorithm that takes into account the variance estimates of the arm for minimizing cumulative regret and thereby answers an open question raised by \citet{auer2010ucb}, where the authors conjectured that an UCB-Improved like arm-elimination algorithm can greatly benefit by taking into consideration the variance of the arms. Also, it is the first algorithm that follows the same proof technique of UCB-Improved and achieves a gap-independent regret bound of $O\left( \sqrt{KT} \right)$ thereby, closing the gap of UCB-Improved which achieved a gap-independent regret bound of $O\left( \sqrt{KT\log K} \right)$.

	The rest of the paper is organized as follows. In section~\ref{sec:eucbv} we present the  EUCBV algorithm. Our main theoretical results are stated in section~\ref{sec:results}, while the proofs are established in   section \ref{sec:proofTheorem}. Section~\ref{sec:expt} contains results and discussions from our numerical experiments. We draw our conclusions in section \ref{sec:conc} and section \ref{sec:app} is Appendix (supplementary material).

	%discuss about future works.

	%The section \ref{sec:app} containing further proofs is given as supplementary.

### 2017-10-11 EUCBV/ealgo.tex
Latest on 11/10/2017

%%%%%%%%%%%%%%%% alg-custom-block %%%%%%%%%%%%
%\algblock{ArmElim}{EndArmElim}
%\algnewcommand\algorithmicArmElim{\textbf{\em Arm Elimination}}
% \algnewcommand\algorithmicendArmElim{}
%\algrenewtext{ArmElim}[1]{\algorithmicArmElim\ #1}
%\algrenewtext{EndArmElim}{\algorithmicendArmElim}
%
%\algblock{ResParam}{EndResParam}
%\algnewcommand\algorithmicResParam{\textbf{\em Reset Parameters}}
% \algnewcommand\algorithmicendResParam{}
%\algrenewtext{ResParam}[1]{\algorithmicResParam\ #1}
%\algrenewtext{EndResParam}{\algorithmicendResParam}

\begin{algorithm}[!h]
\caption{EUCBV}
\label{alg:eucbv}
\begin{algorithmic}
\State {\bf Input:} Time horizon $T$, exploration parameters $\rho$ and $\psi$.
\State {\bf Initialization:} Set $m:=0$, $B_{0}:=\mathcal{A}$, $\epsilon_{0}:=1$, $M=\big \lfloor \frac{1}{2}\log_{2} \frac{T}{e}\big\rfloor$, $n_{0}=\big\lceil\frac{\log{(\psi T\epsilon_{0}^{2})}}{2\epsilon_{0}}\big\rceil$ and  $N_{0}=Kn_{0}$.
\State Pull each arm once
\For{$t=K+1,..,T$}	
\State Pull arm $i\in \argmax_{j\in B_{m}}\bigg\lbrace \hat{r}_{j} + \sqrt{\frac{\rho(\hat{v}_{j}+2)\log{(\psi T\epsilon_{m})}}{4 z_{j}}} \bigg\rbrace$, where $z_j$ is the number of times arm $j$ has been pulled.
%\State $t:=t+1$
\ArmElim
\State For each arm $i \in B_{m}$, remove arm $i$ from $B_{m}$ if,
\begin{align*}
%%%%%%%%%%%%%%%%%%%%%%%
%& \hat{r}_{i} + \sqrt{\frac{\rho\hat{v}_{i}\log{(\psi T\epsilon_{m})}}{4 z_{i}} + \frac{\rho\log{(\psi T\epsilon_{m})}}{4 z_{i}}} < \max_{{j}\in B_{m}}\bigg\lbrace\hat{r}_{j} -\sqrt{\frac{\rho\hat{v}_{j}\log{(\psi T\epsilon_{m})}}{4 z_{j}} + \frac{\rho\log{(\psi T\epsilon_{m})}}{4 z_{j}}} \bigg\rbrace
%%%%%%%%%%%%%%%%%%%%%%%
 \hat{r}_{i} + & \sqrt{\frac{\rho(\hat{v}_{i}+2)\log{(\psi T\epsilon_{m})}}{4 z_{i}}}  
  < \max_{{j}\in B_{m}}\bigg\lbrace\hat{r}_{j} -\sqrt{\frac{\rho(\hat{v}_{j}+2)\log{(\psi T\epsilon_{m})}}{4 z_{j}}} \bigg\rbrace
\end{align*}
\EndArmElim

\If{$t\geq N_{m}$ and $m\leq M$}
\ResParam
\State $\epsilon_{m+1}:=\frac{\epsilon_{m}}{2}$\vspace{0.5ex}
\State $B_{m+1}:=B_{m}$
\State $n_{m+1}:=\bigg\lceil\frac{\log{(\psi T\epsilon_{m+1}^{2})}}{2\epsilon_{m+1}}\bigg\rceil$
\State $N_{m+1}:=t+|B_{m+1}| n_{m+1}$
\State $m:=m+1$
\EndResParam
\EndIf
\State Stop if $|B_{m}|=1$ and pull ${i}\in B_{m}$ till $T$ is reached.
\EndFor
\end{algorithmic}
%\vspace*{-0.42em}
\end{algorithm}
%\vspace*{-0.42em}
\textbf{2.1 Notations:} We denote the set of arms by $\A$, with the individual arms labeled $i$, where  $i=1,\ldots,K$. We denote an arbitrary round of EUCBV by $m$. For simplicity, we assume that the optimal arm is unique and denote it by ${*}$. We denote the sample mean of the rewards for an arm $i$ at time instant $t$ by $\hat{r}_{i}(t)=\frac{1}{z_{i}(t)}\sum_{\ell=1}^{z_i(t)} X_{i,\ell}$, where $X_{i,\ell}$ is the reward sample received when arm $i$ is pulled for the $\ell$-th time, and $z_i(t)$ is the number of times arm $i$ has been pulled until timestep $t$. We denote the true variance of an arm by $\sigma_i^{2}$ while $\hat{v}_{i}(t)$ is the estimated variance, i.e., $\hat{v}_{i}(t)=\frac{1}{z_i(t)}\sum_{\ell=1}^{z_{i}(t)}(X_{i,\ell}-\hat{r}_{i})^{2}$. Whenever there is no ambiguity about the underlaying  time index $t$, for simplicity we neglect $t$ from the notations and simply use  $\hat{r}_i, \hat{v}_i,$ and $z_i$ to denote the respective quantities. We assume the rewards of all arms are bounded in $[0,1]$.

\textbf{2.2 The algorithm:} Earlier round-based arm elimination algorithms like Median Elimination \citep{even2006action} and UCB-Improved mainly suffered from two basic problems: \\
\begin{inparaenum}[\bfseries(i)]
\item \textit{Initial exploration:} Both of these algorithms pull each arm equal number of times in each round, and hence waste a significant number of pulls in initial explorations. \\
\item \textit{Conservative arm-elimination:} In UCB-Improved, arms are eliminated conservatively, i.e, only after $\epsilon_{m}<\frac{\Delta_{i}}{2}$, 
% the sub-optimal arm $i$ is discarded with high probability. 
where the quantity $\epsilon_{m}$ is initialized to $1$ and halved after every round. In the worst case scenario when $K$ is large, and the gaps are uniform  ($r_{1}=r_{2}=\cdots=r_{K-1}<r^{*}$) and small this results in very high regret.\\
\end{inparaenum}
%For any round $m$ UCB-Improved pulls all arms $n_{m}=\left\lceil \frac{ 2\log(T\epsilon_{m})}{\epsilon_{m}} \right\rceil$ number of times. The quantity $\epsilon_{m}$ is initialized to $1$ and halved after every round.
\\
	The EUCBV algorithm, which is mainly based on the arm elimination technique of the UCB-Improved algorithm,  remedies these by employing exploration regulatory factor $\psi$ and arm elimination parameter $\rho$ for aggressive elimination of sub-optimal arms. Along with these, similar to CCB \citep{liu2016modification} algorithm, EUCBV uses optimistic greedy sampling whereby at every timestep it only pulls the arm with the highest upper confidence bound rather than pulling all the arms equal number of times in each round. Also, unlike the UCB-Improved, UCB1, MOSS and OCUCB algorithms (which are based on mean estimation) EUCBV employs mean and variance estimates (as in \citet{audibert2009exploration}) for arm elimination. Further, we allow for arm-elimination at every time-step, which is in contrast to the earlier work (e.g., \citet{auer2010ucb}; \citet{even2006action}) where the arm elimination takes place only at the end of the respective exploration rounds.

### 2017-10-11 EUCBV/expts.tex
Latest on 11/10/2017

In this section, we conduct extensive empirical evaluations of EUCBV against several other popular MAB  algorithms. We use expected cumulative regret as the metric of comparison. The comparison is conducted against the following algorithms: KLUCB+ \citep{garivier2011kl}, DMED \citep{honda2010asymptotically}, MOSS \citep{audibert2009minimax}, UCB1 \citep{auer2002finite}, UCB-Improved \citep{auer2010ucb}, Median Elimination \citep{even2006action}, Thompson Sampling (TS) \citep{agrawal2011analysis}, OCUCB \citep{lattimore2015optimally}, Bayes-UCB (BU) \citep{kaufmann2012bayesian} and UCB-V \citep{audibert2009exploration}\footnote{The implementation for KLUCB, Bayes-UCB and DMED were taken from \citet{CapGarKau12}}. The parameters of EUCBV algorithm for all the experiments are set as follows: $\psi=\frac{T}{K^2}$ and $\rho =0.5$ (as in Corollary \ref{Result:Corollary:1}). Note that KLUCB+ empirically outperforms KLUCB (as shown in \citet{garivier2011kl}).

\begin{figure}[!h]
    \centering
    \begin{tabular}{cc}
    \setlength{\tabcolsep}{0.1pt}
    \subfigure[0.25\textwidth][Expt-$1$: $20$ Bernoulli-distributed arms ]
    %with $r_{i_{{i}\neq {*}}}=0.07$ and $r^{*}=0.1$
    {
    		\pgfplotsset{
		tick label style={font=\Large},
		label style={font=\Large},
		legend style={font=\Large},
		ylabel style={yshift=5pt},
		%legend style={legendshift=32pt},
		}
        \begin{tikzpicture}[scale=0.6]
      	\begin{axis}[
		xlabel={timestep},
		ylabel={Cumulative Regret},
		grid=major,
        %clip mode=individual,grid,grid style={gray!30},
        clip=true,
        %clip mode=individual,grid,grid style={gray!30},
  		legend style={at={(0.5,1.5)},anchor=north, legend columns=3} ]
      	% UCB
		\addplot table{EUCBV/results/NewExpt/Expt1/UCBV01_comp_subsampled.txt};
		\addplot table{EUCBV/results/NewExpt/Expt1/EUCBV01_comp_subsampled.txt};
		\addplot table{EUCBV/results/NewExpt/Expt1/KLUCB01_comp_subsampled.txt};
		\addplot table{EUCBV/results/NewExpt/Expt1/MOSS01_comp_subsampled.txt};
		\addplot table{EUCBV/results/NewExpt/Expt1/DMED01_comp_subsampled.txt};
		\addplot table{EUCBV/results/NewExpt/Expt1/UCB01_comp_subsampled.txt};
		\addplot table{EUCBV/results/NewExpt/Expt1/TS01_comp_subsampled.txt};
		\addplot table{EUCBV/results/NewExpt/Expt1/OCUCB01_comp_subsampled.txt};
		\addplot table{EUCBV/results/NewExpt/Expt1/BU01_comp_subsampled.txt};
      	\legend{UCB-V,EUCBV,KLUCB+,MOSS,DMED,UCB1,TS,OCUCB,BU}      	
      	\end{axis}
      	\end{tikzpicture}
  		\label{fig:1}
    }
    &
    \subfigure[0.25\textwidth][Expt-$2$: $3$ Group Mean Setting ]
    %with $r_{i_{{i}\neq {*}:1-33}}=0.1$, $r_{i_{{i}\neq {*}:34-99}}=0.6$, $r^{*}_{i=100}=0.9$ and $\sigma_{i=1:100}^{2} = 0.3$
    {
    		\pgfplotsset{
		tick label style={font=\Large},
		label style={font=\Large},
		legend style={font=\Large},
		ylabel style={yshift=5pt},
		}
        \begin{tikzpicture}[scale=0.6]
        \begin{axis}[
		xlabel={timestep},
		ylabel={Cumulative Regret},
        %clip mode=individual,grid,grid style={gray!30},
       	grid=major,
       	clip=true,
  		legend style={at={(0.5,1.5)},anchor=north, legend columns=3} ]
      	% UCB
		\addplot table{EUCBV/results/NewExpt/Expt2/UCBV01_comp_subsampled.txt};
		\addplot table{EUCBV/results/NewExpt/Expt2/EUCBV01_comp_subsampled.txt};
		\addplot table{EUCBV/results/NewExpt/Expt2/KLUCB01_comp_subsampled.txt};
		\addplot table{EUCBV/results/NewExpt/Expt2/MOSS01_comp_subsampled.txt};
		\addplot table{EUCBV/results/NewExpt/Expt2/UCBR01_comp_subsampled.txt};
		\addplot table{EUCBV/results/NewExpt/Expt2/UCB01_comp_subsampled.txt};
		\addplot table{EUCBV/results/NewExpt/Expt2/TS01_comp_subsampled.txt};
		\addplot table{EUCBV/results/NewExpt/Expt2/OCUCB01_comp_subsampled.txt};
		\addplot table{EUCBV/results/NewExpt/Expt2/BU01_comp_subsampled.txt};      	
      	\legend{UCB-V,EUCBV,KLUCB-G+,MOSS,UCB-Imp,UCB1,TS-G,OCUCB,BU-G}
      	\end{axis}
      	\end{tikzpicture}
   		\label{fig:2}
    }
    \end{tabular}
    \caption{A comparison of the cumulative regret incurred by the various bandit algorithms. }
    \label{fig:karmed}
    \vspace*{-1em}
\end{figure}
% For the purpose of performance comparison

\textbf{Experiment-1 (Bernoulli with uniform gaps):} This experiment is conducted to observe the performance of EUCBV over a short horizon. The horizon $T$ is set to $60000$. The testbed comprises of $20$ Bernoulli distributed arms with expected rewards of the arms as $r_{1:19}=0.07$ and $r^{*}_{20}=0.1$ and these type of cases are frequently encountered in web-advertising domain (see \cite{garivier2011kl}). The regret is averaged over $100$ independent runs and is shown in Figure \ref{fig:1}. EUCBV, MOSS, OCUCB, UCB1, UCB-V, KLUCB+, TS, BU and DMED are run in this experimental setup. Not only do we observe that EUCBV performs better than all the non-variance based algorithms such as MOSS, OCUCB, UCB-Improved and UCB1, but it also outperforms UCBV because of the choice of the exploration parameters. Because of the small gaps and short horizon $T$, we do not compare with UCB-Improved and Median Elimination for this test-case.

\textbf{Experiment-2 (Gaussian $3$ Group Mean Setting):} This experiment is conducted to observe the performance of EUCBV over a large horizon in Gaussian distribution testbed. This setting comprises of a large horizon of $T = 3\times 10^{5}$ timesteps and a large set of arms. This testbed comprises of $100$ arms involving Gaussian reward distributions with expected rewards of the arms in $3$ groups, $r_{1:66}=0.07$, $r_{67:99}=0.01$ and $r^{*}_{100}=0.09$ with variance set as $\sigma_{1:66}^{2} = 0.01,\sigma_{67:99}^{2} = 0.25$ and $\sigma^{2}_{100}=0.25$. The regret is averaged over $100$ independent runs and is shown in Figure \ref{fig:2}. From the results in Figure \ref{fig:2}, we observe that since the gaps are small and the variances of the optimal arm and the arms farthest from the optimal arm are the highest, EUCBV, which allocates pulls proportional to the variances of the arms, outperforms all the non-variance based algorithms MOSS, OCUCB, UCB1, UCB-Improved and Median-Elimination ($\epsilon=0.1,\delta=0.1$). The performance of Median-Elimination is extremely weak in comparison with the other algorithms and its plot is not shown in Figure \ref{fig:2}. We omit its plot in order to more clearly show the difference between EUCBV, MOSS and OCUCB. Also note that the order of magnitude in the y-axis (cumulative regret) of Figure \ref{fig:2} is $10^4$. KLUCB-Gauss+ (denoted by KLUCB-G+), TS-G and BU-G are initialized with Gaussian priors. Both KLUCB-G+ and UCBV which is a variance-aware algorithm perform much worse than TS-G and EUCBV. The performance of DMED is similar to KLUCB-G+ in this setup and its plot is omitted.

\begin{figure}[!h]
    \centering
    \begin{tabular}{cc}
    \subfigure[0.25\textwidth][Expt-$3$: Failure of TS]
    {
    		\pgfplotsset{
		tick label style={font=\Large},
		label style={font=\Large},
		legend style={font=\Large},
		ylabel style={yshift=5pt},
		}
        \begin{tikzpicture}[scale=0.6]
      	\begin{axis}[
		ylabel={Cumulative Regret},
		xlabel={timestep},
		grid=major,
        %clip mode=individual,grid,grid style={gray!30},
        clip=true,
        %clip mode=individual,grid,grid style={gray!30},
  		legend style={at={(0.5,1.3)},anchor=north, legend columns=3} ]
      	% UCB
		\addplot table{EUCBV/results/NewExpt/Expt3/UCBV01_comp_subsampled.txt};
		\addplot table{EUCBV/results/NewExpt/Expt3/EUCBV01_comp_subsampled.txt};
		\addplot table{EUCBV/results/NewExpt/Expt3/MOSS01_comp_subsampled.txt};
		\addplot table{EUCBV/results/NewExpt/Expt3/TS01_comp_subsampled.txt};
		\addplot table{EUCBV/results/NewExpt/Expt3/OCUCB01_comp_subsampled.txt};
		\addplot table{EUCBV/results/NewExpt/Expt3/BU01_comp_subsampled.txt};
      	\legend{UCBV,EUCBV,MOSS,TS-G,OCUCB,BU-G} 
      	\end{axis}
      	\end{tikzpicture}
  		\label{fig:3}
    }
    &
    \subfigure[0.25\textwidth][Expt-$4$: $3$ Group Variance Setting]
    %with $r_{i_{{i}\neq {*}}}=0.05$ and $r^{*}=0.1$
    {
    	\pgfplotsset{
		tick label style={font=\Large},
		label style={font=\Large},
		legend style={font=\Large},
		ylabel style={yshift=5pt},
		}
        \begin{tikzpicture}[scale=0.6]
        \begin{axis}[
		xlabel={timestep},
		ylabel={Cumulative Regret},
        %clip mode=individual,grid,grid style={gray!30},
		grid=major,
		clip=true,
  		legend style={at={(0.5,1.3)},anchor=north, legend columns=3} ]
        % UCB
		\addplot table{EUCBV/results/NewExpt/Expt41/UCBV01_comp_subsampled.txt};
		\addplot table{EUCBV/results/NewExpt/Expt41/EUCBV01_comp_subsampled.txt};
		\addplot table{EUCBV/results/NewExpt/Expt41/MOSS01_comp_subsampled.txt};
		\addplot table{EUCBV/results/NewExpt/Expt41/TS01_comp_subsampled.txt};
		\addplot table{EUCBV/results/NewExpt/Expt41/OCUCB01_comp_subsampled.txt};
		\addplot table{EUCBV/results/NewExpt/Expt41/BU01_comp_subsampled.txt};
      	\legend{UCBV,EUCBV,MOSS,TS-G,OCUCB,BU-G} 
      	\end{axis}
        \end{tikzpicture}
        \label{fig:4}
    }
	\end{tabular}
	\label{fig:furtherExpt1}
    \caption{Further Experiments with EUCBV}
    \vspace*{-1em}
\end{figure}
%\vspace*{-0.5em}

%Because of the poor performance of Bayes-UCB and KL-UCB in the last two experiments we do not implement them in this setup.
%Please note that algorithms like Thompson Sampling or Bayes-UCB are too slow to be run for such large arms (see \citet{lattimore2015optimally}) and  over such large horizon.
%This also corroborates the finding of \citet{lattimore2015optimally} which states that MOSS breaks down only when the number of arms are exceptionally large or the horizon is unreasonably high and gaps are very small. We consistently see that in uniform gap testcases EUCBV outperforms OCUCB.

\textbf{Experiment-3 (Failure of TS):} This experiment is conducted to demonstrate that in certain environments when the horizon is large, gaps are small and the variance of the optimal arm is high, the Bayesian algorithms (like TS) do not perform well but EUCBV performs exceptionally well. This experiment is conducted on $100$ Gaussian distributed arms such that expected rewards of the arms $r_{1:10}=0.045$, $r_{11:99}=0.04$, $r^{*}_{100}=0.05$ and the variance is set as $\sigma_{1:10}^{2}=0.01$,   $\sigma_{100}^{2}=0.25$ and $T=4\times 10^5$. The variance of the arms $i=11:99$ are chosen uniform randomly between $[0.2,0.24]$. TS and BU with Gaussian priors fail because here the chosen variance values are such that only variance-aware algorithms with appropriate exploration factors will perform  well or otherwise it will get bogged down in costly exploration. The algorithms that are not variance-aware will spend a significant amount of pulls trying to find the optimal arm. The result is shown in Figure \ref{fig:3}. Predictably EUCBV, which allocates pulls proportional to the variance of the arms, outperforms its closest competitors TS-G, BU-G, UCBV, MOSS and OCUCB. The plots for KLUCB-G+, DMED, UCB1, UCB-Improved and Median Elimination are omitted from the figure as their performance is extremely weak in comparison with other algorithms. We omit their plots to clearly show how EUCBV outperforms its nearest competitors. Note that EUCBV by virtue of its aggressive exploration parameters outperforms UCBV in all the experiments even though UCBV is a variance-based algorithm. The performance of TS-G is also weak and this is in line with the observation in \citet{lattimore2015optimally} that the worst case regret of TS when Gaussian prior is used is $\Omega\left( \sqrt{KT\log T}\right)$.

\textbf{Experiment-4 (Gaussian $3$ Group Variance setting):} This experiment is conducted to show that when the gaps are uniform and variance of the arms are the only discriminative factor then the EUCBV performs extremely well over a very large horizon and over a large number of arms. This testbed comprises of $100$ arms with Gaussian reward distributions, where the expected rewards of the arms are $r_{1:99}=0.09$ and $r^{*}_{100}=0.1$. The variances of the arms are divided into $3$ groups. The group $1$ consist of arms $i=1:49$ where the variances are chosen uniform randomly between $[0.0,0.05]$, group $2$ consist of arms $i=50:99$ where the variances are chosen uniform randomly between $[0.19,0.24]$ and for the optimal arm $i=100$ (group $3$) the variance is set as $\sigma_{*}^{2}=0.25$. We report the cumulative regret averaged over $100$ independent runs. The horizon is set at $T=4\times 10^{5}$ timesteps. We report the performance of MOSS,BU-G, UCBV, TS-G and OCUCB who are the closest competitors of EUCBV over this uniform gap setup. From the results in Figure \ref{fig:4}, it is evident that the growth of regret for EUCBV  is much lower than that of TS-G, MOSS, BU-G, OCUCB and UCBV. Because of the poor performance of KLUCB-G+ in the last two experiments we do not implement it in this setup. Also, note that for optimal performance BU-G, TS-G and KLUCB-G+ require the knowledge of the type of distribution to set their priors . Also, in all the experiments with Gaussian distributions EUCBV significantly outperforms all the Bayesian algorithms initialized with Gaussian priors.

### 2017-10-11 EUCBV/intro.tex
Latest on 11/10/2017

In this paper, we deal with the stochastic multi-armed bandit (MAB) setting. In its classical form, stochastic MABs represent a sequential learning problem where a learner is exposed to a finite set of actions (or arms) and needs to choose one of the actions at each timestep. After choosing (or pulling) an arm the learner  receives a reward, which is conceptualized as an independent random draw from stationary distribution associated with the selected arm. 
%Each of these rewards is random and drawn independently from the distribution associated with each arm. 
The mean of the reward distribution associated with an arm $i$ is denoted by $r_i$ whereas the mean of the reward distribution of the optimal arm $*$ is denoted by $r^*$ such that $r_i < r^*, \forall i\in \A$, where $\A$ is the set of arms such that $|\A|=K$. With this formulation the learner faces the task of balancing exploitation and exploration. In other words, should the learner pull the arm which currently has the best known estimates or explore arms more thoroughly to ensure that a correct decision is being made. The objective in the stochastic bandit problem is to minimize the cumulative regret, which is defined as follows:
\begin{align*}
R_{T}=r^{*}T - \sum_{i\in \A} r_{i}z_{i}(T),
\end{align*}
where $T$ is the number of timesteps, and  $z_{i}(T)$ is the number of times the algorithm has chosen arm $i$ up to timestep $T$.
The expected regret of an algorithm after $T$ timesteps can be written as,
\begin{align*}
\E[R_{T}]= \sum_{i=1}^{K} \E[z_i (T)] \Delta_i,
\end{align*}
where $\Delta_{i}=r^{*}-r_{i}$ is the gap between the means of the optimal arm and the $i$-th arm.

% One of the fundamental assumptions in stochastic MAB is that the distribution associated with each arm does not change over the entire time horizon $T$.

	In recent years the MAB setting has garnered extensive popularity because of its simple learning  model and its practical applications in a wide-range of industries, including, but not limited to, mobile channel allocations, online advertising and computer simulation games.

	%industry defined problems

### 2017-10-11 EUCBV/proofTheorem.tex
Latest on 11/10/2017

%\subsection{Lemma 1}
%\label{sec:proofTheorem:Lemma1}
We first present a few technical lemmas that is required  to prove the result in Theorem \ref{Result:Theorem:1}.

\begin{lemma}
\label{proofTheorem:Lemma:1}
If $T\geq K^{2.4}$, $\psi=\frac{T}{ K^2}$, $\rho=\frac{1}{2}$ and $m\leq \frac{1}{2} \log_2\left(\frac{T}{e}\right) $, then,
\begin{align*}
\dfrac{\rho m \log(2)}{\log(\psi T) - 2m\log( 2)} \leq \frac{3}{2}.
\end{align*}
\end{lemma}

\begin{lemma}
\label{proofTheorem:Lemma:2}
If $T\geq K^{2.4}$, $\psi=\frac{T}{ K^2}$, $\rho =\frac{1}{2}$, $m_i = min\lbrace m|\sqrt{4\epsilon_{m} } < \frac{\Delta_i}{4} \rbrace $ and $c_{i} =\sqrt{\frac{\rho (\hat{v}_i + 2)\log (\psi T\epsilon_{m_{i}})}{4 z_i}}$, then,
%\begin{align*}
\center $c_{i} < \frac{\Delta_i}{4}$.
%\end{align*}
\end{lemma}

\begin{lemma}
\label{proofTheorem:Lemma:3}
If $m_i = min\lbrace m|\sqrt{4\epsilon_{m} } < \frac{\Delta_i}{4} \rbrace $,  $c_{i} = \sqrt{\frac{\rho (\hat{v}_i + 2) \log (\psi T\epsilon_{m_{i}})}{4 z_{i}}}$ and $n_{m_i} = \frac{\log{(\psi T\epsilon_{m_{i}})}}{2\epsilon_{m_{i}}}$ then we can show that,
\begin{align*}
\mathbb{P}(\hat{r}_{i}> r_{i} + c_{i})\le \dfrac{2}{(\psi  T\epsilon_{m_{i}})^{\frac{3\rho}{2}}}.
\end{align*}
\end{lemma}

%\begin{lemma}
%\label{proofTheorem:Lemma:3}
%If $m_i = min\lbrace m|\sqrt{4\epsilon_{m} } < \frac{\Delta_i}{4} \rbrace $,  $\bar{c}_i=\sqrt{\frac{\rho (\sigma_{i}^{2}+\sqrt{\epsilon_{m_{i}}} + 2)\log(\psi T\epsilon_{m_{i}})}{4z_i}}$ and $n_{m_i} = \frac{\log{(\psi T\epsilon_{m_{i}})}}{2\epsilon_{m_{i}}}$ then we can show that,
%\begin{align*}
%\mathbb{P}\left( \hat{r}_{i} > r_{i}+ \bar{c}_i\right) 
%+ \mathbb{P}\left( \hat{v}_{i}\geq \sigma_{i}^{2}+\sqrt{\epsilon_{m_{i}}}\right) \leq \dfrac{2}{(\psi  T\epsilon_{m_{i}})^{\frac{3\rho}{2}}}.
%\end{align*}
%\end{lemma}

\begin{lemma}
\label{proofTheorem:Lemma:4}
If $m_i = min\lbrace m|\sqrt{4\epsilon_{m} } < \frac{\Delta_i}{4} \rbrace $, $\psi=\frac{T}{ K^2}$, $\rho=\frac{1}{2}$, $c_{i} =\sqrt{\frac{\rho(\hat{v}_i + 2)\log (\psi T\epsilon_{m_{i}})}{4 z_{i}}}$ and $n_{m_i}=\frac{\log{(\psi T\epsilon_{m_{i}}^{2})}}{2\epsilon_{m_{i}}}$ then in the $m_i$-th round, 
\begin{align*}
\Pb\lbrace c^{*} > c_i \rbrace  \leq \dfrac{182 K^4}{T^{\frac{5}{4}}\sqrt{\epsilon_{m_i}}}.
\end{align*}
\end{lemma}

\begin{lemma}
\label{proofTheorem:Lemma:5}
If $m_i = min\lbrace m|\sqrt{4\epsilon_{m} } < \frac{\Delta_i}{4} \rbrace $,$\psi=\frac{T}{ K^2}$, $\rho=\frac{1}{2}$, $c_{i} =\sqrt{\frac{\rho (\hat{v}_i + 2)\log (\psi T\epsilon_{m_{i}})}{4 z_i}}$ and $n_{m_i}=\frac{\log{(\psi T\epsilon_{m_{i}}^{2})}}{2\epsilon_{m_{i}}}$ then in the $m_i$-th round, 
\begin{align*}
\Pb\lbrace z_i < n_{m_i} \rbrace  \leq \dfrac{182 K^4}{T^{\frac{5}{4}}\sqrt{\epsilon_{m_i}}}.
\end{align*}
\end{lemma}

%\begin{lemma}
%\label{proofTheorem:Lemma:6}
%For $T\geq K^{2.4}$, $\epsilon_{m_i}\geq \sqrt{\frac{e}{T}}$, $\psi=\frac{T}{K^2}$ and $\rho=\frac{1}{2}$,  
%\begin{align*}
%\dfrac{6K}{(\psi T \epsilon_{m_i})^{\frac{3\rho}{2}}} > \dfrac{K\log T}{(\psi T)^{3\rho}}\sum_{m=0}^{m_i}\dfrac{1}{\epsilon_{m_i}^{3\rho + 1}}
%\end{align*}
%\end{lemma}

%\begin{lemma}
%\label{proofTheorem:Lemma:6}
%For all bounded rewards in $[0,1]$, $\frac{\Delta_i}{4} \geq \frac{\Delta_i}{4\sigma_i^2 + 4} $.
%\end{lemma}

\begin{lemma}
\label{proofTheorem:Lemma:6}
For two integer constants $c_1$ and $c_2$, if $20 c_1 \leq c_2$ then,
\begin{align*}
c_1 \frac{4\sigma_i^2 + 4}{\Delta_i}\log\bigg( \frac{T\Delta_i^2}{K}\bigg) \leq c_2 \frac{\sigma_i^2}{\Delta_i}\log\bigg( \frac{T\Delta_i^2}{K}\bigg).
\end{align*}
\end{lemma}

%\begin{lemma}
%\label{proofTheorem:Lemma:8}
%If $m_*$ be the first round that the optimal arm $*$ gets eliminated, then we can show that the regret is upper bounded by,
%
%\begin{align*}
%\sum_{m_{*}=0}^{max_{j\in \A^{'}}m_{j}}\sum_{i\in \A^{''}:m_{i}>m_{*}}\bigg(\dfrac{388 K}{(\psi  T\epsilon_{m_{*}})^{\frac{3\rho}{2}}} \bigg).T\max_{j\in \A^{''}:m_{j}\geq m_{*}}{\Delta}_{j} \\
%%%%%%%%%%%%%%%%%%%%%%%%%
% \leq\sum_{i\in \A^{'}}\dfrac{C_2^{'} K^{\frac{5}{2}}}{\sqrt{T\Delta_i}} +\sum_{i\in \A^{''}\setminus \A^{'}}\dfrac{C_2^{'} K^{\frac{5}{2}}}{\sqrt{T b}}
%\end{align*}
%
%\end{lemma}

The proofs of lemmas \ref{proofTheorem:Lemma:1} - \ref{proofTheorem:Lemma:6} can be found in Appendix ~\ref{App:Lemma:1}, ~\ref{App:Lemma:2}, ~\ref{App:Lemma:3}, ~\ref{App:Lemma:4}, ~\ref{App:Lemma:5} and
 ~\ref{App:Lemma:6} respectively.

%The proofs of all the Lemmas can be found in Appendix ~\ref{App:Lemma:1} - Appendix ~\ref{App:Lemma:9} respectively.

\subsection*{Proof of Theorem 1}
\label{sec:proofTheorem:Theorem1}
\begin{customproof}{1}
For each sub-optimal arm ${i}\in\mathcal{A}$, let $m_{i}=\min{\left\lbrace m|\sqrt{4\epsilon_{m_i}} < \frac{\Delta_{i}}{4}\right\rbrace}$. Also, let $\A^{'}=\lbrace i\in \A: \Delta_{i} > b \rbrace$ and $\A^{''}=\lbrace i\in \A: \Delta_{i} > 0 \rbrace$. Note that as all rewards are bounded in $[0,1]$, it implies that $0\leq \sigma_i^2 \leq \frac{1}{4},\forall i\in \A$. Now, as in \citet{auer2010ucb}, we bound the regret under the following two cases: 
\begin{itemize}
\item {Case $(a)$}: some sub-optimal arm ${i}$ is not eliminated in round $m_{i}$ or before and the optimal arm ${*}\in B_{m_{i}}$
\item {Case $(b)$}: an arm ${i}\in B_{m_i}$ is eliminated in round $m_{i}$ (or before), or there is no optimal arm $*\in B_{m_i}$
\end{itemize} 
The details of each case are contained in the following sub-sections.

%Note that in in round $m_i$ as $\sqrt{4\epsilon_{m_i}} < \dfrac{\Delta_{i}}{4}$ implies that $\sqrt{4\epsilon_{m_i}} < \dfrac{\Delta_{i}}{4\sigma_i^2}$, since $\sigma_i^2\in (0,1]$

\textbf{Case $(a)$:}
For simplicity, let $c_{i} := \sqrt{\frac{\rho (\hat{v}_i + 2) \log (\psi T\epsilon_{m_{i}})}{4 z_{i}}}$ denote the length of the confidence interval corresponding to arm $i$ in round $m_i$. Thus, in round $m_i$ (or before) whenever $z_i \geq n_{m_{i}}\ge\frac{\log{(\psi T\epsilon_{m_{i}}^{2})}}{2\epsilon_{m_{i}}}$, by applying Lemma \ref{proofTheorem:Lemma:2} we obtain $c_{i} < \frac{\Delta_{i}}{4}$.
%\begin{align*}
%	c_{i} < \dfrac{\Delta_{i}}{4} 
%\end{align*}
Now, the sufficient conditions for arm $i$ to get eliminated by an optimal arm in round $m_i$ is given by
	\begin{eqnarray}
	\hat{r}_{i} \leq r_{i} + c_{i} \text{, } 
 	\hat{r}^{*} \geq r^{*} - c^{*} \text{, } c_{i} \geq c^* \text{ and } z_i \geq n_{m_i} \label{eq:armelim-casea}.
	\end{eqnarray}

Indeed, in round $m_i$ suppose (\ref{eq:armelim-casea}) holds, then we have
%	 
  \begin{align*}
\hat{r}_{i} + c_{i}&\leq r_{i} + 2c_{i} 
= r_{i} + 4c_{i} - 2c_{i} \\
 &< r_{i} + \Delta_{i} - 2c_{i}
 \leq r^{*} -2c^{*} 
 \leq \hat{r}^{*} - c^{*}
  \end{align*}
  so that a sub-optimal arm ${i} \in \A^{'}$ gets eliminated.	
Thus, the probability of the complementary event of these four conditions in (\ref{eq:armelim-casea}) yields a bound on the probability that arm $i$ is not eliminated in round $m_i$. Following the proof of Lemma 1 of \citet{audibert2009exploration} we can show that a bound on the complementary of the first condition is given by,

\begin{align}
\mathbb{P}(\hat{r}_{i}> r_{i} + c_{i})
&\leq \mathbb{P}\left( \hat{r}_{i} > r_{i}+ \bar{c}_i\right) 
+ \mathbb{P}\left( \hat{v}_{i}\geq \sigma_{i}^{2}+\sqrt{\epsilon_{m_{i}}}\right)\label{eq:prob_eq2}
\end{align}
where 
\begin{align*}
\bar{c}_i=\sqrt{\dfrac{\rho (\sigma_{i}^{2}+\sqrt{\epsilon_{m_{i}}} + 2)\log(\psi T\epsilon_{m_{i}})}{4n_{m_i}}}.
\end{align*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Shifted as Lemma
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Note that, substituting $ n_{m_i} \geq \frac{\log{(\psi T\epsilon_{m_{i}})}}{2\epsilon_{m_{i}}}$, $\bar{c}_i$ can be simplified to obtain,
%\begin{align}
%\bar{c}_i
%\leq \sqrt{\dfrac{\rho\epsilon_{m_{i}}(\sigma_{i}^{2}+\sqrt{\epsilon_{m_{i}}} + 2)}{2}}\leq \sqrt{ \epsilon_{m_{i}}}.
%\label{si_bar_equn}
%\end{align}
%%
%The first term in the LHS of (\ref{eq:prob_eq2}) can be bounded using the Bernstein inequality as below:
%\begin{align}
%&\mathbb{P}\left( \hat{r}_{i} > r_{i}+ \bar{c}_i\right)\nonumber 
%\le \exp\left(- \dfrac{(\bar{c}_i)^2 z_{i}}{2\sigma_i^2 + \frac{2}{3}\bar{c}_i} \right)\nonumber 
%%%%%%%%%%%%%%%%
%\\
%& \overset{(a)}{\le} \exp\left(- \rho \left(\dfrac{3\sigma_{i}^{2}+3\sqrt{\epsilon_{m_{i}}} + 6}{6\sigma_i^2 + 2\sqrt{\epsilon_{m_i}}} \right)\log(\psi  T\epsilon_{m_{i}}\right)\nonumber \\
%%%%%%%%%%%%%%%%
%% &\le \exp\left(- \rho (\sigma_{i}^{2}+\sqrt{\epsilon_{m_{i}}} + 2)\log(\psi  T\epsilon_{m_{i}})\right)\nonumber \\
%%%%%%%%%%%%%%%%
%& \overset{(b)}{\leq} \exp\left(- \rho \log(\psi  T\epsilon_{m_{i}})\right) 
%%%%%%%%%%%%%%%%
%\le \dfrac{1}{(\psi  T\epsilon_{m_{i}})^{\rho}}
%\label{lhs1_equn}
%\end{align}
%where, $(a)$ is obtained by substituting equation \ref{si_bar_equn} and $(b)$ occurs because for all $\sigma_{i}^2 \in [0,1]$, $\left(\dfrac{3\sigma_{i}^{2}+3\sqrt{\epsilon_{m_{i}}} + 6}{6\sigma_i^2 + 2\sqrt{\epsilon_{m_i}}}\right) \geq 1$ .
%
% 
%The second term in the LHS of (\ref{eq:prob_eq2}) can be simplified as follows:
%\begin{align}
%&\mathbb{P}\bigg\lbrace \hat{v}_{i}\geq \sigma_{i}^{2}+\sqrt{\epsilon_{m_{i}}}\bigg\rbrace\nonumber\\
%%%%%%%%%%%%%%%%%%%
%&\leq \mathbb{P}\bigg\lbrace \dfrac{1}{n_{i}}\sum_{t=1}^{n_{i}}(X_{i,t}-r_{i})^{2}-(\hat{r}_{i}-r_{i})^{2}\geq \sigma_{i}^{2}+\sqrt{\epsilon_{m_{i}}}\bigg\rbrace\nonumber\\
%%%%%%%%%%%%%%%%%%%
%&\leq \mathbb{P}\bigg\lbrace \dfrac{\sum_{t=1}^{n_{i}}(X_{i,t}-r_{i})^{2}}{n_{i}}\geq \sigma_{i}^{2}+\sqrt{\epsilon_{m_{i}}} \bigg\rbrace\nonumber\\
%%%%%%%%%%%%%%%%%%%
%&\overset{(a)}{\leq} \mathbb{P}\bigg\lbrace \dfrac{\sum_{t=1}^{n_{i}}(X_{i,t}-r_{i})^{2}}{n_{i}}\geq \sigma_{i}^{2} + \bar{c}_i\bigg\rbrace \nonumber\\
%%%%%%%%%%%%%%%%%%%
%&\overset{(b)}{\leq} \exp\left(- \rho \left(\dfrac{3\sigma_{i}^{2}+3\sqrt{\epsilon_{m_{i}}} + 6}{6\sigma_i^2 + 2\sqrt{\epsilon_{m_i}}} \right)\log(\psi  T\epsilon_{m_{i}})\right)
%%%%%%%%%%%%%%%%%%
%\le \dfrac{1}{(\psi  T\epsilon_{m_{i}})^{\rho}}
%\label{lhs2_equn}
%\end{align}
%where inequality $(a)$ is obtained using (\ref{si_bar_equn}), while $(b)$ follows from the Bernstein inequality.

%Thus, using (\ref{lhs1_equn}) and (\ref{lhs2_equn}) in (\ref{eq:prob_eq2}) we obtain $\mathbb{P}(\hat{r}_{i}> r_{i} + c_{i})\le \dfrac{2}{(\psi  T\epsilon_{m_{i}})^{\rho}}$.

From Lemma \ref{proofTheorem:Lemma:3} we can show that $\mathbb{P}(\hat{r}_{i}> r_{i} + c_{i})\leq\mathbb{P}\left( \hat{r}_{i} > r_{i}+ \bar{c}_i\right) + \mathbb{P}\left( \hat{v}_{i}\geq \sigma_{i}^{2}+\sqrt{\epsilon_{m_{i}}}\right) \leq \frac{2}{(\psi  T\epsilon_{m_{i}})^{\frac{3\rho}{2}}}$. Similarly, $\mathbb{P}\lbrace\hat{r}^{*} < r^{*} - c^{*}\rbrace \leq \frac{2}{(\psi  T\epsilon_{m_{i}})^{\frac{3\rho}{2}}}$. Summing the above two contributions, the probability that a sub-optimal arm ${i}$ is not eliminated on or before $m_{i}$-th round by the first two conditions in  (\ref{eq:armelim-casea}) is,  
\begin{eqnarray}
\bigg(\dfrac{4}{(\psi T\epsilon_{m_{i}})^{\frac{3\rho}{2}}} \bigg). \label{eq:arm:elim:c1}
\end{eqnarray}

Again, from Lemma \ref{proofTheorem:Lemma:4} and Lemma \ref{proofTheorem:Lemma:5} we can bound the probability of the  complementary of the event $c_{i} \geq c^* $ and $ z_i \geq n_{m_i}$ by,

\begin{eqnarray}
\dfrac{182 K^4}{T^{\frac{5}{4}}\sqrt{\epsilon_{m_i}}} + \dfrac{182 K^4}{T^{\frac{5}{4}}\sqrt{\epsilon_{m_i}}}\leq \dfrac{364 K^4}{T^{\frac{5}{4}}\sqrt{\epsilon_{m_i}}}. \label{eq:arm:elim:c2}
\end{eqnarray}

Also, for eq. $(\ref{eq:arm:elim:c1})$ we can show that for any $\epsilon_{m_i}\in[\sqrt{\frac{e}{T}},1]$
\begin{eqnarray}
\bigg(\dfrac{4}{(\psi T\epsilon_{m_{i}})^{\frac{3\rho}{2}}} \bigg) &\overset{(a)}{\leq} \bigg(\dfrac{4}{(\frac{T^2}{K^2}\epsilon_{m_{i}})^{\frac{3}{4}}} \bigg)\leq \bigg(\dfrac{4 K^{\frac{3}{2}}}{(T^\frac{3}{2} \epsilon_{m_i}^{\frac{1}{4}}\sqrt{\epsilon_{m_{i}}})}\bigg) \nonumber \\
%%%%%%%%%%%%%%%%%%%%%%%
&\overset{(b)}{\leq} \bigg(\dfrac{4 K^{\frac{3}{2}}}{(T^{\frac{3}{2}-\frac{1}{8}}\sqrt{\epsilon_{m_{i}}})}  \bigg)
\leq \dfrac{4 K^4}{T^{\frac{5}{4}}\sqrt{\epsilon_{m_i}}}. \label{eq:arm:elim:c3}
\end{eqnarray}

Here, in $(a)$ we substitute the values of $\psi$ and $\rho$ and $(b)$ follows from the identity $\epsilon_{m_i}^{\frac{1}{4}}\geq (\frac{e}{T})^{\frac{1}{8}} $ as $\epsilon_{m_i}\geq \sqrt{\frac{e}{T}}$.

Summing up over all arms in $\A^{'}$ and bounding the regret for all the \textit{four} arm elimination conditions in (\ref{eq:armelim-casea}) by $(\ref{eq:arm:elim:c2}) + (\ref{eq:arm:elim:c3})$ for each arm $i\in \A^{'}$ trivially by $T\Delta_{i}$, we obtain
	\begin{align*}
&\sum_{i\in \A^{'}}\bigg(\dfrac{4 K^4 T\Delta_i}{T^{\frac{5}{4}}\sqrt{\epsilon_{m_i}}}\bigg) + \sum_{i\in \A^{'}}\bigg(\dfrac{364 K^4 T\Delta_i}{T^{\frac{5}{4}}\sqrt{\epsilon_{m_i}}}\bigg)\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\overset{(a)}{\leq}\sum_{i\in \A^{'}}\bigg(\dfrac{368 K^4 T\Delta_{i}}{T^{\frac{5}{4}}\left(\frac{\Delta_{i}^{2}}{4.16}\right)^{\frac{1}{2}}}\bigg)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\overset{(b)}{\leq} \sum_{i\in \A^{'}}\bigg(\dfrac{C_1 K^4}{(T)^{\frac{1}{4}}}\bigg).\\  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\end{align*}

%   \begin{align*}
%&\sum_{i\in \A^{'}}\bigg(\dfrac{388 K T\Delta_{i}}{(\psi T\epsilon_{m_{i}})^{\frac{3\rho}{2}}}\bigg)
%\leq\sum_{i\in \A^{'}}\bigg(\dfrac{388 K T\Delta_{i}}{(\psi T\dfrac{\Delta_{i}^{2}}{4.16})^{\frac{3\rho}{2}}}\bigg)\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%&\leq \sum_{i\in \A^{'}}\bigg(\dfrac{388.2^{2+2\frac{3\rho}{2}}.16^{\frac{3\rho}{2}} K T^{1-\frac{3\rho}{2}}}{\psi^{\frac{3\rho}{2}}\Delta_{i}^{2\frac{3\rho}{2} -1}}\bigg)\\  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%& \overset{(a)}{\leq} \sum_{i\in \A^{'}}\bigg(\dfrac{388.2^{2+\frac{3}{2}}.16^{\frac{3}{4}} K T^{1-\frac{3}{4}}}{(\frac{T}{K^2})^{\frac{3}{4}}\Delta_{i}^{2.\frac{3}{4} -1}}\bigg)\leq \sum_{i\in \A^{'}}\dfrac{C_1 K^{\frac{5}{2}}}{\sqrt{T\Delta_i}}  
%   \end{align*}
%Here in $(a)$ we substitute the values of $\rho$ and $\psi$ and $C_1$ denotes a constant integer value.\\
Here, $(a)$ happens because $\sqrt{4\epsilon_{m_i}} < \frac{\Delta_i}{4}$, and in $(b)$, $C_1$ denotes a constant integer value.\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Case (b)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{Case $(b)$:} Here, there are two sub-cases to be considered.
% \subsection*{Case $b$: \textit{An arm ${i}\in B_{m_i}$ is eliminated in round $m_{i}$ or before or there is no $*\in B_{m_i}$}}

\noindent
\textbf{Case $(b1)$ (\textit{${*}\in B_{m_{i}}$ and each ${i}\in \A^{'}$ is  eliminated on or before $m_{i}$ }): } Since we are eliminating a sub-optimal arm ${i}$ on or before round $m_{i}$, it is pulled no longer than, 
 \begin{align*}
 z_{i} < \bigg\lceil\dfrac{\log{(\psi T\epsilon_{m_{i}}^{2})}}{2\epsilon_{m_{i}}}\bigg\rceil
 \end{align*}
%\hspace*{4em}
%%$, since $\sqrt{\rho_{a}\epsilon_{m_{i}}}\leq\dfrac{\Delta_{i}}{2}
So, the total contribution of ${i}$  till round $m_{i}$ is given by, 
\begin{align*}
&\Delta_{i}\bigg\lceil\dfrac{\log{(\psi T\epsilon_{m_{i}}^{2})}}{2\epsilon_{m_{i}}}\bigg\rceil
\overset{(a)}{\leq}    \Delta_{i}\bigg\lceil\dfrac{\log{(\psi T(\dfrac{\Delta_{i}}{16 \times 256})^{4})}}{2(\dfrac{\Delta_{i}}{4\sqrt{4}})^{2}}\bigg\rceil \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\leq   \Delta_{i}\bigg(1+\dfrac{32\log{(\psi T(\dfrac{\Delta_{i}^{4}}{16384})}}{\Delta_{i}^{2}}\bigg)
\leq \Delta_{i}\bigg(1+\dfrac{32\log{(\psi T\Delta_{i}^{4})}}{\Delta_{i}^{2}}\bigg) .
\end{align*}

Here, $(a)$ happens because $\sqrt{4\epsilon_{m_{i}}} < \frac{\Delta_{i}}{4}$. Summing over all arms in $\A^{'}$ the total regret is given by, 
\begin{align*}
&\sum_{i\in \A^{'}}\Delta_{i}\bigg(1+\dfrac{32\log{(\psi T\Delta_{i}^{4}})}{\Delta_{i}^{2}}\bigg) = \sum_{i\in \A^{'}}\bigg(\Delta_{i} +\dfrac{32\log{(\psi T\Delta_{i}^{4}})}{\Delta_{i}}\bigg) \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\overset{(a)}{\leq} \sum_{i\in \A^{'}} \left(\Delta_{i}+\dfrac{64\log{( \frac{T\Delta_{i}^{2}}{K})}}{\Delta_{i}}\right)\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\overset{(b)}{\leq} \sum_{i\in \A^{'}} \left(\Delta_{i} +\dfrac{16(4\sigma_i^2 + 4)\log{( \frac{T\Delta_{i}^{2}}{K})}}{\Delta_{i}}\right)\\
&%%%%%%%%%%%%%%%%%%%%%%%%%%%
\overset{(c)}{\leq} \sum_{i\in \A^{'}} \left(\Delta_{i} +\dfrac{320\sigma_i^2\log{( \frac{T\Delta_{i}^{2}}{K})}}{\Delta_{i}}\right).\\
\end{align*}

We obtain $(a)$ by substituting the value of $\psi$, $(b)$ from $0\leq\sigma_i^2 \leq\frac{1}{4},\forall i\in \A$ and $(c)$ from Lemma \ref{proofTheorem:Lemma:6}.\\

\noindent
\textbf{Case $(b2)$ (\textit{Optimal arm ${*}$ is eliminated by a sub-optimal arm):  }} Firstly, if conditions of Case $a$ holds then the optimal arm ${*}$ will not be eliminated in round $m=m_{*}$ or it will lead to the contradiction that $r_{i}>r^{*}$. In any round $m_{*}$, if the optimal arm ${*}$ gets eliminated then for any round from $1$ to $m_{j}$ all arms ${j}$ such that $m_{j}< m_{*}$ were eliminated according to assumption in Case $a$. Let the arms surviving till $m_{*}$ round be denoted by $\A^{'}$. This leaves any arm $a_{b}$ such that $m_{b}\geq m_{*}$ to still survive and eliminate arm ${*}$ in round $m_{*}$. Let such arms that survive ${*}$ belong to $\A^{''}$. Also maximal regret per step after eliminating ${*}$ is the maximal $\Delta_{j}$ among the remaining arms ${j}$ with $m_{j}\geq m_{*}$.  Let $m_{b}=\min\left\lbrace m|\sqrt{4\epsilon_{m}}<\frac{\Delta_{b}}{4}\right\rbrace$. Hence, the maximal regret after eliminating the arm ${*}$ is upper bounded by,

\begin{align*}
&\sum_{m_{*}=0}^{max_{j\in \A^{'}}m_{j}}\sum_{i\in \A^{''}:m_{i}>m_{*}}\bigg(\dfrac{368 K^4}{(T^{\frac{5}{4}}\sqrt{\epsilon_{m_{*}}})} \bigg).T\max_{j\in \A^{''}:m_{j}\geq m_{*}}{\Delta}_{j}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\leq\sum_{m_{*}=0}^{max_{j\in \A^{'}}m_{j}}\sum_{i\in \A^{''}:m_{i}>m_{*}}\bigg(\dfrac{368 K^4 \sqrt{4}}{(T^{\frac{5}{4}}\sqrt{\epsilon_{m_{*}}})} \bigg).T.4\sqrt{\epsilon_{m_{*}}}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\overset{(a)}{\leq}\sum_{m_{*}=0}^{max_{j\in \A^{'}}m_{j}}\sum_{i\in \A^{''}:m_{i}>m_{*}}\bigg(\dfrac{C_2 K^4}{T^{\frac{1}{4}}\epsilon_{m_{*}}^{\frac{1}{2}-\frac{1}{2}}} \bigg)\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\leq\sum_{i\in \A^{''}:m_{i}>m_{*}}\sum_{m_{*}=0}^{\min{\lbrace m_{i},m_{b}\rbrace}}\bigg(\dfrac{C_2 K^4}{T^{\frac{1}{4}}} \bigg)\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\leq\sum_{i\in \A^{'}}\bigg(\dfrac{C_2 K^4}{T^{\frac{1}{4}}} \bigg)+\sum_{i\in \A^{''}\setminus \A^{'}}\bigg(\dfrac{C_2 K^4}{T^{\frac{1}{4}}} \bigg).\\
\end{align*}
Here at $(a)$, $C_2$ denotes an integer constant.

%\begin{align*}
%\sum_{m_{*}=0}^{max_{j\in \A^{'}}m_{j}}\sum_{i\in \A^{''}:m_{i}>m_{*}}\bigg(\dfrac{388 K}{(\psi  T\epsilon_{m_{*}})^{\frac{3\rho}{2}}} \bigg).T\max_{j\in \A^{''}:m_{j}\geq m_{*}}{\Delta}_{j}
%\end{align*}
%
%Again applying Lemma \ref{proofTheorem:Lemma:8} we can show that the above expression is upper bounded by 
%\begin{align*}
%\sum_{i\in \A^{'}}\dfrac{C_2^{'} K^{\frac{5}{2}}}{\sqrt{T\Delta_i}} +\sum_{i\in \A^{''}\setminus \A^{'}}\dfrac{C_2^{'} K^{\frac{5}{2}}}{\sqrt{T b}}
%\end{align*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Moved to Appendix as Lemma 9
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\begin{align*}
%&\sum_{m_{*}=0}^{max_{j\in \A^{'}}m_{j}}\sum_{i\in \A^{''}:m_{i}>m_{*}}\bigg(\dfrac{388 K}{(\psi  T\epsilon_{m_{*}})^{\frac{3\rho}{2}}} \bigg).T\max_{j\in \A^{''}:m_{j}\geq m_{*}}{\Delta}_{j}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%&\leq\sum_{m_{*}=0}^{max_{j\in \A^{'}}m_{j}}\sum_{i\in \A^{''}:m_{i}>m_{*}}\bigg(\dfrac{388 K\sqrt{4}}{(\psi  T\epsilon_{m_{*}})^{\frac{3\rho}{2}}} \bigg).T.4\sqrt{\epsilon_{m_{*}}}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%&\leq\sum_{m_{*}=0}^{max_{j\in \A^{'}}m_{j}}\sum_{i\in \A^{''}:m_{i}>m_{*}}C_2 K\bigg(\dfrac{T^{1-\frac{3\rho}{2}}}{\psi^{\frac{3\rho}{2}}\epsilon_{m_{*}}^{\frac{3\rho}{2}-\frac{1}{2}}} \bigg)\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%&\leq\sum_{i\in \A^{''}:m_{i}>m_{*}}\sum_{m_{*}=0}^{\min{\lbrace m_{i},m_{b}\rbrace}}\bigg(\dfrac{C_2 K T^{1-\frac{3\rho}{2}}}{\psi^{\frac{3\rho}{2}}2^{-(\frac{3\rho}{2} -\frac{1}{2})m_{*}}} \bigg)\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%&\leq\sum_{i\in \A^{'}}\bigg(\dfrac{C_2 K T^{1-\frac{3\rho}{2}}}{\psi^{\frac{3\rho}{2}}2^{-(\frac{3\rho}{2} -\frac{1}{2})m_{*}}} \bigg)+\sum_{i\in \A^{''}\setminus \A^{'}}\bigg(\dfrac{C_2 K T^{1-\frac{3\rho}{2} }}{\psi^{\frac{3\rho}{2}}2^{-(\frac{3\rho}{2} -\frac{1}{2})m_{b}}} \bigg)\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%&\leq\sum_{i\in \A^{'}}\bigg(\dfrac{C_2 K T^{1-\frac{3\rho}{2}}.2^{\frac{\frac{3\rho}{2}}{2}-\frac{1}{4}}}{\psi^{\frac{3\rho}{2}}\Delta_{i}^{\frac{3\rho}{2} -\frac{1}{2}}} \bigg)+\sum_{i\in \A^{''}\setminus \A^{'}}\bigg(\dfrac{C_2 K T^{1-\frac{3\rho}{2}}.2^{\frac{\frac{3\rho}{2}}{2}-\frac{1}{4}}}{\psi^{\frac{3\rho}{2}}b^{\frac{3\rho}{2} -\frac{1}{2}}} \bigg)\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%&\leq\sum_{i\in \A^{'}}\bigg(\dfrac{ C_2 K 2^{\frac{\frac{3\rho}{2}}{2}+\frac{19}{4}}.T^{1-\frac{3\rho}{2} } }{\psi^{\rho}\Delta_{i}^{2\frac{3\rho}{2} -1}} \bigg)+\sum_{i\in \A^{''}\setminus \A^{'}}\bigg(\dfrac{C_2 K 2^{\frac{\frac{3\rho}{2}}{2}+\frac{19}{4}}.T^{1-\frac{3\rho}{2}} }{\psi^{\frac{3\rho}{2} }b^{2\frac{3\rho}{2}-1}} \bigg)\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%&\overset{(a)}{\leq}\sum_{i\in \A^{'}}\bigg(\dfrac{C_2^{'} K .T^{1-\frac{3}{4}}}{(\frac{T}{K^2})^{\frac{3}{4}}\Delta_{i}^{2.\frac{3}{4} -1}} \bigg)+\sum_{i\in \A^{''}\setminus \A^{'}}\bigg(\dfrac{C_2^{'} K T^{1-\frac{3}{4}}}{(\frac{T}{K^2})^{\frac{3}{4}}b^{2.\frac{3}{4}-1}} \bigg)\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%&\leq\sum_{i\in \A^{'}}\dfrac{C_2^{'} K^{\frac{5}{2}}}{\sqrt{T\Delta_i}} +\sum_{i\in \A^{''}\setminus \A^{'}}\dfrac{C_2^{'} K^{\frac{5}{2}}}{\sqrt{T b}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\end{align*}
%In the above simplification, $(a)$ is obtained by substituting the values of $\psi$ and $\rho$.

Finally, summing up the regrets in \textbf{Case a} and \textbf{Case b}, the total regret is given by
\begin{align*}
\E [R_{T}] \leq &\sum\limits_{i\in \A :\Delta_{i} > b}\bigg\lbrace \dfrac{C_0 K^{4}}{T^{\frac{1}{4}}} + \bigg(\Delta_{i}+\dfrac{320\sigma_i^2\log{(\frac{T\Delta_{i}^{2}}{K})}}{\Delta_{i}}\bigg)\bigg \rbrace\\ 
  & +\sum\limits_{i\in \A :0 < \Delta_{i}\leq b} \dfrac{C_2 K^{4}}{T^{\frac{1}{4}}} + \max_{i\in \A :0 < \Delta_{i}\leq b}\Delta_{i}T
\end{align*}

where $C_0, C_1, C_2$ are integer constants s.t. $C_0 = C_1 + C_2$.
\end{customproof}

### 2017-10-11 EUCBV/related.tex
Latest on 11/10/2017

%There has been a significant amount of research in the area of stochastic MABs. One of the earliest work can be traced to \cite{thompson1933likelihood}, which deals with  the problem of choosing between two treatments to administer on patients who come in sequentially. Other seminal works include that of  \cite{robbins1952some} and then that of \cite{lai1985asymptotically} which established an asymptotic lower bound for the cumulative regret. It showed that for any consistent allocation strategy, we can have
%$\liminf_{T \to \infty}\frac{\E[R_{T}]}{\log T}\geq\sum_{\{i:r_{i}<r^{*}\}}\frac{(r^{*}-r_{i})}{D(Q_{i}||Q^{*})},$
%where $D(Q_{i}||Q^{*})$ is the Kullback-Leibler divergence between the reward densities $Q_{i}$ and $Q^{*}$, corresponding to arms with mean $r_{i}$ and $r^{*}$, respectively.

	Bandit problems have been extensively studied in several earlier works such as \citet{thompson1933likelihood}, \citet{robbins1952some} and \citet{lai1985asymptotically}. Lai and Robbins in  \citet{lai1985asymptotically} established an asymptotic lower bound for the cumulative regret. Over the years stochastic MABs have seen several algorithms with strong regret guarantees. For further reference an interested reader can look into \citet{bubeck2012regret}. The upper confidence bound algorithms balance the exploration-exploitation dilemma by linking the uncertainty in estimate of an arm with the number of times an arm is pulled, and therefore ensuring sufficient exploration. One of the earliest among these algorithms is UCB1 \citep{auer2002finite}, which has a gap-dependent regret upper bound of  $O\left(\frac{K\log T}{\Delta}\right)$, where $\Delta = \min_{i:\Delta_i>0} \Delta_i$. This result is asymptotically order-optimal for the class of distributions considered. But, the worst case gap-independent regret bound of UCB1 is found to be  $O \left(\sqrt{KT\log T}\right)$. In the later work of \citet{audibert2009minimax}, the authors propose the MOSS algorithm and showed that the worst case gap-independent regret bound of MOSS is $O\left( \sqrt{KT} \right)$ which improves upon UCB1 by a factor of order $\sqrt{\log T}$. However, the gap-dependent regret of MOSS is $O\left( \frac{K^{2}\log\left(T\Delta^{2}/K\right)}{\Delta}\right)$ and in certain regimes, this can be worse than even UCB1 (see \citet{audibert2009minimax,lattimore2015optimally}).

	 The UCB-Improved algorithm, proposed in \citet{auer2010ucb}, is a round-based\footnote{An algorithm is \textit{round-based} if it pulls all the arms equal number of times in each round and then eliminates one or more arms that it deems  to be sub-optimal.} variant of UCB1, that 
incurs a gap-dependent regret bound of $O\left(\frac{K\log (T\Delta^{2})}{\Delta}\right)$, which is better than that of UCB1. On the other hand, the worst case gap-independent regret bound of UCB-Improved is $O\left(\sqrt{KT\log K}\right)$. Recently in \citet{lattimore2015optimally}, the authors showed that  the algorithm OCUCB achieves order-optimal gap-dependent regret bound of $O\left(\sum_{i=2}^{K}\frac{\log\left(T/H_i\right)}{\Delta_i}\right)$ where $H_i=\sum_{j=1}^{K}\min\left\lbrace \frac{1}{\Delta_i^2},\frac{1}{\Delta_j^2}\right\rbrace$, and a gap-independent regret bound of $O\left( \sqrt{KT}\right)$. This is the best known gap-dependent and gap-independent regret bounds in the stochastic MAB framework. However, unlike our proposed EUCBV algorithm, OCUCB does not take into account the variance of the arms; as a result, empirically  we find  that our algorithm outperforms OCUCB in all the environments considered.

	In contrast to the above work, the UCBV \citep{audibert2009exploration} algorithm utilizes variance estimates to compute the confidence intervals for each arm. UCBV has a gap-dependent regret bound of $O\left(\frac{K\sigma_{\max}^{2}\log T}{\Delta}\right)$, where $\sigma_{\max}^{2}$ denotes the maximum variance among all the arms $i\in \A$. Its gap-independent regret bound can be inferred to be same as that of UCB1 i.e $O \left(\sqrt{KT\log T}\right)$. Empirically, \citet{audibert2009exploration} showed that UCBV outperforms UCB1 in several scenarios.

	Another notable design principle which has recently gained a lot of popularity is the Thompson Sampling (TS) algorithm (\citep{thompson1933likelihood}, \citep{agrawal2011analysis})  and  Bayes-UCB (BU) algorithm \citep{kaufmann2012bayesian}. % which employs the Bayesian approach in solving the MAB problem.
The TS algorithm maintains a posterior reward distribution for each arm; at each round, the algorithm samples values from these distribution and the arm corresponding to the highest sample value is chosen. Although TS is found to perform extremely well when the reward distributions are Bernoulli, it is established that with Gaussian priors the worst case regret can be as bad as $\Omega \left( \sqrt{KT\log T}\right)$ \citep{lattimore2015optimally}. The BU algorithm is an extension of the TS algorithm that takes quartile deviations into consideration while choosing arms.

	The final design principle we state is the information theoretic approach of DMED  \citep{honda2010asymptotically} and KLUCB \citep{garivier2011kl} algorithms. The algorithm KLUCB uses Kullbeck-Leibler divergence to compute the upper confidence bound for the arms. KLUCB is stable for a short horizon and is known to reach the \citet{lai1985asymptotically} lower bound in the special case of Bernoulli distribution. However, \citet{garivier2011kl} showed that KLUCB, MOSS and UCB1 algorithms are  empirically outperformed by UCBV in the exponential distribution as they do not take the variance of the arms into consideration.

### 2017-10-11 tbandit/appendix.tex
Latest on 11/10/2017

\appendix
\begin{align*}
& H_{1}^{\sigma}=\sum_{i=1}^{K}\frac{\sigma_{i}+\sqrt{\sigma_{i}^{2}+(16/3)\Delta_{i}}}{\Delta_{i}^{2}}\\
& H_{2}^{\sigma}=\min_{i\in \mathcal{A}} i\tilde{\Delta}_{(i)}^{-2} \text{, where } \tilde{\Delta}_{i}^{-2}=\frac{\sigma_{i}+\sqrt{\sigma_{i}^{2}+(16/3)\Delta_{i}}}{\Delta_{i}^{2}}
%& H_{2}^{\sigma}=\min_{i\in \mathcal{A}} i\frac{12\sigma_{(i)}^{2} + \Delta_{(i)}}{12\Delta_{(i)}^{2}}
\end{align*}

We know that $\sigma_{i}\in [0,1], \forall i\in \mathcal{A}$ and $\Delta_{i}\in [0,1], \forall i\in \mathcal{A}$ and so $\sigma_{i}^{2} \leq \sigma_{i}$ and $\sqrt{\Delta_{i}} \geq \Delta_{i}$.

\begin{align*}
(3\Delta_{i}^{2}).\left(\frac{4\sigma_{i}^{2}+\Delta_{i}+4}{12\sigma_{i}^{2}+\Delta_{i}}\right) & >  \left(\frac{12\Delta_{i}^{2}}{12\sigma_{i}^{2}+\Delta_{i}}\right)\\
& > \left(\frac{12\Delta_{i}^{2}}{12\sigma_{i}^{2}+12\Delta_{i}}\right)\\
& > \left(\frac{\Delta_{i}^{2}}{\sigma_{i}+\Delta_{i}}\right)\\
%& > \left(\frac{\Delta_{i}^{2}}{\sigma_{i}+(\sigma_{i}^{2} + (16/3)\Delta_{i})}\right)\\
& > \left(\frac{\Delta_{i}^{2}}{\sigma_{i}+\sqrt{\sigma_{i}^{2} + (16/3)\Delta_{i}}}\right)\\
& > \left(\frac{1}{\min_{i}i\tilde{\Delta}_{i}^{2}}\right)\\
\end{align*}

Now, from \cite{audibert2010best} we know that,
\begin{align*}
\sum_{i=1}^{K}\tilde{\Delta}_{i}^{-2} = \tilde{\Delta}_{(2)}^{-2} + \sum_{i=2}^{K}\frac{1}{i}i\tilde{\Delta}_{(i)}^{-2} &\leq \bar{\log K}\min_{i}i\tilde{\Delta}_{(i)}^{-2}\\
& \leq \log(2K) H_{2}^{\sigma}, \text{ as $\bar{\log K} \leq \log(2K)$}
\end{align*}

So, $H_{2}^{\sigma} \leq H_{1}^{\sigma} \leq \log(2K) H_{2}^{\sigma}$

\textbf{Regarding union bound}\\
\begin{align*}
\Pb\lbrace\xi_1 \cup \xi_2\rbrace &= \Pb\lbrace\xi_1\rbrace + \Pb\lbrace\xi_2\rbrace - \Pb\lbrace\xi_1 \cap \xi_2\rbrace\\
 &\leq \Pb\lbrace\xi_1\rbrace + \Pb\lbrace\xi_2\rbrace
\end{align*}
So,
\begin{align*}
1-\Pb\lbrace\xi_1 \cup \xi_2\rbrace \geq 1-\Pb\lbrace\xi_1\rbrace + \Pb\lbrace\xi_2\rbrace \geq \E[\Ls(T)] \end{align*}

\section{Cumulative Regret Bound}

\begin{theorem}
\label{proofTheorem:Prop:1}
The regret $R_T$ for AugUCB satisfies
\begin{align*}
&\E [R_{T}]\\
& \leq \sum\limits_{i\in A:\Delta_{i} > b}\bigg\lbrace \dfrac{T\Delta_{i}}{( \frac{3}{2} T\Delta_i^{2})^{\psi_{m_i}}}
  + \left( \Delta_i +\dfrac{22\Delta_i\psi_{m_i}\log( \frac{3}{2} T\Delta_i^2)}{ \Delta_i}\right)\\
  & \bigg(\dfrac{4T^{1-\psi_{m_i}}2^{\psi_{m_i}-\frac{1}{2}}}{\Delta_{i}^{\psi_{m_i}-\frac{1}{2}}} \bigg)\bigg \rbrace +\sum_{i\in A: 0 < \Delta_{i} \leq b}\bigg(\dfrac{4T^{1-\psi_{m_i}}2^{\psi_{m_i}-\frac{1}{2}}}{b^{\psi_{m_i}-\frac{1}{2}}} \bigg) \\
  & + \max_{\substack{i\in A: \\ \Delta_{i}\leq b}}\Delta_{i}T, \text{  for all $b\geq\sqrt{\frac{e}{T}}$}. 
\end{align*} 
\end{theorem}

\begin{proof}
\textbf{\textit{Case a: A sub-optimal arm i is not eliminated on or before round $m_{i}$ with $ * \in B_{m_i}$}}
\newline
%%%%%%%%%%%%%
For any arm $i\in A$, if it is eliminated from active set $B_{m_{i}}$ then the below two events have to come true,
\begin{align}
\hat{r}_{i} + s_{i} < \tau - s_{i}, \label{eq:armelim-var-casea1}\\
\hat{r}_{i} - s_{i} > \tau + s_{i}, \label{eq:armelim-var-caseb1}
\end{align}

From Theorem \ref{Result:Theorem:1}, we know that a sub-optimal arm $i\in\mathcal{A}$, the probability that it is not correctly eliminated in the $m_i$-th round (or before) is also bounded by $4\exp\left(- \dfrac{3\rho \psi_{m_i}}{2} \left(\dfrac{\sigma_{i}^{2}+\sqrt{\rho\epsilon_{m_{i}}}+1}{3\sigma_{i}^{2}+\sqrt{\rho \epsilon_{m_{i}}}}\right) \log( T\epsilon_{m_{i}}) \right)$.

Summing over all arms in $\mathcal{A}^{'}$ and trivially bounding the regret for each arm $i\in \mathcal{A}^{'}$,

\begin{align*}
&\sum_{i\in A^{'}}T\Delta_{i}\exp\left(- \dfrac{3\rho \psi_{m_i}}{2} \left(\dfrac{\sigma_{i}^{2}+\sqrt{\rho\epsilon_{m_{i}}}+1}{3\sigma_{i}^{2}+\sqrt{\rho \epsilon_{m_{i}}}}\right) \log( T\epsilon_{m_{i}}) \right)\\
&\overset{(a)}{\le}  \sum_{i\in A^{'}}T\Delta_{i} \exp\left(- \dfrac{3\rho \psi_{m_i}}{2} \log( T\epsilon_{m_{i}}) \right)\\
&\overset{(b)}{\le}  \sum_{i\in A^{'}}T\Delta_{i} \exp\left(-\psi_{m_i} \log( T\epsilon_{m_{i}}) \right)\\
&\overset{(c)}{\le}  \sum_{i\in A^{'}}\dfrac{T\Delta_{i}}{( T\dfrac{\Delta_i^{2}}{\rho})^{\psi_{m_i}}} \leq \sum_{i\in A^{'}}\dfrac{T\Delta_{i}}{( \frac{3}{2} T\Delta_i^{2})^{\psi_{m_i}}}
\end{align*}

In the above formulation, $(a)$ happens because  $\left(\dfrac{\sigma_{i}^{2}+\sqrt{\rho\epsilon_{m_{i}}}+1}{3\sigma_{i}^{2}+\sqrt{\rho \epsilon_{m_{i}}}}\right) \geq 1$. For $(b)$ we put $\rho=\dfrac{2}{3}$ and for $(c)$ we take the help of the inequality $\sqrt{\rho \epsilon_{m_i}} < \Delta_i$ in the $m_i$-th round.

\textbf{\textit{Case b: A sub-optimal arm i is either eliminated on or before round $m_{i}$ or there is no $ * \in B_{m_i}$}}

\textbf{\textit{Case b1: A sub-optimal arm i is in $B_{m_i}$}}

A sub-optimal arm is in $B_{m_i}$ and hence pulled no more than,
\begin{align*}
\left\lceil \dfrac{2\psi_{m_i}\log( T\epsilon_{m_i})}{\epsilon_{m_i}} \right\rceil\leq \left\lceil \dfrac{32\psi_{m_i}\log( \frac{3}{2} T\Delta_i^2)}{\frac{3}{2} \Delta_i^2}\right\rceil
\end{align*}

Hence, the total contribution to the expected regret is,
\begin{align*}
&\sum_{i\in A^{'}} \left\lceil \dfrac{32\Delta_i\psi_{m_i}\log( \frac{3}{2} T\Delta_i^2)}{\frac{3}{2} \Delta_i^2}\right\rceil\\
&\leq \sum_{i\in A^{'}} \left( \Delta_i +\dfrac{22\Delta_i\psi_{m_i}\log( \frac{3}{2} T\Delta_i^2)}{ \Delta_i}\right)
\end{align*}

\textbf{\textit{Case b2: Optimal arm ${*}$ is eliminated by a sub-optimal arm}}

	Firstly, if conditions of Case $a$ holds then the optimal arm ${*}$ will not be eliminated in round $m=m_{*}$ or it will lead to the contradiction that $r_{i}>r^{*}$. In any round $m_{*}$, if the optimal arm ${*}$ gets eliminated then for any round from $1$ to $m_{j}$ all arms ${j}$ such that $m_{j}< m_{*}$ were eliminated according to assumption in Case $a$. Let the arms surviving till $m_{*}$ round be denoted by $A^{'}$. This leaves any arm $a_{b}$ such that $m_{b}\geq m_{*}$ to still survive and eliminate arm ${*}$ in round $m_{*}$. Let such arms that survive ${*}$ belong to $A^{''}$. Also maximal regret per step after eliminating ${*}$ is the maximal $\Delta_{j}$ among the remaining arms ${j}$ with $m_{j}\geq m_{*}$.  Let $m_{b}=\min\lbrace m|\sqrt{\rho\epsilon_{m}}<\dfrac{\Delta_{b}}{2}\rbrace$. Hence, the maximal regret after eliminating the arm ${*}$ is upper bounded by, 
\begin{align*}
&\sum_{m_{*}=0}^{max_{j\in A^{'}}m_{j}}\sum_{i\in A^{''}:m_{i}>m_{*}}\bigg(\dfrac{1}{(  T\epsilon_{m_{*}})^{\psi_{m_i}}} \bigg).T\max_{j\in A^{''}:m_{j}\geq m_{*}}{\Delta}_{j}\\
&\leq\sum_{m_{*}=0}^{max_{j\in A^{'}}m_{j}}\sum_{i\in A^{''}:m_{i}>m_{*}}\bigg(\dfrac{1}{(  T\epsilon_{m_{*}})^{\psi_{m_i}}} \bigg).T.2\sqrt{\rho\epsilon_{m_{*}}}\\
&\leq\sum_{m_{*}=0}^{max_{j\in A^{'}}m_{j}}\sum_{i\in A^{''}:m_{i}>m_{*}}\bigg(\dfrac{4T^{1-\psi_{m_i}}}{\epsilon_{m_{*}}^{\psi_{m_i}-\frac{1}{2}}} \bigg)\\
&\leq\sum_{i\in A^{''}:m_{i}>m_{*}}\sum_{m_{*}=0}^{\min{\lbrace m_{i},m_{b}\rbrace}}\bigg(\dfrac{4T^{1-\psi_{m_i}}}{2^{-(\psi_{m_i}-\frac{1}{2})m_{*}}} \bigg)\\
&\leq\sum_{i\in A^{'}}\bigg(\dfrac{4T^{1-\psi_{m_i}}}{2^{-(\psi_{m_i}-\frac{1}{2})m_{*}}} \bigg)+\sum_{i\in A^{''}\setminus A^{'}}\bigg(\dfrac{4T^{1-\psi_{m_i}}}{2^{-(\psi_{m_i}-\frac{1}{2})m_{b}}} \bigg)\\
&\leq\sum_{i\in A^{'}}\bigg(\dfrac{4T^{1-\psi_{m_i}}*2^{\psi_{m_i}-\frac{1}{2}}}{\Delta_{i}^{\psi_{m_i}-\frac{1}{2}}} \bigg)+\sum_{i\in A^{''}\setminus A^{'}}\bigg(\dfrac{4T^{1-\psi_{m_i}}*2^{\psi_{m_i}-\frac{1}{2}}}{b^{\psi_{m_i}-\frac{1}{2}}} \bigg)\\
&\leq\sum_{i\in A^{'}}\bigg(\dfrac{4T^{1-\psi_{m_i}}2^{\psi_{m_i}-\frac{1}{2}}}{\Delta_{i}^{\psi_{m_i}-\frac{1}{2}}} \bigg)+\sum_{i\in A^{''}\setminus A^{'}}\bigg(\dfrac{4T^{1-\psi_{m_i}}2^{\psi_{m_i}-\frac{1}{2}}}{b^{\psi_{m_i}-\frac{1}{2}}} \bigg)\\
%& = \sum_{i\in A^{'}}\bigg(\dfrac{ C_{2}(\rho_{a}) T^{1-\rho_{a}}}{\Delta_{i}^{4\rho_{a}-1}} \bigg)+\sum_{i\in A^{''}\setminus A^{'}}\bigg(\dfrac{C_{2(\rho_{a})}T^{1-\rho_{a}}}{b^{4\rho_{a}-1}} \bigg) \text{, where } C_2(x) = \frac{2^{2x+\frac{3}{2}}x^{2x}}{\psi^{x}}
\end{align*}

%\text{, since } \sqrt{\rho_{a}\epsilon_{m}}<\dfrac{\Delta_{i}}{2}

Summing up \textbf{Case a} and \textbf{Case b}, the total expected regret is given by,
\begin{align*}
 &\sum\limits_{i\in A:\Delta_{i} > b}\bigg\lbrace \dfrac{T\Delta_{i}}{( \frac{3}{2} T\Delta_i^{2})^{\psi_{m_i}}}
  + \left( \Delta_i +\dfrac{22\Delta_i\psi_{m_i}\log( \frac{3}{2} T\Delta_i^2)}{ \Delta_i}\right)\\
  & \bigg(\dfrac{4T^{1-\psi_{m_i}}2^{\psi_{m_i}-\frac{1}{2}}}{\Delta_{i}^{\psi_{m_i}-\frac{1}{2}}} \bigg)\bigg \rbrace +\sum_{i\in A: 0 < \Delta_{i} \leq b}\bigg(\dfrac{4T^{1-\psi_{m_i}}2^{\psi_{m_i}-\frac{1}{2}}}{b^{\psi_{m_i}-\frac{1}{2}}} \bigg)
\end{align*}

% R_{T} \leq &\sum\limits_{i\in A:\Delta_{i}\geq b}\bigg\lbrace\bigg(\dfrac{2^{1+4\rho_{a}}\rho_{a}^{2\rho_{a}}T^{1-\rho_{a}}}{\psi^{\rho_{a}}\Delta_{i}^{4\rho_{a}-1}}\bigg) + \bigg(\Delta_{i}+\dfrac{32\rho_{a}\log{(\psi  T\dfrac{\Delta_{i}^{4}}{16\rho_{a}^{2}})}}{\Delta_{i}}\bigg)\\
%&  +  \bigg(\dfrac{T^{1-\rho_{a}}\rho_{a}^{2\rho_{a}}2^{2\rho_{a}+\frac{3}{2}}}{\psi^{\rho_{a}}\Delta_{i}^{4\rho_{a} -1}} \bigg) \bigg \rbrace+\sum\limits_{i\in A:0\leq\Delta_{i}\leq b}\bigg(\dfrac{T^{1-\rho_{a}}\rho_{a}^{2\rho_{a}}2^{2\rho_{a}+\frac{3}{2}}}{\psi^{\rho_{a}}b^{4\rho_{a} -1}} \bigg) + max_{i:\Delta_{i}\leq b}\Delta_{i}T

\end{proof}

### 2017-10-11 tbandit/conclusion.tex
Latest on 11/10/2017

We proposed the AugUCB algorithm for a fixed-budget, pure-exploration TBP. Our algorithm employs both mean and variance estimates for arm elimination. This, to our knowledge is the first variance-based algorithm for the specific TBP that we have considered. We first prove an upper bound on the expected loss incurred by AugUCB. We then conduct simulation experiments to validate the performance of AugUCB. In comparison with APT, CSAR and other non variance-based algorithms, we find that the performance of AugUCB is significantly better. Further, the performance of AugUCB is comparable with UCBEV (which is also variance-based), although the latter exhibits a slightly better performance.  However, UCBEV is not implementable in practice as it requires computing problem complexity, $H_{\sigma,1}$, while AugUCB (requiring no such inputs) can be easily deployed in real-life scenarios. It would be an interesting future work to design an anytime version of the AugUCB algorithm.

%Although UCBEV provides a better guarantee, it is important to emphasize that UCBEV has access to the problem complexity, and is hence not realistic in practice. This is in contrast to AugUCB whose implementation does not require any such complexity inputs. 
%Finally, through extensive simulation experiments we have validated the performance of AugUCB.

%From a theoretical viewpoint we conclude the expected loss AugUCB is more than UCBEV (which has access to problem complexity). From the numerical experiments on settings with large number of arms with different mean and variance, we observed that AugUCB outperforms all the non-variance aware algorithms.
%This is also the first paper to apply elimination by variance estimation in the TBP problem by modifying UCB-Improved and CCB algorithms. 
% It would be interesting future research to come up with an anytime version of AugUCB algorithm. This is also the first paper to apply elimination by variance estimation in the TBP problem by modifying UCB-Improved and CCB algorithms.

### 2017-10-11 tbandit/contribution.tex
Latest on 11/10/2017

In this paper we propose the Augmented UCB (AugUCB) algorithm for the fixed-budget setting of a specific combinatorial, pure-exploration, stochastic MAB called the thresholding bandit problem.
%In this paper we propose AugUCB algorithm for the fixed-budget, comp thresholding bandit problem.
 AugUCB essentially combines the approach of UCB-Improved, CCB \citep{liu2016modification} and APT algorithms. Our algorithm takes into account the empirical variances of the arms along with mean estimates; to the best of our knowledge this is the first variance-based algorithm for the considered TBP. 
Thus, we also address an open problem discussed in \cite{auer2010ucb} of designing an algorithm that can eliminate arms based on variance estimates. In this regard, note that both CSAR and APT are not variance-based algorithms.

\begin{table}[b]
\caption{AugUCB vs.\ State of the art}
\label{tab:regret-bds}
\begin{center}
\begin{tabular}{|p{2.3cm}|p{8.4cm}|}
% \toprule
\hline
Algorithm  & Upper Bound on Expected Loss \\
% \midrule
\hline
\hline
AugUCB      &$ \exp\left(- \dfrac{T}{4096 \log(K\log K)H_{\sigma,2}} + \log\left(2KT\right) \right) $ \\
\hline
\hline
UCBEV		&$\exp\left(-\dfrac{1}{512}\frac{T-2K}{H_{\sigma,1}} + \log\left(6KT\right)\right)$ \\
%\midrule
\hline
\hline
APT         &$\exp\left(-\dfrac{T}{64 H_1}+2\log((\log(T)+1)K)\right)$ \\
% \midrule
\hline
\hline
CSAR		&$\exp\left(-\dfrac{T-K}{72\log(K)H_{CSAR,2}}+2\log(K)\right)$ \\
%\midrule
\hline

%\bottomrule
\end{tabular}
\end{center}
\end{table}

Our theoretical contribution comprises 
 proving an upper bound on the expected loss incurred by AugUCB (Theorem~\ref{tbandit:Result:Theorem:1}).
In Table \ref{tab:regret-bds} we compare the upper bound on the losses incurred by the various algorithms, including AugUCB. The terms $H_1, H_2$, $H_{CSAR,2}, H_{\sigma,1}$ and $H_{\sigma,2}$ represent various problem complexities, and are as defined in Section~\ref{tbandit:results}. From Section~\ref{tbandit:results} we note that, for all $K\ge8$, we have
\begin{align*}
\log\left(K\log K\right) H_{\sigma,2} > \log(2K) H_{\sigma,2} \ge H_{\sigma,1}.
\end{align*}
%; relation between these quantities are also given in Section~\ref{results} 
%The term containing $H_{\sigma,2}$ is comparable to the similar terms (containing $H_{\sigma,1}$) for the error probability of GapE-V \cite{gabillon2011multi} algorithm which we modify to perform in the TBP problem and name it as UCBEV.
Thus, it follows that the upper bound for UCBEV is better than that for AugUCB.
 %The error probability of UCBEV for single bandit multi-armed case is given in Table \ref{tab:regret-bds}. We see that $\log(\frac{3}{16} K\log K) H_2^{\sigma} > \log(2K) H_2^{\sigma} \ge H_1^{\sigma}$ and hence our algorithm is weaker with respect to UCBEV for single  multi-armed bandit scenario.
 However, implementation of UCBEV algorithm requires $H_{\sigma,1}$ as input, whose computation is not realistic in practice. In contrast, our AugUCB algorithm requires no such complexity factor as input. 
%Theoretically, we can compare the first term (containing $H_2$) of our expected loss and see that for all $K\geq 4$, $ H_2 \log(\frac{3}{16} K\log K) > (\log K)H_{CSAR,2}\geq H_1 $ and hence our result is weaker than CSAR and APT.

Proceeding with the comparisons, we emphasize that the upper bound for  AugUCB is, in fact, not comparable with that of APT and CSAR; this is because the complexity term $H_{\sigma,2}$ is not explicitly comparable with either $H_1$ or $H_{CSAR,2}$. However, through extensive simulation experiments we find that AugUCB significantly outperforms both APT, CSAR and other non variance-based algorithms. AugUCB also outperforms UCBEV under explorations where non-optimal values of $H_{\sigma,1}$  are used. In particular, we consider experimental scenarios comprising large number of arms, with the variances of arms in $S_\tau$ being large. AugUCB, being variance based, exhibits superior performance under these settings.  
%

%Empirically we show that for a large number of arms when the variance of the arms lying above $\tau$ are high, our algorithm performs better than all other algorithms, except the algorithm UCBEV which has access to the underlying problem complexity and also is a variance-aware algorithm. 
%
%AugUCB requires one input parameter and the exact choice for the parameter is derived in Theorem \ref{Result:Theorem:1}. Also, unlike SAR or CSAR, AugUCB does not have explicit accept or reject sets rather the arm elimination condition simply removes arm(s) if it is sufficiently sure that the mean of the arms are very high or very low about the threshold based on mean and variance estimation thereby re-allocating the remaining budget among the surviving arms. This although is a tactic similar to SAR or CSAR, but here at any round, an arbitrary number of arms can be accepted or rejected thereby improving upon SAR and CSAR which accepts/rejects one arm in every round. Also their round lengths are non-adaptive and they pull all the arms equal number of times in each round. 
%At every timestep AugUCB pulls the arm that minimizes thereby making this an anytime algorithm whereby we need not finish every round. 
%Irrespective of this case AugUCB also employs elimination of arms based on mean estimation only and is the first such algorithm which uses elimination by both mean and variance estimation simultaneously.

The remainder of the paper is organized as follows. In section \ref{tbandit:algorithm} we present our AugUCB algorithm. 
Section \ref{tbandit:results} contains our main theorem on expected loss, while section \ref{tbandit:expt} contains simulation experiments. We finally draw our conclusions in section \ref{tbandit:conclusion}.
%in section \ref{notation} we introduce the notations and the

### 2017-10-11 tbandit/expt.tex
Latest on 11/10/2017

In this section, we empirically compare the  performance of AugUCB against APT, UCBE, UCBEV, CSAR and the uniform-allocation (UA) algorithms. A brief note about these algorithms are as follows:
%\begin{itemize}

$\bullet$ APT: This algorithm is from \cite{locatelli2016optimal}; we set $\epsilon=0.05$, which is the margin-of-error within which APT suggests the set of good arms.

$\bullet$ AugUCB: This is the Augmented-UCB algorithm proposed in this paper; as in Theorem \ref{Result:Theorem:1} we set $\rho=\frac{1}{3}$.

$\bullet$ UCBE: This is a modification of the algorithm in \cite{audibert2009exploration} (as it was originally proposed for the best arm identification problem); here, we set $a=\frac{T-K}{H_1}$, and at each time-step an arm $i\in\argmin\left\lbrace |\hat{r}_{i} -\tau|-\sqrt{\frac{a}{n_{i}}} \right\rbrace$ is pulled.

$\bullet$ UCBEV: This is a modification of the algorithm in \cite{gabillon2011multi} (proposed for the TopM problem); its implementation is identical to UCBE, but with $a = \frac{T-2K}{H_{\sigma,1}}$. As mentioned earlier, note that UCBEV's implementation would not be possible in real scenarios, as it requires computing the problem complexity $H_{\sigma,1}$. However, for theoretical reasons we show the best performance achievable by UCBEV. In experiment 6 we perform further explorations of UCBEV with alternate settings of $a$.

$\bullet$ CSAR:  Modification of the successive-reject algorithm in \cite{chen2014combinatorial}; here, we reject the arm farthest from $\tau$ after each round.

$\bullet$ UA: The naive strategy where at each time-step an arm is uniformly sampled from $\mathcal{A}$ (the set of all arms); however, UA is known to be optimal if all arms are equally difficult to classify. 
%\end{itemize}

%We also implement the uniform-allocation (labeled UA) strategy,  CSAR is modified for the TBP setting such that it behaves as a Successive Reject algorithm whereby it rejects the arm farthest from $\tau$ after each round.
%Similarly we modify the UCBE \cite{audibert2009exploration} and UCBEV \cite{gabillon2011multi} algorithms  (originally proposed for single best arm and TopM identification problems, respectively) to suit the TBP setting. 
%%to \cite{locatelli2016optimal} to suit the goal of finding arms above the threshold $\tau$. 
%Following  \cite{locatelli2016optimal} the exploration parameter $a$ in UCBE is set to $a=\frac{T-K}{H_1}$, while for UCBEV we set $a = \frac{T-2K}{H_{\sigma,1}}$. Then, at each time-step $t=1,2,..,T$ we pull the arm that minimizes
% $\lbrace |\hat{r}_{i} -\tau|-\sqrt{\frac{a}{n_{i}}} \rbrace$, where $a$ is set as mentioned above for UCBE and UCBEV respectively. Finally, for AugUCB we take $\rho=\frac{1}{3}$ as in  Theorem \ref{Result:Theorem:1}.

%Again, for UCBEV, following \cite{gabillon2011multi}, we modify it such that the exploration parameter $a = \frac{T-2K}{H_{\sigma,1}}$. Then for each timestep $t=1,2,..,T$ we pull the arm that minimizes $\lbrace |\hat{r}_{i} -\tau|-\sqrt{\frac{a}{n_{i}}} \rbrace$, where $n_{i}$ is the number of times the arm $i$ is pulled till $t-1$ timestep and $a$ is set as mentioned above for UCBE and UCBEV respectively. Also, APT is run with $\epsilon=0.05$, which denotes the precision with which the algorithm suggests the best set of arms and we modify CSAR as per \cite{locatelli2016optimal} such that it behaves as a Successive Reject algorithm whereby it rejects the arm farthest from $\tau$ after each phase. For AugUCB we take $\rho_{\mu}=\frac{1}{8}$ and $\rho_v=\frac{1}{3}$ as in Theorem \ref{Result:Theorem:1}. In all the testbeds AugUCB, APT, CSAR, Uniform Allocation, UCBE and UCBEV are run with the same settings as mentioned above.

\noindent
Motivated by the settings considered in \cite{locatelli2016optimal}, 
we design six different experimental scenarios that are obtained by varying the arm means and variances. 
%We conduct a set of six experiments with different reward means and variances. 
Across all experiments consists of $K=100$  arms (indexed $i=1,2,\cdots,100$) of which ${S}_\tau=\{6,7,\cdots,10\}$, where we have fixed $\tau=0.5$.
%in all the experiments, the threshold $\tau$ is set to $0.5$. %for all experiments. 
%Also, the number of arms in each experiment is $K=100$ , of which $\lbrace 6,7,8,9,10 \rbrace$ arms have their reward means above $\tau$. 
In all the experiments, each algorithm is run independently for $10000$ time-steps. At every time-step, the output set,  $\hat{S}_\tau$, suggested by each algorithm is recorded; the output is counted as an error if $\hat{S}_\tau\ne S_\tau$. In Figure~1, for each experiment, we have reported the percentage of error incurred by the different algorithms as a function of time; Error percentage is obtained by repeating each experiment independently  for $500$ iterations, and then respectively computing the fraction of errors. The details of the considered experiments are as follows.

%that is obtained by computing the fraction of errors when   The experiment is repeated for $500$ independent iterations, and the average error percentage is plotted against the $10000$ time-steps.

 %The output is considered erroneous if the correct set of arms is not $i=\lbrace 6,7,8,9,10 \rbrace$ (true for all the experiments). The error percentage over $500$ runs is plotted against $10000$ timesteps.

 %For the uniform allocation algorithm, for each $t=1,2,..,T$ the arms are sampled uniformly.

%Also we run AugUCBM with arm elimination just by mean estimation and AugUCBV with arm elimination just by variance estimation. For AugUCBM, at every timestep we pull arm that minimizes $i\in\argmin_{j\in B_{m}}\bigg\lbrace |\hat{r}_{j} - \tau | - 2c_{j}\bigg\rbrace$ while for AugUCBV we pull arm that minimizes $i\in\argmin_{j\in B_{m}}\bigg\lbrace |\hat{r}_{j} - \tau | - 2s_{j}\bigg\rbrace$.

%	The first experiment is conducted on a testbed of $100$ arms involving

\textbf{Experiment-1:} The reward distributions are Gaussian with  means  $r_{1:4}=0.2+(0:3)\cdot0.05$, $r_{5}=0.45$, $r_{6}=0.55$, $r_{7:10}=0.65+(0:3)\cdot0.05$ and $r_{11:100}=0.4$. Thus, the means of the first $10$ arms follow an arithmetic progression. The remaining arms have identical means; this setting is chosen because now a significant budget is required in exploring these arms, thus increasing the problem complexity.

 The corresponding variances are $\sigma_{1:5}^{2}=0.5$ and $\sigma_{6:10}^{2}=0.6$, while $\sigma_{11:100}^{2}$ is chosen independently and uniform in the  interval $[0.38,0.42]$;
% Then $\sigma_{11:100}^{2}$ is chosen uniform randomly between $0.38-0.42$.
note that, the variances of the arms in $S_\tau$ are higher than those of the other arms.
% The means in the testbed are chosen in such a way that any algorithm has to spend a significant amount of budget to explore all the arms and variance is chosen in such a way that the arms above $\tau$ have high variance whereas arms below $\tau$ have lower variance. 
 The corresponding  results are shown in Figure \ref{Fig:budgetExpt1},
 from where we see that UCBEV, which has access to the problem complexity while being variance-aware, outperforms all other algorithm (including UCBE which also has access to the problem complexity but does not take into account the variances of the arms).  Interestingly, the performance of our AugUCB (without requiring any complexity input) is comparable with UCBEV, while it 
   % with the said parameters 
 outperforms UCBE, APT and the other non variance-aware algorithms that we have considered. 	
%AugUCBM with just mean estimation performs worse than AugUCB or AugUCBV, which have a matching performance in this setup.

\begin{figure}[th!]
    \centering
    \begin{tabular}{cc}
    \subfigure[0.32\textwidth][Expt-$1$: Arithmetic Progression (Gaussian)]
    {
    		\pgfplotsset{
		tick label style={font=\Large},
		label style={font=\Large},
		legend style={font=\Large},
		}
        \begin{tikzpicture}[scale=0.6]
      	\begin{axis}[
		xlabel={Time-step},
		ylabel={Error Percentage},
		grid=major,
        %clip mode=individual,grid,grid style={gray!30},
        clip=true,
        %clip mode=individual,grid,grid style={gray!30},
  		legend style={at={(0.5,1.3)},anchor=north, legend columns=3} ]
      	% UCB
		\addplot table{tbandit/results/budgetTestAP/APT12_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestAP/AugUCBV1_comp_subsampled.txt};
		%\addplot table{results/budgetTestAP/AugUCBV_1_13_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestAP/UCBEM1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestAP/UCBEMV1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestAP/SR1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestAP/UA1_comp_subsampled.txt};
		%\addplot table{results/budgetTestAP/AugUCBM12_comp_subsampled.txt};
		%\addplot table{results/budgetTestAP/AugUCBV1_comp_subsampled.txt};
      	%\legend{APT,AugUCB,UCBE,UCBEV,CSAR,Unif Alloc,AugUCBM,AugUCBV}
      	\legend{APT,AugUCB,UCBE,UCBEV,CSAR,UA}
      	\end{axis}
      	\end{tikzpicture}
  		\label{Fig:budgetExpt1}
    }
    &
    \subfigure[0.32\textwidth][Expt-$2$: Geometric Progression (Gaussian)]
    {
    	\pgfplotsset{
		tick label style={font=\Large},
		label style={font=\Large},
		legend style={font=\Large},
		}
        \begin{tikzpicture}[scale=0.6]
        \begin{axis}[
		xlabel={Time-step},
		ylabel={Error Percentage},
        %clip mode=individual,grid,grid style={gray!30},
		grid=major,
		clip=true,
  		legend style={at={(0.5,1.3)},anchor=north, legend columns=3} ]
        % UCB
		\addplot table{tbandit/results/budgetTestGP/APT12_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGP/AugUCBV1_comp_subsampled.txt};
		%\addplot table{results/budgetTestGP/AugUCBV_1_13_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGP/UCBEM1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGP/UCBEMV1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGP/SR1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGP/UA1_comp_subsampled.txt};
		%\addplot table{results/budgetTestGP/AugUCBM12_comp_subsampled.txt};
		%\addplot table{results/budgetTestGP/AugUCBV1_comp_subsampled.txt};
        %\legend{APT,AugUCB,UCBE,UCBEV,CSAR,Unif Alloc,AugUCBM,AugUCBV}
        \legend{APT,AugUCB,UCBE,UCBEV,CSAR,UA}
      	\end{axis}
      	\label{Fig:budgetExpt2}
        \end{tikzpicture}
    }
    \end{tabular}

	\begin{tabular}{cc}
	\centering
    \subfigure[0.32\textwidth][Expt-$3$: Three Group Setting (Gaussian)]
    {
    		\pgfplotsset{
		tick label style={font=\Large},
		label style={font=\Large},
		legend style={font=\Large},
		}
        \begin{tikzpicture}[scale=0.6]
        \begin{axis}[
		xlabel={Time-step},
		ylabel={Error Percentage},
        %clip mode=individual,grid,grid style={gray!30},
       	grid=major,
       	clip=true,
  		legend style={at={(0.5,1.3)},anchor=north, legend columns=3} ]
      	% UCB
		\addplot table{tbandit/results/budgetTestGR1/APT1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR1/AugUCB1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR1/UCBEM1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR1/UCBEMV1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR1/SR1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR1/UA1_comp_subsampled.txt};
        \legend{APT,AugUCB,UCBE,UCBEV,CSAR,UA}
      	\end{axis}
      	\end{tikzpicture}
   		\label{Fig:budgetExpt3} 
    }
    &
    \subfigure[0.32\textwidth][Expt-$4$: Two Group Setting (Gaussian) ]
    {
    	\pgfplotsset{
		tick label style={font=\Large},
		label style={font=\Large},
		legend style={font=\Large},
		}
        \begin{tikzpicture}[scale=0.6]
        \begin{axis}[
		xlabel={Time-step},
		ylabel={Error Percentage},
        %clip mode=individual,grid,grid style={gray!30},
		grid=major,
		clip=true,
  		legend style={at={(0.5,1.3)},anchor=north, legend columns=3} ]
        % UCB
		\addplot table{tbandit/results/budgetTestGR2/APT1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR2/AugUCBV1_comp_subsampled.txt};
		%\addplot table{results/budgetTestGP/AugUCBV_1_13_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR2/UCBEM1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR2/UCBEMV1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR2/SR1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR2/UA1_comp_subsampled.txt};
		%\addplot table{results/budgetTestGP/AugUCBM12_comp_subsampled.txt};
		%\addplot table{results/budgetTestGP/AugUCBV1_comp_subsampled.txt};
        %\legend{APT,AugUCB,UCBE,UCBEV,CSAR,Unif Alloc,AugUCBM,AugUCBV}
        \legend{APT,AUgUCB,UCBE,UCBEV,CSAR,UA}
        %\legend{APT,AugUCB,UCBE,UCBEV,CSAR,Unif Alloc}
      	\end{axis}
      	\label{Fig:budgetExpt4}
        \end{tikzpicture}
    }
    \end{tabular}

	\begin{tabular}{cc}
    \subfigure[0.32\textwidth][Expt-$5$: Two Group Setting (Advance) ]
    {
    	\pgfplotsset{
		tick label style={font=\Large},
		label style={font=\Large},
		legend style={font=\Large},
		}
        \begin{tikzpicture}[scale=0.6]
        \begin{axis}[
		xlabel={Time-step},
		ylabel={Error Percentage},
        %clip mode=individual,grid,grid style={gray!30},
		grid=major,
		clip=true,
  		legend style={at={(0.5,1.3)},anchor=north, legend columns=3} ]
        % UCB
		\addplot table{tbandit/results/budgetTestGR4/APT1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR4/AugUCB1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR4/UCBEM1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR4/UCBEMV1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR4/SR1_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR4/UA1_comp_subsampled.txt};
        \legend{APT,AUgUCB,UCBE,UCBEV,CSAR,UA}
      	\end{axis}
      	\label{Fig:budgetExpt5}
        \end{tikzpicture}
    }
    &
    \subfigure[0.32\textwidth][Expt-$6$: Two Group Setting (Advance) ]
    {
    	\pgfplotsset{
		tick label style={font=\Large},
		label style={font=\Large},
		legend style={font=\Large},
		}
        \begin{tikzpicture}[scale=0.6]
        \begin{axis}[
		xlabel={Time-step},
		ylabel={Error Percentage},
        %clip mode=individual,grid,grid style={gray!30},
		grid=major,
		clip=true,
  		legend style={at={(0.5,1.3)},anchor=north, legend columns=2} ]
        % UCB
		\addplot table{tbandit/results/budgetTestGR3/testUCBEMV1_0.25_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR4/AugUCB1_comp_subsampled.txt};
		%\addplot table{results/budgetTestGP/AugUCBV_1_13_comp_subsampled.txt};
		%\addplot table{results/budgetTestGR3/testUCBEMV1_0.25_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR3/testUCBEMV1_256_comp_subsampled.txt};
		\addplot table{tbandit/results/budgetTestGR4/UCBEMV1_comp_subsampled.txt};
		%\addplot table{results/budgetTestGR3/testUCBEMV1_64_comp_subsampled.txt};
		%\addplot table{results/budgetTestGP/AugUCBM12_comp_subsampled.txt};
		%\addplot table{results/budgetTestGP/AugUCBV1_comp_subsampled.txt};
        %\legend{APT,AugUCB,UCBE,UCBEV,CSAR,Unif Alloc,AugUCBM,AugUCBV}
        \legend{UCBEV($0.25$), AugUCB, UCBEV($256$), UCBEV($1$)}
        %\legend{UCBEV($0.06$),AUgUCB,UCBEV($0.25$),UCBEV($1$),UCBEV($64$),UCBEV($256$)}
        %\legend{APT,AugUCB,UCBE,UCBEV,CSAR,Unif Alloc}
      	\end{axis}
      	\label{Fig:budgetExpt6}
        \end{tikzpicture}
    }
    \end{tabular}
    \caption{Performances of the various TBP algorithms in terms of error percentage vs. time-step, for  six different experimental scenarios.}
    \label{fig:budgetExpt}
    \vspace{-6mm}
\end{figure}

\textbf{Experiment-2:} We again consider  Gaussian reward distributions. However, here the means of the first $10$ arms constitute a geometric progression. Formally, the reward means are $r_{1:4}=0.4-(0.2)^{1:4}$, $r_{5}=0.45$, $r_{6}=0.55$, $r_{7:10}=0.6+(0.2)^{5-(1:4)}$ and $r_{11:100}=0.4$; the arm variances are as in experiment-$1$. The corresponding results are shown in Figure \ref{Fig:budgetExpt2}.  We again observe AugUCB outperforming the other algorithms, except UCBEV.

\textbf{Experiment-3:} Here, the first
$10$ arms are partitioned into three groups, with all arms in a group being assigned the same mean; the reward distributions are again Gaussian. Specifically, the reward means are $r_{1:3}=0.1$, $r_{4:7}=\lbrace 0.35, 0.45, 0.55, 0.65\rbrace$ and $r_{8:10}=0.9$; as before,  $r_{11:100}=0.4$ and all the variances are as in Experiment-$1$. The results for this scenario are presented in Figure \ref{Fig:budgetExpt3}. The observations are inline with those made in the previous experiments.

\textbf{Experiment-4:} The setting is similar to that considered in Experiment-3, but with the first $10$ arms partitioned into two groups; the respective means are $r_{1:5}=0.45$, $r_{6:10}=0.55$. The corresponding results are shown in Figure \ref{Fig:budgetExpt4}, from where the good performance of AugUCB is again validated.

\textbf{Experiment-5:} This is again the two group setting involving Gaussian reward distributions. The reward means are as in Experiment-4, while the variances are  $\sigma_{1:5}^{2}=0.3$ and $\sigma_{6:10}^{2}=0.8$;  $\sigma_{11:100}^{2}$ are independently and uniformly chosen in the interval $[0.2,0.3]$.  The corresponding results are shown in Figure \ref{Fig:budgetExpt5}.
 We refer to this setup as \emph{Advanced} because here the chosen variance values are such that only  variance-aware algorithms will perform well.Hence, we see that UCBEV performs very well in comparison with the other algorithms. However,  it is interesting to note that the performance of  AugUCB catches-up with UCBEV as the time-step increases, while significantly outperforming the other non-variance aware algorithms.

\textbf{Experiment-6:} We use the same setting as in Experiment-5, but conduct more exploration of UCBEV with different values of the exploration parameter $a$. The corresponding results are shown in Figure \ref{Fig:budgetExpt6}. As studied in \cite{locatelli2016optimal}, we implement UCBEV with $ a_{i} = 4^{i} \frac{T-2K}{H_{\sigma,1}}$ for $i = -1,0,4$. Here, $a_{0}$ corresponds to UCBEV($1$) (in Figure \ref{Fig:budgetExpt6}) which is UCBEV run with the optimal choice of $H_{\sigma ,1}$. For other choices of $a_i$ we see that UCBEV($a_i$) is significantly outperformed by AugUCB.

Finally, note that in all the above experiments, the CSAR algorithm, although performs well initially, quickly exhausts its budget and saturates at a higher error percentage. This is because it pulls all arms equally in each round, with the round lengths being non-adaptive.

### 2017-10-11 tbandit/ijcai17.tex
Latest on 11/10/2017

%%%% ijcai17.tex

\typeout{IJCAI-17 Instructions for Authors}

% These are the instructions for authors for IJCAI-17.
% They are the same as the ones for IJCAI-11 with superficical wording
%   changes only.

\documentclass{article}
% The file ijcai17.sty is the style file for IJCAI-17 (same as ijcai07.sty).
\usepackage{ijcai17}

% Use the postscript times font!
\usepackage{times}

\usepackage{macros}

\usepackage{latexsym}

\title{Thresholding Bandits with Augmented UCB}
%\author{Author names withheld}

\author{Subhojyoti Mukherjee${}^1$, K. P. Naveen${}^2$, Nandan
Sudarsanam${}^3$, Balaraman Ravindran${}^1$\\
${}^1$Department of Computer Science \& Engineering,\\ ${}^2$Department of Electrical Engineering,
${}^3$Department of Management Studies,\\ Indian Institute of
Technology Madras}

\begin{document}
\maketitle

\vspace*{2mm}
\begin{abstract}
In this paper we propose the Augmented-UCB (AugUCB) algorithm for a fixed-budget version of the thresholding bandit problem (TBP), where the objective is to identify a set of arms whose quality is above a threshold. A key feature of AugUCB is that it uses both mean and variance estimates to eliminate arms that have been sufficiently explored; to the best of our knowledge this is the first algorithm to employ such an approach for the considered TBP.  Theoretically, we obtain an upper bound on the loss (probability of mis-classification) incurred by AugUCB. Although UCBEV in literature provides a better guarantee, it is important to emphasize that UCBEV has access to problem complexity (whose computation requires arms' mean and variances), and hence is not realistic in practice; this is in contrast to AugUCB whose implementation does not require any such complexity inputs. We conduct extensive simulation experiments to validate the performance of AugUCB. Through our simulation work, we establish that AugUCB, owing to its utilization of variance estimates, performs significantly better than the state-of-the-art APT, CSAR and other non variance-based algorithms.
\end{abstract}

%\begin{keywords}
%Multi-Armed Bandit, Regret, Exploration-exploitation, UCB
%\end{keywords}

\section{Introduction}
\label{intro}
\input{intro}
%\subsection{Motivation}
%\label{motivation}
\input{motivation}
\subsection{Related Work}
\label{prevRes}
\input{prevRes}

\subsection{Our Contribution}
\label{contribution}
\input{contribution}
%
%\section{Notation Used and Assumptions}
%\label{notation}
%\input{notation}
%
%
\vspace*{-1em}
\section{Augmented-UCB Algorithm}
\label{algorithm}
\input{algo}
%
\vspace{-2mm}
\section{Theoretical Results}
\label{results}
\input{results}
%
%
%\vspace{-1em}
\vspace{-5mm}
\section{Numerical Experiments}
\label{expt}
\input{expt}
%
%\vspace{-1.2em}
\vspace{-1mm}
\section{Conclusion}
\label{conclusion}
\input{conclusion}

% Acknowledgments---Will not appear in anonymized version
%\acks{We thank a bunch of people.}

%\clearpage
%\newpage
%\bibliographystyle{named}
%\bibliography{ijcai17}

%\clearpage
%\newpage
%\section{Appendix}
%\label{appendix}
%\input{appendix}

\end{document}

### 2017-10-11 tbandit/intro.tex
Latest on 11/10/2017

Stochastic multi-armed bandit (MAB) problems are instances of the classic sequential decision-making scenario; specifically an MAB problem comprises of a learner and a collection of actions (or arms), denoted $\mathcal{A}$. In each trial the learner plays (or pulls) an arm $i\in\mathcal{A}$ which yields independent and identically distributed (i.i.d.) reward samples from a distribution (corresponding to arm $i$), whose expectation is denoted by $r_i$. 
%whose rewards are  samples from the distribution specific to the arm $i\in A$ and whose expected reward is denoted by $r_{i},\forall i\in A$. 
The learner's objective is to identify an arm corresponding to the maximum expected reward, denoted $r^{*}$. Thus, at each time-step the learner 
%selects an arm $i$ and hence
is faced with the \emph{exploration vs.\ exploitation dilemma}, where it can pull an arm which has yielded the highest mean reward (denoted $\hat{r}_{i}$) thus far (\emph{exploitation}) or continue to explore other arms with the prospect of finding a better arm 
%superior performance 
whose performance has not been observed sufficiently (\emph{exploration}).

%In the stochastic multi-armed bandit setting a learning agent is required to choose from a set of decisions or arms at every round. The agent is then presented with a reward for that round, which is an independent draw from a stationary distribution specific to the arm selected. The agent, however, does not know the mean of the distributions associated with each arm, denoted by $r_{i}$, including the optimal arm which will give it the best reward, denoted by $r^{*}$. The agent attempts to make arm choices that will maximize some performance measure by keeping track of the reward that has been gathered from previous selections of the arm, for each arm. This is called the estimated mean reward of an arm denoted by $\hat{r}_{i}$. The bandit problem can be conceptualized as a sequential decision making process where the agent is at each round presented with an \emph{exploration-exploitation dilemma}. The agent could pull the arm which has the highest observed mean reward till now (exploitation) or to explore other arms, with the prospect of finding superior performance which was previously unobserved (exploration).

%
%	Formally, let $r_i$, $i=1,\ldots,K$ denote the mean rewards of the $K$ arms and $r^* = \max_i r_i$ the optimal mean reward. The objective in some of the stochastic bandit problem is to minimize the cumulative regret, which is defined as follows:
%\begin{align*}
%R_{T}=r^{*}T - \sum_{i\in A} r_{i}N_{i}(T),
%\end{align*}
%where $T$ is the number of rounds, $N_{i}(T)=\sum_{m=1}^T I(I_m=i)$ is the number of times the algorithm chose arm $i$ up to round $T$.
%The expected regret of an algorithm after $T$ rounds can be written as,
%
%\begin{align*}
%\E[R_{T}]= \sum_{i=1}^K \E[N_i(T)] \Delta_i,
%\end{align*}
%where $\Delta_{i}=r^{*}-r_{i}$ denotes the gap between the means of the optimal arm and of the $i$-th arm.

Pure-exploration MAB problems are unlike their traditional (exploration vs.\ exploitation)  counterparts where the  objective is to minimize the cumulative regret (which is the total loss incurred by the learner for not playing the optimal arm throughout the time horizon $T$). Instead, in pure-exploration problems a learning algorithm, until time $T$, can invest entirely on exploring the arms without being concerned about the loss incurred while exploring; the objective is to minimize the probability that the arm recommended at time $T$ is not the best arm.  In this paper, we further consider a combinatorial version of the pure-exploration MAB, called the thresholding bandit problem (TBP).  Here, the learning algorithm is provided with a threshold $\tau$, and the objective, after exploring for $T$ rounds, is to  output all arms $i$ whose $r_{i}$ is above $\tau$. 
It is important to emphasize that the \emph{thresholding} bandit problem is different from the \emph{threshold} bandit setup studied in \cite{abernethy2016threshold}, where the learner receives an unit reward whenever the value of an observation is above a threshold.

%%%%%%%%%%%%%%%
% Old para
%%%%%%%%%%%%%%%
%Pure-exploration problems are unlike their traditional (exploration vs.\ exploitation) counterparts where the  objective is to minimize the cumulative regret, which is the total loss incurred by the learner for not playing the optimal arm throughout the time horizon $T$. Instead, in the pure exploration setup the learning algorithm is provided with a threshold $\tau$, and the objective, after exploring for $T$ rounds, is to  output all arms $i$ whose $r_{i}$ is above $\tau$. Thus, the learning algorithm, until  time $T$, can invest entirely on exploring the arms  without being concerned about the loss incurred while exploring. It is important to emphasize that the \emph{thresholding bandit} problem is different from the \emph{threshold bandit} setup studied in \cite{abernethy2016threshold}, where the learner receives an unit reward whenever the value of an observation is above a threshold. 
%<<<<<<< Updated upstream
%Pure-exploration problems are unlike their traditional (exploration vs.\ exploitation) counterparts where the  objective is to minimize the cumulative regret, which is the total loss incurred by the learner for not playing the optimal arm throughout the time horizon $T$. In this paper we study the fixed-budget setting of a specific combinatorial pure-exploration problem, called the thresholding bandit problem (TBP), in the context of (MAB) setting. In this pure-exploration setup the learning algorithm is provided with a threshold $\tau$, and the objective, after exploring for $T$ rounds, is to  output all arms $i$ whose $r_{i}$ is above $\tau$. Thus, the learning algorithm, until time $T$, can invest entirely on exploring the arms  without being concerned about the loss incurred while exploring. It is important to emphasize that the \emph{thresholding} bandit problem is different from the \emph{threshold} bandit setup studied in \cite{abernethy2016threshold}, where the learner receives an unit reward whenever the value of an observation is above a threshold. 
%=======

%Pure-exploration problems are unlike their traditional (exploration vs.\ exploitation) counterparts where the  objective is to minimize the cumulative regret, which is the total loss incurred by the learner for not playing the optimal arm throughout the time horizon $T$. Instead, in the pure exploration setup the learning algorithm is provided with a threshold $\tau$, and the objective, after exploring for $T$ rounds, is to  output all arms $i$ whose $r_{i}$ is above $\tau$. Thus, the learning algorithm, until  time $T$, can invest entirely on exploring the arms  without being concerned about the loss incurred while exploring. It is important to emphasize that the \emph{thresholding bandit} problem is different from the \emph{threshold bandit} setup studied in \cite{abernethy2016threshold}, where the learner receives an unit reward whenever the value of an observation is above a threshold. 
%>>>>>>> Stashed changes

% reward on each time-step depends on a threshold value and the learner receives the reward only if the reward is above the threshold.

%This is a specific instance of combinatorial pure exploration where the learning algorithm can explore as much as possible given a fixed horizon $T$ and not be concerned with the usual exploration-exploitation dilemma.

Formally, the problem we consider is the following. First, we define the set $S_{\tau}=\lbrace i\in \mathcal{A}: r_{i}\geq \tau \rbrace$. Note that, $S_\tau$ is the set of all arms whose reward mean is greater than $\tau$. Let 
$S_\tau^c$ % =\mathcal{A}\backslash S_\tau$
 denote the complement of $S_\tau$, i.e.,  $S_{\tau}^{c}=\lbrace i\in \mathcal{A}: r_{i} < \tau \rbrace$. Next, let $\hat{S}_{\tau}=\hat{S}_{\tau}(T)\subseteq \mathcal{A}$ denote the recommendation of a learning algorithm (under consideration) after $T$ time units of exploration, while $\hat{S}_{\tau}^c$ denotes its complement.
%  Also we define $\hat{S}_{\tau}=\hat{S}_{\tau}(T)\subset \mathcal{A}$ and its complementary set $\hat{S}_{\tau}^{C}$ as the recommendation of the learning algorithm after $T$ rounds. 
% Given such sets exists, 
The performance of the learning agent is measured by the accuracy with which it can classify the arms into $S_{\tau}$ and $S_{\tau}^{c}$ after time horizon $T$. Equivalently, using $\mathbb{I}(E)$ to denote the indicator of an event $E$, the \emph{loss} $\mathcal{L}(T)$ is defined as
\begin{align*}
\Ls (T) = \mathbb{I}\big(\lbrace S_{\tau}\cap \hat{S}_{\tau}^{c}\neq \emptyset\rbrace    \cup    \lbrace\hat{S}_{\tau}\cap S_{\tau}^{c}\neq \emptyset\rbrace\big).
\end{align*}			
Finally, the goal of the learning agent is to minimize the expected loss:
% So, the expected loss after $T$ rounds is,
\begin{align*}
\E[\Ls(T)] = \Pb\big(\lbrace S_{\tau}\cap \hat{S}_{\tau}^{c} \neq \emptyset \rbrace  \cup   \lbrace \hat{S}_{\tau}\cap S_{\tau}^{c} \neq \emptyset\rbrace\big).
\end{align*}
Note that the expected loss is simply the \emph{probability of mis-classification} (i.e., error), that occurs either if a good arm is rejected or a bad arm is accepted as a good one.
% (represented by the events $\lbrace S_{\tau}\cap \hat{S}_{\tau}^{c} \neq \emptyset \rbrace$ and $\lbrace \hat{S}_{\tau}\cap S_{\tau}^{c} \neq \emptyset\rbrace$, respectively).

%which we can say is the probability of making mistake, that is whether the learning agent at the end of round $T$ rejects arms from $S_{\tau}$ or accepts arms from $S_{\tau}^{C}$ in its final recommendation.

%Also, we are looking at an anytime algorithm, so the knowledge of $T$ may not be known to the learner.

### 2017-10-11 tbandit/notation.tex
Latest on 11/10/2017

\textbf{Notation and assumptions:} $\mathcal{A}$ denotes the set of arms, and $|\mathcal{A}|=K$ is the number of arms in $\mathcal{A}$. 
%Arms generic arm is indexed by $i,j\in\mathcal{A}$. 
For arm $i\in\mathcal{A}$, we use $r_{i}$ to denote the true mean of the distribution from which the rewards are sampled, while $\hat{r}_{i}(t)$ denotes the estimated mean at time $t$. Formally, using $n_i(t)$ to denote the number of times arm $i$ has been pulled until time $t$, we have $\hat{r}_{i}(t)=\frac{1}{n_{i}(t)}\sum_{z=1}^{n_i(t)} X_{i,z}$, where $X_{i,z}$ is the reward sample received when arm $i$ is pulled for the $z$-th time. %
Similarly, we use $\sigma_{i}^{2}$ to denote the true variance of the reward distribution corresponding to arm $i$, while $\hat{v}_{i}(t)$ is the estimated variance, i.e., $\hat{v}_{i}(t)=\frac{1}{n_i(t)}\sum_{z=1}^{n_{i}(t)}(X_{i,z}-\hat{r}_{i})^{2}$. Whenever there is no ambiguity about the underlaying  time index $t$, for simplicity we neglect $t$ from the notations and simply use  $\hat{r}_i, \hat{v}_i,$ and $n_i, $ to denote the respective quantities.  Let  $\Delta_{i}=|\tau-r_{i}|$ denote the distance of the true mean from the threshold $\tau$. Also, the rewards are assumed to take values in $[0,1]$.

%%%%%%%%%%
%1-sub-gaussian assumption removed
%%%%%%%%%%
%Along the lines of \cite{locatelli2016optimal} we assume that all the reward distributions are $1$-sub-Gaussian (note that,  $1$-sub-Gaussian includes Gaussian distributions with variance less than $1$, distributions supported on an interval of length less than 2, etc).

### 2017-10-11 tbandit/prevRes.tex
Latest on 11/10/2017

Significant amount of literature is available on the stochastic MAB setting with respect to minimizing the cumulative regret. While the seminal work of \cite{robbins1952some}, \cite{thompson1933likelihood},  and \cite{lai1985asymptotically} prove asymptotic lower bounds on the cumulative regret, the more recent work of \cite{auer2002finite} propose the UCB1 algorithm that provides finite time-horizon guarantees. Also, subsequent work such as \cite{audibert2009minimax} and \cite{auer2010ucb} have improved the upper bounds on the cumulative regret. The authors in \cite{auer2010ucb} have proposed a \emph{round-based}\footnote{An algorithm is said to be \textit{round-based} if it pulls all the arms equal number of times in each round, and then proceeds to eliminate one or more arms that it identifies to be sub-optimal.} version of the UCB algorithm, referred to as UCB-Improved. Of special mention is the work of \cite{audibert2009exploration} where the authors have introduced a \emph{variance-aware} UCB algorithm, referred to as UCB-V; it is shown that the algorithms that take into account variance estimation along with mean estimation tends to perform better than the algorithms that solely focuses on mean estimation, for instance, such as UCB1.
For a more detail survey of literature on UCB algorithms, we refer the reader to \cite{bubeck2012regret}.

%An early work involving a bandit setup is \cite{thompson1933likelihood}, where the author deals with the problem of choosing between two treatments to administer on patients who come in sequentially. Following the seminal work of  \cite{robbins1952some}, bandit algorithms have been extensively studied in a variety of applications. From a theoretical standpoint, an asymptotic lower bound for the regret was established in \cite{lai1985asymptotically}. Several other works such as \cite{auer2002finite},  \cite{audibert2009minimax} and \cite{auer2010ucb} have shown results for minimizing cumulative regret in stochastic bandit setup whereas works such as \cite{auer2002nonstochastic} have concentrated on adversarial bandit setup.

%	In the pure exploration setup, a significant amount of research has been done on finding the best arm(s) from a set of arms.

In this work we are particularly interested in \emph{pure-exploration MABs},  where the focus in primarily on simple regret rather than the cumulative regret. The relationship between cumulative regret and simple regret is proved in \cite{bubeck2011pure} where the authors prove that minimizing the simple regret necessarily results in maximizing the cumulative regret.
The pure exploration problem has been explored  mainly under the following two settings:

	\emph{1. Fixed Budget setting:} Here the learning algorithm has to suggest the best arm(s) within a fixed time-horizon $T$, that is usually given as an input. The objective is to maximize the probability of returning the best arm(s).  This is the scenario we consider in our paper. In \cite{audibert2010best} the authors propose the  UCBE and the Successive Reject (SR) algorithm, and prove simple-regret guarantees for the problem of identifying the single best arm.  In the combinatorial fixed budget setup \cite{gabillon2011multi} propose the GapE and GapE-V algorithms that suggest, with high probability, the best $m$ 
	% (given as input)
	 arms at the end of the time budget. Similarly, \cite{bubeck2013multiple} introduce the  Successive Accept Reject (SAR) algorithm, which is an extension of the SR algorithm; SAR is a round based algorithm whereby at the end of each round an arm is either accepted or rejected (based on certain confidence conditions) until the top $m$ arms are suggested at the end of the budget with high probability. A similar combinatorial setup was explored in \cite{chen2014combinatorial} where the authors propose the Combinatorial Successive Accept Reject (CSAR) algorithm, which is similar in concept to SAR but with a more general setup.

	\emph{2. Fixed Confidence setting:} In this setting the learning algorithm has to suggest the best arm(s) with a fixed confidence (given as input) with as fewer number of attempts as possible. The single best arm identification has been studied in \cite{even2006action}, while for the combinatorial setup \cite{kalyanakrishnan2012pac} have proposed the LUCB algorithm which, on termination, returns  $m$ arms which are at least $\epsilon$ close to the true top-$m$ arms with probability at least $1-\delta$. For a detail survey of this setup we refer the reader to \cite{jamieson2014best}.

Apart from these two settings some unified approaches has also been suggested in \cite{gabillon2012best} which proposes the algorithms UGapEb and UGapEc which can work in both the above two settings. The thresholding bandit problem is a specific instance of the pure-exploration setup of \cite{chen2014combinatorial}. In the latest work of \cite{locatelli2016optimal} Anytime Parameter-Free Thresholding (APT) algorithm comes up with an improved anytime guarantee than CSAR for the thresholding bandit problem.

%	\emph{1. Fixed Budget setting:} In this setting the learning algorithm has to suggest the best arm(s) within a fixed number of attempts that is given as an input. The objective here is to maximize the probability of returning the best arm(s). One of the foremost papers to deal with single best arm identification is \cite{audibert2009exploration} where the authors come up with the algorithm UCBE and Successive Reject(SR) with simple regret guarantees. The relationship between cumulative regret and simple regret is proved in \cite{bubeck2011pure} where the authors prove that minimizing the simple regret necessarily results in maximizing the cumulative regret. In the combinatorial fixed budget setup \cite{gabillon2011multi} come up with Gap-E and Gap-EV algorithm which suggests the best $m$ (given as input) arms at the end of the budget with high probability. Similarly, \cite{bubeck2013multiple} comes up with the algorithm Successive Accept Reject(SAR) which is an extension of the SR algorithm. SAR is a round based algorithm whereby at the end of round an arm is either accepted or rejected based on certain conditions till the required top $m$ arms are suggested at the end of the budget with high probability. 
%
%	\emph{2 Fixed Confidence setting:} In this setting the the learning algorithm has to suggest the best arm(s) with a fixed (given as input) confidence with as less number of attempts as possible. The single best arm identification has been handled in \cite{even2006action} where they come up with an algorithm called Successive Elimination (SE) which comes up with an arm that is $\epsilon$ close to the optimal arm. In the combinatorial setup recently \cite{kalyanakrishnan2012pac} have suggested the LUCB algorithm which on termination returns $m$ arms which are atleast $\epsilon$ close to the true top $m$ arms with $1-\delta$ probability.
%
%	Apart from these two settings some unified approach has also been suggested in \cite{gabillon2012best} which proposes the algorithms UGapEb and UGapEc which can work in both the above two settings. A similar combinatorial setup was also explored in \cite{chen2014combinatorial} where the authors come up with more similarities and dissimilarities between these two settings in a more general setup. In their work, the learning algorithm, called Combinatorial Successive Accept Reject (CSAR) is similar to SAR with a more general setup. The thresholding bandit problem is a specific instance of the pure exploration setup of \cite{chen2014combinatorial}. In the latest work in \cite{locatelli2016optimal} the algorithm Anytime Parameter-Free Thresholding (APT) algorithm comes up with a better anytime guarantee than CSAR for the thresholding bandit problem.

### 2017-10-11 EUCBV/codes/BayesUCB.py

@@ -1,0 +1,215 @@
+'''
+Created on Oct 6, 2015
+
+@author: Subhojyoti
+'''
+
+import math
+import random
+import numpy
+from scipy import special
+from scipy.stats import beta
+#from random import betavariate
+#from scipy.special import btdtri
+import scipy
+
+class ucb1_2(object):
+    '''
+    classdocs
+    '''
+
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+
+    
+     
+    def rewards(self,choice):
+        #return random.gauss(self.means[choice],0.5)
+        return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+        
+    def ucb1(self,numActions):
+    
+        #Set the environment
+        self.numActions=numActions
+        
+        self.payoffSums = [0] * self.numActions
+        self.numPlays = [0] * self.numActions
+        self.ucbs = [0] * self.numActions
+        self.upbs = [0] * self.numActions
+        self.numRounds = 200000
+        #self.numRounds = 60000
+        #numRounds = 250000
+        
+        self.arm_reward = [0]*numActions
+        
+        #bestAction=arms/2
+        self.bestAction=self.numActions-2
+        
+        #biases = [1.0 / k for k in range(5,5+numActions)]
+        #means = [0.5 + b for b in biases]
+        self.means =[0.07 for i in range(self.numActions)]
+        
+        '''
+        i=(1*self.numActions)/3
+        while i<self.numActions:
+            self.means[i]=0.05
+            i=i+1
+        
+        i=(2*self.numActions)/3
+        while i<self.numActions:
+            self.means[i]=0.03
+            i=i+1
+        '''
+        self.means[self.bestAction]=0.1
+        
+        
+        # initialize empirical sums
+        '''
+        for i in range(self.numActions):
+            self.payoffSums[i] = self.rewards(i)
+            self.numPlays[i]=self.numPlays[i]+1
+        '''
+        
+        theta=[1.0 for i in range(self.numActions)]
+        cumulativeReward = 0
+        bestActionCumulativeReward = 0
+        self.actionRegret=[]
+
+
+        t=1
+        '''
+        for i in range(self.numActions):
+            theReward = self.rewards(i)
+            #self.numPlays[i]=self.numPlays[i]+1
+
+            action=i
+            theReward = self.rewards(action)
+            #print theReward,action
+            self.arm_reward[action]=self.arm_reward[action]+theReward
[…]

### 2017-10-11 EUCBV/codes/BayesUCB_expt2.py

@@ -1,0 +1,237 @@
+'''
+Created on Oct 6, 2015
+
+@author: Subhojyoti
+'''
+
+import math
+import random
+import numpy
+from scipy import special
+from scipy.stats import beta
+from scipy.stats import norm
+from scipy.stats import t
+#from random import betavariate
+#from scipy.special import btdtri
+import scipy
+
+class ucb1_2(object):
+    '''
+    classdocs
+    '''
+
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+
+    
+     
+    def rewards(self,choice):
+        return random.gauss(self.means[choice],self.variance[choice])
+        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+        
+    def ucb1(self,numActions):
+    
+        #Set the environment
+        self.numActions=numActions
+        
+        self.payoffSums = [0] * self.numActions
+        self.sqpayoffSums = [0] * self.numActions
+        self.numPlays = [1] * self.numActions
+        self.ucbs = [0] * self.numActions
+        self.upbs = [0] * self.numActions
+        self.numRounds = 300000
+        #self.numRounds = 60000
+        #numRounds = 250000
+        
+        self.arm_reward = [0]*numActions
+        
+        #bestAction=arms/2
+        self.bestAction=self.numActions-2
+        
+        #biases = [1.0 / k for k in range(5,5+numActions)]
+        #means = [0.5 + b for b in biases]
+        self.means =[0.01 for i in range(self.numActions)]
+        self.variance=[0.25 for i in range(self.numActions)]
+
+
+
+        for i in range(0,1*self.numActions/3):
+            self.means[i]=0.07
+            self.variance[i]=0.01
+        
+        '''
+        i=(1*self.numActions)/3
+        while i<self.numActions:
+            self.means[i]=0.05
+            i=i+1
+        
+        i=(2*self.numActions)/3
+        while i<self.numActions:
+            self.means[i]=0.03
+            i=i+1
+        '''
+        self.means[self.bestAction]=0.09
+        self.variance[self.bestAction]=0.25
+        
+        
+        # initialize empirical sums
+        '''
+        for i in range(self.numActions):
+            self.payoffSums[i] = self.rewards(i)
+            self.numPlays[i]=self.numPlays[i]+1
+        '''
+        
+        theta=[1.0 for i in range(self.numActions)]
[…]

### 2017-10-11 EUCBV/codes/BayesUCB_expt3.py

@@ -1,0 +1,244 @@
+'''
+Created on Oct 6, 2015
+
+@author: Subhojyoti
+'''
+
+import math
+import random
+import numpy
+from scipy import special
+from scipy.stats import beta
+from scipy.stats import norm
+from scipy.stats import t
+#from random import betavariate
+#from scipy.special import btdtri
+import scipy
+import fileinput
+
+class ucb1_2(object):
+    '''
+    classdocs
+    '''
+
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+
+    
+     
+    def rewards(self,choice):
+        return random.gauss(self.means[choice],self.variance[choice])
+        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+
+    def readenv(self):
+        data=[]
+        filename="env/env1.txt"
+        for line in fileinput.input([filename]):
+
+            try:
+                line1 = [line.split(", ") or line.split("\n") ]
+                #print numpy.shape(line1)
+                #print line1
+                take=[]
+                for i in range(len(line1[0])):
+                    take.append(float(line1[0][i]))
+                #print take
+                data.append(take)
+            except ValueError,e:
+                print e
+        #print data
+        self.means=(data[0])
+        self.variance=(data[1])
+        
+    def ucb1(self,numActions):
+    
+        #Set the environment
+        self.numActions=numActions
+        
+        self.payoffSums = [0] * self.numActions
+        self.sqpayoffSums = [0] * self.numActions
+        self.numPlays = [1] * self.numActions
+        self.ucbs = [0] * self.numActions
+        self.upbs = [0] * self.numActions
+        self.numRounds = 400000
+        #self.numRounds = 60000
+        #numRounds = 250000
+        
+        self.arm_reward = [0]*numActions
+        
+        #bestAction=arms/2
+        self.bestAction=self.numActions - 2
+        
+        #biases = [1.0 / k for k in range(5,5+numActions)]
+        #means = [0.5 + b for b in biases]
+
+
+
+        self.means=[]
+        self.variance=[]
+        self.readenv()
+
+        print self.means
+        
+        
+        # initialize empirical sums
+        '''
+        for i in range(self.numActions):
+            self.payoffSums[i] = self.rewards(i)
[…]

### 2017-10-11 EUCBV/codes/BayesUCB_expt4.py

@@ -1,0 +1,244 @@
+'''
+Created on Oct 6, 2015
+
+@author: Subhojyoti
+'''
+
+import math
+import random
+import numpy
+from scipy import special
+from scipy.stats import beta
+from scipy.stats import norm
+from scipy.stats import t
+#from random import betavariate
+#from scipy.special import btdtri
+import scipy
+import fileinput
+
+class ucb1_2(object):
+    '''
+    classdocs
+    '''
+
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+
+    
+     
+    def rewards(self,choice):
+        return random.gauss(self.means[choice],self.variance[choice])
+        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+
+    def readenv(self):
+        data=[]
+        filename="env/env3.txt"
+        for line in fileinput.input([filename]):
+
+            try:
+                line1 = [line.split(", ") or line.split("\n") ]
+                #print numpy.shape(line1)
+                #print line1
+                take=[]
+                for i in range(len(line1[0])):
+                    take.append(float(line1[0][i]))
+                #print take
+                data.append(take)
+            except ValueError,e:
+                print e
+        #print data
+        self.means=(data[0])
+        self.variance=(data[1])
+        
+    def ucb1(self,numActions):
+    
+        #Set the environment
+        self.numActions=numActions
+        
+        self.payoffSums = [0] * self.numActions
+        self.sqpayoffSums = [0] * self.numActions
+        self.numPlays = [1] * self.numActions
+        self.ucbs = [0] * self.numActions
+        self.upbs = [0] * self.numActions
+        self.numRounds = 400000
+        #self.numRounds = 60000
+        #numRounds = 250000
+        
+        self.arm_reward = [0]*numActions
+        
+        #bestAction=arms/2
+        self.bestAction=self.numActions - 2
+        
+        #biases = [1.0 / k for k in range(5,5+numActions)]
+        #means = [0.5 + b for b in biases]
+
+
+
+        self.means=[]
+        self.variance=[]
+        self.readenv()
+
+        print self.means
+        
+        
+        # initialize empirical sums
+        '''
+        for i in range(self.numActions):
+            self.payoffSums[i] = self.rewards(i)
[…]

### 2017-10-11 EUCBV/codes/CCB.py

@@ -1,0 +1,276 @@
+'''
+Created on Dec 21, 2016
+
+@author: Subhojyoti
+'''
+
+
+import math
+import random
+import numpy
+from sets import Set
+
+class ClusUCB(object):
+    '''
+    classdocs
+    '''
+
+    min1=-9999999
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+
+
+
+    #Calculate rewards
+    def rewards(self,choice, timesteps):
+        #Gaussain Reward
+        #return random.gauss(self.means[choice],1)
+        #Bernoulli Reward(1 sample from Binomial Distribution)
+        return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+
+    #Count the number of remaining arms
+    def remArms(self):
+        count=0
+        arm=-1
+        for i in range(self.numActions):
+            if self.B[i]!=-1:
+                count=count+1
+                arm=i
+        return count
+
+    def ArmElimination(self):
+
+        max1=self.min1
+        for i in range(self.numActions):
+            
+            if max1<self.avgPayOffSums[i]:
+                max1=self.avgPayOffSums[i]
+                take=i
+            
+        
+        c=math.sqrt(( math.log(self.horizon*self.rangetake*self.rangetake))/(2*self.nm))
+
+        for i in range(self.numActions):
+
+            if (self.avgPayOffSums[i] + c < self.avgPayOffSums[take] - c) and i!=take:
+            #if self.avgPayOffSums[b] + c*math.sqrt(self.weight*1.0/self.rangetake) < self.avgPayOffSums[take1] - c*math.sqrt(self.weight*1.0/self.rangetake):
+                        
+                self.B[i]=-1
+                #print "Remove Arm:"+ str(i)
+
+
+                
+    #Calculate number of pulls each round
+    def calculate_pulls(self):
+
+
+        #self.func=math.log(self.horizon)
+        #self.func=self.horizon / math.log(self.horizon*self.numActions)
+        self.nm=int(math.ceil((2*math.log(self.horizon*self.rangetake*self.rangetake))/(self.rangetake*self.rangetake)))
+        self.T=self.timestep + self.nm*self.remArms()
+                
+        print "nm:"+str(self.nm)
+        return self.nm
+
+
+    '''
+    Running the Clustered UCB
+    '''
+
+    def clusUCB(self,arms,p,turn,wrong):
+
+        '''
+        Set Environment
+        '''
[…]

### 2017-10-11 EUCBV/codes/DMED.py

@@ -1,0 +1,223 @@
+'''
+Created on May 12, 2016
+
+@author: Subhojyoti
+
+code taken from: http://mloss.org/software/view/415/
+'''
+
+
+import math
+import random
+import numpy
+
+class DMED(object):
+    '''
+    classdocs
+    '''
+
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+
+    #Calculate Divergence Function
+    def kl(self,p,q,eps = 1e-15):
+        p = max(p, eps); 
+        p = min(p, 1-eps);  
+        q = max(q, eps); 
+        q = min(q, 1-eps);
+        y = p*math.log(p/q) + (1-p)*math.log((1-p)/(1-q));
+        return y
+   
+    #Calculate rewards
+    def rewards(self,choice):
+        #Gaussain Reward
+        #return random.gauss(self.means[choice],1)
+        #Bernoulli Reward(1 sample from Binomial Distribution)
+        return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+        
+    def DMED(self,numActions):
+
+        #genuine = true -> DMED,
+        #genuine = false -> DMED+(less aggressive)
+
+        self.genuine=True
+
+        #Set the environment
+        self.numActions=numActions
+        
+        self.N = [0] * self.numActions
+        self.S = [0] * self.numActions
+        self.L = [i for i in range(self.numActions)]
+        
+        self.payoffSums = [0] * self.numActions
+        self.numPlays = [0] * self.numActions
+        self.ucbs = [0] * self.numActions
+        self.upbs = [0] * self.numActions
+        #self.numRounds = 3000000
+        self.numRounds = 60000
+        #numRounds = 250000
+        
+        self.arm_reward = [0]*numActions
+        
+        #bestAction=arms/2
+        self.bestAction=self.numActions-2
+        
+
+        self.means =[0.07 for i in range(self.numActions)]
+        
+        '''
+        i=(1*self.numActions)/3
+        while i<self.numActions:
+            self.means[i]=0.05
+            i=i+1
+        
+        i=(2*self.numActions)/3
+        while i<self.numActions:
+            self.means[i]=0.03
+            i=i+1
+        '''
+        
+        t=1.0
+        self.means[self.bestAction]=0.1
+        
+
+        
+        cumulativeReward = 0
+        bestActionCumulativeReward = 0
+        self.actionRegret=[]
+        
+        for i in range(self.numActions):
[…]

### 2017-10-11 EUCBV/codes/DMED_expt2.py

@@ -1,0 +1,234 @@
+'''
+Created on May 12, 2016
+
+@author: Subhojyoti
+'''
+
+
+import math
+import random
+import numpy
+
+class DMED(object):
+    '''
+    classdocs
+    '''
+
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+        
+    def kl(self,p,q,eps = 1e-15):
+        p = max(p, eps); 
+        p = min(p, 1-eps);  
+        q = max(q, eps); 
+        q = min(q, 1-eps);
+        y = p*math.log(p/q) + (1-p)*math.log((1-p)/(1-q));
+        return y
+   
+    
+    def rewards(self,choice):
+        return random.gauss(self.means[choice],self.variance[choice])
+        #print sum(numpy.random.binomial(1,self.means[choice],200))/200.0
+        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+        
+    def DMED(self,numActions):
+
+        #genuine = true -> DMED, false -> DMED+(less aggressive)
+
+        #Set the environment
+        self.numActions=numActions
+        
+        self.N = [0] * self.numActions
+        self.S = [0] * self.numActions
+        self.L = [i for i in range(self.numActions)]
+        
+        self.payoffSums = [0] * self.numActions
+        self.numPlays = [0] * self.numActions
+        self.ucbs = [0] * self.numActions
+        self.upbs = [0] * self.numActions
+        #self.numRounds = 3000000
+        self.numRounds = 300000
+        #numRounds = 250000
+        
+        self.arm_reward = [0]*numActions
+        
+        #bestAction=arms/2
+        self.bestAction=self.numActions-2
+        
+        #biases = [1.0 / k for k in range(5,5+numActions)]
+        #means = [0.5 + b for b in biases]
+        self.means =[0.01 for i in range(self.numActions)]
+        self.variance =[0.25 for i in range(self.numActions)]
+
+
+        i=(1*self.numActions)/3
+        while i<self.numActions:
+            self.means[i]=0.07
+            self.variance[i]=0.01
+            i=i+1
+
+        '''
+        i=(2*self.numActions)/3
+        while i<self.numActions:
+            self.means[i]=0.03
+            i=i+1
+        '''
+        self.means[self.bestAction]=0.09
+        self.variance[self.bestAction]=0.25
+        
+        self.genuine=False
+        
+        cumulativeReward = 0
+        bestActionCumulativeReward = 0
[…]

### 2017-10-11 EUCBV/codes/EUCBV_expt1.py

@@ -1,0 +1,321 @@
+'''
+Created on Apr 1, 2017
+
+@author: Subhojyoti
+'''
+
+import math
+import random
+import numpy
+from sets import Set
+
+class EUCBV(object):
+    '''
+    classdocs
+    '''
+
+    min1=-9999999
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+
+
+
+    #Calculate rewards
+    def rewards(self,choice, timesteps):
+        #Gaussain Reward
+        #return random.gauss(self.means[choice],0.3)
+        #Bernoulli Reward(1 sample from Binomial Distribution)
+        return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+
+    #Count the number of remaining arms
+    def remArms(self):
+        count=0
+        for i in range(self.numActions):
+            if self.B[i]!=-1:
+                count=count+1
+        return count
+
+    def exp_func(self):
+        
+        #self.func=1.0
+        #self.func=math.log(self.horizon)
+        #self.func=self.numActions*self.numActions*self.horizon
+        #self.func=self.horizon / math.log(self.horizon*self.numActions)
+        self.func=self.horizon / (self.numActions*self.numActions)
+        return self.func
+
+    def upperBoundVar(self, numPlays, arm):
+        vj=abs((self.sqPayOffSums[arm]/(self.numPlays[arm])) - (self.avgPayOffSums[arm]*self.avgPayOffSums[arm]))
+        #return math.sqrt(self.rho * vj * max(math.log(( self.exp_func()*self.numRounds*self.delta_tilda)),0) / (4*numPlays) + (self.rho * max(0,math.log((self.exp_func()*self.numRounds*self.delta_tilda))) / (4*numPlays)))
+        return math.sqrt((self.rho * (vj+2.0) * max(math.log(( self.exp_func()*self.numRounds*self.delta_tilda)),0)) / (4.0*numPlays) )
+
+    '''
+    def upperBoundVarExp(self, numPlays, arm):
+        vj=((self.sqPayOffSums[arm]/self.numPlays[arm]) - (self.avgPayOffSums[arm]*self.avgPayOffSums[arm]))
[…]

### 2017-10-11 EUCBV/codes/EUCBV_expt2.py

@@ -1,0 +1,334 @@
+'''
+Created on Apr 1, 2017
+
+@author: Subhojyoti
+'''
+
+import math
+import random
+import numpy
+from sets import Set
+
+class EUCBV(object):
+    '''
+    classdocs
+    '''
+
+    min1=-9999999
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+
+
+
+    #Calculate rewards
+    def rewards(self,choice, timesteps):
+        #Gaussain Reward
+        return random.gauss(self.means[choice],self.variance[choice])
+        #Bernoulli Reward(1 sample from Binomial Distribution)
+        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+
+    #Count the number of remaining arms
+    def remArms(self):
+        count=0
+        for i in range(self.numActions):
+            if self.B[i]!=-1:
+                count=count+1
+        return count
+
+    def exp_func(self):
+        
+        #self.func=1.0
+        #self.func=math.log(self.horizon)
+        #self.func=self.numActions*self.numActions*self.horizon
+        #self.func=self.horizon / math.log(self.horizon*self.numActions)
+        self.func=self.horizon / (self.numActions*self.numActions)
+        return self.func
+
+    def upperBoundVar(self, numPlays, arm):
+        vj=((self.sqPayOffSums[arm]/self.numPlays[arm]) - (self.avgPayOffSums[arm]*self.avgPayOffSums[arm]))
+        #return math.sqrt(self.rho * vj * max(math.log(( self.exp_func()*self.numRounds*self.delta_tilda)),0) / (4*numPlays) + (self.rho * max(0,math.log((self.exp_func()*self.numRounds*self.delta_tilda))) / (4*numPlays)))
+        return math.sqrt((self.rho * (vj+2.0) * max(math.log(( self.exp_func()*self.numRounds*self.delta_tilda)),0)) / (4.0 *numPlays) )
+
+
+
+    #Arm Elimination
+    def ArmElimination(self):
+
+        take=self.min1
+        for i in range(0,self.numActions):
+            if self.B[i]!=-1:
+                if take < self.avgPayOffSums[i]:
+                    take = i
+
+        for i in range(0,self.numActions):
+
+            if self.B[i]!=-1:
+                #c=math.sqrt((self.rho * math.log(self.exp_func() *self.horizon*self.rangetake))/(2*self.nm))
+
[…]

### 2017-10-11 EUCBV/codes/EUCBV_expt3.py

@@ -1,0 +1,301 @@
+'''
+Created on Apr 1, 2017
+
+@author: Subhojyoti
+'''
+
+import math
+import random
+import numpy
+import fileinput
+
+class EUCBV(object):
+    '''
+    classdocs
+    '''
+
+    min1=-9999999
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+
+
+
+    #Calculate rewards
+    def rewards(self,choice, timesteps):
+        #Gaussain Reward
+        return random.gauss(self.means[choice],self.variance[choice])
+        #Bernoulli Reward(1 sample from Binomial Distribution)
+        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+
+    def readenv(self):
+        data=[]
+        filename="env/env1.txt"
+        for line in fileinput.input([filename]):
+
+            try:
+                line1 = [line.split(", ") or line.split("\n") ]
+                #print numpy.shape(line1)
+                #print line1
+                take=[]
+                for i in range(len(line1[0])):
+                    take.append(float(line1[0][i]))
+                #print take
+                data.append(take)
+            except ValueError,e:
+                print e
+        #print data
+        self.means=(data[0])
+        self.variance=(data[1])
+
+    #Count the number of remaining arms
+    def remArms(self):
+        count=0
+        for i in range(self.numActions):
+            if self.B[i]!=-1:
+                count=count+1
+        return count
+
+    def exp_func(self):
+        
+        #self.func=1.0
+        #self.func=math.log(self.horizon)
+        #self.func=self.numActions*self.numActions*self.horizon
+        #self.func=self.horizon / math.log(self.horizon*self.numActions)
+        self.func=self.horizon / (self.numActions*self.numActions)
+        return self.func
+
+    def upperBoundVar(self, numPlays, arm):
+        vj=((self.sqPayOffSums[arm]/self.numPlays[arm]) - (self.avgPayOffSums[arm]*self.avgPayOffSums[arm]))
+        #return math.sqrt(self.rho * vj * max(math.log(( self.exp_func()*self.numRounds*self.delta_tilda)),0) / (4*numPlays) + (self.rho * max(0,math.log((self.exp_func()*self.numRounds*self.delta_tilda))) / (4*numPlays)))
+        return math.sqrt((self.rho * (vj+2.0) * max(math.log(( self.exp_func()*self.numRounds*self.delta_tilda)),0)) / (4.0 *numPlays) )
+
[…]

### 2017-10-11 EUCBV/codes/EUCBV_expt4.py

@@ -1,0 +1,302 @@
+'''
+Created on Apr 1, 2017
+
+@author: Subhojyoti
+'''
+
+import math
+import random
+import numpy
+from sets import Set
+import fileinput
+
+class EUCBV(object):
+    '''
+    classdocs
+    '''
+
+    min1=-9999999
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+
+
+
+    #Calculate rewards
+    def rewards(self,choice, timesteps):
+        #Gaussain Reward
+        return random.gauss(self.means[choice],self.variance[choice])
+        #Bernoulli Reward(1 sample from Binomial Distribution)
+        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+
+    def readenv(self):
+        data=[]
+        filename="env/env3.txt"
+        for line in fileinput.input([filename]):
+
+            try:
+                line1 = [line.split(", ") or line.split("\n") ]
+                #print numpy.shape(line1)
+                #print line1
+                take=[]
+                for i in range(len(line1[0])):
+                    take.append(float(line1[0][i]))
+                #print take
+                data.append(take)
+            except ValueError,e:
+                print e
+        #print data
+        self.means=(data[0])
+        self.variance=(data[1])
+
+    #Count the number of remaining arms
+    def remArms(self):
+        count=0
+        for i in range(self.numActions):
+            if self.B[i]!=-1:
+                count=count+1
+        return count
+
+    def exp_func(self):
+        
+        #self.func=1.0
+        #self.func=math.log(self.horizon)
+        #self.func=self.numActions*self.numActions*self.horizon
+        #self.func=self.horizon / math.log(self.horizon*self.numActions)
+        self.func=self.horizon / (self.numActions*self.numActions)
+        return self.func
+
+    def upperBoundVar(self, numPlays, arm):
+        vj=((self.sqPayOffSums[arm]/self.numPlays[arm]) - (self.avgPayOffSums[arm]*self.avgPayOffSums[arm]))
+        #return math.sqrt(self.rho * vj * max(math.log(( self.exp_func()*self.numRounds*self.delta_tilda)),0) / (4*numPlays) + (self.rho * max(0,math.log((self.exp_func()*self.numRounds*self.delta_tilda))) / (4*numPlays)))
[…]

### 2017-10-11 EUCBV/codes/KLUCB_expt2.py

@@ -1,0 +1,328 @@
+'''
+Created on Oct 6, 2015
+
+@author: Subhojyoti
+'''
+
+import math
+import random
+import numpy
+
+class klucbTest(object):
+    '''
+    classdocs
+    '''
+
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+
+
+
+    def upperBound(self, step, numPlays):
+        #return math.sqrt(2 * math.log(step + 1) / numPlays)
+        return math.sqrt(max(math.log((step + 1.0)/(self.numActions*numPlays)),0.0) / numPlays)
+
+
+    def rewards(self,choice):
+
+        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+        return random.gauss(self.means[choice],self.variance[choice])
+
+
+    def klucbGauss(self, x, d, sig2=1., precision=0.):
+        """klUCB index computation for Gaussian distributions.
+
+        Note that it does not require any search.
+        """
+        return x + math.sqrt(2*sig2*d)
+
+    def klucbBern(self, x, d, precision=1e-6):
+        """klUCB index computation for Bernoulli distributions."""
+        upperbound = min(1., self.klucbGauss(x, d))
+        #upperbound = min(1.,klucbPoisson(x,d)) # also safe, and better ?
+        return self.klucb(x, d, self.klBern, upperbound, precision)
+
+
+    def klBern(self, x, y):
+        """Kullback-Leibler divergence for Bernoulli distributions."""
+
+        eps = 1e-15
+        x = min(max(x, eps), 1-eps)
+        y = min(max(y, eps), 1-eps)
+        return x*math.log(x/y) + (1-x)*math.log((1-x)/(1-y))
+
+    def klucb(self, x, d, div, upperbound, lowerbound=-float('inf'), precision=1e-6):
+        """
+        The generic klUCB index computation.
+
+        Input args.: x, d, div, upperbound, lowerbound=-float('inf'), precision=1e-6,
+        where div is the KL divergence to be used.
+        """
+        l = max(x, lowerbound)
+        #upperbound = self.klucbGauss(x, d, precision)
+        u = upperbound
+        while u-l>precision:
+            m = (l+u)/2
+
+            if div(x, m)>d:
+                u = m
+            else:
+                l = m
+        return (l+u)/2
+
+#     def klucbGauss(self, x, d, sig2=1., precision=0.):
+#         """klUCB index computation for Gaussian distributions.
+#
[…]

### 2017-10-11 EUCBV/codes/KLUCB_expt4.py

@@ -1,0 +1,333 @@
+'''
+Created on Oct 6, 2015
+
+@author: Subhojyoti
+'''
+
+import math
+import random
+import numpy
+
+class klucbTest(object):
+    '''
+    classdocs
+    '''
+
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+
+
+
+    def upperBound(self, step, numPlays):
+        #return math.sqrt(2 * math.log(step + 1) / numPlays)
+        return math.sqrt(max(math.log((step + 1.0)/(self.numActions*numPlays)),0.0) / numPlays)
+
+
+    def rewards(self,choice):
+
+        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+        return random.gauss(self.means[choice],self.variance[choice])
+
+
+    def klucbGauss(self, x, d, sig2=1., precision=0.):
+        """klUCB index computation for Gaussian distributions.
+
+        Note that it does not require any search.
+        """
+        return x + math.sqrt(2*sig2*d)
+
+    def klucbBern(self, x, d, precision=1e-6):
+        """klUCB index computation for Bernoulli distributions."""
+        upperbound = min(1., self.klucbGauss(x, d))
+        #upperbound = min(1.,klucbPoisson(x,d)) # also safe, and better ?
+        return self.klucb(x, d, self.klBern, upperbound, precision)
+
+
+    def klBern(self, x, y):
+        """Kullback-Leibler divergence for Bernoulli distributions."""
+
+        eps = 1e-15
+        x = min(max(x, eps), 1-eps)
+        y = min(max(y, eps), 1-eps)
+        return x*math.log(x/y) + (1-x)*math.log((1-x)/(1-y))
+
+    def klucb(self, x, d, div, upperbound, lowerbound=-float('inf'), precision=1e-6):
+        """
+        The generic klUCB index computation.
+
+        Input args.: x, d, div, upperbound, lowerbound=-float('inf'), precision=1e-6,
+        where div is the KL divergence to be used.
+        """
+        l = max(x, lowerbound)
+        #upperbound = self.klucbGauss(x, d, precision)
+        u = upperbound
+        while u-l>precision:
+            m = (l+u)/2
+
+            if div(x, m)>d:
+                u = m
+            else:
+                l = m
+        return (l+u)/2
+
+#     def klucbGauss(self, x, d, sig2=1., precision=0.):
+#         """klUCB index computation for Gaussian distributions.
+#
[…]

### 2017-10-11 EUCBV/codes/MOSS.py

@@ -1,0 +1,183 @@
+'''
+Created on Oct 6, 2015
+
+@author: Subhojyoti
+'''
+
+import math
+import random
+import numpy
+
+class MOSS(object):
+    '''
+    classdocs
+    '''
+
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+        
+        
+    
+    def upperBound(self, step, numPlays):
+        #return math.sqrt(2 * math.log(step + 1) / numPlays)
+        #return math.sqrt(max(math.log((step + 1.0)/(self.numActions*numPlays)),0.0) / numPlays)
+        return math.sqrt(max(math.log((self.numRounds)/(1.0*self.numActions*numPlays)),0.0) / numPlays)
+    
+     
+    def rewards(self,choice):
+        
+        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+        return random.gauss(self.means[choice],0.5)
+        
+    def moss(self,numActions):
+    
+        #Set the environment
+        self.numActions=numActions
+        
+        self.payoffSums = [0] * self.numActions
+        self.numPlays = [0] * self.numActions
+        self.ucbs = [0] * self.numActions
+        self.upbs = [0] * self.numActions
+        #self.numRounds = self.numActions*self.numActions*self.numActions
+        self.numRounds = 500000
+        #self.numRounds = self.numActions*math.pow(10,3)
+        
+        self.arm_reward = [0]*numActions
+        
+        #bestAction=arms/2
+        self.bestAction=self.numActions-2
+        
+        
+        self.means =[0.8 for i in range(self.numActions)]
+
+        for i in range(0,1*self.numActions/3):
+            self.means[i]=0.5
+
+        '''
+        #i=(1*self.numActions)/3
+        for i in range(self.numActions/3):
+            self.means[i]=0.01
+        '''
+        '''
+        i=(2*self.numActions)/3
+        while i<self.numActions:
+            self.means[i]=0.4
+            i=i+1
+        '''
+        self.means[self.bestAction]=0.9
+        
+        print self.means
+        
+        # initialize empirical sums
+        
+        cumulativeReward = 0
+        bestActionCumulativeReward = 0
+        self.actionRegret=[]
+        t=1
+        
+        for i in range(self.numActions):
+            theReward = self.rewards(i)
+            #self.numPlays[i]=self.numPlays[i]+1
+            
+            action=i
+            theReward = self.rewards(action)
+            #print theReward,action
[…]

### 2017-10-11 EUCBV/codes/MOSS_expt2.py

@@ -1,0 +1,187 @@
+'''
+Created on Oct 6, 2015
+
+@author: Subhojyoti
+'''
+
+import math
+import random
+import numpy
+
+class MOSS(object):
+    '''
+    classdocs
+    '''
+
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+        
+        
+    
+    def upperBound(self, step, numPlays):
+        #return math.sqrt(2 * math.log(step + 1) / numPlays)
+        return math.sqrt(max(math.log((self.numRounds)/(1.0*self.numActions*numPlays)),0.0) / numPlays)
+        #return math.sqrt(max(math.log((step + 1.0)/(self.numActions*numPlays)),0.0) / numPlays)
+    
+     
+    def rewards(self,choice):
+        
+        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+        return random.gauss(self.means[choice],self.variance[choice])
+        
+    def moss(self,numActions):
+    
+        #Set the environment
+        self.numActions=numActions
+        
+        self.payoffSums = [0] * self.numActions
+        self.numPlays = [0] * self.numActions
+        self.ucbs = [0] * self.numActions
+        self.upbs = [0] * self.numActions
+        #self.numRounds = self.numActions*self.numActions*self.numActions
+        self.numRounds = 300000
+        #self.numRounds = self.numActions*math.pow(10,3)
+        
+        self.arm_reward = [0]*numActions
+        
+        #bestAction=arms/2
+        self.bestAction=self.numActions-2
+        
+        
+        self.means =[0.01 for i in range(self.numActions)]
+        self.variance=[0.25 for i in range(self.numActions)]
+
+
+        for i in range(0,1*self.numActions/3):
+            self.means[i]=0.07
+            self.variance[i]=0.01
+
+        '''
+        #i=(1*self.numActions)/3
+        for i in range(self.numActions/3):
+            self.means[i]=0.01
+        '''
+        '''
+        i=(2*self.numActions)/3
+        while i<self.numActions:
+            self.means[i]=0.4
+            i=i+1
+        '''
+        self.means[self.bestAction]=0.09
+        self.variance[self.bestAction]=0.25
+        
+        print self.means
+        
+        # initialize empirical sums
+        
+        cumulativeReward = 0
+        bestActionCumulativeReward = 0
+        self.actionRegret=[]
+        t=1
+        
+        for i in range(self.numActions):
+            theReward = self.rewards(i)
[…]

### 2017-10-11 EUCBV/codes/MOSS_expt3.py

@@ -1,0 +1,187 @@
+'''
+Created on Oct 6, 2015
+
+@author: Subhojyoti
+'''
+
+import math
+import random
+import numpy
+import fileinput
+
+class MOSS(object):
+    '''
+    classdocs
+    '''
+
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+        
+    def readenv(self):
+        data=[]
+        filename="env/env1.txt"
+        for line in fileinput.input([filename]):
+
+            try:
+                line1 = [line.split(", ") or line.split("\n") ]
+                #print numpy.shape(line1)
+                #print line1
+                take=[]
+                for i in range(len(line1[0])):
+                    take.append(float(line1[0][i]))
+                #print take
+                data.append(take)
+            except ValueError,e:
+                print e
+        #print data
+        self.means=(data[0])
+        self.variance=(data[1])
+    
+    def upperBound(self, step, numPlays):
+        return math.sqrt(max(math.log((self.numRounds)/(1.0*self.numActions*numPlays)),0.0) / numPlays)
+    
+     
+    def rewards(self,choice):
+        
+        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+        return random.gauss(self.means[choice],self.variance[choice])
+        
+    def moss(self,numActions):
+    
+        #Set the environment
+        self.numActions=numActions
+        
+        self.payoffSums = [0] * self.numActions
+        self.numPlays = [0] * self.numActions
+        self.ucbs = [0] * self.numActions
+        self.upbs = [0] * self.numActions
+        #self.numRounds = 100000 + self.numActions*self.numActions*self.numActions
+        self.numRounds = 400000
+        #self.numRounds = self.numActions*math.pow(10,3)
+        
+        self.arm_reward = [0]*numActions
+        
+        #bestAction=arms/2
+        self.bestAction=self.numActions-2
+        
+        
+        self.means=[]
+        self.variance=[]
+        self.readenv()
+
+        
+        print self.means
+        
+        # initialize empirical sums
+        
+        cumulativeReward = 0
+        bestActionCumulativeReward = 0
+        self.actionRegret=[]
+        t=1
+        
+        for i in range(self.numActions):
+            theReward = self.rewards(i)
+            #self.numPlays[i]=self.numPlays[i]+1
+            
+            action=i
+            theReward = self.rewards(action)
[…]

### 2017-10-11 EUCBV/codes/MOSS_expt4.py

@@ -1,0 +1,196 @@
+'''
+Created on Oct 6, 2015
+
+@author: Subhojyoti
+'''
+
+import math
+import random
+import numpy
+import  fileinput
+
+class MOSS(object):
+    '''
+    classdocs
+    '''
+
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+        
+    def readenv(self):
+        data=[]
+        filename="env/env3.txt"
+        for line in fileinput.input([filename]):
+
+            try:
+                line1 = [line.split(", ") or line.split("\n") ]
+                #print numpy.shape(line1)
+                #print line1
+                take=[]
+                for i in range(len(line1[0])):
+                    take.append(float(line1[0][i]))
+                #print take
+                data.append(take)
+            except ValueError,e:
+                print e
+        #print data
+        self.means=(data[0])
+        self.variance=(data[1])
+    
+    def upperBound(self, step, numPlays):
+        #return math.sqrt(2 * math.log(step + 1) / numPlays)
+        #print math.sqrt(max(math.log((self.numRounds)/(self.numActions*numPlays)),0.0) / numPlays)
+        '''
+        try:
+            return math.sqrt(max(math.log((self.numRounds)/(1.0*self.numActions*numPlays)),0.0) / numPlays)
+        except Exception as err:
+            print (self.numRounds)/(self.numActions*numPlays)
+            print(format(err))
+        '''
+        #return math.sqrt(max(math.log((step + 1.0)/(self.numActions*numPlays)),0.0) / numPlays)
+        return math.sqrt(max(math.log((self.numRounds)/(1.0*self.numActions*numPlays)),0.0) / numPlays)
+    
+     
+    def rewards(self,choice):
+        
+        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+        return random.gauss(self.means[choice],self.variance[choice])
+        
+    def moss(self,numActions):
+    
+        #Set the environment
+        self.numActions=numActions
+        
+        self.payoffSums = [0] * self.numActions
+        self.numPlays = [0] * self.numActions
+        self.ucbs = [0] * self.numActions
+        self.upbs = [0] * self.numActions
+        #self.numRounds = 100000 + self.numActions*self.numActions*self.numActions
+        self.numRounds = 400000
+        #self.numRounds = self.numActions*math.pow(10,3)
+        
+        self.arm_reward = [0]*numActions
+        
+        #bestAction=arms/2
[…]

### 2017-10-11 EUCBV/codes/OCUCB.py

@@ -1,0 +1,186 @@
+'''
+Created on Dec 21, 2016
+
+@author: Subhojyoti
+'''
+
+
+import math
+import random
+import numpy
+
+class ucb1_2(object):
+    '''
+    classdocs
+    '''
+
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+        
+        
+    
+    def upperBound(self, step, numPlays):
+        self.alpha=2.0
+        self.psi=2.0
+        return math.sqrt((self.alpha * math.log((self.psi*self.numRounds) / (step))) / numPlays)
+    
+     
+    def rewards(self,choice):
+        #return random.gauss(self.means[choice],1)
+        #print sum(numpy.random.binomial(1,self.means[choice],200))/200.0
+        return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+        
+    def ucb1(self,numActions):
+    
+        #Set the environment
+        self.numActions=numActions
+        
+        self.payoffSums = [0] * self.numActions
+        self.numPlays = [0] * self.numActions
+        self.ucbs = [0] * self.numActions
+        self.upbs = [0] * self.numActions
+        #self.numRounds = 3000000
+        #self.numRounds = 300000
+        #numRounds = 250000
+        self.numRounds = self.numActions*self.numActions*self.numActions
+        
+        self.arm_reward = [0]*numActions
+        
+        #bestAction=arms/2
+        self.bestAction=self.numActions-2
+        
+        #biases = [1.0 / k for k in range(5,5+numActions)]
+        #means = [0.5 + b for b in biases]
+        self.means =[0.05 for i in range(self.numActions)]
+
+        for i in range(0,1*self.numActions/3):
+            self.means[i]=0.01
+
+        '''
+        i=(1*self.numActions)/3
+        while i<self.numActions:
+            self.means[i]=0.05
+            i=i+1
+        
+        i=(2*self.numActions)/3
+        while i<self.numActions:
+            self.means[i]=0.03
+            i=i+1
+        '''
+        self.means[self.bestAction]=0.1
+        
+        
+        # initialize empirical sums
+        t=1
+        cumulativeReward = 0
+        bestActionCumulativeReward = 0
+        self.actionRegret=[]
+        
+        for i in range(self.numActions):
+            theReward = self.rewards(i)
+            #self.numPlays[i]=self.numPlays[i]+1
+            
+            action=i
+            self.arm_reward[action]=self.arm_reward[action]+theReward
[…]

### 2017-10-11 EUCBV/codes/OCUCB_expt2.py

@@ -1,0 +1,188 @@
+'''
+Created on Dec 21, 2016
+
+@author: Subhojyoti
+'''
+
+
+import math
+import random
+import numpy
+
+class ucb1_2(object):
+    '''
+    classdocs
+    '''
+
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+        
+        
+    
+    def upperBound(self, step, numPlays):
+        self.alpha=2.1
+        self.psi=2.0
+        return math.sqrt((self.alpha * math.log((self.psi*self.numRounds) / (step))) / numPlays)
+    
+     
+    def rewards(self,choice):
+        return random.gauss(self.means[choice],self.variance[choice])
+        #print sum(numpy.random.binomial(1,self.means[choice],200))/200.0
+        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+        
+    def ucb1(self,numActions):
+    
+        #Set the environment
+        self.numActions=numActions
+        
+        self.payoffSums = [0] * self.numActions
+        self.numPlays = [0] * self.numActions
+        self.ucbs = [0] * self.numActions
+        self.upbs = [0] * self.numActions
+        #self.numRounds = 3000000
+        self.numRounds = 300000
+        #numRounds = 250000
+        #self.numRounds = self.numActions*self.numActions*self.numActions
+        
+        self.arm_reward = [0]*numActions
+        
+        #bestAction=arms/2
+        self.bestAction=self.numActions-2
+        
+        #biases = [1.0 / k for k in range(5,5+numActions)]
+        #means = [0.5 + b for b in biases]
+        self.means =[0.01 for i in range(self.numActions)]
+        self.variance =[0.25 for i in range(self.numActions)]
+
+        for i in range(0,1*self.numActions/3):
+            self.means[i]=0.07
+            self.variance[i]=0.01
+
+        '''
+        i=(1*self.numActions)/3
+        while i<self.numActions:
+            self.means[i]=0.05
+            i=i+1
+        
+        i=(2*self.numActions)/3
+        while i<self.numActions:
+            self.means[i]=0.03
+            i=i+1
+        '''
+        self.means[self.bestAction]=0.09
+        self.variance[self.bestAction]=0.25
+        
+        
+        # initialize empirical sums
+        t=1
+        cumulativeReward = 0
+        bestActionCumulativeReward = 0
+        self.actionRegret=[]
+        
+        for i in range(self.numActions):
+            theReward = self.rewards(i)
[…]

### 2017-10-11 EUCBV/codes/OCUCB_expt3.py

@@ -1,0 +1,191 @@
+'''
+Created on Dec 21, 2016
+
+@author: Subhojyoti
+'''
+
+
+import math
+import random
+import numpy
+import fileinput
+
+class ucb1_2(object):
+    '''
+    classdocs
+    '''
+
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+        
+        
+    
+    def upperBound(self, step, numPlays):
+        self.alpha=2.0
+        self.psi=2.0
+        return math.sqrt((self.alpha * math.log((self.psi*self.numRounds) / (step))) / numPlays)
+    
+     
+    def rewards(self,choice):
+        return random.gauss(self.means[choice],self.variance[choice])
+        #print sum(numpy.random.binomial(1,self.means[choice],200))/200.0
+        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+
+    def readenv(self):
+        data=[]
+        filename="env/env1.txt"
+        for line in fileinput.input([filename]):
+
+            try:
+                line1 = [line.split(", ") or line.split("\n") ]
+                #print numpy.shape(line1)
+                #print line1
+                take=[]
+                for i in range(len(line1[0])):
+                    take.append(float(line1[0][i]))
+                #print take
+                data.append(take)
+            except ValueError,e:
+                print e
+        #print data
+        self.means=(data[0])
+        self.variance=(data[1])
+
+    def ucb1(self,numActions):
+    
+        #Set the environment
+        self.numActions=numActions
+        
+        self.payoffSums = [0] * self.numActions
+        self.numPlays = [0] * self.numActions
+        self.ucbs = [0] * self.numActions
+        self.upbs = [0] * self.numActions
+        #self.numRounds = 3000000
+        self.numRounds = 400000
+        #numRounds = 250000
+        #self.numRounds = 100000 + self.numActions*self.numActions*self.numActions
+        
+        self.arm_reward = [0]*numActions
+        
+        #bestAction=arms/2
+        self.bestAction=self.numActions-2
+        
+
+        self.means=[]
+        self.variance=[]
+        self.readenv()
+        
+        
+        # initialize empirical sums
+        t=1
+        cumulativeReward = 0
+        bestActionCumulativeReward = 0
+        self.actionRegret=[]
+        
+        for i in range(self.numActions):
+            theReward = self.rewards(i)
+            #self.numPlays[i]=self.numPlays[i]+1
[…]

### 2017-10-11 EUCBV/codes/OCUCB_expt4.py

@@ -1,0 +1,191 @@
+'''
+Created on Dec 21, 2016
+
+@author: Subhojyoti
+'''
+
+
+import math
+import random
+import numpy
+import fileinput
+
+class ucb1_2(object):
+    '''
+    classdocs
+    '''
+
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+
+    
+    def upperBound(self, step, numPlays):
+        self.alpha=2.1
+        self.psi=2.0
+        return math.sqrt((self.alpha * math.log((self.psi*self.numRounds) / (step))) / numPlays)
+    
+
+    def readenv(self):
+        data=[]
+        filename="env/env3.txt"
+        for line in fileinput.input([filename]):
+
+            try:
+                line1 = [line.split(", ") or line.split("\n") ]
+                #print numpy.shape(line1)
+                #print line1
+                take=[]
+                for i in range(len(line1[0])):
+                    take.append(float(line1[0][i]))
+                #print take
+                data.append(take)
+            except ValueError,e:
+                print e
+        #print data
+        self.means=(data[0])
+        self.variance=(data[1])
+
+    def rewards(self,choice):
+        return random.gauss(self.means[choice],self.variance[choice])
+        #print sum(numpy.random.binomial(1,self.means[choice],200))/200.0
+        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+        
+    def ucb1(self,numActions):
+    
+        #Set the environment
+        self.numActions=numActions
+        
+        self.payoffSums = [0] * self.numActions
+        self.numPlays = [0] * self.numActions
+        self.ucbs = [0] * self.numActions
+        self.upbs = [0] * self.numActions
+        #self.numRounds = 3000000
+        #self.numRounds = 300000
+        self.numRounds = 400000
+        #self.numRounds = 100000 + self.numActions*self.numActions*self.numActions
+        
+        self.arm_reward = [0]*numActions
+        
+        #bestAction=arms/2
+        self.bestAction=self.numActions-2
+        
+        #biases = [1.0 / k for k in range(5,5+numActions)]
+        #means = [0.5 + b for b in biases]
+        self.means=[]
+        self.variance=[]
+        self.readenv()
+        
+        
+        # initialize empirical sums
+        t=1
+        cumulativeReward = 0
+        bestActionCumulativeReward = 0
+        self.actionRegret=[]
+        
+        for i in range(self.numActions):
[…]

### 2017-10-11 EUCBV/codes/ThompsonSampling.py

@@ -1,0 +1,169 @@
+'''
+Created on Oct 6, 2015
+
+@author: Subhojyoti
+'''
+
+import math
+import random
+import numpy
+#from random import betavariate
+#from scipy.special import btdtri
+
+
+class   TS(object):
+    '''
+    classdocs
+    '''
+
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+        
+     
+   #Calculate rewards
+    def rewards(self,choice):
+
+        #Bernoulli Reward(1 sample from Binomial Distribution)
+        return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+        
+    def TS(self,numActions):
+    
+        #Set the environment
+        self.numActions=numActions
+        
+        self.payoffSums = [0] * self.numActions
+        self.numPlays = [0] * self.numActions
+        self.ucbs = [0] * self.numActions
+        self.upbs = [0] * self.numActions
+        #self.numRounds = 3000000
+        self.numRounds = 20000
+        #numRounds = 250000
+        
+        self.arm_reward = [0]*numActions
+        
+
+        self.bestAction=self.numActions-2
+        
+
+        self.means =[0.07 for i in range(self.numActions)]
+        
+        '''
+        i=(1*self.numActions)/3
+        while i<self.numActions:
+            self.means[i]=0.05
+            i=i+1
+        
+        i=(2*self.numActions)/3
+        while i<self.numActions:
+            self.means[i]=0.03
+            i=i+1
+        '''
+        self.means[self.bestAction]=0.1
+        
+        
+        # initialize empirical sums
+        '''
+        for i in range(self.numActions):
+            self.payoffSums[i] = self.rewards(i)
+            self.numPlays[i]=self.numPlays[i]+1
+        '''
+        
+        theta=[0.0]*self.numActions
+        success=[0.0]*self.numActions
+        failure=[0.0]*self.numActions
+        
+        for i in range(self.numActions):
+            theta[i]=random.betavariate(success[i]+1,failure[i]+1)
+            
+
+        cumulativeReward = 0
+        bestActionCumulativeReward = 0
+            
+        self.actionRegret=[]
+        t=1
+        while True:
+
+            
+            for i in range(self.numActions):
+
+                theta[i]=random.betavariate(success[i]+1,failure[i]+1)
+            
+            action=max(range(self.numActions), key=lambda i: theta[i])
+            
+
+
+            theReward = self.rewards(action)
+            
[…]

### 2017-10-11 EUCBV/codes/ThompsonSampling_expt1.py

@@ -1,0 +1,190 @@
+'''
+Created on Oct 6, 2015
+
+@author: Subhojyoti
+'''
+
+import math
+import random
+import numpy
+#from random import betavariate
+#from scipy.special import btdtri
+
+
+class ucb1_2(object):
+    '''
+    classdocs
+    '''
+
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+
+
+    
+     
+    def rewards(self,choice):
+        #return random.gauss(self.means[choice],self.variance[choice])
+        return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+        
+    def ucb1(self,numActions):
+    
+        #Set the environment
+        self.numActions=numActions
+        
+        self.payoffSums = [0] * self.numActions
+        self.numPlays = [0] * self.numActions
+        self.ucbs = [0] * self.numActions
+        self.upbs = [0] * self.numActions
+        #self.numRounds = 300000
+        self.numRounds = 60000
+        #self.numRounds = 100000 + self.numActions*self.numActions*self.numActions
+        #numRounds = 250000
+        
+        self.arm_reward = [0]*numActions
+        
+        #bestAction=arms/2
+        self.bestAction=self.numActions-2
+        
+        
+        self.means =[0.01 for i in range(self.numActions)]
+        self.variance =[0.7 for i in range(self.numActions)]
+        
+
+        i=(1*self.numActions)/3
+        while i<self.numActions:
+            self.means[i]=0.07
+            self.variance[i]=0.1
+            i=i+1
+
+        '''
+        i=(2*self.numActions)/3
+        while i<self.numActions:
+            self.means[i]=0.03
+            i=i+1
+        '''
+        self.means[self.bestAction]=0.1
+        self.variance[self.bestAction]=0.7
+        
+        
+        # initialize empirical sums
+        '''
+        for i in range(self.numActions):
+            self.payoffSums[i] = self.rewards(i)
+            self.numPlays[i]=self.numPlays[i]+1
+        '''
+        
+        theta=[0.0]*self.numActions
+        success=[0.0]*self.numActions
+        failure=[0.0]*self.numActions
+        
+        for i in range(self.numActions):
+            theta[i]=random.betavariate(success[i]+1,failure[i]+1)
+            #theta[i]=random.gauss((self.payoffSums[i]/(self.numPlays[i])) ,(1.0/(self.numPlays[i])))
+            
+        #t = numActions
+        
+        cumulativeReward = 0
[…]

### 2017-10-11 EUCBV/codes/ThompsonSampling_expt2_eucbv.py

@@ -1,0 +1,187 @@
+'''
+Created on Oct 6, 2015
+
+@author: Subhojyoti
+'''
+
+import math
+import random
+import numpy
+#from random import betavariate
+#from scipy.special import btdtri
+
+
+class ucb1_2(object):
+    '''
+    classdocs
+    '''
+
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+     
+    def rewards(self,choice):
+        return random.gauss(self.means[choice],self.variance[choice])
+        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+        
+    def ucb1(self,numActions):
+    
+        #Set the environment
+        self.numActions=numActions
+        
+        self.payoffSums = [0] * self.numActions
+        self.numPlays = [1.0] * self.numActions
+        self.ucbs = [0] * self.numActions
+        self.upbs = [0] * self.numActions
+        self.numRounds = 300000
+        #self.numRounds = 60000
+        #self.numRounds = 100000 + self.numActions*self.numActions*self.numActions
+        #numRounds = 250000
+        
+        self.arm_reward = [0]*numActions
+        
+        #bestAction=arms/2
+        self.bestAction=self.numActions-2
+        
+        
+        self.means =[0.1 for i in range(self.numActions)]
+        self.variance =[0.25 for i in range(self.numActions)]
+
+
+        i=(1*self.numActions)/3
+        while i<self.numActions:
+            self.means[i]=0.8
+            self.variance[i]=0.1
+            i=i+1
+
+        '''
+        i=(2*self.numActions)/3
+        while i<self.numActions:
+            self.means[i]=0.03
+            i=i+1
+        '''
+        self.means[self.bestAction]=0.9
+        self.variance[self.bestAction]=0.25
+        
+        
+        # initialize empirical sums
+        '''
+        for i in range(self.numActions):
+            self.payoffSums[i] = self.rewards(i)
+            self.numPlays[i]=self.numPlays[i]+1
+        '''
+        
+        theta=[0.0]*self.numActions
+        success=[0.0]*self.numActions
+        failure=[0.0]*self.numActions
+        
+        for i in range(self.numActions):
+            #theta[i]=random.betavariate(success[i]+1,failure[i]+1)
+            theta[i]=random.gauss((self.payoffSums[i]/(self.numPlays[i])) ,(1.0/(self.numPlays[i])))
+            
+        #t = numActions
+        
+        cumulativeReward = 0
+        bestActionCumulativeReward = 0
[…]

### 2017-10-11 EUCBV/codes/ThompsonSampling_expt3_eucbv.py

@@ -1,0 +1,194 @@
+'''
+Created on Oct 6, 2015
+
+@author: Subhojyoti
+'''
+
+import math
+import random
+import numpy
+import fileinput
+#from random import betavariate
+#from scipy.special import btdtri
+
+
+class ucb1_2(object):
+    '''
+    classdocs
+    '''
+
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+        
+
+    def rewards(self,choice):
+        return random.gauss(self.means[choice],self.variance[choice])
+        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+
+    def readenv(self):
+        data=[]
+        filename="env/env1.txt"
+        for line in fileinput.input([filename]):
+
+            try:
+                line1 = [line.split(", ") or line.split("\n") ]
+                #print numpy.shape(line1)
+                #print line1
+                take=[]
+                for i in range(len(line1[0])):
+                    take.append(float(line1[0][i]))
+                #print take
+                data.append(take)
+            except ValueError,e:
+                print e
+        #print data
+        self.means=(data[0])
+        self.variance=(data[1])
+
+    def ucb1(self,numActions):
+    
+        #Set the environment
+        self.numActions=numActions
+        
+        self.payoffSums = [0] * self.numActions
+        self.numPlays = [1.0] * self.numActions
+        self.ucbs = [0] * self.numActions
+        self.upbs = [0] * self.numActions
+        self.numRounds = 400000
+        #self.numRounds = 60000
+        #self.numRounds = 100000 + self.numActions*self.numActions*self.numActions
+        #numRounds = 250000
+        
+        self.arm_reward = [0]*numActions
+        
+        #bestAction=arms/2
+        self.bestAction=self.numActions-2
+        
+        
+        self.means=[]
+        self.variance=[]
+        self.readenv()
+        
+        
+        # initialize empirical sums
+        '''
+        for i in range(self.numActions):
+            self.payoffSums[i] = self.rewards(i)
+            self.numPlays[i]=self.numPlays[i]+1
+        '''
+        
+        theta=[0.0]*self.numActions
+        success=[0.0]*self.numActions
+        failure=[0.0]*self.numActions
+        
+        for i in range(self.numActions):
+            #theta[i]=random.betavariate(success[i]+1,failure[i]+1)
[…]

### 2017-10-11 EUCBV/codes/ThompsonSampling_expt4_eucbv.py

@@ -1,0 +1,202 @@
+'''
+Created on Oct 6, 2015
+
+@author: Subhojyoti
+'''
+
+import math
+import random
+import numpy
+#from random import betavariate
+#from scipy.special import btdtri
+import fileinput
+
+
+class ucb1_2(object):
+    '''
+    classdocs
+    '''
+
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+        
+
+        
+    
+    def upperBound(self, step, numPlays):
+        return math.sqrt(2 * math.log(step + 1) / numPlays)
+    
+    
+     
+    def rewards(self,choice):
+        return random.gauss(self.means[choice],self.variance[choice])
+        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+
+
+    def readenv(self):
+        data=[]
+        filename="env/env3.txt"
+        for line in fileinput.input([filename]):
+
+            try:
+                line1 = [line.split(", ") or line.split("\n") ]
+                #print numpy.shape(line1)
+                #print line1
+                take=[]
+                for i in range(len(line1[0])):
+                    take.append(float(line1[0][i]))
+                #print take
+                data.append(take)
+            except ValueError,e:
+                print e
+        #print data
+        self.means=(data[0])
+        self.variance=(data[1])
+
+    def ucb1(self,numActions):
+    
+        #Set the environment
+        self.numActions=numActions
+        
+        self.payoffSums = [0] * self.numActions
+        self.numPlays = [1] * self.numActions
+        self.ucbs = [0] * self.numActions
+        self.upbs = [0] * self.numActions
+        #self.numRounds = 3000000
+        self.numRounds = 400000
+        #self.numRounds = 100000 + self.numActions*self.numActions*self.numActions
+        #numRounds = 250000
+        
+        self.arm_reward = [0]*numActions
+        
+        #bestAction=arms/2
+        self.bestAction=self.numActions-2
+        
+        
+        self.means=[]
+        self.variance=[]
+        self.readenv()
+        
+        
+        # initialize empirical sums
+        '''
+        for i in range(self.numActions):
+            self.payoffSums[i] = self.rewards(i)
+            self.numPlays[i]=self.numPlays[i]+1
+        '''
+        
+        theta=[0.0]*self.numActions
+        success=[0.0]*self.numActions
+        failure=[0.0]*self.numActions
+        
[…]

### 2017-10-11 EUCBV/codes/UCBRevisited.py

@@ -1,0 +1,238 @@
+'''
+Created on Jul 28, 2015
+
+@author: Subhojyoti
+'''
+
+import math
+import random
+import numpy
+
+class UCBRevisted(object):
+    '''
+    classdocs
+    '''
+    
+    def __init__(self):
+        '''
+        Constructor
+        '''
+
+    
+    #Calculate rewards
+    def rewards(self,choice, timestep):
+        #Gaussain Reward
+        return random.gauss(self.means[choice],self.variance[choice])
+        #Bernoulli Reward(1 sample from Binomial Distribution)
+        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+
+    #UpperBound Definition
+    def upperBound(self, step, numPlays,horizon,delta_tilda):
+    
+        #return math.sqrt( math.log10(horizon*delta_tilda*delta_tilda) / ((2*numPlays)*math.log10(math.e)) ) 
+        
+        return math.sqrt( math.log(horizon*delta_tilda*delta_tilda) / ((2*self.nm)) )
+        #return math.sqrt( math.log(horizon*delta_tilda*delta_tilda) / ((2*numPlays)) ) 
+        #return math.sqrt( math.log10(horizon*delta_tilda*delta_tilda) / ((2*self.nm)*math.log10(math.e)) )
+    
+    def ucbRevisited(self,arms,turn,wrong):
+
+        #Set the environment
+        self.numActions = arms
+        self.horizon=300000
+        self.bestAction=self.numActions-2
+
+        self.numRounds = 0.5*math.floor(math.log10(self.horizon/math.e)/math.log10(2))
+
+        self.means =[0.01 for i in range(self.numActions)]
+        self.variance =[0.25 for i in range(self.numActions)]
+
+
+        i=(1*self.numActions)/3
+        while i<self.numActions:
+            self.means[i]=0.07
+            self.variance[i]=0.01
+            i=i+1
+
+        '''
+        i=(2*self.numActions)/3
+        while i<self.numActions:
+            self.means[i]=0.03
+            i=i+1
+        '''
+        self.means[self.bestAction]=0.09
+        self.variance[self.bestAction]=0.25
+
+
+        self.arm_reward = [0]*self.numActions
+
+        self.actionRegret=[]
+        
+        
+
+        
+        self.timestep=0
+        self.m=0
+        self.delta_tilda=1.0
+        self.B=[0 for i in range(self.numActions)]
[…]

### 2017-10-11 EUCBV/codes/create_environment.py

@@ -1,0 +1,94 @@
+'''
+Created on Jan 27, 2016
+
+@author: Subhojyoti
+'''
+
+import math
+import random
+import numpy
+import fileinput
+
+class CreateEnvironment(object):
+    '''
+    classdocs
+    '''
+
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+    
+
+
+    def readenv(self):
+        data=[]
+        filename="env/GR3.txt"
+        for line in fileinput.input([filename]):
+
+            try:
+                line1 = [line.split(", ") or line.split("\n") ]
+                #print numpy.shape(line1)
+                #print line1
+                take=[]
+                for i in range(len(line1[0])):
+                    take.append(float(line1[0][i]))
+                #print take
+                data.append(take)
+            except ValueError,e:
+                print e
+        #print data
+        self.means=(data[0])
+        self.variance=(data[1])
+
+    def create(self,numActions):
+    
+        #Set the environment
+
+        self.numActions=numActions
+        self.bestAction =  self.numActions - 2
+
+        '''
+        self.means =[]
+        self.variance=[]
+        self.readenv()
+        '''
+
+        self.means =[0.09 for i in range(self.numActions)]
+        self.variance=[0.0 for i in range(self.numActions)]
+
+
+        for i in range(0, int((0.5)*self.numActions)):
+            self.variance[i]=numpy.random.uniform(0.0,0.05)
+
+        for i in range(int((0.5)*self.numActions), self.numActions):
+            self.variance[i]=numpy.random.uniform(0.19,0.24)
+
+        for i in range(10, self.numActions):
+            self.means[i]=numpy.random.uniform(0.09,0.09)
+
+        self.means[self.bestAction] = 0.1
+        self.variance[self.bestAction] = 0.25
+
+        f = open('env/env3.txt', 'w')
+        f.writelines("%s\n" % (', '.join(["%.3f" % i for i in self.means])))
+        f.writelines("%s\n" % (', '.join(["%.3f" % i for i in self.variance])))
+        f.close()
+
+
+        print self.means
+        print self.variance
+
+
+
+
+        
+
+if __name__ == "__main__":
+
+        numActions=100
+        obj=CreateEnvironment()
+        obj.create(numActions)
+
+                

### 2017-10-11 EUCBV/codes/medianElim.py

@@ -1,0 +1,198 @@
+'''
+Created on Jul 28, 2015
+
+@author: Subhojyoti
+'''
+
+import math
+import random
+import numpy
+#import statistics
+
+class medianElim(object):
+    '''
+    classdocs
+    '''
+    
+    min1=-9999999
+    
+    def __init__(self):
+        '''
+        Constructor
+        '''
+        #print self.numRounds
+        #print self.means
+        
+    
+    def rewards(self,choice,t):
+        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+        return random.gauss(self.means[choice],self.variance[choice])
+    
+    
+    def remArms(self):
+        count=0
+        arm=-1
+        for i in range(self.numActions):
+            if self.B[i]!=-1:
+                count=count+1
+                arm=i
+        return count
+        
+    def medianElimimation(self,arms,epsilon,delta,wrong,turn):
+        
+        self.numActions = arms
+        self.horizon=300000
+        
+        self.bestAction=self.numActions-2
+
+        self.means =[0.1 for i in range(self.numActions)]
+        self.variance =[0.7 for i in range(self.numActions)]
+
+
+        i=(1*self.numActions)/3
+        while i<self.numActions:
+            self.means[i]=0.8
+            self.variance[i]=0.1
+            i=i+1
+
+        '''
+        i=(2*self.numActions)/3
+        while i<self.numActions:
+            self.means[i]=0.03
+            i=i+1
+        '''
+        self.means[self.bestAction]=0.9
+        self.variance[self.bestAction]=0.7
+        
+
+        print "Means: "+str(self.means)
+
+        self.arm_reward = [0]*self.numActions
+        
+        self.timestep=0
+        self.B=[0 for i in range(self.numActions)]
+        
+        self.payoffSums = [0] * self.numActions
+        self.numPlays = [0] * self.numActions
+        self.avgPayOffSums = [0] * self.numActions
+        
+        self.cumulativeReward = 0
+        self.bestActionCumulativeReward = 0
+        self.regret = 0
+        
+        self.arm_reward = [0]*self.numActions
+
+        self.actionRegret=[]
+
+        l=1
+        epsilon_l=epsilon*0.25
+        delta_l=delta*0.5
+        
+        while True:
+            
+            print "\n\nRound: "+str(l)
+            self.numRounds = int(math.ceil((1/(epsilon_l*0.5))*math.log(3/delta_l)))
+            print "nm: "+str(self.numRounds)
+            
[…]

### 2017-10-11 EUCBV/codes/plot5.py

@@ -1,0 +1,266 @@
+'''
+Created on Sept 5, 2016
+
+@author: Subhojyoti
+'''
+
+from matplotlib import pyplot as plt
+import numpy
+import fileinput
+import threading
+import  multiprocessing
+from multiprocessing import Manager
+
+
+class plot4(object):
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+
+    out_file='NewExpt/expt5/plotFinal'
+
+    def column(self,A, j):
+        return [A[i][j] for i in range(len(A))]
+
+    def transpose(self,A):
+        return [self.column(A, j) for j in range(len(A[0]))]
+
+    def plot_show(self,actionRegret,legend):
+
+        episode=[]
+
+        for t in range(0,self.timestep):
+            actionRegret[t]=actionRegret[t]/self.limit
+            episode.append(t);
+
+
+        #print self.actionRegret
+        #plot1,=plt.plot(episode,actionRegret,'r--',color='red',label='ClusUCB');
+        #plot2,=plt.plot(episode,actionRegret1,color='green',label='MOSS');
+        ax1 = plt.subplot(111)
+        plt.ylabel('Cumulative Regret',fontsize=18)
+        plt.xlabel('timesteps',fontsize=18)
+        ax1.plot(episode, actionRegret,label=legend)
+
+
+        plt.legend(bbox_to_anchor=(0., 1.02, 1., .102), loc=2,
+               ncol=2, mode="expand", borderaxespad=0.)
+
+        plt.show()
+
+    def fileReadWrite(self,id,name,filename,actionRegret):
+
+
+        t=0
+        count=0
+        for line in fileinput.input([filename]):
+
+            try:
+
+                line1=line.split("\n")
+                take=float(line1[0])
+
+
+                actionRegret[t]=actionRegret[t]+take
+                t=t+1
+                if t==self.timestep:
+                    t=0
+                    count=count+1
+                    print str(filename)+": "+str(count)
+
+                #prev=take
+                '''
+                if count==6:
+                    print t
+                    break
+                '''
+            except ValueError,e:
+                print  str(filename)+ " Error:" +str(e) +": Count: " +str(count)+ " t: "+str(t)
[…]

### 2017-10-11 EUCBV/codes/ucb1.py

@@ -1,0 +1,155 @@
+'''
+Created on Oct 6, 2015
+
+@author: Subhojyoti
+'''
+
+import math
+import random
+import numpy
+
+class ucb1(object):
+    '''
+    classdocs
+    '''
+
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+        
+        
+    #UpperBound Definition
+    def upperBound(self, step, numPlays):
+        return math.sqrt(2 * math.log(step + 1) / numPlays)
+    
+     
+    #Calculate rewards
+    def rewards(self,choice):
+        #Gaussain Reward
+        #return random.gauss(self.means[choice],1)
+        #Bernoulli Reward(1 sample from Binomial Distribution)
+        return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+        
+    def ucb1(self,numActions):
+    
+        #Set the environment
+        self.numActions=numActions
+        
+        self.payoffSums = [0] * self.numActions
+        self.numPlays = [0] * self.numActions
+        self.ucbs = [0] * self.numActions
+        self.upbs = [0] * self.numActions
+        #self.numRounds = 3000000
+        self.numRounds = 60000
+        #numRounds = 250000
+        
+        self.arm_reward = [0]*numActions
+
+        self.bestAction=self.numActions-2
+
+        self.means =[0.06 for i in range(self.numActions)]
+        
+
+        for i in range(self.numActions/3):
+            self.means[i]=0.01
+
+        '''
+        i=(2*self.numActions)/3
+        while i<self.numActions:
+            self.means[i]=0.03
+            i=i+1
+        '''
+        self.means[self.bestAction]=0.1
+        
+        
+        # initialize empirical sums pull each arm once
+        t=1
+        cumulativeReward = 0
+        bestActionCumulativeReward = 0
+        self.actionRegret=[]
+        
+        for i in range(self.numActions):
+            theReward = self.rewards(i)
+
+            
+            action=i
+            self.arm_reward[action]=self.arm_reward[action]+theReward
+            self.numPlays[action] += 1
+            self.payoffSums[action] += theReward
+
+            cumulativeReward += theReward
+            bestActionCumulativeReward += theReward if action == self.bestAction else self.rewards(self.bestAction)
+            regret = bestActionCumulativeReward - cumulativeReward
+            
+            self.actionRegret.append(regret)
+            
+            t = t + 1
+            
+
+        while True:
[…]

### 2017-10-11 EUCBV/codes/ucb1_expt2.py

@@ -1,0 +1,180 @@
+'''
+Created on Oct 6, 2015
+
+@author: Subhojyoti
+'''
+
+import math
+import random
+import numpy
+
+class ucb1_2(object):
+    '''
+    classdocs
+    '''
+
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+        
+        
+    
+    def upperBound(self, step, numPlays):
+        return math.sqrt(2 * math.log(step + 1) / numPlays)
+    
+     
+    def rewards(self,choice):
+        return random.gauss(self.means[choice],self.variance[choice])
+        #print sum(numpy.random.binomial(1,self.means[choice],200))/200.0
+        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+        
+    def ucb1(self,numActions):
+    
+        #Set the environment
+        self.numActions=numActions
+        
+        self.payoffSums = [0] * self.numActions
+        self.numPlays = [0] * self.numActions
+        self.ucbs = [0] * self.numActions
+        self.upbs = [0] * self.numActions
+        #self.numRounds = 3000000
+        self.numRounds = 300000
+        #numRounds = 250000
+        
+        self.arm_reward = [0]*numActions
+        
+        #bestAction=arms/2
+        self.bestAction=self.numActions-2
+        
+        
+        self.means =[0.01 for i in range(self.numActions)]
+        self.variance =[0.25 for i in range(self.numActions)]
+        
+
+        for i in range(self.numActions/3):
+            self.means[i]=0.07
+            self.variance[i]=0.01
+
+
+        '''
+        i=(2*self.numActions)/3
+        while i<self.numActions:
+            self.means[i]=0.03
+            i=i+1
+        '''
+        self.means[self.bestAction]=0.09
+        self.variance[self.bestAction]=0.25
+        
+        
+        # initialize empirical sums
+        t=1
+        cumulativeReward = 0
+        bestActionCumulativeReward = 0
+        self.actionRegret=[]
+        
+        for i in range(self.numActions):
+            theReward = self.rewards(i)
+            #self.numPlays[i]=self.numPlays[i]+1
+            
+            action=i
+            self.arm_reward[action]=self.arm_reward[action]+theReward
+            self.numPlays[action] += 1
+            self.payoffSums[action] += theReward
+            
+            #f1.writelines("ucbs: (%s)" % (', '.join(["%.8f" % ucb for ucb in ucbs])))
[…]

### 2017-10-11 EUCBV/codes/ucbV.py

@@ -1,0 +1,171 @@
+'''
+Created on May 10, 2016
+
+@author: Subhojyoti
+'''
+
+import math
+import random
+import numpy
+
+class ucbV(object):
+    '''
+    classdocs
+    '''
+
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+        
+        
+    #UpperBound Definition
+    def upperBound(self, step, numPlays,payoffSums,sqpayoffSums):
+
+        vj=1.0/numPlays*((payoffSums - (payoffSums/numPlays))*(payoffSums - (payoffSums/numPlays)))
+        return (math.sqrt((2*vj*math.log(step+1))/numPlays)+math.log(step+1)/numPlays)
+    
+     
+    #Calculate rewards
+    def rewards(self,choice):
+        #Gaussain Reward
+        #return random.gauss(self.means[choice],1)
+        #Bernoulli Reward(1 sample from Binomial Distribution)
+        return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+        
+    def ucbV(self,numActions):
+    
+        #Set the environment
+        self.numActions=numActions
+        
+        self.payoffSums = [0] * self.numActions
+        self.sqpayoffSums = [0] * self.numActions
+        self.numPlays = [0] * self.numActions
+        self.ucbs = [0] * self.numActions
+        self.upbs = [0] * self.numActions
+        #self.numRounds = 3000000
+        self.numRounds = 60000
+        #numRounds = 250000
+        
+        self.arm_reward = [0]*numActions
+
+        self.bestAction=self.numActions-2
+        
+
+        self.means =[0.07 for i in range(self.numActions)]
+        
+        '''
+        i=(1*self.numActions)/3
+        while i<self.numActions:
+            self.means[i]=0.05
+            i=i+1
+        
+        i=(2*self.numActions)/3
+        while i<self.numActions:
+            self.means[i]=0.03
+            i=i+1
+        '''
+        
+        self.means[self.bestAction]=0.1
+        
+        cumulativeReward = 0
+        bestActionCumulativeReward = 0
+        self.actionRegret=[]
+
+        # initialize empirical sums pull each arm once
+        
+        t=1
+       
+        for i in range(self.numActions):
+            theReward = self.rewards(i)
+            self.payoffSums[i] += theReward
+            self.sqpayoffSums[i] += abs( theReward*theReward)
+            self.numPlays[i]=self.numPlays[i]+1
+                
+            cumulativeReward += theReward
[…]

### 2017-10-11 EUCBV/codes/ucbV_expt2.py

@@ -1,0 +1,207 @@
+'''
+Created on May 10, 2016
+
+@author: Subhojyoti
+'''
+
+import math
+import random
+import numpy
+
+class ucbV(object):
+    '''
+    classdocs
+    '''
+
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+        
+        
+    
+    def upperBound(self, step, numPlays,payoffSums,sqpayoffSums):
+        #return math.sqrt(2 * math.log(step + 1) / numPlays)
+        #x=payoffSums / numPlays
+        #print sqpayoffSums,numPlays,step
+        
+        vj=abs(((sqpayoffSums/numPlays) - (payoffSums/numPlays)*(payoffSums/numPlays)))
+        #vj=1.0/numPlays*((payoffSums - (payoffSums/numPlays))*(payoffSums - (payoffSums/numPlays)))
+        #print vj
+        return (math.sqrt((2.0*vj*math.log(step+1))/numPlays)+math.log(step+1)/numPlays)
+    
+     
+    def rewards(self,choice):
+        return random.gauss(self.means[choice],self.variance[choice])
+        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+        
+    def ucb1(self,numActions):
+    
+        #Set the environment
+        self.numActions=numActions
+        
+        self.payoffSums = [0] * self.numActions
+        self.sqpayoffSums = [0] * self.numActions
+        self.numPlays = [0] * self.numActions
+        self.ucbs = [0] * self.numActions
+        self.upbs = [0] * self.numActions
+        #self.numRounds = 3000000
+        self.numRounds = 300000
+        #numRounds = 250000
+        
+        self.arm_reward = [0]*numActions
+        
+        #bestAction=arms/2
+        self.bestAction=self.numActions-2
+
+        self.means =[0.01 for i in range(self.numActions)]
+        self.variance =[0.25 for i in range(self.numActions)]
+
+
+        i=(1*self.numActions)/3
+        while i<self.numActions:
+            self.means[i]=0.07
+            self.variance[i]=0.01
+            i=i+1
+
+        '''
+        i=(2*self.numActions)/3
+        while i<self.numActions:
+            self.means[i]=0.03
+            i=i+1
+        '''
+        self.means[self.bestAction]=0.09
+        self.variance[self.bestAction]=0.25
+
+        '''
+        for i in range(0,1*self.numActions/3):
+            self.means[i]=0.1
[…]

### 2017-10-11 EUCBV/codes/ucbV_expt3.py

@@ -1,0 +1,192 @@
+'''
+Created on May 10, 2016
+
+@author: Subhojyoti
+'''
+
+import math
+import random
+import numpy
+import fileinput
+
+class ucbV(object):
+    '''
+    classdocs
+    '''
+
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+        
+        
+    
+    def upperBound(self, step, numPlays,payoffSums,sqpayoffSums):
+        #return math.sqrt(2 * math.log(step + 1) / numPlays)
+        #x=payoffSums / numPlays
+        #print sqpayoffSums,numPlays,step
+        
+        vj=abs(((sqpayoffSums/numPlays) - (payoffSums/numPlays)*(payoffSums/numPlays)))
+        #vj=1.0/numPlays*((payoffSums - (payoffSums/numPlays))*(payoffSums - (payoffSums/numPlays)))
+        #print vj
+        return (math.sqrt((2*vj*math.log(step+1))/numPlays)+math.log(step+1)/numPlays)
+    
+    def readenv(self):
+        data=[]
+        filename="env/env1.txt"
+        for line in fileinput.input([filename]):
+
+            try:
+                line1 = [line.split(", ") or line.split("\n") ]
+                #print numpy.shape(line1)
+                #print line1
+                take=[]
+                for i in range(len(line1[0])):
+                    take.append(float(line1[0][i]))
+                #print take
+                data.append(take)
+            except ValueError,e:
+                print e
+        #print data
+        self.means=(data[0])
+        self.variance=(data[1])
+
+    def rewards(self,choice):
+        return random.gauss(self.means[choice],self.variance[choice])
+        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+        
+    def ucb1(self,numActions):
+    
+        #Set the environment
+        self.numActions=numActions
+        
+        self.payoffSums = [0] * self.numActions
+        self.sqpayoffSums = [0] * self.numActions
+        self.numPlays = [0] * self.numActions
+        self.ucbs = [0] * self.numActions
+        self.upbs = [0] * self.numActions
+        #self.numRounds = 3000000
+        self.numRounds = 400000
+        #numRounds = 250000
+        
+        self.arm_reward = [0]*numActions
+        
+        #bestAction=arms/2
+        self.bestAction=self.numActions-2
+
+        self.means=[]
+        self.variance=[]
+        self.readenv()
+        
+        cumulativeReward = 0
[…]

### 2017-10-11 EUCBV/codes/ucbV_expt4.py

@@ -1,0 +1,192 @@
+'''
+Created on May 10, 2016
+
+@author: Subhojyoti
+'''
+
+import math
+import random
+import numpy
+import fileinput
+
+class ucbV(object):
+    '''
+    classdocs
+    '''
+
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+        
+        
+    
+    def upperBound(self, step, numPlays,payoffSums,sqpayoffSums):
+        #return math.sqrt(2 * math.log(step + 1) / numPlays)
+        #x=payoffSums / numPlays
+        #print sqpayoffSums,numPlays,step
+        
+        vj=abs(((sqpayoffSums/numPlays) - (payoffSums/numPlays)*(payoffSums/numPlays)))
+        #vj=1.0/numPlays*((payoffSums - (payoffSums/numPlays))*(payoffSums - (payoffSums/numPlays)))
+        #print vj
+        return (math.sqrt((2*vj*math.log(step+1))/numPlays)+math.log(step+1)/numPlays)
+    
+    def readenv(self):
+        data=[]
+        filename="env/env3.txt"
+        for line in fileinput.input([filename]):
+
+            try:
+                line1 = [line.split(", ") or line.split("\n") ]
+                #print numpy.shape(line1)
+                #print line1
+                take=[]
+                for i in range(len(line1[0])):
+                    take.append(float(line1[0][i]))
+                #print take
+                data.append(take)
+            except ValueError,e:
+                print e
+        #print data
+        self.means=(data[0])
+        self.variance=(data[1])
+
+    def rewards(self,choice):
+        return random.gauss(self.means[choice],self.variance[choice])
+        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
+        
+    def ucb1(self,numActions):
+    
+        #Set the environment
+        self.numActions=numActions
+        
+        self.payoffSums = [0] * self.numActions
+        self.sqpayoffSums = [0] * self.numActions
+        self.numPlays = [0] * self.numActions
+        self.ucbs = [0] * self.numActions
+        self.upbs = [0] * self.numActions
+        #self.numRounds = 3000000
+        self.numRounds = 400000
+        #numRounds = 250000
+        
+        self.arm_reward = [0]*numActions
+        
+        #bestAction=arms/2
+        self.bestAction=self.numActions-2
+
+        self.means=[]
+        self.variance=[]
+        self.readenv()
+        
+        cumulativeReward = 0
[…]

### 2017-10-14 Chapter1/ThesisIntro.tex
Latest on 15/10/2017

This document provides a simple template of how the provided
\verb+iitmdiss.cls+ \LaTeX\ class is to be used.  Also provided are
several useful tips to do various things that might be of use when you
write your thesis.

Before reading any further please note that you are strongly advised
against changing any of the formatting options used in the class
provided in this directory, unless you are absolutely sure that it
does not violate the IITM formatting guidelines.  \emph{Please do not
  change the margins or the spacing.}  If you do change the formatting
you are on your own (don't blame me if you need to reprint your entire
thesis).  In the case that you do change the formatting despite these
warnings, the least I ask is that you do not redistribute your style
files to your friends (or enemies).

It is also a good idea to take a quick look at the formatting
guidelines.  Your office or advisor should have a copy.  If they
don't, pester them, they really should have the formatting guidelines
readily available somewhere.

To compile your sources run the following from the command line:
\begin{verbatim}
% latex thesis.tex
% bibtex thesis
% latex thesis.tex
% latex thesis.tex
\end{verbatim}
Modify this suitably for your sources.

To generate PDF's with the links from the \verb+hyperref+ package use
the following command:
\begin{verbatim}
% dvipdfm -o thesis.pdf thesis.dvi
\end{verbatim}

\section{Package Options}

Use this thesis as a basic template to format your thesis.  The
\verb+iitmdiss+ class can be used by simply using something like this:
\begin{verbatim}
\documentclass[PhD]{iitmdiss}  
\end{verbatim}

To change the title page for different degrees just change the option
from \verb+PhD+ to one of \verb+MS+, \verb+MTech+ or \verb+BTech+.
The dual degree pages are not supported yet but should be quite easy
to add.  The title page formatting really depends on how large or
small your thesis title is.  Consequently it might require some hand
tuning.  Edit your version of \verb+iitmdiss.cls+ suitably to do this.
I recommend that this be done once your title is final.

To write a synopsis simply use the \verb+synopsis.tex+ file as a
simple template.  The synopsis option turns this on and can be used as
shown below.
\begin{verbatim}
\documentclass[PhD,synopsis]{iitmdiss}                                
\end{verbatim}

Once again the title page may require some small amount of fine
tuning.  This is again easily done by editing the class file.

This sample file uses the \verb+hyperref+ package that makes all
labels and references clickable in both the generated DVI and PDF
files.  These are very useful when reading the document online and do
not affect the output when the files are printed.

\section{Example Figures and tables}

Fig.~\ref{fig:iitm} shows a simple figure for illustration along with
a long caption.  The formatting of the caption text is automatically
single spaced and indented.  Table~\ref{tab:sample} shows a sample
table with the caption placed correctly.  The caption for this should
always be placed before the table as shown in the example.

\begin{figure}[htpb]
  \begin{center}
    \resizebox{50mm}{!} {\includegraphics *{iitm.eps}}
    \resizebox{50mm}{!} {\includegraphics *{iitm.eps}}
    \caption {Two IITM logos in a row.  This is also an
      illustration of a very long figure caption that wraps around two
      two lines.  Notice that the caption is single-spaced.}
  \label{fig:iitm}
  \end{center}
\end{figure}

\begin{table}[htbp]
  \caption{A sample table with a table caption placed
    appropriately. This caption is also very long and is
    single-spaced.  Also notice how the text is aligned.}
  \begin{center}
  \begin{tabular}[c]{|c|r|} \hline
    $x$ & $x^2$ \\ \hline
    1  &  1   \\
    2  &  4  \\
    3  &  9  \\
    4  &  16  \\
    5  &  25  \\
    6  &  36  \\
    7  &  49  \\
    8  &  64  \\ \hline
  \end{tabular}
  \label{tab:sample}
  \end{center}
\end{table}

\section{Bibliography with BIB\TeX}

I strongly recommend that you use BIB\TeX\ to automatically generate
your bibliography.  It makes managing your references much easier.  It
is an excellent way to organize your references and reuse them.  You
can use one set of entries for your references and cite them in your
thesis, papers and reports.  If you haven't used it anytime before
please invest some time learning how to use it.

I've included a simple example BIB\TeX\ file along in this directory
called \verb+refs.bib+.  The \verb+iitmdiss.cls+ class package which
is used in this thesis and for the synopsis uses the \verb+natbib+
package to format the references along with a customized bibliography
style provided as the \verb+iitm.bst+ file in the directory containing
\verb+thesis.tex+.  Documentation for the \verb+natbib+ package should
be available in your distribution of \LaTeX.  Basically, to cite the
author along with the author name and year use \verb+\cite{key}+ where
\verb+key+ is the citation key for your bibliography entry.  You can
also use \verb+\citet{key}+ to get the same effect.  To make the
citation without the author name in the main text but inside the
parenthesis use \verb+\citep{key}+.  The following paragraph shows how
citations can be used in text effectively.

More information on BIB\TeX\ is available in the book by
\cite{lamport:86}.  There are many
references~\citep{lamport:86,prabhu:xx} that explain how to use
BIB\TeX.  Read the \verb+natbib+ package documentation for more
details on how to cite things differently.

Here are other references for example.  \citet{viz:mayavi} presents a
Python based visualization system called MayaVi in a conference paper.
\citet{pan:pr:flat-fst} illustrates a journal article with multiple
authors.  Python~\citep{py:python} is a programming language and is
cited here to show how to cite something that is best identified with
a URL.

\section{Other useful \LaTeX\ packages}

The following packages might be useful when writing your thesis.

\begin{itemize}  
\item It is very useful to include line numbers in your document.
  That way, it is very easy for people to suggest corrections to your
  text.  I recommend the use of the \texttt{lineno} package for this
  purpose.  This is not a standard package but can be obtained on the
  internet.  The directory containing this file should contain a
  lineno directory that includes the package along with documentation
  for it.

\item The \texttt{listings} package should be available with your
  distribution of \LaTeX.  This package is very useful when one needs
  to list source code or pseudo-code.

\item For special figure captions the \texttt{ccaption} package may be
  useful.  This is specially useful if one has a figure that spans
  more than two pages and you need to use the same figure number.

\item The notation page can be entered manually or automatically
  generated using the \texttt{nomencl} package.

\end{itemize}

More details on how to use these specific packages are available along
with the documentation of the respective packages.

### 2017-10-14 Chapter1/intro.tex
Latest on 15/10/2017

In today's world a large number of problems in science and engineering, robotics and 
game playing, resource management, financial portfolio
management, medical treatment design, ad placement, website optimization and packet routing can be modeled as sequential decision-making under uncertainty. Many of these real-world interesting
sequential decision-making problems can be formulated as reinforcement
learning (RL) problems (\cite{bertsekas1996neuro}, \cite{sutton1998reinforcement}). In an RL problem, an agent interacts with a dynamic, stochastic, and unknown environment, with the goal of finding an action-selection strategy or policy that optimizes some long-term performance measure. Every time when the agent interacts with the environment it receives a signal/reward from the environment based on which it modifies its policy. The agent learns to optimize the choice of actions over several time steps which is learned from the sequences of data that it receives from the environment. This is the crux of online sequential learning. This is in contrast to supervised learning methods that deal with labeled data which are independently and identically distributed (i.i.d.) samples from the domain and train some classifier on the entire training dataset to learn the pattern of this distribution to predict future samples (test dataset) with the assumption that it is sampled from the same domain, whereas the RL agent learns from the samples that are collected from the trajectories generated by its sequential interaction with the system. For an RL agent the trajectory consists of a series of sequential interactions whereby it transitions from one state to another following some dynamics intrinsic to the environment while collecting the reward till some stopping condition is reached. This is known as an episode. For a single-step interaction, i.e., when the episode terminates after a single transition, the problem is captured by the multi-armed bandit (MAB) model. Our work will focus on this idea of MAB model.

### 2017-10-14 Chapter1/motivation.tex
Latest on 15/10/2017

The MAB model fits very well in various real-world scenarios that can be modeled as sequential decision-making problems. Some of which are mentioned as follows:-
\begin{enumerate}
\item \emph{Online Shop Domain (\cite{ghavamzadeh2015bayesian}):} In the online shop domain, a retailer aims to maximize profit by sequentially suggesting products to online shopping customers. In this scenario, at every timestep,  the retailer displays an item to a customer from a pool of items which has the highest probability of being selected by the customer. The episode ends when the customer selects or does not select a product (which will be considered as a loss to the retailer) and the process is again repeated till a pre-specified number of times with the retailer gathering valuable information regarding the customer from this behaviour and modifying its policy to display the next item.
\item \emph{Medical Treatment Design (\cite{thompson1933likelihood}):} Here at every timestep, the agent chooses to administer one out of several treatments sequentially on a patient. Here, the episode ends when the patient responds well or does not respond well to the treatment whereby the agent modifies its policy for the next suggestion.
\item \emph{Financial Portfolio Management:} In financial portfolio management MAB model can be used. Here, the agent is faced with the choice of selecting the most profitable stock option out of several stock options. The simplest strategy where we can employ a bandit model is this; at the start of every trading session the agent suggests a stock to purchase worth Re $1$, while at the closing of the trading session it sells off the stock to witness its value after a day's trading. The  profit recorded is treated as the reward revealed by the environment and the agent modifies its policy for the next day.
%\item \emph{Product Selection:} A company wants to introduce a new product in market and there is a clear separation of the test phase from the commercialization phase. In this case the company tries to minimize the loss it might incur in the commercialization phase by testing as much as possible in the test phase. So from the several variants of the product that are in the test phase the learning agent must suggest a product variant at the end of the test phase that has the highest probability of minimizing loss in the commercialization phase(see \cite{bubeck2011pure}). 
%\item \emph{Mobile Phone Channel Allocation:} Another similar problem as above concerns channel allocation for mobile phone communications (\cite{audibert2009exploration}). Here there is a clear separation between the allocation phase and communication phase whereby in the allocation phase a learning algorithm has to explore as many channels as possible to suggest the best possible channel. Each evaluation of a channel is noisy and the learning algorithm must come up with the best possible suggestion within a very small  number of attempts. 
\end{enumerate}

	The thresholding bandit problem is a special case of combinatorial MAB problem where the learner has to suggest the best set of arms above a real valued threshold. This has several relevant industrial applications. The variants of TopM problem (identifying the best $M$ arms from $K$ given arms) can be readily used in the thresholding problem.

\begin{enumerate}
\item \emph{Product Selection:} A company wants to introduce a new product in market and there is a clear separation of the test phase from the commercialization phase. In this case the company tries to minimize the loss it might incur in the commercialization phase by testing as much as possible in the test phase. So from the several variants of the product that are in the test phase the learning agent must suggest the product variant(s) that are above a particular threshold $\tau$ at the end of the test phase that have the highest probability of minimizing loss in the commercialization phase. A similar problem has been discussed for single best product variant identification without threshold in \cite{bubeck2011pure}. 
\item \emph{Mobile Phone Channel Allocation:} Another similar problem as above concerns channel allocation for mobile phone communications (\cite{audibert2009exploration}). Here there is a clear separation between the allocation phase and communication phase whereby in the allocation phase a learning algorithm has to explore as many channels as possible to suggest the best possible set of channel(s) that are above a particular threshold $\tau$. The threshold depends on the subscription level of the customer. With higher subscription the customer is allowed better channel(s) with the $\tau$ set high. Each evaluation of a channel is noisy and the learning algorithm must come up with the best possible suggestion within a very small  number of attempts.
\item \emph{Anomaly Detection and Classification:} Thresholding bandit can also be used for anomaly detection and classification where we define a cutoff level $\tau$ and for any samples above this cutoff gets classified as an anomaly. For further reading we point the reader to section 3 of \cite{locatelli2016optimal}.
\end{enumerate}

	In all the above examples the MAB model performs well mainly because all of them suffer from \textit{exploration-exploitation dilemma}. This is characterized by action-selection choice faced by the agent where it must decide whether to stay with the action yielding highest reward till now or to explore newer actions which might be more profitable in the long run. MAB's are suited for such scenarios because 
\begin{enumerate}
\item They are easy to implement.
\item The switch between exploration and exploitation is more well defined theoretically.
\item They perform well empirically.
\end{enumerate}

### 2017-10-14 Chapter1/objective.tex
Latest on 15/10/2017

The main objectives of our work.
\begin{enumerate}
\item UCB-Improved has several shortfalls. It conducts too much early exploration and the arm elimination is very conservative. Our proposed algorithm tries to remedy this. We also explore the idea of employing clustering techniques in MAB which, till now has only been studied in the contextual bandit setup (see \cite{li2010contextual}, \cite{bui2012clustered}, \cite{cesa2013gang} , \cite{gentile2014online}, \cite{nguyen2014dynamic}). We propose an algorithm that minimizes cumulative regret in the multi-armed stochastic bandit setup using clustering and improved exploration and performs at par with the best algorithms currently available. We also show that there is a distinct advantage of using clustering in action elimination type of algorithms in MABs.
\item We also propose an algorithm that minimizes probability of error in a combinatorial stochastic bandit setup whereby the learning algorithm, provided with a threshold $\tau$, proposes the best set of arms such that $r_{i}\geq \tau$ at every timestep using action elimination method. This problem is similar to the pure exploration setup with a major difference being that the algorithm has to suggest as many arms whose $r_{i}$ is above $\tau$ which may be more than one arm. Our proposed methodology is in contrast with APT which uses an UCB1 type of strategy to suggest the best arms above the threshold whereas we employ an UCB-Improved type of strategy with better exploration parameters.
\item In both the above scenarios we intend to explore both the theoretical guarantees and empirical performance and verify against the best algorithms available in the field.     
\end{enumerate}

### 2017-10-14 Chapter1/probDef.tex
Latest on 15/10/2017

%Formally, the domain is characterized by the following
%model:
%\begin{itemize}
%\item 
%\end{itemize}
%• A set of possible customer states, X. States can represent intrinsic
%features of the customer such as gender and age, but also dynamic
%quantities such as the items in his shopping cart, or his willingness
%to shop;
%• A set of possible product suggestions and advertisements, A;
%• A probability kernel, P, defined below.
%An episode in the online shop domain begins at time t = 0, when
%a customer with features x0 2 X enters the online shop. Then, a sequential
%interaction between the customer and the online shop begins,
%where at each step t = 0, 1, 2, . . . , an advertisement at 2 A is shown to the customer, and following that the customer makes a decision to
%either (i) add a product to his shopping cart; (ii) not buy the product,
%but continue to shop; (iii) stop shopping and check out. Following the
%customers decision, his state changes to xt+1 (reflecting the change in
%the shopping cart, willingness to continue shopping, etc.). We assume
%that this change is captured by a probability kernel P(xt+1| xt, at).
%When the customer decides to check out, the episode ends, and a
%profit is obtained according to the items he had added to his cart. The
%goal is to find a product suggestion policy, x ! a 2 A, that maximizes
%the expected total profit.
%When the probabilities of customer responses P are known in advance,
%calculating an optimal policy for the online shop domain is basically
%a planning problem, which may be solved using traditional methods
%for resource allocation [Powell, 2011]. A more challenging, but realistic,
%scenario is when P is not completely known beforehand, but has
%to be learned while interacting with customers. A second advantage concerns what is known as the exploitation–
%exploration dilemma: should the decision-maker display only the most
%profitable product suggestions according to his current knowledge
%about P, or rather take exploratory actions that may turn out to be
%less profitable, but provide useful information for future decisions? The
%Bayesian method offers a principled approach to dealing with this difficult
%problem by explicitly quantifying the value of exploration, made
%possible by maintaining a distribution over P. The various parameter configurations in the online shop domain
%lead to the different learning problems surveyed in this paper. In particular:
%• For a single-step interaction, i.e., when the episode terminates
%after a single product suggestion, the problem is captured by the
%multi-armed bandit model of Chapter 3.

We formally define the MAB model in this section. We will mainly focus on the stochastic MAB model in our work. In this setting, the learning algorithm is provided with a set of decisions (or arms) with reward distributions unknown to the algorithm. These decisions can be the items to show the customers, or medical treatment, or the stock options. The learning proceeds in an iterative fashion, where in each timestep, the algorithm chooses an arm and receives a stochastic reward that is drawn from a stationary distribution specific to the arm selected.  There are two types of goal we will be focusing our work on:-

\begin{enumerate}
\item Maximizing cumulative reward over the entire time horizon
\item Minimizing probability of error in suggesting the best arm(s) at any timestep
\end{enumerate}

Given the goal of maximizing the cumulative reward, the learning algorithm faces the exploration-exploitation dilemma, i.e., in each round should the algorithm select the arm which has the highest observed mean reward so far 
(\textit{exploitation}), or should the algorithm choose a new arm to gain more knowledge of the true mean reward of the arms and thereby avert a sub-optimal greedy decision (\textit{exploration}).

Formally, let $r_i$, $i=1,\ldots,K$ denote the mean rewards of the $K$ arms and $r^* = \max_i r_i$ the optimal mean reward. The objective in the stochastic bandit problem is to maximize cumulative reward by  minimizing the cumulative regret, which is defined as follows:
\begin{align*}
R_{T}=r^{*}T - \sum_{i\in A} r_{i}N_{i}(T),
\end{align*}
where $T$ is the number of rounds, $N_{i}(T)=\sum_{m=1}^T I(I_m=i)$ is the number of times the algorithm chose arm $i$ up to round $T$.
The expected regret of an algorithm after $T$ rounds can be written as
%\newline
%\newline
\begin{align*}
\E[R_{T}]= \sum_{i=1}^K \E[N_i(T)] \Delta_i,
\end{align*}
where $\Delta_{i}=r^{*}-r_{i}$ denotes the gap between the means of the optimal arm and of the $i$-th arm.

	In the pure exploration thresholding bandit setup the goal is different than minimizing the cumulative regret. Here the learning algorithm is provided with a threshold $\tau$ and it has to output all such arms $i$ whose mean of reward distribution $r_{i}$ is above $\tau$ after $T$ rounds. This is a specific instance of combinatorial pure exploration where the learning algorithm can explore as much as possible given a fixed horizon $T$ and not be concerned with the usual exploration-exploitation dilemma. Let $A$ be the set of all arms. Formally we can define a set $S_{\tau}=\lbrace i\in A: r_{i}\geq \tau \rbrace$ and the complementary set $S_{\tau}^{C}=\lbrace i\in A: r_{i} < \tau \rbrace$. Also we define $\hat{S}_{\tau}=\hat{S}_{\tau}(T)\subset A$ and its complementary set $\hat{S}_{\tau}^{C}$ as the recommendation of the learning algorithm after $T$ rounds. Given such sets exists, the performance of the learning agent is measured by how much accuracy it can discriminate between $S_{\tau}$ and $S_{\tau}^{C}$ after time horizon $T$.  The loss $\Ls$ is defined as:-
\begin{align*}
\Ls (T) = I\big(\lbrace S_{\tau}\cap \hat{S}_{\tau}^{C}\neq \emptyset\rbrace    \cup    \lbrace\hat{S}_{\tau}\cap S_{\tau}^{C}\neq \emptyset\rbrace\big)
\end{align*}

The goal of the learning agent is to minimize $\Ls (T)$. So, the expected loss after $T$ rounds is 
\begin{align*}
\E[\Ls(T)] = \Pb\big(\lbrace S_{\tau}\cap \hat{S}_{\tau}^{C} \neq \emptyset \rbrace  \cup   \lbrace \hat{S}_{\tau}\cap S_{\tau}^{C} \neq \emptyset\rbrace\big)
\end{align*}

which we can say is the probability of making mistake, that is whether the learning agent at the end of round $T$ rejects arms from $S_{\tau}$ or accepts arms from $S_{\tau}^{C}$ in its final recommendation. Also, we are looking at an anytime algorithm, so the knowledge of $T$ may not be known to the learner.

%Another metric to judge the performance of an algorithm is the notion of simple regret whereby the learning algorithm tries to maximize instantaneous reward at the end of the time horizon $T$  and minimizing the simple regret. Simple regret is defined by:-
%\begin{align*}
%R'_{T}=r^{*} - r_{J_{T}}, \text{where $J_{T}$ is the recommended arm at the end of time horizon $T$}
%\end{align*}
%
%In the motivation section, example $1,2$ and $3$ are the problems minimizing cumulative regret, whereas $4$ and $5$ deal with minimizing simple regret. The latter problem in bandit literature is also known as \textit{pure exploration bandits}.

%The problem, gets more difficult when the $\Delta_{i}$'s are smaller and arm set is larger. Also let $\Delta=min_{i\in A}\Delta_{i}$, that is it is the minimum possible gap over all arms in $A$.

### 2017-10-14 Chapter2/intro.tex
Latest on 15/10/2017

In this chapter, we deal with the stochastic multi-armed bandit (SMAB) setting. In its classical form, stochastic MABs represent a sequential learning problem where a learner is exposed to a finite set of actions (or arms) and needs to choose one of the actions at each timestep. After choosing (or pulling) an arm the learner  receives a reward, which is conceptualized as an independent random draw from stationary distribution associated with the selected arm. Also, note that in SMAB, the distribution associated with each arm is fixed throughout the entire duration of the horizon denoted by $T$.

\begin{algorithm}[!th]
\caption{SMAB algorithm}
\label{alg:SMAB}
\begin{algorithmic}
\State {\bf Input:} Time horizon $T$, $K$ number of arms with unknown parameters of reward distribution
\State \For{ each timestep $t=1,2,\ldots, T$}
\State The learner chooses an arm $i\in\A$, where $A$ is the set of arms and $|A|=K$.
\State The learner observes the reward $X_{i,t}\sim^{i.i.d} D_{i,t}$ where, $D_{i,t}$ is the distribution associated with the arm $i$. 
\State \EndFor
\end{algorithmic}
\end{algorithm}

### 2017-10-14 Chapter2/motivation.tex
Latest on 15/10/2017

--- 2017-10-11 EUCBV/intro.tex
@@
-In this paper, we deal with the stochastic multi-armed bandit (MAB) setting.
-In its classical form, stochastic MABs represent a sequential learning problem where a learner is exposed to a finite set of actions (or arms) and needs to choose one of the actions at each timestep.
-After choosing (or pulling) an arm the learner  receives a reward, which is conceptualized as an independent random draw from stationary distribution associated with the selected arm.
-%Each of these rewards is random and drawn independently from the distribution associated with each arm. 
-The mean of the reward distribution associated with an arm $i$ is denoted by $r_i$ whereas the mean of the reward distribution of the optimal arm $*$ is denoted by $r^*$ such that $r_i < r^*, \forall i\in \A$, where $\A$ is the set of arms such that $|\A|=K$.
-With this formulation the learner faces the task of balancing exploitation and exploration.
-In other words, should the learner pull the arm which currently has the best known estimates or explore arms more thoroughly to ensure that a correct decision is being made.
-The objective in the stochastic bandit problem is to minimize the cumulative regret, which is defined as follows:
-\begin{align*}
-R_{T}=r^{*}T - \sum_{i\in \A} r_{i}z_{i}(T),
-\end{align*}
-where $T$ is the number of timesteps, and  $z_{i}(T)$ is the number of times the algorithm has chosen arm $i$ up to timestep $T$.
-The expected regret of an algorithm after $T$ timesteps can be written as,
-\begin{align*}
-\E[R_{T}]= \sum_{i=1}^{K} \E[z_i (T)] \Delta_i,
-\end{align*}
-where $\Delta_{i}=r^{*}-r_{i}$ is the gap between the means of the optimal arm and the $i$-th arm.
-
-% One of the fundamental assumptions in stochastic MAB is that the distribution associated with each arm does not change over the entire time horizon $T$.
-
+There has been a significant amount of research in the area of stochastic MABs.
+One of the earliest work can be traced to \cite{thompson1933likelihood}, which deals with  the problem of choosing between two treatments to administer on patients who come in sequentially.
 In recent years the MAB setting has garnered extensive popularity because of its simple learning  model and its practical applications in a wide-range of industries, including, but not limited to, mobile channel allocations, online advertising and computer simulation games.
-
-	%industry defined problems

### 2017-10-14 Chapter2/notation.tex
Latest on 15/10/2017

--- 2017-10-11 EUCBV/ealgo.tex
@@
-%%%%%%%%%%%%%%%% alg-custom-block %%%%%%%%%%%%
-%\algblock{ArmElim}{EndArmElim}
-%\algnewcommand\algorithmicArmElim{\textbf{\em Arm Elimination}}
-% \algnewcommand\algorithmicendArmElim{}
-%\algrenewtext{ArmElim}[1]{\algorithmicArmElim\ #1}
-%\algrenewtext{EndArmElim}{\algorithmicendArmElim}
-%
-%\algblock{ResParam}{EndResParam}
-%\algnewcommand\algorithmicResParam{\textbf{\em Reset Parameters}}
-% \algnewcommand\algorithmicendResParam{}
-%\algrenewtext{ResParam}[1]{\algorithmicResParam\ #1}
-%\algrenewtext{EndResParam}{\algorithmicendResParam}
-
-\begin{algorithm}[!h]
-\caption{EUCBV}
-\label{alg:eucbv}
-\begin{algorithmic}
-\State {\bf Input:} Time horizon $T$, exploration parameters $\rho$ and $\psi$.
-\State {\bf Initialization:} Set $m:=0$, $B_{0}:=\mathcal{A}$, $\epsilon_{0}:=1$, $M=\big \lfloor \frac{1}{2}\log_{2} \frac{T}{e}\big\rfloor$, $n_{0}=\big\lceil\frac{\log{(\psi T\epsilon_{0}^{2})}}{2\epsilon_{0}}\big\rceil$ and  $N_{0}=Kn_{0}$.
-\State Pull each arm once
-\For{$t=K+1,..,T$}	
-\State Pull arm $i\in \argmax_{j\in B_{m}}\bigg\lbrace \hat{r}_{j} + \sqrt{\frac{\rho(\hat{v}_{j}+2)\log{(\psi T\epsilon_{m})}}{4 z_{j}}} \bigg\rbrace$, where $z_j$ is the number of times arm $j$ has been pulled.
-%\State $t:=t+1$
-\ArmElim
-\State For each arm $i \in B_{m}$, remove arm $i$ from $B_{m}$ if,
-\begin{align*}
-%%%%%%%%%%%%%%%%%%%%%%%
-%& \hat{r}_{i} + \sqrt{\frac{\rho\hat{v}_{i}\log{(\psi T\epsilon_{m})}}{4 z_{i}} + \frac{\rho\log{(\psi T\epsilon_{m})}}{4 z_{i}}} < \max_{{j}\in B_{m}}\bigg\lbrace\hat{r}_{j} -\sqrt{\frac{\rho\hat{v}_{j}\log{(\psi T\epsilon_{m})}}{4 z_{j}} + \frac{\rho\log{(\psi T\epsilon_{m})}}{4 z_{j}}} \bigg\rbrace
-%%%%%%%%%%%%%%%%%%%%%%%
- \hat{r}_{i} + & \sqrt{\frac{\rho(\hat{v}_{i}+2)\log{(\psi T\epsilon_{m})}}{4 z_{i}}}  
-  < \max_{{j}\in B_{m}}\bigg\lbrace\hat{r}_{j} -\sqrt{\frac{\rho(\hat{v}_{j}+2)\log{(\psi T\epsilon_{m})}}{4 z_{j}}} \bigg\rbrace
-\end{align*}
-\EndArmElim
-
-\If{$t\geq N_{m}$ and $m\leq M$}
-\ResParam
-\State $\epsilon_{m+1}:=\frac{\epsilon_{m}}{2}$\vspace{0.5ex}
-\State $B_{m+1}:=B_{m}$
-\State $n_{m+1}:=\bigg\lceil\frac{\log{(\psi T\epsilon_{m+1}^{2})}}{2\epsilon_{m+1}}\bigg\rceil$
-\State $N_{m+1}:=t+|B_{m+1}| n_{m+1}$
-\State $m:=m+1$
-\EndResParam
-\EndIf
-\State Stop if $|B_{m}|=1$ and pull ${i}\in B_{m}$ till $T$ is reached.
-\EndFor
-\end{algorithmic}
-%\vspace*{-0.42em}
-\end{algorithm}
-%\vspace*{-0.42em}
-\textbf{2.1 Notations:} We denote the set of arms by $\A$, with the individual arms labeled $i$, where  $i=1,\ldots,K$.
+The mean of the reward distribution $D_i$ associated with an arm $i$ is denoted by $r_i$ whereas the mean of the reward distribution of the optimal arm $*$ is denoted by $r^*$ such that $r_i < r^*, \forall i\in \A$, where $\A$ is the set of arms such that $|\A|=K$.
+We denote the individual arms labeled $i$, where  $i=1,\ldots,K$.
 We denote an arbitrary round of EUCBV by $m$.
@@
 We denote the true variance of an arm by $\sigma_i^{2}$ while $\hat{v}_{i}(t)$ is the estimated variance, i.e., $\hat{v}_{i}(t)=\frac{1}{z_i(t)}\sum_{\ell=1}^{z_{i}(t)}(X_{i,\ell}-\hat{r}_{i})^{2}$.
-Whenever there is no ambiguity about the underlaying  time index $t$, for simplicity we neglect $t$ from the notations and simply use  $\hat{r}_i, \hat{v}_i,$ and $z_i$ to denote the respective quantities.
+Whenever there is no ambiguity about the underlying  time index $t$, for simplicity we neglect $t$ from the notations and simply use  $\hat{r}_i, \hat{v}_i,$ and $z_i$ to denote the respective quantities.
 We assume the rewards of all arms are bounded in $[0,1]$.
-
-\textbf{2.2 The algorithm:} Earlier round-based arm elimination algorithms like Median Elimination \citep{even2006action} and UCB-Improved mainly suffered from two basic problems: \\
-\begin{inparaenum}[\bfseries(i)]
-\item \textit{Initial exploration:} Both of these algorithms pull each arm equal number of times in each round, and hence waste a significant number of pulls in initial explorations. \\
-\item \textit{Conservative arm-elimination:} In UCB-Improved, arms are eliminated conservatively, i.e, only after $\epsilon_{m}<\frac{\Delta_{i}}{2}$, 
-% the sub-optimal arm $i$ is discarded with high probability. 
-where the quantity $\epsilon_{m}$ is initialized to $1$ and halved after every round.
-In the worst case scenario when $K$ is large, and the gaps are uniform  ($r_{1}=r_{2}=\cdots=r_{K-1}<r^{*}$) and small this results in very high regret.\\
-\end{inparaenum}
-%For any round $m$ UCB-Improved pulls all arms $n_{m}=\left\lceil \frac{ 2\log(T\epsilon_{m})}{\epsilon_{m}} \right\rceil$ number of times.
-The quantity $\epsilon_{m}$ is initialized to $1$ and halved after every round.
-\\
-	The EUCBV algorithm, which is mainly based on the arm elimination technique of the UCB-Improved algorithm,  remedies these by employing exploration regulatory factor $\psi$ and arm elimination parameter $\rho$ for aggressive elimination of sub-optimal arms.
-Along with these, similar to CCB \citep{liu2016modification} algorithm, EUCBV uses optimistic greedy sampling whereby at every timestep it only pulls the arm with the highest upper confidence bound rather than pulling all the arms equal number of times in each round.
-Also, unlike the UCB-Improved, UCB1, MOSS and OCUCB algorithms (which are based on mean estimation) EUCBV employs mean and variance estimates (as in \citet{audibert2009exploration}) for arm elimination.
-Further, we allow for arm-elimination at every time-step, which is in contrast to the earlier work (e.g., \citet{auer2010ucb}; \citet{even2006action}) where the arm elimination takes place only at the end of the respective exploration rounds.

### 2017-10-14 Chapter2/probDef.tex
Latest on 15/10/2017

--- 2017-10-11 EUCBV/intro.tex
@@
-In this paper, we deal with the stochastic multi-armed bandit (MAB) setting.
-In its classical form, stochastic MABs represent a sequential learning problem where a learner is exposed to a finite set of actions (or arms) and needs to choose one of the actions at each timestep.
-After choosing (or pulling) an arm the learner  receives a reward, which is conceptualized as an independent random draw from stationary distribution associated with the selected arm.
-%Each of these rewards is random and drawn independently from the distribution associated with each arm. 
-The mean of the reward distribution associated with an arm $i$ is denoted by $r_i$ whereas the mean of the reward distribution of the optimal arm $*$ is denoted by $r^*$ such that $r_i < r^*, \forall i\in \A$, where $\A$ is the set of arms such that $|\A|=K$.
-With this formulation the learner faces the task of balancing exploitation and exploration.
-In other words, should the learner pull the arm which currently has the best known estimates or explore arms more thoroughly to ensure that a correct decision is being made.
+With the formulation of SMAB stated in algorithm \ref{alg:SMAB}, the learner faces the task of balancing exploitation and exploration.
+In other words, should the learner pull the arm which currently has the best-known estimates (exploit) or explore arms more thoroughly to ensure that a correct decision is being made.
+This is termed as the \textit{exploration-exploitation dilemma}, one of the fundamental challenges of Reinforcement learning.
+
 	The objective in the stochastic bandit problem is to minimize the cumulative regret, which is defined as follows:
@@
 where $\Delta_{i}=r^{*}-r_{i}$ is the gap between the means of the optimal arm and the $i$-th arm.
-
-% One of the fundamental assumptions in stochastic MAB is that the distribution associated with each arm does not change over the entire time horizon $T$.
-
-	In recent years the MAB setting has garnered extensive popularity because of its simple learning  model and its practical applications in a wide-range of industries, including, but not limited to, mobile channel allocations, online advertising and computer simulation games.
-
-	%industry defined problems

### 2017-10-14 Chapter2/related.tex
Latest on 15/10/2017

--- 2017-10-11 EUCBV/related.tex
@@
-%There has been a significant amount of research in the area of stochastic MABs.
-One of the earliest work can be traced to \cite{thompson1933likelihood}, which deals with  the problem of choosing between two treatments to administer on patients who come in sequentially.
-Other seminal works include that of  \cite{robbins1952some} and then that of \cite{lai1985asymptotically} which established an asymptotic lower bound for the cumulative regret.
+	SMAB problems have been extensively studied in several earlier works such as \citet{thompson1933likelihood}, \citet{robbins1952some} and \citet{lai1985asymptotically}.
+Lai and Robbins in  \citet{lai1985asymptotically} established an asymptotic lower bound for the cumulative regret.
 It showed that for any consistent allocation strategy, we can have
-%$\liminf_{T \to \infty}\frac{\E[R_{T}]}{\log T}\geq\sum_{\{i:r_{i}<r^{*}\}}\frac{(r^{*}-r_{i})}{D(Q_{i}||Q^{*})},$
-%where $D(Q_{i}||Q^{*})$ is the Kullback-Leibler divergence between the reward densities $Q_{i}$ and $Q^{*}$, corresponding to arms with mean $r_{i}$ and $r^{*}$, respectively.
+\begin{align*}
+\liminf_{T \to \infty}\frac{\E[R_{T}]}{\log T}\geq\sum_{\{i:r_{i}<r^{*}\}}\frac{(r^{*}-r_{i})}{D(Q_{i}||Q^{*})}
+\end{align*}	
+where $D(Q_{i}||Q^{*})$ is the Kullback-Leibler divergence between the reward densities $Q_{i}$ and $Q^{*}$, corresponding to arms with mean $r_{i}$ and $r^{*}$, respectively.
 
-	Bandit problems have been extensively studied in several earlier works such as \citet{thompson1933likelihood}, \citet{robbins1952some} and \citet{lai1985asymptotically}.
-Lai and Robbins in  \citet{lai1985asymptotically} established an asymptotic lower bound for the cumulative regret.
-Over the years stochastic MABs have seen several algorithms with strong regret guarantees.
+	Over the years SMABs have seen several algorithms with strong regret guarantees.
 For further reference an interested reader can look into \citet{bubeck2012regret}.
@@
 
-	 The UCB-Improved algorithm, proposed in \citet{auer2010ucb}, is a round-based\footnote{An algorithm is \textit{round-based} if it pulls all the arms equal number of times in each round and then eliminates one or more arms that it deems  to be sub-optimal.} variant of UCB1, that
-incurs a gap-dependent regret bound of $O\left(\frac{K\log (T\Delta^{2})}{\Delta}\right)$, which is better than that of UCB1.
+	 The UCB-Improved algorithm, proposed in \citet{auer2010ucb}, is a round-based variant of UCB1.
+An algorithm is \textit{round-based} if it pulls all the arms equal number of times in each round and then eliminates one or more arms that it deems  to be sub-optimal.
+UCB-Improved incurs a gap-dependent regret bound of $O\left(\frac{K\log (T\Delta^{2})}{\Delta}\right)$, which is better than that of UCB1.
 On the other hand, the worst case gap-independent regret bound of UCB-Improved is $O\left(\sqrt{KT\log K}\right)$.

### 2017-10-14 Chapter3/contribution.tex
Latest on 15/10/2017

--- 2017-10-11 EUCBV/contribution.tex
@@
-In this paper we propose the Efficient-UCB-Variance (henceforth referred to as EUCBV) algorithm for the stochastic MAB setting.
+In this chapter we propose the Efficient-UCB-Variance (henceforth referred to as EUCBV) algorithm for the stochastic MAB setting.
 EUCBV combines the approach of UCB-Improved, CCB \citep{liu2016modification} and UCBV algorithms.
@@
 
-	The rest of the paper is organized as follows.
+	The rest of the chapter is organized as follows.
 In section~\ref{sec:eucbv} we present the  EUCBV algorithm.

### 2017-10-14 Chapter3/ealgo.tex
Latest on 15/10/2017

--- 2017-10-11 EUCBV/ealgo.tex
@@
-%%%%%%%%%%%%%%%% alg-custom-block %%%%%%%%%%%%
-%\algblock{ArmElim}{EndArmElim}
-%\algnewcommand\algorithmicArmElim{\textbf{\em Arm Elimination}}
-% \algnewcommand\algorithmicendArmElim{}
-%\algrenewtext{ArmElim}[1]{\algorithmicArmElim\ #1}
-%\algrenewtext{EndArmElim}{\algorithmicendArmElim}
-%
-%\algblock{ResParam}{EndResParam}
-%\algnewcommand\algorithmicResParam{\textbf{\em Reset Parameters}}
-% \algnewcommand\algorithmicendResParam{}
-%\algrenewtext{ResParam}[1]{\algorithmicResParam\ #1}
-%\algrenewtext{EndResParam}{\algorithmicendResParam}
-
 \begin{algorithm}[!h]
@@
 %\vspace*{-0.42em}
-\textbf{2.1 Notations:} We denote the set of arms by $\A$, with the individual arms labeled $i$, where  $i=1,\ldots,K$.
-We denote an arbitrary round of EUCBV by $m$.
-For simplicity, we assume that the optimal arm is unique and denote it by ${*}$.
-We denote the sample mean of the rewards for an arm $i$ at time instant $t$ by $\hat{r}_{i}(t)=\frac{1}{z_{i}(t)}\sum_{\ell=1}^{z_i(t)} X_{i,\ell}$, where $X_{i,\ell}$ is the reward sample received when arm $i$ is pulled for the $\ell$-th time, and $z_i(t)$ is the number of times arm $i$ has been pulled until timestep $t$.
-We denote the true variance of an arm by $\sigma_i^{2}$ while $\hat{v}_{i}(t)$ is the estimated variance, i.e., $\hat{v}_{i}(t)=\frac{1}{z_i(t)}\sum_{\ell=1}^{z_{i}(t)}(X_{i,\ell}-\hat{r}_{i})^{2}$.
-Whenever there is no ambiguity about the underlaying  time index $t$, for simplicity we neglect $t$ from the notations and simply use  $\hat{r}_i, \hat{v}_i,$ and $z_i$ to denote the respective quantities.
-We assume the rewards of all arms are bounded in $[0,1]$.
 
-\textbf{2.2 The algorithm:} Earlier round-based arm elimination algorithms like Median Elimination \citep{even2006action} and UCB-Improved mainly suffered from two basic problems: \\
+\textbf{The algorithm:} Earlier round-based arm elimination algorithms like Median Elimination \citep{even2006action} and UCB-Improved mainly suffered from two basic problems: \\
 \begin{inparaenum}[\bfseries(i)]

### 2017-10-14 Chapter3/expts.tex
Latest on 15/10/2017

--- 2017-10-11 EUCBV/expts.tex
@@
       	% UCB
-		\addplot table{EUCBV/results/NewExpt/Expt1/UCBV01_comp_subsampled.txt};
-		\addplot table{EUCBV/results/NewExpt/Expt1/EUCBV01_comp_subsampled.txt};
-		\addplot table{EUCBV/results/NewExpt/Expt1/KLUCB01_comp_subsampled.txt};
-		\addplot table{EUCBV/results/NewExpt/Expt1/MOSS01_comp_subsampled.txt};
-		\addplot table{EUCBV/results/NewExpt/Expt1/DMED01_comp_subsampled.txt};
-		\addplot table{EUCBV/results/NewExpt/Expt1/UCB01_comp_subsampled.txt};
-		\addplot table{EUCBV/results/NewExpt/Expt1/TS01_comp_subsampled.txt};
-		\addplot table{EUCBV/results/NewExpt/Expt1/OCUCB01_comp_subsampled.txt};
-		\addplot table{EUCBV/results/NewExpt/Expt1/BU01_comp_subsampled.txt};
+		\addplot table{Chapter3/results/NewExpt/Expt1/UCBV01_comp_subsampled.txt};
+		\addplot table{Chapter3/results/NewExpt/Expt1/EUCBV01_comp_subsampled.txt};
+		\addplot table{Chapter3/results/NewExpt/Expt1/KLUCB01_comp_subsampled.txt};
+		\addplot table{Chapter3/results/NewExpt/Expt1/MOSS01_comp_subsampled.txt};
+		\addplot table{Chapter3/results/NewExpt/Expt1/DMED01_comp_subsampled.txt};
+		\addplot table{Chapter3/results/NewExpt/Expt1/UCB01_comp_subsampled.txt};
+		\addplot table{Chapter3/results/NewExpt/Expt1/TS01_comp_subsampled.txt};
+		\addplot table{Chapter3/results/NewExpt/Expt1/OCUCB01_comp_subsampled.txt};
+		\addplot table{Chapter3/results/NewExpt/Expt1/BU01_comp_subsampled.txt};
       	\legend{UCB-V,EUCBV,KLUCB+,MOSS,DMED,UCB1,TS,OCUCB,BU}      	
@@
       	% UCB
-		\addplot table{EUCBV/results/NewExpt/Expt2/UCBV01_comp_subsampled.txt};
-		\addplot table{EUCBV/results/NewExpt/Expt2/EUCBV01_comp_subsampled.txt};
-		\addplot table{EUCBV/results/NewExpt/Expt2/KLUCB01_comp_subsampled.txt};
-		\addplot table{EUCBV/results/NewExpt/Expt2/MOSS01_comp_subsampled.txt};
-		\addplot table{EUCBV/results/NewExpt/Expt2/UCBR01_comp_subsampled.txt};
-		\addplot table{EUCBV/results/NewExpt/Expt2/UCB01_comp_subsampled.txt};
-		\addplot table{EUCBV/results/NewExpt/Expt2/TS01_comp_subsampled.txt};
-		\addplot table{EUCBV/results/NewExpt/Expt2/OCUCB01_comp_subsampled.txt};
-		\addplot table{EUCBV/results/NewExpt/Expt2/BU01_comp_subsampled.txt};      	
+		\addplot table{Chapter3/results/NewExpt/Expt2/UCBV01_comp_subsampled.txt};
+		\addplot table{Chapter3/results/NewExpt/Expt2/EUCBV01_comp_subsampled.txt};
+		\addplot table{Chapter3/results/NewExpt/Expt2/KLUCB01_comp_subsampled.txt};
+		\addplot table{Chapter3/results/NewExpt/Expt2/MOSS01_comp_subsampled.txt};
+		\addplot table{Chapter3/results/NewExpt/Expt2/UCBR01_comp_subsampled.txt};
+		\addplot table{Chapter3/results/NewExpt/Expt2/UCB01_comp_subsampled.txt};
+		\addplot table{Chapter3/results/NewExpt/Expt2/TS01_comp_subsampled.txt};
+		\addplot table{Chapter3/results/NewExpt/Expt2/OCUCB01_comp_subsampled.txt};
+		\addplot table{Chapter3/results/NewExpt/Expt2/BU01_comp_subsampled.txt};      	
       	\legend{UCB-V,EUCBV,KLUCB-G+,MOSS,UCB-Imp,UCB1,TS-G,OCUCB,BU-G}
@@
       	% UCB
-		\addplot table{EUCBV/results/NewExpt/Expt3/UCBV01_comp_subsampled.txt};
-		\addplot table{EUCBV/results/NewExpt/Expt3/EUCBV01_comp_subsampled.txt};
-		\addplot table{EUCBV/results/NewExpt/Expt3/MOSS01_comp_subsampled.txt};
-		\addplot table{EUCBV/results/NewExpt/Expt3/TS01_comp_subsampled.txt};
-		\addplot table{EUCBV/results/NewExpt/Expt3/OCUCB01_comp_subsampled.txt};
-		\addplot table{EUCBV/results/NewExpt/Expt3/BU01_comp_subsampled.txt};
+		\addplot table{Chapter3/results/NewExpt/Expt3/UCBV01_comp_subsampled.txt};
+		\addplot table{Chapter3/results/NewExpt/Expt3/EUCBV01_comp_subsampled.txt};
+		\addplot table{Chapter3/results/NewExpt/Expt3/MOSS01_comp_subsampled.txt};
+		\addplot table{Chapter3/results/NewExpt/Expt3/TS01_comp_subsampled.txt};
+		\addplot table{Chapter3/results/NewExpt/Expt3/OCUCB01_comp_subsampled.txt};
+		\addplot table{Chapter3/results/NewExpt/Expt3/BU01_comp_subsampled.txt};
       	\legend{UCBV,EUCBV,MOSS,TS-G,OCUCB,BU-G} 
@@
         % UCB
-		\addplot table{EUCBV/results/NewExpt/Expt41/UCBV01_comp_subsampled.txt};
-		\addplot table{EUCBV/results/NewExpt/Expt41/EUCBV01_comp_subsampled.txt};
-		\addplot table{EUCBV/results/NewExpt/Expt41/MOSS01_comp_subsampled.txt};
-		\addplot table{EUCBV/results/NewExpt/Expt41/TS01_comp_subsampled.txt};
-		\addplot table{EUCBV/results/NewExpt/Expt41/OCUCB01_comp_subsampled.txt};
-		\addplot table{EUCBV/results/NewExpt/Expt41/BU01_comp_subsampled.txt};
+		\addplot table{Chapter3/results/NewExpt/Expt41/UCBV01_comp_subsampled.txt};
+		\addplot table{Chapter3/results/NewExpt/Expt41/EUCBV01_comp_subsampled.txt};
+		\addplot table{Chapter3/results/NewExpt/Expt41/MOSS01_comp_subsampled.txt};
+		\addplot table{Chapter3/results/NewExpt/Expt41/TS01_comp_subsampled.txt};
+		\addplot table{Chapter3/results/NewExpt/Expt41/OCUCB01_comp_subsampled.txt};
+		\addplot table{Chapter3/results/NewExpt/Expt41/BU01_comp_subsampled.txt};
       	\legend{UCBV,EUCBV,MOSS,TS-G,OCUCB,BU-G} 
@@
 %\vspace*{-0.5em}
-
-%Because of the poor performance of Bayes-UCB and KL-UCB in the last two experiments we do not implement them in this setup.
-%Please note that algorithms like Thompson Sampling or Bayes-UCB are too slow to be run for such large arms (see \citet{lattimore2015optimally}) and  over such large horizon.
-%This also corroborates the finding of \citet{lattimore2015optimally} which states that MOSS breaks down only when the number of arms are exceptionally large or the horizon is unreasonably high and gaps are very small.
-We consistently see that in uniform gap testcases EUCBV outperforms OCUCB.
 

### 2017-10-14 Chapter4/intro.tex
Latest on 15/10/2017

Pure-exploration MAB problems are unlike their traditional (exploration vs.\ exploitation)  counterparts, the SMABs, where the  objective is to minimize the cumulative regret. The cumulative regret is the total loss incurred by the learner for not playing the optimal arm throughout the time horizon $T$. The SMABs were extensively discussed in Chapter \ref{chap:SMAB} and \ref{chap:EUCBV}. An interested reader can read through the previous chapters or can continue from here. Though we re-use the ideas from SMABs, the goal of pure exploration setup is distinctly different from that of cumulative regret minimization of SMABs and the required algorithms to understand this setup and our proposed algorithm are mentioned in this chapter itself.

	In pure-exploration problems a learning algorithm, until time $T$, can invest entirely on exploring the arms without being concerned about the loss incurred while exploring; the objective is to minimize the probability that the arm recommended at time $T$ is not the best arm.  In this paper, we further consider a combinatorial version of the pure-exploration MAB, called the thresholding bandit problem (TBP).  Here, the learning algorithm is provided with a threshold $\tau$, and the objective, after exploring for $T$ rounds, is to  output all arms $i$ whose $r_{i}$ is above $\tau$. 
It is important to emphasize that the \emph{thresholding} bandit problem is different from the \emph{threshold} bandit setup studied in \cite{abernethy2016threshold}, where the learner receives an unit reward whenever the value of an observation is above a threshold.

### 2017-10-14 Chapter4/notation.tex
Latest on 15/10/2017

--- 2017-10-11 tbandit/notation.tex
@@
-\textbf{Notation and assumptions:} $\mathcal{A}$ denotes the set of arms, and $|\mathcal{A}|=K$ is the number of arms in $\mathcal{A}$. 
-%Arms generic arm is indexed by $i,j\in\mathcal{A}$. 
+To benefit the reader, we again recall the notations we stated in chapter \ref{chap:SMAB} and also a few additional notations.
+$\mathcal{A}$ denotes the set of arms, and $|\mathcal{A}|=K$ is the number of arms in $\mathcal{A}$.
 For arm $i\in\mathcal{A}$, we use $r_{i}$ to denote the true mean of the distribution from which the rewards are sampled, while $\hat{r}_{i}(t)$ denotes the estimated mean at time $t$.

### 2017-10-14 Chapter4/probDef.tex
Latest on 15/10/2017

--- 2017-10-11 tbandit/intro.tex
@@
-Stochastic multi-armed bandit (MAB) problems are instances of the classic sequential decision-making scenario; specifically an MAB problem comprises of a learner and a collection of actions (or arms), denoted $\mathcal{A}$.
-In each trial the learner plays (or pulls) an arm $i\in\mathcal{A}$ which yields independent and identically distributed (i.i.d.) reward samples from a distribution (corresponding to arm $i$), whose expectation is denoted by $r_i$.
-%whose rewards are  samples from the distribution specific to the arm $i\in A$ and whose expected reward is denoted by $r_{i},\forall i\in A$. 
-The learner's objective is to identify an arm corresponding to the maximum expected reward, denoted $r^{*}$. Thus, at each time-step the learner 
-%selects an arm $i$ and hence
-is faced with the \emph{exploration vs.\ exploitation dilemma}, where it can pull an arm which has yielded the highest mean reward (denoted $\hat{r}_{i}$) thus far (\emph{exploitation}) or continue to explore other arms with the prospect of finding a better arm
-%superior performance 
-whose performance has not been observed sufficiently (\emph{exploration}).
-
-%In the stochastic multi-armed bandit setting a learning agent is required to choose from a set of decisions or arms at every round.
-The agent is then presented with a reward for that round, which is an independent draw from a stationary distribution specific to the arm selected.
-The agent, however, does not know the mean of the distributions associated with each arm, denoted by $r_{i}$, including the optimal arm which will give it the best reward, denoted by $r^{*}$.
-The agent attempts to make arm choices that will maximize some performance measure by keeping track of the reward that has been gathered from previous selections of the arm, for each arm.
-This is called the estimated mean reward of an arm denoted by $\hat{r}_{i}$.
-The bandit problem can be conceptualized as a sequential decision making process where the agent is at each round presented with an \emph{exploration-exploitation dilemma}.
-The agent could pull the arm which has the highest observed mean reward till now (exploitation) or to explore other arms, with the prospect of finding superior performance which was previously unobserved (exploration).
-
-%
-%	Formally, let $r_i$, $i=1,\ldots,K$ denote the mean rewards of the $K$ arms and $r^* = \max_i r_i$ the optimal mean reward.
-The objective in some of the stochastic bandit problem is to minimize the cumulative regret, which is defined as follows:
-%\begin{align*}
-%R_{T}=r^{*}T - \sum_{i\in A} r_{i}N_{i}(T),
-%\end{align*}
-%where $T$ is the number of rounds, $N_{i}(T)=\sum_{m=1}^T I(I_m=i)$ is the number of times the algorithm chose arm $i$ up to round $T$.
-%The expected regret of an algorithm after $T$ rounds can be written as,
-%
-%\begin{align*}
-%\E[R_{T}]= \sum_{i=1}^K \E[N_i(T)] \Delta_i,
-%\end{align*}
-%where $\Delta_{i}=r^{*}-r_{i}$ denotes the gap between the means of the optimal arm and of the $i$-th arm.
-
-Pure-exploration MAB problems are unlike their traditional (exploration vs.\ exploitation)  counterparts where the  objective is to minimize the cumulative regret (which is the total loss incurred by the learner for not playing the optimal arm throughout the time horizon $T$).
-Instead, in pure-exploration problems a learning algorithm, until time $T$, can invest entirely on exploring the arms without being concerned about the loss incurred while exploring; the objective is to minimize the probability that the arm recommended at time $T$ is not the best arm.
-In this paper, we further consider a combinatorial version of the pure-exploration MAB, called the thresholding bandit problem (TBP).
-Here, the learning algorithm is provided with a threshold $\tau$, and the objective, after exploring for $T$ rounds, is to  output all arms $i$ whose $r_{i}$ is above $\tau$.
-It is important to emphasize that the \emph{thresholding} bandit problem is different from the \emph{threshold} bandit setup studied in \cite{abernethy2016threshold}, where the learner receives an unit reward whenever the value of an observation is above a threshold.
-
-%%%%%%%%%%%%%%%
-% Old para
-%%%%%%%%%%%%%%%
-%Pure-exploration problems are unlike their traditional (exploration vs.\ exploitation) counterparts where the  objective is to minimize the cumulative regret, which is the total loss incurred by the learner for not playing the optimal arm throughout the time horizon $T$.
-Instead, in the pure exploration setup the learning algorithm is provided with a threshold $\tau$, and the objective, after exploring for $T$ rounds, is to  output all arms $i$ whose $r_{i}$ is above $\tau$.
-Thus, the learning algorithm, until  time $T$, can invest entirely on exploring the arms  without being concerned about the loss incurred while exploring.
-It is important to emphasize that the \emph{thresholding bandit} problem is different from the \emph{threshold bandit} setup studied in \cite{abernethy2016threshold}, where the learner receives an unit reward whenever the value of an observation is above a threshold.
-%<<<<<<< Updated upstream
-%Pure-exploration problems are unlike their traditional (exploration vs.\ exploitation) counterparts where the  objective is to minimize the cumulative regret, which is the total loss incurred by the learner for not playing the optimal arm throughout the time horizon $T$.
-In this paper we study the fixed-budget setting of a specific combinatorial pure-exploration problem, called the thresholding bandit problem (TBP), in the context of (MAB) setting.
-In this pure-exploration setup the learning algorithm is provided with a threshold $\tau$, and the objective, after exploring for $T$ rounds, is to  output all arms $i$ whose $r_{i}$ is above $\tau$.
-Thus, the learning algorithm, until time $T$, can invest entirely on exploring the arms  without being concerned about the loss incurred while exploring.
-It is important to emphasize that the \emph{thresholding} bandit problem is different from the \emph{threshold} bandit setup studied in \cite{abernethy2016threshold}, where the learner receives an unit reward whenever the value of an observation is above a threshold.
-%=======
-
-%Pure-exploration problems are unlike their traditional (exploration vs.\ exploitation) counterparts where the  objective is to minimize the cumulative regret, which is the total loss incurred by the learner for not playing the optimal arm throughout the time horizon $T$.
-Instead, in the pure exploration setup the learning algorithm is provided with a threshold $\tau$, and the objective, after exploring for $T$ rounds, is to  output all arms $i$ whose $r_{i}$ is above $\tau$.
-Thus, the learning algorithm, until  time $T$, can invest entirely on exploring the arms  without being concerned about the loss incurred while exploring.
-It is important to emphasize that the \emph{thresholding bandit} problem is different from the \emph{threshold bandit} setup studied in \cite{abernethy2016threshold}, where the learner receives an unit reward whenever the value of an observation is above a threshold.
-%>>>>>>> Stashed changes
-
-% reward on each time-step depends on a threshold value and the learner receives the reward only if the reward is above the threshold.
-
-%This is a specific instance of combinatorial pure exploration where the learning algorithm can explore as much as possible given a fixed horizon $T$ and not be concerned with the usual exploration-exploitation dilemma.
-
 Formally, the problem we consider is the following.
@@
 Let
-$S_\tau^c$ % =\mathcal{A}\backslash S_\tau$
- denote the complement of $S_\tau$, i.e.,  $S_{\tau}^{c}=\lbrace i\in \mathcal{A}: r_{i} < \tau \rbrace$.
+$S_\tau^c$ denote the complement of $S_\tau$, i.e.,  $S_{\tau}^{c}=\lbrace i\in \mathcal{A}: r_{i} < \tau \rbrace$.
 Next, let $\hat{S}_{\tau}=\hat{S}_{\tau}(T)\subseteq \mathcal{A}$ denote the recommendation of a learning algorithm (under consideration) after $T$ time units of exploration, while $\hat{S}_{\tau}^c$ denotes its complement.
-%  Also we define $\hat{S}_{\tau}=\hat{S}_{\tau}(T)\subset \mathcal{A}$ and its complementary set $\hat{S}_{\tau}^{C}$ as the recommendation of the learning algorithm after $T$ rounds. 
-% Given such sets exists, 
+
 The performance of the learning agent is measured by the accuracy with which it can classify the arms into $S_{\tau}$ and $S_{\tau}^{c}$ after time horizon $T$.
@@
 Finally, the goal of the learning agent is to minimize the expected loss:
-% So, the expected loss after $T$ rounds is,
 \begin{align*}
@@
 Note that the expected loss is simply the \emph{probability of mis-classification} (i.e., error), that occurs either if a good arm is rejected or a bad arm is accepted as a good one.
-% (represented by the events $\lbrace S_{\tau}\cap \hat{S}_{\tau}^{c} \neq \emptyset \rbrace$ and $\lbrace \hat{S}_{\tau}\cap S_{\tau}^{c} \neq \emptyset\rbrace$, respectively).
-
-%which we can say is the probability of making mistake, that is whether the learning agent at the end of round $T$ rejects arms from $S_{\tau}$ or accepts arms from $S_{\tau}^{C}$ in its final recommendation.
-
-%Also, we are looking at an anytime algorithm, so the knowledge of $T$ may not be known to the learner.

### 2017-10-14 Chapter5/algo.tex
Latest on 15/10/2017

\textbf{The Algorithm:} The Augmented-UCB (AugUCB) algorithm is presented in Algorithm~\ref{alg:augucb}.
AugUCB is essentially based on the arm elimination method of the UCB-Improved \cite{auer2010ucb}, but adapted to the thresholding bandit setting proposed in \cite{locatelli2016optimal}. However, unlike the UCB improved (which is based on mean estimation) our algorithm employs \emph{variance estimates} (as in \cite{audibert2009exploration}) for arm elimination; to the best of our knowledge this is the first variance-aware  algorithm for the thresholding bandit problem. Further, we allow for arm-elimination at each time-step, which is in contrast to the earlier work (e.g., \cite{auer2010ucb,chen2014combinatorial}) where the arm elimination task is deferred to the end of the respective exploration rounds. The details are presented below.

% In algorithm \ref{alg:augucb}, hence referred to as AugUCB, we have two exploration parameters, $\rho_{\mu}$ and $\rho_v$ which are the arm elimination parameters. $\psi_{m}$ is the exploration regulatory factor. 
%The main approach is based on the UCB-Improved algorithm with modifications suited for the thresholding bandit problem. 
The active set $B_{0}$ is initialized with all the arms from $\mathcal{A}$. We divide the entire budget $T$ into rounds/phases like in UCB-Improved, CCB, SAR and CSAR. At every time-step AugUCB checks for arm elimination conditions, while updating parameters at the end of each round. As suggested by \cite{liu2016modification} to make AugUCB to overcome too much early exploration, we no longer pull all the arms equal number of times in each round. Instead, we choose an arm in the active set $B_m$ that minimizes $(|\hat{r}_{i} - \tau |-2s_i)$ where 
%$\min_{i\in B_{m}}\big\lbrace |\hat{r}_{i} - \tau | - 2\sqrt{\frac{\rho_v\psi_m \hat{V}_{i} \log ( T \epsilon_{m})}{4 n_{i}} + \frac{\rho_v\psi_m \log{( T\epsilon_{m})}}{4 n_{i}}} \big\rbrace $
\begin{small}
\begin{align*}
s_i & = \sqrt{\frac{\rho\psi_m (\hat{v}_{i}+1) \log ( T \epsilon_{m})}{4 n_{i}}} %+ \frac{\rho\psi_m \log{( T\epsilon_{m})}}{4 n_{i}}}.
\end{align*}
\end{small} 
with $\rho$ being the arm elimination parameter and $\psi_{m}$ being the exploration regulatory factor.
%  in the active set $B_{m}$. 
The above condition ensures that an arm closer to the threshold $\tau$ is pulled; 
%and with suitable choice of $\rho_{\mu}$ and $\rho_v$ we can fine tune the exploration. 
parameter $\rho$ can be used to fine tune the elimination interval.
The choice of exploration factor, $\psi_m$,
% $\psi_m=\frac{T\epsilon_m}{(\log(\frac{3}{16} K\log K))^{2}}$ 
comes directly from \cite{audibert2010best} and \cite{bubeck2011pure} where it is  stated that in pure exploration setup, the exploring factor must be linear in $T$ (so that an exponentially small probability of error is achieved) rather than being logarithmic in $T$ (which is more suited for minimizing cumulative regret).

\begin{algorithm}[t!]
\caption{AugUCB}
\label{alg:augucb}
\begin{algorithmic}
\State {\bf Input:} Time budget $T$; parameter $\rho$; 
% $\rho_{\mu}$, $\rho_v$ 
  threshold $\tau$
\State {\bf Initialization:} $B_{0}=\mathcal{A}$; $m=0$; $\epsilon_{0}=1$;
\begin{small}
\begin{align*}
M&=\left\lfloor \frac{1}{2}\log_{2} \frac{T}{e}\right\rfloor; 
\hspace{2mm}\psi_{0}=\frac{T\epsilon_{0}}{128\Big(\log(\frac{3}{16}K\log K)\Big)^2}; \\
\ell_{0}&=\left\lceil \frac{2\psi_0\log( T\epsilon_{0})}{\epsilon_{0}} \right\rceil;
\hspace{2mm}N_{0}=K\ell_{0}
\end{align*}
\end{small}
%$M=\left\lfloor \frac{1}{2}\log_{2} \frac{T}{e}\right\rfloor $,  
%$\psi_{0}=\frac{T\epsilon_{0}}{(\log(\frac{3}{16}K\log K)^2}$,
% $\ell_{0}=\left\lceil \frac{2\psi\log( T\epsilon_{0})}{\epsilon_{0}} \right\rceil$ and 
% $N_{0}=K\ell_{0} $. Pull each arm once.
\State Pull each arm once
\vspace{-2mm}
\State \For{$t=K+1,..,T$}
\State Pull arm $j\in\argmin_{i\in B_{m}}\Big\lbrace |\hat{r}_{i} - \tau | - 2s_{i}\Big\rbrace$
% \State where $s_j=\sqrt{\frac{\rho\psi_{m}\hat{v}_{j}\log{( T\epsilon_{m})}}{4 n_{j}} + \frac{\rho\psi_{m} \log{(T\epsilon_{m})}}{4 n_{j}}}$
\State $t\leftarrow t+1$ 
\vspace{-4mm}
%\ArmElim
%\State For each arm $i \in B_{m}$, remove arm ${i}$ from $B_{m}$ if
%\begin{align*}
%\hat{r}_{i} + c_i  < \tau - c_i \mbox{ or } \hat{r}_{i} - c_i  > \tau + c_i \\
%\text{where $c_i=\sqrt{\frac{\rho_{\mu}\psi_{m}\log{( T\epsilon_{m})}}{2 n_{i}}}$}
%\end{align*}
%\EndArmElim
%\ArmElimV
%\State \For{$i\in B_m$}
%\State For each arm $i \in B_{m}$, remove arm ${i}$ from $B_{m}$ if
\State \For{$i\in B_m$}
\vspace{-4mm}
\State \If{$(\hat{r}_{i} + s_i  < \tau - s_i)$ or $(\hat{r}_{i} - s_i > \tau + s_i)$}
\State $B_m\leftarrow B_m\backslash\{i\}$\hspace{4mm} (Arm deletion)
\EndIf
\EndFor
%\begin{align*}
%\hat{r}_{i} + s_i  < \tau - s_i,\hspace{1mm} \mbox{ or } \hspace{1mm}\hat{r}_{i} - s_i  > \tau + s_i \\
%% \text{where $s_i=\sqrt{\frac{\rho\psi_{m}\hat{v}_{i}\log{( T\epsilon_{m})}}{4 n_{i}} + \frac{\rho\psi_{m} \log{(T\epsilon_{m})}}{4 n_{i}}}$}
%\end{align*}
%\EndFor
%\EndArmElimV
\vspace{-2mm}
\State \If{$t\geq N_{m}$ and $m \leq M$}
%\ResetParam
\State \textbf{Reset Parameters}
\State $\epsilon_{m+1}\leftarrow\frac{\epsilon_{m}}{2}$
\State $B_{m+1} \leftarrow B_{m}$
\State $\psi_{m+1}\leftarrow \frac{T\epsilon_{m+1}}{128(\log(\frac{3}{16}K\log K))^{2}}$
\State $\ell_{m+1}\leftarrow\left\lceil \frac{2\psi_{m+1}\log( T\epsilon_{m+1})}{\epsilon_{m+1}} \right\rceil$
\State $N_{m+1} \leftarrow t + |B_{m+1}|\ell_{m+1}$
\State $m \leftarrow m+1$
%\EndResetParam
\EndIf
\EndFor
\State \textbf{Output:} $\hat{S}_{\tau}=\lbrace i: \hat{r}_{i}\geq \tau \rbrace$.
\end{algorithmic}
\end{algorithm}

%Also because of the said condition, like \cite{liu2016modification} we also claim that AugUCB is an anytime algorithm.

### 2017-10-14 Chapter5/expt.tex
Latest on 15/10/2017

--- 2017-10-11 tbandit/expt.tex
@@
 
-%We also implement the uniform-allocation (labeled UA) strategy,  CSAR is modified for the TBP setting such that it behaves as a Successive Reject algorithm whereby it rejects the arm farthest from $\tau$ after each round.
-%Similarly we modify the UCBE \cite{audibert2009exploration} and UCBEV \cite{gabillon2011multi} algorithms  (originally proposed for single best arm and TopM identification problems, respectively) to suit the TBP setting.
-%%to \cite{locatelli2016optimal} to suit the goal of finding arms above the threshold $\tau$. 
-%Following  \cite{locatelli2016optimal} the exploration parameter $a$ in UCBE is set to $a=\frac{T-K}{H_1}$, while for UCBEV we set $a = \frac{T-2K}{H_{\sigma,1}}$.
-Then, at each time-step $t=1,2,..,T$ we pull the arm that minimizes
-% $\lbrace |\hat{r}_{i} -\tau|-\sqrt{\frac{a}{n_{i}}} \rbrace$, where $a$ is set as mentioned above for UCBE and UCBEV respectively.
-Finally, for AugUCB we take $\rho=\frac{1}{3}$ as in  Theorem \ref{Result:Theorem:1}.
-
-%Again, for UCBEV, following \cite{gabillon2011multi}, we modify it such that the exploration parameter $a = \frac{T-2K}{H_{\sigma,1}}$.
-Then for each timestep $t=1,2,..,T$ we pull the arm that minimizes $\lbrace |\hat{r}_{i} -\tau|-\sqrt{\frac{a}{n_{i}}} \rbrace$, where $n_{i}$ is the number of times the arm $i$ is pulled till $t-1$ timestep and $a$ is set as mentioned above for UCBE and UCBEV respectively.
-Also, APT is run with $\epsilon=0.05$, which denotes the precision with which the algorithm suggests the best set of arms and we modify CSAR as per \cite{locatelli2016optimal} such that it behaves as a Successive Reject algorithm whereby it rejects the arm farthest from $\tau$ after each phase.
-For AugUCB we take $\rho_{\mu}=\frac{1}{8}$ and $\rho_v=\frac{1}{3}$ as in Theorem \ref{Result:Theorem:1}.
-In all the testbeds AugUCB, APT, CSAR, Uniform Allocation, UCBE and UCBEV are run with the same settings as mentioned above.
-
 \noindent
@@
 we design six different experimental scenarios that are obtained by varying the arm means and variances.
-%We conduct a set of six experiments with different reward means and variances. 
 Across all experiments consists of $K=100$  arms (indexed $i=1,2,\cdots,100$) of which ${S}_\tau=\{6,7,\cdots,10\}$, where we have fixed $\tau=0.5$.
-%in all the experiments, the threshold $\tau$ is set to $0.5$. %for all experiments. 
-%Also, the number of arms in each experiment is $K=100$ , of which $\lbrace 6,7,8,9,10 \rbrace$ arms have their reward means above $\tau$. 
 In all the experiments, each algorithm is run independently for $10000$ time-steps.
@@
 
-%that is obtained by computing the fraction of errors when   The experiment is repeated for $500$ independent iterations, and the average error percentage is plotted against the $10000$ time-steps.
-
- %The output is considered erroneous if the correct set of arms is not $i=\lbrace 6,7,8,9,10 \rbrace$ (true for all the experiments).
-The error percentage over $500$ runs is plotted against $10000$ timesteps.
-
- %For the uniform allocation algorithm, for each $t=1,2,..,T$ the arms are sampled uniformly.
-
-%Also we run AugUCBM with arm elimination just by mean estimation and AugUCBV with arm elimination just by variance estimation.
-For AugUCBM, at every timestep we pull arm that minimizes $i\in\argmin_{j\in B_{m}}\bigg\lbrace |\hat{r}_{j} - \tau | - 2c_{j}\bigg\rbrace$ while for AugUCBV we pull arm that minimizes $i\in\argmin_{j\in B_{m}}\bigg\lbrace |\hat{r}_{j} - \tau | - 2s_{j}\bigg\rbrace$.
-
-%	The first experiment is conducted on a testbed of $100$ arms involving
-
 \textbf{Experiment-1:} The reward distributions are Gaussian with  means  $r_{1:4}=0.2+(0:3)\cdot0.05$, $r_{5}=0.45$, $r_{6}=0.55$, $r_{7:10}=0.65+(0:3)\cdot0.05$ and $r_{11:100}=0.4$.
@@
 
- The corresponding variances are $\sigma_{1:5}^{2}=0.5$ and $\sigma_{6:10}^{2}=0.6$, while $\sigma_{11:100}^{2}$ is chosen independently and uniform in the  interval $[0.38,0.42]$;
-% Then $\sigma_{11:100}^{2}$ is chosen uniform randomly between $0.38-0.42$.
-note that, the variances of the arms in $S_\tau$ are higher than those of the other arms.
-% The means in the testbed are chosen in such a way that any algorithm has to spend a significant amount of budget to explore all the arms and variance is chosen in such a way that the arms above $\tau$ have high variance whereas arms below $\tau$ have lower variance.
- The corresponding  results are shown in Figure \ref{Fig:budgetExpt1},
- from where we see that UCBEV, which has access to the problem complexity while being variance-aware, outperforms all other algorithm (including UCBE which also has access to the problem complexity but does not take into account the variances of the arms).
-Interestingly, the performance of our AugUCB (without requiring any complexity input) is comparable with UCBEV, while it
-   % with the said parameters 
- outperforms UCBE, APT and the other non variance-aware algorithms that we have considered. 	
-%AugUCBM with just mean estimation performs worse than AugUCB or AugUCBV, which have a matching performance in this setup.
+ The corresponding variances are $\sigma_{1:5}^{2}=0.5$ and $\sigma_{6:10}^{2}=0.6$, while $\sigma_{11:100}^{2}$ is chosen independently and uniform in the  interval $[0.38,0.42]$; note that, the variances of the arms in $S_\tau$ are higher than those of the other arms.
+The corresponding  results are shown in Figure \ref{Fig:budgetExpt1}, from where we see that UCBEV, which has access to the problem complexity while being variance-aware, outperforms all other algorithm (including UCBE which also has access to the problem complexity but does not take into account the variances of the arms).
+Interestingly, the performance of our AugUCB (without requiring any complexity input) is comparable with UCBEV, while it outperforms UCBE, APT and the other non variance-aware algorithms that we have considered.
 
@@
       	% UCB
-		\addplot table{tbandit/results/budgetTestAP/APT12_comp_subsampled.txt};
-		\addplot table{tbandit/results/budgetTestAP/AugUCBV1_comp_subsampled.txt};
-		%\addplot table{results/budgetTestAP/AugUCBV_1_13_comp_subsampled.txt};
-		\addplot table{tbandit/results/budgetTestAP/UCBEM1_comp_subsampled.txt};
-		\addplot table{tbandit/results/budgetTestAP/UCBEMV1_comp_subsampled.txt};
-		\addplot table{tbandit/results/budgetTestAP/SR1_comp_subsampled.txt};
-		\addplot table{tbandit/results/budgetTestAP/UA1_comp_subsampled.txt};
-		%\addplot table{results/budgetTestAP/AugUCBM12_comp_subsampled.txt};
-		%\addplot table{results/budgetTestAP/AugUCBV1_comp_subsampled.txt};
-      	%\legend{APT,AugUCB,UCBE,UCBEV,CSAR,Unif Alloc,AugUCBM,AugUCBV}
+		\addplot table{Chapter5/results/budgetTestAP/APT12_comp_subsampled.txt};
+		\addplot table{Chapter5/results/budgetTestAP/AugUCBV1_comp_subsampled.txt};
+		\addplot table{Chapter5/results/budgetTestAP/UCBEM1_comp_subsampled.txt};
+		\addplot table{Chapter5/results/budgetTestAP/UCBEMV1_comp_subsampled.txt};
+		\addplot table{Chapter5/results/budgetTestAP/SR1_comp_subsampled.txt};
+		\addplot table{Chapter5/results/budgetTestAP/UA1_comp_subsampled.txt};
+
       	\legend{APT,AugUCB,UCBE,UCBEV,CSAR,UA}
@@
         % UCB
-		\addplot table{tbandit/results/budgetTestGP/APT12_comp_subsampled.txt};
-		\addplot table{tbandit/results/budgetTestGP/AugUCBV1_comp_subsampled.txt};
-		%\addplot table{results/budgetTestGP/AugUCBV_1_13_comp_subsampled.txt};
-		\addplot table{tbandit/results/budgetTestGP/UCBEM1_comp_subsampled.txt};
-		\addplot table{tbandit/results/budgetTestGP/UCBEMV1_comp_subsampled.txt};
-		\addplot table{tbandit/results/budgetTestGP/SR1_comp_subsampled.txt};
-		\addplot table{tbandit/results/budgetTestGP/UA1_comp_subsampled.txt};
-		%\addplot table{results/budgetTestGP/AugUCBM12_comp_subsampled.txt};
-		%\addplot table{results/budgetTestGP/AugUCBV1_comp_subsampled.txt};
-        %\legend{APT,AugUCB,UCBE,UCBEV,CSAR,Unif Alloc,AugUCBM,AugUCBV}
+		\addplot table{Chapter5/results/budgetTestGP/APT12_comp_subsampled.txt};
+		\addplot table{Chapter5/results/budgetTestGP/AugUCBV1_comp_subsampled.txt};
+		\addplot table{Chapter5/results/budgetTestGP/UCBEM1_comp_subsampled.txt};
+		\addplot table{Chapter5/results/budgetTestGP/UCBEMV1_comp_subsampled.txt};
+		\addplot table{Chapter5/results/budgetTestGP/SR1_comp_subsampled.txt};
+		\addplot table{Chapter5/results/budgetTestGP/UA1_comp_subsampled.txt};
         \legend{APT,AugUCB,UCBE,UCBEV,CSAR,UA}
@@
       	% UCB
-		\addplot table{tbandit/results/budgetTestGR1/APT1_comp_subsampled.txt};
-		\addplot table{tbandit/results/budgetTestGR1/AugUCB1_comp_subsampled.txt};
-		\addplot table{tbandit/results/budgetTestGR1/UCBEM1_comp_subsampled.txt};
-		\addplot table{tbandit/results/budgetTestGR1/UCBEMV1_comp_subsampled.txt};
-		\addplot table{tbandit/results/budgetTestGR1/SR1_comp_subsampled.txt};
-		\addplot table{tbandit/results/budgetTestGR1/UA1_comp_subsampled.txt};
+		\addplot table{Chapter5/results/budgetTestGR1/APT1_comp_subsampled.txt};
+		\addplot table{Chapter5/results/budgetTestGR1/AugUCB1_comp_subsampled.txt};
+		\addplot table{Chapter5/results/budgetTestGR1/UCBEM1_comp_subsampled.txt};
+		\addplot table{Chapter5/results/budgetTestGR1/UCBEMV1_comp_subsampled.txt};
+		\addplot table{Chapter5/results/budgetTestGR1/SR1_comp_subsampled.txt};
+		\addplot table{Chapter5/results/budgetTestGR1/UA1_comp_subsampled.txt};
         \legend{APT,AugUCB,UCBE,UCBEV,CSAR,UA}
@@
         % UCB
-		\addplot table{tbandit/results/budgetTestGR2/APT1_comp_subsampled.txt};
-		\addplot table{tbandit/results/budgetTestGR2/AugUCBV1_comp_subsampled.txt};
-		%\addplot table{results/budgetTestGP/AugUCBV_1_13_comp_subsampled.txt};
-		\addplot table{tbandit/results/budgetTestGR2/UCBEM1_comp_subsampled.txt};
-		\addplot table{tbandit/results/budgetTestGR2/UCBEMV1_comp_subsampled.txt};
-		\addplot table{tbandit/results/budgetTestGR2/SR1_comp_subsampled.txt};
-		\addplot table{tbandit/results/budgetTestGR2/UA1_comp_subsampled.txt};
-		%\addplot table{results/budgetTestGP/AugUCBM12_comp_subsampled.txt};
-		%\addplot table{results/budgetTestGP/AugUCBV1_comp_subsampled.txt};
-        %\legend{APT,AugUCB,UCBE,UCBEV,CSAR,Unif Alloc,AugUCBM,AugUCBV}
+		\addplot table{Chapter5/results/budgetTestGR2/APT1_comp_subsampled.txt};
+		\addplot table{Chapter5/results/budgetTestGR2/AugUCBV1_comp_subsampled.txt};
+		\addplot table{Chapter5/results/budgetTestGR2/UCBEM1_comp_subsampled.txt};
+		\addplot table{Chapter5/results/budgetTestGR2/UCBEMV1_comp_subsampled.txt};
+		\addplot table{Chapter5/results/budgetTestGR2/SR1_comp_subsampled.txt};
+		\addplot table{Chapter5/results/budgetTestGR2/UA1_comp_subsampled.txt};
         \legend{APT,AUgUCB,UCBE,UCBEV,CSAR,UA}
@@
         % UCB
-		\addplot table{tbandit/results/budgetTestGR4/APT1_comp_subsampled.txt};
-		\addplot table{tbandit/results/budgetTestGR4/AugUCB1_comp_subsampled.txt};
-		\addplot table{tbandit/results/budgetTestGR4/UCBEM1_comp_subsampled.txt};
-		\addplot table{tbandit/results/budgetTestGR4/UCBEMV1_comp_subsampled.txt};
-		\addplot table{tbandit/results/budgetTestGR4/SR1_comp_subsampled.txt};
-		\addplot table{tbandit/results/budgetTestGR4/UA1_comp_subsampled.txt};
+		\addplot table{Chapter5/results/budgetTestGR4/APT1_comp_subsampled.txt};
+		\addplot table{Chapter5/results/budgetTestGR4/AugUCB1_comp_subsampled.txt};
+		\addplot table{Chapter5/results/budgetTestGR4/UCBEM1_comp_subsampled.txt};
+		\addplot table{Chapter5/results/budgetTestGR4/UCBEMV1_comp_subsampled.txt};
+		\addplot table{Chapter5/results/budgetTestGR4/SR1_comp_subsampled.txt};
+		\addplot table{Chapter5/results/budgetTestGR4/UA1_comp_subsampled.txt};
         \legend{APT,AUgUCB,UCBE,UCBEV,CSAR,UA}
@@
         % UCB
-		\addplot table{tbandit/results/budgetTestGR3/testUCBEMV1_0.25_comp_subsampled.txt};
-		\addplot table{tbandit/results/budgetTestGR4/AugUCB1_comp_subsampled.txt};
-		%\addplot table{results/budgetTestGP/AugUCBV_1_13_comp_subsampled.txt};
-		%\addplot table{results/budgetTestGR3/testUCBEMV1_0.25_comp_subsampled.txt};
-		\addplot table{tbandit/results/budgetTestGR3/testUCBEMV1_256_comp_subsampled.txt};
-		\addplot table{tbandit/results/budgetTestGR4/UCBEMV1_comp_subsampled.txt};
-		%\addplot table{results/budgetTestGR3/testUCBEMV1_64_comp_subsampled.txt};
-		%\addplot table{results/budgetTestGP/AugUCBM12_comp_subsampled.txt};
-		%\addplot table{results/budgetTestGP/AugUCBV1_comp_subsampled.txt};
-        %\legend{APT,AugUCB,UCBE,UCBEV,CSAR,Unif Alloc,AugUCBM,AugUCBV}
+		\addplot table{Chapter5/results/budgetTestGR3/testUCBEMV1_0.25_comp_subsampled.txt};
+		\addplot table{Chapter5/results/budgetTestGR4/AugUCB1_comp_subsampled.txt};
+		\addplot table{Chapter5/results/budgetTestGR3/testUCBEMV1_256_comp_subsampled.txt};
+		\addplot table{Chapter5/results/budgetTestGR4/UCBEMV1_comp_subsampled.txt};
         \legend{UCBEV($0.25$), AugUCB, UCBEV($256$), UCBEV($1$)}
-        %\legend{UCBEV($0.06$),AUgUCB,UCBEV($0.25$),UCBEV($1$),UCBEV($64$),UCBEV($256$)}
-        %\legend{APT,AugUCB,UCBE,UCBEV,CSAR,Unif Alloc}
       	\end{axis}

### 2017-10-14 EUCBV/codes/BayesUCB.py

@@ -1,215 +1,0 @@
-'''
-Created on Oct 6, 2015
-
-@author: Subhojyoti
-'''
-
-import math
-import random
-import numpy
-from scipy import special
-from scipy.stats import beta
-#from random import betavariate
-#from scipy.special import btdtri
-import scipy
-
-class ucb1_2(object):
-    '''
-    classdocs
-    '''
-
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-
-    
-     
-    def rewards(self,choice):
-        #return random.gauss(self.means[choice],0.5)
-        return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-        
-    def ucb1(self,numActions):
-    
-        #Set the environment
-        self.numActions=numActions
-        
-        self.payoffSums = [0] * self.numActions
-        self.numPlays = [0] * self.numActions
-        self.ucbs = [0] * self.numActions
-        self.upbs = [0] * self.numActions
-        self.numRounds = 200000
-        #self.numRounds = 60000
-        #numRounds = 250000
-        
-        self.arm_reward = [0]*numActions
-        
-        #bestAction=arms/2
-        self.bestAction=self.numActions-2
-        
-        #biases = [1.0 / k for k in range(5,5+numActions)]
-        #means = [0.5 + b for b in biases]
-        self.means =[0.07 for i in range(self.numActions)]
-        
-        '''
-        i=(1*self.numActions)/3
-        while i<self.numActions:
-            self.means[i]=0.05
-            i=i+1
-        
-        i=(2*self.numActions)/3
-        while i<self.numActions:
-            self.means[i]=0.03
-            i=i+1
-        '''
-        self.means[self.bestAction]=0.1
-        
-        
-        # initialize empirical sums
-        '''
-        for i in range(self.numActions):
-            self.payoffSums[i] = self.rewards(i)
-            self.numPlays[i]=self.numPlays[i]+1
-        '''
-        
-        theta=[1.0 for i in range(self.numActions)]
-        cumulativeReward = 0
-        bestActionCumulativeReward = 0
-        self.actionRegret=[]
-
-
-        t=1
-        '''
-        for i in range(self.numActions):
-            theReward = self.rewards(i)
-            #self.numPlays[i]=self.numPlays[i]+1
-
-            action=i
-            theReward = self.rewards(action)
-            #print theReward,action
-            self.arm_reward[action]=self.arm_reward[action]+theReward
[…]

### 2017-10-14 EUCBV/codes/BayesUCB_expt2.py

@@ -1,237 +1,0 @@
-'''
-Created on Oct 6, 2015
-
-@author: Subhojyoti
-'''
-
-import math
-import random
-import numpy
-from scipy import special
-from scipy.stats import beta
-from scipy.stats import norm
-from scipy.stats import t
-#from random import betavariate
-#from scipy.special import btdtri
-import scipy
-
-class ucb1_2(object):
-    '''
-    classdocs
-    '''
-
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-
-    
-     
-    def rewards(self,choice):
-        return random.gauss(self.means[choice],self.variance[choice])
-        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-        
-    def ucb1(self,numActions):
-    
-        #Set the environment
-        self.numActions=numActions
-        
-        self.payoffSums = [0] * self.numActions
-        self.sqpayoffSums = [0] * self.numActions
-        self.numPlays = [1] * self.numActions
-        self.ucbs = [0] * self.numActions
-        self.upbs = [0] * self.numActions
-        self.numRounds = 300000
-        #self.numRounds = 60000
-        #numRounds = 250000
-        
-        self.arm_reward = [0]*numActions
-        
-        #bestAction=arms/2
-        self.bestAction=self.numActions-2
-        
-        #biases = [1.0 / k for k in range(5,5+numActions)]
-        #means = [0.5 + b for b in biases]
-        self.means =[0.01 for i in range(self.numActions)]
-        self.variance=[0.25 for i in range(self.numActions)]
-
-
-
-        for i in range(0,1*self.numActions/3):
-            self.means[i]=0.07
-            self.variance[i]=0.01
-        
-        '''
-        i=(1*self.numActions)/3
-        while i<self.numActions:
-            self.means[i]=0.05
-            i=i+1
-        
-        i=(2*self.numActions)/3
-        while i<self.numActions:
-            self.means[i]=0.03
-            i=i+1
-        '''
-        self.means[self.bestAction]=0.09
-        self.variance[self.bestAction]=0.25
-        
-        
-        # initialize empirical sums
-        '''
-        for i in range(self.numActions):
-            self.payoffSums[i] = self.rewards(i)
-            self.numPlays[i]=self.numPlays[i]+1
-        '''
-        
-        theta=[1.0 for i in range(self.numActions)]
[…]

### 2017-10-14 EUCBV/codes/BayesUCB_expt3.py

@@ -1,244 +1,0 @@
-'''
-Created on Oct 6, 2015
-
-@author: Subhojyoti
-'''
-
-import math
-import random
-import numpy
-from scipy import special
-from scipy.stats import beta
-from scipy.stats import norm
-from scipy.stats import t
-#from random import betavariate
-#from scipy.special import btdtri
-import scipy
-import fileinput
-
-class ucb1_2(object):
-    '''
-    classdocs
-    '''
-
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-
-    
-     
-    def rewards(self,choice):
-        return random.gauss(self.means[choice],self.variance[choice])
-        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-
-    def readenv(self):
-        data=[]
-        filename="env/env1.txt"
-        for line in fileinput.input([filename]):
-
-            try:
-                line1 = [line.split(", ") or line.split("\n") ]
-                #print numpy.shape(line1)
-                #print line1
-                take=[]
-                for i in range(len(line1[0])):
-                    take.append(float(line1[0][i]))
-                #print take
-                data.append(take)
-            except ValueError,e:
-                print e
-        #print data
-        self.means=(data[0])
-        self.variance=(data[1])
-        
-    def ucb1(self,numActions):
-    
-        #Set the environment
-        self.numActions=numActions
-        
-        self.payoffSums = [0] * self.numActions
-        self.sqpayoffSums = [0] * self.numActions
-        self.numPlays = [1] * self.numActions
-        self.ucbs = [0] * self.numActions
-        self.upbs = [0] * self.numActions
-        self.numRounds = 400000
-        #self.numRounds = 60000
-        #numRounds = 250000
-        
-        self.arm_reward = [0]*numActions
-        
-        #bestAction=arms/2
-        self.bestAction=self.numActions - 2
-        
-        #biases = [1.0 / k for k in range(5,5+numActions)]
-        #means = [0.5 + b for b in biases]
-
-
-
-        self.means=[]
-        self.variance=[]
-        self.readenv()
-
-        print self.means
-        
-        
-        # initialize empirical sums
-        '''
-        for i in range(self.numActions):
-            self.payoffSums[i] = self.rewards(i)
[…]

### 2017-10-14 EUCBV/codes/BayesUCB_expt4.py

@@ -1,244 +1,0 @@
-'''
-Created on Oct 6, 2015
-
-@author: Subhojyoti
-'''
-
-import math
-import random
-import numpy
-from scipy import special
-from scipy.stats import beta
-from scipy.stats import norm
-from scipy.stats import t
-#from random import betavariate
-#from scipy.special import btdtri
-import scipy
-import fileinput
-
-class ucb1_2(object):
-    '''
-    classdocs
-    '''
-
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-
-    
-     
-    def rewards(self,choice):
-        return random.gauss(self.means[choice],self.variance[choice])
-        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-
-    def readenv(self):
-        data=[]
-        filename="env/env3.txt"
-        for line in fileinput.input([filename]):
-
-            try:
-                line1 = [line.split(", ") or line.split("\n") ]
-                #print numpy.shape(line1)
-                #print line1
-                take=[]
-                for i in range(len(line1[0])):
-                    take.append(float(line1[0][i]))
-                #print take
-                data.append(take)
-            except ValueError,e:
-                print e
-        #print data
-        self.means=(data[0])
-        self.variance=(data[1])
-        
-    def ucb1(self,numActions):
-    
-        #Set the environment
-        self.numActions=numActions
-        
-        self.payoffSums = [0] * self.numActions
-        self.sqpayoffSums = [0] * self.numActions
-        self.numPlays = [1] * self.numActions
-        self.ucbs = [0] * self.numActions
-        self.upbs = [0] * self.numActions
-        self.numRounds = 400000
-        #self.numRounds = 60000
-        #numRounds = 250000
-        
-        self.arm_reward = [0]*numActions
-        
-        #bestAction=arms/2
-        self.bestAction=self.numActions - 2
-        
-        #biases = [1.0 / k for k in range(5,5+numActions)]
-        #means = [0.5 + b for b in biases]
-
-
-
-        self.means=[]
-        self.variance=[]
-        self.readenv()
-
-        print self.means
-        
-        
-        # initialize empirical sums
-        '''
-        for i in range(self.numActions):
-            self.payoffSums[i] = self.rewards(i)
[…]

### 2017-10-14 EUCBV/codes/CCB.py

@@ -1,276 +1,0 @@
-'''
-Created on Dec 21, 2016
-
-@author: Subhojyoti
-'''
-
-
-import math
-import random
-import numpy
-from sets import Set
-
-class ClusUCB(object):
-    '''
-    classdocs
-    '''
-
-    min1=-9999999
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-
-
-
-    #Calculate rewards
-    def rewards(self,choice, timesteps):
-        #Gaussain Reward
-        #return random.gauss(self.means[choice],1)
-        #Bernoulli Reward(1 sample from Binomial Distribution)
-        return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-
-    #Count the number of remaining arms
-    def remArms(self):
-        count=0
-        arm=-1
-        for i in range(self.numActions):
-            if self.B[i]!=-1:
-                count=count+1
-                arm=i
-        return count
-
-    def ArmElimination(self):
-
-        max1=self.min1
-        for i in range(self.numActions):
-            
-            if max1<self.avgPayOffSums[i]:
-                max1=self.avgPayOffSums[i]
-                take=i
-            
-        
-        c=math.sqrt(( math.log(self.horizon*self.rangetake*self.rangetake))/(2*self.nm))
-
-        for i in range(self.numActions):
-
-            if (self.avgPayOffSums[i] + c < self.avgPayOffSums[take] - c) and i!=take:
-            #if self.avgPayOffSums[b] + c*math.sqrt(self.weight*1.0/self.rangetake) < self.avgPayOffSums[take1] - c*math.sqrt(self.weight*1.0/self.rangetake):
-                        
-                self.B[i]=-1
-                #print "Remove Arm:"+ str(i)
-
-
-                
-    #Calculate number of pulls each round
-    def calculate_pulls(self):
-
-
-        #self.func=math.log(self.horizon)
-        #self.func=self.horizon / math.log(self.horizon*self.numActions)
-        self.nm=int(math.ceil((2*math.log(self.horizon*self.rangetake*self.rangetake))/(self.rangetake*self.rangetake)))
-        self.T=self.timestep + self.nm*self.remArms()
-                
-        print "nm:"+str(self.nm)
-        return self.nm
-
-
-    '''
-    Running the Clustered UCB
-    '''
-
-    def clusUCB(self,arms,p,turn,wrong):
-
-        '''
-        Set Environment
-        '''
[…]

### 2017-10-14 EUCBV/codes/DMED.py

@@ -1,223 +1,0 @@
-'''
-Created on May 12, 2016
-
-@author: Subhojyoti
-
-code taken from: http://mloss.org/software/view/415/
-'''
-
-
-import math
-import random
-import numpy
-
-class DMED(object):
-    '''
-    classdocs
-    '''
-
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-
-    #Calculate Divergence Function
-    def kl(self,p,q,eps = 1e-15):
-        p = max(p, eps); 
-        p = min(p, 1-eps);  
-        q = max(q, eps); 
-        q = min(q, 1-eps);
-        y = p*math.log(p/q) + (1-p)*math.log((1-p)/(1-q));
-        return y
-   
-    #Calculate rewards
-    def rewards(self,choice):
-        #Gaussain Reward
-        #return random.gauss(self.means[choice],1)
-        #Bernoulli Reward(1 sample from Binomial Distribution)
-        return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-        
-    def DMED(self,numActions):
-
-        #genuine = true -> DMED,
-        #genuine = false -> DMED+(less aggressive)
-
-        self.genuine=True
-
-        #Set the environment
-        self.numActions=numActions
-        
-        self.N = [0] * self.numActions
-        self.S = [0] * self.numActions
-        self.L = [i for i in range(self.numActions)]
-        
-        self.payoffSums = [0] * self.numActions
-        self.numPlays = [0] * self.numActions
-        self.ucbs = [0] * self.numActions
-        self.upbs = [0] * self.numActions
-        #self.numRounds = 3000000
-        self.numRounds = 60000
-        #numRounds = 250000
-        
-        self.arm_reward = [0]*numActions
-        
-        #bestAction=arms/2
-        self.bestAction=self.numActions-2
-        
-
-        self.means =[0.07 for i in range(self.numActions)]
-        
-        '''
-        i=(1*self.numActions)/3
-        while i<self.numActions:
-            self.means[i]=0.05
-            i=i+1
-        
-        i=(2*self.numActions)/3
-        while i<self.numActions:
-            self.means[i]=0.03
-            i=i+1
-        '''
-        
-        t=1.0
-        self.means[self.bestAction]=0.1
-        
-
-        
-        cumulativeReward = 0
-        bestActionCumulativeReward = 0
-        self.actionRegret=[]
-        
-        for i in range(self.numActions):
[…]

### 2017-10-14 EUCBV/codes/DMED_expt2.py

@@ -1,234 +1,0 @@
-'''
-Created on May 12, 2016
-
-@author: Subhojyoti
-'''
-
-
-import math
-import random
-import numpy
-
-class DMED(object):
-    '''
-    classdocs
-    '''
-
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-        
-    def kl(self,p,q,eps = 1e-15):
-        p = max(p, eps); 
-        p = min(p, 1-eps);  
-        q = max(q, eps); 
-        q = min(q, 1-eps);
-        y = p*math.log(p/q) + (1-p)*math.log((1-p)/(1-q));
-        return y
-   
-    
-    def rewards(self,choice):
-        return random.gauss(self.means[choice],self.variance[choice])
-        #print sum(numpy.random.binomial(1,self.means[choice],200))/200.0
-        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-        
-    def DMED(self,numActions):
-
-        #genuine = true -> DMED, false -> DMED+(less aggressive)
-
-        #Set the environment
-        self.numActions=numActions
-        
-        self.N = [0] * self.numActions
-        self.S = [0] * self.numActions
-        self.L = [i for i in range(self.numActions)]
-        
-        self.payoffSums = [0] * self.numActions
-        self.numPlays = [0] * self.numActions
-        self.ucbs = [0] * self.numActions
-        self.upbs = [0] * self.numActions
-        #self.numRounds = 3000000
-        self.numRounds = 300000
-        #numRounds = 250000
-        
-        self.arm_reward = [0]*numActions
-        
-        #bestAction=arms/2
-        self.bestAction=self.numActions-2
-        
-        #biases = [1.0 / k for k in range(5,5+numActions)]
-        #means = [0.5 + b for b in biases]
-        self.means =[0.01 for i in range(self.numActions)]
-        self.variance =[0.25 for i in range(self.numActions)]
-
-
-        i=(1*self.numActions)/3
-        while i<self.numActions:
-            self.means[i]=0.07
-            self.variance[i]=0.01
-            i=i+1
-
-        '''
-        i=(2*self.numActions)/3
-        while i<self.numActions:
-            self.means[i]=0.03
-            i=i+1
-        '''
-        self.means[self.bestAction]=0.09
-        self.variance[self.bestAction]=0.25
-        
-        self.genuine=False
-        
-        cumulativeReward = 0
-        bestActionCumulativeReward = 0
[…]

### 2017-10-14 EUCBV/codes/EUCBV_expt1.py

@@ -1,321 +1,0 @@
-'''
-Created on Apr 1, 2017
-
-@author: Subhojyoti
-'''
-
-import math
-import random
-import numpy
-from sets import Set
-
-class EUCBV(object):
-    '''
-    classdocs
-    '''
-
-    min1=-9999999
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-
-
-
-    #Calculate rewards
-    def rewards(self,choice, timesteps):
-        #Gaussain Reward
-        #return random.gauss(self.means[choice],0.3)
-        #Bernoulli Reward(1 sample from Binomial Distribution)
-        return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-
-    #Count the number of remaining arms
-    def remArms(self):
-        count=0
-        for i in range(self.numActions):
-            if self.B[i]!=-1:
-                count=count+1
-        return count
-
-    def exp_func(self):
-        
-        #self.func=1.0
-        #self.func=math.log(self.horizon)
-        #self.func=self.numActions*self.numActions*self.horizon
-        #self.func=self.horizon / math.log(self.horizon*self.numActions)
-        self.func=self.horizon / (self.numActions*self.numActions)
-        return self.func
-
-    def upperBoundVar(self, numPlays, arm):
-        vj=abs((self.sqPayOffSums[arm]/(self.numPlays[arm])) - (self.avgPayOffSums[arm]*self.avgPayOffSums[arm]))
-        #return math.sqrt(self.rho * vj * max(math.log(( self.exp_func()*self.numRounds*self.delta_tilda)),0) / (4*numPlays) + (self.rho * max(0,math.log((self.exp_func()*self.numRounds*self.delta_tilda))) / (4*numPlays)))
-        return math.sqrt((self.rho * (vj+2.0) * max(math.log(( self.exp_func()*self.numRounds*self.delta_tilda)),0)) / (4.0*numPlays) )
-
-    '''
-    def upperBoundVarExp(self, numPlays, arm):
-        vj=((self.sqPayOffSums[arm]/self.numPlays[arm]) - (self.avgPayOffSums[arm]*self.avgPayOffSums[arm]))
[…]

### 2017-10-14 EUCBV/codes/EUCBV_expt2.py

@@ -1,334 +1,0 @@
-'''
-Created on Apr 1, 2017
-
-@author: Subhojyoti
-'''
-
-import math
-import random
-import numpy
-from sets import Set
-
-class EUCBV(object):
-    '''
-    classdocs
-    '''
-
-    min1=-9999999
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-
-
-
-    #Calculate rewards
-    def rewards(self,choice, timesteps):
-        #Gaussain Reward
-        return random.gauss(self.means[choice],self.variance[choice])
-        #Bernoulli Reward(1 sample from Binomial Distribution)
-        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-
-    #Count the number of remaining arms
-    def remArms(self):
-        count=0
-        for i in range(self.numActions):
-            if self.B[i]!=-1:
-                count=count+1
-        return count
-
-    def exp_func(self):
-        
-        #self.func=1.0
-        #self.func=math.log(self.horizon)
-        #self.func=self.numActions*self.numActions*self.horizon
-        #self.func=self.horizon / math.log(self.horizon*self.numActions)
-        self.func=self.horizon / (self.numActions*self.numActions)
-        return self.func
-
-    def upperBoundVar(self, numPlays, arm):
-        vj=((self.sqPayOffSums[arm]/self.numPlays[arm]) - (self.avgPayOffSums[arm]*self.avgPayOffSums[arm]))
-        #return math.sqrt(self.rho * vj * max(math.log(( self.exp_func()*self.numRounds*self.delta_tilda)),0) / (4*numPlays) + (self.rho * max(0,math.log((self.exp_func()*self.numRounds*self.delta_tilda))) / (4*numPlays)))
-        return math.sqrt((self.rho * (vj+2.0) * max(math.log(( self.exp_func()*self.numRounds*self.delta_tilda)),0)) / (4.0 *numPlays) )
-
-
-
-    #Arm Elimination
-    def ArmElimination(self):
-
-        take=self.min1
-        for i in range(0,self.numActions):
-            if self.B[i]!=-1:
-                if take < self.avgPayOffSums[i]:
-                    take = i
-
-        for i in range(0,self.numActions):
-
-            if self.B[i]!=-1:
-                #c=math.sqrt((self.rho * math.log(self.exp_func() *self.horizon*self.rangetake))/(2*self.nm))
-
[…]

### 2017-10-14 EUCBV/codes/EUCBV_expt3.py

@@ -1,301 +1,0 @@
-'''
-Created on Apr 1, 2017
-
-@author: Subhojyoti
-'''
-
-import math
-import random
-import numpy
-import fileinput
-
-class EUCBV(object):
-    '''
-    classdocs
-    '''
-
-    min1=-9999999
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-
-
-
-    #Calculate rewards
-    def rewards(self,choice, timesteps):
-        #Gaussain Reward
-        return random.gauss(self.means[choice],self.variance[choice])
-        #Bernoulli Reward(1 sample from Binomial Distribution)
-        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-
-    def readenv(self):
-        data=[]
-        filename="env/env1.txt"
-        for line in fileinput.input([filename]):
-
-            try:
-                line1 = [line.split(", ") or line.split("\n") ]
-                #print numpy.shape(line1)
-                #print line1
-                take=[]
-                for i in range(len(line1[0])):
-                    take.append(float(line1[0][i]))
-                #print take
-                data.append(take)
-            except ValueError,e:
-                print e
-        #print data
-        self.means=(data[0])
-        self.variance=(data[1])
-
-    #Count the number of remaining arms
-    def remArms(self):
-        count=0
-        for i in range(self.numActions):
-            if self.B[i]!=-1:
-                count=count+1
-        return count
-
-    def exp_func(self):
-        
-        #self.func=1.0
-        #self.func=math.log(self.horizon)
-        #self.func=self.numActions*self.numActions*self.horizon
-        #self.func=self.horizon / math.log(self.horizon*self.numActions)
-        self.func=self.horizon / (self.numActions*self.numActions)
-        return self.func
-
-    def upperBoundVar(self, numPlays, arm):
-        vj=((self.sqPayOffSums[arm]/self.numPlays[arm]) - (self.avgPayOffSums[arm]*self.avgPayOffSums[arm]))
-        #return math.sqrt(self.rho * vj * max(math.log(( self.exp_func()*self.numRounds*self.delta_tilda)),0) / (4*numPlays) + (self.rho * max(0,math.log((self.exp_func()*self.numRounds*self.delta_tilda))) / (4*numPlays)))
-        return math.sqrt((self.rho * (vj+2.0) * max(math.log(( self.exp_func()*self.numRounds*self.delta_tilda)),0)) / (4.0 *numPlays) )
-
[…]

### 2017-10-14 EUCBV/codes/EUCBV_expt4.py

@@ -1,302 +1,0 @@
-'''
-Created on Apr 1, 2017
-
-@author: Subhojyoti
-'''
-
-import math
-import random
-import numpy
-from sets import Set
-import fileinput
-
-class EUCBV(object):
-    '''
-    classdocs
-    '''
-
-    min1=-9999999
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-
-
-
-    #Calculate rewards
-    def rewards(self,choice, timesteps):
-        #Gaussain Reward
-        return random.gauss(self.means[choice],self.variance[choice])
-        #Bernoulli Reward(1 sample from Binomial Distribution)
-        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-
-    def readenv(self):
-        data=[]
-        filename="env/env3.txt"
-        for line in fileinput.input([filename]):
-
-            try:
-                line1 = [line.split(", ") or line.split("\n") ]
-                #print numpy.shape(line1)
-                #print line1
-                take=[]
-                for i in range(len(line1[0])):
-                    take.append(float(line1[0][i]))
-                #print take
-                data.append(take)
-            except ValueError,e:
-                print e
-        #print data
-        self.means=(data[0])
-        self.variance=(data[1])
-
-    #Count the number of remaining arms
-    def remArms(self):
-        count=0
-        for i in range(self.numActions):
-            if self.B[i]!=-1:
-                count=count+1
-        return count
-
-    def exp_func(self):
-        
-        #self.func=1.0
-        #self.func=math.log(self.horizon)
-        #self.func=self.numActions*self.numActions*self.horizon
-        #self.func=self.horizon / math.log(self.horizon*self.numActions)
-        self.func=self.horizon / (self.numActions*self.numActions)
-        return self.func
-
-    def upperBoundVar(self, numPlays, arm):
-        vj=((self.sqPayOffSums[arm]/self.numPlays[arm]) - (self.avgPayOffSums[arm]*self.avgPayOffSums[arm]))
-        #return math.sqrt(self.rho * vj * max(math.log(( self.exp_func()*self.numRounds*self.delta_tilda)),0) / (4*numPlays) + (self.rho * max(0,math.log((self.exp_func()*self.numRounds*self.delta_tilda))) / (4*numPlays)))
[…]

### 2017-10-14 EUCBV/codes/KLUCB.py

@@ -1,295 +1,0 @@
-'''
-Created on Oct 6, 2015
-
-@author: Subhojyoti
-
-code taken from: http://mloss.org/software/view/415/
-'''
-
-import math
-import random
-import numpy
-
-class klucbTest(object):
-    '''
-    classdocs
-    '''
-
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-        
-        
-    #UpperBound Definition
-    def upperBound(self, step, numPlays):
-        #return math.sqrt(2 * math.log(step + 1) / numPlays)
-        return math.sqrt(max(math.log((step + 1.0)/(self.numActions*numPlays)),0.0) / numPlays)
-    
-     
-    #Calculate rewards
-    def rewards(self,choice):
-        #Gaussain Reward
-        #return random.gauss(self.means[choice],1)
-        #Bernoulli Reward(1 sample from Binomial Distribution)
-        return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-     
-    
-    def klucbGauss(self, x, d, sig2=1., precision=0.):
-        """klUCB index computation for Gaussian distributions.
-    
-        Note that it does not require any search.
-        """
-        return x + math.sqrt(2*sig2*d)
-
-    def klucbBern(self, x, d, precision=1e-6):
-        """klUCB index computation for Bernoulli distributions."""
-        upperbound = min(1., self.klucbGauss(x, d))
-        #upperbound = min(1.,klucbPoisson(x,d)) # also safe, and better ?
-        return self.klucb(x, d, self.klBern, upperbound, precision)
-
-
-    def klBern(self, x, y):
-        """Kullback-Leibler divergence for Bernoulli distributions."""
-        
-        eps = 1e-15
-        x = min(max(x, eps), 1-eps)
-        y = min(max(y, eps), 1-eps)
-        return x*math.log(x/y) + (1-x)*math.log((1-x)/(1-y))
-    
-    def klucb(self, x, d, div, upperbound, lowerbound=-float('inf'), precision=1e-6):
-        """
-        The generic klUCB index computation.
-    
-        Input args.: x, d, div, upperbound, lowerbound=-float('inf'), precision=1e-6,
-        where div is the KL divergence to be used.
-        """
-        l = max(x, lowerbound)
-        #upperbound = self.klucbGauss(x, d, precision)
-        u = upperbound
-        while u-l>precision:
-            m = (l+u)/2
-            
-            if div(x, m)>d:
-                u = m
-            else:
-                l = m
[…]

### 2017-10-14 EUCBV/codes/KLUCB_expt2.py

@@ -1,328 +1,0 @@
-'''
-Created on Oct 6, 2015
-
-@author: Subhojyoti
-'''
-
-import math
-import random
-import numpy
-
-class klucbTest(object):
-    '''
-    classdocs
-    '''
-
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-
-
-
-    def upperBound(self, step, numPlays):
-        #return math.sqrt(2 * math.log(step + 1) / numPlays)
-        return math.sqrt(max(math.log((step + 1.0)/(self.numActions*numPlays)),0.0) / numPlays)
-
-
-    def rewards(self,choice):
-
-        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-        return random.gauss(self.means[choice],self.variance[choice])
-
-
-    def klucbGauss(self, x, d, sig2=1., precision=0.):
-        """klUCB index computation for Gaussian distributions.
-
-        Note that it does not require any search.
-        """
-        return x + math.sqrt(2*sig2*d)
-
-    def klucbBern(self, x, d, precision=1e-6):
-        """klUCB index computation for Bernoulli distributions."""
-        upperbound = min(1., self.klucbGauss(x, d))
-        #upperbound = min(1.,klucbPoisson(x,d)) # also safe, and better ?
-        return self.klucb(x, d, self.klBern, upperbound, precision)
-
-
-    def klBern(self, x, y):
-        """Kullback-Leibler divergence for Bernoulli distributions."""
-
-        eps = 1e-15
-        x = min(max(x, eps), 1-eps)
-        y = min(max(y, eps), 1-eps)
-        return x*math.log(x/y) + (1-x)*math.log((1-x)/(1-y))
-
-    def klucb(self, x, d, div, upperbound, lowerbound=-float('inf'), precision=1e-6):
-        """
-        The generic klUCB index computation.
-
-        Input args.: x, d, div, upperbound, lowerbound=-float('inf'), precision=1e-6,
-        where div is the KL divergence to be used.
-        """
-        l = max(x, lowerbound)
-        #upperbound = self.klucbGauss(x, d, precision)
-        u = upperbound
-        while u-l>precision:
-            m = (l+u)/2
-
-            if div(x, m)>d:
-                u = m
-            else:
-                l = m
-        return (l+u)/2
-
-#     def klucbGauss(self, x, d, sig2=1., precision=0.):
-#         """klUCB index computation for Gaussian distributions.
-#
[…]

### 2017-10-14 EUCBV/codes/KLUCB_expt4.py

@@ -1,333 +1,0 @@
-'''
-Created on Oct 6, 2015
-
-@author: Subhojyoti
-'''
-
-import math
-import random
-import numpy
-
-class klucbTest(object):
-    '''
-    classdocs
-    '''
-
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-
-
-
-    def upperBound(self, step, numPlays):
-        #return math.sqrt(2 * math.log(step + 1) / numPlays)
-        return math.sqrt(max(math.log((step + 1.0)/(self.numActions*numPlays)),0.0) / numPlays)
-
-
-    def rewards(self,choice):
-
-        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-        return random.gauss(self.means[choice],self.variance[choice])
-
-
-    def klucbGauss(self, x, d, sig2=1., precision=0.):
-        """klUCB index computation for Gaussian distributions.
-
-        Note that it does not require any search.
-        """
-        return x + math.sqrt(2*sig2*d)
-
-    def klucbBern(self, x, d, precision=1e-6):
-        """klUCB index computation for Bernoulli distributions."""
-        upperbound = min(1., self.klucbGauss(x, d))
-        #upperbound = min(1.,klucbPoisson(x,d)) # also safe, and better ?
-        return self.klucb(x, d, self.klBern, upperbound, precision)
-
-
-    def klBern(self, x, y):
-        """Kullback-Leibler divergence for Bernoulli distributions."""
-
-        eps = 1e-15
-        x = min(max(x, eps), 1-eps)
-        y = min(max(y, eps), 1-eps)
-        return x*math.log(x/y) + (1-x)*math.log((1-x)/(1-y))
-
-    def klucb(self, x, d, div, upperbound, lowerbound=-float('inf'), precision=1e-6):
-        """
-        The generic klUCB index computation.
-
-        Input args.: x, d, div, upperbound, lowerbound=-float('inf'), precision=1e-6,
-        where div is the KL divergence to be used.
-        """
-        l = max(x, lowerbound)
-        #upperbound = self.klucbGauss(x, d, precision)
-        u = upperbound
-        while u-l>precision:
-            m = (l+u)/2
-
-            if div(x, m)>d:
-                u = m
-            else:
-                l = m
-        return (l+u)/2
-
-#     def klucbGauss(self, x, d, sig2=1., precision=0.):
-#         """klUCB index computation for Gaussian distributions.
-#
[…]

### 2017-10-14 EUCBV/codes/MOSS.py

@@ -1,183 +1,0 @@
-'''
-Created on Oct 6, 2015
-
-@author: Subhojyoti
-'''
-
-import math
-import random
-import numpy
-
-class MOSS(object):
-    '''
-    classdocs
-    '''
-
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-        
-        
-    
-    def upperBound(self, step, numPlays):
-        #return math.sqrt(2 * math.log(step + 1) / numPlays)
-        #return math.sqrt(max(math.log((step + 1.0)/(self.numActions*numPlays)),0.0) / numPlays)
-        return math.sqrt(max(math.log((self.numRounds)/(1.0*self.numActions*numPlays)),0.0) / numPlays)
-    
-     
-    def rewards(self,choice):
-        
-        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-        return random.gauss(self.means[choice],0.5)
-        
-    def moss(self,numActions):
-    
-        #Set the environment
-        self.numActions=numActions
-        
-        self.payoffSums = [0] * self.numActions
-        self.numPlays = [0] * self.numActions
-        self.ucbs = [0] * self.numActions
-        self.upbs = [0] * self.numActions
-        #self.numRounds = self.numActions*self.numActions*self.numActions
-        self.numRounds = 500000
-        #self.numRounds = self.numActions*math.pow(10,3)
-        
-        self.arm_reward = [0]*numActions
-        
-        #bestAction=arms/2
-        self.bestAction=self.numActions-2
-        
-        
-        self.means =[0.8 for i in range(self.numActions)]
-
-        for i in range(0,1*self.numActions/3):
-            self.means[i]=0.5
-
-        '''
-        #i=(1*self.numActions)/3
-        for i in range(self.numActions/3):
-            self.means[i]=0.01
-        '''
-        '''
-        i=(2*self.numActions)/3
-        while i<self.numActions:
-            self.means[i]=0.4
-            i=i+1
-        '''
-        self.means[self.bestAction]=0.9
-        
-        print self.means
-        
-        # initialize empirical sums
-        
-        cumulativeReward = 0
-        bestActionCumulativeReward = 0
-        self.actionRegret=[]
-        t=1
-        
-        for i in range(self.numActions):
-            theReward = self.rewards(i)
-            #self.numPlays[i]=self.numPlays[i]+1
-            
-            action=i
-            theReward = self.rewards(action)
-            #print theReward,action
[…]

### 2017-10-14 EUCBV/codes/MOSS_expt2.py

@@ -1,187 +1,0 @@
-'''
-Created on Oct 6, 2015
-
-@author: Subhojyoti
-'''
-
-import math
-import random
-import numpy
-
-class MOSS(object):
-    '''
-    classdocs
-    '''
-
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-        
-        
-    
-    def upperBound(self, step, numPlays):
-        #return math.sqrt(2 * math.log(step + 1) / numPlays)
-        return math.sqrt(max(math.log((self.numRounds)/(1.0*self.numActions*numPlays)),0.0) / numPlays)
-        #return math.sqrt(max(math.log((step + 1.0)/(self.numActions*numPlays)),0.0) / numPlays)
-    
-     
-    def rewards(self,choice):
-        
-        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-        return random.gauss(self.means[choice],self.variance[choice])
-        
-    def moss(self,numActions):
-    
-        #Set the environment
-        self.numActions=numActions
-        
-        self.payoffSums = [0] * self.numActions
-        self.numPlays = [0] * self.numActions
-        self.ucbs = [0] * self.numActions
-        self.upbs = [0] * self.numActions
-        #self.numRounds = self.numActions*self.numActions*self.numActions
-        self.numRounds = 300000
-        #self.numRounds = self.numActions*math.pow(10,3)
-        
-        self.arm_reward = [0]*numActions
-        
-        #bestAction=arms/2
-        self.bestAction=self.numActions-2
-        
-        
-        self.means =[0.01 for i in range(self.numActions)]
-        self.variance=[0.25 for i in range(self.numActions)]
-
-
-        for i in range(0,1*self.numActions/3):
-            self.means[i]=0.07
-            self.variance[i]=0.01
-
-        '''
-        #i=(1*self.numActions)/3
-        for i in range(self.numActions/3):
-            self.means[i]=0.01
-        '''
-        '''
-        i=(2*self.numActions)/3
-        while i<self.numActions:
-            self.means[i]=0.4
-            i=i+1
-        '''
-        self.means[self.bestAction]=0.09
-        self.variance[self.bestAction]=0.25
-        
-        print self.means
-        
-        # initialize empirical sums
-        
-        cumulativeReward = 0
-        bestActionCumulativeReward = 0
-        self.actionRegret=[]
-        t=1
-        
-        for i in range(self.numActions):
-            theReward = self.rewards(i)
[…]

### 2017-10-14 EUCBV/codes/MOSS_expt3.py

@@ -1,187 +1,0 @@
-'''
-Created on Oct 6, 2015
-
-@author: Subhojyoti
-'''
-
-import math
-import random
-import numpy
-import fileinput
-
-class MOSS(object):
-    '''
-    classdocs
-    '''
-
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-        
-    def readenv(self):
-        data=[]
-        filename="env/env1.txt"
-        for line in fileinput.input([filename]):
-
-            try:
-                line1 = [line.split(", ") or line.split("\n") ]
-                #print numpy.shape(line1)
-                #print line1
-                take=[]
-                for i in range(len(line1[0])):
-                    take.append(float(line1[0][i]))
-                #print take
-                data.append(take)
-            except ValueError,e:
-                print e
-        #print data
-        self.means=(data[0])
-        self.variance=(data[1])
-    
-    def upperBound(self, step, numPlays):
-        return math.sqrt(max(math.log((self.numRounds)/(1.0*self.numActions*numPlays)),0.0) / numPlays)
-    
-     
-    def rewards(self,choice):
-        
-        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-        return random.gauss(self.means[choice],self.variance[choice])
-        
-    def moss(self,numActions):
-    
-        #Set the environment
-        self.numActions=numActions
-        
-        self.payoffSums = [0] * self.numActions
-        self.numPlays = [0] * self.numActions
-        self.ucbs = [0] * self.numActions
-        self.upbs = [0] * self.numActions
-        #self.numRounds = 100000 + self.numActions*self.numActions*self.numActions
-        self.numRounds = 400000
-        #self.numRounds = self.numActions*math.pow(10,3)
-        
-        self.arm_reward = [0]*numActions
-        
-        #bestAction=arms/2
-        self.bestAction=self.numActions-2
-        
-        
-        self.means=[]
-        self.variance=[]
-        self.readenv()
-
-        
-        print self.means
-        
-        # initialize empirical sums
-        
-        cumulativeReward = 0
-        bestActionCumulativeReward = 0
-        self.actionRegret=[]
-        t=1
-        
-        for i in range(self.numActions):
-            theReward = self.rewards(i)
-            #self.numPlays[i]=self.numPlays[i]+1
-            
-            action=i
-            theReward = self.rewards(action)
[…]

### 2017-10-14 EUCBV/codes/MOSS_expt4.py

@@ -1,196 +1,0 @@
-'''
-Created on Oct 6, 2015
-
-@author: Subhojyoti
-'''
-
-import math
-import random
-import numpy
-import  fileinput
-
-class MOSS(object):
-    '''
-    classdocs
-    '''
-
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-        
-    def readenv(self):
-        data=[]
-        filename="env/env3.txt"
-        for line in fileinput.input([filename]):
-
-            try:
-                line1 = [line.split(", ") or line.split("\n") ]
-                #print numpy.shape(line1)
-                #print line1
-                take=[]
-                for i in range(len(line1[0])):
-                    take.append(float(line1[0][i]))
-                #print take
-                data.append(take)
-            except ValueError,e:
-                print e
-        #print data
-        self.means=(data[0])
-        self.variance=(data[1])
-    
-    def upperBound(self, step, numPlays):
-        #return math.sqrt(2 * math.log(step + 1) / numPlays)
-        #print math.sqrt(max(math.log((self.numRounds)/(self.numActions*numPlays)),0.0) / numPlays)
-        '''
-        try:
-            return math.sqrt(max(math.log((self.numRounds)/(1.0*self.numActions*numPlays)),0.0) / numPlays)
-        except Exception as err:
-            print (self.numRounds)/(self.numActions*numPlays)
-            print(format(err))
-        '''
-        #return math.sqrt(max(math.log((step + 1.0)/(self.numActions*numPlays)),0.0) / numPlays)
-        return math.sqrt(max(math.log((self.numRounds)/(1.0*self.numActions*numPlays)),0.0) / numPlays)
-    
-     
-    def rewards(self,choice):
-        
-        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-        return random.gauss(self.means[choice],self.variance[choice])
-        
-    def moss(self,numActions):
-    
-        #Set the environment
-        self.numActions=numActions
-        
-        self.payoffSums = [0] * self.numActions
-        self.numPlays = [0] * self.numActions
-        self.ucbs = [0] * self.numActions
-        self.upbs = [0] * self.numActions
-        #self.numRounds = 100000 + self.numActions*self.numActions*self.numActions
-        self.numRounds = 400000
-        #self.numRounds = self.numActions*math.pow(10,3)
-        
-        self.arm_reward = [0]*numActions
-        
-        #bestAction=arms/2
[…]

### 2017-10-14 EUCBV/codes/OCUCB.py

@@ -1,186 +1,0 @@
-'''
-Created on Dec 21, 2016
-
-@author: Subhojyoti
-'''
-
-
-import math
-import random
-import numpy
-
-class ucb1_2(object):
-    '''
-    classdocs
-    '''
-
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-        
-        
-    
-    def upperBound(self, step, numPlays):
-        self.alpha=2.0
-        self.psi=2.0
-        return math.sqrt((self.alpha * math.log((self.psi*self.numRounds) / (step))) / numPlays)
-    
-     
-    def rewards(self,choice):
-        #return random.gauss(self.means[choice],1)
-        #print sum(numpy.random.binomial(1,self.means[choice],200))/200.0
-        return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-        
-    def ucb1(self,numActions):
-    
-        #Set the environment
-        self.numActions=numActions
-        
-        self.payoffSums = [0] * self.numActions
-        self.numPlays = [0] * self.numActions
-        self.ucbs = [0] * self.numActions
-        self.upbs = [0] * self.numActions
-        #self.numRounds = 3000000
-        #self.numRounds = 300000
-        #numRounds = 250000
-        self.numRounds = self.numActions*self.numActions*self.numActions
-        
-        self.arm_reward = [0]*numActions
-        
-        #bestAction=arms/2
-        self.bestAction=self.numActions-2
-        
-        #biases = [1.0 / k for k in range(5,5+numActions)]
-        #means = [0.5 + b for b in biases]
-        self.means =[0.05 for i in range(self.numActions)]
-
-        for i in range(0,1*self.numActions/3):
-            self.means[i]=0.01
-
-        '''
-        i=(1*self.numActions)/3
-        while i<self.numActions:
-            self.means[i]=0.05
-            i=i+1
-        
-        i=(2*self.numActions)/3
-        while i<self.numActions:
-            self.means[i]=0.03
-            i=i+1
-        '''
-        self.means[self.bestAction]=0.1
-        
-        
-        # initialize empirical sums
-        t=1
-        cumulativeReward = 0
-        bestActionCumulativeReward = 0
-        self.actionRegret=[]
-        
-        for i in range(self.numActions):
-            theReward = self.rewards(i)
-            #self.numPlays[i]=self.numPlays[i]+1
-            
-            action=i
-            self.arm_reward[action]=self.arm_reward[action]+theReward
[…]

### 2017-10-14 EUCBV/codes/OCUCB_expt2.py

@@ -1,188 +1,0 @@
-'''
-Created on Dec 21, 2016
-
-@author: Subhojyoti
-'''
-
-
-import math
-import random
-import numpy
-
-class ucb1_2(object):
-    '''
-    classdocs
-    '''
-
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-        
-        
-    
-    def upperBound(self, step, numPlays):
-        self.alpha=2.1
-        self.psi=2.0
-        return math.sqrt((self.alpha * math.log((self.psi*self.numRounds) / (step))) / numPlays)
-    
-     
-    def rewards(self,choice):
-        return random.gauss(self.means[choice],self.variance[choice])
-        #print sum(numpy.random.binomial(1,self.means[choice],200))/200.0
-        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-        
-    def ucb1(self,numActions):
-    
-        #Set the environment
-        self.numActions=numActions
-        
-        self.payoffSums = [0] * self.numActions
-        self.numPlays = [0] * self.numActions
-        self.ucbs = [0] * self.numActions
-        self.upbs = [0] * self.numActions
-        #self.numRounds = 3000000
-        self.numRounds = 300000
-        #numRounds = 250000
-        #self.numRounds = self.numActions*self.numActions*self.numActions
-        
-        self.arm_reward = [0]*numActions
-        
-        #bestAction=arms/2
-        self.bestAction=self.numActions-2
-        
-        #biases = [1.0 / k for k in range(5,5+numActions)]
-        #means = [0.5 + b for b in biases]
-        self.means =[0.01 for i in range(self.numActions)]
-        self.variance =[0.25 for i in range(self.numActions)]
-
-        for i in range(0,1*self.numActions/3):
-            self.means[i]=0.07
-            self.variance[i]=0.01
-
-        '''
-        i=(1*self.numActions)/3
-        while i<self.numActions:
-            self.means[i]=0.05
-            i=i+1
-        
-        i=(2*self.numActions)/3
-        while i<self.numActions:
-            self.means[i]=0.03
-            i=i+1
-        '''
-        self.means[self.bestAction]=0.09
-        self.variance[self.bestAction]=0.25
-        
-        
-        # initialize empirical sums
-        t=1
-        cumulativeReward = 0
-        bestActionCumulativeReward = 0
-        self.actionRegret=[]
-        
-        for i in range(self.numActions):
-            theReward = self.rewards(i)
[…]

### 2017-10-14 EUCBV/codes/OCUCB_expt3.py

@@ -1,191 +1,0 @@
-'''
-Created on Dec 21, 2016
-
-@author: Subhojyoti
-'''
-
-
-import math
-import random
-import numpy
-import fileinput
-
-class ucb1_2(object):
-    '''
-    classdocs
-    '''
-
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-        
-        
-    
-    def upperBound(self, step, numPlays):
-        self.alpha=2.0
-        self.psi=2.0
-        return math.sqrt((self.alpha * math.log((self.psi*self.numRounds) / (step))) / numPlays)
-    
-     
-    def rewards(self,choice):
-        return random.gauss(self.means[choice],self.variance[choice])
-        #print sum(numpy.random.binomial(1,self.means[choice],200))/200.0
-        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-
-    def readenv(self):
-        data=[]
-        filename="env/env1.txt"
-        for line in fileinput.input([filename]):
-
-            try:
-                line1 = [line.split(", ") or line.split("\n") ]
-                #print numpy.shape(line1)
-                #print line1
-                take=[]
-                for i in range(len(line1[0])):
-                    take.append(float(line1[0][i]))
-                #print take
-                data.append(take)
-            except ValueError,e:
-                print e
-        #print data
-        self.means=(data[0])
-        self.variance=(data[1])
-
-    def ucb1(self,numActions):
-    
-        #Set the environment
-        self.numActions=numActions
-        
-        self.payoffSums = [0] * self.numActions
-        self.numPlays = [0] * self.numActions
-        self.ucbs = [0] * self.numActions
-        self.upbs = [0] * self.numActions
-        #self.numRounds = 3000000
-        self.numRounds = 400000
-        #numRounds = 250000
-        #self.numRounds = 100000 + self.numActions*self.numActions*self.numActions
-        
-        self.arm_reward = [0]*numActions
-        
-        #bestAction=arms/2
-        self.bestAction=self.numActions-2
-        
-
-        self.means=[]
-        self.variance=[]
-        self.readenv()
-        
-        
-        # initialize empirical sums
-        t=1
-        cumulativeReward = 0
-        bestActionCumulativeReward = 0
-        self.actionRegret=[]
-        
-        for i in range(self.numActions):
-            theReward = self.rewards(i)
-            #self.numPlays[i]=self.numPlays[i]+1
[…]

### 2017-10-14 EUCBV/codes/OCUCB_expt4.py

@@ -1,191 +1,0 @@
-'''
-Created on Dec 21, 2016
-
-@author: Subhojyoti
-'''
-
-
-import math
-import random
-import numpy
-import fileinput
-
-class ucb1_2(object):
-    '''
-    classdocs
-    '''
-
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-
-    
-    def upperBound(self, step, numPlays):
-        self.alpha=2.1
-        self.psi=2.0
-        return math.sqrt((self.alpha * math.log((self.psi*self.numRounds) / (step))) / numPlays)
-    
-
-    def readenv(self):
-        data=[]
-        filename="env/env3.txt"
-        for line in fileinput.input([filename]):
-
-            try:
-                line1 = [line.split(", ") or line.split("\n") ]
-                #print numpy.shape(line1)
-                #print line1
-                take=[]
-                for i in range(len(line1[0])):
-                    take.append(float(line1[0][i]))
-                #print take
-                data.append(take)
-            except ValueError,e:
-                print e
-        #print data
-        self.means=(data[0])
-        self.variance=(data[1])
-
-    def rewards(self,choice):
-        return random.gauss(self.means[choice],self.variance[choice])
-        #print sum(numpy.random.binomial(1,self.means[choice],200))/200.0
-        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-        
-    def ucb1(self,numActions):
-    
-        #Set the environment
-        self.numActions=numActions
-        
-        self.payoffSums = [0] * self.numActions
-        self.numPlays = [0] * self.numActions
-        self.ucbs = [0] * self.numActions
-        self.upbs = [0] * self.numActions
-        #self.numRounds = 3000000
-        #self.numRounds = 300000
-        self.numRounds = 400000
-        #self.numRounds = 100000 + self.numActions*self.numActions*self.numActions
-        
-        self.arm_reward = [0]*numActions
-        
-        #bestAction=arms/2
-        self.bestAction=self.numActions-2
-        
-        #biases = [1.0 / k for k in range(5,5+numActions)]
-        #means = [0.5 + b for b in biases]
-        self.means=[]
-        self.variance=[]
-        self.readenv()
-        
-        
-        # initialize empirical sums
-        t=1
-        cumulativeReward = 0
-        bestActionCumulativeReward = 0
-        self.actionRegret=[]
-        
-        for i in range(self.numActions):
[…]

### 2017-10-14 EUCBV/codes/ThompsonSampling.py

@@ -1,169 +1,0 @@
-'''
-Created on Oct 6, 2015
-
-@author: Subhojyoti
-'''
-
-import math
-import random
-import numpy
-#from random import betavariate
-#from scipy.special import btdtri
-
-
-class   TS(object):
-    '''
-    classdocs
-    '''
-
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-        
-     
-   #Calculate rewards
-    def rewards(self,choice):
-
-        #Bernoulli Reward(1 sample from Binomial Distribution)
-        return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-        
-    def TS(self,numActions):
-    
-        #Set the environment
-        self.numActions=numActions
-        
-        self.payoffSums = [0] * self.numActions
-        self.numPlays = [0] * self.numActions
-        self.ucbs = [0] * self.numActions
-        self.upbs = [0] * self.numActions
-        #self.numRounds = 3000000
-        self.numRounds = 20000
-        #numRounds = 250000
-        
-        self.arm_reward = [0]*numActions
-        
-
-        self.bestAction=self.numActions-2
-        
-
-        self.means =[0.07 for i in range(self.numActions)]
-        
-        '''
-        i=(1*self.numActions)/3
-        while i<self.numActions:
-            self.means[i]=0.05
-            i=i+1
-        
-        i=(2*self.numActions)/3
-        while i<self.numActions:
-            self.means[i]=0.03
-            i=i+1
-        '''
-        self.means[self.bestAction]=0.1
-        
-        
-        # initialize empirical sums
-        '''
-        for i in range(self.numActions):
-            self.payoffSums[i] = self.rewards(i)
-            self.numPlays[i]=self.numPlays[i]+1
-        '''
-        
-        theta=[0.0]*self.numActions
-        success=[0.0]*self.numActions
-        failure=[0.0]*self.numActions
-        
-        for i in range(self.numActions):
-            theta[i]=random.betavariate(success[i]+1,failure[i]+1)
-            
-
-        cumulativeReward = 0
-        bestActionCumulativeReward = 0
-            
-        self.actionRegret=[]
-        t=1
-        while True:
-
-            
-            for i in range(self.numActions):
-
-                theta[i]=random.betavariate(success[i]+1,failure[i]+1)
-            
-            action=max(range(self.numActions), key=lambda i: theta[i])
-            
-
-
-            theReward = self.rewards(action)
-            
[…]

### 2017-10-14 EUCBV/codes/ThompsonSampling_expt1.py

@@ -1,190 +1,0 @@
-'''
-Created on Oct 6, 2015
-
-@author: Subhojyoti
-'''
-
-import math
-import random
-import numpy
-#from random import betavariate
-#from scipy.special import btdtri
-
-
-class ucb1_2(object):
-    '''
-    classdocs
-    '''
-
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-
-
-    
-     
-    def rewards(self,choice):
-        #return random.gauss(self.means[choice],self.variance[choice])
-        return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-        
-    def ucb1(self,numActions):
-    
-        #Set the environment
-        self.numActions=numActions
-        
-        self.payoffSums = [0] * self.numActions
-        self.numPlays = [0] * self.numActions
-        self.ucbs = [0] * self.numActions
-        self.upbs = [0] * self.numActions
-        #self.numRounds = 300000
-        self.numRounds = 60000
-        #self.numRounds = 100000 + self.numActions*self.numActions*self.numActions
-        #numRounds = 250000
-        
-        self.arm_reward = [0]*numActions
-        
-        #bestAction=arms/2
-        self.bestAction=self.numActions-2
-        
-        
-        self.means =[0.01 for i in range(self.numActions)]
-        self.variance =[0.7 for i in range(self.numActions)]
-        
-
-        i=(1*self.numActions)/3
-        while i<self.numActions:
-            self.means[i]=0.07
-            self.variance[i]=0.1
-            i=i+1
-
-        '''
-        i=(2*self.numActions)/3
-        while i<self.numActions:
-            self.means[i]=0.03
-            i=i+1
-        '''
-        self.means[self.bestAction]=0.1
-        self.variance[self.bestAction]=0.7
-        
-        
-        # initialize empirical sums
-        '''
-        for i in range(self.numActions):
-            self.payoffSums[i] = self.rewards(i)
-            self.numPlays[i]=self.numPlays[i]+1
-        '''
-        
-        theta=[0.0]*self.numActions
-        success=[0.0]*self.numActions
-        failure=[0.0]*self.numActions
-        
-        for i in range(self.numActions):
-            theta[i]=random.betavariate(success[i]+1,failure[i]+1)
-            #theta[i]=random.gauss((self.payoffSums[i]/(self.numPlays[i])) ,(1.0/(self.numPlays[i])))
-            
-        #t = numActions
-        
-        cumulativeReward = 0
[…]

### 2017-10-14 EUCBV/codes/ThompsonSampling_expt2_eucbv.py

@@ -1,187 +1,0 @@
-'''
-Created on Oct 6, 2015
-
-@author: Subhojyoti
-'''
-
-import math
-import random
-import numpy
-#from random import betavariate
-#from scipy.special import btdtri
-
-
-class ucb1_2(object):
-    '''
-    classdocs
-    '''
-
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-     
-    def rewards(self,choice):
-        return random.gauss(self.means[choice],self.variance[choice])
-        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-        
-    def ucb1(self,numActions):
-    
-        #Set the environment
-        self.numActions=numActions
-        
-        self.payoffSums = [0] * self.numActions
-        self.numPlays = [1.0] * self.numActions
-        self.ucbs = [0] * self.numActions
-        self.upbs = [0] * self.numActions
-        self.numRounds = 300000
-        #self.numRounds = 60000
-        #self.numRounds = 100000 + self.numActions*self.numActions*self.numActions
-        #numRounds = 250000
-        
-        self.arm_reward = [0]*numActions
-        
-        #bestAction=arms/2
-        self.bestAction=self.numActions-2
-        
-        
-        self.means =[0.1 for i in range(self.numActions)]
-        self.variance =[0.25 for i in range(self.numActions)]
-
-
-        i=(1*self.numActions)/3
-        while i<self.numActions:
-            self.means[i]=0.8
-            self.variance[i]=0.1
-            i=i+1
-
-        '''
-        i=(2*self.numActions)/3
-        while i<self.numActions:
-            self.means[i]=0.03
-            i=i+1
-        '''
-        self.means[self.bestAction]=0.9
-        self.variance[self.bestAction]=0.25
-        
-        
-        # initialize empirical sums
-        '''
-        for i in range(self.numActions):
-            self.payoffSums[i] = self.rewards(i)
-            self.numPlays[i]=self.numPlays[i]+1
-        '''
-        
-        theta=[0.0]*self.numActions
-        success=[0.0]*self.numActions
-        failure=[0.0]*self.numActions
-        
-        for i in range(self.numActions):
-            #theta[i]=random.betavariate(success[i]+1,failure[i]+1)
-            theta[i]=random.gauss((self.payoffSums[i]/(self.numPlays[i])) ,(1.0/(self.numPlays[i])))
-            
-        #t = numActions
-        
-        cumulativeReward = 0
-        bestActionCumulativeReward = 0
[…]

### 2017-10-14 EUCBV/codes/ThompsonSampling_expt3_eucbv.py

@@ -1,194 +1,0 @@
-'''
-Created on Oct 6, 2015
-
-@author: Subhojyoti
-'''
-
-import math
-import random
-import numpy
-import fileinput
-#from random import betavariate
-#from scipy.special import btdtri
-
-
-class ucb1_2(object):
-    '''
-    classdocs
-    '''
-
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-        
-
-    def rewards(self,choice):
-        return random.gauss(self.means[choice],self.variance[choice])
-        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-
-    def readenv(self):
-        data=[]
-        filename="env/env1.txt"
-        for line in fileinput.input([filename]):
-
-            try:
-                line1 = [line.split(", ") or line.split("\n") ]
-                #print numpy.shape(line1)
-                #print line1
-                take=[]
-                for i in range(len(line1[0])):
-                    take.append(float(line1[0][i]))
-                #print take
-                data.append(take)
-            except ValueError,e:
-                print e
-        #print data
-        self.means=(data[0])
-        self.variance=(data[1])
-
-    def ucb1(self,numActions):
-    
-        #Set the environment
-        self.numActions=numActions
-        
-        self.payoffSums = [0] * self.numActions
-        self.numPlays = [1.0] * self.numActions
-        self.ucbs = [0] * self.numActions
-        self.upbs = [0] * self.numActions
-        self.numRounds = 400000
-        #self.numRounds = 60000
-        #self.numRounds = 100000 + self.numActions*self.numActions*self.numActions
-        #numRounds = 250000
-        
-        self.arm_reward = [0]*numActions
-        
-        #bestAction=arms/2
-        self.bestAction=self.numActions-2
-        
-        
-        self.means=[]
-        self.variance=[]
-        self.readenv()
-        
-        
-        # initialize empirical sums
-        '''
-        for i in range(self.numActions):
-            self.payoffSums[i] = self.rewards(i)
-            self.numPlays[i]=self.numPlays[i]+1
-        '''
-        
-        theta=[0.0]*self.numActions
-        success=[0.0]*self.numActions
-        failure=[0.0]*self.numActions
-        
-        for i in range(self.numActions):
-            #theta[i]=random.betavariate(success[i]+1,failure[i]+1)
[…]

### 2017-10-14 EUCBV/codes/ThompsonSampling_expt4_eucbv.py

@@ -1,202 +1,0 @@
-'''
-Created on Oct 6, 2015
-
-@author: Subhojyoti
-'''
-
-import math
-import random
-import numpy
-#from random import betavariate
-#from scipy.special import btdtri
-import fileinput
-
-
-class ucb1_2(object):
-    '''
-    classdocs
-    '''
-
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-        
-
-        
-    
-    def upperBound(self, step, numPlays):
-        return math.sqrt(2 * math.log(step + 1) / numPlays)
-    
-    
-     
-    def rewards(self,choice):
-        return random.gauss(self.means[choice],self.variance[choice])
-        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-
-
-    def readenv(self):
-        data=[]
-        filename="env/env3.txt"
-        for line in fileinput.input([filename]):
-
-            try:
-                line1 = [line.split(", ") or line.split("\n") ]
-                #print numpy.shape(line1)
-                #print line1
-                take=[]
-                for i in range(len(line1[0])):
-                    take.append(float(line1[0][i]))
-                #print take
-                data.append(take)
-            except ValueError,e:
-                print e
-        #print data
-        self.means=(data[0])
-        self.variance=(data[1])
-
-    def ucb1(self,numActions):
-    
-        #Set the environment
-        self.numActions=numActions
-        
-        self.payoffSums = [0] * self.numActions
-        self.numPlays = [1] * self.numActions
-        self.ucbs = [0] * self.numActions
-        self.upbs = [0] * self.numActions
-        #self.numRounds = 3000000
-        self.numRounds = 400000
-        #self.numRounds = 100000 + self.numActions*self.numActions*self.numActions
-        #numRounds = 250000
-        
-        self.arm_reward = [0]*numActions
-        
-        #bestAction=arms/2
-        self.bestAction=self.numActions-2
-        
-        
-        self.means=[]
-        self.variance=[]
-        self.readenv()
-        
-        
-        # initialize empirical sums
-        '''
-        for i in range(self.numActions):
-            self.payoffSums[i] = self.rewards(i)
-            self.numPlays[i]=self.numPlays[i]+1
-        '''
-        
-        theta=[0.0]*self.numActions
-        success=[0.0]*self.numActions
-        failure=[0.0]*self.numActions
-        
[…]

### 2017-10-14 EUCBV/codes/UCBRevisited.py

@@ -1,238 +1,0 @@
-'''
-Created on Jul 28, 2015
-
-@author: Subhojyoti
-'''
-
-import math
-import random
-import numpy
-
-class UCBRevisted(object):
-    '''
-    classdocs
-    '''
-    
-    def __init__(self):
-        '''
-        Constructor
-        '''
-
-    
-    #Calculate rewards
-    def rewards(self,choice, timestep):
-        #Gaussain Reward
-        return random.gauss(self.means[choice],self.variance[choice])
-        #Bernoulli Reward(1 sample from Binomial Distribution)
-        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-
-    #UpperBound Definition
-    def upperBound(self, step, numPlays,horizon,delta_tilda):
-    
-        #return math.sqrt( math.log10(horizon*delta_tilda*delta_tilda) / ((2*numPlays)*math.log10(math.e)) ) 
-        
-        return math.sqrt( math.log(horizon*delta_tilda*delta_tilda) / ((2*self.nm)) )
-        #return math.sqrt( math.log(horizon*delta_tilda*delta_tilda) / ((2*numPlays)) ) 
-        #return math.sqrt( math.log10(horizon*delta_tilda*delta_tilda) / ((2*self.nm)*math.log10(math.e)) )
-    
-    def ucbRevisited(self,arms,turn,wrong):
-
-        #Set the environment
-        self.numActions = arms
-        self.horizon=300000
-        self.bestAction=self.numActions-2
-
-        self.numRounds = 0.5*math.floor(math.log10(self.horizon/math.e)/math.log10(2))
-
-        self.means =[0.01 for i in range(self.numActions)]
-        self.variance =[0.25 for i in range(self.numActions)]
-
-
-        i=(1*self.numActions)/3
-        while i<self.numActions:
-            self.means[i]=0.07
-            self.variance[i]=0.01
-            i=i+1
-
-        '''
-        i=(2*self.numActions)/3
-        while i<self.numActions:
-            self.means[i]=0.03
-            i=i+1
-        '''
-        self.means[self.bestAction]=0.09
-        self.variance[self.bestAction]=0.25
-
-
-        self.arm_reward = [0]*self.numActions
-
-        self.actionRegret=[]
-        
-        
-
-        
-        self.timestep=0
-        self.m=0
-        self.delta_tilda=1.0
-        self.B=[0 for i in range(self.numActions)]
[…]

### 2017-10-14 EUCBV/codes/create_environment.py

@@ -1,94 +1,0 @@
-'''
-Created on Jan 27, 2016
-
-@author: Subhojyoti
-'''
-
-import math
-import random
-import numpy
-import fileinput
-
-class CreateEnvironment(object):
-    '''
-    classdocs
-    '''
-
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-    
-
-
-    def readenv(self):
-        data=[]
-        filename="env/GR3.txt"
-        for line in fileinput.input([filename]):
-
-            try:
-                line1 = [line.split(", ") or line.split("\n") ]
-                #print numpy.shape(line1)
-                #print line1
-                take=[]
-                for i in range(len(line1[0])):
-                    take.append(float(line1[0][i]))
-                #print take
-                data.append(take)
-            except ValueError,e:
-                print e
-        #print data
-        self.means=(data[0])
-        self.variance=(data[1])
-
-    def create(self,numActions):
-    
-        #Set the environment
-
-        self.numActions=numActions
-        self.bestAction =  self.numActions - 2
-
-        '''
-        self.means =[]
-        self.variance=[]
-        self.readenv()
-        '''
-
-        self.means =[0.09 for i in range(self.numActions)]
-        self.variance=[0.0 for i in range(self.numActions)]
-
-
-        for i in range(0, int((0.5)*self.numActions)):
-            self.variance[i]=numpy.random.uniform(0.0,0.05)
-
-        for i in range(int((0.5)*self.numActions), self.numActions):
-            self.variance[i]=numpy.random.uniform(0.19,0.24)
-
-        for i in range(10, self.numActions):
-            self.means[i]=numpy.random.uniform(0.09,0.09)
-
-        self.means[self.bestAction] = 0.1
-        self.variance[self.bestAction] = 0.25
-
-        f = open('env/env3.txt', 'w')
-        f.writelines("%s\n" % (', '.join(["%.3f" % i for i in self.means])))
-        f.writelines("%s\n" % (', '.join(["%.3f" % i for i in self.variance])))
-        f.close()
-
-
-        print self.means
-        print self.variance
-
-
-
-
-        
-
-if __name__ == "__main__":
-
-        numActions=100
-        obj=CreateEnvironment()
-        obj.create(numActions)
-
-                

### 2017-10-14 EUCBV/codes/medianElim.py

@@ -1,198 +1,0 @@
-'''
-Created on Jul 28, 2015
-
-@author: Subhojyoti
-'''
-
-import math
-import random
-import numpy
-#import statistics
-
-class medianElim(object):
-    '''
-    classdocs
-    '''
-    
-    min1=-9999999
-    
-    def __init__(self):
-        '''
-        Constructor
-        '''
-        #print self.numRounds
-        #print self.means
-        
-    
-    def rewards(self,choice,t):
-        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-        return random.gauss(self.means[choice],self.variance[choice])
-    
-    
-    def remArms(self):
-        count=0
-        arm=-1
-        for i in range(self.numActions):
-            if self.B[i]!=-1:
-                count=count+1
-                arm=i
-        return count
-        
-    def medianElimimation(self,arms,epsilon,delta,wrong,turn):
-        
-        self.numActions = arms
-        self.horizon=300000
-        
-        self.bestAction=self.numActions-2
-
-        self.means =[0.1 for i in range(self.numActions)]
-        self.variance =[0.7 for i in range(self.numActions)]
-
-
-        i=(1*self.numActions)/3
-        while i<self.numActions:
-            self.means[i]=0.8
-            self.variance[i]=0.1
-            i=i+1
-
-        '''
-        i=(2*self.numActions)/3
-        while i<self.numActions:
-            self.means[i]=0.03
-            i=i+1
-        '''
-        self.means[self.bestAction]=0.9
-        self.variance[self.bestAction]=0.7
-        
-
-        print "Means: "+str(self.means)
-
-        self.arm_reward = [0]*self.numActions
-        
-        self.timestep=0
-        self.B=[0 for i in range(self.numActions)]
-        
-        self.payoffSums = [0] * self.numActions
-        self.numPlays = [0] * self.numActions
-        self.avgPayOffSums = [0] * self.numActions
-        
-        self.cumulativeReward = 0
-        self.bestActionCumulativeReward = 0
-        self.regret = 0
-        
-        self.arm_reward = [0]*self.numActions
-
-        self.actionRegret=[]
-
-        l=1
-        epsilon_l=epsilon*0.25
-        delta_l=delta*0.5
-        
-        while True:
-            
-            print "\n\nRound: "+str(l)
-            self.numRounds = int(math.ceil((1/(epsilon_l*0.5))*math.log(3/delta_l)))
-            print "nm: "+str(self.numRounds)
-            
[…]

### 2017-10-14 EUCBV/codes/plot5.py

@@ -1,266 +1,0 @@
-'''
-Created on Sept 5, 2016
-
-@author: Subhojyoti
-'''
-
-from matplotlib import pyplot as plt
-import numpy
-import fileinput
-import threading
-import  multiprocessing
-from multiprocessing import Manager
-
-
-class plot4(object):
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-
-    out_file='NewExpt/expt5/plotFinal'
-
-    def column(self,A, j):
-        return [A[i][j] for i in range(len(A))]
-
-    def transpose(self,A):
-        return [self.column(A, j) for j in range(len(A[0]))]
-
-    def plot_show(self,actionRegret,legend):
-
-        episode=[]
-
-        for t in range(0,self.timestep):
-            actionRegret[t]=actionRegret[t]/self.limit
-            episode.append(t);
-
-
-        #print self.actionRegret
-        #plot1,=plt.plot(episode,actionRegret,'r--',color='red',label='ClusUCB');
-        #plot2,=plt.plot(episode,actionRegret1,color='green',label='MOSS');
-        ax1 = plt.subplot(111)
-        plt.ylabel('Cumulative Regret',fontsize=18)
-        plt.xlabel('timesteps',fontsize=18)
-        ax1.plot(episode, actionRegret,label=legend)
-
-
-        plt.legend(bbox_to_anchor=(0., 1.02, 1., .102), loc=2,
-               ncol=2, mode="expand", borderaxespad=0.)
-
-        plt.show()
-
-    def fileReadWrite(self,id,name,filename,actionRegret):
-
-
-        t=0
-        count=0
-        for line in fileinput.input([filename]):
-
-            try:
-
-                line1=line.split("\n")
-                take=float(line1[0])
-
-
-                actionRegret[t]=actionRegret[t]+take
-                t=t+1
-                if t==self.timestep:
-                    t=0
-                    count=count+1
-                    print str(filename)+": "+str(count)
-
-                #prev=take
-                '''
-                if count==6:
-                    print t
-                    break
-                '''
-            except ValueError,e:
-                print  str(filename)+ " Error:" +str(e) +": Count: " +str(count)+ " t: "+str(t)
[…]

### 2017-10-14 EUCBV/codes/ucb1.py

@@ -1,155 +1,0 @@
-'''
-Created on Oct 6, 2015
-
-@author: Subhojyoti
-'''
-
-import math
-import random
-import numpy
-
-class ucb1(object):
-    '''
-    classdocs
-    '''
-
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-        
-        
-    #UpperBound Definition
-    def upperBound(self, step, numPlays):
-        return math.sqrt(2 * math.log(step + 1) / numPlays)
-    
-     
-    #Calculate rewards
-    def rewards(self,choice):
-        #Gaussain Reward
-        #return random.gauss(self.means[choice],1)
-        #Bernoulli Reward(1 sample from Binomial Distribution)
-        return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-        
-    def ucb1(self,numActions):
-    
-        #Set the environment
-        self.numActions=numActions
-        
-        self.payoffSums = [0] * self.numActions
-        self.numPlays = [0] * self.numActions
-        self.ucbs = [0] * self.numActions
-        self.upbs = [0] * self.numActions
-        #self.numRounds = 3000000
-        self.numRounds = 60000
-        #numRounds = 250000
-        
-        self.arm_reward = [0]*numActions
-
-        self.bestAction=self.numActions-2
-
-        self.means =[0.06 for i in range(self.numActions)]
-        
-
-        for i in range(self.numActions/3):
-            self.means[i]=0.01
-
-        '''
-        i=(2*self.numActions)/3
-        while i<self.numActions:
-            self.means[i]=0.03
-            i=i+1
-        '''
-        self.means[self.bestAction]=0.1
-        
-        
-        # initialize empirical sums pull each arm once
-        t=1
-        cumulativeReward = 0
-        bestActionCumulativeReward = 0
-        self.actionRegret=[]
-        
-        for i in range(self.numActions):
-            theReward = self.rewards(i)
-
-            
-            action=i
-            self.arm_reward[action]=self.arm_reward[action]+theReward
-            self.numPlays[action] += 1
-            self.payoffSums[action] += theReward
-
-            cumulativeReward += theReward
-            bestActionCumulativeReward += theReward if action == self.bestAction else self.rewards(self.bestAction)
-            regret = bestActionCumulativeReward - cumulativeReward
-            
-            self.actionRegret.append(regret)
-            
-            t = t + 1
-            
-
-        while True:
[…]

### 2017-10-14 EUCBV/codes/ucb1_expt2.py

@@ -1,180 +1,0 @@
-'''
-Created on Oct 6, 2015
-
-@author: Subhojyoti
-'''
-
-import math
-import random
-import numpy
-
-class ucb1_2(object):
-    '''
-    classdocs
-    '''
-
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-        
-        
-    
-    def upperBound(self, step, numPlays):
-        return math.sqrt(2 * math.log(step + 1) / numPlays)
-    
-     
-    def rewards(self,choice):
-        return random.gauss(self.means[choice],self.variance[choice])
-        #print sum(numpy.random.binomial(1,self.means[choice],200))/200.0
-        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-        
-    def ucb1(self,numActions):
-    
-        #Set the environment
-        self.numActions=numActions
-        
-        self.payoffSums = [0] * self.numActions
-        self.numPlays = [0] * self.numActions
-        self.ucbs = [0] * self.numActions
-        self.upbs = [0] * self.numActions
-        #self.numRounds = 3000000
-        self.numRounds = 300000
-        #numRounds = 250000
-        
-        self.arm_reward = [0]*numActions
-        
-        #bestAction=arms/2
-        self.bestAction=self.numActions-2
-        
-        
-        self.means =[0.01 for i in range(self.numActions)]
-        self.variance =[0.25 for i in range(self.numActions)]
-        
-
-        for i in range(self.numActions/3):
-            self.means[i]=0.07
-            self.variance[i]=0.01
-
-
-        '''
-        i=(2*self.numActions)/3
-        while i<self.numActions:
-            self.means[i]=0.03
-            i=i+1
-        '''
-        self.means[self.bestAction]=0.09
-        self.variance[self.bestAction]=0.25
-        
-        
-        # initialize empirical sums
-        t=1
-        cumulativeReward = 0
-        bestActionCumulativeReward = 0
-        self.actionRegret=[]
-        
-        for i in range(self.numActions):
-            theReward = self.rewards(i)
-            #self.numPlays[i]=self.numPlays[i]+1
-            
-            action=i
-            self.arm_reward[action]=self.arm_reward[action]+theReward
-            self.numPlays[action] += 1
-            self.payoffSums[action] += theReward
-            
-            #f1.writelines("ucbs: (%s)" % (', '.join(["%.8f" % ucb for ucb in ucbs])))
[…]

### 2017-10-14 EUCBV/codes/ucbV.py

@@ -1,171 +1,0 @@
-'''
-Created on May 10, 2016
-
-@author: Subhojyoti
-'''
-
-import math
-import random
-import numpy
-
-class ucbV(object):
-    '''
-    classdocs
-    '''
-
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-        
-        
-    #UpperBound Definition
-    def upperBound(self, step, numPlays,payoffSums,sqpayoffSums):
-
-        vj=1.0/numPlays*((payoffSums - (payoffSums/numPlays))*(payoffSums - (payoffSums/numPlays)))
-        return (math.sqrt((2*vj*math.log(step+1))/numPlays)+math.log(step+1)/numPlays)
-    
-     
-    #Calculate rewards
-    def rewards(self,choice):
-        #Gaussain Reward
-        #return random.gauss(self.means[choice],1)
-        #Bernoulli Reward(1 sample from Binomial Distribution)
-        return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-        
-    def ucbV(self,numActions):
-    
-        #Set the environment
-        self.numActions=numActions
-        
-        self.payoffSums = [0] * self.numActions
-        self.sqpayoffSums = [0] * self.numActions
-        self.numPlays = [0] * self.numActions
-        self.ucbs = [0] * self.numActions
-        self.upbs = [0] * self.numActions
-        #self.numRounds = 3000000
-        self.numRounds = 60000
-        #numRounds = 250000
-        
-        self.arm_reward = [0]*numActions
-
-        self.bestAction=self.numActions-2
-        
-
-        self.means =[0.07 for i in range(self.numActions)]
-        
-        '''
-        i=(1*self.numActions)/3
-        while i<self.numActions:
-            self.means[i]=0.05
-            i=i+1
-        
-        i=(2*self.numActions)/3
-        while i<self.numActions:
-            self.means[i]=0.03
-            i=i+1
-        '''
-        
-        self.means[self.bestAction]=0.1
-        
-        cumulativeReward = 0
-        bestActionCumulativeReward = 0
-        self.actionRegret=[]
-
-        # initialize empirical sums pull each arm once
-        
-        t=1
-       
-        for i in range(self.numActions):
-            theReward = self.rewards(i)
-            self.payoffSums[i] += theReward
-            self.sqpayoffSums[i] += abs( theReward*theReward)
-            self.numPlays[i]=self.numPlays[i]+1
-                
-            cumulativeReward += theReward
[…]

### 2017-10-14 EUCBV/codes/ucbV_expt2.py

@@ -1,207 +1,0 @@
-'''
-Created on May 10, 2016
-
-@author: Subhojyoti
-'''
-
-import math
-import random
-import numpy
-
-class ucbV(object):
-    '''
-    classdocs
-    '''
-
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-        
-        
-    
-    def upperBound(self, step, numPlays,payoffSums,sqpayoffSums):
-        #return math.sqrt(2 * math.log(step + 1) / numPlays)
-        #x=payoffSums / numPlays
-        #print sqpayoffSums,numPlays,step
-        
-        vj=abs(((sqpayoffSums/numPlays) - (payoffSums/numPlays)*(payoffSums/numPlays)))
-        #vj=1.0/numPlays*((payoffSums - (payoffSums/numPlays))*(payoffSums - (payoffSums/numPlays)))
-        #print vj
-        return (math.sqrt((2.0*vj*math.log(step+1))/numPlays)+math.log(step+1)/numPlays)
-    
-     
-    def rewards(self,choice):
-        return random.gauss(self.means[choice],self.variance[choice])
-        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-        
-    def ucb1(self,numActions):
-    
-        #Set the environment
-        self.numActions=numActions
-        
-        self.payoffSums = [0] * self.numActions
-        self.sqpayoffSums = [0] * self.numActions
-        self.numPlays = [0] * self.numActions
-        self.ucbs = [0] * self.numActions
-        self.upbs = [0] * self.numActions
-        #self.numRounds = 3000000
-        self.numRounds = 300000
-        #numRounds = 250000
-        
-        self.arm_reward = [0]*numActions
-        
-        #bestAction=arms/2
-        self.bestAction=self.numActions-2
-
-        self.means =[0.01 for i in range(self.numActions)]
-        self.variance =[0.25 for i in range(self.numActions)]
-
-
-        i=(1*self.numActions)/3
-        while i<self.numActions:
-            self.means[i]=0.07
-            self.variance[i]=0.01
-            i=i+1
-
-        '''
-        i=(2*self.numActions)/3
-        while i<self.numActions:
-            self.means[i]=0.03
-            i=i+1
-        '''
-        self.means[self.bestAction]=0.09
-        self.variance[self.bestAction]=0.25
-
-        '''
-        for i in range(0,1*self.numActions/3):
-            self.means[i]=0.1
[…]

### 2017-10-14 EUCBV/codes/ucbV_expt3.py

@@ -1,192 +1,0 @@
-'''
-Created on May 10, 2016
-
-@author: Subhojyoti
-'''
-
-import math
-import random
-import numpy
-import fileinput
-
-class ucbV(object):
-    '''
-    classdocs
-    '''
-
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-        
-        
-    
-    def upperBound(self, step, numPlays,payoffSums,sqpayoffSums):
-        #return math.sqrt(2 * math.log(step + 1) / numPlays)
-        #x=payoffSums / numPlays
-        #print sqpayoffSums,numPlays,step
-        
-        vj=abs(((sqpayoffSums/numPlays) - (payoffSums/numPlays)*(payoffSums/numPlays)))
-        #vj=1.0/numPlays*((payoffSums - (payoffSums/numPlays))*(payoffSums - (payoffSums/numPlays)))
-        #print vj
-        return (math.sqrt((2*vj*math.log(step+1))/numPlays)+math.log(step+1)/numPlays)
-    
-    def readenv(self):
-        data=[]
-        filename="env/env1.txt"
-        for line in fileinput.input([filename]):
-
-            try:
-                line1 = [line.split(", ") or line.split("\n") ]
-                #print numpy.shape(line1)
-                #print line1
-                take=[]
-                for i in range(len(line1[0])):
-                    take.append(float(line1[0][i]))
-                #print take
-                data.append(take)
-            except ValueError,e:
-                print e
-        #print data
-        self.means=(data[0])
-        self.variance=(data[1])
-
-    def rewards(self,choice):
-        return random.gauss(self.means[choice],self.variance[choice])
-        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-        
-    def ucb1(self,numActions):
-    
-        #Set the environment
-        self.numActions=numActions
-        
-        self.payoffSums = [0] * self.numActions
-        self.sqpayoffSums = [0] * self.numActions
-        self.numPlays = [0] * self.numActions
-        self.ucbs = [0] * self.numActions
-        self.upbs = [0] * self.numActions
-        #self.numRounds = 3000000
-        self.numRounds = 400000
-        #numRounds = 250000
-        
-        self.arm_reward = [0]*numActions
-        
-        #bestAction=arms/2
-        self.bestAction=self.numActions-2
-
-        self.means=[]
-        self.variance=[]
-        self.readenv()
-        
-        cumulativeReward = 0
[…]

### 2017-10-14 EUCBV/codes/ucbV_expt4.py

@@ -1,192 +1,0 @@
-'''
-Created on May 10, 2016
-
-@author: Subhojyoti
-'''
-
-import math
-import random
-import numpy
-import fileinput
-
-class ucbV(object):
-    '''
-    classdocs
-    '''
-
-
-    def __init__(self):
-        '''
-        Constructor
-        '''
-        
-        
-    
-    def upperBound(self, step, numPlays,payoffSums,sqpayoffSums):
-        #return math.sqrt(2 * math.log(step + 1) / numPlays)
-        #x=payoffSums / numPlays
-        #print sqpayoffSums,numPlays,step
-        
-        vj=abs(((sqpayoffSums/numPlays) - (payoffSums/numPlays)*(payoffSums/numPlays)))
-        #vj=1.0/numPlays*((payoffSums - (payoffSums/numPlays))*(payoffSums - (payoffSums/numPlays)))
-        #print vj
-        return (math.sqrt((2*vj*math.log(step+1))/numPlays)+math.log(step+1)/numPlays)
-    
-    def readenv(self):
-        data=[]
-        filename="env/env3.txt"
-        for line in fileinput.input([filename]):
-
-            try:
-                line1 = [line.split(", ") or line.split("\n") ]
-                #print numpy.shape(line1)
-                #print line1
-                take=[]
-                for i in range(len(line1[0])):
-                    take.append(float(line1[0][i]))
-                #print take
-                data.append(take)
-            except ValueError,e:
-                print e
-        #print data
-        self.means=(data[0])
-        self.variance=(data[1])
-
-    def rewards(self,choice):
-        return random.gauss(self.means[choice],self.variance[choice])
-        #return sum(numpy.random.binomial(1,self.means[choice],1))/1.0
-        
-    def ucb1(self,numActions):
-    
-        #Set the environment
-        self.numActions=numActions
-        
-        self.payoffSums = [0] * self.numActions
-        self.sqpayoffSums = [0] * self.numActions
-        self.numPlays = [0] * self.numActions
-        self.ucbs = [0] * self.numActions
-        self.upbs = [0] * self.numActions
-        #self.numRounds = 3000000
-        self.numRounds = 400000
-        #numRounds = 250000
-        
-        self.arm_reward = [0]*numActions
-        
-        #bestAction=arms/2
-        self.bestAction=self.numActions-2
-
-        self.means=[]
-        self.variance=[]
-        self.readenv()
-        
-        cumulativeReward = 0
[…]

### 2017-10-17 Appendix/AppendixConc.tex
Latest on 17/10/2017

\subsection{Sample space}

\subsection{Events}

\subsection{Sigma-algebra}

\subsubsection{Borel-sigma algebra}

\subsection{Measure}

\subsubsection{The probability measure}

\subsection{The triplet}

\subsection{Filtration}

\section{Martingale}

\subsection{Super-martingale}

\subsection{Sub-martingale}

\section{Convergence theorems}

\subsection{Monotone convergence theorem}

\subsection{Dominated convergence theorem}

\subsection{Fatou's Lemma}

\section{Sub-Gaussian distribution}

Let a random variable $X\in \R$ with variance as $\sigma^2$. Then $X$ is said to be $\sigma$-sub-gaussian for $\sigma\geq 0$ such that $\E[X] = 0$ and its moment generating function satisfies for all $\lambda \in \R $ the following condition,

\begin{align*}
\E[\exp{\lambda X}]\leq \exp\left( - \dfrac{\lambda^2\sigma^2}{2}\right)
\end{align*}

Also, note that sub-gaussian distribution is a class of distribution rather than a distribution itself.

\begin{remark}
A random variable $X\in[0,1]$ is said to be $\dfrac{1}{2}-sub-gaussian$ with its moment generating function satisfying the condition,

\begin{align*}
\E[\exp{\lambda X}]\leq \exp\left( - \dfrac{\lambda^2}{8}\right), \forall \lambda \in \R
\end{align*}

\end{remark}

\section{Concentration Inequalities}

In this section we state some of the concentration inequalities used in the proofs in several chapters of the thesis. Concentration inequality deals with the control of the tail of the average of independent random variables from their expected mean.

	Let, $X_1,X_2,\ldots,X_n$ be a sequence of independent random variables defined on a probability space $(\omega,\mathcal{F},\Pb)$, is bounded in $[a_i,b_i],\forall i=1,2,\ldots, n$. Let $S_n$ denote the sum of the random variables such that $S_n = X_1 + X_2 + \ldots + X_n$,  $\hat{r} = \dfrac{S_n}{n}$ and $E[S_n]=r$. Let $\mathcal{F}_n$ be an increasing sequence of $\sigma$-fields of $\mathcal{F}$ such that for each $n$, $\sigma(X_{1},\ldots,X_n)\subset \mathcal{F}_t$ and for $q>t$, $X_q$ is independent of $\mathcal{F}_n$.

\subsection{Markov's inequality}

Markov's inequality states that, for any $\epsilon > 0$,

\begin{align*}
\Pb[S_n > \epsilon] \leq \dfrac{\E[S_n]}{\epsilon}
\end{align*}

\subsection{Chernoff-Hoeffding Bound}

Chernoff-Hoeffding gives us the following inequality regarding the sums of independent random variables $S_n$ and their deviation from their expectation $\E[S_n]=r$, for any $\epsilon > 0$,

\begin{align*}
&\Pb\lbrace S_n - n\E[S_n] \geq \epsilon \rbrace \leq \exp\left( -\dfrac{2\epsilon^2}{n \sum_{i=1}^n(a_i -b_i)}\right) \\
%%%%%%%%%%%%%%%%%%%%%%
&=\Pb\lbrace S_n - n\E[S_n] \leq - \epsilon \rbrace \leq \exp\left( -\dfrac{2\epsilon^2}{n \sum_{i=1}^n(a_i -b_i)}\right)
\end{align*}

Considering all the random variables bounded in $[0,1]$, the above two inequalities can be reduced to,

\begin{align*}
&\Pb\lbrace \left|\dfrac{S_n}{n} - \E[S_n]\right| \geq \epsilon \rbrace \leq 2\exp\left( - 2\epsilon^2 n \right) \\
%%%%%%%%%%%%%%%%%%%%%%
&=\Pb\lbrace \left|\hat{r} - r\right| \geq \epsilon \rbrace \leq 2\exp\left( - 2\epsilon^2 n \right)
\end{align*}

\subsection{Empirical Bernstein inequality}

Similar to Chernoff-Hoeffding bound, empirical Bernstein inequality gives us the following inequality regarding the sums of independent random variables $S_n$ and their deviation from their expectation $\E[S_n]=r$, for any $\epsilon > 0$,

\begin{align*}
&\Pb\lbrace S_n - n\E[S_n] \geq \epsilon \rbrace \leq \exp\left( -\dfrac{2\epsilon^2}{\left(2\sigma^2 + \frac{2 b_{\max} \epsilon}{3}\right) n \sum_{i=1}^n(a_i -b_i)}\right), \\
%%%%%%%%%%%%%%%%%%%%%%
&\Pb\lbrace S_n - n\E[S_n] \leq - \epsilon \rbrace \leq \exp\left( -\dfrac{2\epsilon^2}{\left(2\sigma^2 + \frac{2 b_{\max} \epsilon}{3}\right) n \sum_{i=1}^n(a_i -b_i)}\right)
\end{align*}

Considering all the random variables bounded in $[0,1]$, the above two inequalities can be reduced to,

\begin{align*}
&\Pb\lbrace \left|\dfrac{S_n}{n} - \E[S_n]\right| \geq \epsilon \rbrace \leq 2\exp\left( -\dfrac{2\epsilon^2 n}{\left(2\sigma^2 + \frac{2\epsilon}{3}\right)}\right) \\
%%%%%%%%%%%%%%%%%%%%%%
&=\Pb\lbrace \left|\hat{r} - r\right| \geq \epsilon \rbrace \leq 2\exp\left( -\dfrac{2\epsilon^2 n}{\left(2\sigma^2 + \frac{2\epsilon}{3}\right)}\right)
\end{align*}

### 2017-10-17 Chapter1/feedback.tex
Latest on 17/10/2017

In an online sequential setting, the feedback that the learner receives from the environment can be characterized into three broad categories, full information feedback, partial information feedback and bandit feedback.

	To illustrate the different types of feedback we will take help of the following example. Let a learner be given a set of actions $i\in\A$ such that $|A|=K$. Let, the environment be such that each action has a probability distribution $D_i$ attached to it which is fixed throughout the time horizon $T$. The learning proceeds as follows:-

\begin{algorithm}[!th]
\caption{An online sequential game}
\label{alg:OSeqGame}
\begin{algorithmic}
\State {\bf Input:} Time horizon $T$, $K$ number of arms with unknown parameters of reward distribution
\State \For{ each timestep $t=1,2,\ldots, T$}
\State The environment chooses a reward $r_{i,t},\forall i\in\A$.
\State The learner chooses $m$ actions such that $m < K$, where $A$ is the set of arms and $|A|=K$.
\State The learner observes the reward $R_{m,t}=F\left( r_{i,t}\right)$.
\State \EndFor
\end{algorithmic}
\end{algorithm}

%Let $G(V,E)$ denote a graph where $V$ denotes the set of nodes in the graph and $E$ denotes the set of edges of the graph. Let there be a single starting node, denoted by $\mathcal{s}\in V$ from where the learner must start and try to reach the destination node denoted by $\mathcal{d}\in V$. Each edge has a delay associated with it which is unknown to the learner. This delay is an $i.i.d$ random variable from the distribution $D_{ij}$ associated with the edge $e_{ij}$ between the vertices $v_i$ and $v_j$. Whenever an edge is chosen the environment reveals to the learner  At every timestep the learner chooses a set of edges and receives some form of feedback from the environment. The goal of the learner is to find the path from $s$ to $d$ which has the minimum delay associated with it.

\subsection{Full information feedback}
In full information feedback, when a learner selects $m$ actions then the environment reveals the rewards of all the actions $i\in \A$. Hence, in this form of feedback  the learner observes $R_{m,t} = \lbrace r_{i,t},\forall i\in\A\rbrace$.

\subsection{Partial information feedback}
In partial information feedback, when a learner selects $m$ actions then the environment reveals the rewards of only those $m$ actions for $m\in \A$. Hence, in this form of feedback  the learner observes $R_{m,t} = \lbrace r_{m,t},\forall m\in\A\rbrace$. This is also sometimes called the semi-bandit feedback.

\subsection{Bandit feedback}
In bandit feedback, when a learner selects $m$ actions then the environment reveals a cumulative reward of those $m$ actions for $m\in \A$. Hence, in this form of feedback  the learner observes $R_{m,t} = \sum_{q=1}^{m} r_{q,t}$. Note, that when $m=1$, then the learner observes the reward of only that action that it has chosen out of $K$ actions.

### 2017-10-17 Chapter1/types.tex
Latest on 17/10/2017

In this section we discuss on the various types of bandits that are available in literature.

\subsection{Types of Bandits based on Environment}

\subsubsection{Stochastic Bandits}
In stochastic bandits, the distribution associated with each of the arms remains fixed throughout the time horizon $T$. Some of the notable papers associated with this type of setup are \citet{robbins1952some}, \citet{lai1985asymptotically},  \citet{agrawal1995sample}, \citet{auer2002finite}, \citet{auer2010ucb}, \citet{audibert2009minimax}, \citet{lattimore2015optimally}, etc. Chapter \ref{chap:SMAB} and Chapter \ref{chap:EUCBV} is based on this setup where we discuss extensively on the latest state-of-the-art algorithms.

\subsubsection{Non-stochastic Bandits}

In non-stochastic setting the distribution associated with each arm varies over the duration of the play. Two natoable examples of this are:-

\begin{itemize}
\item \textbf{Adversarial bandits: } In adversarial bandits, an adversary decides the payoff for each arm before the learner selects an arm. This adversary may or may not be oblivious to the learning algorithm employed by the learner. In each of these cases a different guarantee on the performance of the learner can be arrived at. Some of the important papers in this setting are \citet{auer2002nonstochastic}, \citet{auer2002nonstochastic}, \citet{auer2002using}, \citet{kocak2014efficient}.

\item \textbf{Piece-wise stationary:} Another setup under this setting can be the piece-wise stationary setting. In this setting, the distribution associated with each arm is not fixed throughout the time horizon and changes either arbitrarily at particular changepoints, or changes at a fixed period. The distribution associated with each arm then  remains fixed till the next chnagepoint is encountered. Chapter (to be added) is based on this.
\end{itemize}

\subsubsection{Contextual Bandits}

The idea of clustering has been extensively studied in the contextual bandit setup, an extension of the MAB where side information or features are attached to each arm. The clustering is done over the features representing the arms to capture the complexity of the problem better when a large-number of arms are involved. Typical examples of this setting are in web-advertising domain, news article selection, etc. Some notable papers available for this setting are   \citet{auer2002using}, \citet{langford2008epoch}, \citet{li2010contextual}, \citet{beygelzimer2011contextual}, \citet{slivkins2014contextual},etc.

%

%Clustering has been extensively studied in the area of contextual MAB. In contextual MAB, there are side-information or features attached to each arm (see  \citet{auer2002using,langford2008epoch,li2010contextual,beygelzimer2011contextual, slivkins2014contextual}).   \cite{bui2012clustered,cesa2013gang,gentile2014online}. Please note that we do not cluster over the context rather we cluster the arms into groups.

\subsection{Types of Bandits based on goal}

\subsubsection{Cumulative regret minimization}

\subsubsection{Simple regret minimization}

\subsubsection{External Regret minimization}

\subsection{Collaborative Bandits}

Distributed bandits are specific setup of MAB where a network of bandits collaborate with each other to identify the optimal arm(s) (see \citet{awerbuch2008competitive,liu2010distributed,szorenyi2013gossip,hillel2013distributed}). In our setting we can assign each of the $p$ clusters to individual bandits and at the end of each round they can share information synchronously to identify the optimal arm. This naturally results in a speedup of operation and helps in identifying the best arm faster. The clustering in this case is typically done over the feature space \citet{bui2012clustered}, \citet{cesa2013gang}, \citet{gentile2014online}.

### 2017-10-17 Chapter2/related.tex
Latest on 17/10/2017

@@
+\subsection{Lower bound in SMAB}
+
 	SMAB problems have been extensively studied in several earlier works such as \citet{thompson1933likelihood}, \citet{robbins1952some} and \citet{lai1985asymptotically}.
@@
 
+\subsection{The Upper Confidence bound approach}
+
 	Over the years SMABs have seen several algorithms with strong regret guarantees.
@@
 The upper confidence bound algorithms balance the exploration-exploitation dilemma by linking the uncertainty in estimate of an arm with the number of times an arm is pulled, and therefore ensuring sufficient exploration.
-One of the earliest among these algorithms is UCB1 \citep{auer2002finite}, which has a gap-dependent regret upper bound of  $O\left(\frac{K\log T}{\Delta}\right)$, where $\Delta = \min_{i:\Delta_i>0} \Delta_i$.
+
+\subsubsection{UCB1 Algorithm}
+
+	One of the earliest among these algorithms is UCB1 algorithm proposed in \citet{auer2002finite}. The algorithm is mentioned
+
+\begin{algorithm}[h!]
+\caption{UCB1}
+\label{alg:ucb1}
+\begin{algorithmic}[1]
+\State Pull each arm once
+ \For{$t=K+1,..., T$}
+\State Pull the arm such that $\argmax_{i\in A}\bigg\lbrace\hat{r}_{i} + \sqrt{\dfrac{2\log (t)}{n_i}}\bigg\rbrace$
+\State $t:=t+1 $
+ \EndFor
+\end{algorithmic}
+\end{algorithm}
+
+	UCB1 has a gap-dependent regret upper bound of  $O\left(\frac{K\log T}{\Delta}\right)$, where $\Delta = \min_{i:\Delta_i>0} \Delta_i$.
 This result is asymptotically order-optimal for the class of distributions considered.
 But, the worst case gap-independent regret bound of UCB1 is found to be  $O \left(\sqrt{KT\log T}\right)$.
-In the later work of \citet{audibert2009minimax}, the authors propose the MOSS algorithm and showed that the worst case gap-independent regret bound of MOSS is $O\left( \sqrt{KT} \right)$ which improves upon UCB1 by a factor of order $\sqrt{\log T}$.
-However, the gap-dependent regret of MOSS is $O\left( \frac{K^{2}\log\left(T\Delta^{2}/K\right)}{\Delta}\right)$ and in certain regimes, this can be worse than even UCB1 (see \citet{audibert2009minimax,lattimore2015optimally}).
+
+\subsubsection{UCB-Improved Algorithm}
+
+\begin{algorithm}[!h]
+\caption{UCB-Improved}
+\label{alg:ucbi}
+\begin{algorithmic}[1]
+\State {\bf Input:} Time horizon $T$
+\State {\bf Initialization:} Set $B_{0}:=A$ and $\epsilon_{0}:=1$.
+\For{$m=0,1,..\big \lfloor \dfrac{1}{2}\log_{2} \dfrac{T}{e}\big\rfloor$}	
+\State Pull each arm in $B_m$, $n_{m}=\bigg\lceil\dfrac{2\log{( T\epsilon_{m}^{2})}}{\tilde{\Delta}_{m}}\bigg\rceil$ number of times.
+%so that the total  it has been pulled is
+\ArmElim
+\State For each $i \in B_{m}$, delete arm ${i}$ from $B_{m}$ if,
+\begin{align*}
+\hat{r}_{i} + \sqrt{\dfrac{\log{(T\epsilon_{m}^{2})}}{2 n_{m}}}  < \max_{{j}\in B_{m}}\bigg\lbrace\hat{r}_{j} -\sqrt{\dfrac{\log{( T\epsilon_{m}^{2})}}{2 n_{m}}} \bigg\rbrace
+\end{align*}
+\EndArmElim
+%\ResParam
+\State Set $\epsilon_{m+1}:=\dfrac{\epsilon_{m}}{2}$, Set $B_{m+1}:=B_{m}$
+%\EndResParam
+\State Stop if $|B_{m}|=1$ and pull ${i}\in B_{m}$ till $n$ is reached.
+\EndFor
+\end{algorithmic}
+\end{algorithm}
 
@@
 On the other hand, the worst case gap-independent regret bound of UCB-Improved is $O\left(\sqrt{KT\log K}\right)$.
+
+\subsubsection{MOSS Algorithm}
+
+\begin{algorithm}[!h]
+\caption{MOSS}
+\label{alg:moss}
+\begin{algorithmic}[1]
+\State Pull each arm once
+ \For{$t=K+1,..., T$}
+\State Pull the arm such that $\argmax_{i\in A}\bigg\lbrace\hat{r}_{i} + \sqrt{\dfrac{\max\lbrace 0,\log(\frac{T}{K s_i})\rbrace}{s_i}}\bigg\rbrace$
+\State $t:=t+1 $
+ \EndFor
+\end{algorithmic}
+\end{algorithm}
+
+	In the later work of \citet{audibert2009minimax}, the authors propose the MOSS algorithm and showed that the worst case gap-independent regret bound of MOSS is $O\left( \sqrt{KT} \right)$ which improves upon UCB1 by a factor of order $\sqrt{\log T}$.
+However, the gap-dependent regret of MOSS is $O\left( \frac{K^{2}\log\left(T\Delta^{2}/K\right)}{\Delta}\right)$ and in certain regimes, this can be worse than even UCB1 (see \citet{audibert2009minimax,lattimore2015optimally}).
+
 	Recently in \citet{lattimore2015optimally}, the authors showed that  the algorithm OCUCB achieves order-optimal gap-dependent regret bound of $O\left(\sum_{i=2}^{K}\frac{\log\left(T/H_i\right)}{\Delta_i}\right)$ where $H_i=\sum_{j=1}^{K}\min\left\lbrace \frac{1}{\Delta_i^2},\frac{1}{\Delta_j^2}\right\rbrace$, and a gap-independent regret bound of $O\left( \sqrt{KT}\right)$.
@@
 However, unlike our proposed EUCBV algorithm, OCUCB does not take into account the variance of the arms; as a result, empirically  we find  that our algorithm outperforms OCUCB in all the environments considered.
+
+\begin{algorithm}[h!]
+\caption{UCBV}
+\label{alg:ucbv}
+\begin{algorithmic}[1]
+\State Pull each arm once
+ \For{$t=K+1,..., T$}
+\State Pull the arm such that $\max_{i\in A}\bigg\lbrace\hat{r}_{i} + \sqrt{\dfrac{2\hat{v}_i\log (t)}{s_i}} + \dfrac{3\log (t)}{3}\bigg\rbrace$
+\State $t:=t+1 $
+ \EndFor
+\end{algorithmic}
+\end{algorithm}
 
@@
 Empirically, \citet{audibert2009exploration} showed that UCBV outperforms UCB1 in several scenarios.
+
+\subsection{Bayesian Approach}
+
+\begin{algorithm}[!h]
+\caption{Bernoulli Thompson Sampling}
+\label{alg:ts}
+\begin{algorithmic}
+\State {\bf Input:} Time horizon $T$; 
+\State {\bf Initialization:} For each arm $i:=1$ to $K$ set $S_i =0$ and $F_i =0$
+\State \For{$t=1,..,T$}
+\State \For{$i=1,..,K$}
+\State Sample $\theta_{i}(t)$ from the $Beta(S_i+1,F_i+1)$ distribution.
+\EndFor
+\State Play the arm $i(t):=\argmax_i\theta_i(t)$ and observe reward $X_{i,t}$.
+\If{$X_{i,t}=1$}
+$S_i (t) = S_i (t) + 1$
+\Else{$F_i (t) = F_i (t) + 1$}
+\EndIf
+\EndFor
+\end{algorithmic}
+\end{algorithm}
 
@@
 
+\subsection{Information Theoretic approach}
+
 	The final design principle we state is the information theoretic approach of DMED  \citep{honda2010asymptotically} and KLUCB \citep{garivier2011kl} algorithms.

### 2017-10-17 Chapter4/prevRes.tex
Latest on 17/10/2017

Significant amount of literature is available on the stochastic MAB setting with respect to minimizing the cumulative regret. Chapter \ref{chap:SMAB} and \ref{chap:EUCBV} deals with that. In this work we are particularly interested in \emph{pure-exploration MABs},  where the focus in primarily on simple regret rather than the cumulative regret. The relationship between cumulative regret and simple regret is proved in \citet{bubeck2011pure} where the authors prove that minimizing the simple regret necessarily results in maximizing the cumulative regret.
The pure exploration problem has been explored  mainly under the following two settings:

\subsection{Fixed Budget setting}

Here the learning algorithm has to suggest the best arm(s) within a fixed time-horizon $T$, that is usually given as an input. The objective is to maximize the probability of returning the best arm(s).  This is the scenario we consider in this chapter. Some of the important algorithms used in pure exploration setting are discussed in the next part.

\subsubsection{UCB-Exploration Algorithm}

\begin{algorithm}[!h]
\caption{UCBE}
\label{alg:ucbe}
\begin{algorithmic}[1]
\State \textbf{Input: } The budget $T$
\State Pull each arm once
\For{$t=K+1,..., T$}
\State Pull the arm such that $\argmax_{i\in \A}\bigg\lbrace\hat{r}_{i} + \sqrt{\dfrac{a}{n_i}}\bigg\rbrace$, where $a = \dfrac{25(T-K)}{36 H_1}$ and $H_1 = \sum_{i=1}^{K}\dfrac{1}{\Delta_i^2}$.
\State $t:=t+1 $
\EndFor
\end{algorithmic}
\end{algorithm}

In \citet{audibert2010best} the authors propose the  UCBE and the Successive Reject (SR) algorithm, and prove simple-regret guarantees for the problem of identifying the single best arm.  In the combinatorial fixed budget setup \citet{gabillon2011multi} propose the GapE and GapE-V algorithms that suggest, with high probability, the best $m$ arms at the end of the time budget.

\subsubsection{Successive Reject Algorithm}

\begin{algorithm}[h!]
\caption{Successive Reject(SR)}
\label{alg:sr}
\begin{algorithmic}[1]
\State \textbf{Input: } The budget $T$
\State \textbf{Initialization: } $n_0 = 0$
\State \textbf{Definition: } $\bar{\log K} = \dfrac{1}{2} + \sum_{i=2}^{K}\dfrac{1}{i}$, $n_k = \dfrac{1}{\bar{\log K}}\dfrac{T-K}{K + 1 - m}$
\For{For each phase $m=1,..., K-1$}
\State For each $i \in B_{m}$, select arm $i$ for $n_k - n_{k-1}$ rounds.
\State Let $B_{m+1} = B_m\setminus \argmin_{i\in B_m} \hat{r}_i$
(remove one element from $B_m$ , if there
is a tie, select randomly the arm to dismiss among the worst arms).
\State $m:=m+1 $
\EndFor
\State Output the single remaining $i\in B_{m}$.
\end{algorithmic}
\end{algorithm}

Similarly, \citet{bubeck2013multiple} introduce the  Successive Accept Reject (SAR) algorithm, which is an extension of the SR algorithm; SAR is a round based algorithm whereby at the end of each round an arm is either accepted or rejected (based on certain confidence conditions) until the top $m$ arms are suggested at the end of the budget with high probability. A similar combinatorial setup was explored in \citet{chen2014combinatorial} where the authors propose the Combinatorial Successive Accept Reject (CSAR) algorithm, which is similar in concept to SAR but with a more general setup.

\subsection{Fixed Confidence setting}

In this setting the learning algorithm has to suggest the best arm(s) with a fixed confidence (given as input) with as fewer number of attempts as possible. The single best arm identification has been studied in \citet{even2006action}, while for the combinatorial setup \citet{kalyanakrishnan2012pac} have proposed the LUCB algorithm which, on termination, returns  $m$ arms which are at least $\epsilon$ close to the true top-$m$ arms with probability at least $1-\delta$. For a detail survey of this setup we refer the reader to \citet{jamieson2014best}.

\subsection{Unified Setting}
Apart from these two settings some unified approaches has also been suggested in \citet{gabillon2012best} which proposes the algorithms UGapEb and UGapEc which can work in both the above two settings. The thresholding bandit problem is a specific instance of the pure-exploration setup of \citet{chen2014combinatorial}.

### 2017-10-17 Chapter4/prevResAPT.tex
Latest on 17/10/2017

\begin{algorithm}[!h]
\caption{APT}
\label{alg:apt}
\begin{algorithmic}
\State {\bf Input:} Time horizon $T$, threshold $\tau$, tolerance factor $\epsilon\geq 0$
\State Pull each arm once
\State \For{$t=K+1,..,T$}
\State Pull arm $j\in\argmin_{i\in A}\big\lbrace \left(|\hat{r}_{i} - \tau | + \epsilon\right)\sqrt{n_i}\big\rbrace$ and observe the reward for arm $j$.
\EndFor
\State \textbf{Output:} $\hat{S}_{\tau}=\lbrace i: \hat{r}_{i}\geq \tau \rbrace$.
\end{algorithmic}
\end{algorithm}

In the latest work of \citet{locatelli2016optimal} Anytime Parameter-Free Thresholding (APT) algorithm comes up with an improved anytime guarantee than CSAR for the thresholding bandit problem.

### 2017-11-04 Chapter2/conclusion.tex
Latest on 5/11/2017

In this chapter we looked at the stochastic multi-armed bandit (SMAB) setting and discussed how it is important in the general reinforcement learning setup. We also looked at the various state-of-the-art algorithms in the literature for the SMAB setting and discussed the advantages and disadvantages of them. The regret bounds that have been proven for the said algorithms have also been discussed at length and their confidence intervals have also been compared against each other. In the next chapter we provide our solution to this SMAB setting which achieves an almost order-optimal regret bound.

### 2017-11-04 Chapter2/motivation.tex
Latest on 5/11/2017

@@
 There has been a significant amount of research in the area of stochastic MABs.
-One of the earliest work can be traced to \cite{thompson1933likelihood}, which deals with  the problem of choosing between two treatments to administer on patients who come in sequentially.
-In recent years the MAB setting has garnered extensive popularity because of its simple learning  model and its practical applications in a wide-range of industries, including, but not limited to, mobile channel allocations, online advertising and computer simulation games.
+One of the earliest work can be traced to \citet{thompson1933likelihood}, which deals with  the problem of choosing between two treatments to administer on patients who come in sequentially.
+In \citet{thompson1935theory} this work was extended to include more general cases of finitely many treatments.
+In recent years the SMAB setting has garnered extensive popularity because of its simple learning  model and its practical applications in a wide-range of industries, including, but not limited to, mobile channel allocations, online advertising and computer simulation games.
+Some of these problems have been already discussed in chapter \ref{chap:intro}, section \ref{motivation} and an interested reader can refer to it.

### 2017-11-04 Chapter2/notation.tex
Latest on 5/11/2017

@@
-The mean of the reward distribution $D_i$ associated with an arm $i$ is denoted by $r_i$ whereas the mean of the reward distribution of the optimal arm $*$ is denoted by $r^*$ such that $r_i < r^*, \forall i\in \A$, where $\A$ is the set of arms such that $|\A|=K$.
+\begin{assumption}
+\label{SMAB:assm:1}
+In the considered SMAB setting we assume the optimal arm to be unique and it is denoted by $*$.
+\end{assumption}
+
+\begin{assumption}
+\label{SMAB:assm:2}
+We assume the rewards of all arms are bounded in $[0,1]$.
+\end{assumption}
+
+\textbf{Notations:} The mean of the reward distribution $D_i$ associated with an arm $i$ is denoted by $r_i$ whereas the mean of the reward distribution of the optimal arm $*$ is denoted by $r^*$ such that $r_i < r^*, \forall i\in \A$, where $\A$ is the set of arms such that $|\A|=K$.
 We denote the individual arms labeled $i$, where  $i=1,\ldots,K$.
-We denote an arbitrary round of EUCBV by $m$.
-For simplicity, we assume that the optimal arm is unique and denote it by ${*}$.
 We denote the sample mean of the rewards for an arm $i$ at time instant $t$ by $\hat{r}_{i}(t)=\frac{1}{z_{i}(t)}\sum_{\ell=1}^{z_i(t)} X_{i,\ell}$, where $X_{i,\ell}$ is the reward sample received when arm $i$ is pulled for the $\ell$-th time, and $z_i(t)$ is the number of times arm $i$ has been pulled until timestep $t$.
@@
 Whenever there is no ambiguity about the underlying  time index $t$, for simplicity we neglect $t$ from the notations and simply use  $\hat{r}_i, \hat{v}_i,$ and $z_i$ to denote the respective quantities.
-We assume the rewards of all arms are bounded in $[0,1]$.
+Also, $\Delta$ denotes the minimum gap such that $\Delta=\min_{i\in\A}\lbrace \Delta_{i}\rbrace$.
+
+%For simplicity, we assume that the optimal arm is unique and denote it by ${*}$.
+%We denote an arbitrary round of EUCBV by $m$.

### 2017-11-04 Chapter2/probDef.tex
Latest on 5/11/2017

@@
-With the formulation of SMAB stated in algorithm \ref{alg:SMAB}, the learner faces the task of balancing exploitation and exploration.
-In other words, should the learner pull the arm which currently has the best-known estimates (exploit) or explore arms more thoroughly to ensure that a correct decision is being made.
-This is termed as the \textit{exploration-exploitation dilemma}, one of the fundamental challenges of Reinforcement learning.
+With the formulation of SMAB stated in algorithm \ref{alg:SMAB}, the learner seeks to identify the optimal arm as quickly as possible to maximize its rewards.
+In the pursuit of this, the learner faces the task of balancing exploitation and exploration.
+In other words, should the learner pull the arm which currently has the best-known estimates (exploit) or explores arms more thoroughly to ensure that a correct decision is being made.
+This is termed as the \textit{exploration-exploitation dilemma}, one of the fundamental challenges of reinforcement learning as discussed in chapter \ref{chap:intro}.
 
-	The objective in the stochastic bandit problem is to minimize the cumulative regret, which is defined as follows:
+    The objective of the learner in the SMAB setting is to maximize his rewards or in other words, to minimize the cumulative regret, which is defined as follows:
 \begin{align*}
@@
 where $\Delta_{i}=r^{*}-r_{i}$ is the gap between the means of the optimal arm and the $i$-th arm.
+In the theoretical analysis of each algorithm, we try to obtain bounds on this cumulative regret.
+These bounds can be both asymptotic or for a finite horizon.
+Again, these regret bounds can be either gap-dependent or gap-independent bounds.
+
+\begin{enumerate}
+\item\textbf{Asymptotic regret bounds:} These type of regret bounds are valid for a large horizon $T$ tending to infinity.
+In other words, if the guarantees of these bounds to be held true then an infinite number of samples needs to be collected.
+
+\item\textbf{Finite horizon regret bounds:} These type of regret bounds are valid for a finite horizon when a limited number of samples are allowed to be collected.
+Note, that the knowledge of horizon may or may not be known to the learner.
+
+\item\textbf{Gap-Dependent regret bounds:} In gap-dependent or problem dependent regret bounds the regret is obtained as a measure of the gap $\Delta_{i}=r^{*}-r_{i}$ for an arm $i\in\A$ along with the time horizon and number of arms.
+It is so called because the regret bound depends explicitly on the means of the arms considered for that environment along with the stated assumptions on the distribution.
+
+\item\textbf{Gap-Independent regret bounds:} In gap-independent regret bound the regret does not contain the gaps and is stated explicitly in terms of the number of arms and the horizon.
+This is because the regret depends only on the distributional assumption, but not on the means of the arms considered.
+In fact, gap-independent regret bounds point to something more general and informative.
+These type of bounds actually give us the maximum possible regret such that no matter what is the policy, there will be an environment on which the policy achieves almost the same regret as the gap-independent regret upper bound.
+This leads to the notion of minimax regret.
+
+\item\textbf{Minimax regret bounds:} For a finite horizon $T$, $K$ number of arms, for all set of possible policies $\pi_{T,K}$ over $T$ and $K$ and all possible environment class $\mathcal{E}$ the minimax regret is given by,
+\begin{align*}
+R_T(\mathcal{E})=\inf_{\pi\in\pi_{T,K}}\sup_{E\in\mathcal{E}}R_T(\pi,E).
+\end{align*}
+
+Hence, this value is independent of any specific choice of a policy $\pi$ but only depends on $T$, $K$ and $\mathcal{E}$ where the dependence on $K$ is hidden in $\mathcal{E}$.
+\end{enumerate}

### 2017-11-04 Chapter2/related.tex
Latest on 5/11/2017

@@
 
-	SMAB problems have been extensively studied in several earlier works such as \citet{thompson1933likelihood}, \citet{robbins1952some} and \citet{lai1985asymptotically}.
+    SMAB problems have been extensively studied in several earlier works such as \citet{thompson1933likelihood},  \citet{thompson1935theory}, \citet{robbins1952some} and \citet{lai1985asymptotically}.
 Lai and Robbins in  \citet{lai1985asymptotically} established an asymptotic lower bound for the cumulative regret.
@@
 \begin{align*}
-\liminf_{T \to \infty}\frac{\E[R_{T}]}{\log T}\geq\sum_{\{i:r_{i}<r^{*}\}}\frac{(r^{*}-r_{i})}{D(Q_{i}||Q^{*})}
+\liminf_{T \to \infty}\frac{\E[R_{T}]}{\log T}\geq\sum_{\{i:r_{i}<r^{*}\}}\frac{(r^{*}-r_{i})}{KL(Q_{i}||Q^{*})}
 \end{align*}    
-where $D(Q_{i}||Q^{*})$ is the Kullback-Leibler divergence between the reward densities $Q_{i}$ and $Q^{*}$, corresponding to arms with mean $r_{i}$ and $r^{*}$, respectively.
+where $KL(Q_{i}||Q^{*})$ is the Kullback-Leibler divergence between the reward densities $Q_{i}$ and $Q^{*}$, corresponding to arms with mean $r_{i}$ and $r^{*}$, respectively.
 
-\subsection{The Upper Confidence bound approach}
+\subsection{The Upper Confidence Bound approach}
 
     Over the years SMABs have seen several algorithms with strong regret guarantees.
-For further reference an interested reader can look into \citet{bubeck2012regret}.
-The upper confidence bound algorithms balance the exploration-exploitation dilemma by linking the uncertainty in estimate of an arm with the number of times an arm is pulled, and therefore ensuring sufficient exploration.
+For further reference, an interested reader can look into \citet{bubeck2012regret}.
+In the next few subsections, we will explicitly focus on the upper confidence bound algorithms which is a type of non-Bayesian algorithm widely used in SMAB setting.
+The upper confidence bound or UCB algorithms balance the exploration-exploitation dilemma by linking the uncertainty in the estimate of an arm with the number of times an arm is pulled and therefore ensuring sufficient exploration.
 
@@
 
-	One of the earliest among these algorithms is UCB1 algorithm proposed in \citet{auer2002finite}. The algorithm is mentioned
+    One of the earliest among these algorithms is UCB1 algorithm proposed first in \citet{agrawal1995sample} and subsequently analyzed in \citet{auer2002finite}.
+The UCB1 algorithm (as stated in \citet{auer2002finite}) is mentioned in algorithm \ref{alg:ucb1}.
 
-\begin{algorithm}[h!]
+\begin{algorithm}[!th]
 \caption{UCB1}
@@
 
+    The intuition behind this algorithm is simple and it follows from the ideas of concentration inequalities in probability measure theory.
+The term $\sqrt{\dfrac{2\log (t)}{n_i}}$ is called the confidence interval of the arm $i$ and it signifies a measure of uncertainty over the arm $i$ based on the history of observed rewards for that arm.
+Therefore, lesser the confidence interval, higher is our confidence that the estimated mean $\hat{r}_i$ is lying close to the expected mean $r_i$ of the arm $i$.
+Also, note that the confidence interval decreases at the rate of $O\left( \dfrac{1}{\sqrt{n_i}}\right)$ which signifies the rate of convergence of $\hat{r}_i$ to $r_i$ and depends on the number of time the arm has been pulled.
+
     UCB1 has a gap-dependent regret upper bound of  $O\left(\frac{K\log T}{\Delta}\right)$, where $\Delta = \min_{i:\Delta_i>0} \Delta_i$.
@@
 
-\begin{algorithm}[!h]
+\begin{algorithm}[!th]
 \caption{UCB-Improved}
@@
 \State {\bf Input:} Time horizon $T$
-\State {\bf Initialization:} Set $B_{0}:=A$ and $\epsilon_{0}:=1$.
+\State {\bf Initialization:} Set $B_{0}:= \A$ and $\epsilon_{0}:=1$.
 \For{$m=0,1,..\big \lfloor \dfrac{1}{2}\log_{2} \dfrac{T}{e}\big\rfloor$}    
-\State Pull each arm in $B_m$, $n_{m}=\bigg\lceil\dfrac{2\log{( T\epsilon_{m}^{2})}}{\tilde{\Delta}_{m}}\bigg\rceil$ number of times.
+\State Pull each arm in $B_m$, $n_{m}=\bigg\lceil\dfrac{2\log{( T\epsilon_{m}^{2})}}{\epsilon_{m}}\bigg\rceil$ number of times.
 %so that the total  it has been pulled is
@@
 
-	The UCB-Improved algorithm, proposed in \citet{auer2010ucb}, is a round-based variant of UCB1.
+    The UCB-Improved  stated in algorithm \ref{alg:ucbi}, proposed in \citet{auer2010ucb}, is a round-based variant of UCB1.
 An algorithm is \textit{round-based} if it pulls all the arms equal number of times in each round and then eliminates one or more arms that it deems to be sub-optimal.
+Note, that in this algorithm the confidence interval term is $\sqrt{\dfrac{\log{( T\epsilon_{m}^{2})}}{2 n_{m}}}$ which is constant in the $m$-th round as $n_m$ is fixed for that round and all arms are being pulled an equal number of times in each round.
+This is unlike UCB1 algorithm where the confidence interval term depends on $n_i$ which is a random variable.
+Also, note that in UCB-Improved the knowledge of horizon is required before-hand to calculate the confidence intervals whereas no such input is required for UCB1.
+
     UCB-Improved incurs a gap-dependent regret bound of $O\left(\frac{K\log (T\Delta^{2})}{\Delta}\right)$, which is better than that of UCB1.
-On the other hand, the worst case gap-independent regret bound of UCB-Improved is $O\left(\sqrt{KT\log K}\right)$.
+On the other hand, the worst case gap-independent regret bound of UCB-Improved is $O\left(\sqrt{KT\log K}\right)$.Empirically, UCB-Improved is out-performed by UCB1 in almost all environments.
+This stems from the fact that UCB-Improved is pulling all arms equal number of times in each round and hence spends a significant number of pulls in initial exploration as opposed to UCB1 thereby incurring higher regret.
 
@@
 
-\begin{algorithm}[!h]
+\begin{algorithm}[!th]
 \caption{MOSS}
@@
 This is the best known gap-dependent and gap-independent regret bounds in the stochastic MAB framework.
-However, unlike our proposed EUCBV algorithm, OCUCB does not take into account the variance of the arms; as a result, empirically  we find  that our algorithm outperforms OCUCB in all the environments considered.
+However, unlike our proposed EUCBV algorithm (in chapter \ref{chap:EUCBV}), OCUCB does not take into account the variance of the arms; as a result, empirically  we find  that our algorithm outperforms OCUCB in all the environments considered.
 
-\begin{algorithm}[h!]
+\subsubsection{UCB-Variance algorithm}
+
+\begin{algorithm}[!th]
 \caption{UCBV}
@@
     In contrast to the above work, the UCBV \citep{audibert2009exploration} algorithm utilizes variance estimates to compute the confidence intervals for each arm.
+In UCBV the confidence interval term is given by $\sqrt{\dfrac{2\hat{v}_i\log (t)}{s_i}} + \dfrac{3\log (t)}{3}$ where $\hat{v}_i$ denotes the empirical variance of the arm $i$.
+Hence, the confidence interval makes sure that the arms whose variances are high are pulled more often to get a better estimates of their $\hat{r}_i$.
+
     UCBV has a gap-dependent regret bound of $O\left(\frac{K\sigma_{\max}^{2}\log T}{\Delta}\right)$, where $\sigma_{\max}^{2}$ denotes the maximum variance among all the arms $i\in \A$.
@@
 
-\begin{algorithm}[!h]
+\begin{algorithm}[!th]
 \caption{Bernoulli Thompson Sampling}
@@
     Another notable design principle which has recently gained a lot of popularity is the Thompson Sampling (TS) algorithm (\citep{thompson1933likelihood}, \citep{agrawal2011analysis})  and  Bayes-UCB (BU) algorithm \citep{kaufmann2012bayesian}.
-% which employs the Bayesian approach in solving the MAB problem.
-The TS algorithm maintains a posterior reward distribution for each arm; at each round, the algorithm samples values from these distribution and the arm corresponding to the highest sample value is chosen.
-Although TS is found to perform extremely well when the reward distributions are Bernoulli, it is established that with Gaussian priors the worst case regret can be as bad as $\Omega \left( \sqrt{KT\log T}\right)$ \citep{lattimore2015optimally}.
+This TS is stated in algorithm \ref{alg:ts}.
+The TS algorithm maintains a posterior reward distribution for each arm; at each round, the algorithm samples values from these distributions and the arm corresponding to the highest sample value is chosen.
+Although TS is found to perform extremely well when the reward distributions are Bernoulli, it is established that with Gaussian priors the worst-case regret can be as bad as $\Omega \left( \sqrt{KT\log T}\right)$ \citep{lattimore2015optimally}.
 The BU algorithm is an extension of the TS algorithm that takes quartile deviations into consideration while choosing arms.
@@
 
-	The final design principle we state is the information theoretic approach of DMED  \citep{honda2010asymptotically} and KLUCB \citep{garivier2011kl} algorithms.
+    The final design principle we state is the information theoretic approach of DMED  \citep{honda2010asymptotically} and KLUCB \citep{garivier2011kl},\citep{cappe2013kullback} algorithms.
 The algorithm KLUCB uses Kullbeck-Leibler divergence to compute the upper confidence bound for the arms.
@@
 However, \citet{garivier2011kl} showed that KLUCB, MOSS and UCB1 algorithms are empirically outperformed by UCBV in the exponential distribution as they do not take the variance of the arms into consideration.
+
+\subsection{Discussion on the various confidence intervals}

### 2017-11-05 Chapter2/intro.tex
Latest on 5/11/2017

@@
 \begin{algorithm}[!th]
-\caption{SMAB algorithm}
+\caption{SMAB formulation}
 \label{alg:SMAB}
@@
 \State \For{ each timestep $t=1,2,\ldots, T$}
-\State The learner chooses an arm $i\in\A$, where $A$ is the set of arms and $|A|=K$.
-\State The learner observes the reward $X_{i,t}\sim^{i.i.d} D_{i,t}$ where, $D_{i,t}$ is the distribution associated with the arm $i$. 
+\State The learner chooses an arm $i\in\A$, where $\A$ is the set of arms and $|\A|=K$.
+\State The learner observes the reward $X_{i,t}\sim^{i.i.d} D_{i}$ where, $D_{i}$ is the distribution associated with the arm $i$. 
 \State \EndFor
@@
 \end{algorithm}
+
+The rest of the chapter is organized as follows.
+We specify all the notations and assumptions in section~\ref{sec:notations}.
+Then we define the problem statement for the SMAB setting in section~\ref{sec:probDef}.
+In the next section~\ref{sec:motivation} we discuss the motivations behind the SMAB setting.
+In section~\ref{sec:related} we discuss extensively on the various state-of-the-art algorithms available for the SMAB setting.
+Finally, we draw our conclusions in section \ref{chap2:conc}.

### 2017-11-05 Chapter2/related.tex
Latest on 5/11/2017

@@
  \For{$t=K+1,..., T$}
-\State Pull the arm such that $\argmax_{i\in A}\bigg\lbrace\hat{r}_{i} + \sqrt{\dfrac{\max\lbrace 0,\log(\frac{T}{K s_i})\rbrace}{s_i}}\bigg\rbrace$
+\State Pull the arm such that $\argmax_{i\in \A}\bigg\lbrace\hat{r}_{i} + \sqrt{\dfrac{\max\lbrace 0,\log(\frac{T}{K n_i})\rbrace}{n_i}}\bigg\rbrace$
 \State $t:=t+1 $
@@
 \subsection{Discussion on the various confidence intervals}
+
+\begin{table}[!ht]
+\caption{Confidence interval of different algorithms}
+\label{tab:conf-comp}
+\begin{center}
+\begin{tabular}{|p{5em}|p{10em}|p{4em}|p{12em}|}
+\hline
+Algorithm  &  Confidence interval & Horizon as input & Remarks \\
+\hline
+\hline
+UCB1        & $\sqrt{\dfrac{2\log (t)}{n_i}}$ & No & \\%\midrule
+\hline
+\hline
+UCBV        & $\sqrt{\dfrac{2\hat{v}_i\log (t)}{s_i}} + \dfrac{3\log (t)}{3}$ & No & Confidence interval uses variance estimation.\\
+\hline
+\hline
+UCB-Imp 		& $\sqrt{\dfrac{\log{( T\epsilon_{m}^{2})}}{2 n_{m}}}$ & Yes & Same confidence interval for all arms in a particular round.\\%\midrule
+\hline
+\hline
+MOSS	     	& $\sqrt{\dfrac{\max\lbrace 0,\log(\frac{T}{K n_i})\rbrace}{n_i}}$ & Yes & Confidence interval is based on dividing the horizon uniformly for $K$ arms.\\%\midrule
+\hline
+\hline
+OCUCB     	& $\sqrt{\dfrac{2\log(\frac{2T}{t})}{n_i}}$ & Yes & \\\midrule
+\end{tabular}
+\end{center}
+%\vspace*{-2em}
+\end{table}

### 2017-11-05 Chapter3/contribution.tex
Latest on 5/11/2017

@@
 
-	The rest of the chapter is organized as follows.
-In section~\ref{sec:eucbv} we present the  EUCBV algorithm.
-Our main theoretical results are stated in section~\ref{sec:results}, while the proofs are established in   section \ref{sec:proofTheorem}.
-Section~\ref{sec:expt} contains results and discussions from our numerical experiments.
-We draw our conclusions in section \ref{sec:conc} and section \ref{sec:app} is Appendix (supplementary material).
-
 	%discuss about future works.

### 2017-11-05 Chapter3/introduction.tex
Latest on 5/11/2017

--- 2017-10-11 EUCBV/EUCBV.tex
@@
-\def\year{2018}\relax
-%File: formatting-instruction.tex
-\documentclass[letterpaper]{article} %DO NOT CHANGE THIS
-\usepackage{aaai18}  %Required
-\usepackage{times}  %Required
-\usepackage{helvet}  %Required
-\usepackage{courier}  %Required
-\usepackage{url}  %Required
-\usepackage{graphicx}  %Required
-
-\usepackage{macros}
-
-\frenchspacing  %Required
-\setlength{\pdfpagewidth}{8.5in}  %Required
-\setlength{\pdfpageheight}{11in}  %Required
-%PDF Info Is Required:
-  \pdfinfo{
-/Title (2018 Formatting Instructions for Authors Using LaTeX)
-/Author (AAAI Press Staff)}
-\setcounter{secnumdepth}{2}  
- \begin{document}
-% The file aaai.sty is the style file for AAAI Press 
-% proceedings, working notes, and technical reports.
-%
-\title{Efficient-UCBV: An Almost Optimal Algorithm using Variance Estimates}
-\author{Author names withheld}
-
-\maketitle
-
-\begin{abstract}
-We propose a novel variant of the UCB algorithm (referred to as Efficient-UCB-Variance (EUCBV)) for minimizing cumulative regret in the stochastic multi-armed bandit (MAB) setting.
+In this chapter we look at a novel variant of the UCB algorithm (referred to as Efficient-UCB-Variance (EUCBV)) for minimizing cumulative regret in the stochastic multi-armed bandit (SMAB) setting.
 EUCBV incorporates the arm elimination strategy proposed in UCB-Improved \citep{auer2010ucb}, while taking into account the variance estimates to compute the arms' confidence bounds, similar to UCBV \citep{audibert2009exploration}.
@@
 
-%\Keywords{Stochastic multi-armed bandits, cumulative regret, UCB-Improved, UCBV.}
-\end{abstract}
-
-\section{Introduction}
-\label{sec:intro}
-\input{intro}
-
-\subsection{Related Work}
-\label{sec:related}
-\input{related}
-
-\subsection{Our Contributions}
-\label{sec:contri}
-\input{contribution}
-
-\section{Algorithm: Efficient UCB Variance}
-\label{sec:eucbv}
-\input{ealgo}
-
-\section{Main Results} 
-\label{sec:results}
-\input{results}
-
-\section{Proofs}
-\label{sec:proofTheorem}
-\input{proofTheorem}
-
-\section{Experiments}
-\label{sec:expt}
-\input{expts}
-
-\section{Conclusion and Future Works}
-\label{sec:conc}
-\input{Conclusion}
-
-\clearpage
-\newpage
-
-\bibliography{biblio}
-\bibliographystyle{aaai}
-
-\clearpage
-\newpage
-
-\section{Appendix}
-\label{sec:app}
-\input{Appendix}
-
-\end{document}
+	The rest of the chapter is organized as follows.
+We elaborate our contributions in section~\ref{sec:contri} and in section~\ref{sec:eucbv} we present the  EUCBV algorithm.
+Our main theoretical results are stated in section~\ref{sec:results}, while the proofs are established in   section \ref{sec:proofTheorem}.
+Section~\ref{sec:expt} contains results and discussions from our numerical experiments.
+We draw our conclusions in section \ref{sec:conc} and section \ref{sec:app:EUCBV} is Appendix which contains the proofs of the lemmas that have been used for proving the main result.

### 2017-11-05 Chapter2/conclusion.tex
Latest on 6/11/2017

@@
-In this chapter we looked at the stochastic multi-armed bandit (SMAB) setting and discussed how it is important in the general reinforcement learning setup.
+In this chapter, we looked at the stochastic multi-armed bandit (SMAB) setting and discussed how it is important in the general reinforcement learning setup.
 We also looked at the various state-of-the-art algorithms in the literature for the SMAB setting and discussed the advantages and disadvantages of them.
 The regret bounds that have been proven for the said algorithms have also been discussed at length and their confidence intervals have also been compared against each other.
-In the next chapter we provide our solution to this SMAB setting which achieves an almost order-optimal regret bound.
+In the next chapter, we provide our solution to this SMAB setting which achieves an almost order-optimal regret bound.

### 2017-11-05 Chapter2/related.tex
Latest on 6/11/2017

@@
 \begin{algorithmic}[1]
+\State \textbf{Input:} $K$ number of arms with unknown parameters of reward distribution
 \State Pull each arm once
@@
 \begin{algorithmic}[1]
-\State {\bf Input:} Time horizon $T$
+\State {\bf Input:} Time horizon $T$, $K$ number of arms with unknown parameters of reward distribution
 \State {\bf Initialization:} Set $B_{0}:= \A$ and $\epsilon_{0}:=1$.
@@
 \begin{algorithmic}[1]
+\State \textbf{Input:} Time horizon $T$, $K$ number of arms with unknown parameters of reward distribution
 \State Pull each arm once
@@
 \begin{algorithmic}[1]
+\State \textbf{Input:} $K$ number of arms with unknown parameters of reward distribution
 \State Pull each arm once
  \For{$t=K+1,..., T$}
-\State Pull the arm such that $\max_{i\in A}\bigg\lbrace\hat{r}_{i} + \sqrt{\dfrac{2\hat{v}_i\log (t)}{s_i}} + \dfrac{3\log (t)}{3}\bigg\rbrace$
+\State Pull the arm such that $\max_{i\in A}\bigg\lbrace\hat{r}_{i} + \sqrt{\dfrac{2\hat{v}_i\log (t)}{s_i}} + \dfrac{3\log (t)}{2}\bigg\rbrace$
 \State $t:=t+1 $
@@
 \begin{algorithmic}
-\State {\bf Input:} Time horizon $T$; 
+\State {\bf Input:} $K$ number of arms with unknown parameters of reward distribution
 \State {\bf Initialization:} For each arm $i:=1$ to $K$ set $S_i =0$ and $F_i =0$
@@
 
+A comparative analysis of the confidence interval of the UCB algorithms is discussed in table \ref{tab:conf-comp}.
+
 \begin{table}[!ht]
@@
 \hline
-UCB1        & $\sqrt{\dfrac{2\log (t)}{n_i}}$ & No & \\%\midrule
+UCB1        & $\sqrt{\dfrac{2\log (t)}{n_i}}$ & No & Loose confidence interval leading to high regret upper bounds.\\%\midrule
 \hline
 \hline
-UCBV        & $\sqrt{\dfrac{2\hat{v}_i\log (t)}{s_i}} + \dfrac{3\log (t)}{3}$ & No & Confidence interval uses variance estimation.\\
+UCBV        & $\sqrt{\dfrac{2\hat{v}_i\log (t)}{s_i}} + \dfrac{3\log (t)}{2}$ & No & Confidence interval uses variance estimation.\\
 \hline
@@
 \hline
-OCUCB     	& $\sqrt{\dfrac{2\log(\frac{2T}{t})}{n_i}}$ & Yes & \\\midrule
+OCUCB     	& $\sqrt{\dfrac{2\log(\frac{2T}{t})}{n_i}}$ & Yes & Tightest confidence interval leading to order-optimal regret bounds.\\\midrule
 \end{tabular}

### 2017-11-05 Chapter3/Conclusion.tex
Latest on 6/11/2017

--- 2017-10-11 EUCBV/Conclusion.tex
@@
-In this paper, we studied the EUCBV algorithm which takes into account the empirical variance of the arms and  employs aggressive exploration parameters in conjunction with non-uniform arm selection (as opposed to UCB-Improved) to eliminate sub-optimal arms.
+In this chapter, we studied the EUCBV algorithm which takes into account the empirical variance of the arms and employs aggressive exploration parameters in conjunction with non-uniform arm selection (as opposed to UCB-Improved) to eliminate sub-optimal arms.
 Our theoretical analysis conclusively established that EUCBV exhibits an order-optimal gap-independent regret bound of $O\left(\sqrt{KT}\right)$.
@@
 An anytime algorithm does not need the horizon $T$ as an input parameter.
-
-%\section*{Acknowledgement} This work was supported by a funding from IIT Madras under project CSE/14-15/831/ RFTP/BRAV.

### 2017-11-05 Chapter3/introduction.tex
Latest on 6/11/2017

@@
-In this chapter we look at a novel variant of the UCB algorithm (referred to as Efficient-UCB-Variance (EUCBV)) for minimizing cumulative regret in the stochastic multi-armed bandit (SMAB) setting.
-EUCBV incorporates the arm elimination strategy proposed in UCB-Improved \citep{auer2010ucb}, while taking into account the variance estimates to compute the arms' confidence bounds, similar to UCBV \citep{audibert2009exploration}.
-Through a theoretical analysis we establish that EUCBV incurs a \emph{gap-dependent} regret bound of {\scriptsize $O\left( \dfrac{K\sigma^2_{\max} \log (T\Delta^2 /K)}{\Delta}\right)$} after $T$ trials, where $\Delta$ is the minimal gap between optimal and sub-optimal arms; the above bound is an improvement over that of existing state-of-the-art UCB algorithms (such as UCB1, UCB-Improved, UCBV,  MOSS).
-Further, EUCBV incurs a \emph{gap-independent} regret bound of {\scriptsize $O\left(\sqrt{KT}\right)$}  which is an improvement over that of UCB1, UCBV and UCB-Improved, while being comparable with that of MOSS and OCUCB.
-Through an extensive numerical study we show that EUCBV significantly outperforms the popular UCB variants (like MOSS, OCUCB, etc.) as well as Thompson sampling and Bayes-UCB algorithms.
+In this chapter, we look at a novel variant of the UCB algorithm (referred to as Efficient-UCB-Variance (EUCBV)) for minimizing cumulative regret in the stochastic multi-armed bandit (SMAB) setting.
+EUCBV incorporates the arm elimination strategy proposed in UCB-Improved \citep{auer2010ucb} while taking into account the variance estimates to compute the arms' confidence bounds, similar to UCBV \citep{audibert2009exploration}.
+Through a theoretical analysis we establish that EUCBV incurs a \emph{gap-dependent} regret bound of {$O\left( \dfrac{K\sigma^2_{\max} \log (T\Delta^2 /K)}{\Delta}\right)$} after $T$ trials, where $\Delta$ is the minimal gap between optimal and sub-optimal arms; the above bound is an improvement over that of existing state-of-the-art UCB algorithms (such as UCB1, UCB-Improved, UCBV,  MOSS).
+Further, EUCBV incurs a \emph{gap-independent} regret bound of {$O\left(\sqrt{KT}\right)$}  which is an improvement over that of UCB1, UCBV and UCB-Improved, while being comparable with that of MOSS and OCUCB.
+Through an extensive numerical study, we show that EUCBV significantly outperforms the popular UCB variants (like MOSS, OCUCB, etc.) as well as Thompson sampling and Bayes-UCB algorithms.
 
@@
 Section~\ref{sec:expt} contains results and discussions from our numerical experiments.
-We draw our conclusions in section \ref{sec:conc} and section \ref{sec:app:EUCBV} is Appendix which contains the proofs of the lemmas that have been used for proving the main result.
+We draw our conclusions in section \ref{sec:conc} and Appendix \ref{sec:app:EUCBV} contains the proofs of the lemmas that have been used for proving the main result.
+
+%scriptsize

### 2017-11-05 Chapter4/conc.tex
Latest on 6/11/2017

In this chapter, we looked at the pure exploration MAB and thresholding bandit (TBP) setting which is a special case of combinatorial pure exploration MAB. We then looked at the various state-of-the-art algorithms in the literature for the pure-exploration setting and discussed the advantages and disadvantages of them. Then we looked at the latest algorithm for the TBP setting. The expected loss that has been proven for the said algorithms have also been discussed at length and their exploration parameters have also been compared against each other. In the next chapter, we provide our solution to this TBP setting which uses variance estimation to find the set of arms above the threshold.

### 2017-11-05 Chapter4/intro.tex
Latest on 6/11/2017

@@
+In the previous chapters \ref{chap:SMAB} and \ref{chap:EUCBV} we studied the stochastic multi-armed bandit (SMAB) setting with the goal of minimizing cumulative regret.
+In this chapter we will study another setting called Pure-exploration multi-armed bandits.
+An interested reader can read through the previous chapters or can continue from here.
+Though we re-use the ideas from SMABs, the goal of pure exploration setup is distinctly different from that of cumulative regret minimization of SMABs and the required algorithms to understand this setup are mentioned in this chapter itself.
 Pure-exploration MAB problems are unlike their traditional (exploration vs.\ exploitation)  counterparts, the SMABs, where the  objective is to minimize the cumulative regret.
 The cumulative regret is the total loss incurred by the learner for not playing the optimal arm throughout the time horizon $T$.
-The SMABs were extensively discussed in Chapter \ref{chap:SMAB} and \ref{chap:EUCBV}.
-An interested reader can read through the previous chapters or can continue from here.
-Though we re-use the ideas from SMABs, the goal of pure exploration setup is distinctly different from that of cumulative regret minimization of SMABs and the required algorithms to understand this setup and our proposed algorithm are mentioned in this chapter itself.
-
 	In pure-exploration problems a learning algorithm, until time $T$, can invest entirely on exploring the arms without being concerned about the loss incurred while exploring; the objective is to minimize the probability that the arm recommended at time $T$ is not the best arm.
-In this paper, we further consider a combinatorial version of the pure-exploration MAB, called the thresholding bandit problem (TBP).
+In this chapter, we further consider a combinatorial version of the pure-exploration MAB, called the thresholding bandit problem (TBP).
 Here, the learning algorithm is provided with a threshold $\tau$, and the objective, after exploring for $T$ rounds, is to  output all arms $i$ whose $r_{i}$ is above $\tau$.
 It is important to emphasize that the \emph{thresholding} bandit problem is different from the \emph{threshold} bandit setup studied in \cite{abernethy2016threshold}, where the learner receives an unit reward whenever the value of an observation is above a threshold.
+
+	The rest of the chapter is organized as follows.
+We specify all the notations and assumptions in section~\ref{tbandit:notations}.
+Then we define the problem statement for the TBP setting in section~\ref{tbandit:probDef}.
+In the next section~\ref{tbandit:motivation} we discuss the motivations behind the TBP setting.
+In section~\ref{tbandit:prevRes} we discuss extensively on the various state-of-the-art algorithms available for the pure exploration setting and then in section~\ref{tbandit:prevResAPT} we discuss the latest works done in the TBP setting.
+Finally, we draw our conclusions in section \ref{tbandit:conc}.

### 2017-11-05 Chapter5/contribution.tex
Latest on 6/11/2017

--- 2017-10-11 tbandit/contribution.tex
@@
-In this paper we propose the Augmented UCB (AugUCB) algorithm for the fixed-budget setting of a specific combinatorial, pure-exploration, stochastic MAB called the thresholding bandit problem.
+We propose the Augmented UCB (AugUCB) algorithm for the fixed-budget setting of a specific combinatorial, pure-exploration, stochastic MAB called the thresholding bandit problem.
 %In this paper we propose AugUCB algorithm for the fixed-budget, comp thresholding bandit problem.

### 2017-11-05 Chapter5/intro.tex
Latest on 6/11/2017

--- 2017-10-11 tbandit/ijcai17.tex
@@
-%%%% ijcai17.tex
-
-\typeout{IJCAI-17 Instructions for Authors}
-
-% These are the instructions for authors for IJCAI-17.
-% They are the same as the ones for IJCAI-11 with superficical wording
-%   changes only.
-
-\documentclass{article}
-% The file ijcai17.sty is the style file for IJCAI-17 (same as ijcai07.sty).
-\usepackage{ijcai17}
-
-% Use the postscript times font!
-\usepackage{times}
-
-\usepackage{macros}
-
-\usepackage{latexsym}
-
-\title{Thresholding Bandits with Augmented UCB}
-%\author{Author names withheld}
-
-\author{Subhojyoti Mukherjee${}^1$, K. P. Naveen${}^2$, Nandan
-Sudarsanam${}^3$, Balaraman Ravindran${}^1$\\
-${}^1$Department of Computer Science \& Engineering,\\ ${}^2$Department of Electrical Engineering,
-${}^3$Department of Management Studies,\\ Indian Institute of
-Technology Madras}
-
-\begin{document}
-\maketitle
-
-\vspace*{2mm}
-\begin{abstract}
-In this paper we propose the Augmented-UCB (AugUCB) algorithm for a fixed-budget version of the thresholding bandit problem (TBP), where the objective is to identify a set of arms whose quality is above a threshold.
+In this chapter we look at the Augmented-UCB (AugUCB) algorithm for a fixed-budget version of the thresholding bandit problem (TBP), where the objective is to identify a set of arms whose expected mean is above a threshold.
 A key feature of AugUCB is that it uses both mean and variance estimates to eliminate arms that have been sufficiently explored; to the best of our knowledge this is the first algorithm to employ such an approach for the considered TBP.
@@
 Through our simulation work, we establish that AugUCB, owing to its utilization of variance estimates, performs significantly better than the state-of-the-art APT, CSAR and other non variance-based algorithms.
-\end{abstract}
-
-%\begin{keywords}
-%Multi-Armed Bandit, Regret, Exploration-exploitation, UCB
-%\end{keywords}
-
-\section{Introduction}
-\label{intro}
-\input{intro}
-%\subsection{Motivation}
-%\label{motivation}
-\input{motivation}
-\subsection{Related Work}
-\label{prevRes}
-\input{prevRes}
-
-\subsection{Our Contribution}
-\label{contribution}
-\input{contribution}
-%
-%\section{Notation Used and Assumptions}
-%\label{notation}
-%\input{notation}
-%
-%
-\vspace*{-1em}
-\section{Augmented-UCB Algorithm}
-\label{algorithm}
-\input{algo}
-%
-\vspace{-2mm}
-\section{Theoretical Results}
-\label{results}
-\input{results}
-%
-%
-%\vspace{-1em}
-\vspace{-5mm}
-\section{Numerical Experiments}
-\label{expt}
-\input{expt}
-%
-%\vspace{-1.2em}
-\vspace{-1mm}
-\section{Conclusion}
-\label{conclusion}
-\input{conclusion}
-
-% Acknowledgments---Will not appear in anonymized version
-%\acks{We thank a bunch of people.}
-
-%\clearpage
-%\newpage
-%\bibliographystyle{named}
-%\bibliography{ijcai17}
-
-%\clearpage
-%\newpage
-%\section{Appendix}
-%\label{appendix}
-%\input{appendix}
-
-\end{document}

### 2017-11-24 Chapter1/feedback.tex
Latest on 24/11/2017

@@
 	To illustrate the different types of feedback we will take help of the following example.
-Let a learner be given a set of actions $i\in\A$ such that $|A|=K$.
+Let a learner be given a set of finite actions $i\in\A$ such that $|\A|=K$.
 Let, the environment be such that each action has a probability distribution $D_i$ attached to it which is fixed throughout the time horizon $T$.
-The learning proceeds as follows:-
+The learning proceeds as follows, at every timestep the learner selects $m\in\A$ actions and observes some form of feedback vector $R^{obs}_{t}$ (which will be characterized later).
+Before the learner selects the  the set of arms the environment draws the feedback vector $F^{env}_t\in[0,1]^{K}$ of $K$ i.i.d random rewards for all actions $i\in\A$ from $D_i,\forall i\in\A$ which it decides to reveal in particular format depending on the form of feedback chosen for the game, that is full information, partial information or bandit feedback.
+This game is shown in algorithm \ref{alg:OSeqGame}.
 
@@
 \State \For{ each timestep $t=1,2,\ldots, T$}
-\State The environment chooses a reward $r_{i,t},\forall i\in\A$.
-\State The learner chooses $m$ actions such that $m < K$, where $A$ is the set of arms and $|A|=K$.
-\State The learner observes the reward $R_{m,t}=F\left( r_{i,t}\right)$.
+\State The environment chooses a reward vector $F^{env}_{t}= \left[r_{i,t}\sim^{i.i.d} D_{i},\forall i\in\A\right]$.
+\State The learner chooses $m$ actions such that $m < K$, where $\A$ is the set of arms and $|\A|=K$.
+\State The learner observes the reward vector $R^{obs}_{t}\subseteq F^{env}_{t}$.
 \State \EndFor
@@
 In full information feedback, when a learner selects $m$ actions then the environment reveals the rewards of all the actions $i\in \A$.
-Hence, in this form of feedback  the learner observes $R_{m,t} = \lbrace r_{i,t},\forall i\in\A\rbrace$.
+Hence, in this form of feedback  the learner observes $R^{obs}_{t} = F^{env}_{t}=[r_{i,t},\forall i\in\A]$.
+This has been studied in many forms previously in \citet{takimoto2003path}, \citet{kalai2005efficient} or in online prediction with full information feedback in \citet{cesa2006prediction}.
 
@@
 In partial information feedback, when a learner selects $m$ actions then the environment reveals the rewards of only those $m$ actions for $m\in \A$.
-Hence, in this form of feedback  the learner observes $R_{m,t} = \lbrace r_{m,t},\forall m\in\A\rbrace$.
-This is also sometimes called the semi-bandit feedback.
+Hence, in this form of feedback  the learner observes $R^{obs}_{t} = [ r_{m,t},\forall m\in\A ]$.
+This is also sometimes called the semi-bandit feedback and has been studied in \citet{awerbuch2004adaptive},   \citet{mcmahan2004online} and \citet{gyorgy2007line}.
 
@@
 In bandit feedback, when a learner selects $m$ actions then the environment reveals a cumulative reward of those $m$ actions for $m\in \A$.
-Hence, in this form of feedback  the learner observes $R_{m,t} = \sum_{q=1}^{m} r_{q,t}$.
+Hence, in this form of feedback  the learner observes $R^{obs}_{t} = \sum_{q=1}^{m} r_{q,t}$.
 Note, that when $m=1$, then the learner observes the reward of only that action that it has chosen out of $K$ actions.
+Bandit feedback for single action has been extensively studied in literature with many open problems and we focus on its various interpretations in this thesis.

### 2017-11-24 Chapter1/motivation.tex
Latest on 5/11/2017
Latest on 24/11/2017

@@
 \begin{enumerate}
-\item \emph{Online Shop Domain (\cite{ghavamzadeh2015bayesian}):} In the online shop domain, a retailer aims to maximize profit by sequentially suggesting products to online shopping customers.
+\item \emph{Online Shop Domain:} In the online shop domain \cite{ghavamzadeh2015bayesian}, a retailer aims to maximize profit by sequentially suggesting products to online shopping customers.
 In this scenario, at every timestep, the retailer displays an item to a customer from a pool of items which has the highest probability of being selected by the customer.
-The episode ends when the customer selects or does not select a product (which will be considered as a loss to the retailer) and the process is again repeated till a pre-specified number of times with the retailer gathering valuable information regarding the customer from this behaviour and modifying its policy to display the next item.
-\item \emph{Medical Treatment Design (\cite{thompson1933likelihood}):} Here at every timestep, the agent chooses to administer one out of several treatments sequentially on a patient.
-Here, the episode ends when the patient responds well or does not respond well to the treatment whereby the agent modifies its policy for the next suggestion.
-\item \emph{Financial Portfolio Management:} In financial portfolio management MAB model can be used.
-Here, the agent is faced with the choice of selecting the most profitable stock option out of several stock options.
-The simplest strategy where we can employ a bandit model is this; at the start of every trading session the agent suggests a stock to purchase worth Re $1$, while at the closing of the trading session it sells off the stock to witness its value after a day's trading.
-The  profit recorded is treated as the reward revealed by the environment and the agent modifies its policy for the next day.
-%\item \emph{Product Selection:} A company wants to introduce a new product in market and there is a clear separation of the test phase from the commercialization phase.
+The episode ends when the customer selects or does not select a product (which will be considered as a loss to the retailer).
+This feedback is incorporated by the learner as a feedback from the environment and it modifies its policy for the next suggestion.
+This process is repeated till a pre-specified number of times with the retailer gathering valuable information regarding the customer from this behaviour and modifying its policy to display other items to different customers.
+\item \emph{Medical Treatment Design:} Another interesting domain that MAB model was first studied was for the medical treatment design \cite{thompson1933likelihood},\cite{thompson1935theory}.
+Here at every timestep, the learner chooses to administer one out of several treatments sequentially on a stream of patients who are suffering from the same ailment (say).
+Let's also assume that there is a single treatment which will be able to alleviate the patients from their disease.
+Here, the episode ends when the patient responds well or does not respond well to the treatment whereby the learner modifies its policy for the suggestion to the next patient.
+The goal of the learner is to quickly converge on the best treatment so that whenever a new patient comes with the same ailment, the learner can suggest the best treatment which can relive the patient of its ailment with a high probability.
+\item \emph{Financial Portfolio Management:} In financial portfolio management MAB models can also be used.
+Here, the learner is faced with the choice of selecting the most profitable stock option out of several stock options.
+The simplest strategy where we can employ a bandit model is this; at the start of every trading session the learner suggests a stock to purchase worth Re $1$, while at the closing of the trading session it sells off the stock to witness its value after a day's trading.
+The  profit recorded is treated as the reward revealed by the environment and the learner modifies its policy for the next day.
+Let's assume that no new stock options are being introduced over the considered time horizon and there is a single best stock option which if selected for perpetuity will always give the best returns.
+Then, the goal of the learner is reduced to identifying the best stock option as quickly as possible.
+\item \emph{Product Selection:} A company wants to introduce a new product in market and there is a clear separation of the test phase from the commercialization phase.
 In this case the company tries to minimize the loss it might incur in the commercialization phase by testing as much as possible in the test phase.
-So from the several variants of the product that are in the test phase the learning agent must suggest a product variant at the end of the test phase that has the highest probability of minimizing loss in the commercialization phase(see \cite{bubeck2011pure}).
-%\item \emph{Mobile Phone Channel Allocation:} Another similar problem as above concerns channel allocation for mobile phone communications (\cite{audibert2009exploration}).
-Here there is a clear separation between the allocation phase and communication phase whereby in the allocation phase a learning algorithm has to explore as many channels as possible to suggest the best possible channel.
-Each evaluation of a channel is noisy and the learning algorithm must come up with the best possible suggestion within a very small  number of attempts.
+So from the several variants of the product that are in the test phase the learning learner must suggest the product variant(s) whose qualities are above a particular threshold $\tau$ at the end of the test phase that have the highest probability of minimizing loss in the commercialization phase.
+A similar problem has been discussed for single best product variant identification without threshold in \citet{bubeck2011pure}.
+\item \emph{Mobile Phone Channel Allocation:} Another similar problem as above concerns channel allocation for mobile phone communications \citep{audibert2009exploration}.
+Here there is a clear separation between the allocation phase and communication phase whereby in the allocation phase a learner has to explore as many channels as possible to suggest the best possible set of channel(s) whose qualities are above a particular threshold $\tau$.
+The threshold may depend on the subscription level of the customer such that with higher subscription the customer is allowed better channel(s) with the $\tau$ set high.
+Each evaluation of a channel is noisy and the learning algorithm must come up with the best possible set of suggestions within a very small  number of attempts.
+\item \emph{Anomaly Detection and Classification:} MABs can also be used for anomaly detection where the goal is to seek out extreme values in the data.
+Anomalies may not always be naturally concentrated which was shown in  \citet{steinwart2005classification}.
+To implement a MAB model the best possible way is to define a cut-off level $\tau$ and classify the samples above this level $\tau$ as anomalous along with a tolerance factor which gives it a degree of flexibility.
+Such an approach has already been mentioned in \citet{streeter2006selecting} and further studied in \citet{locatelli2016optimal}.
 \end{enumerate}
 
-	The thresholding bandit problem is a special case of combinatorial MAB problem where the learner has to suggest the best set of arms above a real valued threshold.
-This has several relevant industrial applications.
-The variants of TopM problem (identifying the best $M$ arms from $K$ given arms) can be readily used in the thresholding problem.
-
-\begin{enumerate}
-\item \emph{Product Selection:} A company wants to introduce a new product in market and there is a clear separation of the test phase from the commercialization phase.
-In this case the company tries to minimize the loss it might incur in the commercialization phase by testing as much as possible in the test phase.
-So from the several variants of the product that are in the test phase the learning agent must suggest the product variant(s) that are above a particular threshold $\tau$ at the end of the test phase that have the highest probability of minimizing loss in the commercialization phase.
-A similar problem has been discussed for single best product variant identification without threshold in \cite{bubeck2011pure}.
-\item \emph{Mobile Phone Channel Allocation:} Another similar problem as above concerns channel allocation for mobile phone communications (\cite{audibert2009exploration}).
-Here there is a clear separation between the allocation phase and communication phase whereby in the allocation phase a learning algorithm has to explore as many channels as possible to suggest the best possible set of channel(s) that are above a particular threshold $\tau$.
-The threshold depends on the subscription level of the customer.
-With higher subscription the customer is allowed better channel(s) with the $\tau$ set high.
-Each evaluation of a channel is noisy and the learning algorithm must come up with the best possible suggestion within a very small  number of attempts.
-\item \emph{Anomaly Detection and Classification:} Thresholding bandit can also be used for anomaly detection and classification where we define a cutoff level $\tau$ and for any samples above this cutoff gets classified as an anomaly.
-For further reading we point the reader to section 3 of \cite{locatelli2016optimal}.
-\end{enumerate}
-
-	In all the above examples the MAB model performs well mainly because all of them suffer from \textit{exploration-exploitation dilemma}.
-This is characterized by action-selection choice faced by the agent where it must decide whether to stay with the action yielding highest reward till now or to explore newer actions which might be more profitable in the long run.
+%	In all the above examples the MAB model performs well mainly because all of them suffer from \textit{exploration-exploitation dilemma}.
+This is characterized by action-selection choice faced by the learner where it must decide whether to stay with the action yielding highest reward till now or to explore newer actions which might be more profitable in the long run.
 MAB's are suited for such scenarios because
-\begin{enumerate}
-\item They are easy to implement.
-\item The switch between exploration and exploitation is more well defined theoretically.
-\item They perform well empirically.
-\end{enumerate}
+%\begin{enumerate}
+%\item They are easy to implement.
+%\item The switch between exploration and exploitation is more well defined theoretically.
+%\item They perform well empirically.
+%\end{enumerate}

### 2017-11-24 Chapter1/outline.tex
Latest on 24/11/2017

In the previous sections, we gave an overview of the various type of bandits available in the literature. In this section, we give a general outline of the thesis that is to follow. In chapter \ref{chap:SMAB} we give a detailed overview of the stochastic multi-armed bandit model and the latest available algorithms in this setting. In the next chapter \ref{chap:EUCBV} we introduce our algorithm Efficient UCB Variance (EUCBV) for the stochastic multi-armed bandit model. We give theoretical guarantees on the performance of EUCBV and also show in numerical simulations that it indeed performs very well as compared to the state-of-the-art algorithms. In the subsequent chapter \ref{chap:tbandit1} we introduce a new variant of pure exploration multi-armed stochastic bandit called the thresholding bandit problem. We analyze the connections between thresholding bandit problem and pure exploration problem and also discuss several existing algorithms in both the settings that are relevant to carefully analyze the thresholding bandit problem. Then in chapter \ref{chap:tbandit2} we introduce our solution for the thresholding bandit problem, called the Augemented UCB (AugUCB) algorithm. We analyze our algorithm AugUCB and derive theoretical guarantees for it as well as show in numerical experiments that it indeed outperforms several state-of-the-art algorithms in the thresholding bandit setting. Finally, in chapter \ref{chap:psbandit} we introduce the piecewise-stochastic bandit model which is a new variant that strides between the stochastic and adversarial setting. We discuss extensively on this setting and also provide our solution to this setting and show in numerical simulations that our solution is very close to the optimal solution.

### 2017-11-24 Chapter1/types.tex
Latest on 24/11/2017

@@
 In each of these cases a different guarantee on the performance of the learner can be arrived at.
-Some of the important papers in this setting are \citet{auer2002nonstochastic}, \citet{auer2002nonstochastic}, \citet{auer2002using}, \citet{kocak2014efficient}.
+Some of the important papers in this setting are \citet{auer2002nonstochastic}, \citet{auer2002using}, \citet{kocak2014efficient}.
 
@@
 The distribution associated with each arm then  remains fixed till the next chnagepoint is encountered.
-Chapter (to be added) is based on this.
+Several recent works have focussed on this such as  \citep{garivier2011upper}, \citep{mellor2013thompson}, and \citep{allesiardo2017non}.
+In our thesis, chapter \ref{chap:psbandit} is based on this setting.
 \end{itemize}
@@
 
+In bandit literature, based on the goal we can divide bandits into several categories.
+To illustrate his we put forward a simple scenario let us consider a stochastic bandit scenario where there are $K$ arms labeled $i=1,2,\ldots,K$ with their expected means of reward distributions ($D_i$) be denoted by $r_i$.
+Also let there be single optimal arm $*$ such that $r^* = \max_{i\in\A}r_i$.
+
 \subsubsection{Cumulative regret minimization}
+In cumulative regret minimization the goal of the bandit is to minimize the cumulative regret which is the total loss suffered by the learner throughout the time horizon $T$ for not choosing the optimal arm.
+Formally, we can define the cumulative regret as,
+
+\begin{eqnarray}
+R_{T} = \sum_{t=1}^{T}r^* - \sum_{i\neq *}r_{i}n_{i,T} \label{eqn:chap1:regret}
+\end{eqnarray}
+
+where, $n_{i,T}$ is the number of times the learner has chosen arm $i$ over the entire horizon $T$. We can further reduce equation \ref{eqn:chap1:regret} to obtain,
+
+\begin{align*}
+R_{T} = \sum_{t=1}^{T}r^* - \sum_{i\neq *}r_{i}n_{i,T} = \sum_{i=1}^{K}\Delta_{i}n_{i,T}
+\end{align*}
+
+where $\Delta_{i}=r^* - r_i$ is called the gap between the optimal and the sub-optimal arm.
 
 \subsubsection{Simple regret minimization}
+In simple regret minimization the goal of the bandit is to minimize the instantaneous regret that is suffered at any  timestep by the learner.
+Formally, the simple regret at $t$-th timestep where $J_n\in\A$ is the recommendation by the learner at timestep $t$ is defined,
 
-\subsubsection{External Regret minimization}
+\begin{align*}
+SR_{t} = r^* - r_{J_{n}} = \Delta_{J_n}
+\end{align*}
+
+where, $\Delta_{J_n}$ is the instantaneous gap between the expected mean of he optimal arm and the recommended arm by the learner.
+
+\subsubsection{Weak Regret minimization}
+In the non-stochastic scenario, when the distribution associated with each arm changes, the notion of regret is defined differently than cumulative regret.
+In this scenario, considering that there is a single best arm, the learner is more interested in minimizing the worst-case regret.
+Formally, for any sequence of actions $\left( j_1, \ldots , j_T \right)$ over the time horizon $T$, the weak regret for single best action is defined as the difference between,
+\begin{align*}
+G_{\max}(j_1,\ldots,j_T) - G_{\pi}(T)
+\end{align*}
+where, $G_{\max}(j_1,\ldots,j_T) = \max_{i\in\A}\sum_{t=1}^{T}x_{i_t}$ is the return of the globally best action over the entire horizon $T$ and $G_{\pi}(T)$ is the return following the policy $\pi$ over the horizon $T$ instead of choosing $j_1,\ldots,j_T$.
 
@@
 The clustering in this case is typically done over the feature space \citet{bui2012clustered}, \citet{cesa2013gang}, \citet{gentile2014online}.
+
+\subsection{Bandits with Corrupt Feedback}
+
+\subsection{Conservative Bandits}

### 2017-11-24 Chapter4/prevRes.tex
Latest on 24/11/2017

@@
 
-Here the learning algorithm has to suggest the best arm(s) within a fixed time-horizon $T$, that is usually given as an input.
+Here the learning algorithm has to suggest the best arm(s) within a fixed budget or time-horizon $T$, that is given as an input.
 The objective is to maximize the probability of returning the best arm(s).
@@
 
-\begin{algorithm}[!h]
+One of the first algorithms proposed for the fixed budget setting is the UCB-Exploration (UCBE) algorithm in \citet{audibert2010best} used for identifying a single best arm.
+This is shown in algorithm \ref{alg:ucbe}.
+
+\begin{algorithm}[!ht]
 \caption{UCBE}
@@
 \begin{algorithmic}[1]
-\State \textbf{Input: } The budget $T$
+\State \textbf{Input: } The budget $T$, exploration parameter $a$
 \State Pull each arm once
@@
 
-In \citet{audibert2010best} the authors propose the  UCBE and the Successive Reject (SR) algorithm, and prove simple-regret guarantees for the problem of identifying the single best arm.
-In the combinatorial fixed budget setup \citet{gabillon2011multi} propose the GapE and GapE-V algorithms that suggest, with high probability, the best $m$ arms at the end of the time budget.
+This algorithm is quite similar to the UCB1 algorithm discussed in \citet{auer2002finite} (see algorithm \ref{alg:ucb1}).
+The major difference between the two algorithms is the confidence interval such that for UCB1 it is designed for minimizing the cumulative regret but for UCBE it is designed for minimizing simple regret.
+An illustrative table comparing the two is provided in table \ref{table:comp-exp}.
+
+\begin{table}
+\caption{Confidence interval and exploration parameters of different algorithms}
+\label{table:comp-exp}
+\begin{center}
+\begin{tabular}{|p{5em}|p{6em}|p{8em}|p{12em}|}
+\hline
+Algorithm  &  Confidence interval & Exploration Parameter$(a)$ & Remarks \\
+\hline
+\hline
+UCB1       & $\sqrt{\dfrac{a}{n_i}}$ & \begin{align*}a = 2\log (t)\end{align*} & $a$ is logarithmic in $t$ to minimize cumulative regret.
+This achieves a balance between exploration and exploitation.
+Hence, the cumulative regret grows logarithmically with $t$.
+\\%\midrule
+\hline
+\hline
+UCBE       & $\sqrt{\dfrac{a}{n_i}}$ & \begin{align*}a = \dfrac{25(T-K)}{36 H_1},\\ \text{ where }H_1 = \sum_{i=1}^{K}\dfrac{1}{\Delta_i^2}\end{align*} & $a$ is linear in $T$ to minimize simple regret.
+Here, the main concern is to minimize the probability of error at the end of budget $T$ and conduct as much exploration as possible.
+Hence, a large $a$ helps to reach exponentially low probability of error.\\\midrule
+\end{tabular}
+\end{center}
+\end{table}
 
@@
 
-\begin{algorithm}[h!]
+The Successive Reject (SR) algorithm has also been proposed in \citet{audibert2010best} and is used for identifying a single best arm.
+This algorithm is quite different than upper confidence bound based algorithms because it does not rely on any explicit confidence interval to select arm at every timestep.
+It is shown in algorithm \ref{alg:sr}.
+
+\begin{algorithm}[!th]
 \caption{Successive Reject(SR)}
@@
 \For{For each phase $m=1,..., K-1$}
-\State For each $i \in B_{m}$, select arm $i$ for $n_k - n_{k-1}$ rounds.
+\State For each $i \in B_{m}$, select arm $i$ for $n_k - n_{k-1}$ timesteps.
 \State Let $B_{m+1} = B_m\setminus \argmin_{i\in B_m} \hat{r}_i$
@@
 \end{algorithm}
+
+From algorithm \ref{alg:sr} we see that SR is a round based algorithm quite similar to UCB-Improved (see algorithm \ref{alg:ucbi}).
+Similar to UCB-Improved, SR pulls all arms equal number of times in each round and then discards some arm that it deems to be sub-optimal until it is left with a single best arm.
+However, SR does not have any explicit confidence interval as UCBE, rather the idea of the confidence interval is hidden in the number of pulls allocated to each arm in every round.
+The number of times each arm is pulled in every round, that is $n_k - n_{k-1}$ timesteps makes sure that the optimal arm is not eliminated in the $k$-th round with high probability.
+
+In the combinatorial fixed budget setup \citet{gabillon2011multi} propose the GapE and GapE-V algorithms that suggest, with high probability, the best $m$ arms at the end of the time budget.
 

### 2017-11-24 Chapter5/expt.tex
Latest on 5/11/2017
Latest on 24/11/2017

@@
 
-$\bullet$ AugUCB: This is the Augmented-UCB algorithm proposed in this paper; as in Theorem \ref{Result:Theorem:1} we set $\rho=\frac{1}{3}$.
+$\bullet$ AugUCB: This is the Augmented-UCB algorithm proposed in this paper; as in Theorem \ref{tbandit:Result:Theorem:1} we set $\rho=\frac{1}{3}$.
 
@@
 		}
-        \begin{tikzpicture}[scale=0.6]
+        \begin{tikzpicture}[scale=0.7]
       	\begin{axis}[
@@
 		}
-        \begin{tikzpicture}[scale=0.6]
+        \begin{tikzpicture}[scale=0.7]
         \begin{axis}[
@@
     \end{tabular}
+\caption{Performances of the various TBP algorithms in terms of error percentage vs. time-step.}
+    \label{fig:budgetExpt1}
+\end{figure}
 
+\begin{figure}[th!]
+    \centering
 	\begin{tabular}{cc}
@@
     \end{tabular}
+    \caption{Performances of the various TBP algorithms in terms of error percentage vs. time-step.}
+    \label{fig:budgetExpt2}
+\end{figure}
 
+\begin{figure}[th!]
+    \centering
 	\begin{tabular}{cc}
@@
     \end{tabular}
-    \caption{Performances of the various TBP algorithms in terms of error percentage vs. time-step, for  six different experimental scenarios.}
-    \label{fig:budgetExpt}
-    \vspace{-6mm}
+    \caption{Performances of the various TBP algorithms in terms of error percentage vs. time-step.}
+    \label{fig:budgetExpt3}
 \end{figure}

### 2017-11-24 Chapter6/expt.tex
Latest on 24/11/2017

In this section we present two experiments in two different environments.

\begin{figure}[!th]
    \centering
    \begin{tabular}{cc}
    %\setlength{\tabcolsep}{0.1pt}
    \subfigure[\Large\textwidth][\large Expt-$1$: $3$ Bernoulli-distributed arms (From Dr. Odalric's Draft).]
    %with $r_{i_{{i}\neq {*}}}=0.07$ and $r^{*}=0.1$
    {
    		\pgfplotsset{
		tick label style={font=\normalsize},
		label style={font=\normalsize},
		legend style={font=\normalsize},
		ylabel style={yshift=12pt},
		%legend style={legendshift=32pt},
		}
        \begin{tikzpicture}[scale=0.7]
      	\begin{axis}[
		xlabel={timestep},
		ylabel={Cumulative Regret},
		grid=major,
        %clip mode=individual,grid,grid style={gray!30},
        clip=true,
        %clip mode=individual,grid,grid style={gray!30},
  		legend style={at={(0.5,1.4)},anchor=north, legend columns=3} ]
      	% UCB

		\addplot table{Chapter6/results/NewExpt/Expt5/comp_subsampled_DUCB01.txt};
		\addplot table{Chapter6/results/NewExpt/Expt5/comp_subsampled_ETS01.txt};
		\addplot table{Chapter6/results/NewExpt/Expt5/comp_subsampled_ETS02.txt};
		\addplot table{Chapter6/results/NewExpt/Expt5/comp_subsampled_ETS03.txt};
		\addplot table{Chapter6/results/NewExpt/Expt5/comp_subsampled_ETS1E01.txt};
		\addplot table{Chapter6/results/NewExpt/Expt5/comp_subsampled_ETS1E02.txt};
		\addplot table{Chapter6/results/NewExpt/Expt5/comp_subsampled_TS01.txt};
		\addplot table{Chapter6/results/NewExpt/Expt5/comp_subsampled_OTS01.txt};
		\addplot table{Chapter6/results/NewExpt/Expt5/comp_subsampled_DTS01.txt};

      	\legend{DUCB($\gamma=1-\frac{1}{4\sqrt{T}}$),ETSDAE1,ETSDAE2,ETSDAE3,ETSD1E1,ETSD1E2,TS,OTS,DTS($\gamma=1-\frac{1}{4\sqrt{T}})$}    
      	\end{axis}
      	\end{tikzpicture}
  		\label{psbandit:fig:1}
    }
    &
    \subfigure[\Large\textwidth][\large Expt-$1$: $3$ Bernoulli-distributed arms (From Dr. Odalric's Draft).]
    %with $r_{i_{{i}\neq {*}}}=0.07$ and $r^{*}=0.1$
    {
    		\pgfplotsset{
		tick label style={font=\normalsize},
		label style={font=\normalsize},
		legend style={font=\normalsize},
		ylabel style={yshift=12pt},
		%legend style={legendshift=32pt},
		}
        \begin{tikzpicture}[scale=0.7]
      	\begin{axis}[
		xlabel={timestep},
		ylabel={Cumulative Regret},
		grid=major,
        %clip mode=individual,grid,grid style={gray!30},
        clip=true,
        %clip mode=individual,grid,grid style={gray!30},
  		legend style={at={(0.5,1.4)},anchor=north, legend columns=3} ]
      	% UCB

		\addplot table{Chapter6/results/NewExpt/Expt5/comp_subsampled_DUCB01.txt};
		\addplot table{Chapter6/results/NewExpt/Expt5/comp_subsampled_ETS04.txt};
		\addplot table{Chapter6/results/NewExpt/Expt5/comp_subsampled_ETS1E03.txt};
		\addplot table{Chapter6/results/NewExpt/Expt5/comp_subsampled_ETS06.txt};
		\addplot table{Chapter6/results/NewExpt/Expt5/comp_subsampled_ETS1E04.txt};
		\addplot table{Chapter6/results/NewExpt/Expt5/comp_subsampled_TS01.txt};
		\addplot table{Chapter6/results/NewExpt/Expt5/comp_subsampled_OTS01.txt};
		\addplot table{Chapter6/results/NewExpt/Expt5/comp_subsampled_DTS01.txt};
		\addplot table{Chapter6/results/NewExpt/Expt5/comp_subsampled_ETS1E06.txt};

      	\legend{DUCB($\gamma=1-\frac{1}{4\sqrt{T}}$),EAggrCPD1,CPD1-E1,EAggrCPD2,CPD2-E1,TS,OTS,DTS($\gamma=1-\frac{1}{4\sqrt{T}})$,CPD2-E1-N}    
      	\end{axis}
      	\end{tikzpicture}
  		\label{psbandit:fig:2}
    }
    \end{tabular}
    \caption{Cumulative regret for various bandit algorithms on a piecewise stochastic 3-armed bandit environment. }
    \label{fig:karmed1}
\end{figure}

%\begin{figure}[!th]
%    \centering
%    \begin{tabular}{c}
%    %\setlength{\tabcolsep}{0.1pt}
%    \subfigure[\Large\textwidth][\large Expt-$1$: $3$ Bernoulli-distributed arms (From Dr. Odalric's Draft).]
%    %with $r_{i_{{i}\neq {*}}}=0.07$ and $r^{*}=0.1$
%    {
%    		\pgfplotsset{
%		tick label style={font=\normalsize},
%		label style={font=\normalsize},
%		legend style={font=\normalsize},
%		ylabel style={yshift=12pt},
%		%legend style={legendshift=32pt},
%		}
%        \begin{tikzpicture}[scale=0.7]
%      	\begin{axis}[
%		xlabel={timestep},
%		ylabel={Cumulative Regret},
%		grid=major,
%        %clip mode=individual,grid,grid style={gray!30},
%        clip=true,
%        %clip mode=individual,grid,grid style={gray!30},
%  		legend style={at={(0.5,1.4)},anchor=north, legend columns=3} ]
%      	% UCB
%		
%		\addplot table{results/NewExpt/Expt5/comp_subsampled_DUCB01.txt};
%		\addplot table{results/NewExpt/Expt5/comp_subsampled_ETS04.txt};
%		\addplot table{results/NewExpt/Expt5/comp_subsampled_ETS1E03.txt};
%		\addplot table{results/NewExpt/Expt5/comp_subsampled_TS01.txt};
%		\addplot table{results/NewExpt/Expt5/comp_subsampled_OTS01.txt};
%		\addplot table{results/NewExpt/Expt5/comp_subsampled_DTS01.txt};
%      	
%      	\legend{DUCB($\gamma=1-\frac{1}{4\sqrt{T}}$),ETSDAE4,ETSD1E3,TS,OTS,DTS($\gamma=1-\frac{1}{4\sqrt{T}})$}    
%      	\end{axis}
%      	\end{tikzpicture}
%  		\label{fig:2}
%    }
%    \end{tabular}
%    \caption{Cumulative regret for various bandit algorithms on a piecewise stochastic 3-armed bandit environment. }
%    \label{fig:karmed2}
%\end{figure}

### 2017-11-24 Chapter6/intro.tex
Latest on 24/11/2017

In this paper, we consider the piece-wise stochastic multi-armed bandit problem, an interesting variation of the stochastic multi-armed bandit problem in sequential decision making. In this setting,  a learning algorithm is provided with a set of decisions (or arms) with reward distributions unknown to the learner. The learning proceeds in an iterative fashion, where in each round, the algorithm chooses an arm and receives a stochastic reward that is drawn from a distribution specific to the arm selected. There exist a finite number of changepoints such that the reward distribution of arms changes at those changepoints. Given the goal of maximizing the cumulative reward, the learner faces the \textit{exploration-exploitation-changepoint} dilemma, i.e., in each round should the algorithm select the arm which has the highest observed reward so far (\textit{exploitation}), or should the algorithm choose a new arm to gain more knowledge of the expected reward of the arms and thereby avert a sub-optimal greedy decision (\textit{exploration}) and finally keep track of the \textit{changepoints}.

### 2017-11-24 Chapter6/notations.tex
Latest on 24/11/2017

In this paper, $T$ denotes the time horizon. $\A$ denotes the set of arms with individual arm is denoted by $i$ such that $i=1,\ldots, K$. We assume that the total number of arms is constant throughout the time horizon and $|\A|=K$. In this setting each arm has a piece-wise stationary distribution associated with it. Let $c_0,c_1,c_2,\ldots,c_G$ denotes $G$ such changepoints which belong to the set $\G$ and $|\G|=G$. Here, $c_0$ is a virtual changepoint which starts at $t=1$. 
We denote each of the \textit{non-overlapping reward generating processes} as $\rho_{c_j}$, $j\in\mathbb{N}$. Note that the learner does not know these changepoints or the total number of changepoints in the environment.

%We assume a global switching model where at particular breakpoint all the arms' distribution changes.

	The distribution associated with individual arm $i$ is denoted by $D_{i,\rho_{c_j:c_{j+1}}}$ for the segment $\rho_{c_j:c_{j+1}}$ whereas the reward drawn from that distribution for the $t$-th time instant is denoted by $X_{i,t}$. We assume all rewards are bounded in $[0,1]$. $n_{i,t_0:t_p}$ denotes the number of times arm $i$ has been pulled from $t_0$ to $t_p$ timesteps. $\mu_{i,t_{c_j:c_{j+1}}}$ denotes the expected mean of the reward distribution $D_{i,\rho_{c_j:c_{j+1}}}$ and $\hat{\mu}_{i,t_0:t_p}$ denotes the sample mean for the arm $i$ from $t_0$ to $t_p$ timesteps.

\begin{definition}
\label{Def:tcj}
We define $t_{c_j}$ for a $c_j\in\G$ between two consecutive segments $\rho_{c_{j-1}:cj}$ and $\rho_{c_j:c_{j+1}}$ as the first time instant that the changepoint $c_j$ happens $\forall i\in\A$, that is,

\begin{align*}
t_{c_j}& = \min\left\lbrace t\in[1,T],\forall i\in\A : \mu_{i,t_{c_{j-1}:c_j}} \neq \mu_{i,t_{c_{j}:c_{j+1}}}   \right\rbrace\\
%%%%%%%%%%%%%%%%%%%%%%%%%%
%&= \min\left\lbrace t\in[1,T],\forall i\in\A: \Delta^{chg}_{i,c_j} \geq \Delta_0 \right\rbrace
\end{align*}

\end{definition}

\begin{assumption}
In this work we have assumed the global changepoint setting and hence $t_{c_j}$ is common across all the arms and the learner does not know the $t_{c_j},\forall c_j\in\G$. 
\end{assumption}

%Also, note that we have assumed that all changepoint gaps $\Delta^{chg}_{i,c_j}$ are above $\Delta_0$.

%\begin{definition}
%\label{Def:d-chg-gap}
%We define a changepoint $c_j$ at time $t_{c_j}$ to be a $d$-optimal changepoint such that for an arm $i\in\A$,
%\begin{align*}
%\left|t_{c_{j-1}} - t_{c_j}\right| \geq d 
%\end{align*}
%
%%\Delta^{chg}_{d,c_j}=\lbrace \exists i\in\A : |\mu_{i,\rho_{c_{j-1}:c_j}}-\mu_{i,\rho_{c_j:c_{j+1}}}|\geq \Delta^{chg}_{i,d}, \text{ where } \\
%%d\geq\dfrac{C\log(t_{c_j}-t_{c_{j-1}})}{\Delta^{chg}_{i,t_{c_j}}}
%
%where $d=\dfrac{C\log(t_{c_j}-t_{c_{j-1}})}{(\Delta^{chg}_{i,c_j})^2}$ and $C$ is an integer constant.
%\end{definition}
%
%\begin{assumption}
%\label{assm:gap}
%We assume that for every two segments $\rho_{c_{j-1}:c_j}$ and $\rho_{c_j:c_{j+1}}$, for $j=1,2,\ldots,G$ there exists atleast one arm $i\in\A$ such that $t_{c_j}$ is a $d$-optimal changepoint.
%\end{assumption}

\begin{assumption}
\label{assm:space-gap}
We assume that for every two consecutive segments $\rho_{c_{j-1}:c_j}$ and $\rho_{c_j:c_{j+1}}, \forall j=1,2,\ldots,G$ all the three  changepoints $t_{c_{j-1}}, t_{c_j}$ and $t_{c_{j+1}}$ satisfy the following condition,
\begin{align*}
\dfrac{d(t_{c_j} - t_{c_{j-1}})}{t_{c_{j+1}} - t_{c_j}} \leq \dfrac{\epsilon_0}{1-\epsilon_0}
\end{align*}
where $d(t_{c_j} - t_{c_{j-1}})$ denotes the delay in detecting a changepoint at $t_{c_j}$ by the learner and $ \epsilon_0 \in (0,1)$.
\end{assumption}

\begin{definition}
\label{Def:chg-gap}
We define the changepoint gap at $t_{c_j}$ for an arm $i\in\A$ between the segments $\rho_{c_{j-1}:c_j}$ and $\rho_{c_j:c_{j+1}}$ as,
\begin{align*}
\Delta^{chg}_{i,c_j}=|\mu_{i,t_{c_{j-1}:c_j}}-\mu_{i,t_{c_j:c_{j+1}}}|.
\end{align*}
\end{definition}

\begin{discussion}
\label{dis:gap-delay}
Thus, assumption \ref{assm:space-gap} makes sure that all the changepoints $t_{c_j},\forall j=1,2,\ldots,G$ are sufficiently far apart to detect a change. A good learner tries to minimize the delay ($d$) in detection of a changepoint at $t_{c_j},\forall c_{j}\in\G$ by achieving atmost a delay of $d\left(t_{c_j} - t_{c_{j-1}}\right) \leq O\left( \dfrac{\log( t_{c_j} - t_{c_{j-1}} )}{\Delta_{i,c_j}^{2}}\right)$. Note, that when the gaps are same such that for all $i\in\A$, $\Delta_{i,c_j}^{chg}=\Delta_{\epsilon_0,c_j}^{chg}$ and $d\left(t_{c_j} - t_{c_{j-1}}\right) = \left( \dfrac{\log( t_{c_j} - t_{c_{j-1}} )}{\Delta_{\epsilon_0,c_j}^{2}}\right)$, then due to assumption \ref{assm:space-gap} we get,
\begin{align*}
\Delta_{\epsilon_0,c_j}^{chg}\geq \sqrt{\dfrac{1-\epsilon_0}{\epsilon_0}\dfrac{\log(t_{c_j} - t_{c_{j-1}})}{(t_{c_{j+1}} - t_{c_{j}})}}.
\end{align*}

Hence, $\Delta_{\epsilon_0,c_j}^{chg}$ is the minimum gap possible that can be detected by the learner given the changepoints $t_{c_{j-1}}, t_{c_j}$ and $t_{c_{j+1}}$ follow assumption \ref{assm:space-gap}.

% that is atleast $\epsilon_0 \geq \dfrac{t_{c_j} - t_{c_{j-1}}}{t_{c_{j+1}} - t_{c_{j-1}}}$. Hence, smaller the $\epsilon_0$, harder it is to detect a changepoint at $t_{c_j}$ and a larger succeeding segment $\rho_{c_j:c_{j+1}}$ is required.
\end{discussion}

%as the preceding segment $t_{c_{j+1}} - t_{c_{j}}$ is smaller and less observation is available from the segment $\rho_{c_{j-1}:c_j}$

\begin{definition}
\label{Def:e-chg-gap}
We define a changepoint gap $\Delta^{chg}_{i,c_j}$ at changepoint $c_j\in\G$ for an arm $i\in\A$ to be an $\epsilon_0$-optimal changepoint such that,
\begin{align*}
\Delta^{chg}_{i,c_j} \geq \Delta_{\epsilon_0,c_j}^{chg}.
\end{align*}
\end{definition}

\begin{assumption}
\label{assm:chg-gap}
In this paper we assume that $\forall c_{j}\in\G$ the changepoint gaps $\Delta^{chg}_{i,c_j},\forall i\in\A$ are $\epsilon_0$-optimal.
\end{assumption}

\begin{definition}
\label{Def:opt-gap}
We define the optimality gap $\Delta^{opt}_{i,c_j}$ for an arm $i_{t'}\neq i^*_{t'},\forall t'\in[t_{c_{j-1}},t_{c_j}]$ as,
\begin{align*}
\Delta^{opt}_{i,c_j}= \mu_{i^*,t_{c_{j-1}:c_j}}-\mu_{i,t_{c_{j-1}:c_j}}.
\end{align*}
\end{definition}

Also, recall from Definition \ref{Def:chg-gap} that the changepoint gap $\Delta^{chg}_{i,c_j}=|\mu_{i,t_{c_{j-1}:c_j}}-\mu_{i,t_{c_j:c_{j+1}}}|$.

\begin{definition}
\label{Def:ratio}
We define $\Psi_{i,c_j}$ as the ratio between $\Delta^{opt}_{i,c_j}$ and $\Delta^{chg}_{i,c_j}$ for the $i$-th arm in $\A$ and the $c_j$-th changepoint in $\G$ such that,

\begin{align*}
\Psi_{i,c_j} = \dfrac{\Delta^{opt}_{i,c_{j+1}}}{\Delta^{chg}_{i,c_j}}
\end{align*}

\end{definition}

%	We define each expert or forecaster as $f_{j}\in \M_{t_0:t_p}$, where $\M_{t_0:t_p}$ is the set of all forecasters from time $t_0$ to $t_p$. $\M^+_{t}$ is the set of new forecasters introduced at time $t$. Also, we define $\hat{L}_{f_i,t_0:t_p}=\sum_{s=t_0}^{t_p}\ell_{f_i ,s}$ as the true cumulative loss suffered by the expert $f_i$ from $t_0$ to $t_p$-th timestep and $\hat{L}_{f_i,t_0:t_p}$ as the estimated cumulative loss suffered by an expert $f_i$ from $t_0$ to $t_p$-th timestep such that $\hat{L}_{f_i,t}=\sum_{s=t_0}^{t_p}\hat{\ell}_{f_i ,s}$. Similarly, we define $L_{i,t_0:t_p}$ and $\hat{L}_{i,t_0:t_p}$ as the true loss and the estimated loss suffered by arm $i$. The weight of an expert $f_i$ at time $t$ is defined as $w_{f_i,t}$ and $\eta$ is defined as a parameter for exploration. Also let $i_{f_j,t}$ be the action suggested by expert $f_j$ at time $t$.

### 2017-11-24 Chapter6/probDef.tex
Latest on 24/11/2017

Given the exploration-exploitation-changepoint dilemma, the objective of the learner in the piecewise-stochastic bandit problem is to minimize the cumulative regret until time $t$, which is defined as follows:
\begin{align*}
R_{t}=\sum_{t'=1}^t\mu_{i^*_{t'}} - \sum_{t'=1}^t\mu_{I_t'}
%R_{t}=\sum_{t'=1}^t\mu_{i^*_{t'}} - \sum_{i=1}^K \left(\mu_{i}n_{i_{t'}\neq i^*_{t'},\forall t'=1:t}\right),
\end{align*}
where $t$ is the number of rounds, $\mu_{i^*_{t'}}$ is the optimal arm at the $t'$ timestep and $\mu_{I_{t'}}$ is the arm chosen by the learner at the $t'$ timestep. Let $n_{i_{t'}\neq i^*_{t'},\forall t'=1:t}$ is the number of times the learner has chosen arm $i$ up to round $t$ when it was not the optimal arm $i^*_{t'}$. The expected regret of an algorithm after $t$ rounds can be written as,

\begin{align*}
\E[R_{t}]&= \E\left[\sum_{t'=1}^t\mu_{i^*_{t'}} - \sum_{t'=1}^t\mu_{I_t}\right]\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&=\sum_{i\neq i^*}^K\left(\mu_{i^*} - \mu_i\right) \E[n_{i_{t'}\neq i^*_{t'},\forall t'=1:t}] \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\overset{(a)}{=}\sum_{i\neq i^*}^K\sum_{j=1}^{G}\Delta^{opt}_{i,c_j}\E[n_{i_{t'}\neq i^*_{t'},\forall t'=t_{c_{j-1}}:t_{c_j}}]
\end{align*}
where $(a)$ is obtained from assumption \ref{assm:chg-gap} and $\Delta^{opt}_{i,c_j}$ is defined as in Definition \ref{Def:opt-gap}.

### 2017-11-24 Chapter6/related.tex
Latest on 24/11/2017

Multi-armed bandits (MAB) have been extensively studied in the \textit{stochastic setting} where the distribution associated with each arm is fixed throughout the time horizon. Starting from the seminal works of \citet{thompson1933likelihood} and  \citet{robbins1952some} and finally in \citet{lai1985asymptotically} the authors provide the asymptotic lower bound for the class of algorithms considered.  The upper confidence bound (UCB) algorithms, which are a type of index-based frequentist strategy, were first proposed in \citet{agrawal1995sample} and the first finite-time analysis for the stochastic setting for this class of algorithms was proved in \citet{auer2002finite}. Over the years several strong UCB type algorithms were proposed for the stochastic setting such as MOSS \citep{audibert2009minimax}, UCBV \citep{audibert2009exploration}, UCB-Improved \citep{auer2010ucb}, OCUCB \citep{lattimore2015optimally}, etc. Further, some of the Bayesian strategies which were proposed for this setting includes the Thompson Sampling \citep{agrawal2012analysis},\citep{agrawal2013further} and Bayes-UCB \citep{kaufmann2012bayesian} algorithms.

Another setting that has greatly motivated the first studies in bandit literature is the \textit{adversarial setting}. In this setting, an adversary chooses the reward for each arm and then the learner selects an arm without the knowledge of the adversary's choice. The adversary may or may not be oblivious to the learner's strategy and this forces the learner to employ a randomized algorithm to confuse the adversary. Previous works on this have focused on constructing different types of exponential weighting algorithms that are based on the Hedge algorithm that has been proposed before in \citet{littlestone1994weighted},\citet{freund1995desicion} and analyzed in \citet{auer1995gambling}. Further variants of this strategy called EXP3 \citep{auer2002nonstochastic} and EXP3IX \citep{kocak2014efficient} have also been proposed which incorporates different strategies for exploration to minimize the loss of the learner.

Striding between these two contrasting settings is the piece-wise stochastic multi-armed bandit setting where there are a finite number of changepoints when the distribution associated with each arm changes abruptly. Hence, this setting is neither as pessimistic as adversarial setting nor as optimistic as the stochastic setting. Therefore, the two broad class of algorithms mentioned before fail to perform optimally in this setting. Several interesting solutions have been proposed before for this setting which can be broadly divided into two categories, passively adaptive and actively adaptive strategies. Passively adaptive strategies like Discounted UCB (DUCB) \citep{kocsis2006discounted}, Switching Window UCB (SW-UCB)  \citep{garivier2011upper} and Discounted Thompson Sampling (DTS) \citep{raj2017taming} do not actively try to locate the changepoints but rather try to minimize their losses by concentrating on past few observations or like Restarting Exp3 (RExp3) \citep{DBLP:journals/corr/BesbesGZ14} behave pessimistically as like Exp3 but restart after pre-determined phases. On the other hand, actively adaptive strategies like Adapt-EVE \citep{hartland2007change}, Windowed-Mean Shift \citep{yu2009piecewise}, EXP3.R \citep{allesiardo2017non}, CUSUM-UCB \citep{liu2017change} try to locate the changepoints and restart the chosen bandit algorithms. Also, there are Bayesian strategies like Global Change-Point Thompson Sampling (GCTS)\citep{mellor2013thompson} which uses Bayesian changepoint detection to locate the changepoints.

### 2017-11-24 Chapter1/types.tex
Latest on 24/11/2017

@@
 
-\begin{itemize}
+\begin{enumerate}
 \item \textbf{Adversarial bandits: } In adversarial bandits, an adversary decides the payoff for each arm before the learner selects an arm.
@@
 In our thesis, chapter \ref{chap:psbandit} is based on this setting.
-\end{itemize}
+\end{enumerate}
 
@@
 where, $\Delta_{J_n}$ is the instantaneous gap between the expected mean of he optimal arm and the recommended arm by the learner.
+In the pure exploration setting the learner tries to minimize the simple regret and we study a very similar setting in chapter \ref{chap:tbandit1} and chapter \ref{chap:tbandit2}.
 
@@
 In this scenario, considering that there is a single best arm, the learner is more interested in minimizing the worst-case regret.
-Formally, for any sequence of actions $\left( j_1, \ldots , j_T \right)$ over the time horizon $T$, the weak regret for single best action is defined as the difference between,
+Formally, for any sequence of actions $\left( j_1, \ldots , j_T \right)$ chosen by the learner over the time horizon $T$, the weak regret for single best action is defined as the difference between,
 \begin{align*}
@@
 \end{align*}
-where, $G_{\max}(j_1,\ldots,j_T) = \max_{i\in\A}\sum_{t=1}^{T}x_{i_t}$ is the return of the globally best action over the entire horizon $T$ and $G_{\pi}(T)$ is the return following the policy $\pi$ over the horizon $T$ instead of choosing $j_1,\ldots,j_T$.
+where, $G_{\max}(j_1,\ldots,j_T) = \max_{i\in\A}\sum_{t=1}^{T}X_{i_t}$ is the return of the globally best action over the entire horizon $T$, $X_{i_t}$ is the reward observed for the $i$-th arm at the $t$-th timestep and $G_{\pi}(T)$ is the return following the policy $\pi$ over the horizon $T$ instead of choosing $j_1,\ldots,j_T$.
+
+\subsection{Contextual Bandits}
+
+Another interesting variation of the MAB model is the contextual bandit setup, where there are contexts or features associated with each arm.
+We can envision this with an example of online news article recommendation where there are users and articles and the goal of the learner is to map the correct article to an user so as to generate the user's  interest.
+Following a similar work in \citet{langford2008epoch} this problem can be formulated as a contextual MAB problem such that at every timestep $t=1,\ldots,T$
+\begin{enumerate}
+\item The learner observes an user $u_t$ and the set of arms (articles) $i\in\A$ along with their feature vectors $\mathcal{v}_{i,t},\forall i\in\A_t$.
+This vector contains information of both the users and the arms and is referred as the context.
+\item On the basis of previous trials the learner pulls an arm $i_t\in\A$ at the $t$-th timestep and observes the reward $X_{i,t}$ for only the arm $i_t\in\A$.
+\item The algorithm then improves its prediction for the next trial with the new observation, $\left(v_{i,t},i_{t}, X_{i,t} \right)$.
+\end{enumerate}
+This type of settings have been extensively studied in \citet{li2010contextual} and \citet{beygelzimer2011contextual}.
 
@@
 
-Distributed bandits are specific setup of MAB where a network of bandits collaborate with each other to identify the optimal arm(s) (see \citet{awerbuch2008competitive,liu2010distributed,szorenyi2013gossip,hillel2013distributed}).
-In our setting we can assign each of the $p$ clusters to individual bandits and at the end of each round they can share information synchronously to identify the optimal arm.
-This naturally results in a speedup of operation and helps in identifying the best arm faster.
-The clustering in this case is typically done over the feature space \citet{bui2012clustered}, \citet{cesa2013gang}, \citet{gentile2014online}.
+Distributed bandits is a special setting where a network of bandits collaborates with each other to identify the best set of arms.
+The contextual MAB model discussed before naturally extends into this setting where a network of bandits try to map articles to a large number of users by collaborating between themselves (see \citet{awerbuch2008competitive,liu2010distributed,szorenyi2013gossip,hillel2013distributed}).
+In this setting, bandits at the end of specific phases share information synchronously or asynchronously amongst each other to identify the best set of arms.
+Further, to learn more complicated structures and interaction between the user and article feature vectors, clustering can be used to cluster the articles and users based on their features and this has been studied in \citet{bui2012clustered}, \citet{cesa2013gang}, \citet{gentile2014online}.
 

### 2017-11-24 Chapter1/types.tex
Latest on 24/11/2017

@@
 
+Another interesting area in the bandit setting is a variant of the stochastic MAB problem in which the
+rewards are corrupted.
+In certain recommender systems it is sometimes vital to preserve the privacy of the users.
+Motivated by these, bandits with corrupt feedback assumes that the rewards it is receiving is corrupted by a stochastic corruption process of known parameters and the goal of the learner is again to maximize the reward by suggesting the best  items to the users in this framework.
+This setting has been analyzed in \citet{DBLP:journals/corr/abs-1708-05033}.
+
 \subsection{Conservative Bandits}
+
+This setting is motivated by the scenario where there is one default safe arm which will always provide the learner with a good reward, but there are several unexplored arms which might provide the learner with better rewards if explored more.
+But the learner cannot do unconstrained exploration as its budget is limited and every time it pulls an arm it has to pay a cost.
+Hence, it must balance between pulling the safe arm and constrained exploration.
+This type of exploration under constraint has been termed as conservative bandits and is studied in \citet{DBLP:conf/icml/WuSLS16} .

### 2017-11-26 Chapter1/intro.tex
Latest on 26/11/2017

@@
-In today's world a large number of problems in science and engineering, robotics and 
-game playing, resource management, financial portfolio
-management, medical treatment design, ad placement, website optimization and packet routing can be modeled as sequential decision-making under uncertainty. Many of these real-world interesting
-sequential decision-making problems can be formulated as reinforcement
-learning (RL) problems (\cite{bertsekas1996neuro}, \cite{sutton1998reinforcement}).
+In today's world artificial intelligence has proved to be a game-changer in designing agents that interact with an evolving environment and make decisions on the fly.
+The main goal of artificial intelligence is to design artificial agents that make dynamic decisions in an evolving environment.
+In pursuit of these the agent can be thought of as making a series of  sequential decisions by interacting with the dynamic environment which provides it with some sort of feedback after every decision which the agent incorporates into its decision-making strategy to formulate the next decision to be made.
+A large number of problems in science and engineering, robotics and game playing, resource management, financial portfolio management, medical treatment design, ad placement, website optimization and packet routing can be modeled as sequential decision-making under uncertainty.
+Many of these real-world interesting
+sequential decision-making problems can be formulated as reinforcement learning (RL) problems (\citep{bertsekas1996neuro}, \citep{sutton1998reinforcement}).
 In an RL problem, an agent interacts with a dynamic, stochastic, and unknown environment, with the goal of finding an action-selection strategy or policy that optimizes some long-term performance measure.
@@
 This is the crux of online sequential learning.
+An illustrative image depicting the reinforcement learning scenario is shown in Figure \ref{fig:rl}.
+
 	This is in contrast to supervised learning methods that deal with labeled data which are independently and identically distributed (i.i.d.) samples from the domain and train some classifier on the entire training dataset to learn the pattern of this distribution to predict future samples (test dataset) with the assumption that it is sampled from the same domain, whereas the RL agent learns from the samples that are collected from the trajectories generated by its sequential interaction with the system.
@@
 Our work will focus on this idea of MAB model.
+
+\begin{figure}[!th]
+\includegraphics[scale=0.7]{Chapter1/img/RL.png}
+\caption{Reinforcement Learning}
+\label{fig:rl}
+\end{figure}
+
+%To express an RL problem more formally, we have to define the idea of Markov Decision Process (MDP) which consists of states, actions, transition probabilities and rewards which in turn helps in deciding the strategy to be followed by the agent.
+
+%An MDP consists of states

### 2017-11-26 Chapter1/types.tex
Latest on 26/11/2017

@@
-In this section we discuss on the various types of bandits that are available in literature.
+In this section, we discuss the various types of bandits that are available in the literature.
 
@@
 
-In non-stochastic setting the distribution associated with each arm varies over the duration of the play. Two natoable examples of this are:-
+In non-stochastic setting, the distribution associated with each arm varies over the duration of the play. Two notable examples of this are:-
 
@@
 This adversary may or may not be oblivious to the learning algorithm employed by the learner.
-In each of these cases a different guarantee on the performance of the learner can be arrived at.
+In each of these cases, a different guarantee on the performance of the learner can be arrived at.
 Some of the important papers in this setting are \citet{auer2002nonstochastic}, \citet{auer2002using}, \citet{kocak2014efficient}.
@@
 In this setting, the distribution associated with each arm is not fixed throughout the time horizon and changes either arbitrarily at particular changepoints, or changes at a fixed period.
-The distribution associated with each arm then  remains fixed till the next chnagepoint is encountered.
+The distribution associated with each arm then remains fixed till the next changepoint is encountered.
 Several recent works have focussed on this such as  \citep{garivier2011upper}, \citep{mellor2013thompson}, and \citep{allesiardo2017non}.
@@
 
-\subsubsection{Contextual Bandits}
-
-The idea of clustering has been extensively studied in the contextual bandit setup, an extension of the MAB where side information or features are attached to each arm.
-The clustering is done over the features representing the arms to capture the complexity of the problem better when a large-number of arms are involved.
-Typical examples of this setting are in web-advertising domain, news article selection, etc.
+%\subsubsection{Contextual Bandits}
+%
+%The idea of clustering has been extensively studied in the contextual bandit setup, an extension of the MAB where side information or features are attached to each arm.
+The clustering is done over the features representing the arms to capture the complexity of the problem better when a large number of arms are involved.
+Typical examples of this setting are in a web-advertising domain, news article selection, etc.
 Some notable papers available for this setting are   \citet{auer2002using}, \citet{langford2008epoch}, \citet{li2010contextual}, \citet{beygelzimer2011contextual}, \citet{slivkins2014contextual},etc.
@@
 In bandit literature, based on the goal we can divide bandits into several categories.
-To illustrate his we put forward a simple scenario let us consider a stochastic bandit scenario where there are $K$ arms labeled $i=1,2,\ldots,K$ with their expected means of reward distributions ($D_i$) be denoted by $r_i$.
+To illustrate his we put forward a simple scenario let us consider a stochastic bandit scenario where there are $K$ arms labeled $i=1,2,\ldots, K$ with their expected means of reward distributions ($D_i$) be denoted by $r_i$.
 Also let there be single optimal arm $*$ such that $r^* = \max_{i\in\A}r_i$.
@@
 
-where, $\Delta_{J_n}$ is the instantaneous gap between the expected mean of he optimal arm and the recommended arm by the learner.
+where $\Delta_{J_n}$ is the instantaneous gap between the expected mean of the optimal arm and the recommended arm by the learner.
 In the pure exploration setting the learner tries to minimize the simple regret and we study a very similar setting in chapter \ref{chap:tbandit1} and chapter \ref{chap:tbandit2}.
@@
 Another interesting variation of the MAB model is the contextual bandit setup, where there are contexts or features associated with each arm.
-We can envision this with an example of online news article recommendation where there are users and articles and the goal of the learner is to map the correct article to an user so as to generate the user's  interest.
-Following a similar work in \citet{langford2008epoch} this problem can be formulated as a contextual MAB problem such that at every timestep $t=1,\ldots,T$
+We can envision this with an example of online news article recommendation where there are users and articles and the goal of the learner is to map the correct article to a user so as to generate the user's  interest.
+Following a similar work in \citet{langford2008epoch} this problem can be formulated as a contextual MAB problem such that at every timestep $t=1,\ldots, T$
 \begin{enumerate}
 \item The learner observes an user $u_t$ and the set of arms (articles) $i\in\A$ along with their feature vectors $\mathcal{v}_{i,t},\forall i\in\A_t$.
-This vector contains information of both the users and the arms and is referred as the context.
+This vector contains information about both the users and the arms and is referred as the context.
 \item On the basis of previous trials the learner pulls an arm $i_t\in\A$ at the $t$-th timestep and observes the reward $X_{i,t}$ for only the arm $i_t\in\A$.
@@
 rewards are corrupted.
-In certain recommender systems it is sometimes vital to preserve the privacy of the users.
+In certain recommender systems, it is sometimes vital to preserve the privacy of the users.
 Motivated by these, bandits with corrupt feedback assumes that the rewards it is receiving is corrupted by a stochastic corruption process of known parameters and the goal of the learner is again to maximize the reward by suggesting the best items to the users in this framework.
@@
 Hence, it must balance between pulling the safe arm and constrained exploration.
-This type of exploration under constraint has been termed as conservative bandits and is studied in \citet{DBLP:conf/icml/WuSLS16} .
+This type of exploration under constraint has been termed as conservative bandits and is studied in \citet{DBLP:conf/icml/WuSLS16}.

### 2017-11-26 Chapter4/connection.tex
Latest on 26/11/2017

The thresholding bandit problem is a specific instance of the pure-exploration setup of \citet{chen2014combinatorial}. To put it in perspective, the considered TBP setup lies at the intersection of the larger pure exploration setting and the stochastic multi-armed bandit (SMAB) setting discussed in chapter \ref{chap:SMAB} and chapter \ref{chap:EUCBV}. This is shown in Figure \ref{fig:con}.

\begin{figure}[!th]
\includegraphics[scale=0.7]{Chapter4/img/connection_TBP.png}
\caption{Connection between TBP, Pure Exploration and SMAB}
\label{fig:con}
\end{figure}

\subsubsection{Challenges in the TBP seeting}

Further, if we look closely into the TBP setting we will see that there are several similarities between the challenges in SMAB setting and the TBP setting.

\begin{enumerate}
\item Closer an arm’s expected reward mean ($r_i$) to $\tau$ $\Rightarrow$ Harder is the problem. This stems from the fact that it becomes increasingly difficult to discriminate between the arms lying above and below $\tau$.
\item Lesser the budget $T$ $\Rightarrow$ Harder is the problem. This is because there are lesser number of pulls available and so the number of samples collected tends to be low.
\item Higher the variance of an arm’s reward distribution $D_i$ $\Rightarrow$ Harder is the problem. This is similar to the first case as it becomes harder to discriminate between the arms lying close to the threshold.
\end{enumerate}

In the theoretical section in chapter \ref{chap:tbandit2} we will try to characterize this hardness and give guarantees that are almost optimal.

### 2017-11-26 Chapter4/prevRes.tex
Latest on 26/11/2017

@@
 \State \textbf{Initialization: } $n_0 = 0$
-\State \textbf{Definition: } $\bar{\log K} = \dfrac{1}{2} + \sum_{i=2}^{K}\dfrac{1}{i}$, $n_k = \dfrac{1}{\bar{\log K}}\dfrac{T-K}{K + 1 - m}$
+\State \textbf{Definition: } $\overline{\log K} = \dfrac{1}{2} + \sum_{i=2}^{K}\dfrac{1}{i}$, $n_m = \dfrac{1}{\bar{\log K}}\dfrac{T-K}{K + 1 - m}$
 \For{For each phase $m=1,..., K-1$}
-\State For each $i \in B_{m}$, select arm $i$ for $n_k - n_{k-1}$ timesteps.
+\State For each $i \in B_{m}$, select arm $i$ for $n_m - n_{m-1}$ timesteps.
 \State Let $B_{m+1} = B_m\setminus \argmin_{i\in B_m} \hat{r}_i$
@@
 However, SR does not have any explicit confidence interval as UCBE, rather the idea of the confidence interval is hidden in the number of pulls allocated to each arm in every round.
-The number of times each arm is pulled in every round, that is $n_k - n_{k-1}$ timesteps makes sure that the optimal arm is not eliminated in the $k$-th round with high probability.
+The number of times each arm is pulled in every round, that is $n_m - n_{m-1}$ timesteps makes sure that the optimal arm is not eliminated in the $m$-th round with high probability.
 
-In the combinatorial fixed budget setup \citet{gabillon2011multi} propose the GapE and GapE-V algorithms that suggest, with high probability, the best $m$ arms at the end of the time budget.
+%In the combinatorial fixed budget setup \citet{gabillon2011multi} propose the GapE and GapE-V algorithms that suggest, with high probability, the best-$p$ arms at the end of the time budget.
 
-Similarly, \citet{bubeck2013multiple} introduce the  Successive Accept Reject (SAR) algorithm, which is an extension of the SR algorithm; SAR is a round based algorithm whereby at the end of each round an arm is either accepted or rejected (based on certain confidence conditions) until the top $m$ arms are suggested at the end of the budget with high probability.
+\subsection{Successive Accept Reject Algorithm for best-p arms setting}
+
+The goal in best p-arms setting is to identify the top $p$ arms out of $K$ given arms where $p$ is supplied as an input.
+Several algorithms have been proposed for these setup starting with \citet{gabillon2011multi} where the authors proposed the GapE and GapE-V algorithms that suggest, with high probability, the best-$p$ arms at the end of the time budget.
+These algorithms are similar to the UCBE type algorithm discussed in previous section.
+In this section we will discuss the Successive Accept Reject strategy shown in algorithm \ref{alg:sar}.
+
+\begin{algorithm}[!th]
+\caption{Successive Accept Reject(SAR)}
+\label{alg:sar}
+\begin{algorithmic}[1]
+\State \textbf{Input: } The budget $T$, $p$ 
+\State \textbf{Initialization: } $n_0 = 0$
+\State \textbf{Definition: } $\overline{\log K} = \dfrac{1}{2} + \sum_{i=2}^{K}\dfrac{1}{i}$, $n_m = \dfrac{1}{\bar{\log K}}\dfrac{T-K}{K + 1 - m}$
+\For{For each phase $m=1,..., K-1$}
+\State For each $i \in B_{m}$, select arm $i$ for $n_m - n_{m-1}$ timesteps.
+\State Let $B'_{m}$ be the set that contains arms in decreasing order of their sample means $\hat{r}_{i},\forall i\in B_{m}$ such that $\hat{r}_{B'_{m}(1),n_m} \geq \hat{r}_{B'_{m}(2),n_m} \geq \ldots \geq \hat{r}_{B'_{m}(K+1-m),n_m}$.
+\State Define the new empirical gaps $\forall i\in B'_{m}$ such that for $1\leq r\leq K+1-m$,
+\begin{align*}
+\Delta_{B'_{m}(r),n_m} =
+    \begin{cases}
+      \hat{r}_{B'_{m}(r),n_m} - \hat{r}_{B'_{m}(p(m)+1),n_m}, & \text{ if }\ r\leq p(m+1) \\
+      \hat{r}_{B'_{m}(p(m)),n_m}  - \hat{r}_{B'_{m}(r),n_m}, & \text{ if }\ r> p(m)+1
+    \end{cases}
+%\Delta_{B'_{m}(r),n_m} = \bigg\lbrace^{\hat{r}_{B'_{m}(r),n_m} - \hat{r}_{B'_{m}(p(m)+1),n_m} \text{, if $r\leq p(m)+1$}}_{\hat{r}_{\hat{r}_{B'_{m}(p(m)),n_m}  - \hat{r}_{B'_{m}(r),n_m} \text{, if $r> p(m)+1$}}}
+\end{align*}
+\State Let $i_m\in \argmax_{i\in B'_m} \hat{\Delta}_{i,n_m}$, then $B_{m+1} = B_m\setminus i_m$ (deactivate $i_m$ with ties broken arbitrarily).
+\State If $\hat{r}_{i_m,n_m} > \hat{r}_{B'_{m}(p(m)+1)}$, then accept $i_m$ and set $p(m+1)=p(m)-1$, $J_{p - p(m+1)}=i_m$.
+\State $m:=m+1 $
+\EndFor
+\State Output the $p$-accepted arms $J_1,J_2,\ldots, J_p$.
+\end{algorithmic}
+\end{algorithm}
+
+\citet{bubeck2013multiple} introduced the  Successive Accept Reject (SAR) algorithm, which is an extension of the SR algorithm; SAR is a round based algorithm whereby at the end of each round an arm is either accepted or rejected (based on certain confidence conditions) until the top $p$ arms are suggested at the end of the budget with high probability.
+Like SR algorithm, the SAR algorithm divides the budget into rounds where in each round it pulls all the arms equal  number of times that is for $n_m - n_{m-1}$ timesteps.
+At the end of the round it orders the arms into a decreasing sequence of their empirical means in $B'_{m}$ and computes for the $p(m)$ empirical best arms in $B'_{m}$ the distance (in terms of their empirical means) to the $(p(m) + 1)$-th empirical best arm in $B'_{m}$.
+Again for the arms not in the $p(m)$ empirical best arms, SAR computes the distance to the $p(m)$-th empirical best arm.
+Finally, SAR deactivates the arm $i_m$ that has the maximum empirical distance.
+If $i_m$ is the empirical best arm in the $m$-th round, then SAR accepts $i_m$ and sets $p(m + 1) = p(m) - 1$ and $J_p - p(m+1) = i_m$, or otherwise SAR rejects  $i_m$.
+
 	A similar combinatorial setup was explored in \citet{chen2014combinatorial} where the authors propose the Combinatorial Successive Accept Reject (CSAR) algorithm, which is similar in concept to SAR but with a more general setup.
@@
 Apart from these two settings some unified approaches has also been suggested in \citet{gabillon2012best} which proposes the algorithms UGapEb and UGapEc which can work in both the above two settings.
-The thresholding bandit problem is a specific instance of the pure-exploration setup of \citet{chen2014combinatorial}.

### 2017-11-26 Chapter4/prevResAPT.tex
Latest on 26/11/2017

@@
-\begin{algorithm}[!h]
+In the latest work of \citet{locatelli2016optimal} Anytime Parameter-Free Thresholding (APT) algorithm comes up with an improved anytime guarantee than CSAR for the thresholding bandit problem.
+APT is stated in algorithm \ref{alg:apt}.
+
+\begin{algorithm}[!th]
 \caption{APT}
@@
 
-In the latest work of \citet{locatelli2016optimal} Anytime Parameter-Free Thresholding (APT) algorithm comes up with an improved anytime guarantee than CSAR for the thresholding bandit problem.
+The APT algorithm is very simple to implement and the logic behind the arm pull directly follows from the challenges in the TBP setting discussed before.
+Note, that the most difficult arms to discriminate are the arms whose expected means are lying close to the threshold $\tau$, hence APT pulls those arms whose sample means $\hat{r}_i$ are lying close to the threshold and the arms which has not been pulled often.
+The second condition is satisfied by the $\sqrt{n_i}$ term which acts very similar to the confidence interval term discussed for UCBE (see algorithm \ref{alg:ucbe}).
+The tolerance level $\epsilon\geq 0$ gives the algorithm a degree of flexibility in pulling the arms close to the threshold.

### 2017-11-27 Chapter2/related.tex
Latest on 26/11/2017
Latest on 27/11/2017

@@
 Also, note that in UCB-Improved the knowledge of horizon is required before-hand to calculate the confidence intervals whereas no such input is required for UCB1.
+An illustrative flowchart depicting the main steps is given in Figure \ref{fig:ucbimp}.
+
+\begin{figure}[!th]
+\includegraphics[scale=0.45]{Chapter2/img/Ucb-Imp.png}
+\caption{Flowchart of UCB-Improved}
+\label{fig:ucbimp}
+\end{figure}
 
@@
 
-    In the later work of \citet{audibert2009minimax}, the authors propose the MOSS algorithm and showed that the worst case gap-independent regret bound of MOSS is $O\left( \sqrt{KT} \right)$ which improves upon UCB1 by a factor of order $\sqrt{\log T}$.
+    In the later work of \citet{audibert2009minimax}, the authors propose the MOSS algorithm (see algorithm \ref{alg:moss}) and showed that the worst case gap-independent regret bound of MOSS is $O\left( \sqrt{KT} \right)$ which improves upon UCB1 by a factor of order $\sqrt{\log T}$.
 However, the gap-dependent regret of MOSS is $O\left( \frac{K^{2}\log\left(T\Delta^{2}/K\right)}{\Delta}\right)$ and in certain regimes, this can be worse than even UCB1 (see \citet{audibert2009minimax,lattimore2015optimally}).
 
-    Recently in \citet{lattimore2015optimally}, the authors showed that  the algorithm OCUCB achieves order-optimal gap-dependent regret bound of $O\left(\sum_{i=2}^{K}\frac{\log\left(T/H_i\right)}{\Delta_i}\right)$ where $H_i=\sum_{j=1}^{K}\min\left\lbrace \frac{1}{\Delta_i^2},\frac{1}{\Delta_j^2}\right\rbrace$, and a gap-independent regret bound of $O\left( \sqrt{KT}\right)$.
+\subsubsection{OCUCB Algorithm}
+
+\begin{algorithm}[!th]
+\caption{OCUCB}
+\label{alg:ocucb}
+\begin{algorithmic}[1]
+\State \textbf{Input:} Time horizon $T$, $K$ number of arms with unknown parameters of reward distribution, exploration parameter $\alpha$ and $\psi$
+\State Pull each arm once
+ \For{$t=K+1,..., T$}
+\State Pull the arm such that $\argmax_{i\in \A}\bigg\lbrace\hat{r}_{i} + \sqrt{\dfrac{\alpha\log(\psi\frac{T}{t})}{n_i}}\bigg\rbrace$
+\State $t:=t+1 $
+ \EndFor
+\end{algorithmic}
+\end{algorithm}
+
+Recently in \citet{lattimore2015optimally}, the authors showed that the algorithm Optimally Confident UCB (OCUCB) (see algorithm \ref{alg:ocucb}) achieves order-optimal gap-dependent regret bound of $O\left(\sum_{i=2}^{K}\frac{\log\left(T/H_i\right)}{\Delta_i}\right)$ where $H_i=\sum_{j=1}^{K}\min\left\lbrace \frac{1}{\Delta_i^2},\frac{1}{\Delta_j^2}\right\rbrace$, and a gap-independent regret bound of $O\left( \sqrt{KT}\right)$.
 This is the best known gap-dependent and gap-independent regret bounds in the stochastic MAB framework.
@@
 
-    In contrast to the above work, the UCBV \citep{audibert2009exploration} algorithm utilizes variance estimates to compute the confidence intervals for each arm.
-In UCBV the confidence interval term is given by $\sqrt{\dfrac{2\hat{v}_i\log (t)}{s_i}} + \dfrac{3\log (t)}{3}$ where $\hat{v}_i$ denotes the empirical variance of the arm $i$.
+    In contrast to the above work, the UCB-Variance (UCBV) algorithm in \citet{audibert2009exploration} utilizes variance estimates to compute the confidence intervals for each arm.
+In UCBV (see algorithm \ref{alg:ucbv}) the confidence interval term is given by $\sqrt{\dfrac{2\hat{v}_i\log (t)}{s_i}} + \dfrac{3\log (t)}{3}$ where $\hat{v}_i$ denotes the empirical variance of the arm $i$.
 Hence, the confidence interval makes sure that the arms whose variances are high are pulled more often to get a better estimates of their $\hat{r}_i$.
@@
 \hline
-OCUCB     	& $\sqrt{\dfrac{2\log(\frac{2T}{t})}{n_i}}$ & Yes & Tightest confidence interval leading to order-optimal regret bounds.\\\midrule
+OCUCB     	& $\sqrt{\dfrac{2\log(\frac{2T}{t})}{n_i}}$ & Yes & Tightest confidence interval with exploration parameter $\alpha=2$, $\psi=2$ leading to order-optimal regret bounds.\\\midrule
 \end{tabular}

### 2017-11-27 Chapter3/Conclusion.tex
Latest on 27/11/2017

@@
 Our theoretical analysis conclusively established that EUCBV exhibits an order-optimal gap-independent regret bound of $O\left(\sqrt{KT}\right)$.
-Empirically, we show that EUCBV performs superbly across diverse experimental settings and outperforms most of the bandit algorithms in a  stochastic MAB setup.
-Our experiments show that EUCBV is extremely stable for larger horizons and performs consistently well across different types of distributions.
-One avenue for future work is to remove the constraint of $T\geq K^{2.4}$ required for EUCBV to reach the order optimal regret bound.
-Another future direction is to come up with an anytime version of EUCBV.
-An anytime algorithm does not need the horizon $T$ as an input parameter.
+Empirically, we show that EUCBV performs superbly across diverse experimental settings and outperforms most of the bandit algorithms in an SMAB setup.
+Our experiments showed that EUCBV is extremely stable for large horizons and performs consistently well across different types of distributions.

### 2017-11-27 Chapter3/proofTheorem.tex
Latest on 27/11/2017

--- 2017-10-11 EUCBV/proofTheorem.tex
@@
 %\label{sec:proofTheorem:Lemma1}
-We first present a few technical lemmas that is required  to prove the result in Theorem \ref{Result:Theorem:1}.
+We first present a few technical lemmas that are required  to prove the result in Theorem \ref{Result:Theorem:1}.
 
@@
 If $T\geq K^{2.4}$, $\psi=\frac{T}{ K^2}$, $\rho =\frac{1}{2}$, $m_i = min\lbrace m|\sqrt{4\epsilon_{m} } < \frac{\Delta_i}{4} \rbrace $ and $c_{i} =\sqrt{\frac{\rho (\hat{v}_i + 2)\log (\psi T\epsilon_{m_{i}})}{4 z_i}}$, then,
-%\begin{align*}
-\center $c_{i} < \frac{\Delta_i}{4}$.
-%\end{align*}
+\begin{align*}
+ c_{i} < \frac{\Delta_i}{4}.
+\end{align*}
 \end{lemma}
@@
 \label{proofTheorem:Lemma:3}
-If $m_i = min\lbrace m|\sqrt{4\epsilon_{m} } < \frac{\Delta_i}{4} \rbrace $,  $c_{i} = \sqrt{\frac{\rho (\hat{v}_i + 2) \log (\psi T\epsilon_{m_{i}})}{4 z_{i}}}$ and $n_{m_i} = \frac{\log{(\psi T\epsilon_{m_{i}})}}{2\epsilon_{m_{i}}}$ then we can show that,
+If $m_i = min\lbrace m|\sqrt{4\epsilon_{m} } < \frac{\Delta_i}{4} \rbrace $,  $c_{i} = \sqrt{\frac{\rho (\hat{v}_i + 2) \log (\psi T\epsilon_{m_{i}})}{4 z_{i}}}$ and $n_{m_i} = \frac{\log{(\psi T\epsilon_{m_{i}})}}{2\epsilon_{m_{i}}}$ then we can show that in the $m_i$-th round,
 \begin{align*}
@@
 %%$, since $\sqrt{\rho_{a}\epsilon_{m_{i}}}\leq\dfrac{\Delta_{i}}{2}
-So, the total contribution of ${i}$  till round $m_{i}$ is given by, 
+So, the total contribution of ${i}$ until round $m_{i}$ is given by, 
 \begin{align*}

### 2017-11-27 Chapter4/prevRes.tex
Latest on 27/11/2017

@@
 \subsection{Unified Setting}
-Apart from these two settings some unified approaches has also been suggested in \citet{gabillon2012best} which proposes the algorithms UGapEb and UGapEc which can work in both the above two settings.
+Apart from these two settings some unified approaches has also been suggested in \citet{gabillon2012best} which proposes the algorithms UGapEb and UGapEc which can work in both the fixed budget setting and fixed confidence  setting.

### 2017-11-27 Chapter6/intro.tex
Latest on 27/11/2017

@@
-In this paper, we consider the piece-wise stochastic multi-armed bandit problem, an interesting variation of the stochastic multi-armed bandit problem in sequential decision making.
+In this chapter, we consider the piece-wise stochastic multi-armed bandit problem, an interesting variation of the stochastic multi-armed bandit (SMAB) problem in sequential decision making.
 In this setting,  a learning algorithm is provided with a set of decisions (or arms) with reward distributions unknown to the learner.

### 2017-11-27 Chapter6/notations.tex
Latest on 27/11/2017

@@
-In this paper, $T$ denotes the time horizon.
+Again, to benefit the reader we state the notations used in this chapter.
+$T$ denotes the time horizon.
 $\A$ denotes the set of arms with individual arm is denoted by $i$ such that $i=1,\ldots, K$.
@@
 $n_{i,t_0:t_p}$ denotes the number of times arm $i$ has been pulled from $t_0$ to $t_p$ timesteps.
-$\mu_{i,t_{c_j:c_{j+1}}}$ denotes the expected mean of the reward distribution $D_{i,\rho_{c_j:c_{j+1}}}$ and $\hat{\mu}_{i,t_0:t_p}$ denotes the sample mean for the arm $i$ from $t_0$ to $t_p$ timesteps.
+$r_{i,t_{c_j:c_{j+1}}}$ denotes the expected mean of the reward distribution $D_{i,\rho_{c_j:c_{j+1}}}$ and $\hat{r}_{i,t_0:t_p}$ denotes the sample mean for the arm $i$ from $t_0$ to $t_p$ timesteps.
 
@@
 \begin{align*}
-t_{c_j}& = \min\left\lbrace t\in[1,T],\forall i\in\A : \mu_{i,t_{c_{j-1}:c_j}} \neq \mu_{i,t_{c_{j}:c_{j+1}}}   \right\rbrace\\
+t_{c_j}& = \min\left\lbrace t\in[1,T],\forall i\in\A : r_{i,t_{c_{j-1}:c_j}} \neq r_{i,t_{c_{j}:c_{j+1}}}   \right\rbrace\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{align*}
-\Delta^{chg}_{i,c_j}=|\mu_{i,t_{c_{j-1}:c_j}}-\mu_{i,t_{c_j:c_{j+1}}}|.
+\Delta^{chg}_{i,c_j}=|r_{i,t_{c_{j-1}:c_j}}-r_{i,t_{c_j:c_{j+1}}}|.
 \end{align*}
@@
 \begin{align*}
-\Delta^{opt}_{i,c_j}= \mu_{i^*,t_{c_{j-1}:c_j}}-\mu_{i,t_{c_{j-1}:c_j}}.
+\Delta^{opt}_{i,c_j}= r_{i^*,t_{c_{j-1}:c_j}}-r_{i,t_{c_{j-1}:c_j}}.
 \end{align*}
@@
 
-Also, recall from Definition \ref{Def:chg-gap} that the changepoint gap $\Delta^{chg}_{i,c_j}=|\mu_{i,t_{c_{j-1}:c_j}}-\mu_{i,t_{c_j:c_{j+1}}}|$.
+Also, recall from Definition \ref{Def:chg-gap} that the changepoint gap $\Delta^{chg}_{i,c_j}=|r_{i,t_{c_{j-1}:c_j}}-r_{i,t_{c_j:c_{j+1}}}|$.
 

### 2017-11-27 Chapter6/probDef.tex
Latest on 27/11/2017

@@
 \begin{align*}
-R_{t}=\sum_{t'=1}^t\mu_{i^*_{t'}} - \sum_{t'=1}^t\mu_{I_t'}
-%R_{t}=\sum_{t'=1}^t\mu_{i^*_{t'}} - \sum_{i=1}^K \left(\mu_{i}n_{i_{t'}\neq i^*_{t'},\forall t'=1:t}\right),
+R_{t}=\sum_{t'=1}^t r_{i^*_{t'}} - \sum_{t'=1}^t r_{I_t'}
+%R_{t}=\sum_{t'=1}^t r_{i^*_{t'}} - \sum_{i=1}^K \left(r_{i}n_{i_{t'}\neq i^*_{t'},\forall t'=1:t}\right),
 \end{align*}
-where $t$ is the number of rounds, $\mu_{i^*_{t'}}$ is the optimal arm at the $t'$ timestep and $\mu_{I_{t'}}$ is the arm chosen by the learner at the $t'$ timestep.
+where $t$ is the number of rounds, $r_{i^*_{t'}}$ is the optimal arm at the $t'$ timestep and $r_{I_{t'}}$ is the arm chosen by the learner at the $t'$ timestep.
 Let $n_{i_{t'}\neq i^*_{t'},\forall t'=1:t}$ is the number of times the learner has chosen arm $i$ up to round $t$ when it was not the optimal arm $i^*_{t'}$.
@@
 \begin{align*}
-\E[R_{t}]&= \E\left[\sum_{t'=1}^t\mu_{i^*_{t'}} - \sum_{t'=1}^t\mu_{I_t}\right]\\
+\E[R_{t}]&= \E\left[\sum_{t'=1}^t r_{i^*_{t'}} - \sum_{t'=1}^t\mu_{\mathbb{I}_t'}\right]\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&=\sum_{i\neq i^*}^K\left(\mu_{i^*} - \mu_i\right) \E[n_{i_{t'}\neq i^*_{t'},\forall t'=1:t}] \\
+&=\sum_{i\neq i^*}^K\left(r_{i^*} - r_i\right) \E[n_{i_{t'}\neq i^*_{t'},\forall t'=1:t}] \\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\overset{(a)}{=}\sum_{i\neq i^*}^K\sum_{j=1}^{G}\Delta^{opt}_{i,c_j}\E[n_{i_{t'}\neq i^*_{t'},\forall t'=t_{c_{j-1}}:t_{c_j}}]
+&\overset{(a)}{=}\sum_{i\neq i^*}^K\sum_{j=1}^{G}\Delta^{opt}_{i,c_j}\E[n_{i_{t',c_j}\neq i^*_{t',c_j},\forall t'=t_{c_{j-1}}:t_{c_j}}]
 \end{align*}

### 2017-11-27 Chapter7/ThesisConc.tex
Latest on 27/11/2017

In this thesis, we studied three complex bandit problems, the stochastic multi-armed bandit (SMAB) with the goal of cumulative regret minimization, pure exploration stochastic thresholding bandit problem (TBP) with the goal of expected loss minimization and piecewise stationary bandits with the goal of finding adaptive algorithms which detect and adapts to changepoints. For the first problem, we devised a novel algorithm called Efficient UCB Variance (EUCBV) which enjoys an order optimal regret bound and performs superbly in diverse stochastic environments. In the second part, the thresholding bandit problem, we came up with the novel algorithm called Augmented UCB (AugUCB) which is the first algorithm to use variance estimation for the considered TBP setting and also empirically outperforms most of the other algorithms. Finally, we studied the piecewise stochastic bandits and proposed several solutions for adaptive algorithms that detect changepoints and try to adapt accordingly.

    There are several directions in which the work done in this thesis can be extended. Starting with the SMAB setting, there are many fundamental questions that need to be answered. Though EUCBV reached an order optimal regret bound of $80\sqrt{KT}$, still the constant associated with the bound is quite large and can be reduced by finer analysis. One avenue for future work is to remove the constraint of $T\geq K^{2.4}$ required for EUCBV to reach the order optimal regret bound. Also, EUCBV does not have any asymptotic guarantee and we do not know whether it can reach the \citet{lai1985asymptotically} asymptotic lower bound discussed in chapter \ref{chap:SMAB}. Recently another algorithm called KL-UCB++ \citep{menard2017minimax} has been proved to be both minimax optimal and asymptotically optimal. Further, EUCBV requires the knowledge of horizon as input and it will be interesting to find an anytime version of EUCBV. Similar anytime version of MOSS \citep{degenne2016anytime} and OCUCB \citep{lattimore2016regret} has also been proposed in literature.

    The thresholding bandit problem is also being intensely studied in the bandit community and there are several directions where this work can be extended. One way is to modify the APT algorithm itself and come up with a variance adaptive version of APT. This has bee recently studied in \citet{kano2017good}. Also, currently there are no lower bounds for the TBP setting considering only variance estimation and it will be interesting to derive a lower bound for this setting. Again, whereas APT is an anytime algorithm AugUCB is not anytime and it needs several modifications to obtain an anytime version of AugUCB. Further, we can also derive a gap-independent and gap-dependent bounds for AugUCB as like APT. In \citet{lattimore2015optimally} the authors showed that APT like UCB1 enjoys a gap-dependent cumulative regret bound of $O\left( \dfrac{K\log T}{\Delta^2}\right)$ and gap-independent regret bound of $O\left( \sqrt{KT\log T}\right)$.

    For the piecewise stochastic bandits we were able to show empirically that the adaptive algorithms we considered are indeed more powerful than passive algorithms and further work needs to be done to derive the regret bounds for these algorithms. Specifically for CPD\ref{alg:CPD3} we find the confidence interval obtained by Laplace method as like UCB-$\delta$ algorithm\citep{abbasi2011improved} very promising and more work needs to be done in this aspect.

    Finally, to summarize everything, the bandit community is actively researching several of these open problems discussed here and we hope to answer some of these problems in near future. Further, several interesting variations of the problems discussed here are also being studied such as the Contextual Thresholding Bandit problem, Combinatorial Bandit problems \citep{cesa2012combinatorial} and more powerful algorithms for changepoint detection.

### 2017-11-27 Chapter3/introduction.tex
Latest on 27/11/2017

@@
 Section~\ref{sec:expt} contains results and discussions from our numerical experiments.
-We draw our conclusions in section \ref{sec:conc} and Appendix \ref{sec:app:EUCBV} contains the proofs of the lemmas that have been used for proving the main result.
+We summarize in section \ref{sec:conc} and Appendix \ref{sec:app:EUCBV} contains the proofs of the lemmas that have been used for proving the main result.
 

### 2017-11-27 Chapter4/intro.tex
Latest on 27/11/2017

@@
 In the next section~\ref{tbandit:motivation} we discuss the motivations behind the TBP setting.
-In section~\ref{tbandit:prevRes} we discuss extensively on the various state-of-the-art algorithms available for the pure exploration setting and then in section~\ref{tbandit:prevResAPT} we discuss the latest works done in the TBP setting.
-Finally, we draw our conclusions in section \ref{tbandit:conc}.
+In section~\ref{tbandit:prevRes} we discuss extensively on the various state-of-the-art algorithms available for the pure exploration setting, in section~\ref{tbandit:connection} we draw the connection between pure exploration and thresholding bandit setting and then in section~\ref{tbandit:prevResAPT} we discuss the latest works done in the TBP setting.
+Finally, we summarize in section \ref{tbandit:conc}.

### 2017-11-30 Chapter5/contribution.tex
Latest on 30/11/2017

@@
 
-The remainder of the paper is organized as follows. In section \ref{tbandit:algorithm} we present our AugUCB algorithm. 
-Section \ref{tbandit:results} contains our main theorem on expected loss, while section \ref{tbandit:expt} contains simulation experiments.
+%The remainder of the paper is organized as follows. In section \ref{tbandit:algorithm} we present our AugUCB algorithm. 
+%Section \ref{tbandit:results} contains our main theorem on expected loss, while section \ref{tbandit:expt} contains simulation experiments.
 We finally draw our conclusions in section \ref{tbandit:conclusion}.

### 2017-11-30 Chapter5/intro.tex
Latest on 30/11/2017

@@
 Through our simulation work, we establish that AugUCB, owing to its utilization of variance estimates, performs significantly better than the state-of-the-art APT, CSAR and other non variance-based algorithms.
+
+The rest of the chapter is organized as follows.
+We elaborate our contributions in section~\ref{tbandit:contribution} and  we present the AugUCB algorithm in section~\ref{tbandit:algorithm}.
+Our main theoretical result on expected loss is stated in section~\ref{tbandit:results}.
+Section~\ref{tbandit:expt} contains numerical simulations on various testbeds to show the performance of AugUCB against state-of-the-art algorithms and finally, we summarize in section \ref{tbandit:conclusion}.

### 2017-11-30 Chapter6/contribution.tex
Latest on 30/11/2017

In this chapter, we propose several actively adaptive upper confidence bound algorithms that try to locate the chnagepoints in the distribution and adapt accordingly. Our solution to the piecewise stochastic problem also depends on restarting where we employ a single expert which tries to minimize the cumulative regret by balancing exploration-exploitation and a changepoint detector which tries to predict a changepoint with high probability when the expert is again restarted with all the past history of actions and rewards erased. We give a general framework such that any of algorithms that has been discussed in chapter \ref{chap:SMAB} and chapter \ref{chap:EUCBV} can be employed to minimize the cumulative regret whereas for the changepoint detection we propose three novel algorithms CPD(\ref{alg:CPD1}), CPD(\ref{alg:CPD2}) and CPD(\ref{alg:CPD3}) based on the three dominating ideas of construction on confidence interval, the union bound involving Chernoff-Hoeffding bound (see Appendix \ref{sec:app:Conc}) as in UCB1 \citep{auer2002finite}, the peeling argument as used in MOSS\citep{audibert2009minimax} and DUCB \citep{garivier2011upper} and finally the Laplace method which has been previously explored in UCB-$\delta$ \citep{abbasi2011improved}.

	Also, in contrast to other existing works we take minimal assumption on the environment considered. The three assumptions taken, that is Assumption\ref{assm:global}, Assumption\ref{assm:space-gap} and Assumption\ref{assm:chg-gap} are the standard assumptions taken by all algorithms which is required for detecting significant changes. Furthermore, among the actively adaptive algorithms, CUSUM-UCB requires only Bernoulli rewards whereas our algorithm is applicable to all sub-Gaussian distribution, EXP3.R is more pessimistic compared to our approach as it employs exponential weighting algorithm that does not fully leverage the piecewise stochastic structure of the environment.

	Empirically, we show that SECPD1 and SECPD2 significantly outperforms several algorithms in piecewise stochastic setting. In all the environment considered SECPD1 and SECPD2 performs better than all the passively adaptive algorithms and most of the actively adaptive algorithms. Also, our proposed algorithms does not require any additional exploration parameters to be tuned. Further, both of the proposed algorithms are anytime algorithm which does not require horizon $T$ as input.

### 2017-11-30 Chapter6/intro.tex
Latest on 30/11/2017

--- 2017-11-24 Chapter6/intro.tex
@@
-In this paper, we consider the piece-wise stochastic multi-armed bandit problem, an interesting variation of the stochastic multi-armed bandit problem in sequential decision making.
+In this chapter, we consider the piece-wise stochastic multi-armed bandit problem, an interesting variation of the stochastic multi-armed bandit (SMAB) problem in sequential decision making which was discussed in detail in chapter \ref{chap:SMAB}.
 In this setting,  a learning algorithm is provided with a set of decisions (or arms) with reward distributions unknown to the learner.
@@
 There exist a finite number of changepoints such that the reward distribution of arms changes at those changepoints.
-Given the goal of maximizing the cumulative reward, the learner faces the \textit{exploration-exploitation-changepoint} dilemma, i.e., in each round should the algorithm select the arm which has the highest observed reward so far (\textit{exploitation}), or should the algorithm choose a new arm to gain more knowledge of the expected reward of the arms and thereby avert a sub-optimal greedy decision (\textit{exploration}) and finally keep track of the \textit{changepoints}.
+Given the goal of maximizing the cumulative reward, the learner faces the \textit{exploration-exploitation-changepoint} dilemma, as opposed to the simple \textit{exploration-exploitation} dilemma, i.e., in each round should the algorithm select the arm which has the highest observed reward so far (\textit{exploitation}), or should the algorithm choose a new arm to gain more knowledge of the expected reward of the arms and thereby avert a sub-optimal greedy decision (\textit{exploration}) and finally keep track of the \textit{changepoints} and adapt accordingly.
+
+    The rest of the chapter is organized as follows.
+We first state the notations, definitions, and assumptions required for this setting in section~\ref{psbandit:notations}.
+Then we define our problem statement in section~\ref{psbandit:probDef} and in section~\ref{psbandit:related} we discuss the related works in this setting.
+We elaborate our contributions in section~\ref{psbandit:contribution} and in section~\ref{psbandit:algorithm} we present the changepoint detection algorithms.
+Section~\ref{psbandit:expt} contains numerical simulations where we test our proposed algorithms and finally we summarize in section \ref{psbandit:conclusion}.

### 2017-11-30 Chapter6/notations.tex
Latest on 30/11/2017

@@
 \begin{assumption}
+\label{assm:global}
 In this work we have assumed the global changepoint setting and hence $t_{c_j}$ is common across all the arms and the learner does not know the $t_{c_j},\forall c_j\in\G$. 

### 2017-11-30 Chapter6/related.tex
Latest on 30/11/2017

@@
 Multi-armed bandits (MAB) have been extensively studied in the \textit{stochastic setting} where the distribution associated with each arm is fixed throughout the time horizon.
-Starting from the seminal works of \citet{thompson1933likelihood} and  \citet{robbins1952some} and finally in \citet{lai1985asymptotically} the authors provide the asymptotic lower bound for the class of algorithms considered.
+This setting has been extensively discussed in chapter~\ref{chap:SMAB}.
+Starting from the seminal works of \citet{thompson1933likelihood}, \citet{robbins1952some} and finally in \citet{lai1985asymptotically} the authors provide the asymptotic lower bound for the class of algorithms considered.
 The upper confidence bound (UCB) algorithms, which are a type of index-based frequentist strategy, were first proposed in \citet{agrawal1995sample} and the first finite-time analysis for the stochastic setting for this class of algorithms was proved in \citet{auer2002finite}.
@@
 
-Another setting that has greatly motivated the first studies in bandit literature is the \textit{adversarial setting}.
-In this setting, an adversary chooses the reward for each arm and then the learner selects an arm without the knowledge of the adversary's choice.
+Another setting that has greatly motivated the first studies in bandit literature is the \textit{adversarial setting} which was briefly described in chapter~\ref{chap:intro}.
+In this setting, at every timestep, an adversary chooses the reward for each arm and then the learner selects an arm without the knowledge of the adversary's choice.
 The adversary may or may not be oblivious to the learner's strategy and this forces the learner to employ a randomized algorithm to confuse the adversary.
@@
 Several interesting solutions have been proposed before for this setting which can be broadly divided into two categories, passively adaptive and actively adaptive strategies.
-Passively adaptive strategies like Discounted UCB (DUCB) \citep{kocsis2006discounted}, Switching Window UCB (SW-UCB)  \citep{garivier2011upper} and Discounted Thompson Sampling (DTS) \citep{raj2017taming} do not actively try to locate the changepoints but rather try to minimize their losses by concentrating on past few observations or like Restarting Exp3 (RExp3) \citep{DBLP:journals/corr/BesbesGZ14} behave pessimistically as like Exp3 but restart after pre-determined phases.
+Passively adaptive strategies like Discounted UCB (DUCB) \citep{kocsis2006discounted}, Switching Window UCB (SW-UCB)  \citep{garivier2011upper} and Discounted Thompson Sampling (DTS) \citep{raj2017taming} do not actively try to locate the changepoints but rather try to minimize their losses by concentrating on past few observations.
+Similarly, algorithms like Restarting Exp3 (RExp3) \citep{DBLP:journals/corr/BesbesGZ14} behave pessimistically as like Exp3 but restart after pre-determined phases.
+Hence, RExp3 can also be termed as a passively adaptive algorithm.
 On the other hand, actively adaptive strategies like Adapt-EVE \citep{hartland2007change}, Windowed-Mean Shift \citep{yu2009piecewise}, EXP3.R \citep{allesiardo2017non}, CUSUM-UCB \citep{liu2017change} try to locate the changepoints and restart the chosen bandit algorithms.

### 2017-12-01 Chapter1/intro.tex
Latest on 27/11/2017
Latest on 1/12/2017

@@
-In today's world artificial intelligence has proved to be a game-changer in designing agents that interact with an evolving environment and make decisions on the fly.
+In today's world, artificial intelligence has proved to be a game-changer in designing agents that interact with an evolving environment and make decisions on the fly.
 The main goal of artificial intelligence is to design artificial agents that make dynamic decisions in an evolving environment.
-In pursuit of these the agent can be thought of as making a series of  sequential decisions by interacting with the dynamic environment which provides it with some sort of feedback after every decision which the agent incorporates into its decision-making strategy to formulate the next decision to be made.
+In pursuit of these, the agent can be thought of as making a series of sequential decisions by interacting with the dynamic environment which provides it with some sort of feedback after every decision which the agent incorporates into its decision-making strategy to formulate the next decision to be made.
 A large number of problems in science and engineering, robotics and game playing, resource management, financial portfolio management, medical treatment design, ad placement, website optimization and packet routing can be modeled as sequential decision-making under uncertainty.
@@
 This is the crux of online sequential learning.
+
+    This is in contrast to supervised learning methods that deal with labeled data which are independently and identically distributed (i.i.d.) samples from the considered domain and train some classifier on the entire training dataset to learn the pattern of this distribution to predict the labels of future samples (test dataset) with the assumption that it is sampled from the same domain.
+In contrast to this, an RL agent learns from the samples that are collected from the trajectories generated by its sequential interaction with the system.
+For an RL agent, the trajectory consists of a series of sequential interactions whereby it transitions from one state to another following some dynamics intrinsic to the environment while collecting the reward till some stopping condition is reached.
+This is known as an episode.
+Here, for an action $i_t$ taken by the agent at the $t$-th timestep, the agent transitions from its current state denoted by $S_{i,t}$ to state $S_{i,t+1}$ and observes the reward $X_{i,t}$.
 An illustrative image depicting the reinforcement learning scenario is shown in Figure \ref{fig:rl}.
 
-	This is in contrast to supervised learning methods that deal with labeled data which are independently and identically distributed (i.i.d.) samples from the domain and train some classifier on the entire training dataset to learn the pattern of this distribution to predict future samples (test dataset) with the assumption that it is sampled from the same domain, whereas the RL agent learns from the samples that are collected from the trajectories generated by its sequential interaction with the system.
-For an RL agent the trajectory consists of a series of sequential interactions whereby it transitions from one state to another following some dynamics intrinsic to the environment while collecting the reward till some stopping condition is reached.
-This is known as an episode.
-For a single-step interaction, i.e., when the episode terminates after a single transition, the problem is captured by the multi-armed bandit (MAB) model.
-Our work will focus on this idea of MAB model.
-
 \begin{figure}[!th]
-\includegraphics[scale=0.7]{Chapter1/img/RL.png}
+\includegraphics[scale=0.45]{Chapter1/img/RL1.png}
 \caption{Reinforcement Learning}
@@
 
-%To express an RL problem more formally, we have to define the idea of Markov Decision Process (MDP) which consists of states, actions, transition probabilities and rewards which in turn helps in deciding the strategy to be followed by the agent.
+%To express an RL problem more formally, we have to define the idea of Markov Decision Process (MDP) which consists of states, actions, transition probabilities, and rewards which in turn helps in deciding the strategy to be followed by the agent.
 

### 2017-12-01 connBandits.tex
Latest on 1/12/2017

As defined in the previous section, an episode consist of a series of sequential interaction where as agent transitions from one state to another based on some intrinsic dynamics of the environment while collecting the rewards and choosing actions based on some action-selecting strategy. Now, for a single-step interaction, i.e., when the episode terminates after a single transition, the problem is captured by the multi-armed bandit (MAB) model. Infact the MAB model can be considered as a single looping state when the agent after taking an action, and observing the reward transitions back to the same state.

### 2017-12-01 Chapter1/connBandits.tex

--- 2017-12-01 connBandits.tex
@@
 Infact the MAB model can be considered as a single looping state when the agent after taking an action, and observing the reward transitions back to the same state.
+That single looping state consist of several finite number of actions which are called as arms.
+
+	The name bandit originated from the concept of casino slot machine where there are levers which are called as arms and the learner can pull one lever and observes the reward associated with that arm which is sampled from a distribution associated with the specific arm.
+This game is repeated $T$ times and the goal of the learner is to maximize its profit.

### 2017-12-01 Chapter1/contribution.tex
Latest on 1/12/2017

The main contributions of the thesis are as follows:-
\begin{enumerate}
\item We proposed a novel algorithm for the stochastic multi-armed bandit (MAB) problem. Our proposed Efficient UCB Variance method, referred to as EUCBV is an arm elimination algorithm based on UCB-Improved and UCBV strategy which takes into account the empirical variance of the arms and along with aggressive exploration factors eliminate sub-optimal arms. Through a theoretical analysis, we establish that EUCBV achieves a better gap-dependent regret upper bound than UCB-Improved, MOSS, UCB1, and UCBV algorithms. EUCBV enjoys an order optimal gap-independent regret bound same as that of OCUCB and MOSS, and better than UCB-Improved, UCB1 and UCBV. Empirically, in several considered environments EUCBV outperforms most of the state-of-the-art algorithms.

\item We proposed the Augmented-UCB (AugUCB) algorithm for a fixed-budget version of the thresholding bandit problem (TBP), where the objective is to identify a set of arms whose quality is above a threshold. A key feature of AugUCB is that it uses both mean and variance estimates to eliminate arms that have been sufficiently explored. This is the first algorithm to employ such an approach for the considered TBP. Furthermore, in numerical evaluations we establish in several considered environments that AugUCB outperforms all the algorithms that does not take into consideration the variance of the arms in their action selection strategy.

\item We proposed a general framework of bandit algorithms that combines change-point detection algorithm with aggregation of expert strategies in order to define efficient pulling strategies in context of the piecewise stochastic  distributions. The algorithms that we proposed for the piecewise stochastic setting are actively adaptive algorithms which performs very similarly to the oracle algorithm which has access to the changepoints and suffers no additional delay in adapting to the changing environment. 
\end{enumerate}

### 2017-12-01 Chapter1/objective.tex
Latest on 1/12/2017

@@
-The main objectives of our work.
+The main objectives of the thesis are as follows:-
 \begin{enumerate}
-\item UCB-Improved has several shortfalls.
-It conducts too much early exploration and the arm elimination is very conservative.
-Our proposed algorithm tries to remedy this.
-We also explore the idea of employing clustering techniques in MAB which, till now has only been studied in the contextual bandit setup (see \cite{li2010contextual}, \cite{bui2012clustered}, \cite{cesa2013gang} , \cite{gentile2014online}, \cite{nguyen2014dynamic}).
-We propose an algorithm that minimizes cumulative regret in the multi-armed stochastic bandit setup using clustering and improved exploration and performs at par with the best algorithms currently available.
-We also show that there is a distinct advantage of using clustering in action elimination type of algorithms in MABs.
-\item We also propose an algorithm that minimizes probability of error in a combinatorial stochastic bandit setup whereby the learning algorithm, provided with a threshold $\tau$, proposes the best set of arms such that $r_{i}\geq \tau$ at every timestep using action elimination method.
-This problem is similar to the pure exploration setup with a major difference being that the algorithm has to suggest as many arms whose $r_{i}$ is above $\tau$ which may be more than one arm.
-Our proposed methodology is in contrast with APT which uses an UCB1 type of strategy to suggest the best arms above the threshold whereas we employ an UCB-Improved type of strategy with better exploration parameters.
-\item In both the above scenarios we intend to explore both the theoretical guarantees and empirical performance and verify against the best algorithms available in the field.     
+\item The first objective of this thesis is to study the area of stochastic multi-armed bandit (SMAB) and how to minimize cumulative regret in this setup.
+We intend to give strong gap-dependent and gap-independent regret guarantees in the SMAB setting.
+We also intend to provide algorithm in the SMAB setting that outperforms the current state-of-the-art algorithms in this setting.
+
+\item The second objective of this thesis is to study the area of thresholding bandit problem (TBP) setting where the goal is to minimize the expected loss at the end of a fixed budget provided as input.
+We intend to provide strong guarantees with respect to expected loss and also propose algorithm that does not require any problem complexity as an input.
+We also intend to provide strong empirical evaluations of the algorithm proposed for the TBP setting.
+
+\item The third objective of this thesis is to study the area of piecewise stochastic bandit where again the goal is to minimize the cumulative regret.
+We intend to provide strong algorithms that can adapt to this environment and performs well empirically.
 \end{enumerate}

### 2017-12-01 Chapter1/studyBandit.tex
Latest on 1/12/2017

There are multiple reasons to study the interesting area of bandits. First of all, bandits are the cornerstone of understanding the general reinforcement learning area. Infact, bandits helps us to understand the idea of \textit{exploration-exploitation} dilemma which is the basis to build full, multi-state, general reinforcement learning ideas. Secondly, as stated in \citet{maillard2011apprentissage}, even $50$ years after \cite{robbins1952some} introduced the first idea of bandits, there are many interesting and fruitful areas where bandit concept can be extended in both practical and theoretical terms. Finally, there are several real-life industrial applications ranging from recommendation systems, game theory to anomaly detection where bandit applications have been found to perform exceptionally well. All of these forces us to delve deep into a systemic research of bandits.

### 2017-12-01 Chapter1/types.tex
Latest on 1/12/2017

@@
 In bandit literature, based on the goal we can divide bandits into several categories.
-To illustrate his we put forward a simple scenario let us consider a stochastic bandit scenario where there are $K$ arms labeled $i=1,2,\ldots, K$ with their expected means of reward distributions ($D_i$) be denoted by $r_i$.
+To illustrate this we put forward a simple scenario let us consider a stochastic bandit scenario where there are $K$ arms labeled $i=1,2,\ldots, K$ with their expected means of reward distributions ($D_i$) be denoted by $r_i$.
 Also let there be single optimal arm $*$ such that $r^* = \max_{i\in\A}r_i$.

### 2017-12-01 Chapter3/expts.tex
Latest on 24/11/2017
Latest on 26/11/2017
Latest on 27/11/2017
Latest on 1/12/2017

@@
 The parameters of EUCBV algorithm for all the experiments are set as follows: $\psi=\frac{T}{K^2}$ and $\rho =0.5$ (as in Corollary \ref{Result:Corollary:1}).
-Note that KLUCB+ empirically outperforms KLUCB (as shown in \citet{garivier2011kl}).
+Note that KLUCB+ empirically outperforms KLUCB (see \citet{garivier2011kl}).
 
-\begin{figure}[!h]
+\begin{figure}[!th]
     \centering
@@
 		legend style={font=\Large},
-		ylabel style={yshift=5pt},
+		ylabel style={yshift=12pt},
 		%legend style={legendshift=32pt},
 		}
-        \begin{tikzpicture}[scale=0.6]
+        \begin{tikzpicture}[scale=0.7]
       	\begin{axis}[
@@
 		legend style={font=\Large},
-		ylabel style={yshift=5pt},
+		ylabel style={yshift=12pt},
 		}
-        \begin{tikzpicture}[scale=0.6]
+        \begin{tikzpicture}[scale=0.7]
         \begin{axis}[
@@
 		legend style={font=\Large},
-		ylabel style={yshift=5pt},
+		ylabel style={yshift=12pt},
 		}
-        \begin{tikzpicture}[scale=0.6]
+        \begin{tikzpicture}[scale=0.7]
       	\begin{axis}[

### 2017-12-08 Chapter6/algo1.tex
Latest on 8/12/2017

\subsection{Proposed Algorithms}

In this section, we introduce the an actively adaptive improved changepoint detection algorithm, referred to as ImpCPD as shown in algorithm \ref{alg:ImpCPD}. As discussed before, this algorithm is motivated from UCB-Improved in \citet{auer2010ucb} and is a phase-based algorithm. Further, unlike UCB-Improved which only deals with the exploration-exploitation dilemma, ImpCPD has to handle the exploration-exploitation-changepoint dilemma. In pursuit of this, ImpCPD calls upon an additional sub-routine, the Changpoint-Detection sub-routine in algorithm \ref{alg:CPDI}. This sub-routine is called at the end of every phase to detect the changepoint has occurred or not. Moreover, unlike UCB-Improved, ImpCPD does not pull all arms equally at every timestep, rather between two phases it pulls the arm that maximizes the upper confidence bound as like UCB1 in \citet{auer2002finite}. Also, ImpCPD does not eliminate arms mainly because it deals with a changing environment and it may so happen that for some sub-optimal arm the changepoint is detected very fast and since this is a global changepoint scenario, this helps ImpCPD adapt quickly. Once, the chnagepoint is detected the algorithm restarts as like all the adaptive algorithms by throwing away the past observed data so that the new data from a changed environment is less biased. We also introduce the pseudo arm elimination just like CCB \citep{liu2016modification} algorithm  such that an arm $i$ is never actually eliminated but the active list $B_m$ is just modified to control the phase length.

\begin{algorithm}[!ht]
\caption{Changepoint-Detection-subroutine($m$) (CPDI)}
\label{alg:CPDI}
\begin{algorithmic}
\For{$i=1,..,K$}
\For{$m' = 0 ,\ldots,m$}
\State \If{$\hat{r}_{i,t_0:N_{m'-1}} + \sqrt{\dfrac{\alpha\log(\psi T\epsilon_m^2)}{2n_{i,t_0:N_{m'-1}}}} < \hat{r}_{i,N_{m'-1}:N_{m}} - \sqrt{\dfrac{\alpha\log(\psi T\epsilon_m^2)}{2n_{i,N_{m'-1}:N_{m}}}}$}
\State Return True
\Else{$\hat{r}_{i,t_0:N_{m'-1}} - \sqrt{\dfrac{\alpha\log(\psi T\epsilon_m^2)}{2n_{i,t_0:N_{m'-1}}}} > \hat{r}_{i,N_{m'-1}:N_{m}} + \sqrt{\dfrac{\alpha\log(\psi T\epsilon_m^2)}{2n_{i,N_{m'-1}:N_{m}}}}$}
\State Return True
\EndIf
\EndFor
\EndFor
\end{algorithmic}
\end{algorithm}

\begin{algorithm}[t!]
\caption{ImpCPD}
\label{alg:ImpCPD}
\begin{algorithmic}
\State {\bf Input:} Time horizon $T$; exploration parameter $\alpha$,$\psi$;
\State {\bf Initialization:} $B_{0}=\mathcal{A}$; $m=0$; $\epsilon_{0}=1$;
\begin{align*}
M=\left\lfloor \frac{1}{2}\log_{2} \frac{T}{e}\right\rfloor; \hspace*{2mm};\hspace*{2mm}
\ell_{0}=\left\lceil \dfrac{\log(\psi T\epsilon_{0}^2)}{2\epsilon_{0}} \right\rceil;
\hspace*{2mm}N_{0}=K\ell_{0};t_0 =1; t_p =1.
\end{align*}
\State Pull each arm once
\State \For{$t=K+1,..,T$}
\State Pull arm $j\in\argmin_{i\in\A}\left\lbrace \hat{r}_{i,t_0:t_p} + \sqrt{\dfrac{\alpha\log(\psi T\epsilon_m^2)}{2n_{i,t_0:t_p}}}\right\rbrace$
\State $t:= t+1, t_p := t_p + 1$ 
\State \For{$i\in\A$}
\State \If{$\hat{r}_{i,t_0:t_p} + \sqrt{\dfrac{\alpha\log(\psi T\epsilon_m^2)}{2n_{i,t_0:t_p}}}  < j\in\argmax_{i\in\A}\lbrace\hat{r}_{i,t_0:t_p} - \sqrt{\dfrac{\alpha\log(\psi T\epsilon_m^2)}{2n_{i,t_0:t_p}}}\rbrace$}
\State $|B_m| := |B_m|-1$\hspace*{4mm} (Pseudo arm elimination)
\EndIf
\EndFor
\State \If{$t\geq N_{m}$ and $m \leq M$}
\State \If{CPDI($m$)==True}
\State \textbf{Restart}
\State $B_{m}=\A$; $m=0$; 
\State Set $n_{i,t_0:t_p} = 0, \forall i\in\A$; Set $\hat{r}_{i,t_0:t_p}=0,\forall i\in\A$; $t_0 = 1$; $t_p = 1$;.
\State Pull each arm once
\State \Else{
\State \textbf{Reset Parameters}
\State $\epsilon_{m+1}:=\frac{\epsilon_{m}}{2}$
\State $B_{m+1}:= B_{m}$
\State $\ell_{m+1}:=\left\lceil \dfrac{\log(\psi T\epsilon_{m}^2)}{2\epsilon_{m}} \right\rceil$
\State $N_{m+1}:= t + |B_{m+1}|\ell_{m+1}$
\State $m := m+1$}
\EndIf
\EndIf
\EndFor
\end{algorithmic}
\end{algorithm}

### 2017-12-08 Chapter6/contribution.tex
Latest on 8/12/2017

@@
-In this chapter, we propose several actively adaptive upper confidence bound algorithms that try to locate the chnagepoints in the distribution and adapt accordingly.
-Our solution to the piecewise stochastic problem also depends on restarting where we employ a single expert which tries to minimize the cumulative regret by balancing exploration-exploitation and a changepoint detector which tries to predict a changepoint with high probability when the expert is again restarted with all the past history of actions and rewards erased.
-We give a general framework such that any of algorithms that has been discussed in chapter \ref{chap:SMAB} and chapter \ref{chap:EUCBV} can be employed to minimize the cumulative regret whereas for the changepoint detection we propose three novel algorithms CPD(\ref{alg:CPD1}), CPD(\ref{alg:CPD2}) and CPD(\ref{alg:CPD3}) based on the three dominating ideas of construction on confidence interval, the union bound involving Chernoff-Hoeffding bound (see Appendix \ref{sec:app:Conc}) as in UCB1 \citep{auer2002finite}, the peeling argument as used in MOSS\citep{audibert2009minimax} and DUCB \citep{garivier2011upper} and finally the Laplace method which has been previously explored in UCB-$\delta$ \citep{abbasi2011improved}.
+In this chapter, we propose an actively adaptive upper confidence bound (UCB) algorithm, referred to as Improved Changepoint Detector (ImpCPD), that tries to locate the chnagepoints in the distribution and adapt accordingly to minimize the cumulative regret.
+Our solution to the piecewise stochastic problem also depends on restarting where we employ ImpCPD which tries to minimize the cumulative regret by balancing exploration-exploitation and a changepoint detector which tries to predict a changepoint with high probability.
+When the changepoint is detected ImpCPD is again restarted with all the past history of actions and rewards erased.
+For the changepoint detection we propose a novel algorithm CPDI which works as a subroutine in conjunction with the main ImpCPD algorithm.
+
+%We give a general framework such that any of algorithms that has been discussed in chapter \ref{chap:SMAB} and chapter \ref{chap:EUCBV} can be employed to minimize the cumulative regret whereas
+
+%, CPD(\ref{alg:CPD2}) and CPD(\ref{alg:CPD3}) based on the three dominating ideas of construction on confidence interval, the union bound involving Chernoff-Hoeffding bound (see Appendix \ref{sec:app:Conc}) as in UCB1 \citep{auer2002finite}, the peeling argument as used in MOSS\citep{audibert2009minimax} and DUCB \citep{garivier2011upper} and finally the Laplace method which has been previously explored in UCB-$\delta$ \citep{abbasi2011improved}.
 
@@
 
-	Empirically, we show that SECPD1 and SECPD2 significantly outperforms several algorithms in piecewise stochastic setting.
-In all the environment considered SECPD1 and SECPD2 performs better than all the passively adaptive algorithms and most of the actively adaptive algorithms.
-Also, our proposed algorithms does not require any additional exploration parameters to be tuned.
+	Empirically, we show that ImpCPD significantly outperforms several algorithms in piecewise stochastic setting.
+In all the environment considered ImpCPD performs better than all the passively adaptive algorithms and most of the actively adaptive algorithms.
+
+	%Also, our proposed algorithms does not require any additional exploration parameters to be tuned.
 Further, both of the proposed algorithms are anytime algorithm which does not require horizon $T$ as input.

### 2017-12-08 Chapter6/intro.tex
Latest on 8/12/2017

@@
 We elaborate our contributions in section~\ref{psbandit:contribution} and in section~\ref{psbandit:algorithm} we present the changepoint detection algorithms.
-Section~\ref{psbandit:expt} contains numerical simulations where we test our proposed algorithms and finally we summarize in section \ref{psbandit:conclusion}.
+Section~\ref{psbandit:results} contains our main result, Section~\ref{psbandit:expt} contains numerical simulations where we test our proposed algorithms and finally we summarize in section \ref{psbandit:conclusion}.

### 2017-12-08 Chapter6/mainresult.tex
Latest on 8/12/2017

%\begin{lemma}
%
%\end{lemma}

\begin{theorem}
The expected cumulative regret of ImpCPD algorithm is upper bounded by,
\begin{align*}
\E[R_t] &\leq \sum_{i = 1}^K\sum_{j=1}^{G}\bigg[ 1 
%%%%%%%%%%
+ \dfrac{4T\Delta^{opt}_{i,c_j}\log(\psi T)}{(\psi T)^{\alpha}}\dfrac{M 2^{2\alpha +1}}{(\Delta^{opt}_{i,c_j})^{4\alpha +2}}
%%%%%%%%%%
+ \Delta^{opt}_{i,c_j} + \dfrac{4\log(\psi T(\Delta^{opt}_{i,c_j})^4)}{2(\Delta^{opt}_{i,c_j})}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%
& + \dfrac{2T\Delta^{opt}_{i,c_{j+1}}\log(\psi T)}{(\psi T)^{\alpha}}\dfrac{M 2^{2\alpha + 1}}{(\Delta^{chg}_{i,c_j})^{4\alpha + 2}}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%
&+ \Delta^{opt}_{\max,c_{j+1}} + \dfrac{\Delta^{opt}_{\max,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2\Delta^{chg}_{\epsilon_0,c_j}} + \Delta^{opt}_{i,c_{j+1}} + \dfrac{\Delta^{opt}_{i,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2(\Delta^{chg}_{i,c_j})^2}
\bigg]
\end{align*}

where $\alpha,\psi$ are exploration parameters and $M=\dfrac{1}{2}\log_{2}\dfrac{T}{e}$.
\end{theorem}

\begin{proof}

We proceed as like Theorem 3.1 in \citet{auer2010ucb} and we combine the changepoint detection sub-routine with this.

\textbf{Step 0.(Vital Assumption for proving):} In this proof, we assume that all the changepoints are detected by the algorithm.

\textbf{Step 1.(Define some notations):} In this proof, we define the confidence interval for the $i$-th arm as $s_i=\sqrt{\dfrac{\alpha\log(\psi T\epsilon_m^2)}{n_{i}}}$. The phase numbers are denoted by $m=0,1,\ldots,M$ where $M=\frac{1}{2}\log_{2}\frac{T}{e}$. For the sake of brevity, in this proof we write $n_i$ instead of $n_{i,t_0:t_p}$ denoting only the number of times the arm $i$ is pulled between two restarts, ie, between $t_0$ to $t_p$.

\textbf{Step 2.(Define an optimality stopping phase $m_i$):} We define an optimality stopping phase $m_i$ for a sub-optimal arm $i\in\A$ as the first phase after which the arm $i$ is no longer pulled such that,

\begin{align*}
m_i = \min\left\lbrace m: \sqrt{\alpha\epsilon_{m}} < \dfrac{\Delta^{opt}_{i,c_j}}{4} \right\rbrace
\end{align*}

\textbf{Step 3.(Define a changepoint stopping phase $p_i$):} We define a changepoint stopping phase $p_i$ for an arm $i\in\A$ such that it is the first phase when the changepoint is detected such that,

\begin{align*}
p_i = \min\left\lbrace m: \sqrt{\alpha\epsilon_{m}} < \dfrac{\Delta^{chg}_{i,c_j}}{4} \right\rbrace
\end{align*}

\textbf{Step 4.(Regret for sub-optimal arm $i$ being pulled after $m_i$-th phase):} Note, that on or after the $m_i$-th phase a sub-optimal arm $i$ is not pulled anymore if these four conditions hold,

\begin{eqnarray}
\hat{r}_{i,c_j} < r_{i,c_j} + s_i, \hspace*{2em}  \hat{r}_{i*,c_j} > r_{i*,c_j} - s_{i*}, \hspace*{2em} s_i > s_{i*}, \hspace*{2em} n_i < n_{i*} \label{eq:arm-pull-opt}
\end{eqnarray}

Also, in the $m_i$-th phase if $n_i \geq \ell_{m_i} = \dfrac{\log(\psi T\epsilon_{m_i}^2)}{2\epsilon_{m_i}}$ then we can show that,
\begin{align*}
s_i = \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{m_i}^2)}{2n_{i}}} \leq \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{m_i}^2)}{2\ell_{m_i}}} \leq \sqrt{\alpha\epsilon_{m_i}\dfrac{\log(\psi T\epsilon_{m_i}^2)}{\log(\psi T\epsilon_{m_i}^2)}} \leq \dfrac{\Delta^{opt}_{i,c_j}}{4}.
\end{align*}

If indeed the four conditions in equation \ref{eq:arm-pull-opt} hold then we can show that in the $m_i$-th phase,

\begin{align*}
\hat{r}_{i,c_j} + s_i \leq \hat{r}_{i,c_j} + 4s_i - 2s_i \leq \hat{r}_{i,c_j} + \Delta^{opt}_{i,c_j} - 2s_i \leq \hat{r}_{i*,c_j} - 2s_{i*} \leq \hat{r}_{i*,c_j} - s_{i*}
\end{align*}

Hence, the sub-optimal arm $i$ is no longer pulled on or after the $m_i$-th phase. Therefore, to bound the number of pulls of the sub-optimal arm $i$, we need to bound the probability of the complementary of the four events in equation \ref{eq:arm-pull-chg}.

For the first event in equation \ref{eq:arm-pull-opt}, using Chernoff-Hoeffding bound we can bound the probability of the complementary of that event by,

\begin{align*}
\sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\Pb\lbrace \hat{r}_{i,c_j} \geq  r_{i,c_j} + s_i \rbrace &\leq \sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\exp\left(-2s_i^2n_i \right)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\leq \sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\exp\left(-2\dfrac{\alpha\log(\psi T\epsilon_{m_i}^2)}{2n_i}n_i \right)\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\leq \sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\dfrac{1}{\psi T\epsilon_{m_i}^2} \leq \sum_{m=0}^{m_i}\dfrac{\log(\psi T\epsilon_{m_i}^2)}{2\epsilon_{m_i}}\dfrac{1}{(\psi T\epsilon_{m_i}^2)^{\alpha}} = \dfrac{\log(\psi T)}{2(\psi T)^{\alpha}}\sum_{m=0}^{m_i}\dfrac{1}{\epsilon_{m_i}^{2\alpha +1}}.
\end{align*}

Similarly, for the second event in equation \ref{eq:arm-pull-opt}, we can bound the probability of its complementary event by,

\begin{align*}
\sum_{m=0}^{m_i}\sum_{n_{i*} =1}^{\ell_{m_i}}\Pb\lbrace \hat{r}_{i*,c_j} \leq  r_{i*,c_j} - s_{i*} \rbrace &\leq \sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\exp\left(-2(s_{i*})^2n_{i*} \right)\leq \dfrac{\log(\psi T)}{2(\psi T)^{\alpha}}\sum_{m=0}^{m_i}\dfrac{1}{\epsilon_{m_i}^{2\alpha +1}}.
\end{align*}

Also, for the third event in equation \ref{eq:arm-pull-opt}, we can bound the probability of its complementary event by,

\begin{align*}
\sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\Pb\lbrace s_i < s_{i*}\rbrace \leq \sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\Pb\lbrace n_i > n_{i*}\rbrace \leq \sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\Pb\lbrace \hat{r}_{i,c_j} + s_i > \hat{r}_{i*,c_j} + s_{i*} \rbrace.
\end{align*}

But the event $\hat{r}_{i,c_j} + s_i > \hat{r}_{i*,c_j} + s_i$ is possible only when the following three events occur, $\hat{r}_{i*,c_j} \leq r_{i*,c_j} - s_{i*} , \hat{r}_{i,c_j} \geq r_{i,c_j} + s_i$ and $r_{i*}-r_{i} < 2s_i $. But the third event will not happen for $n_i\geq \ell_{m_i}$. Proceeding as before, we can show that the probability of the remaining two events is bounded by,

\begin{align*}
&\sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\Pb\lbrace s_i < s_{i*}\rbrace \leq \sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\Pb\lbrace n_i > n_{i*}\rbrace \leq \sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\Pb\lbrace \hat{r}_{i,c_j} + s_i > \hat{r}_{i*,c_j} + s_{i*} \rbrace \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
&\leq \sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\left( \Pb\lbrace \hat{r}_{i,c_j} \geq r_{i,c_j} + s_i \rbrace \bigcup \Pb\lbrace \hat{r}_{i*,c_j} \leq r_{i*,c_j} - s_{i*} \rbrace \right)\leq \sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\dfrac{\log(\psi T)}{(\psi T)^{\alpha}}\sum_{m=0}^{m_i}\dfrac{1}{\epsilon_{m_i}^{2\alpha + 1}}.
\end{align*}

Finally for the fourth event in equation \ref{eq:arm-pull-opt}, we can bound the probability of its complementary event by following the same steps as above,

\begin{align*}
\sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\Pb\lbrace n_i > n_{i*}\rbrace \leq \sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\Pb\lbrace r_{i,c_j} + s_i > r_{i*,c_j} + s_{i*} \rbrace \leq \dfrac{\log(\psi T)}{(\psi T)^{\alpha}}\sum_{m=0}^{m_i}\dfrac{1}{\epsilon_{m_i}^{2\alpha +1}}.
\end{align*}

Combining the above four cases we can bound the probability that a sub-optimal arm $i$ will no longer be pulled on or after the $m_i$-th phase by,

\begin{align*}
\dfrac{4\log(\psi T)}{(\psi T)^{\alpha}}\sum_{m=0}^{m_i}\dfrac{1}{\epsilon_{m_i}^{2\alpha +1}}.
\end{align*}

Bounding this trivially by $T\Delta^{opt}_{i,c_j}$ for each arm $i\in\A$ we get the regret suffered for arm $i$ after the $m_i$-th phase  as,

\begin{align*}
\sum_{i\in\A}\left(\dfrac{4T\Delta^{opt}_{i,c_j}\log(\psi T)}{(\psi T)^{\alpha}}\sum_{m=0}^{m_i}\dfrac{1}{\epsilon_{m_i}^{2\alpha +1}}\right) \leq \sum_{i\in\A}\left(\dfrac{4T\Delta^{opt}_{i,c_j}\log(\psi T)}{(\psi T)^{\alpha}}\dfrac{M 2^{2\alpha +1}}{(\Delta^{opt}_{i,c_j})^{4\alpha +2}}\right).
\end{align*}

\textbf{Step 5.(Regret for pulling the sub-optimal arm $i$ on or before $m_i$-th phase):} Either a sub-optimal arm gets pulled $\ell_{m_i}$ number of times till the $m_i$-th phase and after that the probability of it getting pulled is exponentially low (as shown in \textbf{step 4}). Hence, the number of times a sub-optimal arm $i$ is pulled till the $m_i$-th phase is given by,

\begin{align*}
\ell_{m_i} = \left\lceil \dfrac{\log(\psi T\epsilon_{m_i}^2)}{2\epsilon_{m_i}} \right\rceil
\end{align*}

Hence, considering each arm $i\in\A$ the total regret is bounded by,

\begin{align*}
\sum_{i\in\A}\Delta^{opt}_{i,c_j}\left\lceil \dfrac{\log(\psi T\epsilon_{m_i}^2)}{2\epsilon_{m_i}} \right\rceil < \Delta^{opt}_{i,c_j}\left[ 1 + \dfrac{\log(\psi T\epsilon_{m_i}^2)}{2\epsilon_{m_i}} \right] \leq \Delta^{opt}_{i,c_j}\left[ 1 + \dfrac{4\log(\psi T(\Delta^{opt}_{i,c_j})^4)}{2(\Delta^{opt}_{i,c_j})^2}\right].
\end{align*}

\textbf{Step 6.(Regret for not detecting changepoint $c_{j}$ for arm $i$ after the $p_{i}$-th phase):} Proceeding similarly as in \textbf{step 4} we can show that in the $p_i$-th phase for an arm $i$ if $n_{i}\geq\ell_{p_i}$ then,

\begin{align*}
s_i = \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{p_i}^2)}{2n_{i}}} \leq \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{p_i}^2)}{2\ell_{p_i}}} \leq \sqrt{\alpha\epsilon_{p_i}\dfrac{\log(\psi T\epsilon_{p_i}^2)}{\log(\psi T\epsilon_{p_i}^2)}} \leq \dfrac{\Delta^{chg}_{i,c_j}}{4}.
\end{align*}

Furthermore, we can show that if the following two conditions hold for an arm $i$ then the changepoint will definitely get detected, that is,

\begin{eqnarray}
\hat{r}_{i,c_{j-1}} + s_{i} < \hat{r}_{i,c_{j}} - s_{i},\hspace*{4mm} \hat{r}_{i,c_{j-1}} - s_{i} > \hat{r}_{i,c_{j}} + s_{i} \label{eq:arm-pull-chg}.
\end{eqnarray}

Indeed, we can show that if there is a changepoint at $c_j$ such that $r_{i,c_{j-1}} < r_{i,c_j}$ and if the first conditions in equation \ref{eq:arm-pull-chg} hold  in the $p_i$-th phase then,

\begin{align*}
\hat{r}_{i,c_{j-1}} + s_{i} \leq \hat{r}_{i,c_{j-1}} + 4s_{i} - 2s_{i} \leq \hat{r}_{i,c_{j-1}} + \Delta^{chg}_{i,c_j} -2s_{i} \leq \hat{r}_{i,c_{j}} - 2s_i \leq \hat{r}_{i,c_{j}} - s_i.
\end{align*}

Conversely, for the case $r_{i,c_{j-1}} > r_{i,c_j}$ the second condition will hold for the $p_i$-th phase. Now, to bound the regret we need to bound the probability of the complementary of these two events. For the complementary of the first event in equation \ref{eq:arm-pull-chg} by using Chernoff-Hoeffding bound we can show that,

\begin{align*}
&\sum_{m=0}^{p_i}\sum_{n_i=1}^{\ell_{p_i}}\Pb\lbrace \hat{r}_{i,c_{j-1}} \geq  r_{i,c_{j-1}} + s_i \rbrace \leq \sum_{m=0}^{p_i}\sum_{n_i=1}^{\ell_{p_i}}\exp\left(-2s_i^2n_i \right)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\leq \sum_{m=0}^{p_i}\sum_{n_i=1}^{\ell_{p_i}}\exp\left(-2\dfrac{\alpha\log(\psi T\epsilon_{p_i}^2)}{2n_i}n_i \right)\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\leq \sum_{m=0}^{p_i}\sum_{n_i=1}^{\ell_{p_i}}\dfrac{1}{\psi T\epsilon_{p_i}^2} \leq \sum_{m=0}^{p_i}\dfrac{\log(\psi T\epsilon_{p_i}^2)}{2\epsilon_{p_i}}\dfrac{1}{(\psi T)^{\alpha}\epsilon_{p_i}^2} = \dfrac{\log(\psi T)}{2(\psi T)^{\alpha}}\sum_{m=0}^{p_i}\dfrac{1}{\epsilon_{p_i}^{2\alpha + 1}}.
\end{align*}

Also, again by using Chernoff-Hoeffding bound we can show that,

\begin{align*}
\sum_{m=0}^{p_i}\sum_{n_i=\ell_{p_{i-1}}}^{\ell_{p_i}}\Pb\lbrace \hat{r}_{i,c_j} \leq  r_{i,c_j} - s_i \rbrace &\leq \sum_{m=0}^{p_i}\sum_{n_i=\ell_{p_{i-1}}}^{\ell_{p_i}}\exp\left(-2s_i^2n_i \right) \leq \dfrac{\log(\psi T)}{2(\psi T)^{\alpha}}\sum_{m=0}^{p_i}\dfrac{1}{\epsilon_{p_i}^{2\alpha + 1}}.
\end{align*}

Hence, the probability that the changepoint is not detected by the first event is bounded by,
\begin{align*}
\dfrac{\log(\psi T)}{(\psi T)^{\alpha}}\sum_{m=0}^{p_i}\dfrac{1}{\epsilon_{p_i}^{2\alpha + 1}}.
\end{align*}

Similarly, we can bound the probability of the complementary of the second event in equation \ref{eq:arm-pull-chg} as,

\begin{align*}
&\sum_{m=0}^{p_i}\sum_{n_i=1}^{\ell_{p_i}}\Pb\lbrace \hat{r}_{i,c_{j-1}} \leq  r_{i,c_{j-1}} - s_i \rbrace\leq \dfrac{\log(\psi T)}{2(\psi T)^{\alpha}}\sum_{m=0}^{p_i}\dfrac{1}{\epsilon_{p_i}^{2\alpha + 1}} \textbf{,  and  }\\
%%%%%%%%%%%%%%%%%%%%%%%%%
&\sum_{m=0}^{p_i}\sum_{n_i=\ell_{p_{i-1}}}^{\ell_{p_i}}\Pb\lbrace \hat{r}_{i,c_j} \geq  r_{i,c_j} + s_i \rbrace\leq \dfrac{\log(\psi T)}{(\psi T)^{\alpha}}\sum_{m=0}^{p_i}\dfrac{1}{\epsilon_{p_i}^{2\alpha + 1}}.
\end{align*}

Combining the contribution from these two events, we can show that the probability of not detecting the changepoint $c_j$ for the $i$-th arm after the $p_i$-th phase is upper bounded by,

\begin{align*}
\dfrac{2\log(\psi T)}{(\psi T)^{\alpha}}\sum_{m=0}^{p_i}\dfrac{1}{\epsilon_{p_i}^{2\alpha + 1}}.
\end{align*}

Furthermore, bounding the regret trivially (after the changepoint $c_j$) by $\Delta^{opt}_{i,c_{j+1}}$ for each arm $i\in\A$, we get 
\begin{align*}
\sum_{i\in\A}\left(\dfrac{2T\Delta^{opt}_{i,c_{j+1}}\log(\psi T)}{(\psi T)^{\alpha}}\sum_{m=0}^{p_i}\dfrac{1}{\epsilon_{p_i}^{2\alpha + 1}}\right) \leq \sum_{i\in\A}\left(\dfrac{2T\Delta^{opt}_{i,c_{j+1}}\log(\psi T)}{(\psi T)^{\alpha}}\dfrac{M 2^{2\alpha + 1}}{(\Delta^{chg}_{i,c_j})^{4\alpha + 2}}\right).
\end{align*}

\textbf{Step 7.(Regret for not detecting a changepoint $c_{j}$ for arm $i$ on or before the $p_{i}$-th phase):} The regret for not detecting the changepoint $c_j$ on or before the $p_i$-th phase can be broken into two parts, \textbf{(a)} the worst case events from $t_{c_j}$ to $p_{i}$ and \textbf{(b)} the minimum number of pulls $\ell_{p_i}$ required to detect the changepoint. For the first part (a) we can use Assumption \ref{assm:space-gap}, Assumption ref{assm:chg-gap}, Discussion \ref{dis:gap-delay} and Definition \ref{Def:e-chg-gap} to upper bound the regret as,

\begin{align*}
\sum_{i\in\A}\Delta^{opt}_{\max,c_{j+1}}\left\lceil \dfrac{\log(\psi T\epsilon_{p_i}^2)}{2(\Delta^{chg}_{\epsilon_0,c_j})^2} \right\rceil < \Delta^{opt}_{\max,c_{j+1}}\left[ 1 + \dfrac{\log(\psi T\epsilon_{p_i}^2)}{2(\Delta^{chg}_{\epsilon_0,c_j})^2} \right].
\end{align*}

Again, for the second part (b) the arm $i$ can be pulled no more than $\ell_{p_i}$ number of times. Hence, for each arm $i\in\A$  the regret for this case is bounded by,

\begin{align*}
\sum_{i\in\A}\Delta^{opt}_{i,c_{j+1}}\left\lceil \dfrac{\log(\psi T\epsilon_{p_i}^2)}{2\epsilon_{p_i}} \right\rceil <  \Delta^{opt}_{i,c_{j+1}}\left[ 1 + \dfrac{\log(\psi T\epsilon_{p_i}^2)}{2\epsilon_{p_i}} \right].
\end{align*}

Therefor, combining these two parts (a) and (b) we can show that the total regret for not detecting the changepoint till the $p_i$-th phase is given by,

\begin{align*}
&\sum_{i\in\A}\left\lbrace\Delta^{opt}_{\max,c_{j+1}} + \dfrac{\Delta^{opt}_{\max,c_{j+1}}\log(\psi T\epsilon_{p_i}^2)}{2(\Delta^{chg}_{\epsilon_0,c_j})^2} + \Delta^{opt}_{i,c_{j+1}} + \dfrac{\Delta^{opt}_{i,c_{j+1}}\log(\psi T\epsilon_{p_i}^2)}{2\epsilon_{p_i}}\right\rbrace \\
%%%%%%%%%%%%%%%%%%%%%%%%%
&\leq \sum_{i\in\A}\left\lbrace\Delta^{opt}_{\max,c_{j+1}} + \dfrac{\Delta^{opt}_{\max,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2\Delta^{chg}_{\epsilon_0,c_j}} + \Delta^{opt}_{i,c_{j+1}} + \dfrac{\Delta^{opt}_{i,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2(\Delta^{chg}_{i,c_j})^2}\right\rbrace
\end{align*}

\textbf{Step 8.(Final Regret bound):} Combining the assumption in \textbf{Step 0} and from our problem definition we recall that the expected regret till the $T$-th timestep is bounded by,

\begin{align*}
\E[R_{T}]&= \sum_{i = 1}^K\sum_{j=1}^{G}\Delta^{opt}_{i,c_j}\E[n_{i_{t',c_j}\neq i^*_{t',c_j},\forall t'=t_{c_{j-1}}:t_{c_j}}] \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%
& = \sum_{i = 1}^K\sum_{j=1}^{G}\bigg[ 1 
%%%%%%%%%%
+ \underbrace{\dfrac{4T\Delta^{opt}_{i,c_j}\log(\psi T)}{(\psi T)^{\alpha}}\dfrac{M 2^{2\alpha +1}}{(\Delta^{opt}_{i,c_j})^{4\alpha +2}}}_{\textbf{from Step 4}}
%%%%%%%%%%
+ \underbrace{\Delta^{opt}_{i,c_j} + \dfrac{4\log(\psi T(\Delta^{opt}_{i,c_j})^4)}{2(\Delta^{opt}_{i,c_j})}}_{\textbf{from Step 5}}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%
& + \underbrace{\dfrac{2T\Delta^{opt}_{i,c_{j+1}}\log(\psi T)}{(\psi T)^{\alpha}}\dfrac{M 2^{2\alpha + 1}}{(\Delta^{chg}_{i,c_j})^{4\alpha + 2}}}_{\textbf{from Step 6}}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%
&+ \underbrace{ \Delta^{opt}_{\max,c_{j+1}} + \dfrac{\Delta^{opt}_{\max,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2\Delta^{chg}_{\epsilon_0,c_j}} + \Delta^{opt}_{i,c_{j+1}} + \dfrac{\Delta^{opt}_{i,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2(\Delta^{chg}_{i,c_j})^2}}_{\textbf{from Step 7}}
\bigg]
\end{align*}

Hence, we get the main result of the regret bound.

\end{proof}

### 2017-12-08 Chapter6/probDef.tex
Latest on 8/12/2017

@@
-Given the exploration-exploitation-changepoint dilemma, the objective of the learner in the piecewise-stochastic bandit problem is to minimize the cumulative regret until time $t$, which is defined as follows:
+Given the exploration-exploitation-changepoint dilemma, the objective of the learner in the piecewise-stochastic bandit problem is to minimize the cumulative regret until time $T$, which is defined as follows:
 \begin{align*}
-R_{t}=\sum_{t'=1}^t r_{i^*_{t'}} - \sum_{t'=1}^t r_{I_t'}
+R_{T}=\sum_{t'=1}^T r_{i^*_{t'}} - \sum_{t'=1}^T r_{\mathbb{I}_t'}
 %R_{t}=\sum_{t'=1}^t r_{i^*_{t'}} - \sum_{i=1}^K \left(r_{i}n_{i_{t'}\neq i^*_{t'},\forall t'=1:t}\right),
 \end{align*}
-where $t$ is the number of rounds, $r_{i^*_{t'}}$ is the optimal arm at the $t'$ timestep and $r_{I_{t'}}$ is the arm chosen by the learner at the $t'$ timestep.
-Let $n_{i_{t'}\neq i^*_{t'},\forall t'=1:t}$ is the number of times the learner has chosen arm $i$ up to round $t$ when it was not the optimal arm $i^*_{t'}$.
-The expected regret of an algorithm after $t$ rounds can be written as,
+where $T$ is the total number of rounds or horizon, $r_{i^*_{t'}}$ is the optimal arm at the $t'$ timestep and $r_{\mathbb{I}_{t'}}$ is the arm chosen by the learner at the $t'$ timestep.
+Let $n_{i_{t'}\neq i^*_{t'},\forall t'=1:T}$ is the number of times the learner has chosen arm $i$ up to round $T$ when it was not the optimal arm $i^*_{t'}$.
+The expected regret of an algorithm after $T$ rounds can be written as,
 
 \begin{align*}
-\E[R_{t}]&= \E\left[\sum_{t'=1}^t r_{i^*_{t'}} - \sum_{t'=1}^t\mu_{\mathbb{I}_t'}\right]\\
+\E[R_{T}]&= \E\left[\sum_{t'=1}^T r_{i^*_{t'}} - \sum_{t'=1}^t r_{\mathbb{I}_t'}\right]\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&=\sum_{i\neq i^*}^K\left(r_{i^*} - r_i\right) \E[n_{i_{t'}\neq i^*_{t'},\forall t'=1:t}] \\
+&=\sum_{i = 1}^K\left(r_{i^*} - r_i\right) \E[n_{i_{t'}\neq i^*_{t'},\forall t'=1:T}] \\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\overset{(a)}{=}\sum_{i\neq i^*}^K\sum_{j=1}^{G}\Delta^{opt}_{i,c_j}\E[n_{i_{t',c_j}\neq i^*_{t',c_j},\forall t'=t_{c_{j-1}}:t_{c_j}}]
+&\overset{(a)}{=}\sum_{i = 1}^K\sum_{j=1}^{G}\Delta^{opt}_{i,c_j}\E[n_{i_{t',c_j}\neq i^*_{t',c_j},\forall t'=t_{c_{j-1}}:t_{c_j}}]
 \end{align*}

### 2017-12-10 synopsis.tex
Latest on 10/12/2017

\documentclass[MS,synopsis]{iitmdiss}
\usepackage{times}
\usepackage{t1enc}

%\usepackage[dvips]{graphicx}
%\usepackage[hypertex]{hyperref} % hyperlinks for references.
\usepackage{hyperref} % hyperlinks for references.
\usepackage{amsmath} % easier math formulae, align, subequations \ldots
\usepackage{graphicx}
\usepackage{epstopdf}

\usepackage{macros}

\title{A Study on Online Sequential Learning using Bandits}

\author{Subhojyoti Mukherjee}

\date{December 2017}
\department{COMPUTER SCIENCE AND ENGINEERING}

\begin{document}

%\nocite{*}
\maketitle

% The main text will follow from this point so set the page numbering
% to arabic from here on.
\pagenumbering{arabic}
\setcounter{page}{0}
%\newpage
\section{Introduction}
\label{synopsis:intro}
\input{synopsis/intro}

\section{Motivation}
\label{synopsis:motivation}
\input{synopsis/motivation}

\section{Objectives and Scope of Thesis}
\label{synopsis:objThesis}
\input{synopsis/objective}

\section{Contributions of Thesis}
\label{synopsis:contriThesis}
\input{synopsis/contribution}

%\section{Outline of the Thesis}
%\label{synopsis:outline}
%\input{synopsis/outline}
%

\section{Summary of the Research Work}

We divided the research work done into two parts, in the first part we study the stochastic multi-armed bandit setting and propose an order optimal algorithm for this setting. In the second part we study the thresholding bandit problem and propose our solution to this problem. All these have been briefly discussed below.

%and in the third part we study the piecewise stochastic bandit setting and propose  our algorithm for this setting which beats several state-of-the-art algorithms.

\subsection{Efficient UCB Variance: An almost optimal algorithm in Stochastic Multi-Armed Bandit setting}

%\subsubsection{Introduction}
%In this part, we look at the stochastic multi-armed bandit (SMAB) setting and discussed how it is important in the general reinforcement learning setup. We also look at the various state-of-the-art algorithms in the literature for the SMAB setting and discuss the advantages and disadvantages of them. The regret bounds that have been proven for the said algorithms have also been discussed at length and their confidence intervals have also been compared against each other. Also in this part, we provide our solution to the SMAB setting which achieves an almost order-optimal regret bound.

In this part, we deal with the stochastic multi-armed bandit (SMAB) setting. In its classical form, stochastic MABs represent a sequential learning problem where a learner is exposed to a finite set of actions (or arms) and needs to choose one of the actions at each timestep. After choosing (or pulling) an arm the learner receives a reward, which is conceptualized as an independent random draw from stationary distribution associated with the selected arm. Also, note that in SMAB, the distribution associated with each arm is fixed throughout the entire duration of the horizon denoted by $T$. This SMAB formulation is shown in algorithm \ref{alg:SMAB}.

\begin{algorithm}[!th]
\caption{SMAB formulation}
\label{alg:SMAB}
\begin{algorithmic}
\State {\bf Input:} Time horizon $T$, $K$ number of arms with unknown parameters of reward distribution
\State \For{ each timestep $t=1,2,\ldots, T$}
\State The learner chooses an arm $i\in\A$, where $\A$ is the set of arms and $|\A|=K$.
\State The learner observes the reward $X_{i,t}\sim^{i.i.d} D_{i}$ where, $D_{i}$ is the distribution associated with the arm $i$. 
\State \EndFor
\end{algorithmic}
\end{algorithm}

In SMAB setting, the learner seeks to identify the optimal arm as quickly as possible to maximize its rewards. In the pursuit of this, the learner faces the task of balancing exploitation and exploration. In other words, should the learner pull the arm which currently has the best-known estimates (exploit) or explores arms more thoroughly to ensure that a correct decision is being made. This is termed as the \textit{exploration-exploitation dilemma}, one of the fundamental challenges of reinforcement learning.

    The objective of the learner in the SMAB setting is to maximize his rewards or in other words, to minimize the cumulative regret, which is defined as follows:
\begin{align*}
R_{T}=r^{*}T - \sum_{i=1}^{K} r_{i}n_{i}(T),
\end{align*}
where $T$ is the number of timesteps, and  $z_{i}(T)$ is the number of times the algorithm has chosen arm $i$ up to timestep $T$.
The expected regret of an algorithm after $T$ timesteps can be written as,
\begin{align*}
\E[R_{T}]= \sum_{i=1}^{K} \E[n_i (T)] \Delta_i,
\end{align*}
where $\Delta_{i}=r^{*}-r_{i}$ is the gap between the means of the optimal arm and the $i$-th arm. In the theoretical analysis of each algorithm, we try to obtain bounds on this cumulative regret.

%These bounds can be both asymptotic or for a finite horizon. Again, these regret bounds can be either gap-dependent or gap-independent bounds. 
%
%\begin{enumerate}
%\item\textbf{Asymptotic regret bounds:} These type of regret bounds are valid for a large horizon $T$ tending to infinity. In other words, if the guarantees of these bounds to be held true then an infinite number of samples needs to be collected.
%
%\item\textbf{Finite horizon regret bounds:} These type of regret bounds are valid for a finite horizon when a limited number of samples are allowed to be collected. Note, that the knowledge of horizon may or may not be known to the learner.
%
%\item\textbf{Gap-Dependent regret bounds:} In gap-dependent or problem dependent regret bounds the regret is obtained as a measure of the gap $\Delta_{i}=r^{*}-r_{i}$ for an arm $i\in\A$ along with the time horizon and number of arms. It is so called because the regret bound depends explicitly on the means of the arms considered for that environment along with the stated assumptions on the distribution.
%
%\item\textbf{Gap-Independent regret bounds:} In gap-independent regret bound the regret does not contain the gaps and is stated explicitly in terms of the number of arms and the horizon. This is because the regret depends only on the distributional assumption, but not on the means of the arms considered. In fact, gap-independent regret bounds point to something more general and informative. These type of bounds actually give us the maximum possible regret such that no matter what is the policy, there will be an environment on which the policy achieves almost the same regret as the gap-independent regret upper bound. This leads to the notion of minimax regret.
%
%\item\textbf{Minimax regret bounds:} For a finite horizon $T$, $K$ number of arms, for all set of possible policies $\pi_{T,K}$ over $T$ and $K$ and all possible environment class $\mathcal{E}$ the minimax regret is given by,
%\begin{align*}
%R_T(\mathcal{E})=\inf_{\pi\in\pi_{T,K}}\sup_{E\in\mathcal{E}}R_T(\pi,E).
%\end{align*}
%
%Hence, this value is independent of any specific choice of a policy $\pi$ but only depends on $T$, $K$ and $\mathcal{E}$ where the dependence on $K$ is hidden in $\mathcal{E}$.
%\end{enumerate}

\subsubsection{Contributions}

We propose the Efficient-UCB-Variance (henceforth referred to as EUCBV) algorithm for the stochastic MAB setting. EUCBV combines the approach of UCB-Improved \citep{auer2010ucb} , CCB \citep{liu2016modification} and UCBV \citep{audibert2009exploration} algorithms. EUCBV, by virtue of taking into account the empirical variance of the arms, exploration parameters  and non-uniform arm selection (as opposed to UCB-Improved), performs significantly better than the existing algorithms in the stochastic MAB setting. EUCBV outperforms UCBV which also takes into account empirical variance but is less powerful than EUCBV because of the usage of exploration regulatory factor by EUCBV. Also, we carefully design the confidence interval term with the variance estimates along with the pulls allocated to each arm to balance the risk of eliminating the optimal arm against excessive optimism. Theoretically we refine the analysis of \citet{auer2010ucb} and prove that for $T\geq K^{2.4}$ our algorithm is order optimal and achieves a worst case gap-independent regret bound of $O\left( \sqrt{KT} \right)$ which is same as that of MOSS \citep{audibert2009minimax} and OCUCB \citep{lattimore2015optimally} but better than that of UCBV, UCB1 \citep{auer2002finite} and UCB-Improved. Here, $K$ is the total number of arms and $T$ is the total number of available timesteps,  termed as horizon. Also, the gap-dependent regret bound of EUCBV is better than UCB1, UCB-Improved and MOSS but is poorer than OCUCB. However, EUCBV's gap-dependent bound matches OCUCB in the worst case scenario when all the gaps are equal. Through our theoretical analysis we establish the exact values of the exploration parameters for the best performance of EUCBV. Our proof technique is highly generic and can be easily extended to other MAB settings. An illustrative table containing the bounds is provided in Table \ref{tab:comp-bds}.

\begin{table}[t]
\caption{Regret upper bound of different algorithms}
\label{tab:comp-bds}
\begin{center}
\begin{tabular}{|p{5em}|p{12em}|p{7em}|}
\hline
Algorithm  &   \hspace*{1mm}Gap-Dependent & Gap-Independent \\
\hline
\hline
EUCBV		& $O\left( \dfrac{K\sigma_{\max}^{2}\log (\frac{T\Delta^2}{K})}{\Delta}\right)$ & $O\left(\sqrt{KT}\right)$\\
\hline
\hline
UCB1        & $O\left( \dfrac{K\log T}{\Delta} \right)$ & $O\left(\sqrt{KT\log T}\right)$ \\%\midrule
\hline
\hline
UCBV        & $O\left( \dfrac{K\sigma_{\max}^{2}\log T}{\Delta} \right)$ & $O\left(\sqrt{KT\log T}\right)$ \\
\hline
\hline
UCB-Imp 		& $O\left( \dfrac{K\log (T\Delta^2)}{\Delta} \right)$ & $O\left(\sqrt{KT\log K}\right)$ \\%\midrule
\hline
\hline
MOSS	     	& $O\left( \dfrac{K^2\log (T\Delta^2 /K)}{\Delta}\right)$ & $O\left(\sqrt{KT}\right)$\\%\midrule
\hline
\hline
OCUCB     	& $O\left( \dfrac{K\log (T/ H_{i})}{\Delta}\right)$ & $O\left(\sqrt{KT}\right)$\\\midrule
\end{tabular}
\end{center}
%\vspace*{-2em}
\end{table}

Empirically, we show that EUCBV, owing to its estimating the variance of the arms, exploration parameters and non-uniform arm pull, performs significantly better than MOSS, OCUCB, UCB-Improved, UCB1, UCBV, TS \citep{thompson1933likelihood},\citep{agrawal2012analysis}, BU \citep{kaufmann2012bayesian}, DMED \citep{honda2010asymptotically}, KLUCB \citep{garivier2011kl} and Median Elimination \citep{even2006action} algorithms. Note that except UCBV, TS, KLUCB and BU (the last three with Gaussian priors) all the aforementioned algorithms do not take into account the empirical variance estimates of the arms. Also, for the optimal performance of TS, KLUCB and BU one has to have the prior knowledge of the type of distribution, but EUCBV requires no such prior knowledge. EUCBV is the first arm-elimination algorithm that takes into account the variance estimates of the arm for minimizing cumulative regret and thereby answers an open question raised by \citet{auer2010ucb}, where the authors conjectured that an UCB-Improved like arm-elimination algorithm can greatly benefit by taking into consideration the variance of the arms. Also, it is the first algorithm that follows the same proof technique of UCB-Improved and achieves a gap-independent regret bound of $O\left( \sqrt{KT} \right)$ thereby, closing the gap of UCB-Improved which achieved a gap-independent regret bound of $O\left( \sqrt{KT\log K} \right)$.

\subsubsection{The EUCBV algorithm}

\begin{algorithm}[!th]
\caption{EUCBV}
\label{alg:eucbv}
\begin{algorithmic}
\State {\bf Input:} Time horizon $T$, exploration parameters $\rho$ and $\psi$.
\State {\bf Initialization:} Set $m:=0$, $B_{0}:=\mathcal{A}$, $\epsilon_{0}:=1$, $M=\big \lfloor \frac{1}{2}\log_{2} \frac{T}{e}\big\rfloor$, $n_{0}=\big\lceil\frac{\log{(\psi T\epsilon_{0}^{2})}}{2\epsilon_{0}}\big\rceil$ and  $N_{0}=Kn_{0}$.
\State Pull each arm once
\For{$t=K+1,..,T$}	
\State Pull arm $i\in \argmax_{j\in B_{m}}\bigg\lbrace \hat{r}_{j} + \sqrt{\frac{\rho(\hat{v}_{j}+2)\log{(\psi T\epsilon_{m})}}{4 z_{j}}} \bigg\rbrace$, where $z_j$ is the number of times arm $j$ has been pulled.
%\State $t:=t+1$
\ArmElim
\State For each arm $i \in B_{m}$, remove arm $i$ from $B_{m}$ if,
\begin{align*}
 \hat{r}_{i} + & \sqrt{\frac{\rho(\hat{v}_{i}+2)\log{(\psi T\epsilon_{m})}}{4 z_{i}}}  
  < \max_{{j}\in B_{m}}\bigg\lbrace\hat{r}_{j} -\sqrt{\frac{\rho(\hat{v}_{j}+2)\log{(\psi T\epsilon_{m})}}{4 z_{j}}} \bigg\rbrace
\end{align*}
\EndArmElim

\If{$t\geq N_{m}$ and $m\leq M$}
\ResParam
\State $\epsilon_{m+1}:=\frac{\epsilon_{m}}{2}$\vspace{0.5ex}
\State $B_{m+1}:=B_{m}$
\State $n_{m+1}:=\bigg\lceil\frac{\log{(\psi T\epsilon_{m+1}^{2})}}{2\epsilon_{m+1}}\bigg\rceil$
\State $N_{m+1}:=t+|B_{m+1}| n_{m+1}$
\State $m:=m+1$
\EndResParam
\EndIf
\State Stop if $|B_{m}|=1$ and pull ${i}\in B_{m}$ till $T$ is reached.
\EndFor
\end{algorithmic}
%\vspace*{-0.42em}
\end{algorithm}
%\vspace*{-0.42em}

\textbf{The algorithm:} Earlier round-based arm elimination algorithms like Median Elimination \citep{even2006action} and UCB-Improved mainly suffered from two basic problems: \\
\begin{inparaenum}[\bfseries(i)]
\item \textit{Initial exploration:} Both of these algorithms pull each arm equal number of times in each round, and hence waste a significant number of pulls in initial explorations. \\
\item \textit{Conservative arm-elimination:} In UCB-Improved, arms are eliminated conservatively, i.e, only after $\epsilon_{m}<\frac{\Delta_{i}}{2}$, 
% the sub-optimal arm $i$ is discarded with high probability. 
where the quantity $\epsilon_{m}$ is initialized to $1$ and halved after every round. In the worst case scenario when $K$ is large, and the gaps are uniform  ($r_{1}=r_{2}=\cdots=r_{K-1}<r^{*}$) and small this results in very high regret.\\
\end{inparaenum}
%For any round $m$ UCB-Improved pulls all arms $n_{m}=\left\lceil \frac{ 2\log(T\epsilon_{m})}{\epsilon_{m}} \right\rceil$ number of times. The quantity $\epsilon_{m}$ is initialized to $1$ and halved after every round.
\\
	The EUCBV algorithm, which is mainly based on the arm elimination technique of the UCB-Improved algorithm,  remedies these by employing exploration regulatory factor $\psi$ and arm elimination parameter $\rho$ for aggressive elimination of sub-optimal arms. Along with these, similar to CCB \citep{liu2016modification} algorithm, EUCBV uses optimistic greedy sampling whereby at every timestep it only pulls the arm with the highest upper confidence bound rather than pulling all the arms equal number of times in each round. Also, unlike the UCB-Improved, UCB1, MOSS and OCUCB algorithms (which are based on mean estimation) EUCBV employs mean and variance estimates (as in \citet{audibert2009exploration}) for arm elimination. Further, we allow for arm-elimination at every time-step, which is in contrast to the earlier work (e.g., \citet{auer2010ucb}; \citet{even2006action}) where the arm elimination takes place only at the end of the respective exploration rounds.

%	An illustrative flowchart depicting the main steps is shown in Figure \ref{fig:eucbv}.
%	
%\begin{figure}[!th]
%\includegraphics[scale=0.42]{synopsis/img/EUCBV_flow.png}
%\caption{Flowchart of EUCBV algorithm}
%\label{fig:eucbv}
%\end{figure}

\subsubsection{Summary}

Here, we study the Efficient UCB Variance (EUCBV) algorithm which takes into account the empirical variance of the arms and employs aggressive exploration parameters in conjunction with non-uniform arm selection to eliminate sub-optimal arms. Our theoretical analysis conclusively established that EUCBV exhibits an order-optimal gap-independent regret bound of $O\left(\sqrt{KT}\right)$. Empirically, we show that EUCBV performs superbly across diverse experimental settings and outperforms most of the bandit algorithms in an SMAB setup. Our experiments showed that EUCBV is extremely stable for large horizons and performs consistently well across different types of distributions.

\subsection{Augmented UCB for Thresholding Bandits Problem}
%In this part, we study the pure exploration MAB and thresholding bandit (TBP) setting which is a special case of combinatorial pure exploration MAB. We also study the various state-of-the-art algorithms in the literature for the pure-exploration setting and discussed the advantages and disadvantages of them. Then we look at the latest algorithm for the TBP setting. The expected loss that has been proven for the said algorithms have also been discussed at length and their exploration parameters have also been compared against each other. We provide our solution to this TBP setting which uses variance estimation to find the set of arms above the threshold.

In the previous part we studied the stochastic multi-armed bandit (SMAB) setting with the goal of minimizing cumulative regret. In this part we study another setting called pure-exploration multi-armed bandits. Pure-exploration MAB problems are unlike their traditional (exploration vs.\ exploitation)  counterparts, the SMABs, where the  objective is to minimize the cumulative regret. The cumulative regret is the total loss incurred by the learner for not playing the optimal arm throughout the time horizon $T$. 
	In pure-exploration problems a learning algorithm, until time $T$, can invest entirely on exploring the arms without being concerned about the loss incurred while exploring; the objective is to minimize the probability that the arm recommended at time $T$ is not the best arm.  In this chapter, we further consider a combinatorial version of the pure-exploration MAB, called the thresholding bandit problem (TBP).  Here, the learning algorithm is provided with a threshold $\tau$, and the objective, after exploring for $T$ rounds, is to  output all arms $i$ whose $r_{i}$ is above $\tau$. 
It is important to emphasize that the \emph{thresholding} bandit problem is different from the \emph{threshold} bandit setup studied in \cite{abernethy2016threshold}, where the learner receives an unit reward whenever the value of an observation is above a threshold.

Formally, the problem we consider is the following. First, we define the set $S_{\tau}=\lbrace i\in \mathcal{A}: r_{i}\geq \tau \rbrace$. Note that, $S_\tau$ is the set of all arms whose reward mean is greater than threshold $\tau$. Let 
$S_\tau^c$ denote the complement of $S_\tau$, i.e.,  $S_{\tau}^{c}=\lbrace i\in \mathcal{A}: r_{i} < \tau \rbrace$. Next, let $\hat{S}_{\tau}=\hat{S}_{\tau}(T)\subseteq \mathcal{A}$ denote the recommendation of a learning algorithm (under consideration) after $T$ time units of exploration, while $\hat{S}_{\tau}^c$ denotes its complement.

The performance of the learning agent is measured by the accuracy with which it can classify the arms into $S_{\tau}$ and $S_{\tau}^{c}$ after time horizon $T$. Equivalently, using $\mathbb{I}(E)$ to denote the indicator of an event $E$, the \emph{loss} $\mathcal{L}(T)$ is defined as
\begin{align*}
\Ls (T) = \mathbb{I}\big(\lbrace S_{\tau}\cap \hat{S}_{\tau}^{c}\neq \emptyset\rbrace    \cup    \lbrace\hat{S}_{\tau}\cap S_{\tau}^{c}\neq \emptyset\rbrace\big).
\end{align*}			
Finally, the goal of the learning agent is to minimize the expected loss:
\begin{align*}
\E[\Ls(T)] = \Pb\big(\lbrace S_{\tau}\cap \hat{S}_{\tau}^{c} \neq \emptyset \rbrace  \cup   \lbrace \hat{S}_{\tau}\cap S_{\tau}^{c} \neq \emptyset\rbrace\big).
\end{align*}
Note that the expected loss is simply the \emph{probability of mis-classification} (i.e., error), that occurs either if a good arm is rejected or a bad arm is accepted as a good one.

\subsubsection{Contributions}

We propose the Augmented UCB (AugUCB) algorithm for the fixed-budget setting of a specific combinatorial, pure-exploration, stochastic MAB called the thresholding bandit problem. AugUCB essentially combines the approach of UCB-Improved, CCB \citep{liu2016modification} and APT \citep{locatelli2016optimal} algorithms. Our algorithm takes into account the empirical variances of the arms along with mean estimates; to the best of our knowledge this is the first variance-based algorithm for the considered TBP. 
Thus, we also address an open problem discussed in \cite{auer2010ucb} of designing an algorithm that can eliminate arms based on variance estimates. In this regard, note that both CSAR \citep{chen2014combinatorial} and APT are not variance-based algorithms.

\begin{table}[b]
\caption{AugUCB vs.\ State of the art}
\label{tab:regret-bds}
\begin{center}
\begin{tabular}{|p{2.3cm}|p{8.4cm}|}
% \toprule
\hline
Algorithm  & Upper Bound on Expected Loss \\
% \midrule
\hline
\hline
AugUCB      &$ \exp\left(- \dfrac{T}{4096 \log(K\log K)H_{\sigma,2}} + \log\left(2KT\right) \right) $ \\
\hline
\hline
UCBEV		&$\exp\left(-\dfrac{1}{512}\frac{T-2K}{H_{\sigma,1}} + \log\left(6KT\right)\right)$ \\
%\midrule
\hline
\hline
APT         &$\exp\left(-\dfrac{T}{64 H_1}+2\log((\log(T)+1)K)\right)$ \\
% \midrule
\hline
\hline
CSAR		&$\exp\left(-\dfrac{T-K}{72\log(K)H_{CSAR,2}}+2\log(K)\right)$ \\
%\midrule
\hline

%\bottomrule
\end{tabular}
\end{center}
\end{table}

Our theoretical contribution comprises proving an upper bound on the expected loss incurred by AugUCB. In Table \ref{tab:regret-bds} we compare the upper bound on the losses incurred by the various algorithms, including AugUCB. The terms $H_1, H_2$, $H_{CSAR,2}, H_{\sigma,1}$ and $H_{\sigma,2}$ represent various problem complexities. We note that, for all $K\ge 8$, we have
\begin{align*}
\log\left(K\log K\right) H_{\sigma,2} > \log(2K) H_{\sigma,2} \ge H_{\sigma,1}.
\end{align*}

Thus, it follows that the upper bound for UCBEV \citep{gabillon2011multi} is better than that for AugUCB. However, implementation of UCBEV algorithm requires $H_{\sigma,1}$ as input, whose computation is not realistic in practice. In contrast, our AugUCB algorithm requires no such complexity factor as input.

Proceeding with the comparisons, we emphasize that the upper bound for  AugUCB is, in fact, not comparable with that of APT and CSAR; this is because the complexity term $H_{\sigma,2}$ is not explicitly comparable with either $H_1$ or $H_{CSAR,2}$. However, through extensive simulation experiments we find that AugUCB significantly outperforms both APT, CSAR and other non variance-based algorithms. AugUCB also outperforms UCBEV under explorations where non-optimal values of $H_{\sigma,1}$  are used. In particular, we consider experimental scenarios comprising large number of arms, with the variances of arms in $S_\tau$ being large. AugUCB, being variance based, exhibits superior performance under these settings.

\subsubsection{The Augmented UCB algorithm}

\textbf{The algorithm:} The Augmented-UCB (AugUCB) algorithm is presented in Algorithm~\ref{alg:augucb}.
AugUCB is essentially based on the arm elimination method of the UCB-Improved \cite{auer2010ucb}, but adapted to the thresholding bandit setting proposed in \cite{locatelli2016optimal}. However, unlike the UCB improved (which is based on mean estimation) our algorithm employs \emph{variance estimates} (as in \cite{audibert2009exploration}) for arm elimination; to the best of our knowledge this is the first variance-aware  algorithm for the thresholding bandit problem. Further, we allow for arm-elimination at each time-step, which is in contrast to the earlier work (e.g., \cite{auer2010ucb,chen2014combinatorial}) where the arm elimination task is deferred to the end of the respective exploration rounds. The details are presented below.

The active set $B_{0}$ is initialized with all the arms from $\mathcal{A}$. We divide the entire budget $T$ into rounds/phases like in UCB-Improved, CCB, SAR and CSAR. At every time-step AugUCB checks for arm elimination conditions, while updating parameters at the end of each round. As suggested by \cite{liu2016modification} to make AugUCB to overcome too much early exploration, we no longer pull all the arms equal number of times in each round. Instead, we choose an arm in the active set $B_m$ that minimizes $(|\hat{r}_{i} - \tau |-2s_i)$ where 
%$\min_{i\in B_{m}}\big\lbrace |\hat{r}_{i} - \tau | - 2\sqrt{\frac{\rho_v\psi_m \hat{V}_{i} \log ( T \epsilon_{m})}{4 n_{i}} + \frac{\rho_v\psi_m \log{( T\epsilon_{m})}}{4 n_{i}}} \big\rbrace $
\begin{small}
\begin{align*}
s_i & = \sqrt{\frac{\rho\psi_m (\hat{v}_{i}+1) \log ( T \epsilon_{m})}{4 n_{i}}} %+ \frac{\rho\psi_m \log{( T\epsilon_{m})}}{4 n_{i}}}.
\end{align*}
\end{small} 
with $\rho$ being the arm elimination parameter and $\psi_{m}$ being the exploration regulatory factor.
%  in the active set $B_{m}$. 
The above condition ensures that an arm closer to the threshold $\tau$ is pulled; 
%and with suitable choice of $\rho_{\mu}$ and $\rho_v$ we can fine tune the exploration. 
parameter $\rho$ can be used to fine tune the elimination interval.
The choice of exploration factor, $\psi_m$, comes directly from \cite{audibert2010best} and \cite{bubeck2011pure} where it is  stated that in pure exploration setup, the exploring factor must be linear in $T$ (so that an exponentially small probability of error is achieved) rather than being logarithmic in $T$ (which is more suited for minimizing cumulative regret).

\begin{algorithm}[!th]
\caption{AugUCB}
\label{alg:augucb}
\begin{algorithmic}
\State {\bf Input:} Time budget $T$; parameter $\rho$; 
% $\rho_{\mu}$, $\rho_v$ 
  threshold $\tau$
\State {\bf Initialization:} $B_{0}=\mathcal{A}$; $m=0$; $\epsilon_{0}=1$;
\begin{small}
\begin{align*}
M=\left\lfloor \frac{1}{2}\log_{2} \frac{T}{e}\right\rfloor; 
\hspace{2mm}\psi_{0}=\frac{T\epsilon_{0}}{128\Big(\log(\frac{3}{16}K\log K)\Big)^2}; 
\ell_{0}=\left\lceil \frac{2\psi_0\log( T\epsilon_{0})}{\epsilon_{0}} \right\rceil;
\hspace{2mm}N_{0}=K\ell_{0}
\end{align*}
\end{small}
\State Pull each arm once
\vspace{-2mm}
\State \For{$t=K+1,..,T$}
\State Pull arm $j\in\argmin_{i\in B_{m}}\Big\lbrace |\hat{r}_{i} - \tau | - 2s_{i}\Big\rbrace$
% \State where $s_j=\sqrt{\frac{\rho\psi_{m}\hat{v}_{j}\log{( T\epsilon_{m})}}{4 n_{j}} + \frac{\rho\psi_{m} \log{(T\epsilon_{m})}}{4 n_{j}}}$
\State $t\leftarrow t+1$ 
\vspace{-4mm}
\State \For{$i\in B_m$}
\vspace{-4mm}
\State \If{$(\hat{r}_{i} + s_i  < \tau - s_i)$ or $(\hat{r}_{i} - s_i > \tau + s_i)$}
\State $B_m\leftarrow B_m\backslash\{i\}$\hspace{4mm} (Arm deletion)
\EndIf
\EndFor
\vspace{-2mm}
\State \If{$t\geq N_{m}$ and $m \leq M$}
%\ResetParam
\State \textbf{Reset Parameters}
\State $\epsilon_{m+1}\leftarrow\frac{\epsilon_{m}}{2}$
\State $B_{m+1} \leftarrow B_{m}$
\State $\psi_{m+1}\leftarrow \frac{T\epsilon_{m+1}}{128(\log(\frac{3}{16}K\log K))^{2}}$
\State $\ell_{m+1}\leftarrow\left\lceil \frac{2\psi_{m+1}\log( T\epsilon_{m+1})}{\epsilon_{m+1}} \right\rceil$
\State $N_{m+1} \leftarrow t + |B_{m+1}|\ell_{m+1}$
\State $m \leftarrow m+1$
%\EndResetParam
\EndIf
\EndFor
\State \textbf{Output:} $\hat{S}_{\tau}=\lbrace i: \hat{r}_{i}\geq \tau \rbrace$.
\end{algorithmic}
\end{algorithm}

%A simplified illustrative flowchart highlighting the main steps of AugUCB is provided in Figure \ref{fig:augucb}. Also note the similarity between UCB-Improved (Figure \ref{fig:ucbimp}) and AugUCB in this flowchart.
%
%\begin{figure}[!th]
%\includegraphics[scale=0.42]{synopsis/img/AugUCB_flow.png}
%\caption{Flowchart for AugUCB}
%\label{fig:augucb}
%\end{figure}
%

\subsubsection{Summary}
We proposed the AugUCB algorithm for a fixed-budget, pure-exploration TBP. Our algorithm employs both mean and variance estimates for arm elimination. This, to our knowledge is the first variance-based algorithm for the specific TBP that we have considered. We first prove an upper bound on the expected loss incurred by AugUCB. We then conduct simulation experiments to validate the performance of AugUCB. In comparison with APT, CSAR and other non variance-based algorithms, we find that the performance of AugUCB is significantly better. Further, the performance of AugUCB is comparable with UCBEV (which is also variance-based), although the latter exhibits a slightly better performance.  However, UCBEV is not implementable in practice as it requires computing problem complexity, $H_{\sigma,1}$, while AugUCB (requiring no such inputs) can be easily deployed in real-life scenarios.

%Also because of the said condition, like \cite{liu2016modification} we also claim that AugUCB is an anytime algorithm.

%\subsection{Improved Changepoint Detection for Piecewise Stationary Distributions}

\section{Conclusions}
\label{synopsis:Conclusions}
\input{synopsis/ThesisConc}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Bibliography.

%\begin{singlespace}
%\begin{thebibliography}{10}
%\addcontentsline{toc}{section}{Bibliography}
%
%\bibitem{paper1}
%Author 1 and Author 2
%\newblock {\em Paper title}.
%\newblock Journal\ \ {\bf Volume}, Page\ \ (Year).
%\end{thebibliography}
%
%\end{singlespace}

\begin{singlespace}
\bibliographystyle{iitm}
\bibliography{refs}
\end{singlespace}

%%%%%%

\section{Proposed Contents of the Thesis}

In chapter 1 (table \ref{tab:chap1}), we discuss on Reinforcement Learning and its connection to bandits, we give an overview of the various types of bandits available in the literature and also discuss about the main objectives of the thesis and our contributions.

\begin{center}
\begin{table}
\begin{center}
\begin{tabular}{|p{26em}|}
\hline\\
\textbf{1. Introduction to Bandits} \\\hline
1.1 Reinforcement Learning \\
1.2 Connection between Reinforcement Learning and Bandits \\
1.3 Why study Bandits?\\
1.4 Motivation \\
1.5 Types of Information Feedback\\
1.6 Different types of Bandits\\
1.7 Objectives of Thesis\\
1.8 Contributions of Thesis\\
1.9 Outline of the Thesis\\
\hline
\end{tabular}
\end{center}
\caption{Introduction to thesis}
\label{tab:chap1}
\end{table}
\end{center}

In chapter 2 (table \ref{tab:chap2-3}) we give a detailed overview of the stochastic multi-armed bandit model and the latest available algorithms in this setting. In the next chapter 3 (table \ref{tab:chap2-3}) we introduce our algorithm Efficient UCB Variance (EUCBV) for the stochastic multi-armed bandit model. We give theoretical guarantees on the performance of EUCBV and also show in numerical simulations that it indeed performs very well as compared to the state-of-the-art algorithms.

\begin{center}
\begin{table}
\begin{tabular}{p{16em}|p{16em}}
\hline\\
\textbf{2. Stochastic Multi-armed Bandits} & \textbf{3. Efficient UCB Variance: An almost optimal algorithm in SMAB setting}\\\hline
2.1 Introduction to SMAB & 3.1 Introduction\\
2.2 Notations and assumptions & 3.2 Our Contributions\\
2.3 Problem Definition & 3.3 Algorithm: Efficient UCB Variance\\
2.4 Motivation & 3.4 Main Results\\
2.5 Related Work in SMAB & 3.5 Proofs\\
2.6 Summary & 3.6 Experiments\\
& 3.7 Summary\\
& 3.8 Appendix B\\
\hline
\end{tabular}
\caption{Part 1. Stochastic MAB problem}
\label{tab:chap2-3}
\end{table}
\end{center}

In the subsequent chapter 4 (table \ref{tab:chap4-5})  we introduce a new variant of pure exploration multi-armed stochastic bandit called the thresholding bandit problem. We analyze the connections between thresholding bandit problem and pure exploration problem and also discuss several existing algorithms in both the settings that are relevant to carefully analyze the thresholding bandit problem. Then in chapter 5 (table \ref{tab:chap4-5}) we introduce our solution for the thresholding bandit problem, called the Augemented UCB (AugUCB) algorithm. We analyze our algorithm AugUCB and derive theoretical guarantees for it as well as show in numerical experiments that it indeed outperforms several state-of-the-art algorithms in the thresholding bandit setting.

\begin{table}
\begin{tabular}{p{16em}|p{16em}}
\hline\\
\textbf{4. Thresholding Bandits} & \textbf{5. Augmented UCB for Thresholding Bandit Problem}\\\hline
4.1 Introduction to TBP & 5.1 Introduction\\
4.2 Notations and assumptions & 5.2 Our Contributions\\
4.3 Problem Definition & 5.3 Augmented-UCB Algorithm\\
4.4 Motivation & 5.4 Theoretical Results\\
4.5 Related Work in Pure Exploration & 5.5 Numerical Experiments\\
4.6 TBP connection to Pure Exploration & 5.6 Summary\\
4.7 Related Work in TBP &\\
4.8 Summary & \\
\hline
\end{tabular}
\caption{Part 2. Thresholding Bandit Problem}
\label{tab:chap4-5}
\end{table}

Finally, in chapter 6, we conclude with a brief discussion on the work done in the thesis and future directions.

%Finally, in chapter \ref{chap:psbandit} we introduce the piecewise-stochastic bandit model which is a new variant that strides between the stochastic and adversarial setting. We discuss extensively on this setting and also provide our solution to this setting and show in numerical simulations that our solution is very close to the optimal solution.

%\framebox{
%      \vbox{\vspace{2mm}
%%    \hbox to 6.28in { {\bf Improved Changepoint Detection for Piece-wise Stochastic Bandits
%%		\hfill Winter 2017} }
%       \vspace{4mm}
%       \hbox to 6.28in { {\Large \hfill Improved Changepoint Detection for Piece-wise Stochastic Bandits  \hfill} }
%       \vspace{2mm}
%       \hbox to 6.28in { {\it \hfill Subhojyoti Mukherjee, Odalric-Ambrym Maillard \hfill} }
%      \vspace{2mm}}
%   }

%The outline of the thesis is as follows:
%\begin{enumerate}
%\item Introduction to Bandits
%\item Stochastic Multi-armed Bandits
%\item Efficient UCB Variance: An almost optimal algorithm in Stochastic Multi-armed Bandit setting
%\item Thresholding Bandits
%\item Augmented UCB for Thresholding Bandits Problem
%%\item Improved Changepoint Detection for Piecewise Stationary Distributions
%\item Conclusion and Future Direction
%\end{enumerate}

%\vskip 4cm
%%%%%%
\section{Publications}
\subsection{Papers in Refereed Journals}
%\begin{enumerate}
%\item Title \\
%	{\bf Author 1}, Author 2...\\
%	{\it Journal title.}, {\bf Volume}, Page (Year)
%\end{enumerate}
%\begin{enumerate}
%\item Subhojyoti Mukherjee, K.P.~Naveen, Nandan Sudarsanam, and Balaraman Ravindran, ``\textit{Thresholding Bandit with Augmented UCB}'', \newblock{\em Proceedings of the Twenty-Sixth International Joint Conference on
%               Artificial Intelligence, {IJCAI} 2017, Melbourne, Australia, August
%               19-25, 2017,2515-2521}, main conference track.
%\item Subhojyoti Mukherjee, K.P.~Naveen, Nandan Sudarsanam, and Balaraman Ravindran, ``\textit{Efficient UCBV: An Almost Optimal Algorithm using Variance Estimates}'', \newblock{\em To appear in Proceedings of the Thirty-Second Association for the Advancement of Artificial Intelligence, {AAAI} 2018, New Orleans, Louisiana, USA, February 2-7}, main conference track.
%\end{enumerate}

\subsection{Presentations in Conferences}
\begin{enumerate}
\item Presented {\em Thresholding Bandit with Augmented UCB} at the {\bf Twenty-Sixth International Joint Conference on Artificial Intelligence, {IJCAI} 2017}, Melbourne, Australia, August 19-25.
\item To present {\em Efficient UCBV: An Almost Optimal Algorithm using Variance Estimates} at the {\bf To appear in Proceedings of the Thirty-Second Association for the Advancement of Artificial Intelligence, {AAAI} 2018}, New Orleans, Louisiana, USA, February 2-7.
\end{enumerate} 
\end{document}

### 2017-12-10 synopsis/intro.tex
Latest on 10/12/2017

--- 2017-12-01 Chapter1/intro.tex
@@
 \begin{figure}[!th]
-\includegraphics[scale=0.45]{Chapter1/img/RL1.png}
+\includegraphics[scale=0.45]{synopsis/img/RL1.png}
 \caption{Reinforcement Learning}
@@
 
+Now, for a single-step interaction, i.e., when the episode terminates after a single transition, the problem is captured by the multi-armed bandit (MAB) model.
+Infact the MAB model can be considered as a single looping state when the agent after taking an action, and observing the reward transitions back to the same state.
+That single looping state consist of several finite number of actions which are called as arms.
+
+	The name bandit originated from the concept of casino slot machine where there are levers which are called as arms and the learner can pull one lever and observes the reward associated with that arm which is sampled from a distribution associated with the specific arm.
+This game is repeated $T$ times and the goal of the learner is to maximize its profit.
+
 %To express an RL problem more formally, we have to define the idea of Markov Decision Process (MDP) which consists of states, actions, transition probabilities, and rewards which in turn helps in deciding the strategy to be followed by the agent.

### 2017-12-10 synopsis.tex
Latest on 10/12/2017

@@
 
-\begin{center}
-\begin{table}
+%\begin{center}
+\begin{table}[!th]
 \begin{center}
@@
 \end{table}
-\end{center}
+%\end{center}
 
-In chapter 2 (table \ref{tab:chap2-3}) we give a detailed overview of the stochastic multi-armed bandit model and the latest available algorithms in this setting.
-In the next chapter 3 (table \ref{tab:chap2-3}) we introduce our algorithm Efficient UCB Variance (EUCBV) for the stochastic multi-armed bandit model.
+In chapter 2 (table \ref{tab:chap2-3}) we give a detailed overview of the stochastic multi-armed bandit setting and the latest available algorithms in this setting.
+In the next chapter 3 (table \ref{tab:chap2-3}) we introduce our algorithm Efficient UCB Variance (EUCBV) for the stochastic multi-armed bandit setting.
 We give theoretical guarantees on the performance of EUCBV and also show in numerical simulations that it indeed performs very well as compared to the state-of-the-art algorithms.
 
-\begin{center}
-\begin{table}
+\begin{table}[!th]
 \begin{tabular}{p{16em}|p{16em}}
@@
 \end{table}
-\end{center}
 
@@
 
-\begin{table}
+\begin{table}[!th]
 \begin{tabular}{p{16em}|p{16em}}
@@
 
-Finally, in chapter 6, we conclude with a brief discussion on the work done in the thesis and future directions.
+Finally, in chapter 6 (table \ref{tab:chap6}), we conclude with a brief discussion on the work done in the thesis and future directions.
+
+\begin{table}[!th]
+\begin{center}
+\begin{tabular}{|p{16em}|}
+\hline\\
+\textbf{6. Conclusion and Future Direction} \\\hline
+6.1 Conclusion and Future Direction \\
+\hline
+\end{tabular}
+\end{center}
+\caption{Conclusion and Future Direction of thesis}
+\label{tab:chap6}
+\end{table}
 

### 2017-12-10 synopsis.tex
Latest on 10/12/2017

@@
 
+\newpage
+\
+\thispagestyle{empty}
+\clearpage
+
 % The main text will follow from this point so set the page numbering
@@
 \pagenumbering{arabic}
-\setcounter{page}{0}
-%\newpage
+\setcounter{page}{1}
+
+%\afterpage{\null\newpage}
+
 \section{Introduction}
@@
 Also, note that in SMAB, the distribution associated with each arm is fixed throughout the entire duration of the horizon denoted by $T$.
-This SMAB formulation is shown in algorithm \ref{alg:SMAB}.
 
-\begin{algorithm}[!th]
-\caption{SMAB formulation}
-\label{alg:SMAB}
-\begin{algorithmic}
-\State {\bf Input:} Time horizon $T$, $K$ number of arms with unknown parameters of reward distribution
-\State \For{ each timestep $t=1,2,\ldots, T$}
-\State The learner chooses an arm $i\in\A$, where $\A$ is the set of arms and $|\A|=K$.
-\State The learner observes the reward $X_{i,t}\sim^{i.i.d} D_{i}$ where, $D_{i}$ is the distribution associated with the arm $i$. 
-\State \EndFor
-\end{algorithmic}
-\end{algorithm}
+%This SMAB formulation is shown in algorithm \ref{alg:SMAB}.
+%
+%\begin{algorithm}[!th]
+%\caption{SMAB formulation}
+%\label{alg:SMAB}
+%\begin{algorithmic}
+%\State {\bf Input:} Time horizon $T$, $K$ number of arms with unknown parameters of reward distribution
+%\State \For{ each timestep $t=1,2,\ldots, T$}
+%\State The learner chooses an arm $i\in\A$, where $\A$ is the set of arms and $|\A|=K$.
+%\State The learner observes the reward $X_{i,t}\sim^{i.i.d} D_{i}$ where, $D_{i}$ is the distribution associated with the arm $i$. 
+%\State \EndFor
+%\end{algorithmic}
+%\end{algorithm}
 
@@
 This is termed as the \textit{exploration-exploitation dilemma}, one of the fundamental challenges of reinforcement learning.
-
 The objective of the learner in the SMAB setting is to maximize his rewards or in other words, to minimize the cumulative regret, which is defined as follows:
@@
 \end{align*}
-where $\Delta_{i}=r^{*}-r_{i}$ is the gap between the means of the optimal arm and the $i$-th arm. In the theoretical analysis of each algorithm, we try to obtain bounds on this cumulative regret.
+where $\Delta_{i}=r^{*}-r_{i}$ is the gap between the means of the optimal arm and the $i$-th arm.
+
+%In the theoretical analysis of each algorithm, we try to obtain bounds on this cumulative regret.
 
@@
 \EndArmElim
-
 \If{$t\geq N_{m}$ and $m\leq M$}
 \ResParam
-\State $\epsilon_{m+1}:=\frac{\epsilon_{m}}{2}$\vspace{0.5ex}
-\State $B_{m+1}:=B_{m}$
+\State $\epsilon_{m+1}:=\frac{\epsilon_{m}}{2}$; $B_{m+1}:=B_{m}$
 \State $n_{m+1}:=\bigg\lceil\frac{\log{(\psi T\epsilon_{m+1}^{2})}}{2\epsilon_{m+1}}\bigg\rceil$
-\State $N_{m+1}:=t+|B_{m+1}| n_{m+1}$
-\State $m:=m+1$
+\State $N_{m+1}:=t+|B_{m+1}| n_{m+1}$; $m:=m+1$
 \EndResParam
@@
 
-\subsubsection{Summary}
-
-Here, we study the Efficient UCB Variance (EUCBV) algorithm which takes into account the empirical variance of the arms and employs aggressive exploration parameters in conjunction with non-uniform arm selection to eliminate sub-optimal arms.
+%\subsubsection{Summary}
+%
+%Here, we study the Efficient UCB Variance (EUCBV) algorithm which takes into account the empirical variance of the arms and employs aggressive exploration parameters in conjunction with non-uniform arm selection to eliminate sub-optimal arms.
 Our theoretical analysis conclusively established that EUCBV exhibits an order-optimal gap-independent regret bound of $O\left(\sqrt{KT}\right)$.
@@
 
-In the previous part we studied the stochastic multi-armed bandit (SMAB) setting with the goal of minimizing cumulative regret.
-In this part we study another setting called pure-exploration multi-armed bandits.
-Pure-exploration MAB problems are unlike their traditional (exploration vs.\ exploitation)  counterparts, the SMABs, where the  objective is to minimize the cumulative regret.
-The cumulative regret is the total loss incurred by the learner for not playing the optimal arm throughout the time horizon $T$.
+%In the previous part we studied the stochastic multi-armed bandit (SMAB) setting with the goal of minimizing cumulative regret. 
+In this part we study another setting called pure-exploration thresholding multi-armed bandits which are unlike their traditional (exploration vs.\ exploitation)  counterparts, the SMABs, where the  objective is to minimize the cumulative regret.
+%The cumulative regret is the total loss incurred by the learner for not playing the optimal arm throughout the time horizon $T$. 
 In pure-exploration problems a learning algorithm, until time $T$, can invest entirely on exploring the arms without being concerned about the loss incurred while exploring; the objective is to minimize the probability that the arm recommended at time $T$ is not the best arm.
@@
 Next, let $\hat{S}_{\tau}=\hat{S}_{\tau}(T)\subseteq \mathcal{A}$ denote the recommendation of a learning algorithm (under consideration) after $T$ time units of exploration, while $\hat{S}_{\tau}^c$ denotes its complement.
-
 The performance of the learning agent is measured by the accuracy with which it can classify the arms into $S_{\tau}$ and $S_{\tau}^{c}$ after time horizon $T$.
@@
 \hline
-
 %\bottomrule
@@
 In contrast, our AugUCB algorithm requires no such complexity factor as input.
-
 Proceeding with the comparisons, we emphasize that the upper bound for  AugUCB is, in fact, not comparable with that of APT and CSAR; this is because the complexity term $H_{\sigma,2}$ is not explicitly comparable with either $H_1$ or $H_{CSAR,2}$.
@@
 As suggested by \cite{liu2016modification} to make AugUCB to overcome too much early exploration, we no longer pull all the arms equal number of times in each round.
-Instead, we choose an arm in the active set $B_m$ that minimizes $(|\hat{r}_{i} - \tau |-2s_i)$ where
-%$\min_{i\in B_{m}}\big\lbrace |\hat{r}_{i} - \tau | - 2\sqrt{\frac{\rho_v\psi_m \hat{V}_{i} \log ( T \epsilon_{m})}{4 n_{i}} + \frac{\rho_v\psi_m \log{( T\epsilon_{m})}}{4 n_{i}}} \big\rbrace $
-\begin{small}
-\begin{align*}
-s_i & = \sqrt{\frac{\rho\psi_m (\hat{v}_{i}+1) \log ( T \epsilon_{m})}{4 n_{i}}} %+ \frac{\rho\psi_m \log{( T\epsilon_{m})}}{4 n_{i}}}.
-\end{align*}
-\end{small} 
-with $\rho$ being the arm elimination parameter and $\psi_{m}$ being the exploration regulatory factor.
+Instead, we choose an arm in the active set $B_m$ that minimizes $(|\hat{r}_{i} - \tau |-2s_i)$ where $s_i  = \sqrt{\frac{\rho\psi_m (\hat{v}_{i}+1) \log ( T \epsilon_{m})}{4 n_{i}}}$ with $\rho$ being the arm elimination parameter and $\psi_{m}$ being the exploration regulatory factor.
 %  in the active set $B_{m}$. 
@@
 \State \textbf{Reset Parameters}
-\State $\epsilon_{m+1}\leftarrow\frac{\epsilon_{m}}{2}$
-\State $B_{m+1} \leftarrow B_{m}$
-\State $\psi_{m+1}\leftarrow \frac{T\epsilon_{m+1}}{128(\log(\frac{3}{16}K\log K))^{2}}$
-\State $\ell_{m+1}\leftarrow\left\lceil \frac{2\psi_{m+1}\log( T\epsilon_{m+1})}{\epsilon_{m+1}} \right\rceil$
-\State $N_{m+1} \leftarrow t + |B_{m+1}|\ell_{m+1}$
-\State $m \leftarrow m+1$
+\State $\epsilon_{m+1}\leftarrow\frac{\epsilon_{m}}{2}$; $B_{m+1} \leftarrow B_{m}$
+\State $\psi_{m+1}\leftarrow \frac{T\epsilon_{m+1}}{128(\log(\frac{3}{16}K\log K))^{2}}$; $\ell_{m+1}\leftarrow\left\lceil \frac{2\psi_{m+1}\log( T\epsilon_{m+1})}{\epsilon_{m+1}} \right\rceil$
+\State $N_{m+1} \leftarrow t + |B_{m+1}|\ell_{m+1}$; $m \leftarrow m+1$
 %\EndResetParam
@@
 
-\subsubsection{Summary}
-We proposed the AugUCB algorithm for a fixed-budget, pure-exploration TBP.
+%\subsubsection{Summary}
+%We proposed the AugUCB algorithm for a fixed-budget, pure-exploration TBP.
 Our algorithm employs both mean and variance estimates for arm elimination.
@@
 
-Finally, in chapter 6 (table \ref{tab:chap6}), we conclude with a brief discussion on the work done in the thesis and future directions.
+Finally, in chapter 6, we conclude with a brief discussion on the work done in the thesis and future directions.
 
-\begin{table}[!th]
-\begin{center}
-\begin{tabular}{|p{16em}|}
-\hline\\
-\textbf{6. Conclusion and Future Direction} \\\hline
-6.1 Conclusion and Future Direction \\
-\hline
-\end{tabular}
-\end{center}
-\caption{Conclusion and Future Direction of thesis}
-\label{tab:chap6}
-\end{table}
+%(table \ref{tab:chap6})
+%\begin{table}[!th]
+%\begin{center}
+%\begin{tabular}{|p{16em}|}
+%\hline\\
+%\textbf{6. Conclusion and Future Direction} \\\hline
+%6.1 Conclusion and Future Direction \\
+%\hline
+%\end{tabular}
+%\end{center}
+%\caption{Conclusion and Future Direction of thesis}
+%\label{tab:chap6}
+%\end{table}
 

### 2017-12-10 synopsis.tex
Latest on 10/12/2017

@@
 \item Presented {\em Thresholding Bandit with Augmented UCB} at the {\bf Twenty-Sixth International Joint Conference on Artificial Intelligence, {IJCAI} 2017}, Melbourne, Australia, August 19-25.
-\item To present {\em Efficient UCBV: An Almost Optimal Algorithm using Variance Estimates} at the {\bf To appear in Proceedings of the Thirty-Second Association for the Advancement of Artificial Intelligence, {AAAI} 2018}, New Orleans, Louisiana, USA, February 2-7.
+\item To present {\em Efficient UCBV: An Almost Optimal Algorithm using Variance Estimates} at the {\bf Thirty-Second Association for the Advancement of Artificial Intelligence, {AAAI} 2018}, New Orleans, Louisiana, USA, February 2-7.
 \end{enumerate} 

### 2017-12-11 synopsis/intro.tex
Latest on 10/12/2017
Latest on 11/12/2017

@@
 \begin{figure}[!th]
-\includegraphics[scale=0.45]{synopsis/img/RL1.png}
+\begin{center}
+\includegraphics[scale=0.3]{synopsis/img/RL1.png}
 \caption{Reinforcement Learning}
 \label{fig:rl}
+\end{center}
 \end{figure}
@@
 
-	The name bandit originated from the concept of casino slot machine where there are levers which are called as arms and the learner can pull one lever and observes the reward associated with that arm which is sampled from a distribution associated with the specific arm.
+	The name bandit originated from the concept of casino slot machine where there are levers which are termed as arms and the learner can pull one lever and observe the reward associated with that arm which is sampled from a distribution associated with the specific arm.
 This game is repeated $T$ times and the goal of the learner is to maximize its profit.

### 2017-12-11 synopsis/motivation.tex
Latest on 11/12/2017

--- 2017-11-24 Chapter1/motivation.tex
@@
 \begin{enumerate}
-\item \emph{Online Shop Domain:} In the online shop domain \cite{ghavamzadeh2015bayesian}, a retailer aims to maximize profit by sequentially suggesting products to online shopping customers.
+\item \emph{Online Shop Domain:} In the online shop domain \citep{ghavamzadeh2015bayesian}, a retailer aims to maximize profit by sequentially suggesting products to online shopping customers.
 In this scenario, at every timestep, the retailer displays an item to a customer from a pool of items which has the highest probability of being selected by the customer.
@@
 This process is repeated till a pre-specified number of times with the retailer gathering valuable information regarding the customer from this behaviour and modifying its policy to display other items to different customers.
-\item \emph{Medical Treatment Design:} Another interesting domain that MAB model was first studied was for the medical treatment design \cite{thompson1933likelihood},\cite{thompson1935theory}.
+\item \emph{Medical Treatment Design:} Another interesting domain that MAB model was first studied was for the medical treatment design \citep{thompson1933likelihood},\citep{thompson1935theory}.
 Here at every timestep, the learner chooses to administer one out of several treatments sequentially on a stream of patients who are suffering from the same ailment (say).

### 2017-12-11 synopsis.tex
Latest on 10/12/2017
Latest on 11/12/2017

@@
 \textbf{The algorithm:} The Augmented-UCB (AugUCB) algorithm is presented in Algorithm~\ref{alg:augucb}.
-AugUCB is essentially based on the arm elimination method of the UCB-Improved \cite{auer2010ucb}, but adapted to the thresholding bandit setting proposed in \cite{locatelli2016optimal}.
+AugUCB is essentially based on the arm elimination method of the UCB-Improved \citep{auer2010ucb}, but adapted to the thresholding bandit setting proposed in \cite{locatelli2016optimal}.
 However, unlike the UCB improved (which is based on mean estimation) our algorithm employs \emph{variance estimates} (as in \cite{audibert2009exploration}) for arm elimination; to the best of our knowledge this is the first variance-aware  algorithm for the thresholding bandit problem.
@@
 
-Finally, in chapter 6, we conclude with a brief discussion on the work done in the thesis and future directions.
+Finally, in chapter 6, we conclude with a brief summarization on the work done in the thesis and discuss future directions.
 

### 2017-12-11 synopsis.tex
Latest on 11/12/2017

@@
 AugUCB is essentially based on the arm elimination method of the UCB-Improved \citep{auer2010ucb}, but adapted to the thresholding bandit setting proposed in \cite{locatelli2016optimal}.
-However, unlike the UCB improved (which is based on mean estimation) our algorithm employs \emph{variance estimates} (as in \cite{audibert2009exploration}) for arm elimination; to the best of our knowledge this is the first variance-aware  algorithm for the thresholding bandit problem.
+However, unlike the UCB-Improved (which is based on mean estimation) our algorithm employs \emph{variance estimates} (as in \cite{audibert2009exploration}) for arm elimination; to the best of our knowledge this is the first variance-aware  algorithm for the thresholding bandit problem.
 Further, we allow for arm-elimination at each time-step, which is in contrast to the earlier work (e.g., \cite{auer2010ucb,chen2014combinatorial}) where the arm elimination task is deferred to the end of the respective exploration rounds.
@@
 In chapter 1 (table \ref{tab:chap1}), we discuss on Reinforcement Learning and its connection to bandits, we give an overview of the various types of bandits available in the literature and also discuss about the main objectives of the thesis and our contributions.
+Appendix A provides some useful results on Concentration inequalities.
 
@@
 1.9 Outline of the Thesis\\
+2.0 Appendix A\\
 \hline

### 2017-12-11 synopsis.tex
Latest on 11/12/2017

@@
 1.9 Outline of the Thesis\\
-2.0 Appendix A\\
+1.A Appendix A\\
 \hline
@@
 & 3.7 Summary\\
-& 3.8 Appendix B\\
+& 3.B Appendix B\\
 \hline

### 2017-12-11 Chapter6/intro.tex
Latest on 11/12/2017

--- 2017-11-30 Chapter6/intro.tex
@@
 We elaborate our contributions in section~\ref{psbandit:contribution} and in section~\ref{psbandit:algorithm} we present the changepoint detection algorithms.
-Section~\ref{psbandit:expt} contains numerical simulations where we test our proposed algorithms and finally we summarize in section \ref{psbandit:conclusion}.
+Section~\ref{psbandit:results} contains our main result, section~\ref{psbandit:expt} contains numerical simulations where we test our proposed algorithms and finally we summarize in section \ref{psbandit:conclusion}.

### 2017-12-11 Chapter6/notations.tex
Latest on 8/12/2017
Latest on 11/12/2017

@@
 We assume all rewards are bounded in $[0,1]$.
-$n_{i,t_0:t_p}$ denotes the number of times arm $i$ has been pulled from $t_0$ to $t_p$ timesteps.
-$r_{i,t_{c_j:c_{j+1}}}$ denotes the expected mean of the reward distribution $D_{i,\rho_{c_j:c_{j+1}}}$ and $\hat{r}_{i,t_0:t_p}$ denotes the sample mean for the arm $i$ from $t_0$ to $t_p$ timesteps.
+$n_{i,t_0:t}$ denotes the number of times arm $i$ has been pulled from $t_0$ to $t$ timesteps.
+$r_{i,t_{c_j:c_{j+1}}}$ denotes the expected mean of the reward distribution $D_{i,\rho_{c_j:c_{j+1}}}$ and $\hat{r}_{i,t_0:t}$ denotes the sample mean for the arm $i$ from $t_0$ to $t$ timesteps.
 
@@
 Thus, assumption \ref{assm:space-gap} makes sure that all the changepoints $t_{c_j},\forall j=1,2,\ldots,G$ are sufficiently far apart to detect a change.
-A good learner tries to minimize the delay ($d$) in detection of a changepoint at $t_{c_j},\forall c_{j}\in\G$ by achieving atmost a delay of $d\left(t_{c_j} - t_{c_{j-1}}\right) \leq O\left( \dfrac{\log( t_{c_j} - t_{c_{j-1}} )}{\Delta_{i,c_j}^{2}}\right)$.
-Note, that when the gaps are same such that for all $i\in\A$, $\Delta_{i,c_j}^{chg}=\Delta_{\epsilon_0,c_j}^{chg}$ and $d\left(t_{c_j} - t_{c_{j-1}}\right) = \left( \dfrac{\log( t_{c_j} - t_{c_{j-1}} )}{\Delta_{\epsilon_0,c_j}^{2}}\right)$, then due to assumption \ref{assm:space-gap} we get,
+A good learner tries to minimize the delay ($d$) in detection of a changepoint at $t_{c_j},\forall c_{j}\in\G$ by achieving atmost a delay of $d\left(t_{c_j} - t_{c_{j-1}}\right) \leq O\left( \dfrac{\log( t_{c_j} - t_{c_{j-1}} )}{(\Delta^{chg}_{i,c_j})^{2}}\right)$.
+Note, that when the gaps are same such that for all $i\in\A$, $\Delta_{i,c_j}^{chg}=\Delta_{\epsilon_0,c_j}^{chg}$ and $d\left(t_{c_j} - t_{c_{j-1}}\right) = \left( \dfrac{\log( t_{c_j} - t_{c_{j-1}} )}{(\Delta^{chg}_{\epsilon_0,c_j})^{2}}\right)$, then due to assumption \ref{assm:space-gap} we get,
 \begin{align*}
-\Delta_{\epsilon_0,c_j}^{chg}\geq \sqrt{\dfrac{1-\epsilon_0}{\epsilon_0}\dfrac{\log(t_{c_j} - t_{c_{j-1}})}{(t_{c_{j+1}} - t_{c_{j}})}}.
+\Delta_{\epsilon_0,c_j}^{chg}\geq \sqrt{\left(\dfrac{1-\epsilon_0}{\epsilon_0}\right)\dfrac{\log(t_{c_j} - t_{c_{j-1}})}{(t_{c_{j+1}} - t_{c_{j}})}}.
 \end{align*}
@@
 \begin{align*}
-\Psi_{i,c_j} = \dfrac{\Delta^{opt}_{i,c_{j+1}}}{\Delta^{chg}_{i,c_j}}
+\Psi_{i,c_j} = \dfrac{\Delta^{opt}_{i,c_{j}}}{\Delta^{chg}_{i,c_j}}
 \end{align*}

### 2017-12-11 Chapter6/probDef.tex
Latest on 11/12/2017

@@
 where $T$ is the total number of rounds or horizon, $r_{i^*_{t'}}$ is the optimal arm at the $t'$ timestep and $r_{\mathbb{I}_{t'}}$ is the arm chosen by the learner at the $t'$ timestep.
-Let $n_{i_{t'}\neq i^*_{t'},\forall t'=1:T}$ is the number of times the learner has chosen arm $i$ up to round $T$ when it was not the optimal arm $i^*_{t'}$.
+Let $n_{i_{t'}\neq i^*_{t'},\forall t'=1:T}$ is the number of times the learner has chosen arm $i_{t'}$ up to round $T$ when it was not the optimal arm $i^*_{t'}$.
 The expected regret of an algorithm after $T$ rounds can be written as,
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&=\sum_{i = 1}^K\left(r_{i^*} - r_i\right) \E[n_{i_{t'}\neq i^*_{t'},\forall t'=1:T}] \\
+&=\sum_{i = 1}^K\left(r_{i^*_{t'}} - r_{i_{t'}}\right) \E[n_{i_{t'}\neq i^*_{t'},\forall t'=1:T}] \\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{align*}
-where $(a)$ is obtained from assumption \ref{assm:chg-gap} and $\Delta^{opt}_{i,c_j}$ is defined as in Definition \ref{Def:opt-gap}.
+where $(a)$ is obtained from Assumption \ref{assm:chg-gap} and $\Delta^{opt}_{i,c_j}$ is defined as in Definition \ref{Def:opt-gap}.

### 2017-12-11 Chapter6/mainresult.tex
Latest on 11/12/2017

@@
 \begin{theorem}
+\label{psbandit:Theorem:1}
 The expected cumulative regret of ImpCPD algorithm is upper bounded by,
@@
 %%%%%%%%%%
-+ \dfrac{4T\Delta^{opt}_{i,c_j}\log(\psi T)}{(\psi T)^{\alpha}}\dfrac{M 2^{2\alpha +1}}{(\Delta^{opt}_{i,c_j})^{4\alpha +2}}
++ \dfrac{4T^{\frac{3}{2}}\Delta^{opt}_{i,c_j}\log(\psi T (\Delta^{opt}_{i,c_j})^4)}{(\psi)^{\alpha}}
 %%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-& + \dfrac{2T\Delta^{opt}_{i,c_{j+1}}\log(\psi T)}{(\psi T)^{\alpha}}\dfrac{M 2^{2\alpha + 1}}{(\Delta^{chg}_{i,c_j})^{4\alpha + 2}}\\
+& + \dfrac{2T^{\frac{3}{2}}\Delta^{opt}_{i,c_{j+1}}\log(\psi T (\Delta^{chg}_{i,c_j})^4)}{(\psi)^{\alpha}}\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-&+ \Delta^{opt}_{\max,c_{j+1}} + \dfrac{\Delta^{opt}_{\max,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2\Delta^{chg}_{\epsilon_0,c_j}} + \Delta^{opt}_{i,c_{j+1}} + \dfrac{\Delta^{opt}_{i,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2(\Delta^{chg}_{i,c_j})^2}
+&+ \Delta^{opt}_{\max,c_{j+1}} + \dfrac{\Delta^{opt}_{\max,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2(\Delta^{chg}_{\epsilon_0,c_j})^2} + \Delta^{opt}_{i,c_{j+1}} + \dfrac{\Delta^{opt}_{i,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2(\Delta^{chg}_{i,c_j})^2}
 \bigg]
@@
 
-where $\alpha,\psi$ are exploration parameters and $M=\dfrac{1}{2}\log_{2}\dfrac{T}{e}$.
+where $\alpha,\psi$ are exploration parameters and $\Delta^{opt}_{i,c_{G+1}} = 0,\forall i\in\A$.
 \end{theorem}
@@
 
-\textbf{Step 2.(Define an optimality stopping phase $m_i$):} We define an optimality stopping phase $m_i$ for a sub-optimal arm $i\in\A$ as the first phase after which the arm $i$ is no longer pulled such that,
+\textbf{Step 2.(Define an optimality stopping phase $m_{i,c_j}$):} We define an optimality stopping phase $m_{i,c_j}$ for a sub-optimal arm $i\in\A$ as the first phase after which the arm $i$ is no longer pulled till the $c_j$-th changepoint is detected such that,
 
 \begin{align*}
-m_i = \min\left\lbrace m: \sqrt{\alpha\epsilon_{m}} < \dfrac{\Delta^{opt}_{i,c_j}}{4} \right\rbrace
+m_{i,c_j} = \min\left\lbrace m: \sqrt{\alpha\epsilon_{m}} < \dfrac{\Delta^{opt}_{i,c_j}}{4} \right\rbrace
 \end{align*}
 
-\textbf{Step 3.(Define a changepoint stopping phase $p_i$):} We define a changepoint stopping phase $p_i$ for an arm $i\in\A$ such that it is the first phase when the changepoint is detected such that,
+\textbf{Step 3.(Define a changepoint stopping phase $p_{i,c_j}$):} We define a changepoint stopping phase $p_{i,c_j}$ for an arm $i\in\A$ such that it is the first phase when the changepoint $c_j$ is detected such that,
 
 \begin{align*}
-p_i = \min\left\lbrace m: \sqrt{\alpha\epsilon_{m}} < \dfrac{\Delta^{chg}_{i,c_j}}{4} \right\rbrace
+p_{i,c_j} = \min\left\lbrace m: \sqrt{\alpha\epsilon_{m}} < \dfrac{\Delta^{chg}_{i,c_j}}{4} \right\rbrace
 \end{align*}
 
-\textbf{Step 4.(Regret for sub-optimal arm $i$ being pulled after $m_i$-th phase):} Note, that on or after the $m_i$-th phase a sub-optimal arm $i$ is not pulled anymore if these four conditions hold,
+\textbf{Step 4.(Regret for sub-optimal arm $i$ being pulled after $m_{i,c_j}$-th phase):} Note, that on or after the $m_{i,c_j}$-th phase a sub-optimal arm $i$ is not pulled anymore if these four conditions hold,
 
@@
 
-Also, in the $m_i$-th phase if $n_i \geq \ell_{m_i} = \dfrac{\log(\psi T\epsilon_{m_i}^2)}{2\epsilon_{m_i}}$ then we can show that,
+Also, in the $m_{i,c_j}$-th phase if $n_i \geq \ell_{m_{i,c_j}} = \dfrac{\log(\psi T\epsilon_{m_{i,c_j}}^2)}{2\epsilon_{m_{i,c_j}}}$ then we can show that,
 \begin{align*}
-s_i = \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{m_i}^2)}{2n_{i}}} \leq \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{m_i}^2)}{2\ell_{m_i}}} \leq \sqrt{\alpha\epsilon_{m_i}\dfrac{\log(\psi T\epsilon_{m_i}^2)}{\log(\psi T\epsilon_{m_i}^2)}} \leq \dfrac{\Delta^{opt}_{i,c_j}}{4}.
+s_i = \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{m_{i,c_j}}^2)}{2n_{i}}} \leq \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{m_{i,c_j}}^2)}{2\ell_{m_{i,c_j}}}} \leq \sqrt{\alpha\epsilon_{m_{i,c_j}}\dfrac{\log(\psi T\epsilon_{m_{i,c_j}}^2)}{\log(\psi T\epsilon_{m_{i,c_j}}^2)}} \leq \dfrac{\Delta^{opt}_{i,c_j}}{4}.
 \end{align*}
 
-If indeed the four conditions in equation \ref{eq:arm-pull-opt} hold then we can show that in the $m_i$-th phase,
+If indeed the four conditions in equation \ref{eq:arm-pull-opt} hold then we can show that in the $m_{i,c_j}$-th phase,
 
 \begin{align*}
-\hat{r}_{i,c_j} + s_i \leq \hat{r}_{i,c_j} + 4s_i - 2s_i \leq \hat{r}_{i,c_j} + \Delta^{opt}_{i,c_j} - 2s_i \leq \hat{r}_{i*,c_j} - 2s_{i*} \leq \hat{r}_{i*,c_j} - s_{i*}
+\hat{r}_{i,c_j} + s_i \leq {r}_{i,c_j} + 4s_i - 2s_i \leq {r}_{i,c_j} + \Delta^{opt}_{i,c_j} - 2s_i \leq {r}_{i*,c_j} - 2s_{i*} \leq \hat{r}_{i*,c_j} - s_{i*}
 \end{align*}
 
-Hence, the sub-optimal arm $i$ is no longer pulled on or after the $m_i$-th phase.
+Hence, the sub-optimal arm $i$ is no longer pulled on or after the $m_{i,c_j}$-th phase.
 Therefore, to bound the number of pulls of the sub-optimal arm $i$, we need to bound the probability of the complementary of the four events in equation \ref{eq:arm-pull-chg}.
@@
 \begin{align*}
-\sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\Pb\lbrace \hat{r}_{i,c_j} \geq  r_{i,c_j} + s_i \rbrace &\leq \sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\exp\left(-2s_i^2n_i \right)
+&\sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace \hat{r}_{i,c_j} \geq  r_{i,c_j} + s_i \rbrace \leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\exp\left(-2s_i^2n_i \right)
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\leq \sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\exp\left(-2\dfrac{\alpha\log(\psi T\epsilon_{m_i}^2)}{2n_i}n_i \right)\\
+\leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\exp\left(-2\dfrac{\alpha\log(\psi T\epsilon_{m_{i,c_j}}^2)}{2n_i}n_i \right)\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\leq \sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\dfrac{1}{\psi T\epsilon_{m_i}^2} \leq \sum_{m=0}^{m_i}\dfrac{\log(\psi T\epsilon_{m_i}^2)}{2\epsilon_{m_i}}\dfrac{1}{(\psi T\epsilon_{m_i}^2)^{\alpha}} = \dfrac{\log(\psi T)}{2(\psi T)^{\alpha}}\sum_{m=0}^{m_i}\dfrac{1}{\epsilon_{m_i}^{2\alpha +1}}.
+&\leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\dfrac{1}{\psi T\epsilon_{m_{i,c_j}}^2} \leq \sum_{m=0}^{m_{i,c_j}}\dfrac{\log(\psi T\epsilon_{m_{i,c_j}}^2)}{2\epsilon_{m_{i,c_j}}}\dfrac{1}{(\psi T\epsilon_{m_{i,c_j}}^2)^{\alpha}} = \dfrac{\log(\psi T \epsilon_{m_{i,c_j}}^2)}{2(\psi T)^{\alpha}}\sum_{m=0}^{m_{i,c_j}}\dfrac{1}{\epsilon_{m_{i,c_j}}^{2\alpha +1}}.
 \end{align*}
@@
 \begin{align*}
-\sum_{m=0}^{m_i}\sum_{n_{i*} =1}^{\ell_{m_i}}\Pb\lbrace \hat{r}_{i*,c_j} \leq  r_{i*,c_j} - s_{i*} \rbrace &\leq \sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\exp\left(-2(s_{i*})^2n_{i*} \right)\leq \dfrac{\log(\psi T)}{2(\psi T)^{\alpha}}\sum_{m=0}^{m_i}\dfrac{1}{\epsilon_{m_i}^{2\alpha +1}}.
+\sum_{m=0}^{m_{i,c_j}}\sum_{n_{i*} =1}^{\ell_{m_{i,c_j}}}\Pb\lbrace \hat{r}_{i*,c_j} \leq  r_{i*,c_j} - s_{i*} \rbrace &\leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\exp\left(-2(s_{i*})^2n_{i*} \right)\leq \dfrac{\log(\psi T \epsilon_{m_{i,c_j}}^2)}{2(\psi T)^{\alpha}}\sum_{m=0}^{m_i}\dfrac{1}{\epsilon_{m_i}^{2\alpha +1}}.
 \end{align*}
@@
 \begin{align*}
-\sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\Pb\lbrace s_i < s_{i*}\rbrace \leq \sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\Pb\lbrace n_i > n_{i*}\rbrace \leq \sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\Pb\lbrace \hat{r}_{i,c_j} + s_i > \hat{r}_{i*,c_j} + s_{i*} \rbrace.
+\sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace s_i < s_{i*}\rbrace \leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace n_i > n_{i*}\rbrace \leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace \hat{r}_{i,c_j} + s_i > \hat{r}_{i*,c_j} + s_{i*} \rbrace.
 \end{align*}
@@
 But the event $\hat{r}_{i,c_j} + s_i > \hat{r}_{i*,c_j} + s_i$ is possible only when the following three events occur, $\hat{r}_{i*,c_j} \leq r_{i*,c_j} - s_{i*} , \hat{r}_{i,c_j} \geq r_{i,c_j} + s_i$ and $r_{i*}-r_{i} < 2s_i $.
-But the third event will not happen for $n_i\geq \ell_{m_i}$.
+But the third event will not happen for $n_i\geq \ell_{m_{i,c_j}}$.
 Proceeding as before, we can show that the probability of the remaining two events is bounded by,
@@
 \begin{align*}
-&\sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\Pb\lbrace s_i < s_{i*}\rbrace \leq \sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\Pb\lbrace n_i > n_{i*}\rbrace \leq \sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\Pb\lbrace \hat{r}_{i,c_j} + s_i > \hat{r}_{i*,c_j} + s_{i*} \rbrace \\
+&\sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace s_i < s_{i*}\rbrace \leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace n_i > n_{i*}\rbrace \leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace \hat{r}_{i,c_j} + s_i > \hat{r}_{i*,c_j} + s_{i*} \rbrace \\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-&\leq \sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\left( \Pb\lbrace \hat{r}_{i,c_j} \geq r_{i,c_j} + s_i \rbrace \bigcup \Pb\lbrace \hat{r}_{i*,c_j} \leq r_{i*,c_j} - s_{i*} \rbrace \right)\leq \sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\dfrac{\log(\psi T)}{(\psi T)^{\alpha}}\sum_{m=0}^{m_i}\dfrac{1}{\epsilon_{m_i}^{2\alpha + 1}}.
+&\leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\left( \Pb\lbrace \hat{r}_{i,c_j} \geq r_{i,c_j} + s_i \rbrace \bigcup \Pb\lbrace \hat{r}_{i*,c_j} \leq r_{i*,c_j} - s_{i*} \rbrace \right)\leq 2\left(\dfrac{\log(\psi T \epsilon_{m_{i,c_j}}^2)}{2(\psi T)^{\alpha}}\right)\sum_{m=0}^{m_{i,c_j}}\dfrac{1}{\epsilon_{m_{i,c_j}}^{2\alpha + 1}}.
 \end{align*}
 
+%\sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}
 Finally for the fourth event in equation \ref{eq:arm-pull-opt}, we can bound the probability of its complementary event by following the same steps as above,
@@
 \begin{align*}
-\sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\Pb\lbrace n_i > n_{i*}\rbrace \leq \sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_i}}\Pb\lbrace r_{i,c_j} + s_i > r_{i*,c_j} + s_{i*} \rbrace \leq \dfrac{\log(\psi T)}{(\psi T)^{\alpha}}\sum_{m=0}^{m_i}\dfrac{1}{\epsilon_{m_i}^{2\alpha +1}}.
+\sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace n_i > n_{i*}\rbrace \leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace r_{i,c_j} + s_i > r_{i*,c_j} + s_{i*} \rbrace \leq \dfrac{\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi T)^{\alpha}}\sum_{m=0}^{m_{i,c_j}}\dfrac{1}{\epsilon_{m_i}^{2\alpha +1}}.
 \end{align*}
 
-Combining the above four cases we can bound the probability that a sub-optimal arm $i$ will no longer be pulled on or after the $m_i$-th phase by,
+Combining the above four cases we can bound the probability that a sub-optimal arm $i$ will no longer be pulled on or after the $m_{i,c_j}$-th phase by,
 
 \begin{align*}
-\dfrac{4\log(\psi T)}{(\psi T)^{\alpha}}\sum_{m=0}^{m_i}\dfrac{1}{\epsilon_{m_i}^{2\alpha +1}}.
+\dfrac{4\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi T)^{\alpha}}\sum_{m=0}^{m_{i,c_j}}\dfrac{1}{\epsilon_{m_{i,c_j}}^{2\alpha +1}} &\leq \dfrac{4\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi T)^{\alpha}}\sum_{m=0}^{M}\left(\dfrac{1}{\epsilon_{m}}\right)^{2\alpha +1} \overset{(a)}{\leq} \dfrac{4\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi T)^{\alpha}}\left(\dfrac{2(2^M - 1)}{2 - 1}\right)^{2\alpha +1} \\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\overset{(b)}{\leq} \dfrac{4\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi T)^{\alpha}}\left(\sqrt{T}\right)^{2\alpha +1} = \dfrac{4\sqrt{T}\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi)^{\alpha}}.
 \end{align*}
 
-Bounding this trivially by $T\Delta^{opt}_{i,c_j}$ for each arm $i\in\A$ we get the regret suffered for arm $i$ after the $m_i$-th phase  as,
+Here, in $(a)$ we use the standard geometric progression formula and in $(b)$ we substitute the value of $M=\dfrac{1}{2}\log_{2}\dfrac{T}{e}$.
+Bounding this trivially by $T\Delta^{opt}_{i,c_j}$ for each arm $i\in\A$ we get the regret suffered for arm $i$ after the $m_{i,c_j}$-th phase  as,
 
 \begin{align*}
-\sum_{i\in\A}\left(\dfrac{4T\Delta^{opt}_{i,c_j}\log(\psi T)}{(\psi T)^{\alpha}}\sum_{m=0}^{m_i}\dfrac{1}{\epsilon_{m_i}^{2\alpha +1}}\right) \leq \sum_{i\in\A}\left(\dfrac{4T\Delta^{opt}_{i,c_j}\log(\psi T)}{(\psi T)^{\alpha}}\dfrac{M 2^{2\alpha +1}}{(\Delta^{opt}_{i,c_j})^{4\alpha +2}}\right).
+\sum_{i\in\A}\left( \dfrac{4T\Delta^{opt}_{i,c_j}\sqrt{T}\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi)^{\alpha}} \right) \leq \sum_{i\in\A}\left( \dfrac{4T^{\frac{3}{2}}\Delta^{opt}_{i,c_j}\log(\psi T (\Delta^{opt}_{i,c_j})^4)}{(\psi)^{\alpha}} \right).
 \end{align*}
 
-\textbf{Step 5.(Regret for pulling the sub-optimal arm $i$ on or before $m_i$-th phase):} Either a sub-optimal arm gets pulled $\ell_{m_i}$ number of times till the $m_i$-th phase and after that the probability of it getting pulled is exponentially low (as shown in \textbf{step 4}).
-Hence, the number of times a sub-optimal arm $i$ is pulled till the $m_i$-th phase is given by,
+%\begin{align*}
+%\sum_{i\in\A}\left(\dfrac{4T\Delta^{opt}_{i,c_j}\log(\psi T)}{(\psi T)^{\alpha}}\sum_{m=0}^{m_{i,c_j}}\dfrac{1}{\epsilon_{m_{i,c_j}}^{2\alpha +1}}\right) \leq \sum_{i\in\A}\left(\dfrac{4T\Delta^{opt}_{i,c_j}\log(\psi T)}{(\psi T)^{\alpha}}\dfrac{M 2^{2\alpha +1}}{(\Delta^{opt}_{i,c_j})^{4\alpha +2}}\right).
+%\end{align*}
+
+\textbf{Step 5.(Regret for pulling the sub-optimal arm $i$ on or before $m_{i,c_j}$-th phase):} Either a sub-optimal arm gets pulled $\ell_{m_{i,c_j}}$ number of times till the $m_{i,c_j}$-th phase or after that the probability of it getting pulled is exponentially low (as shown in \textbf{step 4}).
+Hence, the number of times a sub-optimal arm $i$ is pulled till the $m_{i,c_j}$-th phase is given by,
 
 \begin{align*}
-\ell_{m_i} = \left\lceil \dfrac{\log(\psi T\epsilon_{m_i}^2)}{2\epsilon_{m_i}} \right\rceil
+n_i < \ell_{m_{i,c_j}} = \left\lceil \dfrac{\log(\psi T\epsilon_{m_{i,c_j}}^2)}{2\epsilon_{m_{i,c_j}}} \right\rceil
 \end{align*}
@@
 \begin{align*}
-\sum_{i\in\A}\Delta^{opt}_{i,c_j}\left\lceil \dfrac{\log(\psi T\epsilon_{m_i}^2)}{2\epsilon_{m_i}} \right\rceil < \Delta^{opt}_{i,c_j}\left[ 1 + \dfrac{\log(\psi T\epsilon_{m_i}^2)}{2\epsilon_{m_i}} \right] \leq \Delta^{opt}_{i,c_j}\left[ 1 + \dfrac{4\log(\psi T(\Delta^{opt}_{i,c_j})^4)}{2(\Delta^{opt}_{i,c_j})^2}\right].
+\sum_{i\in\A}\Delta^{opt}_{i,c_j}\left\lceil \dfrac{\log(\psi T\epsilon_{m_{i,c_j}}^2)}{2\epsilon_{m_{i,c_j}}} \right\rceil < \Delta^{opt}_{i,c_j}\left[ 1 + \dfrac{\log(\psi T\epsilon_{m_{i,c_j}}^2)}{2\epsilon_{m_{i,c_j}}} \right] \leq \Delta^{opt}_{i,c_j}\left[ 1 + \dfrac{4\log(\psi T(\Delta^{opt}_{i,c_j})^4)}{2(\Delta^{opt}_{i,c_j})^2}\right].
 \end{align*}
 
-\textbf{Step 6.(Regret for not detecting changepoint $c_{j}$ for arm $i$ after the $p_{i}$-th phase):} Proceeding similarly as in \textbf{step 4} we can show that in the $p_i$-th phase for an arm $i$ if $n_{i}\geq\ell_{p_i}$ then,
+\textbf{Step 6.(Regret for not detecting changepoint $c_{j}$ for arm $i$ after the $p_{i,c_j}$-th phase):} Proceeding similarly as in \textbf{step 4} we can show that in the $p_{i,c_j}$-th phase for an arm $i$ if $n_{i}\geq\ell_{p_{i,c_j}}$ then,
 
 \begin{align*}
-s_i = \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{p_i}^2)}{2n_{i}}} \leq \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{p_i}^2)}{2\ell_{p_i}}} \leq \sqrt{\alpha\epsilon_{p_i}\dfrac{\log(\psi T\epsilon_{p_i}^2)}{\log(\psi T\epsilon_{p_i}^2)}} \leq \dfrac{\Delta^{chg}_{i,c_j}}{4}.
+s_i = \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{p_{i,c_j}}^2)}{2n_{i}}} \leq \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{p_{i,c_j}}^2)}{2\ell_{p_{i,c_j}}}} \leq \sqrt{\alpha\epsilon_{p_{i,c_j}}\dfrac{\log(\psi T\epsilon_{p_{i,c_j}}^2)}{\log(\psi T\epsilon_{p_{i,c_j}}^2)}} \leq \dfrac{\Delta^{chg}_{i,c_j}}{4}.
 \end{align*}
@@
 
-Indeed, we can show that if there is a changepoint at $c_j$ such that $r_{i,c_{j-1}} < r_{i,c_j}$ and if the first conditions in equation \ref{eq:arm-pull-chg} hold  in the $p_i$-th phase then,
+Indeed, we can show that if there is a changepoint at $c_j$ such that $r_{i,c_{j-1}} < r_{i,c_j}$ and if the first conditions in equation \ref{eq:arm-pull-chg} hold  in the $p_{i,c_j}$-th phase then,
 
 \begin{align*}
-\hat{r}_{i,c_{j-1}} + s_{i} \leq \hat{r}_{i,c_{j-1}} + 4s_{i} - 2s_{i} \leq \hat{r}_{i,c_{j-1}} + \Delta^{chg}_{i,c_j} -2s_{i} \leq \hat{r}_{i,c_{j}} - 2s_i \leq \hat{r}_{i,c_{j}} - s_i.
+\hat{r}_{i,c_{j-1}} + s_{i} \leq {r}_{i,c_{j-1}} + 4s_{i} - 2s_{i} \leq {r}_{i,c_{j-1}} + \Delta^{chg}_{i,c_j} -2s_{i} \leq {r}_{i,c_{j}} - 2s_i \leq \hat{r}_{i,c_{j}} - s_i.
 \end{align*}
 
-Conversely, for the case $r_{i,c_{j-1}} > r_{i,c_j}$ the second condition will hold for the $p_i$-th phase.
+Conversely, for the case $r_{i,c_{j-1}} > r_{i,c_j}$ the second condition will hold for the $p_{i,c_j}$-th phase.
 Now, to bound the regret we need to bound the probability of the complementary of these two events.
@@
 \begin{align*}
-&\sum_{m=0}^{p_i}\sum_{n_i=1}^{\ell_{p_i}}\Pb\lbrace \hat{r}_{i,c_{j-1}} \geq  r_{i,c_{j-1}} + s_i \rbrace \leq \sum_{m=0}^{p_i}\sum_{n_i=1}^{\ell_{p_i}}\exp\left(-2s_i^2n_i \right)
+&\sum_{m=0}^{p_{i,c_j}}\sum_{n_i=1}^{\ell_{p_{i,c_j}}}\Pb\lbrace \hat{r}_{i,c_{j-1}} \geq  r_{i,c_{j-1}} + s_i \rbrace \leq \sum_{m=0}^{p_{i,c_j}}\sum_{n_i=1}^{\ell_{p_{i,c_j}}}\exp\left(-2s_i^2n_i \right)
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\leq \sum_{m=0}^{p_i}\sum_{n_i=1}^{\ell_{p_i}}\exp\left(-2\dfrac{\alpha\log(\psi T\epsilon_{p_i}^2)}{2n_i}n_i \right)\\
+\leq \sum_{m=0}^{p_{i,c_j}}\sum_{n_i=1}^{\ell_{p_{i,c_j}}}\exp\left(-2\dfrac{\alpha\log(\psi T\epsilon_{p_{i,c_j}}^2)}{2n_i}n_i \right)\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\leq \sum_{m=0}^{p_i}\sum_{n_i=1}^{\ell_{p_i}}\dfrac{1}{\psi T\epsilon_{p_i}^2} \leq \sum_{m=0}^{p_i}\dfrac{\log(\psi T\epsilon_{p_i}^2)}{2\epsilon_{p_i}}\dfrac{1}{(\psi T)^{\alpha}\epsilon_{p_i}^2} = \dfrac{\log(\psi T)}{2(\psi T)^{\alpha}}\sum_{m=0}^{p_i}\dfrac{1}{\epsilon_{p_i}^{2\alpha + 1}}.
+&\leq \sum_{m=0}^{p_{i,c_j}}\sum_{n_i=1}^{\ell_{p_{i,c_j}}}\dfrac{1}{\psi T\epsilon_{p_{i,c_j}}^2} \leq \sum_{m=0}^{p_{i,c_j}}\dfrac{\log(\psi T\epsilon_{p_{i,c_j}}^2)}{2\epsilon_{p_{i,c_j}}}\dfrac{1}{(\psi T)^{\alpha}\epsilon_{p_{i,c_j}}^2} = \dfrac{\log(\psi T\epsilon_{p_{i,c_j}}^2)}{2(\psi T)^{\alpha}}\sum_{m=0}^{p_{i,c_j}}\dfrac{1}{\epsilon_{p_{i,c_j}}^{2\alpha + 1}}.
 \end{align*}
@@
 \begin{align*}
-\sum_{m=0}^{p_i}\sum_{n_i=\ell_{p_{i-1}}}^{\ell_{p_i}}\Pb\lbrace \hat{r}_{i,c_j} \leq  r_{i,c_j} - s_i \rbrace &\leq \sum_{m=0}^{p_i}\sum_{n_i=\ell_{p_{i-1}}}^{\ell_{p_i}}\exp\left(-2s_i^2n_i \right) \leq \dfrac{\log(\psi T)}{2(\psi T)^{\alpha}}\sum_{m=0}^{p_i}\dfrac{1}{\epsilon_{p_i}^{2\alpha + 1}}.
+\sum_{m=0}^{p_{i,c_j}}\sum_{n_i=\ell_{p_{i-1}}}^{\ell_{p_{i,c_j}}}\Pb\lbrace \hat{r}_{i,c_j} \leq  r_{i,c_j} - s_i \rbrace &\leq \sum_{m=0}^{p_{i,c_j}}\sum_{n_i=\ell_{p_{i-1, c_j}}}^{\ell_{p_{i,c_j}}}\exp\left(-2s_i^2n_i \right) \leq \dfrac{\log(\psi T\epsilon_{p_{i,c_j}}^2)}{2(\psi T)^{\alpha}}\sum_{m=0}^{p_{i,c_j}}\dfrac{1}{\epsilon_{p_{i,c_j}}^{2\alpha + 1}}.
 \end{align*}
 
-Hence, the probability that the changepoint is not detected by the first event is bounded by,
+Hence, the probability that the changepoint is not detected by the first event in equation \ref{eq:arm-pull-chg} is bounded by,
 \begin{align*}
-\dfrac{\log(\psi T)}{(\psi T)^{\alpha}}\sum_{m=0}^{p_i}\dfrac{1}{\epsilon_{p_i}^{2\alpha + 1}}.
+\dfrac{\log(\psi T)}{(\psi T \epsilon_{p_{i,c_j}}^2)^{\alpha}}\sum_{m=0}^{p_{i,c_j}}\dfrac{1}{\epsilon_{p_{i,c_j}}^{2\alpha + 1}}.
 \end{align*}
@@
 \begin{align*}
-&\sum_{m=0}^{p_i}\sum_{n_i=1}^{\ell_{p_i}}\Pb\lbrace \hat{r}_{i,c_{j-1}} \leq  r_{i,c_{j-1}} - s_i \rbrace\leq \dfrac{\log(\psi T)}{2(\psi T)^{\alpha}}\sum_{m=0}^{p_i}\dfrac{1}{\epsilon_{p_i}^{2\alpha + 1}} \textbf{,  and  }\\
+&\sum_{m=0}^{p_{i,c_j}}\sum_{n_i=1}^{\ell_{p_{i,c_j}}}\Pb\lbrace \hat{r}_{i,c_{j-1}} \leq  r_{i,c_{j-1}} - s_i \rbrace\leq \dfrac{\log(\psi T\epsilon_{p_{i,c_j}}^2)}{2(\psi T)^{\alpha}}\sum_{m=0}^{p_i}\dfrac{1}{\epsilon_{p_{i,c_j}}^{2\alpha + 1}} \textbf{,  and  }\\
 %%%%%%%%%%%%%%%%%%%%%%%%%
-&\sum_{m=0}^{p_i}\sum_{n_i=\ell_{p_{i-1}}}^{\ell_{p_i}}\Pb\lbrace \hat{r}_{i,c_j} \geq  r_{i,c_j} + s_i \rbrace\leq \dfrac{\log(\psi T)}{(\psi T)^{\alpha}}\sum_{m=0}^{p_i}\dfrac{1}{\epsilon_{p_i}^{2\alpha + 1}}.
+&\sum_{m=0}^{p_{i,c_j}}\sum_{n_i=1}^{\ell_{p_{i,c_j}}}\Pb\lbrace \hat{r}_{i,c_j} \geq  r_{i,c_j} + s_i \rbrace\leq \dfrac{\log(\psi T\epsilon_{p_{i,c_j}}^2)}{(\psi T)^{\alpha}}\sum_{m=0}^{p_{i,c_j}}\dfrac{1}{\epsilon_{p_{i,c_j}}^{2\alpha + 1}}.
 \end{align*}
 
-Combining the contribution from these two events, we can show that the probability of not detecting the changepoint $c_j$ for the $i$-th arm after the $p_i$-th phase is upper bounded by,
+%\ell_{p_{i-1,c_j}}
+
+Combining the contribution from these two events, we can show that the probability of not detecting the changepoint $c_j$ for the $i$-th arm after the $p_{i,c_j}$-th phase is upper bounded by,
 
 \begin{align*}
-\dfrac{2\log(\psi T)}{(\psi T)^{\alpha}}\sum_{m=0}^{p_i}\dfrac{1}{\epsilon_{p_i}^{2\alpha + 1}}.
+\dfrac{2\log(\psi T)}{(\psi T\epsilon_{p_{i,c_j}}^2)^{\alpha}}\sum_{m=0}^{p_{i,c_j}}\dfrac{1}{\epsilon_{p_{i,c_j}}^{2\alpha + 1}} \overset{(a)}{\leq} \dfrac{2\sqrt{T}\log(\psi T \epsilon_{p_{i,c_j}}^2)}{(\psi)^{\alpha}} .
 \end{align*}
 
+Here, in $(a)$ we follow the same steps as in \textbf{step 4} to reduce the expression to the above form.
 Furthermore, bounding the regret trivially (after the changepoint $c_j$) by $\Delta^{opt}_{i,c_{j+1}}$ for each arm $i\in\A$, we get
+
 \begin{align*}
-\sum_{i\in\A}\left(\dfrac{2T\Delta^{opt}_{i,c_{j+1}}\log(\psi T)}{(\psi T)^{\alpha}}\sum_{m=0}^{p_i}\dfrac{1}{\epsilon_{p_i}^{2\alpha + 1}}\right) \leq \sum_{i\in\A}\left(\dfrac{2T\Delta^{opt}_{i,c_{j+1}}\log(\psi T)}{(\psi T)^{\alpha}}\dfrac{M 2^{2\alpha + 1}}{(\Delta^{chg}_{i,c_j})^{4\alpha + 2}}\right).
+\sum_{i\in\A}\left( \dfrac{2T\Delta^{opt}_{i,c_{j+1}}\sqrt{T}\log(\psi T \epsilon_{p_{i,c_j}}^2)}{(\psi)^{\alpha}} \right) \leq \sum_{i\in\A}\left( \dfrac{2T^{\frac{3}{2}}\Delta^{opt}_{i,c_{j+1}}\log(\psi T (\Delta^{chg}_{i,c_j})^4)}{(\psi)^{\alpha}} \right).
 \end{align*}
 
-\textbf{Step 7.(Regret for not detecting a changepoint $c_{j}$ for arm $i$ on or before the $p_{i}$-th phase):} The regret for not detecting the changepoint $c_j$ on or before the $p_i$-th phase can be broken into two parts, \textbf{(a)} the worst case events from $t_{c_j}$ to $p_{i}$ and \textbf{(b)} the minimum number of pulls $\ell_{p_i}$ required to detect the changepoint.
+%\begin{align*}
+%\sum_{i\in\A}\left(\dfrac{2T\Delta^{opt}_{i,c_{j+1}}\log(\psi T)}{(\psi T)^{\alpha}}\sum_{m=0}^{p_{i,c_j}}\dfrac{1}{\epsilon_{p_{i,c_j}}^{2\alpha + 1}}\right) \leq \sum_{i\in\A}\left(\dfrac{2T\Delta^{opt}_{i,c_{j+1}}\log(\psi T)}{(\psi T)^{\alpha}}\dfrac{M 2^{2\alpha + 1}}{(\Delta^{chg}_{i,c_j})^{4\alpha + 2}}\right).
+%\end{align*}
+
+\textbf{Step 7.(Regret for not detecting a changepoint $c_{j}$ for arm $i$ on or before the $p_{i,c_j}$-th phase):} The regret for not detecting the changepoint $c_j$ on or before the $p_{i,c_j}$-th phase can be broken into two parts, \textbf{(a)} the worst case events from $t_{c_j}$ to $p_{i}$ and \textbf{(b)} the minimum number of pulls $\ell_{p_{i,c_j}}$ required to detect the changepoint.
 For the first part (a) we can use Assumption \ref{assm:space-gap}, Assumption ref{assm:chg-gap}, Discussion \ref{dis:gap-delay} and Definition \ref{Def:e-chg-gap} to upper bound the regret as,
@@
 \begin{align*}
-\sum_{i\in\A}\Delta^{opt}_{\max,c_{j+1}}\left\lceil \dfrac{\log(\psi T\epsilon_{p_i}^2)}{2(\Delta^{chg}_{\epsilon_0,c_j})^2} \right\rceil < \Delta^{opt}_{\max,c_{j+1}}\left[ 1 + \dfrac{\log(\psi T\epsilon_{p_i}^2)}{2(\Delta^{chg}_{\epsilon_0,c_j})^2} \right].
+\sum_{i\in\A}\Delta^{opt}_{\max,c_{j+1}}\left\lceil \dfrac{\log(\psi T\epsilon_{p_{i,c_j}}^2)}{2(\Delta^{chg}_{\epsilon_0,c_j})^2} \right\rceil < \Delta^{opt}_{\max,c_{j+1}}\left[ 1 + \dfrac{\log(\psi T\epsilon_{p_{i,c_j}}^2)}{2(\Delta^{chg}_{\epsilon_0,c_j})^2} \right].
 \end{align*}
@@
 \begin{align*}
-\sum_{i\in\A}\Delta^{opt}_{i,c_{j+1}}\left\lceil \dfrac{\log(\psi T\epsilon_{p_i}^2)}{2\epsilon_{p_i}} \right\rceil <  \Delta^{opt}_{i,c_{j+1}}\left[ 1 + \dfrac{\log(\psi T\epsilon_{p_i}^2)}{2\epsilon_{p_i}} \right].
+\sum_{i\in\A}\Delta^{opt}_{i,c_{j+1}}\left\lceil \dfrac{\log(\psi T\epsilon_{p_{i,c_j}}^2)}{2\epsilon_{p_{i,c_j}}} \right\rceil <  \Delta^{opt}_{i,c_{j+1}}\left[ 1 + \dfrac{\log(\psi T\epsilon_{p_i}^2)}{2\epsilon_{p_i}} \right].
 \end{align*}
 
-Therefor, combining these two parts (a) and (b) we can show that the total regret for not detecting the changepoint till the $p_i$-th phase is given by,
+Therefore, combining these two parts (a) and (b) we can show that the total regret for not detecting the changepoint till the $p_{i,c_j}$-th phase is given by,
 
 \begin{align*}
-&\sum_{i\in\A}\left\lbrace\Delta^{opt}_{\max,c_{j+1}} + \dfrac{\Delta^{opt}_{\max,c_{j+1}}\log(\psi T\epsilon_{p_i}^2)}{2(\Delta^{chg}_{\epsilon_0,c_j})^2} + \Delta^{opt}_{i,c_{j+1}} + \dfrac{\Delta^{opt}_{i,c_{j+1}}\log(\psi T\epsilon_{p_i}^2)}{2\epsilon_{p_i}}\right\rbrace \\
+&\sum_{i\in\A}\left\lbrace\Delta^{opt}_{\max,c_{j+1}} + \dfrac{\Delta^{opt}_{\max,c_{j+1}}\log(\psi T\epsilon_{p_{i,c_j}}^2)}{2(\Delta^{chg}_{\epsilon_0,c_j})^2} + \Delta^{opt}_{i,c_{j+1}} + \dfrac{\Delta^{opt}_{i,c_{j+1}}\log(\psi T\epsilon_{p_{i,c_j}}^2)}{2\epsilon_{p_i}}\right\rbrace \\
 %%%%%%%%%%%%%%%%%%%%%%%%%
-&\leq \sum_{i\in\A}\left\lbrace\Delta^{opt}_{\max,c_{j+1}} + \dfrac{\Delta^{opt}_{\max,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2\Delta^{chg}_{\epsilon_0,c_j}} + \Delta^{opt}_{i,c_{j+1}} + \dfrac{\Delta^{opt}_{i,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2(\Delta^{chg}_{i,c_j})^2}\right\rbrace
+&\leq \sum_{i\in\A}\left\lbrace\Delta^{opt}_{\max,c_{j+1}} + \dfrac{\Delta^{opt}_{\max,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2(\Delta^{chg}_{\epsilon_0,c_j})^2} + \Delta^{opt}_{i,c_{j+1}} + \dfrac{\Delta^{opt}_{i,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2(\Delta^{chg}_{i,c_j})^2}\right\rbrace
 \end{align*}
 
-\textbf{Step 8.(Final Regret bound):} Combining the assumption in \textbf{Step 0} and from our problem definition we recall that the expected regret till the $T$-th timestep is bounded by,
+\textbf{Step 8.(Final Regret bound):} Combining the assumption in \textbf{Step 0} and the problem definition, the expected regret till the $T$-th timestep is bounded by,
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-& = \sum_{i = 1}^K\sum_{j=1}^{G}\bigg[ 1 
+& \leq \sum_{i = 1}^K\sum_{j=1}^{G}\bigg[ 1 
 %%%%%%%%%%
-+ \underbrace{\dfrac{4T\Delta^{opt}_{i,c_j}\log(\psi T)}{(\psi T)^{\alpha}}\dfrac{M 2^{2\alpha +1}}{(\Delta^{opt}_{i,c_j})^{4\alpha +2}}}_{\textbf{from Step 4}}
++ \underbrace{ \dfrac{4T^{\frac{3}{2}}\Delta^{opt}_{i,c_j}\log(\psi T (\Delta^{opt}_{i,c_j})^4)}{(\psi)^{\alpha}} }_{\textbf{from Step 4}}
 %%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-& + \underbrace{\dfrac{2T\Delta^{opt}_{i,c_{j+1}}\log(\psi T)}{(\psi T)^{\alpha}}\dfrac{M 2^{2\alpha + 1}}{(\Delta^{chg}_{i,c_j})^{4\alpha + 2}}}_{\textbf{from Step 6}}\\
+& + \underbrace{ \dfrac{2T^{\frac{3}{2}}\Delta^{opt}_{i,c_{j+1}}\log(\psi T (\Delta^{chg}_{i,c_j})^4)}{(\psi)^{\alpha}} }_{\textbf{from Step 6}}\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-&+ \underbrace{ \Delta^{opt}_{\max,c_{j+1}} + \dfrac{\Delta^{opt}_{\max,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2\Delta^{chg}_{\epsilon_0,c_j}} + \Delta^{opt}_{i,c_{j+1}} + \dfrac{\Delta^{opt}_{i,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2(\Delta^{chg}_{i,c_j})^2}}_{\textbf{from Step 7}}
+&+ \underbrace{ \Delta^{opt}_{\max,c_{j+1}} + \dfrac{\Delta^{opt}_{\max,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2(\Delta^{chg}_{\epsilon_0,c_j})^2} + \Delta^{opt}_{i,c_{j+1}} + \dfrac{\Delta^{opt}_{i,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2(\Delta^{chg}_{i,c_j})^2}}_{\textbf{from Step 7}}
 \bigg]
@@
 \end{proof}
+
+\begin{corollary}
+\label{psbandit:corollary:1}
+In the worst case scenario, when all the gaps are same, that is $\Delta^{opt}_{i,c_j}=\Delta^{chg}_{i,c_j}=\sqrt{\dfrac{K\log K}{T}}, \forall i\in\A,\forall j\in\G$ and setting $\alpha=\dfrac{1}{2}$ and $\psi = \dfrac{T^2}{K^2}$ then the worst case gap-independent regret bound of ImpCPD is given by,
+
+\begin{align*}
+\E[R_T]\leq 3G\sqrt{\dfrac{K^3\log K}{T}} + 24G\sqrt{KT\log K}\left(\log\left(\sqrt{T}\right)\right) + 16GK^2 \sqrt{(K\log K)}\left(\log\left( \sqrt{T}(\log K)\right) \right).
+\end{align*}
+
+\end{corollary}
+
+\begin{proof}
+
+We first recall the result of Theorem \ref{psbandit:Theorem:1} below,
+
+\begin{align*}
+\E[R_{T}] &\leq \sum_{i = 1}^K\sum_{j=1}^{G}\bigg[ 1 
+%%%%%%%%%%
++ \underbrace{ \dfrac{4T^{\frac{3}{2}}\Delta^{opt}_{i,c_j}\log(\psi T (\Delta^{opt}_{i,c_j})^4)}{(\psi)^{\alpha}} }_{\textbf{part A}}
+%%%%%%%%%%
++ \underbrace{\Delta^{opt}_{i,c_j} + \dfrac{4\log(\psi T(\Delta^{opt}_{i,c_j})^4)}{2(\Delta^{opt}_{i,c_j})}}_{\textbf{part B}}\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+& + \underbrace{ \dfrac{2T^{\frac{3}{2}}\Delta^{opt}_{i,c_{j+1}}\log(\psi T (\Delta^{chg}_{i,c_j})^4)}{(\psi)^{\alpha}} }_{\textbf{part C}}\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&+ \underbrace{ \Delta^{opt}_{\max,c_{j+1}} + \dfrac{\Delta^{opt}_{\max,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2(\Delta^{chg}_{\epsilon_0,c_j})^2} + \Delta^{opt}_{i,c_{j+1}} + \dfrac{\Delta^{opt}_{i,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2(\Delta^{chg}_{i,c_j})^2}}_{\textbf{part D}}
+\bigg]
+\end{align*}
+
+Then, substituting $\Delta^{opt}_{i,c_j}=\Delta^{chg}_{i,c_j}=\sqrt{\dfrac{K\log K}{T}}, \forall i\in\A,\forall j\in\G$ and $\alpha=\dfrac{1}{2}$ and $\psi = \dfrac{T^2}{K^2}$ we can show that for \textbf{part A},
+
+\begin{align*}
+&G\sum_{i\in\A}\underbrace{ \dfrac{4T^{\frac{3}{2}}\Delta^{opt}_{i,c_j}\log(\psi T (\Delta^{opt}_{i,c_j})^4)}{(\psi)^{\alpha}} }_{\textbf{part A}} \leq \dfrac{4GKT^{\frac{3}{2}}\sqrt{\dfrac{K\log K}{T}}\log(\dfrac{T^2}{K^2} T (\sqrt{\dfrac{K\log K}{T}})^4)}{(\dfrac{T^2}{K^2})^{\frac{1}{2}}}\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+  &= 4GK^2 \sqrt{(K\log K)}(\log\left( T(\log K)^2\right) ) = 8K^2 \sqrt{(K\log K)}\left(\log\left( \sqrt{T}(\log K)\right) \right).
+\end{align*}
+
+Again, for \textbf{part B} we can show that,
+
+\begin{align*}
+&G\sum_{i\in\A}\left(\underbrace{\Delta^{opt}_{i,c_j} + \dfrac{4\log(\psi T(\Delta^{opt}_{i,c_j})^4)}{2(\Delta^{opt}_{i,c_j})}}_{\textbf{part B}}\right) \leq GK\sqrt{\dfrac{K\log K}{T}} + \dfrac{4GK\log(\dfrac{T^2}{K^2} T(\sqrt{\dfrac{K\log K}{T}})^4)}{2(\sqrt{\dfrac{K\log K}{T}})} \\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&= GK\sqrt{\dfrac{K\log K}{T}} + \dfrac{8G\sqrt{KT}(\log\left( \sqrt{T}(\log K)\right)) }{\sqrt{\log K}} = G\sqrt{\dfrac{K^3\log K}{T}} + 8G\sqrt{KT\log K}\left(\log\left(\sqrt{T}\right)\right).
+\end{align*}
+
+Similarly to \textbf{part A}, we can reduce \textbf{part C} as,
+
+\begin{align*}
+G\sum_{i\in\A}\underbrace{ \dfrac{2T^{\frac{3}{2}}\Delta^{opt}_{i,c_{j+1}}\log(\psi T (\Delta^{chg}_{i,c_j})^4)}{(\psi)^{\alpha}} }_{\textbf{part C}} \leq 8GK^2 \sqrt{(K\log K)}\left(\log\left( \sqrt{T}(\log K)\right) \right).
+\end{align*}
+
+And finally, for \textbf{part D}, similar to \textbf{part B}, we can show that,
+
+\begin{align*}
+&G\sum_{i\in\A}\left(\underbrace{ \Delta^{opt}_{\max,c_{j+1}} + \dfrac{\Delta^{opt}_{\max,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2(\Delta^{chg}_{\epsilon_0,c_j})^2} + \Delta^{opt}_{i,c_{j+1}} + \dfrac{\Delta^{opt}_{i,c_{j+1}}\log(\psi T(\Delta^{chg}_{i,c_j})^4)}{2(\Delta^{chg}_{i,c_j})^2}}_{\textbf{part D}}\right)\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+& \leq G\sqrt{\dfrac{K^3\log K}{T}} + 8G\sqrt{KT\log K}(\log\left(\sqrt{T}\right) + G\sqrt{\dfrac{K^3\log K}{T}} + 8G\sqrt{KT\log K}(\log\left(\sqrt{T}\right)\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+& = 2G\sqrt{\dfrac{K^3\log K}{T}} + 16G\sqrt{KT\log K}\left(\log\left(\sqrt{T}\right)\right).
+\end{align*}
+
+Hence, combining the four parts we get that,
+
+\begin{align*}
+\E[R_T]&\leq 3G\sqrt{\dfrac{K^3\log K}{T}} + 24G\sqrt{KT\log K}\left(\log\left(\sqrt{T}\right)\right)\\
+%%%%%%%%%%%%%%%%%%%%%%%%%
+& + 16GK^2 \sqrt{(K\log K)}\left(\log\left( \sqrt{T}(\log K)\right) \right).
+\end{align*}
+
+\end{proof}
+
+\begin{discussion}
+From the result in Corollary \ref{psbandit:corollary:1}, we see that the largest contributing factor to the expected regret is of the order $O\left( G\sqrt{KT\log K}\log(\sqrt{T})\right)$.
+\end{discussion}

### 2017-12-13 Chapter6/contribution.tex
Latest on 13/12/2017

@@
-In this chapter, we propose an actively adaptive upper confidence bound (UCB) algorithm, referred to as Improved Changepoint Detector (ImpCPD), that tries to locate the chnagepoints in the distribution and adapt accordingly to minimize the cumulative regret.
+In this chapter, we propose an actively adaptive upper confidence bound (UCB) algorithm, referred to as Improved Changepoint Detector (ImpCPD), that tries to locate the changepoints in the distribution and adapt accordingly to minimize the cumulative regret.
 Our solution to the piecewise stochastic problem also depends on restarting where we employ ImpCPD which tries to minimize the cumulative regret by balancing exploration-exploitation and a changepoint detector which tries to predict a changepoint with high probability.

### 2017-12-13 Chapter6/mainresult.tex
Latest on 11/12/2017
Latest on 13/12/2017

@@
 %%%%%%%%%%
-+ \dfrac{4T^{\frac{3}{2}}\Delta^{opt}_{i,c_j}\log(\psi T (\Delta^{opt}_{i,c_j})^4)}{(\psi)^{\alpha}}
++ \dfrac{4T^{\frac{3}{2}}C_{\gamma}\Delta^{opt}_{i,c_j}\log(\psi T (\Delta^{opt}_{i,c_j})^4)}{(\psi)^{\alpha}}
 %%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-& + \dfrac{2T^{\frac{3}{2}}\Delta^{opt}_{i,c_{j+1}}\log(\psi T (\Delta^{chg}_{i,c_j})^4)}{(\psi)^{\alpha}}\\
+& + \dfrac{2T^{\frac{3}{2}}C_{\gamma}\Delta^{opt}_{i,c_{j+1}}\log(\psi T (\Delta^{chg}_{i,c_j})^4)}{(\psi)^{\alpha}}\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-where $\alpha,\psi$ are exploration parameters and $\Delta^{opt}_{i,c_{G+1}} = 0,\forall i\in\A$.
+where $\alpha,\psi,\gamma$ are exploration parameters, $C_{\gamma}=\left( \dfrac{1+\gamma}{\gamma}\right)$ and $\Delta^{opt}_{i,c_{G+1}} = 0,\forall i\in\A$.
 \end{theorem}
@@
 
-\textbf{Step 0.(Vital Assumption for proving):} In this proof, we assume that all the changepoints are detected by the algorithm.
+\textbf{Step 0.(Vital Assumption for proving):} In this proof, we assume that all the changepoints are detected by the algorithm with some delay.
+Since, all the gaps are significant (Assumption \ref{assm:chg-gap}) and there is sufficient delay between two changepoints (Assumption \ref{assm:space-gap}), we can take this assumption for proving the result.
 
 \textbf{Step 1.(Define some notations):} In this proof, we define the confidence interval for the $i$-th arm as $s_i=\sqrt{\dfrac{\alpha\log(\psi T\epsilon_m^2)}{n_{i}}}$.
-The phase numbers are denoted by $m=0,1,\ldots,M$ where $M=\frac{1}{2}\log_{2}\frac{T}{e}$.
-For the sake of brevity, in this proof we write $n_i$ instead of $n_{i,t_0:t_p}$ denoting only the number of times the arm $i$ is pulled between two restarts, ie, between $t_0$ to $t_p$.
+The phase numbers are denoted by $m=0,1,\ldots,M$ where $M=\frac{1}{2}\log_{1+\gamma}\frac{T}{e}$.
+For the sake of brevity, in this proof we write $n_i$ instead of $n_{i,t_0:t_p}$ denoting the number of times the arm $i$ is pulled between two restarts, ie, between $t_0$ to $t_p$ (as shown in algorithm).
+For each sub-optimal arm $i$, we consider their contribution to cumulative regret individually till each of the changepoint
 
-\textbf{Step 2.(Define an optimality stopping phase $m_{i,c_j}$):} We define an optimality stopping phase $m_{i,c_j}$ for a sub-optimal arm $i\in\A$ as the first phase after which the arm $i$ is no longer pulled till the $c_j$-th changepoint is detected such that,
+\textbf{Step 2.(Define an optimality stopping phase $m_{i,c_j}$):} We define an optimality stopping phase $m_{i,c_j}$ for a sub-optimal arm $i\in\A$ as the first phase after which the arm $i$ is no longer pulled till the $c_j$-th changepoint is detected such that for $\gamma>0$,
 
 \begin{align*}
-m_{i,c_j} = \min\left\lbrace m: \sqrt{\alpha\epsilon_{m}} < \dfrac{\Delta^{opt}_{i,c_j}}{4} \right\rbrace
+m_{i,c_j} = \min\left\lbrace m: \sqrt{\alpha\epsilon_{m}} < \dfrac{\Delta^{opt}_{i,c_j}}{(1+\gamma)^2} \right\rbrace
 \end{align*}
 
-\textbf{Step 3.(Define a changepoint stopping phase $p_{i,c_j}$):} We define a changepoint stopping phase $p_{i,c_j}$ for an arm $i\in\A$ such that it is the first phase when the changepoint $c_j$ is detected such that,
+\textbf{Step 3.(Define a changepoint stopping phase $p_{i,c_j}$):} We define a changepoint stopping phase $p_{i,c_j}$ for an arm $i\in\A$ such that it is the first phase when the changepoint $c_j$ is detected such that for $\gamma > 0$,
 
 \begin{align*}
-p_{i,c_j} = \min\left\lbrace m: \sqrt{\alpha\epsilon_{m}} < \dfrac{\Delta^{chg}_{i,c_j}}{4} \right\rbrace
+p_{i,c_j} = \min\left\lbrace m: \sqrt{\alpha\epsilon_{m}} < \dfrac{\Delta^{chg}_{i,c_j}}{(1+\gamma)^2} \right\rbrace
 \end{align*}
@@
 \begin{align*}
-s_i = \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{m_{i,c_j}}^2)}{2n_{i}}} \leq \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{m_{i,c_j}}^2)}{2\ell_{m_{i,c_j}}}} \leq \sqrt{\alpha\epsilon_{m_{i,c_j}}\dfrac{\log(\psi T\epsilon_{m_{i,c_j}}^2)}{\log(\psi T\epsilon_{m_{i,c_j}}^2)}} \leq \dfrac{\Delta^{opt}_{i,c_j}}{4}.
+s_i = \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{m_{i,c_j}}^2)}{2n_{i}}} \leq \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{m_{i,c_j}}^2)}{2\ell_{m_{i,c_j}}}} \leq \sqrt{\alpha\epsilon_{m_{i,c_j}}\dfrac{\log(\psi T\epsilon_{m_{i,c_j}}^2)}{\log(\psi T\epsilon_{m_{i,c_j}}^2)}} \leq \dfrac{\Delta^{opt}_{i,c_j}}{(1+\gamma)^2}.
 \end{align*}
@@
 \begin{align*}
-\hat{r}_{i,c_j} + s_i \leq {r}_{i,c_j} + 4s_i - 2s_i \leq {r}_{i,c_j} + \Delta^{opt}_{i,c_j} - 2s_i \leq {r}_{i*,c_j} - 2s_{i*} \leq \hat{r}_{i*,c_j} - s_{i*}
+\hat{r}_{i,c_j} + s_i \leq {r}_{i,c_j} + (1+\gamma)^2 s_i - (1+\gamma)s_i \leq {r}_{i,c_j} + \Delta^{opt}_{i,c_j} - (1+\gamma)s_i \leq {r}_{i*,c_j} - (1+\gamma)s_{i*} \leq \hat{r}_{i*,c_j} - s_{i*}
 \end{align*}
@@
 \begin{align*}
-\sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace s_i < s_{i*}\rbrace \leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace n_i > n_{i*}\rbrace \leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace \hat{r}_{i,c_j} + s_i > \hat{r}_{i*,c_j} + s_{i*} \rbrace.
+\sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\sum_{n_{i*}=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace s_i < s_{i*}\rbrace \leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\sum_{n_{i*}=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace n_i > n_{i*}\rbrace \leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\sum_{n_{i*}=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace \hat{r}_{i,c_j} + s_i > \hat{r}_{i*,c_j} + s_{i*} \rbrace.
 \end{align*}
 
-But the event $\hat{r}_{i,c_j} + s_i > \hat{r}_{i*,c_j} + s_i$ is possible only when the following three events occur, $\hat{r}_{i*,c_j} \leq r_{i*,c_j} - s_{i*} , \hat{r}_{i,c_j} \geq r_{i,c_j} + s_i$ and $r_{i*}-r_{i} < 2s_i $.
+But the event $\hat{r}_{i,c_j} + s_i > \hat{r}_{i*,c_j} + s_i$ is possible only when the following three events occur, $\hat{r}_{i*,c_j} \leq r_{i*,c_j} - s_{i*} , \hat{r}_{i,c_j} \geq r_{i,c_j} + s_i$ and $r_{i*}-r_{i} < (1+\gamma)^2 s_i $.
 But the third event will not happen for $n_i\geq \ell_{m_{i,c_j}}$.
@@
 \begin{align*}
-&\sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace s_i < s_{i*}\rbrace \leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace n_i > n_{i*}\rbrace \leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace \hat{r}_{i,c_j} + s_i > \hat{r}_{i*,c_j} + s_{i*} \rbrace \\
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-&\leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\left( \Pb\lbrace \hat{r}_{i,c_j} \geq r_{i,c_j} + s_i \rbrace \bigcup \Pb\lbrace \hat{r}_{i*,c_j} \leq r_{i*,c_j} - s_{i*} \rbrace \right)\leq 2\left(\dfrac{\log(\psi T \epsilon_{m_{i,c_j}}^2)}{2(\psi T)^{\alpha}}\right)\sum_{m=0}^{m_{i,c_j}}\dfrac{1}{\epsilon_{m_{i,c_j}}^{2\alpha + 1}}.
+&\sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\sum_{n_{i*}=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace s_i < s_{i*}\rbrace \leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\sum_{n_{i*}=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace n_i > n_{i*}\rbrace \\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+& \leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\sum_{n_{i*}=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace \hat{r}_{i,c_j} + s_i > \hat{r}_{i*,c_j} + s_{i*} \rbrace \\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\sum_{n_{i*}=1}^{\ell_{m_{i,c_j}}}\left( \Pb\lbrace \hat{r}_{i,c_j} \geq r_{i,c_j} + s_i \rbrace \bigcup \Pb\lbrace \hat{r}_{i*,c_j} \leq r_{i*,c_j} - s_{i*} \rbrace \right)\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\left( \Pb\lbrace \hat{r}_{i,c_j} \geq r_{i,c_j} + s_i \rbrace \right) +  \sum_{m=0}^{m_{i,c_j}}\sum_{n_{i*}=1}^{\ell_{m_{i,c_j}}}\left( \Pb\lbrace \hat{r}_{i*,c_j} \leq r_{i*,c_j} - s_{i*} \rbrace \right) \\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\dfrac{1}{\psi T\epsilon_{m_{i,c_j}}^2} +  \sum_{m=0}^{m_{i,c_j}}\sum_{n_{i*}=1}^{\ell_{m_{i,c_j}}}\dfrac{1}{\psi T\epsilon_{m_{i,c_j}}^2} \\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\leq 2\left(\dfrac{\log(\psi T \epsilon_{m_{i,c_j}}^2)}{2(\psi T)^{\alpha}}\right)\sum_{m=0}^{m_{i,c_j}}\dfrac{1}{\epsilon_{m_{i,c_j}}^{2\alpha + 1}}.
 \end{align*}
@@
 \begin{align*}
-\sum_{m=0}^{m_i}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace n_i > n_{i*}\rbrace \leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace r_{i,c_j} + s_i > r_{i*,c_j} + s_{i*} \rbrace \leq \dfrac{\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi T)^{\alpha}}\sum_{m=0}^{m_{i,c_j}}\dfrac{1}{\epsilon_{m_i}^{2\alpha +1}}.
+\sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\sum_{n_{i*}=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace n_i > n_{i*}\rbrace &\leq \sum_{m=0}^{m_{i,c_j}}\sum_{n_i=1}^{\ell_{m_{i,c_j}}}\sum_{n_{i*}=1}^{\ell_{m_{i,c_j}}}\Pb\lbrace r_{i,c_j} + s_i > r_{i*,c_j} + s_{i*} \rbrace\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\leq \dfrac{\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi T)^{\alpha}}\sum_{m=0}^{m_{i,c_j}}\dfrac{1}{\epsilon_{m_i}^{2\alpha +1}}.
 \end{align*}
@@
 \begin{align*}
-\dfrac{4\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi T)^{\alpha}}\sum_{m=0}^{m_{i,c_j}}\dfrac{1}{\epsilon_{m_{i,c_j}}^{2\alpha +1}} &\leq \dfrac{4\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi T)^{\alpha}}\sum_{m=0}^{M}\left(\dfrac{1}{\epsilon_{m}}\right)^{2\alpha +1} \overset{(a)}{\leq} \dfrac{4\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi T)^{\alpha}}\left(\dfrac{2(2^M - 1)}{2 - 1}\right)^{2\alpha +1} \\
+\dfrac{4\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi T)^{\alpha}}\sum_{m=0}^{m_{i,c_j}}\dfrac{1}{\epsilon_{m_{i,c_j}}^{2\alpha +1}} &\leq \dfrac{4\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi T)^{\alpha}}\sum_{m=0}^{M}\left(\dfrac{1}{\epsilon_{m}}\right)^{2\alpha +1}\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+& \overset{(a)}{\leq} \dfrac{4\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi T)^{\alpha}}\left(\dfrac{(1+\gamma)((1+\gamma)^M - 1)}{(1+\gamma) - 1}\right)^{2\alpha +1} \\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\overset{(b)}{\leq} \dfrac{4\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi T)^{\alpha}}\left(\sqrt{T}\right)^{2\alpha +1} = \dfrac{4\sqrt{T}\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi)^{\alpha}}.
+&\overset{(b)}{\leq} \dfrac{4\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi T)^{\alpha}}\left( \left( \dfrac{1+\gamma}{\gamma}\right) \sqrt{T}\right)^{2\alpha +1} \overset{(c)}{=} \dfrac{4\sqrt{T}\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi)^{\alpha}}.
 \end{align*}
 
-Here, in $(a)$ we use the standard geometric progression formula and in $(b)$ we substitute the value of $M=\dfrac{1}{2}\log_{2}\dfrac{T}{e}$.
+Here, in $(a)$ we use the standard geometric progression formula, in $(b)$ we substitute the value of $M=\dfrac{1}{2}\log_{1+\gamma}\dfrac{T}{e}$ and in $(c)$ we substitute $C_{\gamma}= \left( \dfrac{1+\gamma}{\gamma}\right)$ .
 Bounding this trivially by $T\Delta^{opt}_{i,c_j}$ for each arm $i\in\A$ we get the regret suffered for arm $i$ after the $m_{i,c_j}$-th phase  as,
@@
 \begin{align*}
-\sum_{i\in\A}\left( \dfrac{4T\Delta^{opt}_{i,c_j}\sqrt{T}\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi)^{\alpha}} \right) \leq \sum_{i\in\A}\left( \dfrac{4T^{\frac{3}{2}}\Delta^{opt}_{i,c_j}\log(\psi T (\Delta^{opt}_{i,c_j})^4)}{(\psi)^{\alpha}} \right).
+\sum_{i\in\A}\left( \dfrac{4T\Delta^{opt}_{i,c_j}\sqrt{T}C_{\gamma}\log(\psi T \epsilon_{m_{i,c_j}}^2)}{(\psi)^{\alpha}} \right) \leq \sum_{i\in\A}\left( \dfrac{4T^{\frac{3}{2}}C_{\gamma}\Delta^{opt}_{i,c_j}\log(\psi T (\Delta^{opt}_{i,c_j})^4)}{(\psi)^{\alpha}} \right).
 \end{align*}
@@
 \begin{align*}
-s_i = \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{p_{i,c_j}}^2)}{2n_{i}}} \leq \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{p_{i,c_j}}^2)}{2\ell_{p_{i,c_j}}}} \leq \sqrt{\alpha\epsilon_{p_{i,c_j}}\dfrac{\log(\psi T\epsilon_{p_{i,c_j}}^2)}{\log(\psi T\epsilon_{p_{i,c_j}}^2)}} \leq \dfrac{\Delta^{chg}_{i,c_j}}{4}.
+s_i = \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{p_{i,c_j}}^2)}{2n_{i}}} \leq \sqrt{\dfrac{\alpha\log(\psi T\epsilon_{p_{i,c_j}}^2)}{2\ell_{p_{i,c_j}}}} \leq \sqrt{\alpha\epsilon_{p_{i,c_j}}\dfrac{\log(\psi T\epsilon_{p_{i,c_j}}^2)}{\log(\psi T\epsilon_{p_{i,c_j}}^2)}} \leq \dfrac{\Delta^{chg}_{i,c_j}}{(1+\gamma)^2}.
 \end{align*}
@@
 \begin{align*}
-\hat{r}_{i,c_{j-1}} + s_{i} \leq {r}_{i,c_{j-1}} + 4s_{i} - 2s_{i} \leq {r}_{i,c_{j-1}} + \Delta^{chg}_{i,c_j} -2s_{i} \leq {r}_{i,c_{j}} - 2s_i \leq \hat{r}_{i,c_{j}} - s_i.
+\hat{r}_{i,c_{j-1}} + s_{i} \leq {r}_{i,c_{j-1}} + (1+\gamma)^2 s_{i} - (1+\gamma)s_{i} \leq {r}_{i,c_{j-1}} + \Delta^{chg}_{i,c_j} - (1+\gamma)s_{i} \leq {r}_{i,c_{j}} - (1+\gamma)s_i \leq \hat{r}_{i,c_{j}} - s_i.
 \end{align*}
@@
 \begin{align*}
-\sum_{m=0}^{p_{i,c_j}}\sum_{n_i=\ell_{p_{i-1}}}^{\ell_{p_{i,c_j}}}\Pb\lbrace \hat{r}_{i,c_j} \leq  r_{i,c_j} - s_i \rbrace &\leq \sum_{m=0}^{p_{i,c_j}}\sum_{n_i=\ell_{p_{i-1, c_j}}}^{\ell_{p_{i,c_j}}}\exp\left(-2s_i^2n_i \right) \leq \dfrac{\log(\psi T\epsilon_{p_{i,c_j}}^2)}{2(\psi T)^{\alpha}}\sum_{m=0}^{p_{i,c_j}}\dfrac{1}{\epsilon_{p_{i,c_j}}^{2\alpha + 1}}.
+\sum_{m=0}^{p_{i,c_j}}\sum_{n_i=1}^{\ell_{p_{i,c_j}}}\Pb\lbrace \hat{r}_{i,c_j} \leq  r_{i,c_j} - s_i \rbrace &\leq \sum_{m=0}^{p_{i,c_j}}\sum_{n_i=1}^{\ell_{p_{i,c_j}}}\exp\left(-2s_i^2n_i \right) \leq \dfrac{\log(\psi T\epsilon_{p_{i,c_j}}^2)}{2(\psi T)^{\alpha}}\sum_{m=0}^{p_{i,c_j}}\dfrac{1}{\epsilon_{p_{i,c_j}}^{2\alpha + 1}}.
 \end{align*}
 
+%\ell_{p_{i-1, c_j}}
 Hence, the probability that the changepoint is not detected by the first event in equation \ref{eq:arm-pull-chg} is bounded by,
@@
 \begin{align*}
-\dfrac{2\log(\psi T)}{(\psi T\epsilon_{p_{i,c_j}}^2)^{\alpha}}\sum_{m=0}^{p_{i,c_j}}\dfrac{1}{\epsilon_{p_{i,c_j}}^{2\alpha + 1}} \overset{(a)}{\leq} \dfrac{2\sqrt{T}\log(\psi T \epsilon_{p_{i,c_j}}^2)}{(\psi)^{\alpha}} .
+\dfrac{2\log(\psi T)}{(\psi T\epsilon_{p_{i,c_j}}^2)^{\alpha}}\sum_{m=0}^{p_{i,c_j}}\dfrac{1}{\epsilon_{p_{i,c_j}}^{2\alpha + 1}} \overset{(a)}{\leq} \dfrac{2C_{\gamma}\sqrt{T}\log(\psi T \epsilon_{p_{i,c_j}}^2)}{(\psi)^{\alpha}} .
 \end{align*}
 
-Here, in $(a)$ we follow the same steps as in \textbf{step 4} to reduce the expression to the above form.
+Here, in $(a)$ we substitute $C_{\gamma}=\left( \dfrac{1+\gamma}{\gamma}\right)$ and we follow the same steps as in \textbf{step 4} to reduce the expression to the above form.
 Furthermore, bounding the regret trivially (after the changepoint $c_j$) by $\Delta^{opt}_{i,c_{j+1}}$ for each arm $i\in\A$, we get
@@
 \begin{align*}
-\sum_{i\in\A}\left( \dfrac{2T\Delta^{opt}_{i,c_{j+1}}\sqrt{T}\log(\psi T \epsilon_{p_{i,c_j}}^2)}{(\psi)^{\alpha}} \right) \leq \sum_{i\in\A}\left( \dfrac{2T^{\frac{3}{2}}\Delta^{opt}_{i,c_{j+1}}\log(\psi T (\Delta^{chg}_{i,c_j})^4)}{(\psi)^{\alpha}} \right).
+\sum_{i\in\A}\left( \dfrac{2T\Delta^{opt}_{i,c_{j+1}}\sqrt{T}C_{\gamma}\log(\psi T \epsilon_{p_{i,c_j}}^2)}{(\psi)^{\alpha}} \right) \leq \sum_{i\in\A}\left( \dfrac{2T^{\frac{3}{2}}C_{\gamma}\Delta^{opt}_{i,c_{j+1}}\log(\psi T (\Delta^{chg}_{i,c_j})^4)}{(\psi)^{\alpha}} \right).
 \end{align*}
@@
 %%%%%%%%%%
-+ \underbrace{ \dfrac{4T^{\frac{3}{2}}\Delta^{opt}_{i,c_j}\log(\psi T (\Delta^{opt}_{i,c_j})^4)}{(\psi)^{\alpha}} }_{\textbf{from Step 4}}
++ \underbrace{ \dfrac{4T^{\frac{3}{2}}C_{\gamma}\Delta^{opt}_{i,c_j}\log(\psi T (\Delta^{opt}_{i,c_j})^4)}{(\psi)^{\alpha}} }_{\textbf{from Step 4}}
 %%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-& + \underbrace{ \dfrac{2T^{\frac{3}{2}}\Delta^{opt}_{i,c_{j+1}}\log(\psi T (\Delta^{chg}_{i,c_j})^4)}{(\psi)^{\alpha}} }_{\textbf{from Step 6}}\\
+& + \underbrace{ \dfrac{2T^{\frac{3}{2}}C_{\gamma}\Delta^{opt}_{i,c_{j+1}}\log(\psi T (\Delta^{chg}_{i,c_j})^4)}{(\psi)^{\alpha}} }_{\textbf{from Step 6}}\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-12-23 synopsis/intro1.tex
Latest on 23/12/2017

%In today's world, artificial intelligence has proved to be a game-changer in designing agents that interact with an evolving environment and make decisions on the fly. The main goal of artificial intelligence is to design artificial agents that make dynamic decisions in an evolving environment. In pursuit of these, the agent can be thought of as making a series of sequential decisions by interacting with the dynamic environment which provides it with some sort of feedback after every decision which the agent incorporates into its decision-making strategy to formulate the next decision to be made. A large number of problems in science and engineering, robotics and game playing, resource management, financial portfolio management, medical treatment design, ad placement, website optimization and packet routing can be modeled as sequential decision-making under uncertainty. Many of these real-world interesting online 
%sequential decision-making problems can be formulated as reinforcement learning (RL) problems (\citep{bertsekas1996neuro}, \citep{sutton1998reinforcement}).

In today's world, artificial intelligence has proved to be a game-changer in designing agents that interact with an evolving environment and make decisions on the fly. The main goal of artificial intelligence is to design artificial agents that make dynamic decisions in an evolving environment. In pursuit of these, the agent can be thought of as making a series of sequential decisions by interacting with the dynamic environment which provides it with some sort of feedback or reward after every decision which the agent incorporates into its decision-making strategy to formulate the next decision to be made. In its simplest form, this problem can be captured by the multi-armed bandit (MAB) model. Infact the MAB model can be considered as a single looping state when the agent after taking an action, and observing the reward transitions back to the same state. That single looping state consist of several finite number of actions which are called as arms.

	The name bandit originated from the concept of casino slot machine where there are levers which are termed as arms and the learner can pull one lever and observe the reward associated with that arm, which is sampled from a distribution associated with the specific arm. This game is repeated $T$ times and the goal of the learner is to maximize its profit by finding an action-selection strategy or policy that optimizes some long-term performance measure.

	There are multiple reasons to study the interesting area of bandits. First of all, bandits are the cornerstone of understanding the general reinforcement learning area. Infact, bandits helps us to understand the idea of \textit{exploration-exploitation} dilemma which forms the foundation to build full, multi-state, general reinforcement learning models. Secondly, as stated in \citet{maillard2011apprentissage}, even $50$ years after \cite{robbins1952some} introduced the first idea of bandits, there are many interesting and fruitful areas where bandit concept can be extended in both practical and theoretical terms. Finally, there are several real-life industrial applications ranging from recommendation systems, game theory to anomaly detection where bandit applications have been found to perform exceptionally well. All of these forces us to delve deep into a systemic research of bandits.

%In an RL problem, an agent interacts with a dynamic, stochastic, and unknown environment, with the goal of finding an action-selection strategy or policy that optimizes some long-term performance measure. Every time when the agent interacts with the environment it receives a signal/reward from the environment based on which it modifies its policy. The agent learns to optimize the choice of actions over several time steps which is learned from the sequences of data that it receives from the environment. This is the crux of online sequential learning. 
%
%    This is in contrast to supervised learning methods that deal with labeled data which are independently and identically distributed (i.i.d.) samples from the considered domain and train some classifier on the entire training dataset to learn the pattern of this distribution to predict the labels of future samples (test dataset) with the assumption that it is sampled from the same domain. In contrast to this, an RL agent learns from the samples that are collected from the trajectories generated by its sequential interaction with the system. For an RL agent, the trajectory consists of a series of sequential interactions whereby it transitions from one state to another following some dynamics intrinsic to the environment while collecting the reward till some stopping condition is reached. This is known as an episode. Here, for an action $i_t$ taken by the agent at the $t$-th timestep, the agent transitions from its current state denoted by $S_{i,t}$ to state $S_{i,t+1}$ and observes the reward $X_{i,t}$. An illustrative image depicting the reinforcement learning scenario is shown in Figure \ref{fig:rl}.
%
%\begin{figure}[!th]
%\begin{center}
%\includegraphics[scale=0.3]{synopsis/img/RL1.png}
%\caption{Reinforcement Learning}
%\label{fig:rl}
%\end{center}
%\end{figure}

%Now, for a single-step interaction, i.e., when the episode terminates after a single transition, the problem is captured by the multi-armed bandit (MAB) model. Infact the MAB model can be considered as a single looping state when the agent after taking an action, and observing the reward transitions back to the same state. That single looping state consist of several finite number of actions which are called as arms.

%	The name bandit originated from the concept of casino slot machine where there are levers which are termed as arms and the learner can pull one lever and observe the reward associated with that arm which is sampled from a distribution associated with the specific arm. This game is repeated $T$ times and the goal of the learner is to maximize its profit.

%To express an RL problem more formally, we have to define the idea of Markov Decision Process (MDP) which consists of states, actions, transition probabilities, and rewards which in turn helps in deciding the strategy to be followed by the agent.

%An MDP consists of states

### 2017-12-23 synopsis/motivation.tex
Latest on 23/12/2017

@@
-The MAB model fits very well in various real-world scenarios that can be modeled as sequential decision-making problems. Some of which are mentioned as follows:-
+The MAB model fits very well in various real-world scenarios that can be modeled as decision-making under uncertainty  problems. Some of which are mentioned as follows:-
 \begin{enumerate}
@@
 This process is repeated till a pre-specified number of times with the retailer gathering valuable information regarding the customer from this behaviour and modifying its policy to display other items to different customers.
+In its simplest form,  this can be modeled as a stochastic MAB problem which is studied in the first part of the thesis.
 \item \emph{Medical Treatment Design:} Another interesting domain that MAB model was first studied was for the medical treatment design \citep{thompson1933likelihood},\citep{thompson1935theory}.
@@
 The goal of the learner is to quickly converge on the best treatment so that whenever a new patient comes with the same ailment, the learner can suggest the best treatment which can relive the patient of its ailment with a high probability.
+This problem can also be modeled as a stochastic MAB problem.
 \item \emph{Financial Portfolio Management:} In financial portfolio management MAB models can also be used.
@@
 Then, the goal of the learner is reduced to identifying the best stock option as quickly as possible.
+This is another interesting variation which can modeled as a stochastic MAB problem.
 \item \emph{Product Selection:} A company wants to introduce a new product in market and there is a clear separation of the test phase from the commercialization phase.
@@
 A similar problem has been discussed for single best product variant identification without threshold in \citet{bubeck2011pure}.
+This problem can be modeled as a stochastic thresholding MAB problem which is studied in the second part of the thesis.
 \item \emph{Mobile Phone Channel Allocation:} Another similar problem as above concerns channel allocation for mobile phone communications \citep{audibert2009exploration}.
@@
 Each evaluation of a channel is noisy and the learning algorithm must come up with the best possible set of suggestions within a very small  number of attempts.
+This setting can also be modeled as a stochastic thresholding MAB problem.
 \item \emph{Anomaly Detection and Classification:} MABs can also be used for anomaly detection where the goal is to seek out extreme values in the data.
@@
 Such an approach has already been mentioned in \citet{streeter2006selecting} and further studied in \citet{locatelli2016optimal}.
+Finally, this is also an interesting variation which can be modeled as a stochastic thresholding MAB problem.
 \end{enumerate}

### 2017-12-23 synopsis/intro1.tex
Latest on 23/12/2017

@@
 In pursuit of these, the agent can be thought of as making a series of sequential decisions by interacting with the dynamic environment which provides it with some sort of feedback or reward after every decision which the agent incorporates into its decision-making strategy to formulate the next decision to be made.
-In its simplest form, this problem can be captured by the multi-armed bandit (MAB) model.
-Infact the MAB model can be considered as a single looping state when the agent after taking an action, and observing the reward transitions back to the same state.
+In its simplest form, this problem can be captured by the multi-armed bandit (MAB) model \citep{bertsekas1996neuro}, \citep{sutton1998reinforcement}.
+
+	The name bandit originated from the concept of casino slot machine where there are levers which are termed as arms and the learner can pull one arm and observe the reward associated with that ar.
+This reward is sampled from a probability  distribution associated with that specific arm.
+This game is repeated $T$ times and the goal of the learner is to maximize its profit by finding an action-selection strategy or policy that optimizes some long-term performance measure.
+
+	%Infact the MAB model can be considered as a single looping state when the agent after taking an action, and observing the reward transitions back to the same state.
 That single looping state consist of several finite number of actions which are called as arms.
-
-	The name bandit originated from the concept of casino slot machine where there are levers which are termed as arms and the learner can pull one lever and observe the reward associated with that arm, which is sampled from a distribution associated with the specific arm.
-This game is repeated $T$ times and the goal of the learner is to maximize its profit by finding an action-selection strategy or policy that optimizes some long-term performance measure.
 

### 2017-12-23 synopsis/intro1.tex
Latest on 23/12/2017

@@
 
-	The name bandit originated from the concept of casino slot machine where there are levers which are termed as arms and the learner can pull one arm and observe the reward associated with that ar.
+	The name bandit originated from the concept of casino slot machine where there are levers which are termed as arms and the learner can pull one arm and observe the reward associated with that arm.
 This reward is sampled from a probability  distribution associated with that specific arm.

### 2017-12-23 synopsis/motivation.tex
Latest on 23/12/2017

@@
 In this scenario, at every timestep, the retailer displays an item to a customer from a pool of items which has the highest probability of being selected by the customer.
-The episode ends when the customer selects or does not select a product (which will be considered as a loss to the retailer).
+The one-step interaction ends when the customer selects or does not select a product (which will be considered as a loss to the retailer).
 This feedback is incorporated by the learner as a feedback from the environment and it modifies its policy for the next suggestion.
@@
 Let's also assume that there is a single treatment which will be able to alleviate the patients from their disease.
-Here, the episode ends when the patient responds well or does not respond well to the treatment whereby the learner modifies its policy for the suggestion to the next patient.
+Here, the  one-step interaction ends when the patient responds well or does not respond well to the treatment whereby the learner modifies its policy for the suggestion to the next patient.
 The goal of the learner is to quickly converge on the best treatment so that whenever a new patient comes with the same ailment, the learner can suggest the best treatment which can relive the patient of its ailment with a high probability.

### 2017-12-25 synopsis.tex
Latest on 23/12/2017
Latest on 24/12/2017
Latest on 25/12/2017

@@
 
-\title{A Study on Online Sequential Learning using Bandits}
+\title{Finite-time Analysis of Frequentist Strategies for Multi-armed Bandits}
 
@@
 \label{synopsis:intro}
-\input{synopsis/intro}
+\input{synopsis/intro1}
 
@@
 \ResParam
-\State $\epsilon_{m+1}:=\frac{\epsilon_{m}}{2}$; $B_{m+1}:=B_{m}$
-\State $n_{m+1}:=\bigg\lceil\frac{\log{(\psi T\epsilon_{m+1}^{2})}}{2\epsilon_{m+1}}\bigg\rceil$
+\State $\epsilon_{m+1}:=\frac{\epsilon_{m}}{2}$; $B_{m+1}:=B_{m}$; $n_{m+1}:=\bigg\lceil\frac{\log{(\psi T\epsilon_{m+1}^{2})}}{2\epsilon_{m+1}}\bigg\rceil$
 \State $N_{m+1}:=t+|B_{m+1}| n_{m+1}$; $m:=m+1$
@@
 \\
-	The EUCBV algorithm, which is mainly based on the arm elimination technique of the UCB-Improved algorithm,  remedies these by employing exploration regulatory factor $\psi$ and arm elimination parameter $\rho$ for aggressive elimination of sub-optimal arms.
+	The EUCBV algorithm, which is based on the arm elimination technique of the UCB-Improved algorithm,  remedies these by employing exploration regulatory factor $\psi$ and arm elimination parameter $\rho$ for aggressive elimination of sub-optimal arms.
 Along with these, similar to CCB \citep{liu2016modification} algorithm, EUCBV uses optimistic greedy sampling whereby at every timestep it only pulls the arm with the highest upper confidence bound rather than pulling all the arms equal number of times in each round.
 Also, unlike the UCB-Improved, UCB1, MOSS and OCUCB algorithms (which are based on mean estimation) EUCBV employs mean and variance estimates (as in \citet{audibert2009exploration}) for arm elimination.
-Further, we allow for arm-elimination at every time-step, which is in contrast to the earlier work (e.g., \citet{auer2010ucb}; \citet{even2006action}) where the arm elimination takes place only at the end of the respective exploration rounds.
+Further, we allow for arm-elimination at every time-step, which is in contrast to the earlier work (e.g., \citet{auer2010ucb}; \citet{even2006action}) where the arm elimination takes place at the end of the exploration rounds.
 
@@
 It is important to emphasize that the \emph{thresholding} bandit problem is different from the \emph{threshold} bandit setup studied in \cite{abernethy2016threshold}, where the learner receives an unit reward whenever the value of an observation is above a threshold.
-
 Formally, the problem we consider is the following.
@@
 The details are presented below.
-
 The active set $B_{0}$ is initialized with all the arms from $\mathcal{A}$.
@@
 \section{Proposed Contents of the Thesis}
-
-In chapter 1 (table \ref{tab:chap1}), we discuss on Reinforcement Learning and its connection to bandits, we give an overview of the various types of bandits available in the literature and also discuss about the main objectives of the thesis and our contributions.
+\input{synopsis/contents}
+%The proposed contents of the thesis from chapter 1 to chapter 6 are mentioned below.
+%
+%%In chapter 1, we discuss on Reinforcement Learning and its connection to bandits, we give an overview of the various types of bandits available in the literature and also discuss about the main objectives of the thesis and our contributions.
 Appendix A provides some useful results on Concentration inequalities.
-
+%
+%%(table \ref{tab:chap1})
+%
+%%\begin{center}
+%\begin{table}[!th]
 %\begin{center}
-\begin{table}[!th]
-\begin{center}
-\begin{tabular}{|p{26em}|}
-\hline\\
-\textbf{1. Introduction to Bandits} \\\hline
-1.1 Reinforcement Learning \\
-1.2 Connection between Reinforcement Learning and Bandits \\
-1.3 Why study Bandits?\\
-1.4 Motivation \\
-1.5 Types of Information Feedback\\
-1.6 Different types of Bandits\\
-1.7 Objectives of Thesis\\
-1.8 Contributions of Thesis\\
-1.9 Outline of the Thesis\\
-1.A Appendix A\\
-\hline
-\end{tabular}
-\end{center}
-\caption{Introduction to thesis}
-\label{tab:chap1}
-\end{table}
+%\begin{tabular}{|p{26em}|}
+%\hline\\
+%\textbf{1. Introduction to Bandits} \\\hline
+%1.1 Reinforcement Learning \\
+%1.2 Connection between Reinforcement Learning and Bandits \\
+%1.3 Why study Bandits?\\
+%1.4 Motivation \\
+%1.5 Types of Information Feedback\\
+%1.6 Different types of Bandits\\
+%1.7 Objectives of Thesis\\
+%1.8 Contributions of Thesis\\
+%1.9 Outline of the Thesis\\
+%1.A Appendix A\\
+%\hline
+%\end{tabular}
 %\end{center}
-
-In chapter 2 (table \ref{tab:chap2-3}) we give a detailed overview of the stochastic multi-armed bandit setting and the latest available algorithms in this setting.
-In the next chapter 3 (table \ref{tab:chap2-3}) we introduce our algorithm Efficient UCB Variance (EUCBV) for the stochastic multi-armed bandit setting.
+%%\caption{Chapter 1}
+%\label{tab:chap1}
+%\end{table}
+%%\end{center}
+%
+%
+%%In chapter 2 we give a detailed overview of the stochastic multi-armed bandit setting and the latest available algorithms in this setting.
+In the next chapter 3 we introduce our algorithm Efficient UCB Variance (EUCBV) for the stochastic multi-armed bandit setting.
 We give theoretical guarantees on the performance of EUCBV and also show in numerical simulations that it indeed performs very well as compared to the state-of-the-art algorithms.
-
-\begin{table}[!th]
-\begin{tabular}{p{16em}|p{16em}}
-\hline\\
-\textbf{2. Stochastic Multi-armed Bandits} & \textbf{3. Efficient UCB Variance: An almost optimal algorithm in SMAB setting}\\\hline
-2.1 Introduction to SMAB & 3.1 Introduction\\
-2.2 Notations and assumptions & 3.2 Our Contributions\\
-2.3 Problem Definition & 3.3 Algorithm: Efficient UCB Variance\\
-2.4 Motivation & 3.4 Main Results\\
-2.5 Related Work in SMAB & 3.5 Proofs\\
-2.6 Summary & 3.6 Experiments\\
-& 3.7 Summary\\
-& 3.B Appendix B\\
-\hline
-\end{tabular}
-\caption{Part 1. Stochastic MAB problem}
-\label{tab:chap2-3}
-\end{table}
-
-In the subsequent chapter 4 (table \ref{tab:chap4-5})  we introduce a new variant of pure exploration multi-armed stochastic bandit called the thresholding bandit problem.
+%
+%%(table \ref{tab:chap2-3})
+%
+%\begin{table}[!th]
+%\begin{tabular}{p{16em}|p{16em}}
+%\hline\\
+%\textbf{2. Stochastic Multi-armed Bandits} & \textbf{3. Efficient UCB Variance: An almost optimal algorithm in SMAB setting}\\\hline
+%2.1 Introduction to SMAB & 3.1 Introduction\\
+%2.2 Notations and assumptions & 3.2 Our Contributions\\
+%2.3 Problem Definition & 3.3 Algorithm: Efficient UCB Variance\\
+%2.4 Motivation & 3.4 Main Results\\
+%2.5 Related Work in SMAB & 3.5 Proofs\\
+%2.6 Summary & 3.6 Experiments\\
+%& 3.7 Summary\\
+%& 3.B Appendix B\\
+%\hline
+%\end{tabular}
+%%\caption{Chapter 2 and Chapter 3}
+%\label{tab:chap2-3}
+%\end{table}
+%
+%
+%%In the subsequent chapter 4, we introduce a new variant of pure exploration multi-armed stochastic bandit called the thresholding bandit problem.
 We analyze the connections between thresholding bandit problem and pure exploration problem and also discuss several existing algorithms in both the settings that are relevant to carefully analyze the thresholding bandit problem.
-Then in chapter 5 (table \ref{tab:chap4-5}) we introduce our solution for the thresholding bandit problem, called the Augemented UCB (AugUCB) algorithm.
+Then in chapter 5 we introduce our solution for the thresholding bandit problem, called the Augemented UCB (AugUCB) algorithm.
 We analyze our algorithm AugUCB and derive theoretical guarantees for it as well as show in numerical experiments that it indeed outperforms several state-of-the-art algorithms in the thresholding bandit setting.
-
-\begin{table}[!th]
-\begin{tabular}{p{16em}|p{16em}}
-\hline\\
-\textbf{4. Thresholding Bandits} & \textbf{5. Augmented UCB for Thresholding Bandit Problem}\\\hline
-4.1 Introduction to TBP & 5.1 Introduction\\
-4.2 Notations and assumptions & 5.2 Our Contributions\\
-4.3 Problem Definition & 5.3 Augmented-UCB Algorithm\\
-4.4 Motivation & 5.4 Theoretical Results\\
-4.5 Related Work in Pure Exploration & 5.5 Numerical Experiments\\
-4.6 TBP connection to Pure Exploration & 5.6 Summary\\
-4.7 Related Work in TBP &\\
-4.8 Summary & \\
-\hline
-\end{tabular}
-\caption{Part 2. Thresholding Bandit Problem}
-\label{tab:chap4-5}
-\end{table}
-
-Finally, in chapter 6, we conclude with a brief summarization on the work done in the thesis and discuss future directions.
-
-%(table \ref{tab:chap6})
+%
+%%(table \ref{tab:chap4-5})
+%
+%\begin{table}[!th]
+%\begin{tabular}{p{16em}|p{16em}}
+%\hline\\
+%\textbf{4. Thresholding Bandits} & \textbf{5. Augmented UCB for Thresholding Bandit Problem}\\\hline
+%4.1 Introduction to TBP & 5.1 Introduction\\
+%4.2 Notations and assumptions & 5.2 Our Contributions\\
+%4.3 Problem Definition & 5.3 Augmented-UCB Algorithm\\
+%4.4 Motivation & 5.4 Theoretical Results\\
+%4.5 Related Work in Pure Exploration & 5.5 Numerical Experiments\\
+%4.6 TBP connection to Pure Exploration & 5.6 Summary\\
+%4.7 Related Work in TBP &\\
+%4.8 Summary & \\
+%\hline
+%\end{tabular}
+%%\caption{Chapter 4 and Chapter 5}
+%\label{tab:chap4-5}
+%\end{table}
+%
+%%Finally, in chapter 6, we conclude with a brief summarization on the work done in the thesis and discuss future directions. 
+%
+%
+%
+%%(table \ref{tab:chap6})
 %\begin{table}[!th]
@@
 %\hline\\
-%\textbf{6. Conclusion and Future Direction} \\\hline
-%6.1 Conclusion and Future Direction \\
+%\textbf{6. Conclusions} \\\hline
+%6.1 Conclusions and Future Directions \\
 %\hline
@@
 %\end{center}
-%\caption{Conclusion and Future Direction of thesis}
+%%\caption{Conclusion and Future Direction of thesis}
 %\label{tab:chap6}
@@
 
-%\framebox{
-%      \vbox{\vspace{2mm}
-%%    \hbox to 6.28in { {\bf Improved Changepoint Detection for Piece-wise Stochastic Bandits
-%%		\hfill Winter 2017} }
-%       \vspace{4mm}
-%       \hbox to 6.28in { {\Large \hfill Improved Changepoint Detection for Piece-wise Stochastic Bandits  \hfill} }
-%       \vspace{2mm}
-%       \hbox to 6.28in { {\it \hfill Subhojyoti Mukherjee, Odalric-Ambrym Maillard \hfill} }
-%      \vspace{2mm}}
-%   }
-
-%The outline of the thesis is as follows:
-%\begin{enumerate}
-%\item Introduction to Bandits
-%\item Stochastic Multi-armed Bandits
-%\item Efficient UCB Variance: An almost optimal algorithm in Stochastic Multi-armed Bandit setting
-%\item Thresholding Bandits
-%\item Augmented UCB for Thresholding Bandits Problem
-%%\item Improved Changepoint Detection for Piecewise Stationary Distributions
-%\item Conclusion and Future Direction
-%\end{enumerate}
-
 %\vskip 4cm
 %%%%%%
-\section{Publications}
-\subsection{Papers in Refereed Journals}
+\vspace*{-10mm}
+%\newpage
+\section{Publications from the thesis}
+%\subsection{Papers in Refereed Journals}
 %\begin{enumerate}
@@
 %\end{enumerate}
+\begin{enumerate}
+\item Subhojyoti Mukherjee, K.P.~Naveen, Nandan Sudarsanam, and Balaraman Ravindran, ``\textit{Thresholding Bandit with Augmented UCB}'', \newblock{\em Proceedings of the Twenty-Sixth International Joint Conference on
+               Artificial Intelligence, {IJCAI} 2017, Melbourne, Australia, August
+               19-25, 2017,2515-2521}.
+\item Subhojyoti Mukherjee, K.P.~Naveen, Nandan Sudarsanam, and Balaraman Ravindran, ``\textit{Efficient UCBV: An Almost Optimal Algorithm using Variance Estimates}'', \newblock{\em To appear in Proceedings of the Thirty-Second Association for the Advancement of Artificial Intelligence, {AAAI} 2018, New Orleans, Louisiana, USA, February 2-7}.
+\end{enumerate}
+
+%\subsection{Presentations in Conferences}
 %\begin{enumerate}
-%\item Subhojyoti Mukherjee, K.P.~Naveen, Nandan Sudarsanam, and Balaraman Ravindran, ``\textit{Thresholding Bandit with Augmented UCB}'', \newblock{\em Proceedings of the Twenty-Sixth International Joint Conference on
-%               Artificial Intelligence, {IJCAI} 2017, Melbourne, Australia, August
-%               19-25, 2017,2515-2521}, main conference track.
-%\item Subhojyoti Mukherjee, K.P.~Naveen, Nandan Sudarsanam, and Balaraman Ravindran, ``\textit{Efficient UCBV: An Almost Optimal Algorithm using Variance Estimates}'', \newblock{\em To appear in Proceedings of the Thirty-Second Association for the Advancement of Artificial Intelligence, {AAAI} 2018, New Orleans, Louisiana, USA, February 2-7}, main conference track.
+%\item Presented {\em Thresholding Bandit with Augmented UCB} at the {\bf Twenty-Sixth International Joint Conference on Artificial Intelligence, {IJCAI} 2017}, Melbourne, Australia, August 19-25.
+%\item To present {\em Efficient UCBV: An Almost Optimal Algorithm using Variance Estimates} at the {\bf Thirty-Second Association for the Advancement of Artificial Intelligence, {AAAI} 2018}, New Orleans, Louisiana, USA, February 2-7.
 %\end{enumerate} 
-
-\subsection{Presentations in Conferences}
-\begin{enumerate}
-\item Presented {\em Thresholding Bandit with Augmented UCB} at the {\bf Twenty-Sixth International Joint Conference on Artificial Intelligence, {IJCAI} 2017}, Melbourne, Australia, August 19-25.
-\item To present {\em Efficient UCBV: An Almost Optimal Algorithm using Variance Estimates} at the {\bf Thirty-Second Association for the Advancement of Artificial Intelligence, {AAAI} 2018}, New Orleans, Louisiana, USA, February 2-7.
-\end{enumerate} 
 \end{document}

### 2017-12-25 synopsis/contribution.tex
Latest on 25/12/2017

--- 2017-12-01 Chapter1/contribution.tex
@@
 EUCBV enjoys an order optimal gap-independent regret bound same as that of OCUCB and MOSS, and better than UCB-Improved, UCB1 and UCBV.
-Empirically, in several considered environments EUCBV outperforms most of the state-of-the-art algorithms.
+Empirically, in several environments EUCBV outperforms most of the state-of-the-art algorithms.
 
@@
 This is the first algorithm to employ such an approach for the considered TBP.
-Furthermore, in numerical evaluations we establish in several considered environments that AugUCB outperforms all the algorithms that does not take into consideration the variance of the arms in their action selection strategy.
+Furthermore, in numerical evaluations we establish in several environments that AugUCB outperforms all the algorithms that does not take into consideration the variance of the arms in their action selection strategy.
 
-\item We proposed a general framework of bandit algorithms that combines change-point detection algorithm with aggregation of expert strategies in order to define efficient pulling strategies in context of the piecewise stochastic  distributions.
+%\item We proposed a general framework of bandit algorithms that combines change-point detection algorithm with aggregation of expert strategies in order to define efficient pulling strategies in context of the piecewise stochastic  distributions.
 The algorithms that we proposed for the piecewise stochastic setting are actively adaptive algorithms which performs very similarly to the oracle algorithm which has access to the changepoints and suffers no additional delay in adapting to the changing environment.

### 2018-01-03 Chapter1/contribution.tex
Latest on 4/1/2018

@@
 
-\item We proposed a general framework of bandit algorithms that combines change-point detection algorithm with aggregation of expert strategies in order to define efficient pulling strategies in context of the piecewise stochastic  distributions.
+%\item We proposed a general framework of bandit algorithms that combines change-point detection algorithm with aggregation of expert strategies in order to define efficient pulling strategies in context of the piecewise stochastic  distributions.
 The algorithms that we proposed for the piecewise stochastic setting are actively adaptive algorithms which performs very similarly to the oracle algorithm which has access to the changepoints and suffers no additional delay in adapting to the changing environment.

### 2018-01-03 Chapter1/motivation.tex
Latest on 4/1/2018

@@
-The MAB model fits very well in various real-world scenarios that can be modeled as sequential decision-making problems. Some of which are mentioned as follows:-
+The MAB model fits very well in various real-world scenarios that can be modeled as decision-making under uncertainty  problems. Some of which are as follows:-
 \begin{enumerate}
-\item \emph{Online Shop Domain:} In the online shop domain \cite{ghavamzadeh2015bayesian}, a retailer aims to maximize profit by sequentially suggesting products to online shopping customers.
+\item \emph{Online Shop Domain:} In the online shop domain \citep{ghavamzadeh2015bayesian}, a retailer aims to maximize profit by sequentially suggesting products to online shopping customers.
 In this scenario, at every timestep, the retailer displays an item to a customer from a pool of items which has the highest probability of being selected by the customer.
-The episode ends when the customer selects or does not select a product (which will be considered as a loss to the retailer).
+The one-step interaction ends when the customer selects or does not select a product (which will be considered as a loss to the retailer).
 This feedback is incorporated by the learner as a feedback from the environment and it modifies its policy for the next suggestion.
 This process is repeated till a pre-specified number of times with the retailer gathering valuable information regarding the customer from this behaviour and modifying its policy to display other items to different customers.
-\item \emph{Medical Treatment Design:} Another interesting domain that MAB model was first studied was for the medical treatment design \cite{thompson1933likelihood},\cite{thompson1935theory}.
+In its simplest form,  this can be modeled as a stochastic MAB problem which is studied in the first part of the thesis.
+\item \emph{Medical Treatment Design:} Another interesting domain that MAB model was first studied was for the medical treatment design \citep{thompson1933likelihood},\citep{thompson1935theory}.
 Here at every timestep, the learner chooses to administer one out of several treatments sequentially on a stream of patients who are suffering from the same ailment (say).
 Let's also assume that there is a single treatment which will be able to alleviate the patients from their disease.
-Here, the episode ends when the patient responds well or does not respond well to the treatment whereby the learner modifies its policy for the suggestion to the next patient.
+Here, the  one-step interaction ends when the patient responds well or does not respond well to the treatment whereby the learner modifies its policy for the suggestion to the next patient.
 The goal of the learner is to quickly converge on the best treatment so that whenever a new patient comes with the same ailment, the learner can suggest the best treatment which can relive the patient of its ailment with a high probability.
+This problem can also be modeled as a stochastic MAB problem.
 \item \emph{Financial Portfolio Management:} In financial portfolio management MAB models can also be used.

### 2018-01-03 Chapter1/outline.tex
Latest on 4/1/2018

@@
-In the previous sections, we gave an overview of the various type of bandits available in the literature.
+In this chapter, we gave an overview of the various types of bandits available in the literature and also discussed about the main objectives of the thesis and our contributions.
 In this section, we give a general outline of the thesis that is to follow.
@@
 We analyze our algorithm AugUCB and derive theoretical guarantees for it as well as show in numerical experiments that it indeed outperforms several state-of-the-art algorithms in the thresholding bandit setting.
-Finally, in chapter \ref{chap:psbandit} we introduce the piecewise-stochastic bandit model which is a new variant that strides between the stochastic and adversarial setting.
+Finally, in chapter \ref{ThesisConc} we conclude by briefly summarizing all the problems covered in the thesis and discussing some future directions in which the stated problems can be further extended.
+
+%Finally, in chapter \ref{chap:psbandit} we introduce the piecewise-stochastic bandit model which is a new variant that strides between the stochastic and adversarial setting.
 We discuss extensively on this setting and also provide our solution to this setting and show in numerical simulations that our solution is very close to the optimal solution.

### 2018-01-03 Chapter1/types.tex
Latest on 1/12/2017
Latest on 4/1/2018

@@
 \begin{enumerate}
-\item \textbf{Adversarial bandits: } In adversarial bandits, an adversary decides the payoff for each arm before the learner selects an arm.
+\item \textbf{Adversarial bandits: } One of the first settings that has greatly motivated the studies in bandit literature is the \textit{adversarial setting}.
+In this setting, at every timestep, an adversary chooses the reward for each arm and then the learner selects an arm without the knowledge of the adversary's choice.
+The adversary may or may not be oblivious to the learner's strategy and this forces the learner to employ a randomized algorithm to confuse the adversary.
+Previous works on this have focused on constructing different types of exponential weighting algorithms that are based on the Hedge algorithm that has been proposed before in \citet{littlestone1994weighted},\citet{freund1995desicion} and analyzed in \citet{auer1995gambling}.
+Further variants of this strategy called EXP3 \citep{auer2002nonstochastic}, \citep{auer2002using} and EXP3IX \citep{kocak2014efficient} have also been proposed which incorporates different strategies for exploration to minimize the loss of the learner.
+
+%In adversarial bandits, an adversary decides the payoff for each arm before the learner selects an arm.
 This adversary may or may not be oblivious to the learning algorithm employed by the learner.
 In each of these cases, a different guarantee on the performance of the learner can be arrived at.
-Some of the important papers in this setting are \citet{auer2002nonstochastic}, \citet{auer2002using}, \citet{kocak2014efficient}.
+Some of the important works in this setting can be found in \citet{auer2002nonstochastic}, \citet{auer2002using}, \citet{kocak2014efficient}.
 
-\item \textbf{Piece-wise stationary:} Another setup under this setting can be the piece-wise stationary setting.
+\item \textbf{Piece-wise stationary:} Striding between the two contrasting settings of SMAB and adversarial bandits is the piece-wise stochastic multi-armed bandit setting where there are a finite number of changepoints when the distribution associated with each arm changes abruptly.
+Hence, this setting is neither as pessimistic as adversarial setting nor as optimistic as the stochastic setting.
+Therefore, the two broad class of algorithms mentioned before fail to perform optimally in this setting.
+Several interesting solutions have been proposed before for this setting which can be broadly divided into two categories, passively adaptive and actively adaptive strategies.
+Passively adaptive strategies like Discounted UCB (DUCB) \citep{kocsis2006discounted}, Switching Window UCB (SW-UCB)  \citep{garivier2011upper} and Discounted Thompson Sampling (DTS) \citep{raj2017taming} do not actively try to locate the changepoints but rather try to minimize their losses by concentrating on past few observations.
+Similarly, algorithms like Restarting Exp3 (RExp3) \citep{DBLP:journals/corr/BesbesGZ14} behave pessimistically as like Exp3 but restart after pre-determined phases.
+Hence, RExp3 can also be termed as a passively adaptive algorithm.
+On the other hand, actively adaptive strategies like Adapt-EVE \citep{hartland2007change}, Windowed-Mean Shift \citep{yu2009piecewise}, EXP3.R \citep{allesiardo2017non}, CUSUM-UCB \citep{liu2017change} try to locate the changepoints and restart the chosen bandit algorithms.
+Also, there are Bayesian strategies like Global Change-Point Thompson Sampling (GCTS)\citep{mellor2013thompson} which uses Bayesian changepoint detection to locate the changepoints.
+
+%Another setup under this setting can be the piece-wise stationary setting.
 In this setting, the distribution associated with each arm is not fixed throughout the time horizon and changes either arbitrarily at particular changepoints, or changes at a fixed period.
@@
 \begin{enumerate}
-\item The learner observes an user $u_t$ and the set of arms (articles) $i\in\A$ along with their feature vectors $\mathcal{v}_{i,t},\forall i\in\A_t$.
+\item The learner observes an user $u_t$ and the set of arms (articles) $i\in\A$ along with their feature vectors ${v}_{i,t},\forall i\in\A_t$.
 This vector contains information about both the users and the arms and is referred as the context.

### 2018-01-03 Chapter7/ThesisConc.tex
Latest on 8/12/2017
Latest on 4/1/2018

@@
 
-    For the piecewise stochastic bandits we were able to show empirically that the adaptive algorithms we considered are indeed more powerful than passive algorithms and further work needs to be done to derive the regret bounds for these algorithms.
-Specifically for CPD\ref{alg:CPD3} we find the confidence interval obtained by Laplace method as like UCB-$\delta$ algorithm\citep{abbasi2011improved} very promising and more work needs to be done in this aspect.
+    %For the piecewise stochastic bandits we were able to show empirically that the adaptive algorithms we considered are indeed more powerful than passive algorithms and further work needs to be done to derive the regret bounds for these algorithms.
+    %Specifically for CPD\ref{alg:CPD3} we find the confidence interval obtained by Laplace method as like UCB-$\delta$ algorithm\citep{abbasi2011improved} very promising and more work needs to be done in this aspect.
 

### 2018-01-03 Chapter7/ThesisConc.tex
Latest on 4/1/2018

@@
-In this thesis, we studied three complex bandit problems, the stochastic multi-armed bandit (SMAB) with the goal of cumulative regret minimization, pure exploration stochastic thresholding bandit problem (TBP) with the goal of expected loss minimization and piecewise stationary bandits with the goal of finding adaptive algorithms which detect and adapts to changepoints.
+In this thesis, we studied two complex bandit problems, the stochastic multi-armed bandit (SMAB) with the goal of cumulative regret minimization and pure exploration stochastic thresholding bandit problem (TBP) with the goal of expected loss minimization.
 For the first problem, we devised a novel algorithm called Efficient UCB Variance (EUCBV) which enjoys an order optimal regret bound and performs superbly in diverse stochastic environments.
 In the second part, the thresholding bandit problem, we came up with the novel algorithm called Augmented UCB (AugUCB) which is the first algorithm to use variance estimation for the considered TBP setting and also empirically outperforms most of the other algorithms.
-Finally, we studied the piecewise stochastic bandits and proposed several solutions for adaptive algorithms that detect changepoints and try to adapt accordingly.
+
+% and piecewise stationary bandits with the goal of finding adaptive algorithms which detect and adapts to changepoints
+%Finally, we studied the piecewise stochastic bandits and proposed several solutions for adaptive algorithms that detect changepoints and try to adapt accordingly.
 

### 2018-01-04 Chapter1/types.tex
Latest on 4/1/2017

@@
 In stochastic bandits, the distribution associated with each of the arms remains fixed throughout the time horizon $T$.
-Some of the notable papers associated with this type of setup are \citet{robbins1952some}, \citet{lai1985asymptotically},  \citet{agrawal1995sample}, \citet{auer2002finite}, \citet{auer2010ucb}, \citet{audibert2009minimax}, \citet{lattimore2015optimally}, etc.
-Chapter \ref{chap:SMAB} and Chapter \ref{chap:EUCBV} is based on this setup where we discuss extensively on the latest state-of-the-art algorithms.
+Some of the notable works associated with this type of setup are \citet{robbins1952some}, \citet{lai1985asymptotically},  \citet{agrawal1995sample}, \citet{auer2002finite}, UCB-Improved \citet{auer2010ucb}, \citet{audibert2009minimax}, \citet{lattimore2015optimally}, etc which gives us a broad class of algorithms suited for this setting.
+Chapter \ref{chap:SMAB} and Chapter \ref{chap:EUCBV} is based on this setup where we discuss extensively on the latest state-of-the-art algorithms and discuss their empirical and theoretical performances.
 
@@
 
-\item \textbf{Piece-wise stationary:} Striding between the two contrasting settings of SMAB and adversarial bandits is the piece-wise stochastic multi-armed bandit setting where there are a finite number of changepoints when the distribution associated with each arm changes abruptly.
+\item \textbf{Piece-wise stationary:} Striding between the two contrasting settings of stochastic and adversarial bandits is the \textit{piece-wise stochastic multi-armed bandit setting} where there are a finite number of changepoints when the distribution associated with each arm changes abruptly.
 Hence, this setting is neither as pessimistic as adversarial setting nor as optimistic as the stochastic setting.

### 2018-01-04 Chapter1/types.tex
Latest on 4/1/2017

@@
 Several interesting solutions have been proposed before for this setting which can be broadly divided into two categories, passively adaptive and actively adaptive strategies.
-Passively adaptive strategies like Discounted UCB (DUCB) \citep{kocsis2006discounted}, Switching Window UCB (SW-UCB)  \citep{garivier2011upper} and Discounted Thompson Sampling (DTS) \citep{raj2017taming} do not actively try to locate the changepoints but rather try to minimize their losses by concentrating on past few observations.
+The passively adaptive strategies like Discounted UCB (DUCB) \citep{kocsis2006discounted}, Switching Window UCB (SW-UCB)  \citep{garivier2011upper} and Discounted Thompson Sampling (DTS) first proposed in \citet{raj2017taming} do not actively try to locate the changepoints but rather try to minimize their losses by concentrating on past few observations.
 Similarly, algorithms like Restarting Exp3 (RExp3) \citep{DBLP:journals/corr/BesbesGZ14} behave pessimistically as like Exp3 but restart after pre-determined phases.

### 2018-01-04 Chapter3/introduction.tex
Latest on 4/1/2017

@@
 Our main theoretical results are stated in section~\ref{sec:results}, while the proofs are established in section \ref{sec:proofTheorem}.
-Section~\ref{sec:expt} contains results and discussions from our numerical experiments.
-We summarize in section \ref{sec:conc} and Appendix \ref{sec:app:EUCBV} contains the proofs of the lemmas that have been used for proving the main result.
+Section~\ref{sec:expt} contains results and discussions from our numerical experiments and finally we summarize in section \ref{sec:conc}.
+    %and Appendix \ref{sec:app:EUCBV} contains the proofs of the lemmas that have been used for proving the main result.
 

### 2018-01-04 Chapter3/proofTheorem.tex
Latest on 4/1/2017

@@
 
+\begin{proof}
+The proof is based on contradiction. Suppose
+\begin{eqnarray*}
+\dfrac{\rho m \log(2)}{\log(\psi T) - 2m\log( 2)} > \frac{3}{2}.
+\end{eqnarray*}
+Then, with $\psi=\dfrac{T}{ K^2}$ and $\rho=\dfrac{1}{2}$, we obtain
+\begin{eqnarray*}
+6\log(K) 
+&>& 6\log(T) - 7m\log(2) \\
+&\overset{(a)}{\ge}& 6\log(T) - \frac{7}{2} \log_2\left(\frac{T}{e}\right) \log(2) \\
+&=& 2.5\log(T) + 3.5 \log_2(e)\log(2)  \\
+&\overset{(b)}{=}& 2.5\log(T) +3.5
+\end{eqnarray*}
+where $(a)$ is obtained using $m\leq \dfrac{1}{2} \log_2\left(\dfrac{T}{e}\right)$, while $(b)$ follows from the identity $\log_2(e)\log(2) =1$.
+Finally, for $T\ge K^{2.4}$ we obtain, $6\log(K)>6\log(K)+3.5$, which is a contradiction.
+\hfill $\blacksquare$	
+\end{proof}
+
 \begin{lemma}
@@
 
+\begin{proof}
+
+	In the $m_i$-th round since $z_i\geq n_{m_i}$, by substituting $z_i$ with $n_{m_i}$ we can show that,
+
+\begin{align*}
+	c_{i} &\leq \sqrt{\dfrac{\rho (\hat{v}_i + 2)\epsilon_{m_{i}}\log (\psi T\epsilon_{m_{i}})}{2\log(\psi T\epsilon_{m_{i}}^{2})}} \overset{(a)}{\leq} \sqrt{\dfrac{2\rho\epsilon_{m_{i}}\log (\frac{\psi T\epsilon_{m_{i}}^{2}}{\epsilon_{m_{i}}})}{\log(\psi T\epsilon_{m_{i}}^{2})}} \\
+	%%%%%%%%%%%%%%%%%%%%%%%%%%
+	& = \sqrt{\dfrac{2\rho\epsilon_{m_{i}}\log (\psi T\epsilon_{m_{i}}^{2}) - 2\rho\epsilon_{m_{i}}\log (\epsilon_{m_{i}})}{\log(\psi T\epsilon_{m_{i}}^{2})}} \\
+	%%%%%%%%%%%%%%%%%%%%%%%%%%
+	& \leq  \sqrt{2\rho\epsilon_{m_{i}} - \dfrac{2\rho\epsilon_{m_i}\log(\frac{1}{2^{m_i}})}{\log(\psi T \frac{1}{2^{2m_i}})}} \\
+	%%%%%%%%%%%%%%%%%%%%%%%%%%
+	&\leq \sqrt{2\rho\epsilon_{m_{i}} + \dfrac{2\rho\epsilon_{m_i}\log(2^{m_i})}{\log(\psi T) - \log( 2^{2m_i})}}\\
+	%%%%%%%%%%%%%%%%%%%%%%%%%%
+	& \leq \sqrt{2\rho\epsilon_{m_{i}} + \dfrac{2\rho\epsilon_{m_i}m_i \log(2)}{\log(\psi T) - 2m_i\log( 2)}} \\ 
+	%%%%%%%%%%%%%%%%%%%%%%%%%%
+	 & \overset{(b)}{\leq} \sqrt{2\rho\epsilon_{m_{i}} + 2.\frac{3}{2}\epsilon_{m_i}} 
+	  < \sqrt{4\epsilon_{m_i}} < \dfrac{\Delta_{i}}{4}.
+	\end{align*}
+In the above simplification, $(a)$ is due to $\hat{v}_i \in [0,1]$, while $(b)$ is obtained using Lemma~\ref{proofTheorem:Lemma:1}.
+% < \dfrac{\Delta_{i}}{4 \sigma_i^2} \overset{(c)}{<}
+% and $(c)$ happens because $\sigma_i \in (0,1]$. 
+%Similarly, it can be shown that $c^* < \frac{\Delta_i}{4}$ in round $m_i$.
+\hfill $\blacksquare$	
+\end{proof}
+
 \begin{lemma}
@@
 \end{lemma}
+
+\begin{proof}
+
+We start by recalling from equation (\ref{eq:prob_eq2}) that,
+
+\begin{align}
+\mathbb{P}(\hat{r}_{i}> r_{i} + c_{i})
+&\leq \mathbb{P}\left( \hat{r}_{i} > r_{i}+ \bar{c}_i\right) 
++ \mathbb{P}\left( \hat{v}_{i}\geq \sigma_{i}^{2}+\sqrt{\epsilon_{m_{i}}}\right)\label{eq:prob_eq3}
+\end{align}
+where 
+\begin{align*}
+&c_i =\sqrt{\frac{\rho (\hat{v}_i + 2)\log (\psi T\epsilon_{m_{i}})}{4 z_i}} \text{ and } \\
+&\bar{c}_i=\sqrt{\dfrac{\rho (\sigma_{i}^{2}+\sqrt{\epsilon_{m_{i}}} + 2)\log(\psi T\epsilon_{m_{i}})}{4 z_i}}.
+\end{align*}
+
+Note that, substituting $ z_i \geq n_{m_i} \geq \frac{\log{(\psi T\epsilon_{m_{i}})}}{2\epsilon_{m_{i}}}$, $\bar{c}_i$ can be simplified to obtain,
+\begin{align}
+\bar{c}_i
+\leq \sqrt{\dfrac{\rho\epsilon_{m_{i}}(\sigma_{i}^{2}+\sqrt{\epsilon_{m_{i}}} + 2)}{2}}\leq \sqrt{ \epsilon_{m_{i}}}.
+\label{si_bar_equn}
+\end{align}
+%
+The first term in the LHS of (\ref{eq:prob_eq3}) can be bounded using the Bernstein inequality as below:
+\begin{align}
+&\mathbb{P}\left( \hat{r}_{i} > r_{i}+ \bar{c}_i\right)\nonumber 
+\le \exp\left(- \dfrac{(\bar{c}_i)^2 z_{i}}{2\sigma_i^2 + \frac{2}{3}\bar{c}_i} \right)\nonumber 
+%%%%%%%%%%%%%%%
+\\
+& \overset{(a)}{\le} \exp\left(- \rho \left(\dfrac{3\sigma_{i}^{2}+3\sqrt{\epsilon_{m_{i}}} + 6}{6\sigma_i^2 + 2\sqrt{\epsilon_{m_i}}} \right)\log(\psi  T\epsilon_{m_{i}}\right)\nonumber \\
+%%%%%%%%%%%%%%%
+% &\le \exp\left(- \rho (\sigma_{i}^{2}+\sqrt{\epsilon_{m_{i}}} + 2)\log(\psi  T\epsilon_{m_{i}})\right)\nonumber \\
+%%%%%%%%%%%%%%%
+& \overset{(b)}{\leq} \exp\left(- \rho \log(\psi  T\epsilon_{m_{i}})\right) 
+%%%%%%%%%%%%%%%
+\le \dfrac{1}{(\psi  T\epsilon_{m_{i}})^{\frac{3\rho}{2}}}
+\label{lhs1_equn}
+\end{align}
+where, $(a)$ is obtained by substituting equation \ref{si_bar_equn} and $(b)$ occurs because for all $\sigma_{i}^2 \in [0,\frac{1}{4}]$, $\left(\frac{3\sigma_{i}^{2}+3\sqrt{\epsilon_{m_{i}}} + 6}{6\sigma_i^2 + 2\sqrt{\epsilon_{m_i}}}\right) \geq \frac{3}{2}$ .
+
+The second term in the LHS of (\ref{eq:prob_eq3}) can be simplified as follows:
+\begin{align}
+&\mathbb{P}\bigg\lbrace \hat{v}_{i}\geq \sigma_{i}^{2}+\sqrt{\epsilon_{m_{i}}}\bigg\rbrace\nonumber\\
+%%%%%%%%%%%%%%%%%%
+&\leq \mathbb{P}\bigg\lbrace \dfrac{1}{n_{i}}\sum_{t=1}^{n_{i}}(X_{i,t}-r_{i})^{2}-(\hat{r}_{i}-r_{i})^{2}\geq \sigma_{i}^{2}+\sqrt{\epsilon_{m_{i}}}\bigg\rbrace\nonumber\\
+%%%%%%%%%%%%%%%%%%
+&\leq \mathbb{P}\bigg\lbrace \dfrac{\sum_{t=1}^{n_{i}}(X_{i,t}-r_{i})^{2}}{n_{i}}\geq \sigma_{i}^{2}+\sqrt{\epsilon_{m_{i}}} \bigg\rbrace\nonumber\\
+%%%%%%%%%%%%%%%%%%
+&\overset{(a)}{\leq} \mathbb{P}\bigg\lbrace \dfrac{\sum_{t=1}^{n_{i}}(X_{i,t}-r_{i})^{2}}{n_{i}}\geq \sigma_{i}^{2} + \bar{c}_i\bigg\rbrace \nonumber\\
+%%%%%%%%%%%%%%%%%%
+&\overset{(b)}{\leq} \exp\left(- \rho \left(\dfrac{3\sigma_{i}^{2}+3\sqrt{\epsilon_{m_{i}}} + 6}{6\sigma_i^2 + 2\sqrt{\epsilon_{m_i}}} \right)\log(\psi  T\epsilon_{m_{i}})\right)
+%%%%%%%%%%%%%%%%%
+\le \dfrac{1}{(\psi  T\epsilon_{m_{i}})^{\frac{3\rho}{2}}}
+\label{lhs2_equn}
+\end{align}
+where inequality $(a)$ is obtained using (\ref{si_bar_equn}), while $(b)$ follows from the Bernstein inequality.
+
+Thus, using (\ref{lhs1_equn}) and (\ref{lhs2_equn}) in (\ref{eq:prob_eq3}) we obtain $\mathbb{P}(\hat{r}_{i}> r_{i} + c_{i})\le \dfrac{2}{(\psi  T\epsilon_{m_{i}})^{\frac{3\rho}{2}}}$.
+\hfill $\blacksquare$	
+\end{proof}
 
@@
 
+\begin{proof}
+From the definition of $c_i$ we know that $c_i\propto \frac{1}{z_i}$ as $\psi$ and $T$ are constants. Therefore in the $m_i$-th round,
+\begin{align*}
+&\Pb\lbrace c^{*} > c_i \rbrace
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\leq  \Pb\lbrace  z^* < z_i  \rbrace \\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\leq \sum_{m=0}^{m_i}\sum_{z^* =1}^{n_{m}}\sum_{z_i =1}^{n_{m}}\bigg(\Pb\lbrace \hat{r}^* < r^* - c^{*}\rbrace + \Pb\lbrace \hat{r}_i > r_i + c_i\rbrace\bigg)
+\end{align*}
+
+%Again, we can show that
+%\begin{align*}
+%&\sum_{m=0}^{m_i}\sum_{z^* =1}^{n_{m_i}}\sum_{z_i =1}^{n_{m_i}}\mathbb{I}_{i}\cup\mathbb{I}_{*} \leq \sum_{m=0}^{m_i}|B_{m_i}|n_{m_i} \\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%&\leq \sum_{m=0}^{m_i}\dfrac{4K}{(\psi T \epsilon_{m_i})^{\frac{3\rho}{2}}}\dfrac{\log{(\psi T\epsilon_{m_{i}}^{2})}}{2\epsilon_{m_{i}}} 
+%%\leq 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\overset{(a)}{\leq} \sum_{m=0}^{m_i}\dfrac{4K}{(\psi T \epsilon_{m_i})^{\frac{3\rho}{2}}}\dfrac{2\log(\frac{T}{K})}{2\epsilon_{m_i}}
+%\end{align*}
+%
+%Here, in $(a)$ happens by substituting the value of $\psi$ and considering $\epsilon_{m_i}\in [\sqrt{\frac{e}{T}},1]$.
+
+Now, applying Bernstein inequality and following the same way as in Lemma \ref{proofTheorem:Lemma:3} we can show that,
+\begin{align*}
+&\Pb\lbrace \hat{r}^* < r^* - c^{*}\rbrace \leq \exp(- \frac{(c^{*})^2}{2\sigma_*^2 + \frac{2 c^{*}}{3}} z^*)\leq \frac{4}{(\psi T\epsilon_{m_i})^{\frac{3\rho}{2}}} \\ 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\Pb\lbrace \hat{r}_i > r_i + c_i\rbrace \leq \exp(- \frac{(c_{i})^2}{2\sigma_i^2 + \frac{2 c_{i}}{3}} z_i)\leq \frac{4}{(\psi T\epsilon_{m_i})^{\frac{3\rho}{2}}}
+\end{align*}
+
+Hence, summing everything up, 
+\begin{align*}
+&\Pb\lbrace c^{*} > c_i \rbrace \\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\leq \sum_{m=0}^{m_i}\sum_{z^* =1}^{n_{m}}\sum_{z_i =1}^{n_{m}}\bigg(\Pb\lbrace \hat{r}^* < r^* - c^{*}\rbrace + \Pb\lbrace \hat{r}_i > r_i + c_i\rbrace\bigg)\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\overset{(a)}{\leq} \sum_{m=0}^{m_i}|B_{m}|n_{m}\bigg(\Pb\lbrace \hat{r}^* < r^* - c^{*}\rbrace + \Pb\lbrace \hat{r}_i > r_i + c_i\rbrace\bigg)\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\overset{(b)}{\leq} \sum_{m=0}^{m_i}\dfrac{4K}{(\psi T \epsilon_{m_i})^{\frac{3\rho}{2}}}\dfrac{\log{(\psi T\epsilon_{m}^{2})}}{2\epsilon_{m}}\times 
+\\
+&\bigg(\Pb\lbrace \hat{r}^* < r^* - c^{*}\rbrace + \Pb\lbrace \hat{r}_i > r_i + c_i\rbrace\bigg)\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\overset{(c)}{\leq} \sum_{m=0}^{m_i}\dfrac{4K}{(\psi T \epsilon_{m})^{\frac{3\rho}{2}}}\dfrac{\log(T)}{\epsilon_{m}}\bigg[\frac{4}{(\psi T\epsilon_{m})^{\frac{3\rho}{2}}} + \frac{4}{(\psi T\epsilon_{m})^{\frac{3\rho}{2}}}  \bigg]\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\leq \sum_{m=0}^{m_i}\dfrac{32K\log T}{(\psi T\epsilon_{m})^{3\rho}\epsilon_{m}} \leq 
+\dfrac{32K\log T}{(\psi T)^{3\rho}}\sum_{m=0}^{m_i}\dfrac{1}{\epsilon_{m}^{3\rho + 1}} \\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\overset{(d)}{\leq} \sum_{m=0}^{m_i}\dfrac{32K\log T}{(\psi T)^{3\rho}}\left(\sum_{m=0}^{m_i}\dfrac{1}{\epsilon_{m}}\right)^{3\rho + 1}\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\overset{(e)}{\leq} 
+\dfrac{32 K\log T}{(\frac{T^2}{K^2})^{\frac{3}{2}}}\bigg[\left( 1 + \dfrac{2(2^{ \frac{1}{2}\log_{2} \frac{T}{e}}-1)}{2-1} \right)^{\frac{5}{2}}\bigg] \\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\leq \dfrac{182 K^4 T^{\frac{5}{4}}\log T}{T^3} \overset{(f)}{\leq} \dfrac{182 K^4}{T^{\frac{5}{4}}} \overset{(g)}{\leq} \dfrac{182 K^4}{T^{\frac{5}{4}}\sqrt{\epsilon_{m_i}}}
+\end{align*}
+
+where, $(a)$ comes from the total pulls allocated for all $i\in B_m$ till the $m$-th round, in $(b)$ the arm count $|B_m|$ can be bounded by using equation $(\ref{eq:arm:elim:c1})$ and then we substitute the value of $n_{m}$, $(c)$ happens by substituting the value of $\psi$ and considering $\epsilon_{m}\in [\sqrt{\frac{e}{T}},1]$, $(d)$ follows as $\frac{1}{\epsilon_{m}}\geq 1,\forall m $, in $(e)$ we use the standard geometric progression formula and then we substitute the values of $\rho$ and $\psi$, $(f)$ follows from the inequality $\log T \leq \sqrt{T}$ and $(g)$ is valid for any $\epsilon_{m_i}\in[\sqrt{\frac{e}{T}},1]$.
+
+\hfill $\blacksquare$	
+\end{proof}
+
 \begin{lemma}
@@
 \end{lemma}
+
+\begin{proof}
+Following a similar argument as in Lemma \ref{proofTheorem:Lemma:4}, we can show that in the $m_i$-th round,
+\begin{align*}
+\Pb\lbrace z_i < n_{m_i} \rbrace 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\leq \sum_{m=0}^{m_i}\sum_{z_i =1}^{n_{m}}\sum_{z^* =1}^{n_{m}}\bigg(\Pb\lbrace \hat{r}^* > r^* - c^{*}\rbrace + \Pb\lbrace \hat{r}_i < r_i + c_i\rbrace\bigg) \\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\leq \dfrac{32K\log T}{(\psi T)^{3\rho}}\sum_{m=0}^{m_i}\dfrac{1}{\epsilon_{m}^{3\rho + 1}}\leq \dfrac{182 K^4}{T^{\frac{5}{4}}\sqrt{\epsilon_{m_i}}}.
+\end{align*}
+\hfill $\blacksquare$	
+\end{proof}
 
@@
 
+\begin{proof}
+We again prove this by contradiction. Suppose, 
+\begin{align*}
+c_1 \dfrac{4\sigma_i^2 + 4}{\Delta_i}\log\bigg( \dfrac{T\Delta_i^2}{K}\bigg) > c_2 \dfrac{\sigma_i^2}{\Delta_i}\log\bigg( \dfrac{T\Delta_i^2}{K}\bigg).
+\end{align*}
+
+Further reducing the above two terms we can show that,
+
+\begin{align*}
+& 4c_1\sigma_i^2 + 4c_1 > c_2\sigma_i^2\\
+& \Rightarrow 4c_1.\dfrac{1}{4} + 4c_1 \overset{(a)}{>} \dfrac{c_2}{4}\\
+& \Rightarrow 20 c_1 > c_2.
+\end{align*}
+
+Here, $(a)$ occurs because $0\leq\sigma_i^2 \leq \frac{1}{4},\forall i\in \A$. But, we already know that $20 c_1 \leq c_2$. Hence, 
+\begin{align*}
+c_1 \dfrac{4\sigma_i^2 + 4}{\Delta_i}\log\bigg( \dfrac{T\Delta_i^2}{K}\bigg) \leq c_2 \dfrac{\sigma_i^2}{\Delta_i}\log\bigg( \dfrac{T\Delta_i^2}{K}\bigg).
+\end{align*}
+
+\hfill $\blacksquare$	
+\end{proof}
+
 %\begin{lemma}
@@
 
-The proofs of lemmas \ref{proofTheorem:Lemma:1} - \ref{proofTheorem:Lemma:6} can be found in Appendix ~\ref{App:Lemma:1}, ~\ref{App:Lemma:2}, ~\ref{App:Lemma:3}, ~\ref{App:Lemma:4}, ~\ref{App:Lemma:5} and
- ~\ref{App:Lemma:6} respectively.
+%The proofs of lemmas \ref{proofTheorem:Lemma:1} - \ref{proofTheorem:Lemma:6} can be found in Appendix ~\ref{App:Lemma:1}, ~\ref{App:Lemma:2}, ~\ref{App:Lemma:3}, ~\ref{App:Lemma:4}, ~\ref{App:Lemma:5} and ~\ref{App:Lemma:6} respectively.
 

### 2018-01-08 Chapter1/connBandits.tex
Latest on 8/1/2017

@@
-As defined in the previous section, an episode consist of a series of sequential interaction where as agent transitions from one state to another based on some intrinsic dynamics of the environment while collecting the rewards and choosing actions based on some action-selecting strategy.
+As defined in the previous section, an episode consists of a series of sequential interaction whereas agent transitions from one state to another based on some intrinsic dynamics of the environment while collecting the rewards and choosing actions based on some action-selecting strategy.
 Now, for a single-step interaction, i.e., when the episode terminates after a single transition, the problem is captured by the multi-armed bandit (MAB) model.
-Infact the MAB model can be considered as a single looping state when the agent after taking an action, and observing the reward transitions back to the same state.
-That single looping state consist of several finite number of actions which are called as arms.
+In fact, the MAB model can be considered as a single looping state when the agent after taking an action and observing the reward transitions back to the same state.
+That single looping state consists of several finite number of actions which are called as arms.
 

### 2018-01-08 Chapter1/contribution.tex
Latest on 8/1/2017

--- 2017-12-01 Chapter1/contribution.tex
@@
 This is the first algorithm to employ such an approach for the considered TBP.
-Furthermore, in numerical evaluations we establish in several considered environments that AugUCB outperforms all the algorithms that does not take into consideration the variance of the arms in their action selection strategy.
+Furthermore, in numerical evaluations, we establish in several considered environments that AugUCB outperforms all the algorithms that do not take into consideration the variance of the arms in their action selection strategy.
 
-\item We proposed a general framework of bandit algorithms that combines change-point detection algorithm with aggregation of expert strategies in order to define efficient pulling strategies in context of the piecewise stochastic  distributions.
-The algorithms that we proposed for the piecewise stochastic setting are actively adaptive algorithms which performs very similarly to the oracle algorithm which has access to the changepoints and suffers no additional delay in adapting to the changing environment.
+%\item We proposed a general framework of bandit algorithms that combines change-point detection algorithm with aggregation of expert strategies in order to define efficient pulling strategies in the context of the piecewise stochastic distributions.
+The algorithms that we proposed for the piecewise stochastic setting are actively adaptive algorithms which perform very similarly to the oracle algorithm which has access to the changepoints and suffers no additional delay in adapting to the changing environment.
 \end{enumerate}

### 2018-01-08 Chapter1/feedback.tex
Latest on 26/11/2017
Latest on 8/1/2017

@@
 The learning proceeds as follows, at every timestep the learner selects $m\in\A$ actions and observes some form of feedback vector $R^{obs}_{t}$ (which will be characterized later).
-Before the learner selects the  the set of arms the environment draws the feedback vector $F^{env}_t\in[0,1]^{K}$ of $K$ i.i.d random rewards for all actions $i\in\A$ from $D_i,\forall i\in\A$ which it decides to reveal in particular format depending on the form of feedback chosen for the game, that is full information, partial information or bandit feedback.
+Before the learner selects the set of arms the environment draws the feedback vector $F^{env}_t\in[0,1]^{K}$ of $K$ i.i.d random rewards for all actions $i\in\A$ from $D_i,\forall i\in\A$ which it decides to reveal in particular format depending on the form of feedback chosen for the game, that is full information, partial information or bandit feedback.
 This game is shown in algorithm \ref{alg:OSeqGame}.
@@
 \State The environment chooses a reward vector $F^{env}_{t}= \left[r_{i,t}\sim^{i.i.d} D_{i},\forall i\in\A\right]$.
-\State The learner chooses $m$ actions such that $m < K$, where $\A$ is the set of arms and $|\A|=K$.
+\State The learner chooses $m$ actions such that $m < K$ following some policy $\pi$, where $\A$ is the set of arms and $|\A|=K$.
 \State The learner observes the reward vector $R^{obs}_{t}\subseteq F^{env}_{t}$.
@@
 
-%Let $G(V,E)$ denote a graph where $V$ denotes the set of nodes in the graph and $E$ denotes the set of edges of the graph.
+%Let $G(V, E)$ denote a graph where $V$ denotes the set of nodes in the graph and $E$ denotes the set of edges of the graph.
 Let there be a single starting node, denoted by $\mathcal{s}\in V$ from where the learner must start and try to reach the destination node denoted by $\mathcal{d}\in V$.

### 2018-01-08 Chapter1/motivation.tex
Latest on 8/1/2017

@@
 Here, the one-step interaction ends when the patient responds well or does not respond well to the treatment whereby the learner modifies its policy for the suggestion to the next patient.
-The goal of the learner is to quickly converge on the best treatment so that whenever a new patient comes with the same ailment, the learner can suggest the best treatment which can relive the patient of its ailment with a high probability.
+The goal of the learner is to quickly converge on the best treatment so that whenever a new patient comes with the same ailment, the learner can suggest the best treatment which can relieve the patient of its ailment with a high probability.
 This problem can also be modeled as a stochastic MAB problem.
@@
 Here, the learner is faced with the choice of selecting the most profitable stock option out of several stock options.
-The simplest strategy where we can employ a bandit model is this; at the start of every trading session the learner suggests a stock to purchase worth Re $1$, while at the closing of the trading session it sells off the stock to witness its value after a day's trading.
+The simplest strategy where we can employ a bandit model is this; at the start of every trading session, the learner suggests a stock to purchase worth Re $1$, while at the closing of the trading session it sells off the stock to witness its value after a day's trading.
 The profit recorded is treated as the reward revealed by the environment and the learner modifies its policy for the next day.
-Let's assume that no new stock options are being introduced over the considered time horizon and there is a single best stock option which if selected for perpetuity will always give the best returns.
+Let's assume that no new stock options are being introduced over the considered time horizon and there is a single best stock option which if selected in perpetuity will always give the best returns.
 Then, the goal of the learner is reduced to identifying the best stock option as quickly as possible.
-This is another interesting variation which can modeled as a stochastic MAB problem.
-\item \emph{Product Selection:} A company wants to introduce a new product in market and there is a clear separation of the test phase from the commercialization phase.
-In this case the company tries to minimize the loss it might incur in the commercialization phase by testing as much as possible in the test phase.
-So from the several variants of the product that are in the test phase the learning learner must suggest the product variant(s) whose qualities are above a particular threshold $\tau$ at the end of the test phase that have the highest probability of minimizing loss in the commercialization phase.
+This is another interesting variation which can be modeled as a stochastic MAB problem.
+\item \emph{Product Selection:} A company wants to introduce a new product in the market and there is a clear separation of the test phase from the commercialization phase.
+In this case, the company tries to minimize the loss it might incur in the commercialization phase by testing as much as possible in the test phase.
+So from the several variants of the product that is in the test phase, the learning learner must suggest the product variant(s) whose qualities are above a particular threshold $\tau$ at the end of the test phase that has the highest probability of minimizing the loss in the commercialization phase.
 A similar problem has been discussed for single best product variant identification without threshold in \citet{bubeck2011pure}.
@@
 Here there is a clear separation between the allocation phase and communication phase whereby in the allocation phase a learner has to explore as many channels as possible to suggest the best possible set of channel(s) whose qualities are above a particular threshold $\tau$.
-The threshold may depend on the subscription level of the customer such that with higher subscription the customer is allowed better channel(s) with the $\tau$ set high.
+The threshold may depend on the subscription level of the customer such that with the higher subscription the customer is allowed better channel(s) with the $\tau$ set high.
 Each evaluation of a channel is noisy and the learning algorithm must come up with the best possible set of suggestions within a very small number of attempts.

### 2018-01-08 Chapter1/objective.tex
Latest on 8/1/2017

@@
 We intend to give strong gap-dependent and gap-independent regret guarantees in the SMAB setting.
-We also intend to provide algorithm in the SMAB setting that outperforms the current state-of-the-art algorithms in this setting.
+We also intend to provide the algorithm in the SMAB setting that outperforms the current state-of-the-art algorithms in this setting.
 
 \item The second objective of this thesis is to study the area of thresholding bandit problem (TBP) setting where the goal is to minimize the expected loss at the end of a fixed budget provided as input.
-We intend to provide strong guarantees with respect to expected loss and also propose algorithm that does not require any problem complexity as an input.
+We intend to provide strong guarantees with respect to expected loss and also propose the algorithm that does not require any problem complexity as an input.
 We also intend to provide strong empirical evaluations of the algorithm proposed for the TBP setting.
 
-\item The third objective of this thesis is to study the area of piecewise stochastic bandit where again the goal is to minimize the cumulative regret.
+%\item The third objective of this thesis is to study the area of piecewise stochastic bandit where again the goal is to minimize the cumulative regret.
 We intend to provide strong algorithms that can adapt to this environment and performs well empirically.

### 2018-01-08 Chapter1/studyBandit.tex
Latest on 8/1/2017

@@
 First of all, bandits are the cornerstone of understanding the general reinforcement learning area.
-Infact, bandits helps us to understand the idea of \textit{exploration-exploitation} dilemma which is the basis to build full, multi-state, general reinforcement learning ideas.
+In fact, bandits help us to understand the idea of \textit{exploration-exploitation} dilemma which is the basis to build full, multi-state, general reinforcement learning ideas.
 Secondly, as stated in \citet{maillard2011apprentissage}, even $50$ years after \cite{robbins1952some} introduced the first idea of bandits, there are many interesting and fruitful areas where bandit concept can be extended in both practical and theoretical terms.

### 2018-01-08 Chapter2/motivation.tex
Latest on 8/1/2017

@@
 There has been a significant amount of research in the area of stochastic MABs.
-One of the earliest work can be traced to \citet{thompson1933likelihood}, which deals with  the problem of choosing between two treatments to administer on patients who come in sequentially.
+One of the earliest work can be traced to \citet{thompson1933likelihood}, which deals with the problem of choosing between two treatments to administer to patients who come in sequentially.
 In \citet{thompson1935theory} this work was extended to include more general cases of finitely many treatments.

### 2018-01-08 Chapter4/intro.tex
Latest on 8/1/2017

@@
 In the previous chapters \ref{chap:SMAB} and \ref{chap:EUCBV} we studied the stochastic multi-armed bandit (SMAB) setting with the goal of minimizing cumulative regret.
-In this chapter we will study another setting called Pure-exploration multi-armed bandits.
+In this chapter, we will study another setting called Pure-exploration multi-armed bandits.
 An interested reader can read through the previous chapters or can continue from here.
@@
 Here, the learning algorithm is provided with a threshold $\tau$, and the objective, after exploring for $T$ rounds, is to output all arms $i$ whose $r_{i}$ is above $\tau$.
-It is important to emphasize that the \emph{thresholding} bandit problem is different from the \emph{threshold} bandit setup studied in \cite{abernethy2016threshold}, where the learner receives an unit reward whenever the value of an observation is above a threshold.
+It is important to emphasize that the \emph{thresholding} bandit problem is different from the \emph{threshold} bandit setup studied in \cite{abernethy2016threshold}, where the learner receives a unit reward whenever the value of an observation is above a threshold.
 

### 2018-01-08 Chapter4/prevRes.tex
Latest on 8/1/2017

@@
-Significant amount of literature is available on the stochastic MAB setting with respect to minimizing the cumulative regret.
+A significant amount of literature is available on the stochastic MAB setting with respect to minimizing the cumulative regret.
 Chapter \ref{chap:SMAB} and \ref{chap:EUCBV} deals with that.
-In this work we are particularly interested in \emph{pure-exploration MABs},  where the focus in primarily on simple regret rather than the cumulative regret.
+In this work, we are particularly interested in \emph{pure-exploration MABs},  where the focus is primarily on simple regret rather than the cumulative regret.
 The relationship between cumulative regret and simple regret is proved in \citet{bubeck2011pure} where the authors prove that minimizing the simple regret necessarily results in maximizing the cumulative regret.
-The pure exploration problem has been explored  mainly under the following two settings:
+The pure exploration problem has been explored  mainly in the following two settings:
 
@@
 
-The goal in best p-arms setting is to identify the top $p$ arms out of $K$ given arms where $p$ is supplied as an input.
-Several algorithms have been proposed for these setup starting with \citet{gabillon2011multi} where the authors proposed the GapE and GapE-V algorithms that suggest, with high probability, the best-$p$ arms at the end of the time budget.
-These algorithms are similar to the UCBE type algorithm discussed in previous section.
-In this section we will discuss the Successive Accept Reject strategy shown in algorithm \ref{alg:sar}.
+The goal in the best p-arms setting is to identify the top $p$ arms out of $K$ given arms where $p$ is supplied as an input.
+Several algorithms have been proposed for this setup starting with \citet{gabillon2011multi} where the authors proposed the GapE and GapE-V algorithms that suggest, with high probability, the best-$p$ arms at the end of the time budget.
+These algorithms are similar to the UCBE type algorithm discussed in the previous section.
+In this section, we will discuss the Successive Accept Reject strategy shown in algorithm \ref{alg:sar}.
 
@@
 
-In this setting the learning algorithm has to suggest the best arm(s) with a fixed confidence (given as input) with as fewer number of attempts as possible.
+In this setting, the learning algorithm has to suggest the best arm(s) with a fixed confidence (given as input) with as fewer number of attempts as possible.
 The single best arm identification has been studied in \citet{even2006action}, while for the combinatorial setup \citet{kalyanakrishnan2012pac} have proposed the LUCB algorithm which, on termination, returns  $m$ arms which are at least $\epsilon$ close to the true top-$m$ arms with probability at least $1-\delta$.
-For a detail survey of this setup we refer the reader to \citet{jamieson2014best}.
+For a detailed survey of this setup, we refer the reader to \citet{jamieson2014best}.
 

### 2018-01-08 Chapter4/prevResAPT.tex
Latest on 8/1/2017

@@
-In the latest work of \citet{locatelli2016optimal} Anytime Parameter-Free Thresholding (APT) algorithm comes up with an improved anytime guarantee than CSAR for the thresholding bandit problem.
+In the latest work of \citet{locatelli2016optimal}, Anytime Parameter-Free Thresholding (APT) algorithm comes up with an improved anytime guarantee than CSAR for the thresholding bandit problem.
 APT is stated in algorithm \ref{alg:apt}.
@@
 The APT algorithm is very simple to implement and the logic behind the arm pull directly follows from the challenges in the TBP setting discussed before.
-Note, that the most difficult arms to discriminate are the arms whose expected means are lying close to the threshold $\tau$, hence APT pulls those arms whose sample means $\hat{r}_i$ are lying close to the threshold and the arms which has not been pulled often.
+Note, that the most difficult arms to discriminate are the arms whose expected means are lying close to the threshold $\tau$, hence APT pulls those arms whose sample means $\hat{r}_i$ are lying close to the threshold and the arms which have not been pulled often.
 The second condition is satisfied by the $\sqrt{n_i}$ term which acts very similar to the confidence interval term discussed for UCBE (see algorithm \ref{alg:ucbe}).

### 2018-01-08 Appendix/AppendixConc.tex
Latest on 24/11/2017
Latest on 8/1/2017

@@
-\subsection{Sample space}
-
-\subsection{Events}
-
-\subsection{Sigma-algebra}
-
-\subsubsection{Borel-sigma algebra}
-
-\subsection{Measure}
-
-\subsubsection{The probability measure}
-
-\subsection{The triplet}
-
-\subsection{Filtration}
-
-\section{Martingale}
-
-\subsection{Super-martingale}
-
-\subsection{Sub-martingale}
-
-\section{Convergence theorems}
-
-\subsection{Monotone convergence theorem}
-
-\subsection{Dominated convergence theorem}
-
-\subsection{Fatou's Lemma}
+%\subsection{Sample space}
+%
+%
+%
+%\subsection{Events}
+%
+%
+%
+%\subsection{Sigma-algebra}
+%
+%
+%
+%\subsubsection{Borel-sigma algebra}
+%
+%
+%
+%\subsection{Measure}
+%
+%
+%
+%\subsubsection{The probability measure}
+%
+%
+%
+%\subsection{The triplet}
+%
+%
+%
+%\subsection{Filtration}
+%
+%
+%
+%\section{Martingale}
+%
+%
+%
+%\subsection{Super-martingale}
+%
+%
+%
+%\subsection{Sub-martingale}
+%
+%
+%\section{Convergence theorems}
+%
+%
+%\subsection{Monotone convergence theorem}
+%
+%
+%
+%\subsection{Dominated convergence theorem}
+%
+%
+%
+%\subsection{Fatou's Lemma}
 
@@
 In this section we state some of the concentration inequalities used in the proofs in several chapters of the thesis.
-Concentration inequality deals with the control of the tail of the average of independent random variables from their expected mean.
+Concentration inequality deals with the control of the deviation of the average of independent random variables from their expected mean.
 
@@
 
+The Markov;s inequality gives us a very loose bound which is further tightened by the Chernoff-Hoeffding Bound and Bernstein Inequality.
+
 \subsection{Chernoff-Hoeffding Bound}
+\label{app:chernoff}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%
-&=\Pb\lbrace S_n - n\E[S_n] \leq - \epsilon \rbrace \leq \exp\left( -\dfrac{2\epsilon^2}{n \sum_{i=1}^n(a_i -b_i)}\right)
+&\Pb\lbrace S_n - n\E[S_n] \leq - \epsilon \rbrace \leq \exp\left( -\dfrac{2\epsilon^2}{n \sum_{i=1}^n(a_i -b_i)}\right)
 \end{align*}
 
-Considering all the random variables bounded in $[0,1]$, the above two inequalities can be reduced to,
+Considering all the random variables bounded in $[0,1]$, then both the right and left tail inequality can be reduced to,
 
 \begin{align*}
-&\Pb\lbrace \left|\dfrac{S_n}{n} - \E[S_n]\right| \geq \epsilon \rbrace \leq 2\exp\left( - 2\epsilon^2 n \right) \\
+&\Pb\left\lbrace \left|\dfrac{S_n}{n} - \E[S_n]\right| \geq \epsilon \right\rbrace \leq 2\exp\left( - 2\epsilon^2 n \right) \\
 %%%%%%%%%%%%%%%%%%%%%%
-&=\Pb\lbrace \left|\hat{r} - r\right| \geq \epsilon \rbrace \leq 2\exp\left( - 2\epsilon^2 n \right)
+%&= 2\exp\left( - 2\epsilon^2 n \right)
+\end{align*}
+
+Hence, we obtain that, 
+\begin{align*}
+\Pb\lbrace \left|\hat{r} - r\right| \geq \epsilon \rbrace \leq 2\exp\left( - 2\epsilon^2 n \right)
 \end{align*}
@@
 \subsection{Empirical Bernstein inequality}
+\label{app:bernstein}
 
@@
 
-Considering all the random variables bounded in $[0,1]$, the above two inequalities can be reduced to,
+Considering all the random variables bounded in $[0,1]$, then both the right and left tail inequality can be reduced to,
 
 \begin{align*}
-&\Pb\lbrace \left|\dfrac{S_n}{n} - \E[S_n]\right| \geq \epsilon \rbrace \leq 2\exp\left( -\dfrac{2\epsilon^2 n}{\left(2\sigma^2 + \frac{2\epsilon}{3}\right)}\right) \\
+&\Pb\left\lbrace \left|\dfrac{S_n}{n} - \E[S_n]\right| \geq \epsilon \right\rbrace \leq 2\exp\left( -\dfrac{2\epsilon^2 n}{\left(2\sigma^2 + \frac{2\epsilon}{3}\right)}\right) \\
 %%%%%%%%%%%%%%%%%%%%%%
-&=\Pb\lbrace \left|\hat{r} - r\right| \geq \epsilon \rbrace \leq 2\exp\left( -\dfrac{2\epsilon^2 n}{\left(2\sigma^2 + \frac{2\epsilon}{3}\right)}\right)
+%&=\Pb\lbrace \left|\hat{r} - r\right| \geq \epsilon \rbrace \leq 2\exp\left( -\dfrac{2\epsilon^2 n}{\left(2\sigma^2 + \frac{2\epsilon}{3}\right)}\right)
 \end{align*}
+
+Hence, we obtain that,
+
+\begin{align*}
+\Pb\lbrace \left|\hat{r} - r\right| \geq \epsilon \rbrace \leq 2\exp\left( -\dfrac{2\epsilon^2 n}{\left(2\sigma^2 + \frac{2\epsilon}{3}\right)}\right)
+\end{align*}

### 2018-01-08 Chapter7/ThesisConc.tex
Latest on 8/1/2017

@@
 %Finally, we studied the piecewise stochastic bandits and proposed several solutions for adaptive algorithms that detect changepoints and try to adapt accordingly.
-
-    There are several directions in which the work done in this thesis can be extended.
-Starting with the SMAB setting, there are many fundamental questions that need to be answered.
-Though EUCBV reached an order optimal regret bound of $80\sqrt{KT}$, still the constant associated with the bound is quite large and can be reduced by finer analysis.
-One avenue for future work is to remove the constraint of $T\geq K^{2.4}$ required for EUCBV to reach the order optimal regret bound.
-Also, EUCBV does not have any asymptotic guarantee and we do not know whether it can reach the \citet{lai1985asymptotically} asymptotic lower bound discussed in chapter \ref{chap:SMAB}.
-Recently another algorithm called KL-UCB++ \citep{menard2017minimax} has been proved to be both minimax optimal and asymptotically optimal.
-Further, EUCBV requires the knowledge of horizon as input and it will be interesting to find an anytime version of EUCBV.
-Similar anytime version of MOSS \citep{degenne2016anytime} and OCUCB \citep{lattimore2016regret} has also been proposed in literature.
-
-    The thresholding bandit problem is also being intensely studied in the bandit community and there are several directions where this work can be extended.
-One way is to modify the APT algorithm itself and come up with a variance adaptive version of APT.
-This has bee recently studied in \citet{kano2017good}.
-Also, currently there are no lower bounds for the TBP setting considering only variance estimation and it will be interesting to derive a lower bound for this setting.
-Again, whereas APT is an anytime algorithm AugUCB is not anytime and it needs several modifications to obtain an anytime version of AugUCB.
-Further, we can also derive a gap-independent and gap-dependent bounds for AugUCB as like APT.
-In \citet{lattimore2015optimally} the authors showed that APT like UCB1 enjoys a gap-dependent cumulative regret bound of $O\left( \dfrac{K\log T}{\Delta^2}\right)$ and gap-independent regret bound of $O\left( \sqrt{KT\log T}\right)$.
-
-    %For the piecewise stochastic bandits we were able to show empirically that the adaptive algorithms we considered are indeed more powerful than passive algorithms and further work needs to be done to derive the regret bounds for these algorithms.
-    %Specifically for CPD\ref{alg:CPD3} we find the confidence interval obtained by Laplace method as like UCB-$\delta$ algorithm\citep{abbasi2011improved} very promising and more work needs to be done in this aspect.
-
-    Finally, to summarize everything, the bandit community is actively researching several of these open problems discussed here and we hope to answer some of these problems in near future.
-Further, several interesting variations of the problems discussed here are also being studied such as the Contextual Thresholding Bandit problem, Combinatorial Bandit problems \citep{cesa2012combinatorial} and more powerful algorithms for changepoint detection.

### 2018-01-08 Chapter7/ThesisDir.tex
Latest on 8/1/2017

There are several directions in which the work done in this thesis can be extended. Starting with the SMAB setting, there are many fundamental questions that need to be answered. Though EUCBV reached an order optimal regret bound of $80\sqrt{KT}$, still the constant associated with the bound is quite large and can be reduced by finer analysis. One avenue for future work is to remove the constraint of $T\geq K^{2.4}$ required for EUCBV to reach the order optimal regret bound. Also, EUCBV does not have any asymptotic guarantee and we do not know whether it can reach the \citet{lai1985asymptotically} asymptotic lower bound discussed in chapter \ref{chap:SMAB}. Recently another algorithm called KL-UCB++ \citep{menard2017minimax} has been proved to be both minimax optimal and asymptotically optimal. Further, EUCBV requires the knowledge of horizon as input and it will be interesting to find an anytime version of EUCBV. Similar anytime version of MOSS \citep{degenne2016anytime} and OCUCB \citep{lattimore2016regret} has also been proposed in literature.

    The thresholding bandit problem is also being intensely studied in the bandit community and there are several directions where this work can be extended. One way is to modify the APT algorithm itself and come up with a variance adaptive version of APT. This has bee recently studied in \citet{kano2017good}. Also, currently there are no lower bounds for the TBP setting considering only variance estimation and it will be interesting to derive a lower bound for this setting. Again, whereas APT is an anytime algorithm AugUCB is not anytime and it needs several modifications to obtain an anytime version of AugUCB. Further, we can also derive a gap-independent and gap-dependent bounds for AugUCB as like APT. In \citet{lattimore2015optimally} the authors showed that APT like UCB1 enjoys a gap-dependent cumulative regret bound of $O\left( \dfrac{K\log T}{\Delta^2}\right)$ and gap-independent regret bound of $O\left( \sqrt{KT\log T}\right)$.

    %For the piecewise stochastic bandits we were able to show empirically that the adaptive algorithms we considered are indeed more powerful than passive algorithms and further work needs to be done to derive the regret bounds for these algorithms. 
    %Specifically for CPD\ref{alg:CPD3} we find the confidence interval obtained by Laplace method as like UCB-$\delta$ algorithm\citep{abbasi2011improved} very promising and more work needs to be done in this aspect.

    Finally, to summarize everything, the bandit community is actively researching several of these open problems discussed here and we hope to answer some of these problems in near future. Further, several interesting variations of the problems discussed here are also being studied such as the Contextual Thresholding Bandit problem, Combinatorial Bandit problems \citep{cesa2012combinatorial} and more powerful algorithms for changepoint detection.

### 2018-01-08 abstract.tex
Latest on 8/1/2017

The thesis studies the following topics in the area of Reinforcement Learning: Multi-armed Bandits, Multi-armed bandits in stationary distribution with the goal of cumulative regret minimization and Thresholding bandits in pure exploration setting. The common underlying theme is the study of bandit theory and its application in various types of environments. In the first part of the thesis, we study the classic multi-armed bandit problem in stationary distribution, one of the first setting studied by the bandit community and which successively gave rise to several new directions in bandit theory. We propose a novel algorithm in this setting and compare both theoretically and empirically its performance against the available algorithms in this setting. Our proposed algorithm called Efficient-UCB-Variance (EUCBV) is the first arm-elimination algorithm which uses variance estimation yo eliminate arms as well as achieve an order optimal regret bound. Empirically, we show that EUCBV outperforms most of the state-of-the-art algorithms in the considered environments. In the next part, we study a very specific type of stochastic multi-armed bandit setup called the thresholding bandit problem and discuss extensively on its usage, available state-of-the-art algorithms on this setting and our solution to this problem. We propose the Augmented-UCB algorithm which again uses variance and mean estimation along with arm elimination technique to conduct exploration. We give theoretical guarantees on the expected loss of our algorithm and also analyze its performance against state-of-the-art algorithms in numerical simulations in multiple synthetic environments.

### 2018-01-08 abstract.tex
Latest on 8/1/2017

@@
 We propose a novel algorithm in this setting and compare both theoretically and empirically its performance against the available algorithms in this setting.
-Our proposed algorithm called Efficient-UCB-Variance (EUCBV) is the first arm-elimination algorithm which uses variance estimation yo eliminate arms as well as achieve an order optimal regret bound.
+Our proposed algorithm called Efficient-UCB-Variance (EUCBV) is the first arm-elimination algorithm which uses variance estimation to eliminate arms as well as achieve an order optimal regret bound.
 Empirically, we show that EUCBV outperforms most of the state-of-the-art algorithms in the considered environments.

### 2018-01-08 Chapter3/proofTheorem.tex
Latest on 8/1/2017

@@
 We first present a few technical lemmas that are required to prove the result in Theorem \ref{Result:Theorem:1}.
+
+In Lemma \ref{proofTheorem:Lemma:1} we use the constraint on the horizon, that is $T\geq K^{2.4}$ to derive an inequality which we re-use in Lemma \ref{proofTheorem:Lemma:2} to bound the length of the confidence interval $c_i$ of the $i$-th sub-optimal arm till the $m_i$-th round.
 
@@
 
-\begin{proof}
+\begin{customproof}{}
 The proof is based on contradiction. Suppose
@@
 \hfill $\blacksquare$	
-\end{proof}
+\end{customproof}
+
+In Lemma \ref{proofTheorem:Lemma:2} we bound the length of the confidence interval $c_i$ for the $i$-th arm till the $m_i$-th round.
 
@@
 
-\begin{proof}
+\begin{customproof}{}
 
@@
 \begin{align*}
-	c_{i} &\leq \sqrt{\dfrac{\rho (\hat{v}_i + 2)\epsilon_{m_{i}}\log (\psi T\epsilon_{m_{i}})}{2\log(\psi T\epsilon_{m_{i}}^{2})}} \overset{(a)}{\leq} \sqrt{\dfrac{2\rho\epsilon_{m_{i}}\log (\frac{\psi T\epsilon_{m_{i}}^{2}}{\epsilon_{m_{i}}})}{\log(\psi T\epsilon_{m_{i}}^{2})}} \\
+	c_{i} &\leq \sqrt{\dfrac{\rho (\hat{v}_i + 2)\epsilon_{m_{i}}\log (\psi T\epsilon_{m_{i}})}{2\log(\psi T\epsilon_{m_{i}}^{2})}} \\
+	%%%%%%%%%%%%%%%%%%%%%%%%%%
+	&\overset{(a)}{\leq} \sqrt{\dfrac{2\rho\epsilon_{m_{i}}\log (\frac{\psi T\epsilon_{m_{i}}^{2}}{\epsilon_{m_{i}}})}{\log(\psi T\epsilon_{m_{i}}^{2})}} \\
 	%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \hfill $\blacksquare$	
-\end{proof}
+\end{customproof}
+
+In Lemma \ref{proofTheorem:Lemma:3} we bound the probability of the deviation of the sample mean $\hat{r}_i$ from its expectation $r_i$ till the $m_i$-th round.
 
@@
 \begin{align}
-&\mathbb{P}\left( \hat{r}_{i} > r_{i}+ \bar{c}_i\right)\nonumber 
-\le \exp\left(- \dfrac{(\bar{c}_i)^2 z_{i}}{2\sigma_i^2 + \frac{2}{3}\bar{c}_i} \right)\nonumber 
+\mathbb{P}\left( \hat{r}_{i} > r_{i}+ \bar{c}_i\right)\nonumber 
+&\le \exp\left(- \dfrac{(\bar{c}_i)^2 z_{i}}{2\sigma_i^2 + \frac{2}{3}\bar{c}_i} \right)\nonumber 
 %%%%%%%%%%%%%%%
@@
 \begin{align}
-&\mathbb{P}\bigg\lbrace \hat{v}_{i}\geq \sigma_{i}^{2}+\sqrt{\epsilon_{m_{i}}}\bigg\rbrace\nonumber\\
+\mathbb{P}\bigg\lbrace \hat{v}_{i}\geq \sigma_{i}^{2}+\sqrt{\epsilon_{m_{i}}}\bigg\rbrace
 %%%%%%%%%%%%%%%%%%
@@
 \hfill $\blacksquare$	
-\end{proof}
+\end{customproof}
 
@@
 
+In Lemma \ref{proofTheorem:Lemma:4} we bound the probability of the confidence interval of the optimal arm $c^*$ being greater than the confidence interval $c_i$ of the $i$-th sub-optimal arm till the $m_i$-th round.
+
 \begin{lemma}
@@
 
-\begin{proof}
+\begin{customproof}{}
 From the definition of $c_i$ we know that $c_i\propto \frac{1}{z_i}$ as $\psi$ and $T$ are constants. Therefore in the $m_i$-th round,
@@
 \begin{align*}
-&\Pb\lbrace c^{*} > c_i \rbrace \\
+\Pb\lbrace c^{*} > c_i \rbrace 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \hfill $\blacksquare$	
-\end{proof}
+\end{customproof}
+
+In Lemma \ref{proofTheorem:Lemma:5} we bound the probability of the number of pulls of the $i$-th sub-optimal arm, $z_i$, of not being greater then the allocated $n_{m_i}$ number of pulls till the $m_i$-th round.
 
@@
 
-\begin{proof}
+\begin{customproof}{}
 Following a similar argument as in Lemma \ref{proofTheorem:Lemma:4}, we can show that in the $m_i$-th round,
@@
 
+In Lemma \ref{proofTheorem:Lemma:6} we prove the inequality required to introduce the variance term in the number of pulls of a sub-optimal arm $i$ till the $m_i$-th round.
+
 \begin{lemma}
@@
 
-\begin{proof}
+\begin{customproof}{}
 We again prove this by contradiction. Suppose, 
@@
 \label{sec:proofTheorem:Theorem1}
-\begin{customproof}{1}
+\begin{customproof}{}
 For each sub-optimal arm ${i}\in\mathcal{A}$, let $m_{i}=\min{\left\lbrace m|\sqrt{4\epsilon_{m_i}} < \frac{\Delta_{i}}{4}\right\rbrace}$.
@@
   \begin{align*}
-\hat{r}_{i} + c_{i}&\leq r_{i} + 2c_{i} 
-= r_{i} + 4c_{i} - 2c_{i} \\
- &< r_{i} + \Delta_{i} - 2c_{i}
- \leq r^{*} -2c^{*} 
- \leq \hat{r}^{*} - c^{*}
+\hat{r}_{i} + c_{i}&\leq r_{i} + 2c_{i} \\
+ &= r_{i} + 4c_{i} - 2c_{i} \\
+ &< r_{i} + \Delta_{i} - 2c_{i}\\
+ &\leq r^{*} -2c^{*} \\
+ &\leq \hat{r}^{*} - c^{*}\\
   \end{align*}
@@
 
-Also, for eq. $(\ref{eq:arm:elim:c1})$ we can show that for any $\epsilon_{m_i}\in[\sqrt{\frac{e}{T}},1]$
+Also, for eq. $(\ref{eq:arm:elim:c1})$ we can show that for any $\epsilon_{m_i}\in\left[\sqrt{\frac{e}{T}},1\right]$
 \begin{eqnarray}
-\bigg(\dfrac{4}{(\psi T\epsilon_{m_{i}})^{\frac{3\rho}{2}}} \bigg) &\overset{(a)}{\leq} \bigg(\dfrac{4}{(\frac{T^2}{K^2}\epsilon_{m_{i}})^{\frac{3}{4}}} \bigg)\leq \bigg(\dfrac{4 K^{\frac{3}{2}}}{(T^\frac{3}{2} \epsilon_{m_i}^{\frac{1}{4}}\sqrt{\epsilon_{m_{i}}})}\bigg) \nonumber \\
+\bigg(\dfrac{4}{(\psi T\epsilon_{m_{i}})^{\frac{3\rho}{2}}} \bigg) &\overset{(a)}{\leq} \bigg(\dfrac{4}{(\frac{T^2}{K^2}\epsilon_{m_{i}})^{\frac{3}{4}}} \bigg)
+%%%%%%%%%%%%%%%%%%%%%%%
+\leq \bigg(\dfrac{4 K^{\frac{3}{2}}}{(T^\frac{3}{2} \epsilon_{m_i}^{\frac{1}{4}}\sqrt{\epsilon_{m_{i}}})}\bigg) \nonumber \\
 %%%%%%%%%%%%%%%%%%%%%%%
 &\overset{(b)}{\leq} \bigg(\dfrac{4 K^{\frac{3}{2}}}{(T^{\frac{3}{2}-\frac{1}{8}}\sqrt{\epsilon_{m_{i}}})}  \bigg)
+%%%%%%%%%%%%%%%%%%%%%%%
 \leq \dfrac{4 K^4}{T^{\frac{5}{4}}\sqrt{\epsilon_{m_i}}}. \label{eq:arm:elim:c3}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\overset{(a)}{\leq}\sum_{i\in \A^{'}}\bigg(\dfrac{368 K^4 T\Delta_{i}}{T^{\frac{5}{4}}\left(\frac{\Delta_{i}^{2}}{4.16}\right)^{\frac{1}{2}}}\bigg)
+&\overset{(a)}{\leq}\sum_{i\in \A^{'}}\bigg(\dfrac{368 K^4 T\Delta_{i}}{T^{\frac{5}{4}}\left(\frac{\Delta_{i}^{2}}{4.16}\right)^{\frac{1}{2}}}\bigg)\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\overset{(b)}{\leq} \sum_{i\in \A^{'}}\bigg(\dfrac{C_1 K^4}{(T)^{\frac{1}{4}}}\bigg).\\  
+&\overset{(b)}{\leq} \sum_{i\in \A^{'}}\bigg(\dfrac{C_1 K^4}{(T)^{\frac{1}{4}}}\bigg).\\  
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{align*}
-&\Delta_{i}\bigg\lceil\dfrac{\log{(\psi T\epsilon_{m_{i}}^{2})}}{2\epsilon_{m_{i}}}\bigg\rceil
-\overset{(a)}{\leq}    \Delta_{i}\bigg\lceil\dfrac{\log{(\psi T(\dfrac{\Delta_{i}}{16 \times 256})^{4})}}{2(\dfrac{\Delta_{i}}{4\sqrt{4}})^{2}}\bigg\rceil \\
+\Delta_{i}\bigg\lceil\dfrac{\log{(\psi T\epsilon_{m_{i}}^{2})}}{2\epsilon_{m_{i}}}\bigg\rceil
+&\overset{(a)}{\leq}    \Delta_{i}\bigg\lceil\dfrac{\log{(\psi T(\dfrac{\Delta_{i}}{16 \times 256})^{4})}}{2(\dfrac{\Delta_{i}}{4\sqrt{4}})^{2}}\bigg\rceil \\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\leq   \Delta_{i}\bigg(1+\dfrac{32\log{(\psi T(\dfrac{\Delta_{i}^{4}}{16384})}}{\Delta_{i}^{2}}\bigg)
-\leq \Delta_{i}\bigg(1+\dfrac{32\log{(\psi T\Delta_{i}^{4})}}{\Delta_{i}^{2}}\bigg) .
+&\leq   \Delta_{i}\bigg(1+\dfrac{32\log{(\psi T(\dfrac{\Delta_{i}^{4}}{16384})}}{\Delta_{i}^{2}}\bigg)\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\leq \Delta_{i}\bigg(1+\dfrac{32\log{(\psi T\Delta_{i}^{4})}}{\Delta_{i}^{2}}\bigg) .
 \end{align*}
@@
 \begin{align*}
-&\sum_{i\in \A^{'}}\Delta_{i}\bigg(1+\dfrac{32\log{(\psi T\Delta_{i}^{4}})}{\Delta_{i}^{2}}\bigg) = \sum_{i\in \A^{'}}\bigg(\Delta_{i} +\dfrac{32\log{(\psi T\Delta_{i}^{4}})}{\Delta_{i}}\bigg) \\
+\sum_{i\in \A^{'}}\Delta_{i}\bigg(1+\dfrac{32\log{(\psi T\Delta_{i}^{4}})}{\Delta_{i}^{2}}\bigg) &= \sum_{i\in \A^{'}}\bigg(\Delta_{i} +\dfrac{32\log{(\psi T\Delta_{i}^{4}})}{\Delta_{i}}\bigg) \\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{align*}
-&\sum_{m_{*}=0}^{max_{j\in \A^{'}}m_{j}}\sum_{i\in \A^{''}:m_{i}>m_{*}}\bigg(\dfrac{368 K^4}{(T^{\frac{5}{4}}\sqrt{\epsilon_{m_{*}}})} \bigg).T\max_{j\in \A^{''}:m_{j}\geq m_{*}}{\Delta}_{j}\\
+&\sum_{m_{*}=0}^{max_{j\in \A^{'}}m_{j}} \sum_{i\in \A^{''}:m_{i}>m_{*}}\bigg(\dfrac{368 K^4}{(T^{\frac{5}{4}}\sqrt{\epsilon_{m_{*}}})} \bigg).T\max_{j\in \A^{''}:m_{j}\geq m_{*}}{\Delta}_{j}\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-01-11 Chapter1/connBandits.tex
Latest on 11/1/2017

@@
 As defined in the previous section, an episode consists of a series of sequential interaction whereas agent transitions from one state to another based on some intrinsic dynamics of the environment while collecting the rewards and choosing actions based on some action-selecting strategy.
-Now, for a single-step interaction, i.e., when the episode terminates after a single transition, the problem is captured by the multi-armed bandit (MAB) model.
-In fact, the MAB model can be considered as a single looping state when the agent after taking an action and observing the reward transitions back to the same state.
+The MAB model can be considered as a special case where there is a single looping state and the agent after taking an action and observing the reward transitions back to the same state.
 That single looping state consists of several finite number of actions which are called as arms.
@@
 This game is repeated $T$ times and the goal of the learner is to maximize its profit.
+
+% Now, for a single-step interaction, i.e., when the episode terminates after a single transition, the problem is captured by the multi-armed bandit (MAB) model.

### 2018-01-11 abstract.tex
Latest on 11/1/2017

@@
-The thesis studies the following topics in the area of Reinforcement Learning: Multi-armed Bandits, Multi-armed bandits in stationary distribution with the goal of cumulative regret minimization and Thresholding bandits in pure exploration setting.
+This thesis studies the following topics in the area of Reinforcement Learning: Multi-armed bandits in stationary distribution with the goal of cumulative regret minimization and Thresholding bandits in pure exploration setting.
 The common underlying theme is the study of bandit theory and its application in various types of environments.
-In the first part of the thesis, we study the classic multi-armed bandit problem in stationary distribution, one of the first setting studied by the bandit community and which successively gave rise to several new directions in bandit theory.
-We propose a novel algorithm in this setting and compare both theoretically and empirically its performance against the available algorithms in this setting.
-Our proposed algorithm called Efficient-UCB-Variance (EUCBV) is the first arm-elimination algorithm which uses variance estimation to eliminate arms as well as achieve an order optimal regret bound.
+In the first part of the thesis, we study the classic multi-armed bandit problem with a stationary distribution, one of the first settings studied by the bandit community and which successively gave rise to several new directions in bandit theory.
+We propose a novel algorithm in this setting and compare both theoretically and empirically its performance against the available algorithms.
+Our proposed algorithm termed as Efficient-UCB-Variance (EUCBV) is the first arm-elimination algorithm which uses variance estimation to eliminate arms as well as achieve an order optimal regret bound.
 Empirically, we show that EUCBV outperforms most of the state-of-the-art algorithms in the considered environments.
-In the next part, we study a very specific type of stochastic multi-armed bandit setup called the thresholding bandit problem and discuss extensively on its usage, available state-of-the-art algorithms on this setting and our solution to this problem.
-We propose the Augmented-UCB algorithm which again uses variance and mean estimation along with arm elimination technique to conduct exploration.
+In the next part, we study a specific type of stochastic multi-armed bandit setup called the thresholding bandit problem and discuss its usage, available state-of-the-art algorithms on this setting and our solution to this problem.
+We propose the Augmented-UCB (AugUCB) algorithm which again uses variance and mean estimation along with arm elimination technique to conduct exploration.
 We give theoretical guarantees on the expected loss of our algorithm and also analyze its performance against state-of-the-art algorithms in numerical simulations in multiple synthetic environments.

### 2018-01-11 Chapter1/connBandits.tex
Latest on 12/1/2017

@@
 
-    The name bandit originated from the concept of casino slot machine where there are levers which are called as arms and the learner can pull one lever and observes the reward associated with that arm which is sampled from a distribution associated with the specific arm.
+    The name bandit originated from the concept of casino slot machine where there are levers which are called as arms and the learner can pull one lever and observe the reward associated with that arm which is sampled from a distribution associated with the specific arm.
 This game is repeated $T$ times and the goal of the learner is to maximize its profit.

### 2018-01-11 Chapter4/notation.tex
Latest on 12/1/2017

@@
 For arm $i\in\mathcal{A}$, we use $r_{i}$ to denote the true mean of the distribution from which the rewards are sampled, while $\hat{r}_{i}(t)$ denotes the estimated mean at time $t$.
-Formally, using $n_i(t)$ to denote the number of times arm $i$ has been pulled until time $t$, we have $\hat{r}_{i}(t)=\frac{1}{n_{i}(t)}\sum_{z=1}^{n_i(t)} X_{i,z}$, where $X_{i,z}$ is the reward sample received when arm $i$ is pulled for the $z$-th time.
+Formally, using $z_i(t)$ to denote the number of times arm $i$ has been pulled until time $t$, we have $\hat{r}_{i}(t)=\frac{1}{z_{i}(t)}\sum_{b=1}^{z_i(t)} X_{i,b}$, where $X_{i,b}$ is the reward sample received when arm $i$ is pulled for the $b$-th time.
 %
-Similarly, we use $\sigma_{i}^{2}$ to denote the true variance of the reward distribution corresponding to arm $i$, while $\hat{v}_{i}(t)$ is the estimated variance, i.e., $\hat{v}_{i}(t)=\frac{1}{n_i(t)}\sum_{z=1}^{n_{i}(t)}(X_{i,z}-\hat{r}_{i})^{2}$.
-Whenever there is no ambiguity about the underlaying  time index $t$, for simplicity we neglect $t$ from the notations and simply use  $\hat{r}_i, \hat{v}_i,$ and $n_i, $ to denote the respective quantities.
+Similarly, we use $\sigma_{i}^{2}$ to denote the true variance of the reward distribution corresponding to arm $i$, while $\hat{v}_{i}(t)$ is the estimated variance, i.e., $\hat{v}_{i}(t)=\frac{1}{z_i(t)}\sum_{b=1}^{z_{i}(t)}(X_{i,b}-\hat{r}_{i})^{2}$.
+Whenever there is no ambiguity about the underlaying  time index $t$, for simplicity we neglect $t$ from the notations and simply use  $\hat{r}_i, \hat{v}_i,$ and $z_i, $ to denote the respective quantities.
 Let  $\Delta_{i}=|\tau-r_{i}|$ denote the distance of the true mean from the threshold $\tau$.

### 2018-01-11 Chapter4/prevRes.tex
Latest on 12/1/2017

@@
 \For{$t=K+1,..., T$}
-\State Pull the arm such that $\argmax_{i\in \A}\bigg\lbrace\hat{r}_{i} + \sqrt{\dfrac{a}{n_i}}\bigg\rbrace$, where $a = \dfrac{25(T-K)}{36 H_1}$ and $H_1 = \sum_{i=1}^{K}\dfrac{1}{\Delta_i^2}$.
+\State Pull the arm such that $\argmax_{i\in \A}\bigg\lbrace\hat{r}_{i} + \sqrt{\dfrac{a}{z_i}}\bigg\rbrace$, where $a = \dfrac{25(T-K)}{36 H_1}$ and $H_1 = \sum_{i=1}^{K}\dfrac{1}{\Delta_i^2}$.
 \State $t:=t+1 $
@@
 \hline
-UCB1       & $\sqrt{\dfrac{a}{n_i}}$ & \begin{align*}a = 2\log (t)\end{align*} & $a$ is logarithmic in $t$ to minimize cumulative regret.
+UCB1       & $\sqrt{\dfrac{a}{z_i}}$ & \begin{align*}a = 2\log (t)\end{align*} & $a$ is logarithmic in $t$ to minimize cumulative regret.
 This achieves a balance between exploration and exploitation.
@@
 \hline
-UCBE       & $\sqrt{\dfrac{a}{n_i}}$ & \begin{align*}a = \dfrac{25(T-K)}{36 H_1},\\ \text{ where }H_1 = \sum_{i=1}^{K}\dfrac{1}{\Delta_i^2}\end{align*} & $a$ is linear in $T$ to minimize simple regret.
+UCBE       & $\sqrt{\dfrac{a}{z_i}}$ & \begin{align*}a = \dfrac{25(T-K)}{36 H_1},\\ \text{ where }H_1 = \sum_{i=1}^{K}\dfrac{1}{\Delta_i^2}\end{align*} & $a$ is linear in $T$ to minimize simple regret.
 Here, the main concern is to minimize the probability of error at the end of budget $T$ and conduct as much exploration as possible.

### 2018-01-11 Chapter4/prevResAPT.tex
Latest on 12/1/2017

@@
 \State \For{$t=K+1,..,T$}
-\State Pull arm $j\in\argmin_{i\in A}\big\lbrace \left(|\hat{r}_{i} - \tau | + \epsilon\right)\sqrt{n_i}\big\rbrace$ and observe the reward for arm $j$.
+\State Pull arm $j\in\argmin_{i\in A}\big\lbrace \left(|\hat{r}_{i} - \tau | + \epsilon\right)\sqrt{z_i}\big\rbrace$ and observe the reward for arm $j$.
 \EndFor
@@
 Note, that the most difficult arms to discriminate are the arms whose expected means are lying close to the threshold $\tau$, hence APT pulls those arms whose sample means $\hat{r}_i$ are lying close to the threshold and the arms which have not been pulled often.
-The second condition is satisfied by the $\sqrt{n_i}$ term which acts very similar to the confidence interval term discussed for UCBE (see algorithm \ref{alg:ucbe}).
+The second condition is satisfied by the $\sqrt{z_i}$ term which acts very similar to the confidence interval term discussed for UCBE (see algorithm \ref{alg:ucbe}).
 The tolerance level $\epsilon\geq 0$ gives the algorithm a degree of flexibility in pulling the arms close to the threshold.

### 2018-01-13 Chapter1/feedback.tex
Latest on 13/1/2017

@@
 Let, the environment be such that each action has a probability distribution $D_i$ attached to it which is fixed throughout the time horizon $T$.
-The learning proceeds as follows, at every timestep the learner selects $m\in\A$ actions and observes some form of feedback vector $R^{obs}_{t}$ (which will be characterized later).
+The learning proceeds as follows, at every timestep the learner selects $m\in\A$ actions and observes some form of feedback vector $G^{obs}_{t}$ (which will be characterized later).
 Before the learner selects the set of arms the environment draws the feedback vector $F^{env}_t\in[0,1]^{K}$ of $K$ i.i.d random rewards for all actions $i\in\A$ from $D_i,\forall i\in\A$ which it decides to reveal in particular format depending on the form of feedback chosen for the game, that is full information, partial information or bandit feedback.
@@
 \State The learner chooses $m$ actions such that $m < K$ following some policy $\pi$, where $\A$ is the set of arms and $|\A|=K$.
-\State The learner observes the reward vector $R^{obs}_{t}\subseteq F^{env}_{t}$.
+\State The learner observes the reward vector $G^{obs}_{t}\subseteq F^{env}_{t}$.
 \State \EndFor
@@
 
-\subsection{Full information feedback}
+\subsection{Full Information Feedback}
 In full information feedback, when a learner selects $m$ actions then the environment reveals the rewards of all the actions $i\in \A$.
-Hence, in this form of feedback  the learner observes $R^{obs}_{t} = F^{env}_{t}=[r_{i,t},\forall i\in\A]$.
+Hence, in this form of feedback  the learner observes $G^{obs}_{t} = F^{env}_{t}=[r_{i,t},\forall i\in\A]$.
 This has been studied in many forms previously in \citet{takimoto2003path}, \citet{kalai2005efficient} or in online prediction with full information feedback in \citet{cesa2006prediction}.
 
-\subsection{Partial information feedback}
+\subsection{Partial Information Feedback}
 In partial information feedback, when a learner selects $m$ actions then the environment reveals the rewards of only those $m$ actions for $m\in \A$.
-Hence, in this form of feedback  the learner observes $R^{obs}_{t} = [ r_{m,t},\forall m\in\A ]$.
+Hence, in this form of feedback  the learner observes $G^{obs}_{t} = [ r_{m,t},\forall m\in\A ]$.
 This is also sometimes called the semi-bandit feedback and has been studied in \citet{awerbuch2004adaptive},   \citet{mcmahan2004online} and \citet{gyorgy2007line}.
 
-\subsection{Bandit feedback}
+\subsection{Bandit Feedback}
 In bandit feedback, when a learner selects $m$ actions then the environment reveals a cumulative reward of those $m$ actions for $m\in \A$.
-Hence, in this form of feedback  the learner observes $R^{obs}_{t} = \sum_{q=1}^{m} r_{q,t}$.
+Hence, in this form of feedback  the learner observes $G^{obs}_{t} = \sum_{q=1}^{m} r_{q,t}$.
 Note, that when $m=1$, then the learner observes the reward of only that action that it has chosen out of $K$ actions.

### 2018-01-13 Chapter1/types.tex
Latest on 13/1/2017

@@
 
-\subsection{Types of Bandits based on Environment}
+\subsection{Types of Bandits Based on Environment}
 
@@
 
-\subsection{Types of Bandits based on goal}
+\subsection{Types of Bandits Based on Goal}
 
@@
 
-\subsubsection{Cumulative regret minimization}
+\subsubsection{Cumulative Regret Minimization}
 In cumulative regret minimization the goal of the bandit is to minimize the cumulative regret which is the total loss suffered by the learner throughout the time horizon $T$ for not choosing the optimal arm.
@@
 
-\subsubsection{Simple regret minimization}
+\subsubsection{Simple Regret Minimization}
 In simple regret minimization the goal of the bandit is to minimize the instantaneous regret that is suffered at any  timestep by the learner.

### 2018-01-13 Chapter2/related.tex
Latest on 13/1/2017

@@
-\subsection{Lower bound in SMAB}
+\subsection{Lower Bound in SMAB}
 
@@
 
-\subsection{The Upper Confidence Bound approach}
+\subsection{The Upper Confidence Bound Approach}
 
@@
  \For{$t=K+1,..., T$}
-\State Pull the arm such that $\argmax_{i\in A}\bigg\lbrace\hat{r}_{i} + \sqrt{\dfrac{2\log (t)}{n_i}}\bigg\rbrace$
+\State Pull the arm such that $\argmax_{i\in A}\bigg\lbrace\hat{r}_{i} + \sqrt{\dfrac{2\log (t)}{z_i}}\bigg\rbrace$
 \State $t:=t+1 $
@@
     The intuition behind this algorithm is simple and it follows from the ideas of concentration inequalities in probability measure theory.
-The term $\sqrt{\dfrac{2\log (t)}{n_i}}$ is called the confidence interval of the arm $i$ and it signifies a measure of uncertainty over the arm $i$ based on the history of observed rewards for that arm.
+The term $\sqrt{\dfrac{2\log (t)}{z_i}}$ is called the confidence interval of the arm $i$ and it signifies a measure of uncertainty over the arm $i$ based on the history of observed rewards for that arm.
 Therefore, lesser the confidence interval, higher is our confidence that the estimated mean $\hat{r}_i$ is lying close to the expected mean $r_i$ of the arm $i$.
-Also, note that the confidence interval decreases at the rate of $O\left( \dfrac{1}{\sqrt{n_i}}\right)$ which signifies the rate of convergence of $\hat{r}_i$ to $r_i$ and depends on the number of time the arm has been pulled.
+Also, note that the confidence interval decreases at the rate of $O\left( \dfrac{1}{\sqrt{z_i}}\right)$ which signifies the rate of convergence of $\hat{r}_i$ to $r_i$ and depends on the number of time the arm has been pulled.
 
@@
 Note, that in this algorithm the confidence interval term is $\sqrt{\dfrac{\log{( T\epsilon_{m}^{2})}}{2 n_{m}}}$ which is constant in the $m$-th round as $n_m$ is fixed for that round and all arms are being pulled an equal number of times in each round.
-This is unlike UCB1 algorithm where the confidence interval term depends on $n_i$ which is a random variable.
+This is unlike UCB1 algorithm where the confidence interval term depends on $z_i$ which is a random variable.
 Also, note that in UCB-Improved the knowledge of horizon is required before-hand to calculate the confidence intervals whereas no such input is required for UCB1.
@@
  \For{$t=K+1,..., T$}
-\State Pull the arm such that $\argmax_{i\in \A}\bigg\lbrace\hat{r}_{i} + \sqrt{\dfrac{\max\lbrace 0,\log(\frac{T}{K n_i})\rbrace}{n_i}}\bigg\rbrace$
+\State Pull the arm such that $\argmax_{i\in \A}\bigg\lbrace\hat{r}_{i} + \sqrt{\dfrac{\max\lbrace 0,\log(\frac{T}{K z_i})\rbrace}{z_i}}\bigg\rbrace$
 \State $t:=t+1 $
@@
 
-    In the later work of \citet{audibert2009minimax}, the authors propose the MOSS algorithm (see algorithm \ref{alg:moss}) and showed that the worst case gap-independent regret bound of MOSS is $O\left( \sqrt{KT} \right)$ which improves upon UCB1 by a factor of order $\sqrt{\log T}$.
+    In the later work of \citet{audibert2009minimax}, the authors propose the MOSS algorithm which stands for Minimax Optimal Strategy in the Stochastic case (see algorithm \ref{alg:moss}).
+The confidence interval of MOSS is designed in such a way so as to divide the horizon $T$ proportionally between the number of arms $K$ and the number of pulls $z_i$ that each arm is pulled.
+As the sub-optimal arms are pulled more number of times their confidence interval decreases, indicating that they have been explored sufficiently, forcing MOSS to explore other arms and quickly converging on the optimal arm.
+Theoretically, \citet{audibert2009minimax}  showed that the worst case gap-independent regret bound of MOSS is $O\left( \sqrt{KT} \right)$ which improves upon UCB1 by a factor of order $\sqrt{\log T}$.
 However, the gap-dependent regret of MOSS is $O\left( \frac{K^{2}\log\left(T\Delta^{2}/K\right)}{\Delta}\right)$ and in certain regimes, this can be worse than even UCB1 (see \citet{audibert2009minimax,lattimore2015optimally}).
@@
  \For{$t=K+1,..., T$}
-\State Pull the arm such that $\argmax_{i\in \A}\bigg\lbrace\hat{r}_{i} + \sqrt{\dfrac{\alpha\log(\psi\frac{T}{t})}{n_i}}\bigg\rbrace$
+\State Pull the arm such that $\argmax_{i\in \A}\bigg\lbrace\hat{r}_{i} + \sqrt{\dfrac{\alpha\log(\psi\frac{T}{t})}{z_i}}\bigg\rbrace$
 \State $t:=t+1 $
@@
 
-Recently in \citet{lattimore2015optimally}, the authors showed that the algorithm Optimally Confident UCB (OCUCB) (see algorithm \ref{alg:ocucb}) achieves order-optimal gap-dependent regret bound of $O\left(\sum_{i=2}^{K}\frac{\log\left(T/H_i\right)}{\Delta_i}\right)$ where $H_i=\sum_{j=1}^{K}\min\left\lbrace \frac{1}{\Delta_i^2},\frac{1}{\Delta_j^2}\right\rbrace$, and a gap-independent regret bound of $O\left( \sqrt{KT}\right)$.
+Recently in \citet{lattimore2015optimally}, the authors proposed the Optimally Confident UCB (OCUCB) (see algorithm \ref{alg:ocucb}) which incorporates the increasing timestep $t$ in the confidence interval along with the fixed horizon $T$ and exploration parameters $\psi$ and $\alpha$.
+The authors showed that the algorithm OCUCB achieves order-optimal gap-dependent regret bound of $O\left(\sum_{i=2}^{K}\frac{\log\left(T/H_i\right)}{\Delta_i}\right)$ where $H_i=\sum_{j=1}^{K}\min\left\lbrace \frac{1}{\Delta_i^2},\frac{1}{\Delta_j^2}\right\rbrace$, and a gap-independent regret bound of $O\left( \sqrt{KT}\right)$.
 This is the best known gap-dependent and gap-independent regret bounds in the stochastic MAB framework.
@@
 
-\subsubsection{UCB-Variance algorithm}
+\subsubsection{UCB-Variance Algorithm}
 
@@
 This TS is stated in algorithm \ref{alg:ts}.
-The TS algorithm maintains a posterior reward distribution for each arm; at each round, the algorithm samples values from these distributions and the arm corresponding to the highest sample value is chosen.
+The TS algorithm is initialized with a uniform prior and it maintains a posterior reward distribution for each arm; at each round, the algorithm samples values from these distributions and the arm corresponding to the highest sample value is chosen.
 Although TS is found to perform extremely well when the reward distributions are Bernoulli, it is established that with Gaussian priors the worst-case regret can be as bad as $\Omega \left( \sqrt{KT\log T}\right)$ \citep{lattimore2015optimally}.
@@
 
-\subsection{Information Theoretic approach}
+\subsection{Information Theoretic Approach}
 
@@
 
-\subsection{Discussion on the various confidence intervals}
+\subsection{Discussion on The Various Confidence Intervals}
 
@@
 \hline
-UCB1        & $\sqrt{\dfrac{2\log (t)}{n_i}}$ & No & Loose confidence interval leading to high regret upper bounds.\\%\midrule
+UCB1        & $\sqrt{\dfrac{2\log (t)}{z_i}}$ & No & Loose confidence interval leading to high regret upper bounds.\\%\midrule
 \hline
@@
 \hline
-MOSS	     	& $\sqrt{\dfrac{\max\lbrace 0,\log(\frac{T}{K n_i})\rbrace}{n_i}}$ & Yes & Confidence interval is based on dividing the horizon uniformly for $K$ arms.\\%\midrule
+MOSS	     	& $\sqrt{\dfrac{\max\lbrace 0,\log(\frac{T}{K z_i})\rbrace}{z_i}}$ & Yes & Confidence interval is based on dividing the horizon proportionally between $K$ arms and $z_i$ pulls for each arm.\\%\midrule
 \hline
 \hline
-OCUCB     	& $\sqrt{\dfrac{2\log(\frac{2T}{t})}{n_i}}$ & Yes & Tightest confidence interval with exploration parameter $\alpha=2$, $\psi=2$ leading to order-optimal regret bounds.\\\midrule
+OCUCB     	& $\sqrt{\dfrac{2\log(\frac{2T}{t})}{z_i}}$ & Yes & Tightest confidence interval with exploration parameter $\alpha=2$, $\psi=2$ leading to order-optimal regret bounds.\\\midrule
 \end{tabular}

### 2018-01-13 Chapter4/prevRes.tex
Latest on 13/1/2017

@@
 
-\subsection{Fixed Budget setting}
+\subsection{Fixed Budget Setting}
 
@@
 The major difference between the two algorithms is the confidence interval such that for UCB1 it is designed for minimizing the cumulative regret but for UCBE it is designed for minimizing simple regret.
-An illustrative table comparing the two is provided in table \ref{table:comp-exp}.
+The confidence interval of UCBE is of the order $O\left( T\right)$ instead of $O\left(\log T\right)$ which helps UCBE to conduct sufficient exploration to reach an exponentially low probability of error in suggesting the best arm at the end of budget $T$.
+Note, that the problem complexity factor $H_1$ needs to be provided as input for the initialization of UCBE.
+
+\subsubsection{UCB-Exploration with Variance Algorithm}
+
+The idea of UCBE can be extended to incorporate the estimation of variance while conducting exploration.
+This idea was first proposed in \citet{audibert2010best} and later studied in a different context in \citet{gabillon2011multi} for identifying the $p$-best arms in a fixed-budget setting.
+We present UCB-Exploration-Variance (UCBEV) in Algorithm  \ref{alg:ucbev}.
+Again, as like UCBE, the choice of the confidence interval scales with $T$ rather than $\log (T)$ so that the probability of error in suggesting the best arm at the end of the budget $T$ is exponentially low.
+Again, like UCBE, the problem complexity factor $H_{\sigma,1}$ (see \citet{gabillon2011multi}) needs to be provided as input for the initialization of UCBEV and furthermore incorporates variance estimates in the complexity factor to conduct better exploration.
+
+\begin{algorithm}[!ht]
+\caption{UCBEV}
+\label{alg:ucbev}
+\begin{algorithmic}[1]
+\State \textbf{Input: } The budget $T$, exploration parameter $a$
+\State Pull each arm once
+\For{$t=K+1,..., T$}
+\State Pull the arm such that $\argmax_{i\in \A}\bigg\lbrace\hat{r}_{i} + \sqrt{\dfrac{a}{z_i}}\bigg\rbrace$, where $a = \dfrac{(T-2K)}{H_{\sigma,1}}$ and $H_{\sigma,1}=\sum_{i=1}^{K}\frac{\sigma_{i}+\sqrt{\sigma_{i}^{2}+(16/3)\Delta_{i}}}{\Delta_{i}^{2}}$.
+\State $t:=t+1 $
+\EndFor
+\end{algorithmic}
+\end{algorithm}
+
+\subsubsection{Comparison between UCB1, UCBE, and UCBEV}
+
+An illustrative table comparing the UCB1 for SMAB setting, UCBE, and UCBEV for the pure exploration setting is provided in table \ref{table:comp-exp}.
 
@@
 \begin{center}
-\begin{tabular}{|p{5em}|p{6em}|p{8em}|p{12em}|}
+\begin{tabular}{|p{5em}|p{4em}|p{11em}|p{11em}|}
 \hline
@@
 \hline
-UCBE       & $\sqrt{\dfrac{a}{z_i}}$ & \begin{align*}a = \dfrac{25(T-K)}{36 H_1},\\ \text{ where }H_1 = \sum_{i=1}^{K}\dfrac{1}{\Delta_i^2}\end{align*} & $a$ is linear in $T$ to minimize simple regret.
+UCBE       & $\sqrt{\dfrac{a}{z_i}}$ & {\begin{align*}& a = \dfrac{25(T-K)}{36 H_1},\\& \text{ where }H_1 = \sum_{i=1}^{K}\dfrac{1}{\Delta_i^2} 
+\end{align*} }
+& $a$ is linear in $T$ to minimize simple regret.
 Here, the main concern is to minimize the probability of error at the end of budget $T$ and conduct as much exploration as possible.
-Hence, a large $a$ helps to reach exponentially low probability of error.\\\midrule
+Hence, a large $a$ helps to reach exponentially low probability of error.\\
+\hline
+\hline
+UCBEV      & $\sqrt{\dfrac{a}{z_i}}$ & {\begin{align*} & a = \dfrac{(T-2K)}{H_{\sigma,1}},\\ &\text{ where } \\  & H_{\sigma,1}=\sum_{i=1}^{K}\frac{\sigma_{i}+\sqrt{\sigma_{i}^{2}+(16/3)\Delta_{i}}}{\Delta_{i}^{2}}
+\end{align*}}
+& Like UCBE, $a$ is linear in $T$ to minimize simple regret. Also, incorporates variance estimates to conduct better exploration.\\\midrule
 \end{tabular}
@@
 
-\subsection{Successive Accept Reject Algorithm for best-p arms setting}
+\subsection{Successive Accept Reject Algorithm for Best-p Arms Setting}
 
@@
 
-\subsection{Fixed Confidence setting}
+\subsection{Fixed Confidence Setting}
 
-In this setting, the learning algorithm has to suggest the best arm(s) with a fixed confidence (given as input) with as fewer number of attempts as possible.
+In this setting, the learning algorithm has to suggest the best arm(s) with a fixed confidence (given as input) with a fewer number of attempts as possible.
 The single best arm identification has been studied in \citet{even2006action}, while for the combinatorial setup \citet{kalyanakrishnan2012pac} have proposed the LUCB algorithm which, on termination, returns  $m$ arms which are at least $\epsilon$ close to the true top-$m$ arms with probability at least $1-\delta$.

### 2018-04-18 rebuttal/rebuttal.tex
Latest on 18/4/2018

\documentclass[twoside]{article}
\setlength{\oddsidemargin}{0.25 in}
\setlength{\evensidemargin}{-0.25 in}
\setlength{\topmargin}{-0.6 in}
\setlength{\textwidth}{6.5 in}
\setlength{\textheight}{8.5 in}
\setlength{\headsep}{0.75 in}
\setlength{\parindent}{0 in}
\setlength{\parskip}{0.1 in}

%
% ADD PACKAGES here:
%

\usepackage{amsfonts,graphicx}
%\usepackage{amsmath}
\usepackage{algorithm}
%\usepackage[noend]{algpseudocode}
\usepackage{verbatim}
\usepackage{datetime}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
%\usepackage[margin=1in]{geometry}
\usepackage{natbib}
%\setcitestyle{nocompress}
%\bibpunct{(}{)}{;}{a}{}{,}

% \usepackage[nocompress]{cite}
%\usepackage{graphicx}
%\usepackage[cmex10]{amsmath}
%\usepackage{authblk}
% \usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
\usepackage{macros}
\usepackage{times}

%
% The following commands set up the lecnum (lecture number)
% counter and make various numbering schemes work relative
% to the lecture number.
%
\newcounter{lecnum}
\renewcommand{\thepage}{\arabic{page}}
\renewcommand{\thesection}{\arabic{section}}
\renewcommand{\theequation}{\arabic{equation}}
\renewcommand{\thefigure}{\arabic{figure}}
\renewcommand{\thetable}{\arabic{table}}

%
% The following macro is used to generate the header.
%
\newcommand{\lecture}[4]{
   \pagestyle{myheadings}
   \thispagestyle{plain}
   \newpage
   \setcounter{lecnum}{#1}
   \setcounter{page}{1}
   \noindent
   \begin{center}
   \framebox{
      \vbox{\vspace{2mm}
    %\hbox to 6.28in { {\bf Report on my work with Adobe
		%\hfill Spring 2018} }
       \vspace{4mm}
       \hbox to 6.28in { {\Large \hfill Response to Reviewer Comments on M.S. Thesis \hfill} }
       \vspace{2mm}
       \hbox to 6.28in { \hfill \it{\today} \hfill}
       \vspace{2mm}
       \hbox to 6.28in { \hfill {Name: Subhojyoti Mukherjee} \hfill}
       \vspace{2mm}
       \hbox to 6.28in { \hfill {Roll Number: CS15S300} \hfill}
       \vspace{2mm}
       \hbox to 6.28in { \hfill {Registered for: Master of Science (by Research)} \hfill}
       \vspace{2mm}
       \hbox to 6.28in { \hfill {Guide : Dr. B. Ravindran, Co-Guide : Dr. N. Sudarsanam} \hfill}
       \vspace{2mm}
       }
   }
   \end{center}
   %\markboth{Lecture #1: #2}{Lecture #1: #2}

   \vspace*{4mm}
}

\renewcommand{\cite}[1]{[#1]}
\def\beginrefs{\begin{list}%
        {[\arabic{equation}]}{\usecounter{equation}
         \setlength{\leftmargin}{2.0truecm}\setlength{\labelsep}{0.4truecm}%
         \setlength{\labelwidth}{1.6truecm}}}
\def\endrefs{\end{list}}
\def\bibentry#1{\item[\hbox{[#1]}]}

%Use this command for a figure; it puts a figure in wherever you want it.
%usage: \fig{NUMBER}{SPACE-IN-INCHES}{CAPTION}
\newcommand{\fig}[3]{
			\vspace{#2}
			\begin{center}
			Figure #1:~#3
			\end{center}
	}
% Use these for theorems, lemmas, proofs, etc.
%\newtheorem{theorem}{Theorem}
%\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{proposition}[theorem]{Proposition}
%\newtheorem{claim}[theorem]{Claim}
%\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{definition}[theorem]{Definition}
%\newenvironment{proof}{{\bf Proof:}}{\hfill\rule{2mm}{2mm}}

% **** IF YOU WANT TO DEFINE ADDITIONAL MACROS FOR YOURSELF, PUT THEM HERE:

%\newcommand\E{\mathbb{E}}

\begin{document}
\lecture{1}{A - Title}{Lecturer Name}{scribe-name}

\section{Response to Reviewer 1}

We thank the reviewer for his cogent comments and have made a few necessary changes as suggested by the reviewer.

\begin{enumerate}

\item \textbf{Abstract:}

\textit{Correction Suggested:} Start with a transparent sentence.

\textit{Correction Done:} Wrote a more specific sentence outlying the main theme of the thesis.

This thesis studies the following topics in the area of Reinforcement Learning: classic Multi-armed bandits in stationary distribution with the goal of cumulative regret minimization using variance estimates and Thresholding bandits in pure exploration fixed-budget setting with the goal of instantaneous regret minimization also using variance estimates.

\item \textbf{Chapter 1, subsection 1.1 (Introduction to Bandits):}

\textit{Correction Suggested:} "In pursuit of these, the agent can be thought of as making a series of \textit{sequential decisions}" to  "series of tautological decisions".

\textit{Correction Done:} Kept the sentence in original form. It should be a "series of sequential decisions" in the setting considered.

In pursuit of these, the agent can be thought of as making a series of \textit{sequential decisions}...

\item \textbf{Chapter 2, subsection 2.5.2(The Upper Confidence Bound Approach)}

\textit{Correction Suggested:} Break the paragraph, starting from "Empirically...".

\textit{Correction Done:} Wrote it into two paragraphs now.

	UCB-Improved incurs a gap-dependent regret bound of $O\left(\frac{K\log (T\Delta^{2})}{\Delta}\right)$, which is better than that of UCB1. On the other hand, the worst case gap-independent regret bound of UCB-Improved is $O\left(\sqrt{KT\log K}\right)$.

    Empirically, UCB-Improved is out-performed by UCB1 in almost all environments. This stems from the fact that UCB-Improved is pulling all arms equal number of times in each round and hence spends a significant number of pulls in initial exploration as opposed to UCB1 thereby incurring higher regret.

\item \textbf{Chapter 4, subsection 4.1 (Introduction to Thresholding Bandits):}

\textit{Correction Suggested:} Can go to section 1.9.

\textit{Correction Done:} Removed the line that "An interested reader can
read through the previous chapters or can continue from here."

\item \textbf{Chapter 4, subsection 4.2 (Notations and Assumptions):}

\textit{Correction Suggested:} In the sentence "Whenever there is no ambiguity about the underlaying...." correct "underlaying"

\textit{Correction Done:} Corrected the spelling to, "Whenever there is no ambiguity about the underlying...."

\item \textbf{Chapter 4, subsection 4.6 (Challenges in the TBP seeting):}

\textit{Correction Suggested:} Write more succinctly.

\textit{Correction Done:} Rewrote the paragraph.

Further, if we look closely into the TBP setting we will see that there are several similarities between the challenges in SMAB setting and the TBP setting. These challenges are as follows:-

\begin{enumerate}
\item The more closer an arm’s expected reward mean ($r_i$) is  to $\tau$, the more harder is the problem. This stems from the fact that it becomes increasingly difficult to discriminate between the arms lying above and below $\tau$.
\item Lesser the budget $T$, the more harder is the problem. This is because there are lesser number of pulls available and so the number of samples collected tends to be low.
\item The higher the variance of an arm’s reward distribution $D_i$, the more harder is the problem. This is similar to the first case as it becomes harder to discriminate between the arms lying close to the threshold.
\end{enumerate}

\item  \textbf{Chapter 5, subsection 5.1 (Introduction):}

\textit{Correction Suggested:} Capitalize proper nouns such as "section 1"  to "Section 1", "chapter 1" to "Chapter 1", "table 1" to "Table 1" and "figure 1" to "Figure 1".

\textit{Correction Done:} Rewrote all such usages in the thesis.

The rest of the chapter is organized as follows. We elaborate our contributions in Section~5.2 and  we present the AugUCB algorithm in Section~5.3. Our main theoretical result on expected loss is stated in Section~5.4. Section~5.5 contains numerical simulations on various testbeds to show the performance of AugUCB against state-of-the-art algorithms and finally, we summarize in Section~5.6.

\item \textbf{Chapter 5, subsection 5.4 (Proofs):}

\textit{Correction Suggested:} Proofs can be non-italics format style.

\textit{Correction Done:} I did not tamper with the format specified for MS Thesis, so kept the proof format style unchanged.

\item \textbf{Chapter 6, subsection 6.1 (Conclusions):}

\textit{Correction Suggested:} Some word changes.

\textit{Correction Done:} Rewrote the paragraph with the changes..

In this thesis, we studied two different bandit problems, the stochastic multi-armed bandit (SMAB) with the goal of cumulative regret minimization and pure exploration stochastic thresholding bandit problem (TBP) with the goal of expected loss minimization. For the first problem, we devised a novel algorithm called Efficient UCB Variance (EUCBV) which enjoys an order optimal regret bound and performs very well in diverse stochastic environments. In the second part, the thresholding bandit problem, we came up with the novel algorithm called Augmented UCB (AugUCB) which is the first algorithm to use variance estimation for the considered TBP setting and also empirically outperforms most of the other algorithms.

\end{enumerate}

\end{document}

### 2018-04-18 Chapter1/outline.tex
Latest on 8/1/2017
Latest on 18/4/2018

@@
 In this section, we give a general outline of the thesis that is to follow.
-In chapter \ref{chap:SMAB} we give a detailed overview of the stochastic multi-armed bandit model and the latest available algorithms in this setting.
-In the next chapter \ref{chap:EUCBV} we introduce our algorithm Efficient UCB Variance (EUCBV) for the stochastic multi-armed bandit model.
+In Chapter \ref{chap:SMAB} we give a detailed overview of the stochastic multi-armed bandit model and the latest available algorithms in this setting.
+In the next Chapter \ref{chap:EUCBV} we introduce our algorithm Efficient UCB Variance (EUCBV) for the stochastic multi-armed bandit model.
 We give theoretical guarantees on the performance of EUCBV and also show in numerical simulations that it indeed performs very well as compared to the state-of-the-art algorithms.
-In the subsequent chapter \ref{chap:tbandit1} we introduce a new variant of pure exploration multi-armed stochastic bandit called the thresholding bandit problem.
+In the subsequent Chapter \ref{chap:tbandit1} we introduce a new variant of pure exploration multi-armed stochastic bandit called the thresholding bandit problem.
 We analyze the connections between thresholding bandit problem and pure exploration problem and also discuss several existing algorithms in both the settings that are relevant to carefully analyze the thresholding bandit problem.
-Then in chapter \ref{chap:tbandit2} we introduce our solution for the thresholding bandit problem, called the Augemented UCB (AugUCB) algorithm.
+Then in Chapter \ref{chap:tbandit2} we introduce our solution for the thresholding bandit problem, called the Augmented UCB (AugUCB) algorithm.
 We analyze our algorithm AugUCB and derive theoretical guarantees for it as well as show in numerical experiments that it indeed outperforms several state-of-the-art algorithms in the thresholding bandit setting.
-Finally, in chapter \ref{ThesisConc} we conclude by briefly summarizing all the problems covered in the thesis and discussing some future directions in which the stated problems can be further extended.
+Finally, in Chapter \ref{ThesisConc} we conclude by briefly summarizing all the problems covered in the thesis and discussing some future directions in which the stated problems can be further extended.
 

### 2018-04-18 Chapter2/intro.tex
Latest on 26/11/2017
Latest on 27/11/2017
Latest on 18/4/2018

@@
 Also, note that in SMAB, the distribution associated with each arm is fixed throughout the entire duration of the horizon denoted by $T$.
+This SMAB formulation is shown in algorithm \ref{alg:SMAB}.
 
@@
 The rest of the chapter is organized as follows.
-We specify all the notations and assumptions in section~\ref{sec:notations}.
-Then we define the problem statement for the SMAB setting in section~\ref{sec:probDef}.
-In the next section~\ref{sec:motivation} we discuss the motivations behind the SMAB setting.
-In section~\ref{sec:related} we discuss extensively on the various state-of-the-art algorithms available for the SMAB setting.
-Finally, we draw our conclusions in section \ref{chap2:conc}.
+We specify all the notations and assumptions in Section~\ref{sec:notations}.
+Then we define the problem statement for the SMAB setting in Section~\ref{sec:probDef}.
+In the next Section~\ref{sec:motivation} we discuss the motivations behind the SMAB setting.
+In Section~\ref{sec:related} we discuss extensively on the various state-of-the-art algorithms available for the SMAB setting.
+Finally, we summarize in Section \ref{chap2:conc}.

### 2018-04-18 Chapter2/probDef.tex
Latest on 26/11/2017
Latest on 13/1/2017
Latest on 18/4/2018

@@
-With the formulation of SMAB stated in algorithm \ref{alg:SMAB}, the learner seeks to identify the optimal arm as quickly as possible to maximize its rewards.
+With the formulation of SMAB stated in Algorithm \ref{alg:SMAB}, the learner seeks to identify the optimal arm as quickly as possible to maximize its rewards.
 In the pursuit of this, the learner faces the task of balancing exploitation and exploration.
@@
 \begin{align*}
-R_{T}=r^{*}T - \sum_{i\in \A} r_{i}z_{i}(T),
+R_{T}=r^{*}T - \sum_{i=1}^{K} r_{i}z_{i}(T),
 \end{align*}

### 2018-04-18 Chapter2/related.tex
Latest on 18/4/2018

@@
     One of the earliest among these algorithms is UCB1 algorithm proposed first in \citet{agrawal1995sample} and subsequently analyzed in \citet{auer2002finite}.
-The UCB1 algorithm (as stated in \citet{auer2002finite}) is mentioned in algorithm \ref{alg:ucb1}.
+The UCB1 algorithm (as stated in \citet{auer2002finite}) is mentioned in Algorithm \ref{alg:ucb1}.
 
@@
 
-    The UCB-Improved  stated in algorithm \ref{alg:ucbi}, proposed in \citet{auer2010ucb}, is a round-based variant of UCB1.
+    The UCB-Improved  stated in Algorithm \ref{alg:ucbi}, proposed in \citet{auer2010ucb}, is a round-based variant of UCB1.
 An algorithm is \textit{round-based} if it pulls all the arms equal number of times in each round and then eliminates one or more arms that it deems to be sub-optimal.
@@
     UCB-Improved incurs a gap-dependent regret bound of $O\left(\frac{K\log (T\Delta^{2})}{\Delta}\right)$, which is better than that of UCB1.
-On the other hand, the worst case gap-independent regret bound of UCB-Improved is $O\left(\sqrt{KT\log K}\right)$.Empirically, UCB-Improved is out-performed by UCB1 in almost all environments.
+On the other hand, the worst case gap-independent regret bound of UCB-Improved is $O\left(\sqrt{KT\log K}\right)$.
+
+    Empirically, UCB-Improved is out-performed by UCB1 in almost all environments.
 This stems from the fact that UCB-Improved is pulling all arms equal number of times in each round and hence spends a significant number of pulls in initial exploration as opposed to UCB1 thereby incurring higher regret.
@@
 
-    In the later work of \citet{audibert2009minimax}, the authors propose the MOSS algorithm which stands for Minimax Optimal Strategy in the Stochastic case (see algorithm \ref{alg:moss}).
+    In the later work of \citet{audibert2009minimax}, the authors propose the MOSS algorithm which stands for Minimax Optimal Strategy in the Stochastic case (see Algorithm \ref{alg:moss}).
 The confidence interval of MOSS is designed in such a way so as to divide the horizon $T$ proportionally between the number of arms $K$ and the number of pulls $z_i$ that each arm is pulled.
@@
 
-Recently in \citet{lattimore2015optimally}, the authors proposed the Optimally Confident UCB (OCUCB) (see algorithm \ref{alg:ocucb}) which incorporates the increasing timestep $t$ in the confidence interval along with the fixed horizon $T$ and exploration parameters $\psi$ and $\alpha$.
+Recently in \citet{lattimore2015optimally}, the authors proposed the Optimally Confident UCB (OCUCB) (see Algorithm \ref{alg:ocucb}) which incorporates the increasing timestep $t$ in the confidence interval along with the fixed horizon $T$ and exploration parameters $\psi$ and $\alpha$.
 The authors showed that the algorithm OCUCB achieves order-optimal gap-dependent regret bound of $O\left(\sum_{i=2}^{K}\frac{\log\left(T/H_i\right)}{\Delta_i}\right)$ where $H_i=\sum_{j=1}^{K}\min\left\lbrace \frac{1}{\Delta_i^2},\frac{1}{\Delta_j^2}\right\rbrace$, and a gap-independent regret bound of $O\left( \sqrt{KT}\right)$.
 This is the best known gap-dependent and gap-independent regret bounds in the stochastic MAB framework.
-However, unlike our proposed EUCBV algorithm (in chapter \ref{chap:EUCBV}), OCUCB does not take into account the variance of the arms; as a result, empirically  we find  that our algorithm outperforms OCUCB in all the environments considered.
+However, unlike our proposed EUCBV algorithm (in Chapter \ref{chap:EUCBV}), OCUCB does not take into account the variance of the arms; as a result, empirically  we find  that our algorithm outperforms OCUCB in all the environments considered.
 
@@
     In contrast to the above work, the UCB-Variance (UCBV) algorithm in \citet{audibert2009exploration} utilizes variance estimates to compute the confidence intervals for each arm.
-In UCBV (see algorithm \ref{alg:ucbv}) the confidence interval term is given by $\sqrt{\dfrac{2\hat{v}_i\log (t)}{s_i}} + \dfrac{3\log (t)}{3}$ where $\hat{v}_i$ denotes the empirical variance of the arm $i$.
+In UCBV (see Algorithm \ref{alg:ucbv}) the confidence interval term is given by $\sqrt{\dfrac{2\hat{v}_i\log (t)}{s_i}} + \dfrac{3\log (t)}{3}$ where $\hat{v}_i$ denotes the empirical variance of the arm $i$.
 Hence, the confidence interval makes sure that the arms whose variances are high are pulled more often to get a better estimates of their $\hat{r}_i$.
@@
     Another notable design principle which has recently gained a lot of popularity is the Thompson Sampling (TS) algorithm (\citep{thompson1933likelihood}, \citep{agrawal2011analysis})  and  Bayes-UCB (BU) algorithm \citep{kaufmann2012bayesian}.
-This TS is stated in algorithm \ref{alg:ts}.
+This TS is stated in Algorithm \ref{alg:ts}.
 The TS algorithm is initialized with a uniform prior and it maintains a posterior reward distribution for each arm; at each round, the algorithm samples values from these distributions and the arm corresponding to the highest sample value is chosen.

### 2018-04-18 Chapter3/introduction.tex
Latest on 18/4/2018

@@
     The rest of the chapter is organized as follows.
-We elaborate our contributions in section~\ref{sec:contri} and in section~\ref{sec:eucbv} we present the  EUCBV algorithm.
-Our main theoretical results are stated in section~\ref{sec:results}, while the proofs are established in section \ref{sec:proofTheorem}.
-Section~\ref{sec:expt} contains results and discussions from our numerical experiments and finally we summarize in section \ref{sec:conc}.
+We elaborate our contributions in Section~\ref{sec:contri} and in Section~\ref{sec:eucbv} we present the  EUCBV algorithm.
+Our main theoretical results are stated in Section~\ref{sec:results}, while the proofs are established in Section~\ref{sec:proofTheorem}.
+Section~\ref{sec:expt} contains results and discussions from our numerical experiments and finally we summarize in Section \ref{sec:conc}.
     %and Appendix \ref{sec:app:EUCBV} contains the proofs of the lemmas that have been used for proving the main result.

### 2018-04-18 Chapter4/connection.tex
Latest on 27/11/2017
Latest on 18/4/2018

@@
 The thresholding bandit problem is a specific instance of the pure-exploration setup of \citet{chen2014combinatorial}.
-To put it in perspective, the considered TBP setup lies at the intersection of the larger pure exploration setting and the stochastic multi-armed bandit (SMAB) setting discussed in chapter \ref{chap:SMAB} and chapter \ref{chap:EUCBV}.
+To put it in perspective, the considered TBP setup lies at the intersection of the larger pure exploration setting and the stochastic multi-armed bandit (SMAB) setting discussed in Chapter \ref{chap:SMAB} and Chapter \ref{chap:EUCBV}.
 This is shown in Figure \ref{fig:con}.
@@
 
-Further, if we look closely into the TBP setting we will see that there are several similarities between the challenges in SMAB setting and the TBP setting.
+Further, if we look closely into the TBP setting we will see that there are several similarities between the challenges in SMAB setting and the TBP setting. These challenges are as follows:-
 
 \begin{enumerate}
-\item Closer an arm’s expected reward mean ($r_i$) to $\tau$ $\Rightarrow$ Harder is the problem.
+\item The more closer an arm’s expected reward mean ($r_i$) is  to $\tau$, the more harder is the problem.
 This stems from the fact that it becomes increasingly difficult to discriminate between the arms lying above and below $\tau$.
-\item Lesser the budget $T$ $\Rightarrow$ Harder is the problem. This is because there are lesser number of pulls available and so the number of samples collected tends to be low.
-\item Higher the variance of an arm’s reward distribution $D_i$ $\Rightarrow$ Harder is the problem.
+\item Lesser the budget $T$, the more harder is the problem. This is because there are lesser number of pulls available and so the number of samples collected tends to be low.
+\item The higher the variance of an arm’s reward distribution $D_i$, the more harder is the problem.
 This is similar to the first case as it becomes harder to discriminate between the arms lying close to the threshold.
@@
 
-In the theoretical section in chapter \ref{chap:tbandit2} we will try to characterize this hardness and give guarantees that are almost optimal.
+In the theoretical section in Chapter \ref{chap:tbandit2} we will try to characterize this hardness and give guarantees that are almost optimal.

### 2018-04-18 Chapter4/intro.tex
Latest on 18/4/2018

@@
-In the previous chapters \ref{chap:SMAB} and \ref{chap:EUCBV} we studied the stochastic multi-armed bandit (SMAB) setting with the goal of minimizing cumulative regret.
+In the previous Chapter \ref{chap:SMAB} and Chapter \ref{chap:EUCBV} we studied the stochastic multi-armed bandit (SMAB) setting with the goal of minimizing cumulative regret.
 In this chapter, we will study another setting called Pure-exploration multi-armed bandits.
-An interested reader can read through the previous chapters or can continue from here.
 Though we re-use the ideas from SMABs, the goal of pure exploration setup is distinctly different from that of cumulative regret minimization of SMABs and the required algorithms to understand this setup are mentioned in this chapter itself.
@@
 
+%An interested reader can read through the previous chapters or can continue from here.
+
     The rest of the chapter is organized as follows.
-We specify all the notations and assumptions in section~\ref{tbandit:notations}.
-Then we define the problem statement for the TBP setting in section~\ref{tbandit:probDef}.
-In the next section~\ref{tbandit:motivation} we discuss the motivations behind the TBP setting.
-In section~\ref{tbandit:prevRes} we discuss extensively on the various state-of-the-art algorithms available for the pure exploration setting, in section~\ref{tbandit:connection} we draw the connection between pure exploration and thresholding bandit setting and then in section~\ref{tbandit:prevResAPT} we discuss the latest works done in the TBP setting.
-Finally, we summarize in section \ref{tbandit:conc}.
+We specify all the notations and assumptions in Section~\ref{tbandit:notations}.
+Then we define the problem statement for the TBP setting in Section~\ref{tbandit:probDef}.
+In the next Section~\ref{tbandit:motivation} we discuss the motivations behind the TBP setting.
+In Section~\ref{tbandit:prevRes} we discuss extensively on the various state-of-the-art algorithms available for the pure exploration setting, in Section~\ref{tbandit:connection} we draw the connection between pure exploration and thresholding bandit setting and then in Section~\ref{tbandit:prevResAPT} we discuss the latest works done in the TBP setting.
+Finally, we summarize in Section~\ref{tbandit:conc}.

### 2018-04-18 Chapter4/notation.tex
Latest on 13/1/2017
Latest on 18/4/2018

@@
-To benefit the reader, we again recall the notations we stated in chapter \ref{chap:SMAB} and also a few additional notations.
+To benefit the reader, we again recall the notations we stated in Chapter \ref{chap:SMAB} and also a few additional notations.
 $\mathcal{A}$ denotes the set of arms, and $|\mathcal{A}|=K$ is the number of arms in $\mathcal{A}$.
@@
 Similarly, we use $\sigma_{i}^{2}$ to denote the true variance of the reward distribution corresponding to arm $i$, while $\hat{v}_{i}(t)$ is the estimated variance, i.e., $\hat{v}_{i}(t)=\frac{1}{z_i(t)}\sum_{b=1}^{z_{i}(t)}(X_{i,b}-\hat{r}_{i})^{2}$.
-Whenever there is no ambiguity about the underlaying  time index $t$, for simplicity we neglect $t$ from the notations and simply use  $\hat{r}_i, \hat{v}_i,$ and $z_i, $ to denote the respective quantities.
+Whenever there is no ambiguity about the underlying  time index $t$, for simplicity we neglect $t$ from the notations and simply use  $\hat{r}_i, \hat{v}_i,$ and $z_i, $ to denote the respective quantities.
 Let  $\Delta_{i}=|\tau-r_{i}|$ denote the distance of the true mean from the threshold $\tau$.
-Also, the rewards are assumed to take values in $[0,1]$.
+Also, like Assumption \ref{SMAB:assm:2}, in this setting too we assume that the rewards of all arms are bounded in $[0,1]$.
 

### 2018-04-18 Chapter4/prevRes.tex
Latest on 18/4/2018

@@
 One of the first algorithms proposed for the fixed budget setting is the UCB-Exploration (UCBE) algorithm in \citet{audibert2010best} used for identifying a single best arm.
-This is shown in algorithm \ref{alg:ucbe}.
+This is shown in Algorithm \ref{alg:ucbe}.
 
@@
 
-This algorithm is quite similar to the UCB1 algorithm discussed in \citet{auer2002finite} (see algorithm \ref{alg:ucb1}).
+This algorithm is quite similar to the UCB1 algorithm discussed in \citet{auer2002finite} (see Algorithm \ref{alg:ucb1}).
 The major difference between the two algorithms is the confidence interval such that for UCB1 it is designed for minimizing the cumulative regret but for UCBE it is designed for minimizing simple regret.
@@
 
-An illustrative table comparing the UCB1 for SMAB setting, UCBE, and UCBEV for the pure exploration setting is provided in table \ref{table:comp-exp}.
+An illustrative table comparing the UCB1 for SMAB setting, UCBE, and UCBEV for the pure exploration setting is provided in Table \ref{table:comp-exp}.
 
@@
 This algorithm is quite different than upper confidence bound based algorithms because it does not rely on any explicit confidence interval to select arm at every timestep.
-It is shown in algorithm \ref{alg:sr}.
+It is shown in Algorithm \ref{alg:sr}.
 
@@
 
-From algorithm \ref{alg:sr} we see that SR is a round based algorithm quite similar to UCB-Improved (see algorithm \ref{alg:ucbi}).
+From Algorithm \ref{alg:sr} we see that SR is a round based algorithm quite similar to UCB-Improved (see Algorithm \ref{alg:ucbi}).
 Similar to UCB-Improved, SR pulls all arms equal number of times in each round and then discards some arm that it deems to be sub-optimal until it is left with a single best arm.
@@
 These algorithms are similar to the UCBE type algorithm discussed in the previous section.
-In this section, we will discuss the Successive Accept Reject strategy shown in algorithm \ref{alg:sar}.
+In this section, we will discuss the Successive Accept Reject strategy shown in Algorithm \ref{alg:sar}.
 

### 2018-04-18 Chapter4/prevResAPT.tex
Latest on 18/4/2018

@@
 Note, that the most difficult arms to discriminate are the arms whose expected means are lying close to the threshold $\tau$, hence APT pulls those arms whose sample means $\hat{r}_i$ are lying close to the threshold and the arms which have not been pulled often.
-The second condition is satisfied by the $\sqrt{z_i}$ term which acts very similar to the confidence interval term discussed for UCBE (see algorithm \ref{alg:ucbe}).
+The second condition is satisfied by the $\sqrt{z_i}$ term which acts very similar to the confidence interval term discussed for UCBE (see Algorithm \ref{alg:ucbe}).
 The tolerance level $\epsilon\geq 0$ gives the algorithm a degree of flexibility in pulling the arms close to the threshold.

### 2018-04-18 Chapter5/intro.tex
Latest on 18/4/2018

--- 2017-11-05 Chapter5/intro.tex
@@
 Through our simulation work, we establish that AugUCB, owing to its utilization of variance estimates, performs significantly better than the state-of-the-art APT, CSAR and other non variance-based algorithms.
+
+The rest of the chapter is organized as follows.
+We elaborate our contributions in Section~\ref{tbandit:contribution} and  we present the AugUCB algorithm in Section~\ref{tbandit:algorithm}.
+Our main theoretical result on expected loss is stated in Section~\ref{tbandit:results}.
+Section~\ref{tbandit:expt} contains numerical simulations on various testbeds to show the performance of AugUCB against state-of-the-art algorithms and finally, we summarize in Section~\ref{tbandit:conclusion}.

### 2018-04-18 Chapter7/ThesisConc.tex
Latest on 18/4/2018

@@
-In this thesis, we studied two complex bandit problems, the stochastic multi-armed bandit (SMAB) with the goal of cumulative regret minimization and pure exploration stochastic thresholding bandit problem (TBP) with the goal of expected loss minimization.
-For the first problem, we devised a novel algorithm called Efficient UCB Variance (EUCBV) which enjoys an order optimal regret bound and performs superbly in diverse stochastic environments.
+In this thesis, we studied two different bandit problems, the stochastic multi-armed bandit (SMAB) with the goal of cumulative regret minimization and pure exploration stochastic thresholding bandit problem (TBP) with the goal of expected loss minimization.
+For the first problem, we devised a novel algorithm called Efficient UCB Variance (EUCBV) which enjoys an order optimal regret bound and performs very well in diverse stochastic environments.
 In the second part, the thresholding bandit problem, we came up with the novel algorithm called Augmented UCB (AugUCB) which is the first algorithm to use variance estimation for the considered TBP setting and also empirically outperforms most of the other algorithms.

### 2018-04-18 abstract.tex
Latest on 18/4/2018

@@
-This thesis studies the following topics in the area of Reinforcement Learning: Multi-armed bandits in stationary distribution with the goal of cumulative regret minimization and Thresholding bandits in pure exploration setting.
+This thesis studies the following topics in the area of Reinforcement Learning: classic Multi-armed bandits in stationary distribution with the goal of cumulative regret minimization using variance estimates and Thresholding bandits in pure exploration fixed-budget setting with the goal of instantaneous regret minimization also using variance estimates.
 The common underlying theme is the study of bandit theory and its application in various types of environments.

### 2018-04-18 Chapter2/related.tex
Latest on 18/4/2018

@@
  \For{$t=K+1,..., T$}
-\State Pull the arm such that $\max_{i\in A}\bigg\lbrace\hat{r}_{i} + \sqrt{\dfrac{2\hat{v}_i\log (t)}{s_i}} + \dfrac{3\log (t)}{2}\bigg\rbrace$
+\State Pull the arm such that $\max_{i\in A}\bigg\lbrace\hat{r}_{i} + \sqrt{\dfrac{2\hat{v}_i\log (t)}{z_i}} + \dfrac{3\log (t)}{2}\bigg\rbrace$
 \State $t:=t+1 $
@@
     In contrast to the above work, the UCB-Variance (UCBV) algorithm in \citet{audibert2009exploration} utilizes variance estimates to compute the confidence intervals for each arm.
-In UCBV (see Algorithm \ref{alg:ucbv}) the confidence interval term is given by $\sqrt{\dfrac{2\hat{v}_i\log (t)}{s_i}} + \dfrac{3\log (t)}{3}$ where $\hat{v}_i$ denotes the empirical variance of the arm $i$.
+In UCBV (see Algorithm \ref{alg:ucbv}) the confidence interval term is given by $\sqrt{\dfrac{2\hat{v}_i\log (t)}{z_i}} + \dfrac{3\log (t)}{3}$ where $\hat{v}_i$ denotes the empirical variance of the arm $i$.
 Hence, the confidence interval makes sure that the arms whose variances are high are pulled more often to get a better estimates of their $\hat{r}_i$.
@@
 \hline
-UCBV        & $\sqrt{\dfrac{2\hat{v}_i\log (t)}{s_i}} + \dfrac{3\log (t)}{2}$ & No & Confidence interval uses variance estimation.\\
+UCBV        & $\sqrt{\dfrac{2\hat{v}_i\log (t)}{z_i}} + \dfrac{3\log (t)}{2}$ & No & Confidence interval uses variance estimation.\\
 \hline

### 2019-05-30 Chapter1/contribution.tex
thesis initial draft

@@
 \begin{enumerate}
-\item We proposed a novel algorithm for the stochastic multi-armed bandit (MAB) problem.
-Our proposed Efficient UCB Variance method, referred to as EUCBV is an arm elimination algorithm based on UCB-Improved and UCBV strategy which takes into account the empirical variance of the arms and along with aggressive exploration factors eliminate sub-optimal arms.
-Through a theoretical analysis, we establish that EUCBV achieves a better gap-dependent regret upper bound than UCB-Improved, MOSS, UCB1, and UCBV algorithms.
-EUCBV enjoys an order optimal gap-independent regret bound same as that of OCUCB and MOSS, and better than UCB-Improved, UCB1 and UCBV.
-Empirically, in several considered environments EUCBV outperforms most of the state-of-the-art algorithms.
+\item We propose the MLTimer alogrithm that uses gate-sizing for reducing the leakage power consumption of a digital design.
+We propose a smart one-pass tool that can leverage the right optimization technique at the appropriate stage of the flow thereby improving design productivity.
+A key observation reported in MLTimer is that there exists significant correlation between the timing slacks of gates in the current iteration to the gate replacements in successive iterations.
+MLTimer leverages this observation to reduce the number of STA runs thereby reducing the overall time taken for optimization.
 
-\item We proposed the Augmented-UCB (AugUCB) algorithm for a fixed-budget version of the thresholding bandit problem (TBP), where the objective is to identify a set of arms whose quality is above a threshold.
-A key feature of AugUCB is that it uses both mean and variance estimates to eliminate arms that have been sufficiently explored.
-This is the first algorithm to employ such an approach for the considered TBP.
-Furthermore, in numerical evaluations, we establish in several considered environments that AugUCB outperforms all the algorithms that do not take into consideration the variance of the arms in their action selection strategy.
+\item We propose the Karna algorithm which uses gate-sizing for reducing the information leakage via the power side-channel of a digital design.
+We show that each region in a given design leaks information differently.
+Thus, it is sufficient to optimize gates in the highly sensitive regions to reduce information leakage.
+Karna leverages this observation and optimizes gates in these sensitive regions to reduce the power side-channel vulnerability.
 

### 2019-05-30 Chapter1/feedback.tex
thesis initial draft

@@
 
-\begin{algorithm}[!th]
-\caption{An online sequential game}
-\label{alg:OSeqGame}
-\begin{algorithmic}
-\State {\bf Input:} Time horizon $T$, $K$ number of arms with unknown parameters of reward distribution
-\State \For{ each timestep $t=1,2,\ldots, T$}
-\State The environment chooses a reward vector $F^{env}_{t}= \left[r_{i,t}\sim^{i.i.d} D_{i},\forall i\in\A\right]$.
-\State The learner chooses $m$ actions such that $m < K$ following some policy $\pi$, where $\A$ is the set of arms and $|\A|=K$.
-\State The learner observes the reward vector $G^{obs}_{t}\subseteq F^{env}_{t}$.
-\State \EndFor
-\end{algorithmic}
-\end{algorithm}
+% \begin{algorithm}[!th]
+% \caption{An online sequential game}
+% \label{alg:OSeqGame}
+% \begin{algorithmic}
+% \State {\bf Input:} Time horizon $T$, $K$ number of arms with unknown parameters of reward distribution
+% \State \For{ each timestep $t=1,2,\ldots, T$}
+% \State The environment chooses a reward vector $F^{env}_{t}= \left[r_{i,t}\sim^{i.i.d} D_{i},\forall i\in\A\right]$.
+% \State The learner chooses $m$ actions such that $m < K$ following some policy $\pi$, where $\A$ is the set of arms and $|\A|=K$.
+% \State The learner observes the reward vector $G^{obs}_{t}\subseteq F^{env}_{t}$.
+% \State \EndFor
+% \end{algorithmic}
+% \end{algorithm}
 

### 2019-05-30 Chapter1/intro.tex
thesis initial draft

--- 2017-10-14 Chapter1/intro.tex
@@
-In today's world a large number of problems in science and engineering, robotics and 
-game playing, resource management, financial portfolio
-management, medical treatment design, ad placement, website optimization and packet routing can be modeled as sequential decision-making under uncertainty. Many of these real-world interesting
-sequential decision-making problems can be formulated as reinforcement
-learning (RL) problems (\cite{bertsekas1996neuro}, \cite{sutton1998reinforcement}).
+One of the significant moments that has shaped human history was the invention of the computer.
+What essentially started out as an attempt to replace and replicate simple arithmetic functions now surrounds us on a day-to-day basis taking care of our transport, health, finance and ingratiating itself into our daily lives more and more.
+
+This evolution has largely been made possible due to the invention of the transistor by Bell & Schokley in 1951 which caused computers to go from the size of an airplane hangar to tiny microscopic devices.
+The invention of the transistors enabled chip designers to meet the ever increasing user requirements by halving the size of the transistors and thereby doubling the number of transistors that could be packed into the same area.
+This phenomenon also dubbed as Moore’s law has enabled chip designers meet the exponentially increasing functionality requirements.
+
+In addition to increasing functionality, digital devices are also expected to meet additional constraints which can be enumerated using the tuple {Power, Area and Delay}.
+Depending on the platform in which it gets deployed, the chip designer might have to optimize the same design to meet  two orthogonal constraints.
+For example, when building a server, the processor is expected to be fast while the power and area requirements are relaxed but on the other hand if the same processor is to be used on a IoT device, the designer might have to optimise the design for low power, smaller area while the device might not be expected to perform at the same speed as the server.
+**{ Can we rewrite it with a better example?}
+
+We now discuss the three key objectives that a given digital design is expected to meet. 
+\begin{enumerate}
+    \item \textbf{Delay} With each passing generation 
+\end{enumerate}
+
+%Computers have evolved from being simple calculators to devices that can perform complex operations that are employed in various aspects of our day-to-day lives.  
+%This evolution has been
+
+%For the last 70 years, chip designers have been able to meet this expectation by leveraging Moore's law and adding more transistors.
+
+%Today digital devices can be broadly classified into three different classes \begin{enumerate}
+ %   \item Embedded devices: These devices are expected to interact with various aspects of a user's environment such as temperature, motion etc.
+and make decisions on the fly.
+The emergence of Internet of Things as a popular networking paradigm in the last 3 years has led to an increase in the demand for such devices.
+These class of devices typically application specific and perform either "send and send" or lightweight computation at the
+%\end{enumerate}
+
+%In this evolution, the expectations of the end-user from each generation has been increasing.
+While initial generations were expected to merely speed-up arithmetic operations, the development of commercial compute devices starting with Intel's 4004 processor has led to these devices perform complex mathematical functions at a faster rate, on a smaller device by using a little energy as possible.
+
+% In today's world, artificial intelligence has proved to be a game-changer in designing agents that interact with an evolving environment and make decisions on the fly.
+The main goal of artificial intelligence is to design artificial agents that make dynamic decisions in an evolving environment.
+In pursuit of these, the agent can be thought of as making a series of sequential decisions by interacting with the dynamic environment which provides it with some sort of feedback after every decision which the agent incorporates into its decision-making strategy to formulate the next decision to be made.
+A large number of problems in science and engineering, robotics and game playing, resource management, financial portfolio management, medical treatment design, ad placement, website optimization and packet routing can be modeled as sequential decision-making under uncertainty.
+Many of these real-world interesting
+% sequential decision-making problems can be formulated as reinforcement learning (RL) problems (\citep{bertsekas1996neuro}, \citep{sutton1998reinforcement}).
 In an RL problem, an agent interacts with a dynamic, stochastic, and unknown environment, with the goal of finding an action-selection strategy or policy that optimizes some long-term performance measure.
@@
 This is the crux of online sequential learning.
-This is in contrast to supervised learning methods that deal with labeled data which are independently and identically distributed (i.i.d.) samples from the domain and train some classifier on the entire training dataset to learn the pattern of this distribution to predict future samples (test dataset) with the assumption that it is sampled from the same domain, whereas the RL agent learns from the samples that are collected from the trajectories generated by its sequential interaction with the system.
-For an RL agent the trajectory consists of a series of sequential interactions whereby it transitions from one state to another following some dynamics intrinsic to the environment while collecting the reward till some stopping condition is reached.
+
+%     This is in contrast to supervised learning methods that deal with labeled data which are independently and identically distributed (i.i.d.) samples from the considered domain and train some classifier on the entire training dataset to learn the pattern of this distribution to predict the labels of future samples (test dataset) with the assumption that it is sampled from the same domain.
+In contrast to this, an RL agent learns from the samples that are collected from the trajectories generated by its sequential interaction with the system.
+For an RL agent, the trajectory consists of a series of sequential interactions whereby it transitions from one state to another following some dynamics intrinsic to the environment while collecting the reward till some stopping condition is reached.
 This is known as an episode.
-For a single-step interaction, i.e., when the episode terminates after a single transition, the problem is captured by the multi-armed bandit (MAB) model.
-Our work will focus on this idea of MAB model.
+Here, for an action $i_t$ taken by the agent at the $t$-th timestep, the agent transitions from its current state denoted by $S_{i,t}$ to state $S_{i,t+1}$ and observes the reward $X_{i,t}$.
+An illustrative image depicting the reinforcement learning scenario is shown in Figure \ref{fig:rl}.
+
+% \begin{figure}[!th]
+% \includegraphics[scale=0.45]{Chapter1/img/RL1.png}
+% \caption{Reinforcement Learning}
+% \label{fig:rl}
+% \end{figure}
+
+% %To express an RL problem more formally, we have to define the idea of Markov Decision Process (MDP) which consists of states, actions, transition probabilities, and rewards which in turn helps in deciding the strategy to be followed by the agent.
+
+% %An MDP consists of states

### 2019-05-30 Chapter1/objective.tex
thesis initial draft

@@
 \begin{enumerate}
-\item The first objective of this thesis is to study the area of stochastic multi-armed bandit (SMAB) and how to minimize cumulative regret in this setup.
-We intend to give strong gap-dependent and gap-independent regret guarantees in the SMAB setting.
-We also intend to provide the algorithm in the SMAB setting that outperforms the current state-of-the-art algorithms in this setting.
+\item The first objective of this thesis is to study the impact of gate-sizing on leakage power minimization.
+Our problem formulation takes into account the delay constraints of a given design.
+We also address the issues of scalability and, runtime.
 
-\item The second objective of this thesis is to study the area of thresholding bandit problem (TBP) setting where the goal is to minimize the expected loss at the end of a fixed budget provided as input.
+\item The second objective of this thesis is to study the impact of gate-sizing as a possible countermeasure for power side-channel attacks.
+We propose a gate-sizing algorithm whose objective is to minimize information leakage via the power side-channel.
+We analyze the effectiveness of this algorithm by employing three different cipher designs.
+We also discuss the various factors affecting the convergence of the
+%area of thresholding bandit problem (TBP) setting where the goal is to minimize the expected loss at the end of a fixed budget provided as input.
 We intend to provide strong guarantees with respect to expected loss and also propose the algorithm that does not require any problem complexity as an input.

### 2019-05-30 Chapter1/outline.tex
thesis initial draft

@@
-In this chapter, we gave an overview of the various types of bandits available in the literature and also discussed about the main objectives of the thesis and our contributions.
+ In this chapter, we gave an overview of the power and security issues in digital designs.
+We also discussed the gate-sizing technique and its role in solving the above two problems.
+We now outline the general structure of this thesis.
+In the next chapter, we discuss MLTimer, a learning based lazy evaluation model that uses gate-sizing for solving the leakage power minimization problem in digital circuits.
+We discuss Karna, a gate-sizing algorithm for reducing the power side-channels in digital designs in Chapter 3.
+We compare these two schemes in Chapter 4.
+We conclude by briefly summarizing the problems covered in this thesis and highlight some interesting future directions that they could be further extended.
+
+% various types of bandits available in the literature and also discussed about the main objectives of the thesis and our contributions.
 In this section, we give a general outline of the thesis that is to follow.

### 2019-05-30 Chapter3/background.tex
thesis initial draft

\section{Background on Discrete Sizing Problem}
\label{sec:background}
The TC-DSP problem has been studied extensively in the last 30 years and various optimization techniques have been proposed. In this section, we present a summary of the these efforts.

\subsection{The TC-DSP Problem}
%should check if this wording reflects the equation based formulation.

\noindent Consider a circuit $C$ containing $N$ gates. Let each of the gate be realizable using $m$ choices made available in the standard cell library provided by the standard cell library. Starting from the primary input(s), we define the instant that a signal reaches an input of a gate $g_i$ as the arrival time $A(i)$. Similarly, starting from the primary output(s), we define the maximum limit imposed for each arrival time to ensure operation of the  circuit at the target frequency as the required arrival time $R_{a}(i)$. Slack at the gate $g_i$ is defined as $R_{a}(i) - A(i)$. A positive slack implies that the timing constraint is satisfied, and a negative slack implies that the timing constraint at the particular gate is violated \cite{taucontest}.\\

%Let each of the gate $g_i$ be realizable using several choices of $V_t$ made available in the foundry provided standard-cell library.
 Let $x_{i}^{j}$ denote a discrete variable defined as follows:\\
  \begin{equation}
   {x_{i}^{j}} =
   \left\{
           \begin{array}{lllll}
                  1, \ {\bf if}\ i^{th} gate\  in\ the\ given\ circuit\ is\ realized\\
                  \  \  \ \ with\ j^{th}\ choice\ \ in\ the\ standard\\
                  \   \  \ \ cell\  library\\
                  0, \ {\bf otherwise}\\
          \end{array}
  \right.
  \end{equation}

%
\noindent The optimization problem is to find $x_{i}^{j}$ for lowest leakage power, without violating the critical path timing. Let $fanin(i)$ be the set of all gates driving the $i^{th}$ gate in the circuit. Let $p_{i}^{j}$ and $d_{i}^{j}$ be the power and delay of the gate $g_{i}$ when realized with the $j^{th}$ choice in the standard cell library. $PO(C)$ and $PI(C)$ denote the set of  primary outputs and  primary inputs respectively of the given circuit $C$; and, $T$ denote the timing budget assigned to $C$. The leakage minimization problem for C can be formally stated as follows:
\begin{equation}\label{opt_eqn_1} {\Large{\underset{}{\operatorname{minimize}}\sum_{i=1}^{N} \sum_{j=1}^{m} x_{i}^{j} p_{i}^{j}}}  \end{equation}
\indent \indent \indent \indent \indent such that
\begin{equation}\label{opt_eqn_2} \sum_{j=1}^{m} x_{i}^{j} = 1, \forall i, 1 \leq i \leq N\end{equation}
%\begin{equation}\label{opt_eqn_3}  x_{g_{i,j}} \in \{0,1\}, \forall i, 1 \leq i \leq N_{gate}; \forall j, 1 \leq j \leq m \end{equation}
    \begin{equation}\label{opt_eqn_4} A(i) + \sum_{j=1}^{m} d_{i}^{j} x_{i}^{j} \le A(k), \forall k \in fanin(i)\end{equation}
\begin{equation}\label{opt_eqn_5} A(O) \le T, \forall O \in PO(C) \end{equation}
\begin{equation}\label{opt_eqn_6} A(I) \ge 0, \forall I \in PI(C)\end{equation}\\
\begin{equation} \label{opt_eqn_7} slew(x_{i}^{j}) < max slew(x_{i}^{j}), \forall i,1 \leq i \leq N  \end{equation}
\begin{equation} \label{opt_eqn_8} capacitance(x_{i}^{j})<max capacitance(x_{i}^{j}),  \forall i,1 \leq i \leq N \end{equation} \\

\noindent In the above equations~\ref{opt_eqn_5} and \ref{opt_eqn_6}, $A(O)$ and $A(I)$ denote the arrival-times at primary output wires and primary input wires of $C$ respectively. Equation~\ref{opt_eqn_1} presents the objective function that minimizes the leakage power of the given circuit.
Equation~\ref{opt_eqn_2} ensures that exactly one version of gate $i$ is used among its available $m$ choices.
Equations~\ref{opt_eqn_4}, \ref{opt_eqn_5} and \ref{opt_eqn_6} ensure that the arrival-time constraints are met for all the gates, primary inputs and primary outputs of $C$ respectively.

\noindent The delay of a gate is obtained by using the input slew and load capacitance values to index to an array in the standard cell library. The replacement of a gate with its higher $V_t$ or lower $size$ variants might violate the slew constraints in its fanout cone or capacitance constraints in its fanin cone. Equations ~\ref{opt_eqn_7} and~\ref{opt_eqn_8} ensure that the replacement does not cause such violations.
This formulation has been studied extensively in \cite{hu:12}, \cite{hu:13},\cite{reiman:13}, \cite{li:12}, \cite{ozdal:12},\cite{hu:13}, and \cite{rahman:12} .

\subsection{Prior Work}

Though, the above presented TC-DSP problem formulation has been studied extensively in the last 30 years, the works could not be compared as there was no standard framework to evaluate each proposed solution. Another challenge was that the solutions were largely academic and could not be extended to meet modern technologies. The various challenges faced during the circuit optimization phase in an industrial flow were formulated in \cite{ozdal:12}. The ISPD 2012\cite{ispd:12} contest framework was setup to address the above two challenges. 
It had 7 benchmark netlists. The netlist sizes ranged from $25,000$ gates to $9,50,000$ gates. Each netlist has i) a Verilog file representing the functionality of the circuit; ii) a SPEF file that had the capacitance and resistance value for each net in the design; and, iii) two delay constraint files which could be used to realize a fast and a slow version of the same design respectively.

The various solutions used to tackle the discrete sizing problem can be broadly classified as, i) Non analytical methods which use heuristic based techniques to solve the problem and ii) Analytical methods which try to solve it by posing the problem as a Lagrangian relaxation or as a Convex Optimization problem.

\begin{itemize}
\item \textbf{Non-Analytical Methods:}  Non-Analytical methods rely on greedy heuristics as shown in\cite{hu:12},\cite{mok:12},\cite{reiman:13} and  %dp formulation,
\cite{rahman:12}. %rahman and sachen
        A sensitivity guided heuristic to solve the TC-DSP was proposed by \cite{hu:12}. The authors use a \textit{go-with-the winners} approach. They also observe that evaluating the benchmarks using varying cost functions yields better results. Their proposed solution outperforms the winners of the ISPD2012 contest by a significant margin. A comprehensive survey of the existing leakage optimization techniques is presented in \cite{mok:12}. The authors in \cite{mok:12} also propose a peephole optimization based technique for gate sizing. A simulated annealing based approach to solve the TC-DSP was presented in \cite{reiman:13}. They use the \textit{fanout-of-4 rule} and \textit{logic effort} to initialize the netlist to a good initial configuration. However, their solution fails to achieve timing closure on all benchmark circuits. A $V_t$ optimization technique, that uses a new cost function  $\frac{\delta slack}{\delta leakage}$ where $ \delta slack$, $\delta leakage$ represent the slack variation and leakage variation due to the change in the $V_t$ of the cell respectively, is employed in \cite{rahman:12}. The gates are ranked in ascending order based on the above metric and swapped if there is no timing violation. 
        Dynamic programming based solutions were proposed by \cite{li:12}, \cite{Ketkar:09},\cite{Liu:09} while works like \cite{livramento:14}, \cite{ren:08} employed a network flow based solution. %\cite{Liu:09} use GPU to speedup their DP based solution.
% find the two references.

\item \textbf{Analytical Methods:} Analytical methods try to solve the problem by posing it as 
Convex Optimization Formulation or Lagrangian Formulation. Of these two, the Lagrangian relaxation problem has been shown to be more effective as seen in \cite{ozdal:12}, \cite{li:12},\cite{livramento:14},\cite{flach:13},\cite{livramento:13} and \cite{sharma:15}. The objective is to minimize the total leakage power in the circuit while penalizing any delay violations. A modified formulation that takes into account the capacitance and slew conditions is presented in \cite{li:12}. Their LR formulation improves both the solution quality and the runtime significantly. A multi-threaded approach to solve the problem is presented in \cite{sharma:15}. A new metric to identify the candidate gates that could be replaced with different $V_t$/$size$ choices is presented in \cite{reis:16}.

\end{itemize}

Initial STA engines always processed an entire design, which is impractically expensive for evaluating every 
        replacement~\cite{papa:10}. It is to be noted that replacing the $V_t$/$size$ of a gate $g_i$, changes the arrival times of gates only in the fan-in and fan-out cones\footnote{Fan-in/Fan-out cone of a gate $g$ is defined as the sub-circuit that drives/is driven by the gate $g$\cite{abramovci}.} of $g_i$, while the arrival times of other gates remain unaffected. By performing STA for the entire design, we may end up computing known values repeatedly. 
        To improve the efficiency of the STA engine, several {\em incremental} STA techniques have been proposed in the past~\cite{lee:95},\cite{abato:96},\cite{sapatnekar:96},\cite{mondal:04},\cite{das:06}. In~\cite{lee:95}, {\em incremental} STA is performed by solving the {\em incremental longest path problem}, with a novel algorithm which is linear in the number of edges in the {\em dominance fan-out cone}. In~\cite{abato:96}, a frontier is established by recording the leftmost and rightmost gates in the fan-in and fan-out cone of each gate that gets affected by the change in relative timing values.
Based on a request, incremental timing analysis is performed on the modified design
employing the recorded frontiers of change to limit the timing analysis to 
the {\em affected} regions of the circuit alone. An input based path sensitization approach 
was used for incremental STA in~\cite{sapatnekar:96}.
On a similar note, in~\cite{coudert:97}, the incremental timer is accelerated by only updating a 
set of gates that are in the neighbourhood of the gate whose timing value has been updated. 
In~\cite{mondal:04}, timing queries were modeled using temporal logic and an efficient 
algorithm was proposed to answer those queries. Similarly, in~\cite{das:06}, a more 
efficient incremental STA algorithm which exploits the circuit structure was proposed. 
In all these works, path based algorithms were proposed to 
increase the performance of incremental STA, but none of them except~\cite{abato:96} looked 
at reducing the number of times the incremental STA needs to be performed. 
Even in~\cite{abato:96}, although incremental STA is not performed in every iteration, 
nonetheless some computation is performed in every iteration relating to the signal propagation. 
As a result, the running time complexity does not decrease significantly compared to the use of a normal STA. 
E.g., in~\cite{hu:12}, in spite of using a state-of-art incremental timer, the optimization 
        took greater than $20$ hours for the larger benchmarks $(\ge 540,000)$ in the ISPD 2012 suite. It can be seen from the above works that the STA engines reported so far consume a significant time. The number of times the STA needs to be performed (timing updates) grows linearly with the size of the circuit. Reducing the number of times such updates are performed results in a reduction in the overall running time of the algorithm. This reduction without compromising on the solution quality is the challenge that forms one of the central themes of this paper.

\noindent In the last four years, Machine Learning techniques have shown promise in solving complex optimization problems across various domains \cite{prowatch}. Learning based techniques have also been used to optimize specific bottlenecks in VLSI-CAD as shown in \cite{kahng:2} and \cite{kahng:3}. However to the best of our knowledge ours is the first work to employ Machine Learning for the problem of gate sizing.

%compare both non-analytical and analytical methods.

%~\cite{hu:12},

%The TC-DSP is presented as an instance of Lagrangian Relaxation (LR) problem in~\cite{Hu:11}. The objective is to minimize leakage and the algorithm places a penalty for any delay violations. The timing constraints are introduced in the LR formulation.  The netlist is modeled as a directed acyclic graph and the discrete gate version characteristics are based
%on timing tables provided by the gate library. A Dynamic Programming algorithm
%based on critical tree extraction is proposed to solve the LR optimization problem for discrete gates. An accurate timer is used for sign-off and slack computation.

%ideas that this section should contain: why do we need to take this approach.
%
%
%

### 2019-05-30 Chapter3/biblio.tex
thesis initial draft

\begin{thebibliography}{1}
\bibitem{dennard:74}
R. H. Dennard, F. H. Gaensslen, V. L. Rideout, E. Bassous and A. R. LeBlanc, "Design of ion-implanted MOSFET's with very small physical dimensions", IEEE JSSC ,vol.9 ,no.5 ,1974, pp.256-268.

\bibitem{borkar:99}
Borkar, S., "Design challenges of technology scaling," Micro, IEEE , vol.19, no.4, pp.23,29, Jul-Aug 1999.

\bibitem{kim:03}
N. S. Kim, T. Austin, D. Blaauw, T. Mudge, K. Flautner, J. S. Hu, M. J. Irwin, M. Kandemir and V. Narayanan, V, "Leakage current: Moore's law meets static power", IEEE Computer , vol.36, no.12, 2003, pp.68-75.

%\bibitem{roy:03}
%K. Roy, S. Mukhopadhyay and H. Mahmoodi-Meimand, "Leakage current mechanisms and leakage reduction techniques in deep-submicrometer CMOS circuits", Proceedings of the IEEE , Vol.91, No.2, 2003, pp.305-327.

\bibitem{virat}
V. Gandhi, V.R. Devanathan, V. Visvanathan, M. Patnaik, and V. Kamakoti. "Supply and Body-Bias Voltage Assignment Based Technique for Power and Temperature Control on a Chip at Iso-Performance Conditions". Journal of Low Power Electronics. 9. 207-228. 10.1166/jolpe.2013.1254.

\bibitem{feng:09}
Y. Feng and S. Hu,"The epsilon-approximation to discrete VT assignment for leakage power minimization", International Conference on Computer Aided Design, IEEE/ACM, 2009, pp.281-287.

\bibitem{itrs:2011}
ITRS 2011 Design Chapter. http://www.itrs2.net/2011-itrs.html

\bibitem{kahngtalk}
A. B. Kahng, “PPAC Scaling at 7nm and Below”, Cadence Distinguished Speaker Series talk, San Jose, CA, April 7, 2016.

\bibitem{hu:12}
J. Hu, A. B. Kahng, S. Kang, M.C. Kim and I. L. Markov, "Sensitivity-guided metaheuristics for accurate discrete gate sizing", International Conference on Computer Aided Design, IEEE/ACM, 2012, pp.233-239.

\bibitem{hu:13}
 Andrew B. Kahng, Seokhyeong Kang, Hyein Lee, Igor L. Markov, and Pankit Thapar. 2013. High-performance gate sizing with a signoff timer. In Proceedings of the International Conference on Computer-Aided Design (ICCAD '13). IEEE Press, Piscataway, NJ, USA, 450-457.

\bibitem{mok:12}
S. Mok, J. Lee and P. Gupta, "Discrete sizing for leakage power optimization in physical design: A comparative study", ACM Transactions on Design Automation of Electronic Systems, Vol. 18, No. 1, 15 (2012).

\bibitem{reiman:13}
T. Reimann, G. Posser, G. Flach, M. Johann, and R. Reis, "Simultaneous gate sizing and Vt assignment using fanin/fanout ratio and simulated annealing." in Proc. ISCAS, 2013, pp.2549-2552.

\bibitem{riscv}
N. Gala, A. Menon, R. Bodduna, G. S. Madhusudan and V. Kamakoti, "SHAKTI Processors: An Open-Source Hardware Initiative," 29th International Conference on VLSI Design and 2016 15th International Conference on Embedded Systems (VLSID), Kolkata, 2016, pp. 7-8.

\bibitem{taucontest}
https://sites.google.com/view/taucontest2018/home

\bibitem{li:12}
L. Li, P. Kang, Y. Lu, and H. Zhou, “An efficient algorithm for library-
based cell-type selection in high-performance low-power designs,” in
Proc. ICCAD , Nov. 2012, pp.226-232.

\bibitem{ozdal:12}
M. Ozdal, S. Burns, and J. Hu, “Gate sizing and device technology selection algorithms for high-performance industrial designs,” in Proc. ICCAD , Nov.2012.

 \bibitem{rahman:12}
M. Rahman and C. Sechen, "Post-synthesis leakage power minimization," 2012 Design, Automation \& Test in Europe Conference \& Exhibition (DATE), Dresden, 2012, pp. 99-104.

%\bibitem{wu:08}
%T. H. Wu, L. Xie and A. Davoodi, "A Parallel and Randomized Algorithm for Large-Scale Discrete Dual-Vt Assignment and Continuous Gate Sizing", ASP Journal of Low Power Electronics, Vol. 4, No. 2, pp. 191-201.
%
%\bibitem{boyd:08}
%S. Joshi and S. Boyd, "An Efficient method for large scale gate sizing", IEEE Transactions on Circuits and Systems-I, Vol.55, No.9, 2008, pp.2760-2773.

\bibitem{ispd:12}
M. M. Ozdal, C. Amin, A. Ayupov, S. Burns, G. Wilke, C. Zhuo, "The ISPD -2012 Discrete Cell Sizing Contest and Benchmark Suite", Proc. ACM International Symposium on Physical Design, pp. 161-164, 2012.

\bibitem{ispd:13}
Muhammet Mustafa Ozdal, Chirayu Amin, Andrey Ayupov, Steven M. Burns, Gustavo R. Wilke, and Cheng Zhuo. 2013. An improved benchmark suite for the ISPD-2013 discrete cell sizing contest. In Proceedings of the 2013 ACM International symposium on Physical Design (ISPD '13). ACM, New York, NY, USA, 168-170. DOI: https://doi.org/10.1145/2451916.2451959

\bibitem{Ketkar:09}
S. Hu, M. Ketkar, and J. Hu, “Gate sizing for cell-library-based designs,”
IEEE Transactions on Computer Aided Design
, vol. 28, no. 6, pp. 818-825, 2009

\bibitem{Liu:09}
Y. Liu and J. Hu, “A new algorithm for simultaneous gate sizing and
threshold voltage assignment,” in
Proc.  International  Symposium  on
Physical Design
, 2009, pp. 27-34.

\bibitem{livramento:14}
 Vinicius S. Livramento, Chrystian Guth, José Luís Güntzel, and Marcelo O. Johann. 2014. "A Hybrid Technique for Discrete Gate Sizing Based on Lagrangian Relaxation." ACM Trans. Des. Autom. Electron. Syst. 19, 4, Article 40 (August 2014),pp 40:1-40:25.

\bibitem{ren:08}
H. Ren and S. Dutt, “A Network-Flow Based Cell Sizing Algorithm”,Proc. IWLS, 2008, pp. 7–14.

\bibitem{flach:13}
Flach Guilherme,  Reimann Tiago, Posser Gracieli, Johann Marcelo and Reis Ricardo. "Simultaneous Gate Sizing and Vth Assignment using Lagrangian Relaxation and Delay Sensitivities." Proceedings of IEEE Computer Society Annual Symposium on VLSI, ISVLSI 2013

\bibitem{livramento:13}
V. S. Livramento, C. Guth, J. L. Guntzel, and M. O. Johann, “Fast
and efficient Lagrangian relaxation-based discrete gate sizing,” in
Proc. DATE , 2013, pp. 1855–1860.

\bibitem{sharma:15}
 Ankur Sharma, David Chinnery, Sarvesh Bhardwaj, and Chris Chu. 2015." Fast Lagrangian Relaxation Based Gate Sizing using Multi-Threading." In Proceedings of the IEEE/ACM International Conference on Computer-Aided Design (ICCAD '15). IEEE Press, Piscataway, NJ, USA, 426-433.

\bibitem{reis:16}
 T. J. Reimann, C. C. N. Sze, and R. Reis, “Cell Selection for High-Performance Designs in an Industrial Design Flow,” Ispd, pp. 65–72, 2016.

\bibitem{papa:10}
D. A. Papa, M. D. Moffitt, C. J. Alpert and I. L. Markov, "Speeding Up Physical Synthesis with Transactional Timing Analysis", IEEE Design and Test of Computers, vol.27, no.5, 2010, pp.14-25.

\bibitem{lee:95}
J. Lee and D.T. Tang, "An Algorithm for Incremental Timing Analysis", Design Automation Conference, IEEE/ACM, 1995, pp.696-701.

\bibitem{abato:96}
R. P. Abato, A. D. Drumm, D. J. Hathaway, and L. P. P. P. van Ginnekenl., "Incremental Timing Analysis", US patent, 5,508,937, to IBM Corp., Patent and Trademark Office, 1996.

\bibitem{sapatnekar:96}
S.S. Sapatnekar, "Efficient Calculation of All-Pairs Input-to-Output Delays in Synchronous Sequential Circuits", International Symposium on Circuits and Systems, IEEE, 1996, pp.724-727.

\bibitem{mondal:04}
A. Mondal and C.A. Mandal, "A New Approach to Timing Analysis Using Event Propagation and Temporal Logic",  Design, Automation and Test in Europe ,IEEE, 2004, pp.1198-1203.

\bibitem{das:06}
Debasish Das, Ahmed Shebaita, Hai Zhou, Yehea Ismail, and Kip Killpack, "FA-STAC: A Framework for Fast and Accurate Static Timing Analysis with Coupling", International Conference on Computer Design, IEEE, 2006, pp.43-49.

\bibitem{coudert:97}
O. Coudert, "Gate sizing for constrained delay/power/area optimization", IEEE Transactions on Very Large Scale Integration Systems, Vol.5, No.4, 1997, pp.465-472.

\bibitem{prowatch}
 Milan Patnaik, Chidhambaranathan R, Chirag Garg, Arnab Roy, V. R. Devanathan, Shankar Balachandran, and V. Kamakoti. 2015. "ProWATCh: A Proactive Cross-Layer Workload-Aware Temperature Management Framework for Low-Power Chip Multi-Processors." J. Emerg. Technol. Comput. Syst. 12, 3, Article 22 (September 2015), 25 pages.

\bibitem{kahng:2}
 Seung-Soo Han, Andrew B. Kahng, Siddhartha Nath, and Ashok S. Vydyanathan. 2014. A deep learning methodology to proliferate golden signoff timing. In Proceedings of the conference on Design, Automation \& Test in Europe (DATE '14). European Design and Automation Association, 3001 Leuven, Belgium, Belgium, , Article 260 , 6 pages. 
 \bibitem{kahng:3}
 Song Bian, Michihiro Shintani, Masayuki Hiromoto, and Takashi Sato. 2017. LSTA: Learning-Based Static Timing Analysis for High-Dimensional Correlated On-Chip Variations. In Proceedings of the 54th Annual Design Automation Conference 2017 (DAC '17). ACM, New York, NY, USA, Article 66, 6 pages. DOI: https://doi.org/10.1145/3061639.3062280

\bibitem{kahng:16}
A. B. Kahng, H. Lee, and J. Li, “Measuring progress and value of IC implementation technology,” Proc. 35th Int. Conf. Comput. Des.  - ICCAD ’16, pp. 1–8, 2016.

\bibitem{kahng:14}
 A. B. Kahng, H. Lee, and J. Li, “Horizontal benchmark extension for improved assessment of physical CAD research,” Proc. 24th Ed. Gt. lakes Symp. VLSI - GLSVLSI ’14, pp. 27–32, 2014.

\bibitem{abramovci}
 Abramovici M., Breuer M., Friedman A.: “Digital Systems Testing and Testable Design”, Computer Science. Press, 1990.

\bibitem{SVM}
http://www.cs.columbia.edu/~kathy/cs4701/documents/$jason\_svm\_tutorial.pdf$

\bibitem{libsvm}
Chih-Chung Chang and Chih-Jen Lin, LIBSVM : a library for support vector machines. ACM Transactions on Intelligent Systems and Technology, 2:27:1--27:27, 2011. Software available at http://www.csie.ntu.edu.tw/~cjlin/libsvm

\bibitem{liblinear}
Lee, Mu-Chu, Wei-Lin Chiang, and Chih-Jen Lin. "Fast matrix-vector multiplications for large-scale logistic regression on shared-memory systems." Data Mining (ICDM), 2015 IEEE International Conference on. IEEE, 2015.

\bibitem{OpenTimer}
T. W. Huang and M. D. F. Wong, "OpenTimer: A high-performance timing analysis tool," 2015 IEEE/ACM International Conference on Computer-Aided Design (ICCAD), Austin, TX, 2015, pp. 895-902.
doi: 10.1109/ICCAD.2015.7372666

%\bibitem{osfa:16}
%S. Roy, D. Liu, J. Singh, J. Um and D. Z. Pan, "OSFA: A New Paradigm of Aging Aware Gate-Sizing for Power/Performance Optimizations Under Multiple Operating Conditions," in IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems, vol. 35, no. 10, pp. 1618-1629, Oct. 2016. doi: 10.1109/TCAD.2016.2523439
%
%
%
%
%
%
%
%
%
%
%\bibitem{chinnery:05}
% D. G. Chinnery and K. Keutzer, "Linear programming for sizing, $V_{th}$ and $V_{dd}$ assignment", International Symposium on Low power electronics and design, ACM, 2005, pp.149-154.
%
%\bibitem{ispd:13}
%M. M. Ozdal, C. Amin, A. Ayupov, S. Burns, G. Wilke, C. Zhuo, "An Improved Benchmark Suite for the ISPD-2013 Discrete Cell Sizing Contest", Proc. of ACM International Symposium on Physical Design, pp. 168-170, 2013.
%
%
%
%
%
%%\bibitem{SENSEOPT}
%%http://vlsicad.ucsd.edu/SIZING/optimizer.html
%%\bibitem{craft}
%%CRAFT Program Aims for Affordable Designer Circuits that Do More with Less Power. http://www.darpa.mil/news-events/2015-08-17
%
%
%
%
%
%
%
%
%
%\bibitem{sundarajan:99}
%V. Sundararajan and K. K. Parhi, “Low power synthesis of dual threshold voltage CMOS circuits", International Symposium on Low Power Electronics and Design, IEEE, 1999, pp.139–144. 
%
%
%
%
%
%\bibitem{cormen:01}
%T. H. Cormen, C. Stein, R. L. Rivest and C. E. Leiserson, "Introduction to Algorithms", $2^{nd}$ Edition, 2001, McGraw-Hill Higher Education.
%
%\bibitem{liu:10}
%Y. Liu and J. Hu, "A New Algorithm for Simultaneous Gate Sizing and Threshold Voltage Assignment", IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems, Vol.29, No.2, pp.223-234, Feb. 2010.

\end{thebibliography}

### 2019-05-30 Chapter3/experiment.tex
thesis initial draft

\section{Experimental Setup}
\label{sec:experiment}
\subsection{Learning Module}
We use Support Vector Machines (SVMs) to predict the $V_t$ and $size$ of the netlist. For each gate in the netlist we compute the features mentioned in Section~\ref{sec:proposed}.
We use \emph{liblinearmulticore} package \cite{liblinear}, an open-sourced multi-threaded SVM implementation. It is an extension of libSVM \cite{libsvm} package and it can implement 11 different SVM models. We selected the \emph{L2Regularized logistic regression} model. The output of the SVM engine is the class label followed by class probability. We have a cascaded SVM  consisting of 2-stages for identifying $V_t$. The first stage identifies if it is an $HV_t$ or not. If it is not an $HV_t$ cell then we give it as an input to the second stage. We have a cascaded SVM consisting of 4-stages for identifying the size of the gate. The library has $10$ gate choices and we label the choices from 0-9. The initial SVM identifies if it is $size$ $0$ or not. If it is not the datapoint is fed to the subsequent stage. We decide if a datapoint belongs to a particular class or not by observing the class probabilities. If the class probability is less than the threshold then we label it as an \emph{unsure} datapoint and we initialize it to $HV_t$ and $size = 0$. The output of the SVM is passed to the delay recovery and power recovery modules.

\subsection{Delay and Power recovery}
The delay and power recovery stages are written in C++ and compiled using g++-4.8 . The netlist is represented as a graph using the \textit{Boost Graph Library version 1.53.0}. Each node in the graph has the following properties: 
%\begin{itemize}
i) node id,  ii) node type: a node can be either an input node or  an output node or one of the thirteen Boolean functions implemented in the ISPD contest library, iii)node slack, iv) arrival time, v) output capacitance, vi) fanouts, vii) fanins, viii) $V_t$, ix) $size$,  x) if the classifier is not able to predict the $V_t$ or $size$ properly then the gate is marked as unsure, xi) leakage, and; xii) critical : A node is marked critical if it has timing violations or if it cannot be optimized further that is, it has been assigned lowest $V_t$ and highest $size$ during the delay recovery phase or it has been assigned highest $V_t$ and smallest $size$ during the leakage power optimization phase.
%\end{itemize}

The values of delay and leakage power are assigned to each node, based on the $V_t$ and $size$. We use the timing engine in \cite{OpenTimer} for Static Timing Analysis which has  options for performing both full and incremental static timing analysis. We use the full STA option for our experiments.

We use ISPD 2012 \cite{ispd:12} benchmarks and the ShaktiC core for our experimental setup. ShaktiC is a 64-bit in-order six stage pipeline processor running Linux version $4.13$. The processor implements the RISC-V microarchitecture. The processor incorporates several architectural features such as single and double precision serialized floating point units, a branch predictor unit, a restoring  multiplier, a restoring divider, instruction and data caches for improving the performance and area. The library is split into two versions i) a mixed cell library containing all the gate choices ii) a performance based library containing only the fast gate choices (all the low $V_t$ cells). The target delay for the design is obtained at $660Mhz$ by synthesizing the netlist with the $LV_t$ library. The resulting high performance netlist is then given as an input to our tool, our implementation of \cite{hu:12} and the commercial synthesis tool for leakage power optimization. The design contains $174,756$ combinational cells and $12,301$ sequential cells. We ran the experiments on a 4-core Xeon-E3120 server class machine with 32GB of memory. The \textit{MLTimer} tool is written in C++ and is compiled using g++-4.8.

### 2019-05-30 Chapter3/introduction.tex
thesis initial draft

@@
+\section{Introduction}
+\label{sec:introduction}
+
+\noindent Dennard's law~\cite{dennard:74} states that the power density would remain constant with technology scaling even with the increase in MOS-device density.
+With modern deep nanometer devices, optimization of power consumption has become more complex than optimization for delay or area.
+This is primarily due to the dominance of leakage power in the sub-100$n$$m$ technology.
+Techniques like supply voltage scaling and threshold voltage scaling have been used in past to reduce dynamic power consumption while maintaining/improving timing of critical path.
+However, in sub-100$n$$m$ regime, the exponential increase in sub-threshold leakage due to  threshold voltage scaling has caused leakage power to dominate in microprocessors~\cite{borkar:99,kim:03}.
+It is also to be noted that leakage power dissipation during idle state does not contribute to any useful computation.
+In addition, excessive leakage power dissipation can also cause power wastage leading to a  potential {\em thermal runaway}\cite{virat}.
+This has led to an extensive research on leakage power optimizations at different levels of the VLSI design flow under aggressive timing constraints.
+
+\noindent Gate-sizing and threshold voltage ($V_t$)-sizing are two efficient techniques that are employed at the design stage for reduction of leakage power under timing constraints.
+In particular, gate-sizing has been very effective in the early and middle stages of the physical synthesis flow.
+% * <sristisravan@gmail.com> 2017-06-28T07:45:15.739Z:
+% 
+% Cite some papers for these statements
+% 
+% ^.
+However, in the post-route stage, gate sizing often necessitates 
+incremental placement, which can result in increase of turn-around-time of chip production~\cite{feng:09}.
+On the other hand, $V_t$ sizing provides enough room for significant optimization in power/timing without any effect on placement.
+Though, increasing the threshold voltage for a gate (say $g$) by  $V_t$ sizing can result in reducing the leakage power, it can significantly increase the delay.
+Hence, either gate-sizing or $V_t$ sizing or a mix of both is used to make the optimal choice of each gate depending on the design stage that the chip is present\cite{virat}.
+
+\noindent A standard cell library consists of different versions of the same cell, one for each threshold voltage.
+However, the number of versions for a given cell is finite and it is limited to the discrete values of the threshold voltages specified by the foundry.
+Thus, it is imperative to identify cells from the standard cell library that have appropriate gate-size/$V_t$ within the set of available values to minimize the overall leakage power of the circuit without violating the timing constraints.
+This optimization problem is called the {\em Timing Constrained Discrete Sizing Problem} (TC-DSP). In this paper, we focus on the TC-DSP for leakage power minimization in digital circuits.
+
+\noindent In addition to the sizing problem, the rapidly shrinking fabrication technology has resulted in an increase in the design optimization effort due to various factors such as multiple process, voltage and temperature corners.
+This in turn has resulted in an increase in the design effort (design productivity) of chips to match the estimated parameter values at the design phase to what is desirable in the  post fabrication phase.
+Fast convergence to high quality solutions is thereby required so as to increase design productivity and meet the consumer demand.
+Practically, the problem of increasing design productivity becomes important during the optimization phase of the VLSI design; as the execution time of this phase spans over hours to days.
+%For example, reducing optimization time for a given parameter from 2 minutes to 1 second gives more than 2 orders of magnitude speed-up.
+But from a practical point of view, this reduction is not valuable as the actual reduction is only 119 seconds, which is comparatively very small in the overall design time, that spans several days or months.
+On the other hand, reducing optimization time from 5 days to 1 hour also gives a $2 \times$ speed-up as explained in the previous case.
+But in this case, the actual reduction in running time is 4 days and 23 hours, which can significantly improve the design productivity.
+% * <sristisravan@gmail.com> 2017-06-28T07:43:33.360Z:
+% 
+% 119 seconds
+% 
+% ^ <slpskp@cse.iitm.ac.in> 2017-06-28T14:34:53.507Z.
+
+\indent ITRS 2011 \cite{itrs:2011} highlights the intensity of research carried out on low power design technology improvements.
+However, the designers are not able to effectively leverage all the optimization choices due to runtime constraints.
+For example, consider a design with three cells and a standard cell library with three $V_t$ and ten gate-size choices.
+If we just consider $V_t$ scaling for power optimization, the search space is $3^3$.
+Further, if the designer uses gate-sizing, the search space increases to $3^{10}$.
+Finally, if a mixed sizing technique is employed, the search space increases to $3^{30}$.
+Thus we can see that, design productivity heavily suffers due to a large exploration space available at each phase of optimization.
+The authors in  \cite{kahngtalk} list the following three hypothetical steps to improve design productivity without compromising power goals namely:  \begin{itemize}
+    \item  \textbf{Optimized back-end:} mixed height library floorplan/placement, ultimate place/route, power/clock distribution;
+    \item  \textbf{Modeling/sign-off criteria:} tightened Back End Of Line (BEOL) corners, reduced guardband and Adaptive Voltage Scaling (AVS) aware sign-off; and,
+    \item  \textbf{Bespoke,design-specific-flow:} predictive one-pass flow, optimal tool usage.
+ \end{itemize} 
+ Consider the following pseudocode which represents the template for any iterative greedy gate-sizing optimization algorithm as seen in \cite{hu:12},\cite{hu:13},\cite{mok:12}, and \cite{reiman:13}.
+The algorithm takes as inputs: the Netlist $C$; containing $N$ gates, that needs to be optimized, a multi-$V_t$ standard cell library, the target frequency $F$ and a function $\alpha(C)$.
+The function $\alpha(C)$ takes as inputs the circuit C, the timing values for each logic element got by performing a Static Timing Analysis (STA), and other foundry specific parameters for the different logic elements in C, to compute a cost for every gate in C.
+\begin{algorithm}
+%\algsetup{linenosize=\tiny}
+\scriptsize
+\LinesNumbered
+\title{Greedy Leakage optimization algorithm}
+\caption{The template for an iterative greedy leakage optimization algorithm }
+\label{alg:naive}
+    \KwIn{1) Netlist of the given circuit $C$ containing $N$ gates represented as a Directed Acyclic Graph (DAG).
+2) Target frequency $F$.
+3) A multi-$V_t$ standard cell library containing multiple cells with different threshold voltages and sizes for every gate; and, 4) Cost function $\alpha(C)$ that computes a cost for every gate in $C$.}
+    \KwOut{A leakage optimized netlist running at the target frequency $F$.}
+ $N \leftarrow gate\ count$\;
+
+    \textit{Initial Configuration:} Assign to each of the $N$ gates a cell from the standard cell library matching its functionality.
+The $V_t$ and $size$ of each gate shall vary with different methods employing this template\;
+Set iteration count to $1$\;
+    Run Static Timing Analysis (STA) and compute $\alpha(C)$\; 
+    A $\leftarrow$ list of gates sorted in decreasing order according to cost computed by $\alpha(C)$\;
+
+    \While{A not empty } {
+        \textit{Gate replacement:} Consider the first element of A (the gate g with the largest cost) and replace it with its unexplored slower choices (increase $V_t$ or decrease the $size$) so as to reduce the leakage power.
+Mark the choice as explored for gate g\;
+        Estimate the new power and the new delay of the circuit $C$ by performing STA\;
+        \If{delay violated} { 
+        \textit{Backtrack procedure:} 
+            Undo the gate replacement and delete it from A\;
+        }
+        \Else {
+            Increment iteration count\;
+            Compute $\alpha(C)$\;
+	    If all the choices for gate g, available in the standard cell library, have been explored delete it from A\;
+        }
+        Sort the gates in A according to decreasing order of cost computed by $\alpha(C)$\;
+    }
+\end{algorithm}
+
+\noindent It can be observed that the convergence of the above algorithm crucially depends on the initial configuration, the cost function $\alpha(C)$ which is used to determine the candidate gate for replacement and the number of STA calls.
+Our proposed leakage optimization technique (\textit{MLTimer}) aims at resolving these bottlenecks.
+The main contributions of this work are as follows:
+\begin{itemize} %check if ieee uses itemize or enumerate??
+\item It has been empirically observed that there exists significant correlation between the timing slacks of gates in the current iteration to the gate replacements in the successive iterations.
+The outcome of this replacement is the fast convergence of the leakage optimization algorithm in lesser number of iterations;
+     \item  It can also be seen that a smart one-pass tool that can leverage the right optimization technique at the appropriate stage of the flow can improve design productivity significantly.
+A novel Support Vector Machine (SVM) based classifier, which provides a good initial design configuration is used to generate a leakage optimal design at the end;
+     \item The \textit{MLTimer} algorithm, which leverages the high iterative correlation between timing slacks in the current iteration and the gate replacements in the successive iterations, thereby enabling  {\em lazy timing analysis} to significantly improve the runtime; and,
+\item An {\em Adaptive Window sizing (AWS) scheme for decision making} to perform {\em multiple  replacements} between successive timing updates.
+
+%\item A lazy adaptive heuristic,  that uses the solution provided by the learning algorithm to provide a leakage optimized solution while meeting the delay constraints.
+%\item To the best of our knowledge, this is the first work to use learning to solve the leakage optimization problem.
+%\item The solutions produced by our algorithm {\em Learntimer} are at least {\em an order of magnitude} faster while retaining the same solution quality as that of iterative greedy heuristics.
+%\item We demonstrate the efficiency of our algorithm on the ISPD2012 benchmarks.
+\end{itemize}
+To the best of our knowledge, this is the first work that employs ML technique to solve the well known leakage optimization problem.
+We demonstrate the efficiency of our algorithm on both the ISPD2012 benchmarks and a homegrown RISC-V (SHAKTIC) processor that runs linux~\cite{riscv}.
+
+% \begin{figure*}[!ht]
+%  \begin{center}
+%  \includegraphics[scale=0.45]{fig/predict}
+% \captionsetup{singlelinecheck=off}
+% \caption [The figure shows the impact of the three hypothetical design steps on solution quality and design time.
+The proposed steps are Optimized back-end: $(mixed height library floorplan/placement, ultimate place/route, power/clock distribution)$ Modeling/sign-off criteria $(tightened BEOL corners, reduced guardband and AVS aware sign-off)$.\#1: Bespoke,design-specific-flow $(predictive one-pass flow, optimal tool usage)$ ]{The figure shows the impact of the three hypothetical design steps on solution quality (QoR) and design time.
+The proposed steps are
+
+%  \label{fig:kahng}
+%  \end{center}
+% \end{figure*}
+
+The rest of the manuscript is organized as follows: Section~\ref{sec:background}  presents the problem along with the literature survey.
+Section \ref{sec:motivation} describes the need for a learning based leakage optimization technique.
+Section~\ref{sec:proposed} describes our proposed algorithm while the experimental setup is highlighted in Section~\ref{sec:experiment}.
+The results are presented in ~\ref{sec:results}.
+Section~\ref{sec:conclusion} concludes the paper.
+% * <sristisravan@gmail.com> 2017-06-28T07:46:32.613Z:
+% 
+% What does STA mean?
+% 
+% ^.
+
 In this chapter, we look at a novel variant of the UCB algorithm (referred to as Efficient-UCB-Variance (EUCBV)) for minimizing cumulative regret in the stochastic multi-armed bandit (SMAB) setting.

### 2019-05-30 Chapter3/motivation.tex
thesis initial draft

\section{Motivation}
\label{sec:motivation}
 The ISPD gate-sizing contests aimed at producing robust solutions that could be easily integrated with an industrial flow. However, as pointed out in \cite{reis:16}, \cite{kahng:16} and \cite{kahng:14}, there still exists some significant challenges. As shown in \cite{kahng:14}, while the proposed solutions worked well in the framework of the contest, optimality was not guaranteed when technology nodes were changed. In this section we present an overview of the common bottlenecks that affect the robustness of the current solutions thus highlighting the need for the proposed \textit{MLTimer} solution. Our observations are as follows: 
\begin{itemize}
    \item \textbf{Initial configuration (line 2 of Algorithm~\ref{alg:naive})}: The algorithm needs to initially choose for every gate in their circuit, a cell of similar functionality from the multiple available cells specified in the standard cell library (typically three $V_t$ and ten $size$ options). Some of the recently proposed optimization techniques such as \cite{ozdal:12}, \cite{hu:12},\cite{li:12},\cite{flach:13}, and \cite{livramento:13} initialize all the gates in the netlist with a low power configuration using the largest $V_t$ and smallest $size$. However in an industrial flow this might not be possible as power optimization might be performed several times during each stage of the design flow. Initializing to a power optimal configuration  might create additional problems during the placement and routing stages as the final solution, while meeting the power constraints, might cause violations in the placement and routing constraints.

    \item \textbf{Cost Function $\alpha(C)$}: Heuristic based solutions rely on cost functions to identify the candidate gate for optimization as seen in line 7 of Algorithm~\ref{alg:naive}.  However as seen in \cite{hu:12}, a single cost function for all designs might not be the best option. A poorly chosen cost function can lead to a sub-optimal solution and can increase the overall runtime of the algorithm. %elaborate talk about the impact of the cost function and 
    \item \textbf{Number of Static Timing Analysis (STA) calls (line $8$ of Algorithm~\ref{alg:naive})}: It can be seen from line $8$ of algorithm~\ref{alg:naive} that each replacement  necessitates an STA call to check whether the replacement has caused any timing violations. The number of STA calls made during the iterative process largely contributes to the overall runtime overheads.

\end{itemize}

\noindent Thus, it is important to note that the quality of any leakage optimization heuristic is affected by the initial configuration, cost function and number of STA calls. We present a few empirical observations and inferences that can be leveraged to improve the above three factors.

\noindent {\bf Observation I}

\noindent Initializing each gate in the netlist  with random choices of both $size$ and $V_t$ (heterogeneous configuration) yielded better solutions in terms of  leakage power, delay and run time than the traditional approach. This is because, as we move to lower nanometer technologies, the delay and power do not scale linearly with $size$ and $V_{t}$. As a result, using a sub-optimal initial configuration might necessitate additional optimizations such as delay recovery, fixing slew and capacitance violations thereby resulting in a large running time. However the problem of finding the right initial configuration and the right cost function is impractical as it requires solving the entire TC-DSP in the initial stage. However as shown in Table~\ref{Tab:tab1}  several circuits can be seen to share \textit{structurally similar} sub-circuit patterns. Two sub-circuits are said to be \textit{structurally similar} if there exists an isomorphism (one-to-one mapping of vertices and edges) between them.  We leverage this observation to find the best possible initial configuration for one instance of the sub-circuit and  reuse the same for other occurrences of the sub-circuit. This has resulted in an initial configuration that causes significant reduction in both the overall execution time and the leakage power.
%A gate that has high negative slack could be subjected to delay optimization ($V_t$ downscaling or upsizing) whereas a gate with high positive slack could be subjected to power optimization. Hence, we need to identify the right operating conditions that affect the final configuration of the gate.

%if possible insert table to support the first point.

%\indent Consider the following example ~\ref{fig:example1}. Gate $G_1$ has same fanin and fanout gates but gets assigned different $V_t$ and $gate-size$ configurations. This is because the $G_1$ in ~\ref{fig:example1} has different slack than $G_1$ in ~\ref{fig:example2}. \textbf{It is not enough if the circuits share the same subcircuit pattern, they should also be under identical design conditions.}. This is illustrated in ~\ref{fig:example3} and ~\ref{fig:example4} where the same gate gets assigned same $V_t$ and $gate size$ even though they dont share a completely identical subcircuit pattern but because they share identical operating conditions.

%\indent From the examples and ~\ref{Tab:tab1} we see that different designs have several similarities which could be leveraged to predict a good initial configuration. While we might not be able to predict the exact final solution, the predicted solution can be used as a starting point for optimization.

\begin{table*}[!t]
\centering
    \caption{Table showing the number of shared patterns across benchmarks. Each pattern is formed by using the gate along with its fanins and fanouts. The values highlighted in bold represent the total number of possible patterns for that particular benchmark. Element i,j represents the number of overlapping patterns of benchmark i in benchmark j.}
    \label{Tab:tab1}

    \begin{tabular}{ |p{2.2cm}| p{1cm}| p{1.2cm}| p{1.7cm} |p{1.4cm} | p{1.2cm}|p{1.4cm}|p{1.4cm}|p{1.4cm}|}
\hline
        \textbf{ Benchmark} & \texttt{DMA} & \texttt{pci} &\texttt{des\_perf} &\texttt{vga\_lcd} &\texttt{b19} &\texttt{leon3mp} &\texttt{netcard} & \texttt{ShaktiC} \\ \hline
    \texttt{DMA}       & \textbf{23,109} & 19,663          & 20,558           & 15,439           & 21,899           & 17,703           & 18,225           & 20,330           \\ \hline
\texttt{pci}       & 14,898          & \textbf{29,844} & 29,015           & 28,845           & 29,284           & 26,426           & 26,463           & 22,316           \\ \hline
\texttt{des\_perf} & 90,475          & 86,729          & \textbf{102,427} & 83,768           & 96,677           & 56,599           & 56,535           & 72,306           \\ \hline
\texttt{vga\_lcd}  & 15,439          & 25,316          & 27,339           & \textbf{147,812} & 41,068           & 69,696           & 58,099           & 100,034          \\ \hline
\texttt{b19}       & 182,984         & 166,217         & 181,228          & 166,372          & \textbf{212,674} & 141,619          & 139,733          & 156,877          \\ \hline
\texttt{leon3mp}   & 470,252         & 460,774         & 484,694          & 436,798          & 467,000          & \textbf{540,352} & 538,939          & 495,941          \\ \hline
\texttt{netcard}   & 813,634         & 809,793         & 834,303          & 785,423          & 796,790          & 860,397          & \textbf{860,949} & 777,582          \\ \hline
\texttt{ShaktiC}   & 120,422         & 86,762          & 72,306           & 100,034          & 134,521          & 94,361           & 115,425          & \textbf{174,756} \\ \hline
 \end{tabular}

\centering

\end{table*}

\begin{table*}[!t]
\centering
    \caption{Table showing the relative number of shared patterns across benchmarks. Each pattern is formed by using the gate along with its fanins and fanouts. The values highlighted in bold represent the total number of possible patterns for that particular benchmark.  Element i,j represents the percentage of overlapping patterns of benchmark i in benchmark j.}
    \label{Tab:tab13}

    \begin{tabular}{ |p{2.2cm}| p{1cm}| p{1.2cm}| p{1.7cm} |p{1.4cm} | p{1.2cm}|p{1.4cm}|p{1.4cm}|p{1.4cm}|}
\hline
        \textbf{ Benchmark} & \texttt{DMA} & \texttt{pci} &\texttt{des\_perf} &\texttt{vga\_lcd} &\texttt{b19} &\texttt{leon3mp} &\texttt{netcard} & \texttt{ShaktiC} \\ \hline
   \texttt{DMA}       & 100 & 85  & 89  & 67  & 95  & 77  & 79  & 88  \\ \hline
\texttt{pci}       & 50  & 100 & 97  & 97  & 98  & 89  & 89  & 75  \\ \hline
\texttt{des\_perf} & 88  & 85  & 100 & 82  & 94  & 55  & 55  & 71  \\ \hline
\texttt{vga\_lcd}  & 10  & 17  & 19  & 100 & 28  & 47  & 39  & 68  \\ \hline
\texttt{b19}       & 86  & 78  & 85  & 78  & 100 & 67  & 66  & 74  \\ \hline
\texttt{leon3mp}   & 87  & 85  & 90  & 81  & 86  & 100 & 100 & 92  \\ \hline
\texttt{netcard}   & 95  & 94  & 97  & 91  & 93  & 100 & 100 & 90  \\ \hline
\texttt{ShaktiC}   & 69  & 50  & 41  & 57  & 77  & 54  & 66  & 100 \\ \hline 
 \end{tabular}

\centering

\end{table*}

% \begin{figure} [!h]
% \begin{circuitikz} \draw %[scale=0.5\textwidth]
% %\begin{minipage}{0.5\textwidth}
% (0,2) node[and port] (myand1) {\footnotesize$G_1$ ($SV_t$)}
% (0,0) node[and port] (myand2) {$G_2$($SV_t$)}
% (2,1) node[or port] (myor) {$G_3$($SV_t$)}
% (4,2) node[and port] (myand3){$G_4$($SV_t$)}
% (4,0) node [and port] (myand4){$G_5$($SV_t$)}
% (myand1.out) -- (myor.in 1)
% (myand2.out) -- (myor.in 2)
% (myor.out)--(myand3.in 1)
% (myor.out)--(myand4.in 1);

% \end{circuitikz}
% \qquad
% \begin{circuitikz} \draw %[scale=0.5\textwidth]
% (0,2) node[and port] (myand1) {$G_1$}
% (0,0) node[and port] (myand2) {$G_2$}
% (2,1) node[or port] (myor) {$G_3$}
% (4,2) node[and port] (myand3){$G_4$}
% (4,0) node [and port] (myand4){$G_5$}
% (myand1.out) -- (myor.in 1)
% (myand2.out) -- (myor.in 2)
% (myor.out)--(myand3.in 1)
% (myor.out)--(myand4.in 1);
% %\end{minipage}
% \end{circuitikz}
% \caption{Consider Gate $G_1$ in both the circuits. $G_1$ has the same fanin and fanout gates but gets assigned different $V_t$ and $gate size$}
% \label{fig:example1}

% \end{figure}

% \begin{circuitikz} \draw
% (0,2) node[and port] (myand1) {}
% (0,0) node[and port] (myand2) {}
% (2,1) node[xnor port] (myxnor) {}
% (myand1.out) -- (myxnor.in 1)
% (myand2.out) -- (myxnor.in 2);
% \end{circuitikz}
% \caption{Consider Gate $G_1$ in both the circuits. $G_1$ has the same fanin and fanout gates but gets assigned different $V_t$ and $gate size$}
% \label{fig:example3}

% \begin{circuitikz} \draw
% (0,2) node[and port] (myand1) {}
% (0,0) node[and port] (myand2) {}
% (2,1) node[xnor port] (myxnor) {}
% (myand1.out) -- (myxnor.in 1)
% (myand2.out) -- (myxnor.in 2);
% \end{circuitikz}
% \caption{Consider Gate $G_1$ in both the circuits. $G_1$ has the same fanin and fanout gates but gets assigned different $V_t$ and $gate size$}
% \label{fig:example4}

\noindent {\bf Observation II:}

\noindent A traditional greedy heuristic for the TC-DSP involves the following two stage validation process for every replacement,
\begin{itemize}
\item {\it Local validation stage:} In this stage a gate ($g$) with the highest slack is assigned the next slower version ($V_t$ upscaled or $size$ reduced) to reduce the leakage power, without violating the timing constraint of $g$.
\item {\it Global validation stage:} The assignment of the entire circuit is validated by performing an incremental STA  and the arrival times/slacks are updated for all gates\footnote{Usually arrival times are associated with a net. 
In this paper, we represent the arrival time of a gate as the arrival time at the output of the gate}.
\end{itemize}

\noindent It is interesting to note that in a slack-based greedy heuristic algorithm as described in~\cite{mok:12}, the gates that are higher in the ordering in the current iteration are successively replaced {\it with a high probability} in the next few iterations. We call this correlation between iterations as {\it iterative correlation}. Applying the greedy heuristic on the \texttt{c432} benchmark circuit from the ISCAS benchmark suite, where the gates were ordered in the decreasing order of slack at the end of each iteration, we see that the gates $51, 59, 70$ and $67$ that were in the top $5$ before iteration $1$, got replaced in successive iterations in the same order as given below. Here $\pi_i$ denotes the ordering of gates at the end of iteration $i$. The integers in the lists below denote the gate IDs. The gates that are {\it underlined} are the ones which get replaced in the respective iterations. It was also observed that the algorithms spend a majority of their running time in the global validation stage.\footnote{It can be noted that Gate $51$ is at the top of the list for both $\pi_1$ and $\pi_2$, as it had large amount of positive slack even after replacement in iteration $1$ and that the standard cell library used has more than two $V_t$ versions.} 
\vspace{0.1cm}
% * <sristisravan@gmail.com> 2017-06-28T07:47:57.575Z:
% 
% explain a bit on c432 and b14, maybe in footnote.. i didn't understand this terminology
% 
% ^.
\\
\noindent $\pi_1$: $\underline{51}$  $52$  $59$ $70$ $67$ $72$ $71$ $58$ $74$ $65$ $56$\ldots\\
$\pi_2$: $\underline{51}$ $52$ $59$ $70$ $67$ $72$ $71$ $58$ $74$ $65$ $56$\ldots\\
$\pi_3$: $\underline{59}$ $70$ $67$ $72$ $71$ $58$ $74$ $65$ $56$ $52$ \ldots\\
$\pi_4$: $\underline{70}$ $67$ $59$ $72$ $71$ $58$ $74$ $65$ $56$ $52$\ldots\\
$\pi_5$: $\underline{67}$ $59$ $72$ $71$ $58$ $70$ $74$ $65$ $56$ $52$\ldots

\vspace{0.1cm}

\noindent \noindent{\textbf{ Inference}}: One of the inferences from the above observation is that there exists a scope for reducing the run-time of the algorithm by exploiting the iterative correlation to postpone the global validation. In other words, the STA can be performed  after {\it multiple} gate replacements ({\it lazy timing evaluation}) in contrast to performing the same after every single gate replacement. This in turn,  significantly reduces the number of STA runs and thereby, the running time of the entire algorithm. To empirically justify the above inference, the following experiment was conducted. The greedy heuristics in~\cite{mok:12} was employed on the \texttt{c432} circuit with one gate being replaced in each iteration. We define $\pi^{'}_i = (gr_1, gr_2, gr_{i-1}, g_i, g_{i+1} ....)$, where 
$gr_j$, $1 \leq j < i$, denote the gate replaced in iteration $j$, and $g_k$, $k \geq i$ are the gates in decreasing slack values at iteration $i$.  
We then construct the matrix $\pi^{'} = \{\pi_1^{'}; \pi_2^{'}; \dots\}$. The {\it autocor} command in {\it GNU Octave} software is used to find the correlations between the rows in $\pi_i^{'}$. The autocorrelation function used in this experiment is shown in Equation~\ref{eqn:autocor}, 
where $i$ stands for the iteration number and $r$ for number of gates being replaced in each iteration.
\begin{equation} \label{eqn:autocor} \rho_{i}^{r} = corr(\pi_i,\pi_{i+r}) \end{equation}

\begin{figure}[!t]
\begin{center}
\includegraphics[scale=0.2]{Chapter3/fig/c432_correlation_between_ordering_replacements_with_throwngates.pdf}
\caption{X axis: $i$, Y axis: $\rho(i,i+r)$, where $i$: iteration number and $r$ : number of gate replacements per each iteration for 
\texttt{c432} circuit}
\label{fig:c432-corr}
\end{center}
\end{figure}
\noindent Figure~\ref{fig:c432-corr}
shows the autocorrelation plot of rows of $\pi^{'}$.
The Y-axis shows the correlation and X-axis the iteration number.
Each waveform on this plot shows how the correlation changes in successive iterations.

\noindent From figure~\ref{fig:c432-corr} we see that though there is scope for reducing the runtime by replacing several gates in each iteration, the optimal number of gates $r_{i}^{opt}$ to be replaced in each iteration varies and is not known beforehand. Hence there is a need to define metrics to compute the value of $r_{i}^{opt}$ effectively.\\
\noindent {\bf Observation III:} \\
It is important to note the impact of replacing multiple gates in a single iteration. In order to quantify the impact of replacing multiple gates in a single iteration we define two metrics:

\begin{itemize}
    \item {\it Backtrack (line number $10$ of Algorithm~\ref{alg:naive}) }: In case of a timing violation during a replacement the current replacement needs to be undone and the arrival/required arrival times of all wires in the circuit have to be updated to the old values which it had before the lazy timing update at the end of last iteration. This procedure is referred to as \textit{backtrack}. A large number of backtracks essentially degrades the running time of the TC-DSP optimization algorithm.

    \item {\it Gate replacement window ($r$) }: In Algorithm~\ref{alg:naive}, only one gate is replaced  with a different $V_t$/$size$ per iteration as seen in line $7$ of the algorithm. This can be increased to $r$ gates. Figure~\ref{fig:saturation-of-running-time} shows the plot of running time versus varying $r$. 
It can be seen here that the running time decreases with an increase in $r$. 
After certain value of $r$ ($r_{opt}$), it saturates and does not improve further. 
        This is because, a very high value of $r$ causes too many backtrack operations thereby saturating the running time of the algorithm. This behavior was observed for other circuits also, although the value of $r_{opt}$ was different 
in each case. In general, the value of $r_{opt}$ increases with the size of the circuit as shown 
in Figure~\ref{fig:ropt}. 
\end{itemize}
\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.2]{Chapter3/fig/b14_running_time_vs_window_size.pdf}
\end{center}
\caption{Saturation of Running time (in s) with window size for \texttt{b14}}
\label{fig:saturation-of-running-time}
\end{figure}
\begin{figure}[t]
\begin{center}
\vspace{-0.2in}
\includegraphics[scale=0.2]{Chapter3/fig/ropt.pdf}
\end{center}
\caption{$r_{opt}$ for different benchmarks}
\label{fig:ropt}
  %}
\caption{Figure showing the impact of varying $r$ over different benchmarks.}
\end{figure}

\noindent Figure~\ref{fig:c432-corr} shows that even for $r=20$, the correlation is very good, providing the opportunity for performing {\it lazy timing updates} between gate replacement iterations. If correlation is good for a certain value of $r$, it indicates that we can replace $r$ gates at a time, without violating timing. However, it impacts the run-time significantly if the iterative correlation is less. Further, it can also be observed in Figure~\ref{fig:c432-corr} that the correlation is not uniform across all iterations. Gates higher up in the ordering considered in the first few iterations have a high degree of correlation, whereas gates considered in the middle exhibit lower correlation. Hence replacing a fixed number of gates for each iteration may not effectively 
exploit the iterative correlation, leading to sub-optimal results.

\noindent It can also be observed that while performing {\em lazy timing analysis}, an incremental-STA based update needs multiple {\em incremental STA runs}, one for each replacement. For a large $r$ , running one full blown STA (FSTA) run is much more efficient than running $r$ incremental-STA (ISTA) runs, 
to make the lazy timing update. For this reason, FSTA is employed for making the lazy timing updates during the  optimization.

\noindent \textbf{Inference}: The above observations can lead to the following inferences:

\begin{itemize}
\item Multiple gates can be replaced in a single iteration using {\it lazy timing analysis}.
\item It would be desirable to change the number of gates being replaced  in successive iterations, by exploiting the iterative correlation to 
effectively improve the algorithm running time, without compromising the solution quality.
\end{itemize}

\noindent From the above observations and inferences, we understand that a) multiple gates can be replaced 
in a single iteration using {\em lazy timing analysis} and that the optimal window size ($r$) for best 
savings in running time depends on the iteration. The next section explains how to adaptively vary $r$ to obtain the best savings in running time, without impacting solution quality. As seen in Table~\ref{Tab:tab1} we also see that two different circuits, irrespective of their sizes, can have many sub-circuits in common. This indicates that some of the solutions for smaller benchmarks can be reused for the larger benchmarks. However, the final $V_t$ and $size$ choice is dependent on several other factors apart from identical sub-circuits. Hence appropriate features need to be chosen so that the solutions for a benchmark can be leveraged while solving for others. To this end, we propose \textit{MLTimer} which uses the above observations to speed-up the leakage power optimization algorithm while improving the solution quality.

### 2019-05-30 Chapter3/problem.tex
thesis initial draft

\section{Problem}

\label{sec:problem}

\noindent Consider a circuit $C$ formed using  $N$ gates. Let each of the gate be realizable using $m$ choices made available in the foundry provided standard cell library.\\
Let $p_{i}$ denote the power of the $i^{th}$ cell in the netlist.\\
Let $d_{i}$ denote the delay of the $i^{th}$ cell in the netlist.\\
Let $A_{i}$ denote the input arrival time at the $i^{th}$ cell in the netlist.\\

%Let each of the gate $g_i$ be realizable using several choices of $V_t$ made available in the foundry provided standard-cell library.
 Let $x_{i}^{j}$ denote a discrete variable defined as follows:\\
  \begin{equation}
   {x_{i}^{j}} =
   \left\{
           \begin{array}{lllll}
                  1, \ {\bf if}\ i^{th} gate\  in\ the\ given\ circuit\ is\ realized\\
                  \  \  \ \ with\ j^{th}\ choice\ of\ cell\ in\ the\ standard\ cell\  library\\
                  0, \ {\bf otherwise}\\
          \end{array}
  \right.
  \end{equation}

%
The optimization problem is to find $x_{i}^{j}$ for lowest leakage power, without violating the critical path timing. Let $fanin(i)$ be the set of all gates driving the $i^{th}$ gate.\\
$PO(C)$ and $PI(C)$ denote the set of  primary outputs and  primary inputs respectively of the given circuit $C$; and, $T$ denote the timing budget assigned to $C$.\\
The leakage minimization problem for C can be formally stated as follows:
\begin{equation}\label{opt_eqn_1} {\Large{\underset{}{\operatorname{Minimize}}\sum_{i=1}^{N_{gate}} \sum_{j=1}^{m} x_{i}^{j} p_{i}}}  \end{equation}
\indent \indent \indent \indent \indent such that
\begin{equation}\label{opt_eqn_2} \sum_{j=1}^{m} x_{i}^{j} = 1, \forall i, 1 \leq i \leq N\end{equation}
%\begin{equation}\label{opt_eqn_3}  x_{g_{i,j}} \in \{0,1\}, \forall i, 1 \leq i \leq N_{gate}; \forall j, 1 \leq j \leq m \end{equation}
\begin{equation}\label{opt_eqn_4} A(i) + \sum_{j=1}^{m} d_{i} x_{i}^{j} \le A(k), \forall k \in fanin(i)\end{equation}
\begin{equation}\label{opt_eqn_5} A(O) \le T, \forall O \in PO(C) \end{equation}
\begin{equation}\label{opt_eqn_6} A(I) \ge 0, \forall I \in PI(C)\end{equation}\\

\noindent In the above equations~\ref{opt_eqn_5} and \ref{opt_eqn_6}, $A(O)$ and $A(I)$ denote the arrival-times at primary output wires and primary input wires of C respectively. Equation~\ref{opt_eqn_1} presents the objective function that minimizes the leakage power of the given circuit.
Equation~\ref{opt_eqn_2} ensures that exactly one version of gate $i$ is used among its available $m$ choices.
Equations~\ref{opt_eqn_4}, \ref{opt_eqn_5} and \ref{opt_eqn_6} ensure that the arrival-time constraints are met for all the gates, primary inputs and primary outputs of C respectively. In the next section, we give a detailed account of the related work on the leakage power minimization problem.

### 2019-05-30 Chapter3/proposed.tex
thesis initial draft

\section{The Proposed Algorithm}
\label{sec:proposed}
In this section we detail the working of our proposed \textit{MLTimer} algorithm. The \textit{MLTimer} algorithm consists of the following modules as shown in Figure~\ref{fig:algo}:
\begin{itemize}
    \item \textbf{Learning Module:} This module employs Support Vector Machines (SVM) to predict an initial configuration ($V_t$ and $size$ values) for each gate in the netlist that could ultimately lead to a power and delay optimal solution.
    \item \textbf{Delay Recovery Module:} This module takes the output configuration provided by the learning module and the target delay as inputs. The module then checks the design for any timing violations and fixes them iteratively using Algorithm~\ref{alg:delay}.
    \item \textbf{Leakage Power Recovery Module:} This module uses the solution provided by the delay recovery module to perform leakage optimization.
\end{itemize}

\noindent We now describe the working of each module in detail.

\begin{figure}[!t]
\begin{center}
\includegraphics[scale=0.35]{Chapter3/fig/learntimer.pdf}
\caption{The flowchart describes the various steps of our \textit{MLTimer} algorithm.}
\label{fig:algo}
\end{center}
\end{figure}

\subsection{The Learning Module}
\label{sec:feature}
\noindent As seen in Figure~\ref{fig:algo}, the Learning Module takes the netlist initialized to $HV_t$%\footnote{The standard cell library has three available $V_t$ choices. We designate the largest $V_t$ choice as $HV_t$ $(V_t=2)$, the second as $SV_t$ $(V_t=1)$ and the third and smallest choice as $LV_t$ $(V_t=0)$. The largest $V_t$ choice ($V_t=2$) is slower but better in terms of leakage power whereas the smallest ($V_t=0$) is faster but consumes more leakage power. Similarly the library has ten available $size$ choices which we designate as $size=0$, $size=1$ and so on. The gate with the smallest $size$ ($size=0$) is slower but is power efficient and the gate with the largest $size$ ($size=9$) is faster but consumes more power. }
and smallest size as input and predicts a $V_t$ and $size$ value for every gate in the netlist in order to reduce the delay and power. We saw in the previous section that though two netlists are functionally different they might share several common sub-circuits as show in Table~\ref{Tab:tab1}. However, two matching gates belonging to different structurally similar sub-circuits might differ in other aspects. For example, the second circuit might have a tighter timing constraint because of which using the $V_t$ and $size$ values of the first circuit might not improve the delay or the power. Instead it might worsen the power and the delay of the second instance thereby requiring additional iterations of optimization. Enumerating all the features that affect two matching gates and comparing them is prohibitively time consuming. Machine Learning (ML) techniques help in this regard. 
\noindent The initial configuration for each gate in the netlist is predicted using the Support Vector Machines.  Support Vector Machine \cite{SVM} is a highly memory efficient supervised learning technique that is primarily used for classification and outliers detection. An SVM engine takes in the labeled training data and tries to find a separation boundary that correctly separates each data point across dimensions. Figure~\ref{fig:SVM} shows an example of the hyperplane that a typical SVM engine computes.

\begin{figure}[!t]
 \begin{center}

\includegraphics[scale=2]{Chapter3/fig/optimal-hyperplane}
 \caption{An example of the hyperplane/decision boundary that an SVM engine would compute. The SVM engine will take in the data-points (labeled in red and blue) $\times$ features $(X1,X2)$ and try to find the boundary between the data-points across the dimensions. Every feature accounts for one dimension.}
 \label{fig:SVM}
 \end{center}
 \end{figure}

Since SVM is a supervised learning technique, it needs to be initially trained with a labeled training data. In the first stage, we train two SVM classifiers to predict the $V_t$ and $size$ for each gate in the netlist, respectively. 
 %\subsubsection{Feature selection}
 %
\noindent We saw in Section~\ref{sec:motivation} that the final choice of $V_t$ and $size$ for a gate is not just dependent on its neighbours but on a variety of other design conditions. Hence, we identify seven such design parameters and use them as features for our technique. These features are described below:.
\begin{itemize}
    \item\textbf{  Gate Type}: This represents the functionality of the gate. Each standard cell library has a collection of low-level Boolean functions. For our experiments we use the ISPD contest library which has $13$ gate types. The gate type distribution across the benchmark circuits is shown in Table~\ref{tab:tab2}. 
 \item\textbf{ Sub-circuit}: A sub-circuit $S_i$ of a gate $g_i$ is the set of gates whose timing values are drastically affected by any change in $V_t$/$size$ of gate $g_i$.  For our experiments $S_i$ comprises the immediate fanins and fanouts of $g_i$.
 \item\textbf{ Local Negative Slack (LNS)}: We define LNS of gate $g_i$ ($LNS_i$) as the sum of all the negative slack paths that pass through $g_i$.
 \item\textbf{ Number of Fanins}: This is the number of inputs to the gate $g_i$. It accounts for the impact of modifying the $size$ of a gate $g_i$. Resizing gate $g_i$ might impact all the gates in the fanin cone of $g_i$.
 \item\textbf{ Number of Fanouts}: This is the number of gates driven by $g_i$. A gate with a large number of fanouts cannot be downscaled as it might introduce c.
 \item\textbf{  Number of Negative Slack Paths}: A high value of LNS could be because of i) a large number of negative slack paths passing through the gate $g_i$; or, ii) a small number of paths with extremely negative slack values. This feature helps to distinguish the former from the latter. 
 \item\textbf{ Slack of the Node}: As pointed out in the previous section, the amount of positive slack determines the degree to which the $V_t$ of the gate can be scaled.

\end{itemize}

 \begin{table*}[!ht]
     \caption{The Table shows the distribution of gates across the ISPD2012 benchmark suite and ShaktiC core. We use the gates from \texttt{pci} for training. In column 1, A$\times$B indicates that a gate has $A$ inputs and $B$ outputs.}
\label{tab:tab2}

     %\centering
     \begin{tabular}{|p{2cm}|p{1cm}|p{1.2cm}|p{1.8cm}|p{1cm}|p{1.6cm}|p{1.4cm}|p{1.4cm}|p{1.4cm}|}
\hline
         \textbf{Gate type}   &\texttt{pci}&\texttt{b19}&\texttt{des\_perf}&\texttt{DMA}&\texttt{leon3mp}&\texttt{netcard}&\texttt{vga\_lcd} & \texttt{ShaktiC}\\ \hline
    \texttt{NOT     }& 10,280                & 46,757        & 39,297              & 5,628         & 163,333           & 184,317           & 48,277     & 40,794        \\ \hline
    \texttt{NAND 2$\times$1}& 15,877                & 59,460        & 29,459              & 10,722        & 163,921           & 583,704           & 80,571 & 52,506            \\ \hline
    \texttt{NAND 3$\times$1}& 208                  & 6,267         & 3,930               & 372          & 8,890             & 912              & 192   & 1,387           \\ \hline
    \texttt{NAND 4$\times$1}& 295                  & 8,534         & 3,552               & 547          & 15,454            & 13,836            & 2,278 & 2,368            \\ \hline
    \texttt{NOR 2$\times$1}  & 1,403                 & 37,942        & 16,641              & 2,146         & 29,599            & 24,025            & 2,498   & 31,048           \\ \hline
    \texttt{NOR 3$\times$1}  & 14                   & 89           & 521                & 20           & 26               & 64               & 11          & 855     \\ \hline
    \texttt{NOR 4$\times$1}  & 3                    & 117          & 12                 & 1            & 1                & 6                & 2            & 1,264     \\ \hline
    \texttt{AOI21$\times$1}     & 734                  & 28,821        & 4,610               & 1,228         & 18,875            & 3,850             & 5,296   & 6,260           \\ \hline
    \texttt{AOI22$\times$1}     & 720                  & 14,921        & 919                & 1,886         & 69,817            & 48,792            & 8,449   & 14,447           \\ \hline
    \texttt{OAI21$\times$1}      & 304                  & 8,647         & 3,450               & 471          & 52,855            & 1,384             & 186    & 13,432           \\ \hline
    \texttt{OAI22$\times$1}      & 6                    & 1,119         & 36                 & 88           & 17,581            & 59               & 52       & 10,395         \\ \hline
\texttt{Total gates} & 29,844 &	212,674	& 102,427	& 23,109	& 540,352	& 860,949 &	147,812 & 174,756 \\ \hline
\end{tabular}
\end{table*}

\begin{table}[!ht]
\centering
\caption{The Table shows the percentage distribution of gates across the ISPD2012 benchmark suite and ShaktiC core. We use the gates from \texttt{pci} for training. In column 1, A$\times$B indicates that a gate has $A$ inputs and $B$ outputs.}
\label{tab:tab23}
\begin{tabular}{|l|l|l|l|l|l|l|l|l|}
\hline
Gate type ( percentage) & pci\_bridge & b19   & des\_perf & DMA   & leon3mp & netcard & vga\_lcd  & ShaktiC\\ \hline
    \texttt{NOT     }    & 34.45       & 21.99 & 38.37     & 24.35 & 30.23   & 21.41   & 32.66   & 23.66 \\ \hline
    \texttt{NAND 2$\times$1     }            & 53.2        & 27.96 & 28.76     & 46.4  & 30.34   & 67.8    & 54.51 & 30.04    \\ \hline
    \texttt{NAND 3$\times$1     }   & 0.7         & 2.95  & 3.84      & 1.61  & 1.65    & 0.11    & 0.13  & 0.7   \\ \hline
    \texttt{NAND 4$\times$1     }   & 0.99        & 4.01  & 3.47      & 2.37  & 2.86    & 1.61    & 1.54  & 1.3   \\ \hline
    \texttt{NOR 2$\times$1    }   & 4.7         & 17.84 & 16.25     & 9.29  & 5.48    & 2.79    & 1.69   & 17.77  \\ \hline
    \texttt{NOR  3$\times$1   }   & 0.05        & 0.04  & 0.51      & 0.09  & 0       & 0.01    & 0.01  & 0.49   \\ \hline
    \texttt{NOR  4$\times$1   }   & 0.01        & 0.06  & 0.01      & 0     & 0       & 0       & 0    &  0.72   \\ \hline
    \texttt{AOI  21$\times$1   }   & 2.46        & 13.55 & 4.5       & 5.31  & 3.49    & 0.45    & 3.58  & 3.58   \\ \hline
    \texttt{AOI   22$\times$1  }   & 2.41        & 7.02  & 0.9       & 8.16  & 12.92   & 5.67    & 5.72   & 8.27  \\ \hline
    \texttt{OAI 21$\times$1    }   & 1.02        & 4.07  & 3.37      & 2.04  & 9.78    & 0.16    & 0.13  & 7.69 \\ \hline
    \texttt{OAI  22$\times$1   }   & 0.02        & 0.53  & 0.04      & 0.38  & 3.25    & 0.01    & 0.04  & 5.95   \\ \hline
\end{tabular}
\end{table}

 \begin{table}[!ht]
     \caption{These Tables show the number of gates for each $V_t$ and $size$ in the training dataset obtained from the \texttt{pci} benchmark. It can be seen that the number of gates at $LV_t$ and $SV_t$ are much less compared to the number of $HV_t$ gates. This problem is commonly referred to as class imbalance in Machine Learning. From the fifth and sixth rows of the Table we can see that this problem exists for $size$ also.}
\label{tab:dist}

     \centering

\begin{tabular}{ll}
\begin{tabular}{|l|l|l|l|}
\hline
\multicolumn{2}{|l|}{$V_t$}              & \multicolumn{2}{l|}{Percentage of gates} \\ \hline
\multicolumn{2}{|l|}{$V_t = 0$ $(LV_t)$} & \multicolumn{2}{l|}{8.47}                \\ \hline
\multicolumn{2}{|l|}{$V_t=1$ $(SV_t)$}   & \multicolumn{2}{l|}{1.86}                \\ \hline
\multicolumn{2}{|l|}{$V_t=2$ $(HV_t)$}   & \multicolumn{2}{l|}{89.97}               \\ \hline
\end{tabular}
&
\begin{tabular}{|l|l|l|l|}
\hline
\multicolumn{2}{|l|}{$size$}              & \multicolumn{2}{l|}{Percentage of gates} \\ \hline
\multicolumn{2}{|l|}{0} & \multicolumn{2}{l|}{84.40}                \\ \hline
\multicolumn{2}{|l|}{1}   & \multicolumn{2}{l|}{13.75}                \\ \hline
\multicolumn{2}{|l|}{2}   & \multicolumn{2}{l|}{0.7}               \\ \hline
\multicolumn{2}{|l|}{3}   & \multicolumn{2}{l|}{0.7}               \\ \hline
\multicolumn{2}{|l|}{4}   & \multicolumn{2}{l|}{0.2}               \\ \hline
\multicolumn{2}{|l|}{$> 5$}   & \multicolumn{2}{l|}{0.25}               \\ \hline
\end{tabular}
\end{tabular}
\end{table}

\noindent There is no empirical/analytical technique to prove that the above features are comprehensive but they are good indicators as to what might happen to the chosen gate. For example, a gate with extremely high fanout count is highly unlikely to be downsized though it might have high positive slack because the downsizing may lead to capacitance violations. We extract these features for every gate in the netlist. We represent each gate in the netlist along with its associated features  as a matrix. In the training phase, each row in the matrix is associated with a $V_t$ and $size$ label. In the testing phase, the matrix is provided as the input to the trained SVMs that predict a $V_t$ and $size$ value for each gate in the netlist.

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
% \usepackage{multirow}
% \begin{figure*}[!t]
%  \begin{center}

% \includegraphics[scale=0.2]{fig/chart1}
%  \caption{An example of the hyperplane/decision boundary that an SVM engine would compute. The SVM engine will take in the data-points(labeled in red and blue) $\times$ features (X1,X2) and try to find the boundary between the data-points across the dimensions (one feature==one dimension).}
%  \label{fig:dist2}
%  \end{center}
%  \end{figure*}

% \begin{table*}[!t]
% \begin{minipage}{0.1\linewidth}
% \centering

% \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|l|l|l|}
% \hline
% Gate type   & NOT & \begin{tabular}[c]{@{}l@{}}2-input\\ NAND\end{tabular} & \begin{tabular}[c]{@{}l@{}}3-input\\ NAND\end{tabular} & \begin{tabular}[c]{@{}l@{}}4-input\\ NAND\end{tabular} & \begin{tabular}[c]{@{}l@{}}2-input\\ NOR\end{tabular} & \begin{tabular}[c]{@{}l@{}}3-input\\ NOR\end{tabular} & \begin{tabular}[c]{@{}l@{}}4-input\\ NOR\end{tabular} & \begin{tabular}[c]{@{}l@{}}2-1-AOI\end{tabular} & \begin{tabular}[c]{@{}l@{}}2-2-AOI\end{tabular} & \begin{tabular}[c]{@{}l@{}}2-1-OAI\end{tabular} & \begin{tabular}[c]{@{}l@{}}2-2-OAI\end{tabular} & Total  \\ \hline
% b19         & 46757    & 59460                                                  & 6267                                                   & 8534                                                   & 37942                                                 & 89                                                    & 117                                                   & 28821                                                         & 14921                                                         & 8647                                                          & 1119                                                          & 212674      \\ \hline
% des\_perf   & 39297    & 29459                                                  & 3930                                                   & 3552                                                   & 16641                                                 & 521                                                   & 12                                                    & 4610                                                          & 919                                                           & 3450                                                          & 36                                                            & 102427      \\ \hline
% DMA         & 5628     & 10722                                                  & 372                                                    & 547                                                    & 2146                                                  & 20                                                    & 1                                                     & 1228                                                          & 1886                                                          & 471                                                           & 88                                                            & 23109       \\ \hline
% leon3mp     & 163333   & 163921                                                 & 8890                                                   & 15454                                                  & 29599                                                 & 26                                                    & 1                                                     & 18875                                                         & 69817                                                         & 52855                                                         & 17581                                                         & 540352      \\ \hline
% netcard     & 184317   & 583704                                                 & 912                                                    & 13836                                                  & 24025                                                 & 64                                                    & 6                                                     & 3850                                                          & 48792                                                         & 1384                                                          & 59                                                            & 860949      \\ \hline
% pci\_bridge & 10280    & 15877                                                  & 208                                                    & 295                                                    & 1403                                                  & 14                                                    & 3                                                     & 734                                                           & 720                                                           & 304                                                           & 6                                                             & 29844       \\ \hline
% vga\_lcd    & 48277    & 80571                                                  & 192                                                    & 2278                                                   & 2498                                                  & 11                                                    & 2                                                     & 5296                                                          & 8449                                                          & 186                                                           & 52                                                            & 147812      \\ \hline
% \end{tabular}
% \caption{This table shows the distribution of gates in each ISPD benchmark. We chose pci as it has a uniform distribution of gates. }
% \label{tab:dist2}
% \end{minipage}
% \end{table*}

We use the \texttt{pci} benchmark for generating the training data. It has approximately $30,000$ gates. We use both the slow and fast variants to generate around $60,000$ samples for training the two classifiers. We implemented a greedy replacement heuristic and used it to generate the $V_t$ and $size$ for each gate of all the benchmarks used for training and validating the classifiers. Table~\ref{tab:dist} shows the distribution of the training data-points across $V_t$ and $size$. The aim of the classifier is to predict a good initial configuration which the leakage and delay  steps can use to reach an optimal solution quickly. It is crucial to identify the right set of gates that need to be swapped in order to reach the target solution.

Since SVM is a supervised learning process, the efficiency of the classifier is highly dependent on the number and nature of training examples. Interestingly we see from Table~\ref{tab:dist} that though the total number of examples available is quite high, the number of gates that need to be swapped from their initial configuration are few in number. These are the gates that are of interest to us as they help in identifying the conditions to swap the $V_t$/$size$ of a gate. It can be seen in Table~\ref{tab:dist} that  we only need to swap very few gates $(\approx20\%)$ to reach an optimal configuration for \texttt{pci} benchmark from which we gather our training data. As a result there are less number of datapoints belonging to $LV_t (V_t=0)$ and $SV_t (V_t=1)$ and a similar observation is also true for $size\geq1$. Thus we see that there is a skew in the nature of datapoints available for training. This skew in the dataset is referred to as \textit{class imbalance}. We resolve the class imbalance by the following two techniques:

\begin{itemize}
    \item\textbf{ Use a cascaded classifier}: Cascaded classification is an ensemble learning technique, wherein multiple instances of the classifiers are used to predict the final class label. Instead of treating the problem as a multi-class classification problem we reduce it to a binary classification problem. We construct a series of classifiers for both $V_t$ and $size$. The cascaded classifier architecture is shown in Figure~\ref{fig:vtsvm}. The cascaded classifier setup works as follows: The first stage of the classifier is trained to classify a given datapoint as $HV_t (V_t=2)$ or not $HV_t (V_t< 2)$. If a gate is classified as not $HV_t (V_t<2)$ then it is given as an input to the subsequent stage which determine if the gate is $LV_t (V_t=0)$ or $SV_t (V_t=1)$. We follow a similar procedure for building the SVM that predicts the ${size}$. The  advantage in using a cascaded setup is that the features in each stage can be fine-tuned to perform well for only a specific $V_t$/$size$ which is easier than fine-tuning the features for all the $V_t$s or $sizes$. 
    In order to determine the accuracy of the output class we use a thresholding function. The thresholding function is based on the class probability of the classifier. If the classifier assigns a class-label at random then the class probability will be approximately equal to $0.5$. A value greater than $0.5$ indicates that the predicted $V_t$/$size$ was not randomly assigned. Thus, the class probability is a good metric to determine the accuracy of the classifier. The thresholding function is a hyper-parameter that can be individually tuned for each stage in the cascaded setup. 
\begin{figure*}[!t]
 \begin{center}
 \includegraphics[scale=0.3]{Chapter3/fig/flowchart.pdf}
 \caption{Hierarchical SVM $V_t$ classifier. The first stage $V_t$ classifier classifies the points as $HV_t$ ($V_t = 2 $) or not $HV_t$ ($V_t < 2$) using the thresholding function $T_1$. If the data-point is predicted as not $HV_t$ then it is forwarded to the second stage classifier which uses the thresholding function $T_2$ to classify them as $SV_t$ ($V_t = 1$) and $LV_t$ ($V_t = 0$). The hierarchical $size$ classifier has $5$ -stages.}
 \label{fig:vtsvm}
 \end{center}
 \end{figure*}
%\begin{figure}[!t]
% \begin{center}
% \includegraphics[scale=0.5]{fig/cascaded_size.pdf}
% \caption{Hierarchical SVM $size$ classifier. The first stage $size$ classifier classifies the points as $size = 0$ or $size > 0$ using the thresholding function. The second stage classifier takes the points labelled as $size > 0$ as inputs and uses the thresholding function to classify them as $size = 1$ and $size > 1$. The subsequent \emph{i} stages attempt to classify the input as $size=\emph{i}$ and $size > \emph{i}$.}
% \label{fig:sizesvm}
% \end{center}
% \end{figure}
    \item\textbf{ Boosting the weights of the minority classes}: While the cascaded setup solves the class imbalance problem in the $V_t$ classification, it does not completely resolve the problem in ${size}$ classification. This is because the number of sample points available for the larger sizes is extremely small as can be seen in Table~\ref{tab:dist}. It can be observed from the table that the number of sample points available for $size \geq 2$ is less than $1\%$ which is insufficient for training. This problem is resolved by boosting the weights of the features that belong to the minority classes. During training we manually increase the weights associated with the minority class to improve the performance of each classifier.

\end{itemize}

% Please add the following required packages to your document preamble:
% \usepackage{multirow}

% \begin{table}[!t]
% \parbox{.45\linewidth}{

%    \centering

% \begin{tabular}{cc}
% \hline
% $\mathbf{V_t}$ & \textbf{\begin{tabular}[c]{@{}c@{}}Percentage \\  of gates\end{tabular}} \\ \hline \hline
% 0             & 8.47                                                                     \\ \hline
% 1             & 1.86                                                                     \\ \hline
% 2             & 89.67                                                                    \\ \hline
% \end{tabular}
%  \caption{This table shows the number of cells for each $V_t$ in the training dataset. We number the $V_t$ choices and the $size$ choices. A $V_t$ value of 0 indicates that the cell is an $LV_t$ cell while a $V_t$ value of 2 indicates that it is an $HV_t$ cell.}\label{tab:Vt}

% %\end{table}
% }
% \hfill
% \parbox{.45\linewidth}{
% %\begin{table}[!t]
%     \centering
%     \begin{tabular}{|c|c|}
%     \hline
%         $size$ & percentage of cells \\ \hline
%         0 & 84.40\\ \hline
%         1 & 13.75\\ \hline
%         2 & 0.7\\ \hline
%         3 & 0.7\\ \hline
%         4 & 0.2\\ \hline
%         $\geq 5$ & 0.25 \\ \hline

%         \end{tabular}
%     \caption{This table shows the number of cells for each $size$ in the training dataset. A cell with a $size$ value of 0 indicates that it has the smallest size possible while a cell with a $size$ value of 9 indicates that it has the largest size possible in the standard cell library.}
%     \label{tab:size}
% }
% \end{table}

% \begin{algorithm}[ht]
% %\algsetup{linenosize=\tiny}
%  \LinesNumbered`' 
% %\linesnumbered
% \title{Gateid algorithm}
% \caption{The algorithm that initializes all cells with its respective gateid}
% \label{gateid-algo}
% \KwIn{Netlist of the given circuit C containing N gates represented as a Directed Acyclic Graph (DAG) with each gate initialized to a unique prime number\footnote{The product of prime numbers is always unique and this product can be used to identify recurring sub-circuit patterns} based on gate type. }

% \For {each gate $g$ in $C$}{
%    initialize $gateid.g$ with the prime number corresponding to the gate type of g\;
%    }
%  \For {each gate $g$ in $C$}{  
%    \For{each gate $i$ in $fanins(g)$}{
%         $gateid.g = gateid.g \times gateid.i$\;

%         }

%    \For{each gate $i$ in $fanouts(g)$}{
%        $ gateid.g = gateid.g \times gateid.i$\;

%         }
%     }
% \KwResult{gateid is assigned to each gate}
% \end{algorithm}

%Talking points: No. of datapoints, configuration of the classifier, feature selection,

%~\ref{learnalgo}. The algorithm has two stages \- lines ~\ref{alg:svmbegin} to ~\ref{alg:svmend} generate a good initial configuration for the netlist by using two hierarchical SVM classifiers one for $V_t$ and one for $size$. lines ~\ref{alg:delay} and lines ~\ref{alg:power} perform delay and power recovery to obtain  a leakage and power optimal configuration.

\begin{table}[!t]
 \begin{minipage}{0.45\textwidth}
 \caption{The 2-bit prediction-based window sizing strategy adopted by {\it MLTimer}. \textsuperscript{*} The window size is incremented by a constant factor, denoted using $\alpha$.}
 \label{tab:window-sizing-strategy}

 %\begin{center}
 \centering

 %\scalebox{0.9}{

 \begin{tabular}{|c|c|c|p{4cm}|c|}
 \hline
 State & $v_{i-1}$ &$v_i$ &Description &$r(i+1)$ \\
 \hline
 $S_{00}$ &0 &0 &Timing violation in the last two iterations& $1$ \\
 \hline
 $S_{01}$ &0 &1 &Timing violation in $(i-1)^{th}$ iteration and no timing violation in $i^{th}$ iteration& $(r(i))*2$ \\
 \hline
 $S_{10}$ &1 &0 &No timing violation in $(i-1)^{th}$ iteration and timing violation in $i^{th}$ iteration& $r(i) + \alpha$ \textsuperscript{*} \\
 \hline
 $S_{11}$ &1 &1 &No timing violation in the last two iterations& $r(i)^2$ \\
 %\scalebox{0.9}{

 \hline

 \end{tabular}%}
 %\end{center}
 \end{minipage}\hfill
%\begin{figure}[!ht]
\begin{minipage}{0.35\textwidth}
 \begin{center}
 \includegraphics[scale=0.4]{Chapter3/fig/state_machine_window_sizing}
 \captionof{figure}{Transition diagram for the 2-bit prediction scheme adopted by {\it MLTimer}}
 \label{fig:state-machine-window-sizing}
 \end{center}
\end{minipage}
\end{table}

\begin{algorithm}
%\algsetup{linenosize=\tiny}
  \scriptsize
\LinesNumbered
\title{Delay Recovery Algorithm}
\caption{Delay Recovery Algorithm }
\label{alg:delay}
\KwIn{1. Netlist of the given circuit C containing N gates represented as a Directed Acyclic Graph (DAG),2. $V_t$ and $size$ values predicted by the Learning module,3. the multi-$V_t$ standard cell library and 4. the target frequency $F$.}
    \KwOut{Netlist running at the target frequency $F$.}
 $r = r_{init}$\; 
  $state\leftarrow S_{11}$\;
 $N \leftarrow gate\ count$\; 
    Initialize all the gates in $C$ with the corresponding $V_t$ and $size$ values predicted by the SVM engine. If the learning module is not able to predict a $V_t$/$size$ for a gate initialize them to a power optimal configuration $(V_t=2/size=0)$\; 
  Run STA and compute slack for each gate\; 
    \textit{cost function } $=\frac{\delta delay \times slack}{\delta leakage \times \# paths} $\; 
    For each $g_{j}$ ($1 \le j \le N$),\\ \ \ \ \  compute the cost of decreasing the $V_t$, increasing the $size$, and both\;

 %cost of replacement \leftarrow $\frac{ $ \delta leakage \times slack$ }{$\delta delay \times paths$}$ \;
 A $\leftarrow$ list of replacements sorted in increasing order of \textit{cost function}\;  
%  \tcc{Note that all gates have slack value $\ge$ 0} 
  \While{A not empty}  {
    Take the top $r$ replacements ($A_{1}, A_{2} \ldots A_{r}$) in $A$ \; 
%  \tcc{Local validation}
     For each $A_{j}$ ($1 \le j \le r$),\\ \ \ \ \ Replace $A_{j}$ with its next high performance version (decrease $V_t$ or increase $size$) if $A_{j}$ has positive slack\; 
%  \tcc{Global validation}
      Perform a full STA on C\; 
      \If{ delay violation} {undo all the replacements done in step 12\;
    If $r \leftarrow 1$ mark $A_{j}$ as critical and delete it from A\;
      Update the state as per Figure~\ref{fig:state-machine-window-sizing}\; 
      Update the value of $r$ as per Table~\ref{tab:window-sizing-strategy}, for the new value of state\; 
    }

      \Else {
        Compute the new cost for the committed gates\;

      Update the state as per Figure~\ref{fig:state-machine-window-sizing}\; 
      Update the value of $r$ as per Table~\ref{tab:window-sizing-strategy}, for the new value of state\; 
  }
    }
\end{algorithm}

%write delay and leakage recovery module.

\subsection{Delay Recovery Module}
The performance of the learning module is highly dependent on the number and distribution of examples provided during the training phase. An SVM engine might under perform because of improperly chosen features, class imbalance in the dataset or less number of training examples. One or more of the above factors could lead to false positives and false negatives. These false positives and false negatives could lead to delay violations. We use Algorithm~\ref{alg:delay} to fix the timing violations in the circuit.
As seen in Figure~\ref{fig:algo}, Algorithm~\ref{alg:delay} fixes all the delay violation to ensure that the performance of the given circuit $C$ meets the target frequency. Algorithm~\ref{alg:delay} fits into the template of the iterative greedy algorithm described in Algorithm~\ref{alg:naive} except that multiple gates are replaced in each iteration of the algorithm (line 7 of algorithm~\ref{alg:naive} versus line 11 of algorithm~\ref{alg:delay}). The cost function in line 6 of algorithm~\ref{alg:delay} employed is the same as that in~\cite{hu:12}.

Algorithm~\ref{alg:delay} describes the functionality of the delay recovery module. The algorithm adaptively varies $r$ across each timing update. The value of $r$ is varied within a range $[r_{low}, r_{high}]$.In this algorithm, we initialize $r$ to $r_{low}$ and increment the same after each timing update depending on the $state$ of the timing update, until $r$ reaches $r_{high}$. After $r$ reaches $r_{high}$, it is not incremented further. In the experiments reported in this paper, the value of $r_{high}$ is fixed at $\frac{N}{2}$ ($N$ is the number of gates) based on the profiling done to find the effect of varying $r$ on the algorithm run-time for various benchmarks. Let $r(i)$ denote the value of $r$ in iteration $i$. The state transition diagram shown in Figure~\ref{fig:state-machine-window-sizing} in conjunction with Table~\ref{tab:window-sizing-strategy} describe how the value of $r$ is changed across iterations. The states in Figure~\ref{fig:state-machine-window-sizing} are defined in Table~\ref{tab:window-sizing-strategy}. Let $v(i)$ be set to $1$ if there is no timing violation in iteration $i$ else it is set to $0$. Thus the state machine will be at $S_{v_{i-1},v_i}$ at the end of iteration $i$. For example, if there was a timing violation in both iterations $i-1$ and $i$, the state machine will be in $S_{00}$ at the end of iteration $i$. Table~\ref{tab:window-sizing-strategy} describes the change in the value of $r$ in iteration $i+1$, $(r(i+1))$; that depends on the state in iteration $i$. For example, if the state at iteration $i$ is $S_{10}$, then the value of $r(i)$ is incremented by a small factor $\alpha$ in the next iteration $(r(i+1)=r(i)+\alpha)$.

% The state transition We describe the way $r$ varies using the state transition diagram shown in Figure~\ref{fig:state-machine-window-sizing} and the value of $r$ at the end of every timing update is given in Table~\ref{tab:window-sizing-strategy}. It can observed from this transition diagram that $state$ in timing update $i$ can be represented as $S_{v_{i-1},v_i}$, where $v_{i-1}$ and $v_{i}$ are binary digits that denote the status of $(i-1)^{th}$ and $i^{th}$ timing updates respectively. Here, a status ($v$) of $0$ denotes the occurrence of a timing violation while a $1$ denotes a successful timing update.

From our experiments, we observe that the iterative correlation was very high for the first few timing updates. This implies that maximum number of gates should get replaced during those timing updates, and hence the initial state is set to $S_{11}$, which quadratically scales the window size in successive timing updates. The value of $r_{low}$ is set to $2$. A successful timing update at the end of the first iteration would cause the state to remain at $S_{11}$ while increasing $r$ quadratically to $4$, and a timing violation would cause the state to change to $S_{10}$, causing $r$ to be incremented by a small positive constant $\alpha$. A timing violation in the second update would set the state to $S_{00}$ and the window to $1$. This explains the adaptive window sizing procedure. As shown in Figure~\ref{fig:ropt} replacing $r_{opt}$ number of gates gives the best speed-up possible. However, $r_{opt}$ varies across each timing update. Ideally replacing $r_{opt,i}$\footnote{$r_{opt,i}$ is the optimal window size for the $i^{th}$ update.} gates for each of the $i$ timing updates will result in the best possible speedup. However, the value of $r_{opt,i}$ cannot be precomputed. From our initial experiments we observed that $r_{i+1}$ is strongly related to the outcome of the previous timing updates. By taking into account the outcome of the last $k$-timing updates, the likelihood of obtaining the $r_{opt}$ for the next timing update is maximized. In our setup we use a 2-bit state based sizing scheme. 
\noindent We observed that there is no significant improvement for large values of $k$. This is because the algorithm takes a large amount of time to recover from a suboptimal window size or to get to the optimal window size for a given iteration. We define this phenomenon as inertia. Consider the following scenario. If the current window size is $r_{high}$ and there is a timing violation. The number of iterations required to identify the gate causing the timing violation is $2$. However, for a large value of $k$ this increases thereby causing the algorithm to spend significant amount of time on useless timing updates.

%\noindent We use Algorithm~\ref{alg:delay} to fix the delay violations in the circuit. We initialize the gates in netlist with $V_t$ and $size$ values predicted by the classifiers. We run an initial STA and identify the target gates using the same cost function defined in ~\cite{hu:12}.  Recovering the delay of gate $g_{i}$ will impact the other gates in the fanin/fanout cone of $g_i$. The chosen cost function computes the impact of a change in the $V_t$ or $size$ of a gate on its neighbours by computing the change in slack across all the gates in the fanin and fanout cone of $g_i$ denoted using the term $\delta delay$ in the cost function. A gate with large number of fanins/fanouts might have significantly high $\delta delay$, hence we also take into account the number of negative slack paths passing through the gate $g_i$ using the term $\#paths$. The term $\delta leakage$, which accounts for the change in leakage due to the replacement, prohibits the gate from trading off significantly large amount of power in order to improve performance.

Each execution of the \textbf{while} loop corresponds to one update interval. During each  update interval we do the following:
\begin{itemize}
\item We compute the cost of decreasing the $V_t$, increasing the $size$ and both for every gate and add them to a list \textit{A}.
\item The first $r$ choices in the decreasing order of their cost are replaced.
\item We then check for any timing violations by running a full STA. We do not use an incremental STA because running timing analysis for each gate in the window, would impose significant runtime penalty for large window sizes, ultimately offsetting the speed-up obtained by postponing the timing analysis.
\item If there is a delay violation, undo all the replacements 
\begin{itemize}
\item if $r$ is $1$, then mark the corresponding gate as critical so that it cannot participate in any further timing optimizations.
\item Update $state$ and compute new value of $r$.
\end{itemize}
\item If the timing evaluation is successful
\begin{itemize}
    \item Compute the new costs for the gates that got committed. If the gates cannot participate in further updates (gates have reached lowest $V_t$ or $size$) mark them as critical and remove them from A.
\item Update $state$ and compute the new value of $r$.
\item if value of $r$ is greater than A, then we resize $r$ to $\frac{A.size}{2}$.
\end{itemize}

\end{itemize}

\begin{algorithm}[!t]
%\algsetup{linenosize=\tiny}
  \scriptsize
 \LinesNumbered
 \title{The {\it Leakage Power recovery } algorithm}
 \caption{The Leakage Power recovery algorithm}
 \label{exponential-algo}
\KwIn{1. Netlist of the given circuit C represented as a Directed Acyclic Graph (DAG) running at target frequency $F$,2. initial window size ($r_{low}$) and upper bound on window size ($r_{high}$) and 3. a multi-$V_t$ standard cell library.}
\KwOut{The leakage optimized netlist running at target frequency $F$.} 
  $r = r_{low}$\; 
  $state\leftarrow S_{11}$\;
 $N \leftarrow gate\ count$\;
  Run STA and compute slack for each gate\;
    \textit{cost function} $=slack$\;
 A $\leftarrow$ list of gates with non-zero slacks, sorted in descending order of \textit{cost function}\; 
%  \tcc{Note that all gates have slack value $\ge$ 0} 
  \While{A not empty}  {
    Take the top $r$ gates ($g_{k_1}, g_{k_2} \ldots g_{k_r}$) in $A$ \;
%  \tcc{Local validation}
     For each $g_{k_j}$ ($1 \le j \le r$), replace the gate with its next power optimal version  (increase $V_t$ or decrease $size$) if gate $g_{k_j}$ has sufficient positive slack\;
%  \tcc{Global validation}
      Perform a full STA on C\;
      \If {delay violation} {
          Undo all the replacements done in step 9\;
          If $r\leftarrow1$ mark $A_{j}$ as critical and delete it from A\;
            Update the state as per Figure~\ref{fig:state-machine-window-sizing}\;
      Update the value of $r$ as per Table~\ref{tab:window-sizing-strategy}, for the new value of state\;

      }
      \Else{
          Compute the new cost for the committed gates\;
      Update the state as per Figure~\ref{fig:state-machine-window-sizing}\;
      Update the value of $r$ as per Table~\ref{tab:window-sizing-strategy}, for the new value of state\;
  }
    }
 \end{algorithm}

\subsection {Leakage Power Recovery Module}
The delay recovery module ensures that there are no timing violations in the netlist. An iterative algorithm described in Algorithm~\ref{exponential-algo} is employed to recover the leakage power from the netlist. We initialize the window size $r_{low}$ and $state$ to $S_{11}$.  We perform an initial timing analysis to identify the target gates and follow the steps similar to Algorithm~\ref{alg:delay} to perform multiple gate replacements in order to minimize the leakage power. The leakage recovery algorithm uses \textit{slack} as the cost function to identify gates for replacement in each iteration. In the leakage recovery step, the amount of slack indicates the conduciveness of the gate for replacement.  A gate with a high positive slack  can be replaced without having to worry about the impact on the neighbourhood gates while gates with negative slack or zero slack cannot be chosen for power optimization.  In our algorithm only the gates with positive slack are considered during each iteration.

During each iteration, the gates are sorted in the descending order of slack. The top $r$ gates are selected and replaced with their next slower version provided they have sufficient slack. We then check for timing violations by running a full STA. Though we consider only gates with positive slack, there might be timing violations because two gates in the same path could have positive slack and hence would be chosen for update. However, simultaneous updates on both the gates could result in a timing violation. In case of a delay violation we undo the replacements and update the state variable and $r$. If there is no timing violation we compute the new slack values for all the gates and update the state variable and $r$.

### 2019-05-30 Chapter3/related.tex
thesis initial draft

\section{Related Work}
%\label{sec:related}
\label{sec:related-work}
\noindent The TC-DSP problem being NP-complete~\cite{feng:09}, brute force search cannot find an optimal solution. Several heuristics have been proposed in the past to address this problem~\cite{feng:09,wu:08,fishburn:85,sundarajan:99,liu:10,hu:12, mok:12,coudert:97}. 
In~\cite{fishburn:85} it was shown that the continuous sizing problem 
with area minimization objective is convex, and a greedy sensitivity-based 
heuristic was proposed to solve the same. Similarly, in~\cite{sundarajan:99}, 
a continuous optimization is performed, following which the solutions are 
discretized. However, this type of discretization is known to produce 
suboptimal solutions due to significant round-off errors. In~\cite{feng:09}, 
a polynomial time approximation scheme was proposed, but this scheme does not 
scale well for circuits with large number of gates as the run time runs into minutes even for circuits with less than 5000 gates. Another analytical algorithm was provided for the same 
in~\cite{liu:10}, but this algorithm also takes several minutes even for 
circuits whose gate-count is less than 20,000. Nothing is mentioned in~\cite{liu:10} about the scalability of the running time of the algorithm with respect to large circuits. In~\cite{mok:12}, a survey 
of all the existing algorithms for the sizing problem is provided and is concluded 
that {\em no algorithm exists that consistently provides good results for all circuits}. The ISPD 2012~\cite{ispdcontest1} and ISPD 2013~\cite{ispdcontest2} contests provided a set of benchmark circuits that were targeted at evaluating the quality of any sizing technique. 
However, it was shown in both~\cite{hu:12} and~\cite{mok:12} that iterative 
greedy heuristics are fastest and most effective in solving the TC-DSP.

The TC-DSP is presented as an instance of Lagrangian Relaxation (LR) problem in~\cite{Hu:11}. The objective is to minimize leakage and the algorithm places a penalty for any delay violations. The timing constraints are introduced in the LR formulation.  The netlist is modeled as a directed acyclic graph and the discrete gate version characteristics are based
on timing tables provided by the gate library. A Dynamic Programming algorithm
based on critical tree extraction is proposed to solve the LR optimization problem for discrete gates. An accurate timer is used for sign-off and slack computation.

%~\cite{li:12}, ~\cite{livramento:13}, ~\cite{hu:12} and ~\cite{flach:13} use the ISPD2012 framework. 
 Empirically it is observed in this paper that some commercial synthesis tools consume less time for the design optimization time but the solution quality is far from desirable. To avoid compromise on the solution quality, there are a few heuristics like those proposed in \cite{wu:08} and \cite{hu:12}, which focus on employing parallel and concurrent techniques to reduce the run-time of the optimizer. The speed-up achieved through this parallelization is not significant though the effort involved in parallelizing the code could be significant. A common scalable solution to the TC-DSP problem is to iteratively replace gates with their different  versions and perform a static timing analysis (STA) at the end of every iteration to check for timing violations due to the gate replacements.
 As the optimization process proceeds, the algorithm experiences high rejection rates, making the performance of the STA 
engine very crucial for scalability~\cite{papa:10}. Next, we describe the existing STA techniques reported
in literature. 
%
Initial Static Timing Analysis (STA) engines always processed an entire design, which is impractically expensive for evaluating every 
replacement~\cite{papa:10}. It is to be noted that replacing the $V_t$/gate-size of a gate $g_i$, changes the arrival times of gates only in the fan-in and fan-out cones\footnote{Fan-in/Fan-out cone of a gate $g$ is defined as the sub-circuit that drives/is driven by the gate $g$.} of $g_i$, while the arrival times of other gates remain unaffected. By performing STA for the entire design, we may end up computing known values repeatedly. 
To improve the efficiency of the STA engine, several {\em incremental} STA techniques have been proposed in the past~\cite{lee:95,abato:96,sapatnekar:96,mondal:04,das:06,papa:08}. In~\cite{lee:95}, {\em incremental} STA is performed by solving 
the {\em incremental longest path problem}, with a novel algorithm which is linear in the number of edges in the {\em dominance fan-out cone}. In~\cite{abato:96}, a frontier is established by recording the leftmost and rightmost gates in the fan-in and fan-out cone of each gate that get affected by the change in relative timing values are recorded.
Based on a request, incremental timing analysis is performed on the modified design
employing the recorded frontiers of change to limit the timing analysis to 
the {\em affected} regions of the circuit alone. An input based path sensitization approach 
was used for incremental STA in~\cite{sapatnekar:96}.
On a similar note, in~\cite{coudert:97}, the incremental timer is accelerated by only updating a 
set of gates that are in the neighborhood of the gate whose timing value has been updated. 
In~\cite{mondal:04}, timing queries were modeled using temporal logic and an efficient 
algorithm was proposed to answer those queries. Similarly, in~\cite{das:06}, a more 
efficient incremental STA algorithm which exploits the circuit structure was proposed. 
In all these works, path based algorithms were proposed to 
increase the performance of incremental STA, but none of them except~\cite{abato:96} looked 
at reducing the number of times the incremental STA needs to be performed. 
Even in~\cite{abato:96}, although incremental STA is not performed in every iteration, 
nonetheless some computation is performed in every iteration relating to the signal propagation. 
As a result, the running time complexity does not decrease significantly compared to the use of a normal STA. 
For e.g., in~\cite{hu:12}, in spite of using a state-of-art incremental timer, the optimization 
took greater than 20 hours. It can be seen from the above works that the STA engines reported so far consume a significant time. The number of times the STA needs to be performed (timing updates) grows linearly with the size of the circuit. Reducing the number of times such updates are performed results in a reduction in the overall running time of the algorithm. This reduction without compromising on the solution quality is the challenge that forms one of the central themes of this paper.

%
%This paper uses the {\em lazy timing evaluation} to arrive at a fast algorithm for the TC-DVSP. 
%The {\em laziness} is to avoid performing the STA after every iteration but to perform the same 
%once in several iterations. To sum up, the main contributions of the work are as follows:
%\begin{enumerate}
%\item We observe that iterative {\em slack-based} greedy discrete $V_t$ sizing exhibits %significant 
%speed-up while retaining/improving the solution quality over iterative  {\em sensitivity-based} 
%greedy discrete  sizing~\cite{hu:12,chinnery:05}. 
%\item We show that in iterative slack-based discrete $V_t$ sizing, there is a significant correlation 
%between the ordering of gates based on slack in the current iteration and the ordering of gates that 
%are replaced in successive iterations.
%\item Exploiting this high correlation, this paper proposes a {\em lazy timing analysis} coupled with an {\em Adaptive Window sizing (AWS) scheme for decision making} to perform {\em multiple $V_t$ replacements} between successive timing updates, thereby producing solutions that are at least {\em an order of magnitude} faster and consume lesser leakage power, 
%when compared to an existing commercial multi-$V_t$ synthesis tool.
%\end{enumerate}
{\em Lazy evaluation} is a popular paradigm in improving the computational efficiency of iterative algorithms.
The line sweep algorithm used in the VLSI routing checkers is based on this technique.
In \cite{papa:10}, it was shown that lazy STA when employed for {\em timing optimization} can result in more
than 2$\times$ speed-up, when combined with transactional timing analysis.
{\em It should be noted that lazy updates may not be acceptable for all optimization problems}. 
An {\em optimistic} approach with {\em lazy timing updates},
may lead to unnoticed timing violations that might have occurred on the gates
that have been marked for timing updates. This demands backtracking that actually ends up
increasing the running time of the algorithm, defeating the whole purpose. 
Interestingly, {\em lazy updates} combined with an efficient backtracking procedure can speed 
up the iterative algorithms that solve the {\em timing optimization} problem.

%The leakage power minimization problem has been studied over the last 30 years and there has been a considerable amount of work done in this regard. The work can be primarily divided into two classes: heuristic based approach and analytical approach. 
%Since the leakage power minimization problem is NP-Hard, heuristic based approaches have focussed on  effective search space exploration. Works like %inser references here 
%have focussed on developing metrics that help in identifying the right candidate cells and works like % insert references
%have focussed on novel search space exploration heuristics. However the growing circuit complexity has necessitated the need for  robust heuristics which can both handle placement-aware, routing-aware solutions and the need for faster turn around times has necessitated the need for faster solutions. This is highlighted by the ISPD2012 contest which had weightage for runtime constraints. This has motivated researchers to develop runtime aware heuristics. %insert references 
%have adopted a multi-threaded approach to reduce the run-time overheads. 
%Initial analytical methods focussed on posing the leakage optimization problem as a continous sizing problem. However the degradation in solution qualty incurred due to converting the final solution into a discrete value led researchers to pose the leakage optimization problem as a discrete sizing problem. Recent works like %insert references here
%have focussed on modelling the leakage opitmization problem as a  lagrangian relaxation problem. %insert refeerences 
%have also used multi threading to speed up the optimization process.

%Initial Static Timing Analysis (STA) engines always processed an entire design, 
%which is impractically expensive for evaluating every $V_t$ 
%replacement~\cite{papa:10}. It is to be noted that replacing $V_t$ of a 
%gate $g_i$, changes the arrival times of gates only in the fan-in and 
%fan-out cones of $g_i$, while the arrival times of other gates remain unaffected. By performing STA for the entire design, we may end up computing known values repeatedly. 
%To improve the efficiency of the STA engine, several {\em incremental} STA techniques 
%have been proposed in the past~\cite{lee:95,abato:96,sapatnekar:96,mondal:04,das:06,papa:08}.
%In~\cite{lee:95}, {\em incremental} STA is performed by solving 
%the {\em incremental longest path problem}, with a novel algorithm which is linear in 
%the number of edges in the {\em dominance fan-out cone}. In~\cite{abato:96}, the leftmost 
%and rightmost frontiers of change in relative timing values are %recorded.
%Based on a request, incremental timing analysis is performed on the modified design
%employing the recorded frontiers of change to limit the timing analysis to 
%the {\em affected} regions of the circuit alone. An input based path sensitization approach 
%was used for incremental STA in~\cite{sapatnekar:96}.
%On a similar note, in~\cite{coudert:97}, the incremental timer is accelerated by only updating a 
%neighborhood set of gates. 
%In~\cite{mondal:04}, timing queries were modeled using temporal logic and an efficient 
%algorithm was proposed to answer those queries. Similarly, in~\cite{das:06}, a more 
%efficient incremental STA algorithm which exploits the circuit structure was proposed. 
%In all these works, path based algorithms were proposed to 
%increase the performance of incremental STA, but none of them except~\cite{abato:96} looked 
%at reducing the number of times the incremental STA needs to be performed. 
%Even in~\cite{abato:96}, although incremental STA is not performed in every iteration, 
%nonetheless some computation is performed in every iteration relating to the signal propagation. 
%As a result, the running time complexity does not decrease significantly. 
%For e.g., in~\cite{hu:12}, in spite of using a state-of-art incremental timer, the optimization 
%took $>20$ hours. It can be seen from the above works that the STA engines reported so far consume a significant time. The number of times the STA needs to be performed (timing updates) grows linearly with the size of the circuit. Reducing the number of times such updates are performed results in a reduction in the overall running time of the algorithm. This observation forms the central theme of this paper.

%~\cite{hu:12} ~\cite{mustafa:11} ~\cite{chinnery:05} ~\cite{li:93} ~\cite{dennard:74} ~\cite{borkar:99} ~\cite{baauw:03} ~\cite{hu:09} ~\cite{davoodi:08} ~\cite{boyd:08} ~\cite{flach:14} ~\cite{parhi:99} ~\cite{papa:10} ~\cite{lee:95} ~\cite{sapatnekar:96} ~\cite{papa:08} ~\cite{hu:10}
%~\cite{coudert:97} ~\cite{kahng:16} ~\cite{ketkar:00} ~\cite{Han:2014} ~\cite{Kahng:13} ~\cite{kang:13} ~\cite{chu:15} ~\cite{sharma:15} ~\cite{6513816} ~\cite{reimann:2016} ~\cite{li:2012} ~\cite{Davoodi}

%include ISPD 2012, 2013 opentimer references.

### 2019-05-30 Chapter4/background.tex
thesis initial draft

\section{Background}
\label{sec:background}
In this section we first describe the metric we use to quantify side-channel leakage. We then give an overview of the power consumption of a gate and a typical EDA flow.

{\flushleft \bf Leakage Assessment:}
We use the TVLA metric as a tool to estimate side-channel leakage in {\sf Karna}. TVLA computation involves collecting two sets of power traces; one  with a fixed input and another with random inputs~\cite{becker:2013}. The statistical distance between the distributions of these two sets provides an indication of the leakage. The TVLA metric uses the Welsh t-score to compute this distance. A large magnitude of the TVLA score indicates significant side-channel leakage compared to a small magnitude of TVLA. While the prior works perform TVLA on a manufactured design, our proposed scheme integrates the TVLA methodology during the EDA flow. This enables us to perform a "white-box analysis" of the design. A device is said to pass the TVLA test if the TVLA score is less than 4.5.

%we divide the floorplan into a $N\times N$ grid and compute the t-score for each grid. We then analyze the t-score for each grid and declare the design to be safe iff the t-scores for all the grids have an absolute value of $< 4.5$. We perform specific optimizations for the gates in the grids whose t-score is greater than 4.5.

 %However, this choice is made without taking into account the impact on the security of the design. 
%available particular configuration , at his disposal, a wide variety of configurations for the same gate. The designer chooses a particular configuration in order to meet one or more of area, performance and power requirements. The various choices for a particular gate are typically obtained by varying one of the gate parameters namely $V_t$, $V_{dd}$, load capacitance and the size of the gate. We list the impact of each parameter on the gate's power and delay consumption in Table~\ref{tab1}.

{\flushleft \bf Power Consumption of a Gate.} The  power consumption of a gate is the sum of its dynamic power $P_{dynamic}$ and static power $P_{static}$ consumption. These components are given by the following equations:
\begin{equation*}
P_{dynamic} = \alpha C_{load} V_{dd}^{2} F 
\hspace{15pt}
P_{static} =  V_{dd}\bigg( k e^{-q\frac{V_{t}}{ak_{a}T}}\bigg)\enspace. 
\end{equation*}

The dynamic power consumption of the gate is dependent on the activity factor $\alpha$, the supply voltage $V_{dd}$, the load capacitance $C_{load}$, and the operating frequency $F$. The static power consumption of the gate is dependent on the threshold voltage $V_{t}$, temperature $T$ and constants $k,q$, and $k_{a}$. The operating frequency $F$ is a parameter specified by the user in the EDA flow as a constraint, while $T$, $k,q$, and $k_{a}$ are constants. These parameters cannot be modified by the tool. On the contrary, the tool can modify $V_{dd}$, $V_{t}$, $C_{load}$, and gate size which will have an impact on the area, power, and delay of a design.

%Modifying the other parameters will have an impact on the overall power consumption of the gate and consequently its impact on the side-channel leakage. In {\sf Karna}, for each gate we select a $V_{dd}$, $V_t$ and size value such that the TVLA is within a specified threshold. We perform this optimization while ensuring that the other design constraints like power, area and delay are not violated. \\

{\flushleft \bf Electronic Design Automation (EDA) Flow.}
A typical EDA flow consists of several stages as seen in Figure~\ref{fig:vlsiflow}. Each stage has a specific objective to optimize one or more of the delay, power or area of the design. The modules at each stage rely on timing and power models of the gates to achieve their objective. %This choice can affect the  area, delay, and power of the design. 
Current EDA flows, however, do not account for the impact of these optimizations on the security of the design.

 In a typical EDA flow, the tool chooses a configuration for each gate from several choices that are made available by the foundry in the standard cell library. The choice is made such that the selected gate configurations meet the design requirements of area, power, and delay. Each gate configuration can be obtained by varying one or more of the supply voltage $V_{dd}$, threshold voltage $V_{t}$ and the gate $size$. For example, each gate in our 28nm standard cell library has 90 choices. Each choice can be represented using the tuple ($V_{dd}$,$V_{t}$,$size$). There are 3 choices for $V_{dd}$, 3 for $V_{t}$, and 10 choices for the $size$. Modifying one or more of these parameters may have an impact on the overall delay, power and area of the design.

To select a gate configuration, the EDA tool uses several metrics such as slack and ratio of change in power to change in delay~\cite{hu:12}. In our work, we use {\em slack}, which is defined as the difference in the required arrival time of a signal and the actual arrival time of the signal at the output of a gate. A positive slack implies that the gate has room for optimization while a negative slack implies that the timing constraint at the particular gate is violated.

%based on the constraints specified by the designer. This choice can affect the  area, delay, and power of the design.

%For example, countermeasures such as masking is incorporated in the stage 1, the high-level description stage, while gate level schemes on the other hand is incorporated in stage 2, the gate level synthesis level. Incorporating security at these stages might cause the design to incur delay and area overheads leading to the design not meeting the required area and timing constraints in the subsequent stages. Further, incorporating security in the early stages may get undone by subsequent stages. In this work, we therefore choose to introduce the {\sf Karna} module after the design is placed. At this stage, a realistic estimation of the interconnect delay and power density is known. Thus, in this stage, we can accurately gauge the impact of the proposed security based modifications on the area, delay, and performance of the device.

%A typical EDA flow consists of several stages as shown in Figure~\ref{fig:vlsiflow}. Each stage in the flow has a specific objective -- optimize one or more of the delay, power or area. The modules at each stage rely on timing and power models of the gates to estimate the impact of the optimizations. %An EDA flow, which is security aware,  can address this objective in multiple stages. This choice can affect the other design constraints such as area, performance, and power. For example, countermeasures such as masking is incorporated in the stage 1, the high-level description stage, while gate level schemes on the other hand is incorporated in stage 2, the gate level synthesis level. Incorporating security at these stages might cause the design to incur delay and area overheads leading to the design not meeting the required area and timing constraints in the subsequent stages.

%mention impact of V_t, size and V_dd.
%mention how designer has freedom but that again becomes disadvantageous.

%bring out delay area and security (TVLA).

%use graph. have 3 graphs

% \begin{table*} %add area numbers to reinforce size.
% \centering
% \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
% %\toprule
% %\textbf{Treatments} & \textbf{Response 1} & \textbf{Response 2}\\
% \hline
% $V_t/ size$ & $0$ & $1$ & $2$ & $3$ & $4$ & $5$ & $6$ & $7$ & $8$ & $9$ \\ \hline
% %\midrule
% $HV_t (V_t=2)$ & 1 & 2 & 3 & 4 & 6 & 8 & 16 & 32 & 64 & 128 \\ \hline
% $RV_t (V_t=1)$ & 4 & 8 & 12 & 16 & 24 & 32 & 64 & 128 & 256 & 512 \\ \hline
% $LV_t (V_t=0)$ & 16 & 32 & 48 & 64 & 96 & 128 & 256 & 512 & 1024 & 2048 \\ \hline
% %\bottomrule

% \end{tabular}
% \caption{Table showing the variation of leakage power with $V_t$ and $size$ for an inverter.}
% \label{tab1}
% \end{table*}

### 2019-05-30 Chapter4/introduction.tex
thesis initial draft

\section{Introduction}
% \begin{framed}

% * Introduce EDA based solution from advantages point of view, highlight no overheads, design freedom ( select only gates that have no impact on area,power and delay). re-pitch paragraph 3 .

% * Show none of current EDA flows consider security.

% * Change references, use standard ones and include PC based references.

% * Include figure for indicating hotspots.

% * Move marked paragraph to overview section

% \end{framed}
% \begin{framed}
% 1. Introduction: Add a contributions section.\\
% 2. Background and Literature Survey: Let the literature review be cursory. Elaborate treatment must be written in separate section. Introduce Security -- TVLA, CPA, DPA, Differential and Correlational power analysis; Leakage power optimization -- Vt sizing, gate sizing, Vdd scaling, \\
% 3. Add a Motivation Section -- Highlight the results of the following experiments: (1) Effect of each design optimization on the security of the gate; (2) It is possible to measure this impact at the design stage itself.
% 4. High Level Overview. -- Introduce the high-level components of your solution using a flow chart. \\
% 5. Proposed Solution -- Elaborate on the components mentioned in the High-Level overview.\\
% 6. Theoretical analysis -- can you come up with optimal size of grids. See if effect of design choices on security can be modeled theoretically.\\
% 7. Implementation. -- making the scripts open source. \\
% 8. Experiments -- TBD
% \end{framed}

% We live in a connected world today. This has largely been made possible due to the advent of an era of connected systems that seamlessly interact with each other thereby reducing the load on us. This network, largely referred to as Internet of Things, makes use of small, low cost devices or embedded systems. In the last five years over 5 billion devices have been deployed.

% The ubiquity of IoT means that, of late these devices are entrusted with the responsibility of i) storing sensitive data such as personal information, financial information or medical history in order to improve the quality of our life or ii) using sensitive data in order perform a specific task such as heart rate monitors, password devices etc. At this stage it is important to ask the question "Can these devices be trusted?".

% Figure~\ref{fig:stack} shows the various levels of the system stack. These parts seamlessly interact in order for an application to run, however a violation or misinterpretation of the specification at any level might provide a potential entry point through which the attacker can access sensitive data. It has been shown that time and again these devices have been exploited either through vulnerabilities at the software level or at the hardware level. This has led researchers to focus on developing mechanisms that try and prevent such vulnerabilities from being exploited or identifying novel vulnerabilities.

% It has been shown time and again that these devices can be exploited. The reason for these attacks can be at any level of  by using vulnerabilities existing at various levels of the system stack, ranging from end-user applications to the underlying hardware on which these applications run. Side-channel attack is one such attack that exploits the vulnerability in the hardware of these embedded devices. %{\color{red}Not all hardware attacks are side-channel based, no? Response: I meant all side-channel attacks are hardware attacks..the reverse may or not be true.}

Electronic devices today need to simultaneously meet  stringent requirements of area, power, performance, and security. While all commercially available Electronic Design Automation (EDA) tools provide several optimizations to meet the former three design requirements, most do not have any provisions to address the security requirements of a device. One important security requirement, especially for embedded devices, is to limit the side-channel leakage through the device's power consumption. These leakages, if present, provide clues about the internal computation being performed in the device and  have been used to break crypto-algorithms~\cite{kocher:99} and to reverse engineer software~\cite{park:2018}.

 Most designs address side-channel leakage requirements of a device at the algorithm level by randomizing computations, which  in turn randomizes its side-channel leakage~\cite{akkar:2001}. Other schemes work at the system level by injecting noise in the power supply, which reduces the signal-to-noise ratio in the side-channel leakage~\cite{Wang:2013,tokunaga:2009,singh:2015,mathew:2018}. Both these schemes require specialized circuitry which can drastically affect the area, power, and performance of the design. For example, the  popular algorithmic masking scheme ~\cite{canright}, results in performance degradation of over $3\times$.

%power attacks attempt to either eliminate leakage or randomize it. Most common randomization procedures rely on algorithmic techniques to mask the leakage~\cite{akkar:2001}, while  elimination countermeasures employ specialized gates or transistors to nullify the leakage~\cite{Tiri:2004}. Both these types of countermeasures incur significant overheads in performance, area and power. For example, a typical elimination countermeasure increases chip delay  by $42\%$ and the area overheads by $3.5\times$~\cite{Tiri:2004}. These overheads are not always acceptable for embedded systems, where area and power are highly constrained.

\begin{figure}[!t]
 \centering
  \includegraphics[scale=0.33]{Chapter4/karna.pdf}
  \caption{Figure showing the integration of {\sf Karna} into a standard EDA flow. The {\sf Karna} module inserted in the EDA flow is used to achieve side-channel security while still honoring the design's requirements in area, power, and performance.}
  \label{fig:vlsiflow}
  \vspace{-15pt}
\end{figure}

In this paper, we propose to address the side-channel security requirements of a design through the EDA flow, while still meeting other design requirements of area, power, and performance. We introduce a module called \textsf{Karna} in the EDA flow, that takes the user-specified security level as input and optimizes the parameters of the gates in the placed netlist until the desired side-channel security is achieved (Figure~\ref{fig:vlsiflow}). No specialized circuits to counter side-channel attacks are introduced during the process. The design of \textsf{Karna} is based on two critical observations. First, there are some regions in the design which contribute much more significantly to the side-channel leakage than other regions. It is sufficient to focus on these vulnerable regions in order to reduce side-channel leakage. Second, the gate-level parameters such as supply voltage, threshold voltage, and the gate size can influence the amount of side-channel leakage. 
Carefully selecting these gate-level parameters can therefore reduce side-channel leakage of the gate. 
At a high level, {\sf Karna} first identifies vulnerable regions in the design and then reconfigures the gate parameters present in these regions such that the overall side-channel leakage of the design is reduced. 
%{\sf Karna} is designed to not just achieve the security objectives of the design but also  achieve the other design objective such as area, power and performance.

 In 2005, Tiri et al.~\cite{Verbauwhede:2005} also proposed changes to the EDA flow to prevent side-channel leakage. 
However, their scheme requires specialized gate libraries, that are not always supported by the foundry, and can considerably affect other device parameters. For example, the area of the side-channel protected AES design in~\cite{Verbauwhede:2005} increases by $3.4\times$, while the energy requirement increase by $5.9\times$. {\sf Karna}, on the other hand uses gates available in the standard cell library, and configures parameters like supply voltage, threshold voltage, and size of the vulnerable gates in order to reduce the side-channel leakage in the design phase thereby minimizing the overheads. In our work we demonstrate, using three cipher, that the area and performance and power consumption of the  designs passed through {\sf Karna} is not affected, while the side-channel leakage reduces.
The contributions of this paper are as follows.
\begin{itemize}[leftmargin=1pc]
\item We incorporate {\sf Karna} into the Synopsys design flow {M-2016 12-SP5-4} in order to pinpoint the regions in a placed netlist that contribute significantly to the side-channel leakage. 
\item We incorporate a gate-level power-optimization algorithm, which considers the side-channel security objectives of the design along with the standard design constraints such as area, power and delay.
\item {\sf Karna} provides a tunable parameter by which side-channel security can be traded off with design effort.
\item We test the efficacy of {\sf Karna} on three block cipher implementations: AES, PRESENT, and Simon. Each implementation is synthesized for a 28nm technology node. We demonstrate each design's side-channel resistance using the Test Vector Leakage Assessment (TVLA) metric~\cite{becker:2013} and show that the TVLA scores are less than 4.5 even after 100,000 measurements, while the original design requirements of power, area, and performance are unaffected.
 \end{itemize}

\noindent The outline of the paper is as follows: we introduce the necessary terminology in Section~\ref{sec:background}, motivate the need for {\sf Karna} in Section~\ref{sec:motivation} and describe it in Section~\ref{sec:proposed}. The experimental setup and results are presented in Section~\ref{sec:experiment}. The related work is discussed in Section~\ref{sec:related} and Section~\ref{sec:conclusion} concludes the paper by describing the future directions.

% \todo[inline]{can be moved to discussion section}
% Introducing security optimizations at the earlier stage of the design could cause the subsequent stages in the EDA flow to optimize or remove the changes and thereby render them useless~\cite{danger:2017}. We take into account these two constraints and integrate {\sf Karna} at the post-placement stage in the EDA flow where the delay, power and area of the design can be accurately estimated and also ensuring that the security changes are carried over into the manufactured device.

% Compared to contemporary  countermeasures~\cite{yang:2005,Singh:2017,Wang:2013,Yu:2015}, which ensure security of a manufactured device, our EDA based approach would enable fine-grained control by inserting countermeasures at the design stage itself. Further, unlike other countermeasures, which either require additional operations or new circuitry to be added, our EDA based approach would not have any such overheads. Our solution leverages the fact that EDA tools work at the gate level, which provides several tunable options like the gate's threshold voltage, size, supply voltage and load capacitance thereby enabling the design to meet a wider range of security objectives.

%The motivation for using EDA tools for countering power analysis attacks is due to the observation that not all areas of the design contribute to the side-channel leakage. Thus, there is scope for EDA tools to optimize vulnerable regions for security. %should talk about observation
%As an example, consider Figure~\ref{fig:aes} which shows that not all areas of an AES design contribute equally to the side-channel leakage.

%The methodology of using EDA tools to achieve side-channel security has been addressed in~\cite{Tiri:2005} where the authors introduce specialized libraries to mitigate side-channels. While this scheme efficiently eliminates side-channel leakage from the device it incurs a huge area overhead of 4$\times$~\cite{}. Our proposed scheme, on the other hand, uses the standard cell library and therefore does not incur any overheads. We achieve security by efficiently configuring the available gates.

% . The amount of effort required to characterize the library for security is very high. The points are
% \begin{itemize}
% \item Each gate is characterized for multiple corners and multiple modes so a secure library should be available for each corner and mode
% \item Number of gates increases with each node ( 330 in 32nm to 660 in 28nm).
% \item Area and delay overheads
% \item Library characterization places reliance on the foundry, no way to verify if the gate actually secures the design.
% \end{itemize}
% significant advantages over existing countermeasure techniques.

%In this paper, we propose {\sf Karna}, a security aware module that reduces the side-channel leakage of a design. A user enables the module and specifies the desired level of security using a \texttt{security\_level} option. A high security level will cause the module to aggressively optimize the design for security. Thus a higher security level would imply a higher resistance to power analysis attacks.

%\textbf{Marked} typical EDA flow consists of several stages as shown in Figure~\ref{fig:vlsiflow}. Each stage in the flow has a specific objective to optimize one or more of the delay, power or area. The modules at each stage rely on timing and power models of the gates to achieve their objective. An EDA flow, which is security aware,  can address this objective in multiple stages. This choice can affect the other design constraints such as area, performance, and power. For example, countermeasures such as masking is incorporated in the stage 1, the high-level description stage, while gate level schemes on the other hand is incorporated in stage 2, the gate level synthesis level. Incorporating security at these stages might cause the design to incur delay and area overheads leading to the design not meeting the required area and timing constraints in the subsequent stages. Further, incorporating security in the early stages may get undone by subsequent stages. In this work, we therefore choose to introduce the {\sf Karna} module after the design is placed. At this stage, a realistic estimation of the interconnect delay and power density is known. Thus, in this stage, we can accurately gauge the impact of the proposed security based modifications on the area, delay, and performance of the device.

%

%This security aware EDA flow is validated using an AES-128 netlist synthesized at 28nm technology. We verify the impact of our proposed flow on the area, power and delay constraints using the Synopsys Design Compiler.

### 2019-05-30 Chapter4/proposed.tex
thesis initial draft

\begin{figure}[t]
  \includegraphics[scale=0.28]{Chapter4/karnamodule}
  \caption{Given a placed netlist, {\sf Karna} tries various configurations for gates present in the standard cell library until the required security $\tau$ is obtained.}
  \label{fig:proposed}
%  \vspace{-15pt}
\end{figure}

\section{{\sf Karna}: AN EDA Module to Reduce Side-Channel Leakage}
\label{sec:proposed}
The {\sf Karna} module (shown in Figure~\ref{fig:proposed}) is executed after the placement stage and before the routing stage in the EDA flow. {\sf Karna} takes as input the placed gate-level netlist represented as a directed acyclic graph $\mathbb C$, where the vertices are the gates and the edges represent interconnects. The various timing, power and area related information, obtained from the standard cell library, is then annotated to each node. Other inputs include $\mathbb P_{g}$, the set of all available choices for every gate type in the standard cell library, the target delay for the design D, and the user-specified security level specified as a desired TVLA score $\tau$.

{\sf Karna} works in three steps. It first checks if the design meets the desired level of security $\tau$. If $\tau$ is not met, then {\sf Karna} divides the design into an $N \times N$ grid in order to identify the vulnerable regions in the grid. The algorithm then reconfigures the gates in these vulnerable regions until the desired level of security is achieved. We now discuss the implementation of the {\sf Karna} module in further detail. A detailed description is also specified in  Algorithm~\ref{alg:naive}.

{\flushleft \bf Estimating the side-channel security from the netlist.}
{\sf Karna} first estimates if the design meets the user-specified security level by performing the Test Vector Leakage Assessment~\cite{becker:2013} on the gate-level netlist (Line 1 in Algorithm~\ref{alg:naive}). For this, we select the input vectors as per the setup described in~\cite{becker:2013} and perform gate level simulation. The resultant switching information is recorded in a value change dump (VCD) file, that, along with the netlist, is given as an input to the power analysis tool available in the EDA flow. The tool  records the dynamic power traces for each gate in the netlist over a period of time. These traces can be used to compute the TVLA of the entire netlist as well as for specific regions in the netlist. If the TVLA of the design is less than $\tau$, the design passes the check and the algorithm exits successfully, otherwise {\sf Karna} proceeds to identify the vulnerable regions in the design.

{\flushleft \bf Identifying vulnerable regions.}
 {\sf Karna} uses Observation 2 (in Section~\ref{sec:motivation}) that, not all regions of the netlist contribute equally to the side-channel leakage. Hence, in order to reduce  side-channel leakage of a given design, it is sufficient for {\sf Karna}  to identify and optimize vulnerable regions in the netlist. Lines 2 to 12 in Algorithm~\ref{alg:naive} identify the vulnerable regions in the netlist. In order to do this, {\sf Karna} divides the netlist into an $N\times N$ grid and uses the dynamic power traces obtained in the previous step to compute the TVLA for each region $R$ in the grid. If the TVLA score for the region is greater than $\tau$, {\sf Karna} identifies gates that can be optimized by iterating through each gate in the selected region and adding them to a list $\mathbb W$. 
 A gate can be optimized if it meets the following conditions: {\em (i)} it can be replaced with its next low-power configuration {\em i.e.} if it has sufficient positive slack and, {\em (ii)} the gate is not critical. We define a gate to be critical if it cannot undergo any more reconfigurations. If there are no gates available, $\mathbb W = \emptyset$ (Line 13 in Algorithm~\ref{alg:naive}), and the algorithm reports failure and exits, otherwise, {\sf Karna} moves to the next step to reconfigure the vulnerable gates.

% \begin{framed}
% 1. Start with the flowchart and explain what each step is \\
% 	Explain the TVLA calculation step and how grid level tvla ties to the overall tvla score.\\
%     Explain that the grid can be customized. Explain why you divide into the grid \\
% 2. Explain the leakage optimization algorithm
% 3. Explain the optimization for placement (Need and algorithm)

% \end{framed}

\begin{algorithm}[!t]
%\algsetup{linenosize=\tiny}
  \scriptsize
  %\small
 \LinesNumbered
 \title{The {\sf Karna} algorithm}
 \caption{The {\sf Karna} algorithm}
 \label{alg:naive}
 \KwIn{The design $\mathbb C$ represented as a Directed Acyclic Graph, $\mathbb W$: the set of gates to be reconfigured,
 $\mathbb P_{g}$: the list of all possible configurations for gate g in increasing order of power, D: the delay constraint for the design and $\tau$: the user-specified security level.}

%\KwIn{Netlist of the given design C represented as a Directed Acyclic Graph (DAG), initial window size ($r_{init}$), upper bound on window size ($ry_{high}$), set of $V_t$,$V_{dd}$ and size for every gate sorted in increasing order of power, an array A containing the set of gates sorted by the TVLA score. }
\KwOut{Modified $\mathbb C$ so that the overall TVLA score is less than $\tau$.}

\While{$TVLA(\mathbb C) > \tau$}{
  \tcc{Identifying vulnerable regions}

$\mathbb W \leftarrow \emptyset $ \\
Divide the netlist $\mathbb C$ into $N\times N$ regions \\
%$\mathbb R_{regions} \leftarrow$ set of all regions \;
\For{each region $R$ in the  $N \times N$ grid}{
\If{$TVLA(R) > \tau$}{
\For{each gate $g$ in $R$}{
\If{$slack(g) > 0 $ and $g$ is not critical}{
$\mathbb W = \mathbb W \cup \{g\}$
}
}
}
}
\tcc{Reconfiguring vulnerable gates.}

\If{$\mathbb{W} \neq \emptyset$}{
Sort gates in $\mathbb{W}$ based on TVLA scores\\
\For{ each gate $g$ in $\mathbb W$} {
Let $\mathbb P_{g}[j]$ denote the current configuration of gate $g$\\
Let $\mathbb P_{g}[j-1]$ denote the next low power configuration of $g$\\

\If{$j==0$}{Mark $g$ as critical\\ \Continue}

\If{ $slack(P_{g}[j]) \geq delay(\mathbb P_{g}[j-1])-delay(\mathbb P_{g}[j])$  } {
Reconfigure g from $\mathbb P_{g}[j]$ to $\mathbb P_{g}[j-1]$ }
\Else { 
    Mark $g$ as critical\\
    \Continue }
Perform STA on $\mathbb C$ \\
\If{ $delay(\mathbb{C}) > D$}
{undo the reconfiguration done in Line 23\\
Mark $g$ as critical\\
\Continue
}
}
%Detect and fix slew and capacitance violations\;

}
\Else{
Report Failure and exit\;
}
}
%\If{$TVLA(\mathbb C) < \tau$}{
Report Success and exit\\
%Report Failure and quit\;
%}
% \If{No area violations}{
% Report Success and exit\;
 %
%
%
%
%

%%   $r = r_{init}$\; 
%   $state\leftarrow S_{11}$\;
%  $N \leftarrow gate\ count$\;
%   Run STA and compute slack for each gate\;
% % $sensitivity = $\nicefrac{ $\delta leakage \times slack $ }{$\delta delay \times paths$}$ $\;
%  A $\leftarrow$ list of gates whose TVLA score is greater \texttt{-security\_level} and have positive slack, sorted in descending order of sensitivity\; 
% %  \tcc{Note that all gates have slack value $\ge$ 0} 
%   \While{$A.size \ne 0$}  {
%     Take the top $r$ gates ($g_{k_1}, g_{k_2} \ldots g_{k_r}$) in $A$ \;
% %  \tcc{Local validation}
%      For each $g_{k_j}$ ($1 \le j \le r$), check if the increase in delay due to downsizing or upscaling of with its next $V_{dd}$, $V_t$ or $size$
%      version higher to its current version is lesser than its slack. If it is so, replace \;
% %  \tcc{Global validation}
%       Perform a full STA on C \;
%       If delay violation, undo all the reconfigurations done in step 8 \;
%       If $r=1$ mark gate $g$ as critical\;
%       Update the state as per Figure~\ref{fig:state-machine-window-sizing} \;
%       Update the value of $r$ as per Table~\ref{tab:window-sizing-strategy}, for the new value of state \;
%       Mark all the $r$ gates as replaced and remove from A\;
  %  }
 \end{algorithm}
% \begin{table*}[!ht]
%  \begin{minipage}{0.45\textwidth}
%  %\begin{center}
%  \centering

 %\scalebox{0.9}{

%  \begin{tabular}{|c|c|c|p{4cm}|c|}
%  \hline
%  State & $v_{i-1}$ &$v_i$ &Description &$r(i+1)\textsuperscript{*}$ \\
%  \hline
%  $S_{00}$ &0 &0 &Timing violation in the last two iterations& $1$ \\
%  \hline
%  $S_{01}$ &0 &1 &Timing violation in $(i-1)^{th}$ iteration and no timing violation in $i^{th}$ iteration& $(r(i))*2$ \\
%  \hline
%  $S_{10}$ &1 &0 &No timing violation in $(i-1)^{th}$ iteration and timing violation in $i^{th}$ iteration& $r(i) + \alpha$ \\
%  \hline
%  $S_{11}$ &1 &1 &No timing violation in the last two iterations& $r(i)^2$ \\
%  %\scalebox{0.9}{

%  \hline

%  \end{tabular}%}
%  \caption{The 2-bit prediction-based window sizing strategy adopted by {\it HALTimer}}
%  \label{tab:window-sizing-strategy}
%  %\end{center}
%  \end{minipage}\hfill
% %\begin{figure}[!ht]
% \begin{minipage}{0.35\textwidth}
%  \begin{center}
%  \includegraphics[scale=0.4]{fig/state_machine_window_sizing}
%  \captionof{figure}{Transition diagram for the 2-bit prediction scheme adopted by {\it HALTimer}}
%  \label{fig:state-machine-window-sizing}
%  \end{center}
% \end{minipage}
% \end{table*}

%{\sf Karna} works in three steps. First, it checks if the design meets the security requirement. If no, then it identifies the vulnerable regions and reconfigures the gate configurations in these regions. This process continues until the desired level of security is achieved. {\sf Karna} fails when either all gate configurations have been tried out or there is no more room for optimization. In this section we discuss the details of this process.

%\todo[inline]{fig 4. is it "Mark placement as safe" or "Mark netlist as safe"}

%takes as inputs the gate level representation of the design (gate-level netlist), the user specified security level, the standard cell library files, and $N_{grids}$. The parameter $N_{grids}$ specifies the number of grids the netlist must be divided into.  We now describe each steps in detail.
% \begin{figure}[!ht]
%  \centering
%   \includegraphics[scale=0.5]{fig/flow2.pdf}
%   \caption{The proposed flow. }
%   \label{fig:sub4}
% \end{figure}

%{\flushleft \bf Estimating the Side-Channel Security from the Netlist.} 
%For several input test vectors, {\sf Karna} performs a gate level simulation. The resulting switching information, stored in a value change dump (VCD) file, along with the gate-level netlist is given as an input to a power analysis tool, which records the dynamic power traces of each gate in the netlist over a period of time. These traces are then used to compute the TVLA~\cite{becker:2013} for the netlist. 
%If the TVLA score is less than $\tau$ then {\sf Karna} marks the netlist as safe and successfully exits. Otherwise, the next step is invoked which identifies the vulnerable regions in the design,

%we divide the netlist into grid and use the power trace information to compute the TVLA score for each grid.
%Side-channel leakage of the design can be measured using a metric such as Test Vector Leakage Assessment (TVLA~\cite{becker:2013}). The required security level translates into the permitted TVLA score. If the TVLA score of the design

%If the leakage from a particular grid is not within the limits specified by the user, the gates belonging to that grid are then reconfigured so as to reduce side-channel leakage. Subsequently, each gate in the vulnerable grid is reconfigured by optimizing one or more of the gate parameters such as supply voltage ($V_{dd}$), threshold voltage ($V_{th}$), load capacitance ($C_{load}$), and gate size. Modifying one or more of these gate-level parameters would impact the other design constraints. Therefore, we also verify that the area, power, and delay constraints are met. These operations are iteratively performed until the TVLA of every vulnerable grid in the design is within acceptable limits.

%The {\sf Karna} module takes as inputs the synthesized netlist which is a gate-level representation of the original design realized as per the design requirements realized at the synthesis step. In order to accurately esitmate the impact on the area constraint, the floorplan information, containting the location of each gate is passed via the def file. The module also takes as inputs the standard cell library which contains the power and delay information for each gate. The {\sf Karna} module lets the user specify the desired by the user by using the \texttt{-security\_level} option. The option specifies the TVLA score that the design is expected to meet. A lower TVLA score implies that the design is expected to meet strict security requirements while a higher score relaxes the security constraint for the design.

%As mentioned in the previous section, the occurrence of side channel leakage is due to the presence of gates in the chip that perform differently when compared to that of a random input. The first step of the framework is to identify these vulnerable gates. The framework takes as inputs, the synthesized and placed verilog netlist, the floor-plan information and the library file.

%We first check the post-placed netlist for the presence of side-channel leakage using the TVLA metric described in the Section~\ref{sec:background}.  If the netlist has an acceptable TVLA score, we stop the evaluation else if the netlist has the required TVLA score as specified by the \texttt{security\_level} option. If the design passes the module terminates and we proceed to the next step of the EDA flow. If a design fails to meet the desired level of security we then pass it to the next stage where the {\sf Karna } module identifies the vulnerable gates.

%\item 
% {\flushleft \bf Identifying vulnerable regions in the netlist.} 
%  This step uses the floorplan to divide the netlist into an $N\times N$ grid. {\sf Karna} then computes the TVLA score for each region in the grid using the same power traces estimated in the previous step. This is possible because \todo{fill up} If the TVLA score for a region exceeds the specified security level $\tau$ then that region is marked as unsafe. {\sf Karna} extracts all the gates in these unsafe regions that have a positive slack. The positive slack indicates that the gates can be reconfigured without affecting the delays of the design.  {\sf Karna} sorts these gates based on their TVLA and adds them to a list $\mathbb W$. It then reconfigures gates in the list {$W$}. This reconfiguration is discussed in the  next part of this section.

{\flushleft \bf Reconfiguring gates in unsafe regions.}
% \begin{itemize}
%     \item How we reconfigure gates such that power, delay, and area are not influenced. 
% \end{itemize}
We leverage Observation 3 (Section~\ref{sec:motivation}) that changing gate parameters has an impact on the overall side-channel leakage. {\sf Karna} optimizes gate parameters such that the overall security of the design improves while the design requirements like area, power, and delay remain unaffected. This reconfiguration is done in Lines 13 to 36 in Algorithm~\ref{alg:naive} by using a list $\mathbb P_{g}$ which contains all the possible configurations for gate $g$, sorted in the increasing order of power.
For each gate in $\mathbb W$, {\sf Karna} attempts to reconfigure it from its current configuration ($\mathbb P_g[j]$) to its next low power equivalent ($\mathbb P_g[j-1]$). However, doing so might compromise the design's delay constraint $D$. Hence, {\sf Karna} performs two validations: {\em (i)} a local validation, by checking if the reconfiguration does not violate the slack of the gate (Line 22) and {\em (ii)} a global validation by performing Static Timing Analysis (STA) for the entire design and checking if the arrival times at the outputs of the design do not violate the overall target delay  of the design $D$ (Line 30). The STA routine also checks for slew and capacitance violations and fixes them. If any of these constraints are violated, {\sf Karna} marks the gate as critical. A gate that is marked as critical is barred from taking part in any subsequent reconfiguration in the algorithm. 
The algorithm continues until the TVLA score drops below  $\tau$. This is a success and the result is a netlist $\mathbb C$, with gates suitably configured to meet the side-channel requirements of the design. The algorithm terminates with a failure if there is no room left for optimization.

{\flushleft \bf An example with Simon.} 
A bit-serial implementation of the Simon block cipher\footnote{$https://opencores.org/projects/simon\_core$} requires 622 gates using a standard cell 28nm library. We identify the best possible delay of the design at 1.12ns and set it as the target delay $D$   and the desired security level $\tau$ is 4.5. We use 8000 inputs to perform TVLA analysis for the netlist $\mathbb C$, which we represent as a directed acyclic graph. In the first iteration of {\sf Karna}, the TVLA of the design is at 20.799 (Table~\ref{tab:simon}). 130 gates are identified as vulnerable as they belong to regions that have high TVLA ($< 4.5$). These gates are added to $\mathbb W$ as per Lines 4 to 12 in Algortihm~\ref{alg:naive}. The algorithm then attempts to reconfigure these gates as per the steps described in Lines 14 to 36. For the 28nm library used, each gate has 90 possible configurations. {\sf Karna} chooses suitable gates and then checks if the design meets $\tau$ by performing a second TVLA analysis. It can be seen that, after the first iteration, the TVLA of the design decreases to 10.83. This is still greater than $\tau$, which prompts  another iteration. The second iteration finds 102 vulnerable gates, which are  added to $\mathbb W$. Upon reconfiguring the gates {\sf Karna} once again, the TVLA score reduces to 4.48 which is less than $\tau$. The algorithm then exits successfully.

\begin{table}[t!]
\scriptsize
\caption{Table showing the variation of TVLA, $\mathbb C$, $\mathbb W$, Delay and Power for the Simon cipher implementation in each iteration of Algorithm~\ref{alg:naive}. }
\label{tab:simon}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{}                                            & \textbf{\begin{tabular}[c]{@{}c@{}}$1^{st}$\\ Iteration\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}$2^{nd}$\\ Iteration\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}$3^{rd}$\\ Iteration\end{tabular}} \\ \hline
\begin{tabular}[c]{@{}c@{}}Delay\\ (ns)\end{tabular} & 1.12                                                                     & 1.12                                                             & 1.12                                                             \\ \hline
Power (uW)                                           & 3.70                                                                     & 2.61                                                             & 0.16                                                             \\ \hline
TVLA                                                 & 20.799                                                                   & 10.83                                                            & 4.48                                                             \\ \hline
$\mathbb C$ & \multicolumn{3}{|c|}{622}  \\ \hline
$\tau$ & 4.5 & 4.5 & 4.5 \\ 
\hline
$\mathbb W$ &       130 & 102 & 0 \\ \hline

\end{tabular}
\vspace{-10pt}
\end{table}

{\flushleft \bf Impact of {\sf Karna} on the other design requirements.}
{\sf Karna}, by design, does not violate the power and delay constraints. While the delay constraints are verified at multiple instances in the Algorithm~\ref{alg:naive} (Line 22 and Line 30), the power constraint is inherently met. This is because, {\sf Karna} attempts to replace each gate with its low power equivalents. Thus, the overall power consumption of the design will not increase.

While {\sf Karna} increases the area utilization of the device, it is unlikely to increase the  device size. The reason being, {\sf Karna} never adds any extra gates to the design but only reconfigures a targeted subset of the gates in the entire design. 
Not all the reconfigurations of these gates have an impact on the size. Further, the overall area would only increase if the gates lying at the periphery undergo an increase in size. There is low likelihood of this happening.

{\flushleft \bf Analysis of {\sf Karna}. }
We evaluate {\sf Karna} with respect to success and runtime.

{\flushleft \em Success Analysis.}
The success of {\sf Karna} depends on the value of $\tau$, the target delay of the design $D$, and the number of configurations available for each gate $|\mathbb P_g|$. A high value of $D$ implies that the slack at each gate will be high, thus, fewer gates will be marked critical. Consequently the number of gates taking part in the optimization process increases. Similarly, larger number of configurations available for a gate, will increase the chances that {\sf Karna} will find a gate which can achieve the desired security. A lower value of $\tau$ on the other hand, increases the effort that {\sf Karna} has to put in to achieve  security requirements. This may lead to an infeasible solution.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.35]{Chapter4/fig/tvla.pdf}
\caption{Figure showing the number of failing regions with respect to $\tau$. It can be seen that it varies inversely with $\tau$.}
\label{fig:runtime}
%\vspace{-10pt}
\end{figure}

{\flushleft \em Runtime Analysis.} Each iteration of the {\em while} loop requires one trace collection step  to compute the TVLA in Line 1 and Line 5 of the algorithm. This trace collection takes up major portion of the run time. Besides this, the run time for the rest of {\sf Karna} is considerably small and is influenced mainly by the size of $\mathbb W$, the number of regions, and the security parameter $\tau$. 
A large value of the target delay $D$ implies that a large number of gates get added to $\mathbb W$ in Line 7 of Algorithm~\ref{alg:naive}. Similarly, a small value of $\tau$ indicates more number of regions failing (as seen in Figure~\ref{fig:runtime}), which in turn increases the size of $\mathbb W$. 
A  large value of the grid size will increase the run time as the number of regions that need to be checked in Line 4-5 of Algorithm~\ref{alg:naive} increases.

Other factors that influence the run time are the number of local and global validations performed in Algorithm~\ref{alg:naive}. For each global validation, an STA call is made in Line 29 of Algorithm~\ref{alg:naive}. A full blown STA would have a run time complexity of $\mathcal{O} ( G^{2})$ where $G$ is the total number of gates in the design. In order to reduce the rum time, incremental Static Timing Analysis models such as the one used in~\cite{hu:12} or adaptive lazy timing analysis techniques like~\cite{MLTimer} can be employed.

%\vspace{-3pt}
%The size of $\mathbb W$ also determines the termination

%\todo{Factors influencing solution quality, runtime and factors influencing termination}
%which would cause only a minimal increase in the area. From our experiments, we observed that while the overall area remained constant, the area utilization increased.

%However, reconfiguring each gate with its low power equivalent will increase the delay of that particular gate. {\sf Karna} ensures that the reconfiguration doesn't violate the delay constraint by first checking if the gate has sufficient positive slack to undergo the reconfiguration (Line 22) and also perform Static Timing Analaysis on the design to ensure that the arrival time and required time constraints at all end-points are met (Line 30). It should be noted that though this timing analysis is a costly procedure, it ensures that the delay constraints are not violated.

%The next configuration for each gate is chosen from the list P which consists of all the possible configurations sorted in increasing order. The algorithm traverses this list from right to left iteratively 
% We make use of Observation 3  (Section~\ref{sec:motivation}), i.e.,
% tuning gate parameters such as $V_{dd}$, $V_t$, and size can influence the side-channel leakage from the gate.
% In this step, we focus on optimizing the gate parameters such that the overall security of the design improves while the design parameters like area, power and delay remain unaffected.
% We use the Algorithm~\ref{alg:naive} for optimizing these gate parameters. The algorithm takes as input the synthesized netlist, the target frequency $F$ and, a standard cell library containing multiple cells with different $V_{dd}$, different threshold voltages $V_t$ and sizes for every gate. The netlist is represented as a Directed Acyclic Graph where the gates are represented by the nodes in the graph and the edges represent interconnects. The set of gates belonging to the vulnerable grids are stored in an array A.

% The algorithm works as follows, the gates are sorted in descending order based on their TVLA scores. The gate with the highest score i.e, the gates that are the most vulnerable in the design are the beginning of the list and the gates that are least vulnerable are the end. The algorithm then iteratively tries to optimize the $V_{dd}$, $V_{t}$ and size of each gate. The algorithm then checks for delay violations and commits the change if the proposed optimization doesn't violate the available delay budget of the gate. We then run a timing analysis to check if the proposed change causes any timing violations and undo the change if there are any such violations.

% It should be noted that this method is expensive in terms of runtime as the timing analysis procedure needs to be run for each and every gate in the array A. In order to speedup the optimization process we use the procedure reported in~\cite{MLtimer}. We define the set of gates that can be replaced in each iteration as the gate\_reconfiguration\_window $r$. Figure~\ref{fig:state-machine-window-sizing} and the value of $r$ at the end of every timing update is given in Table~\ref{tab:window-sizing-strategy}. It can be observed from this transition diagram that $state$ in timing update $i$ can be represented as $S_{v_{i-1}},v_i$, where $v_{i-1}$ and $v_i$ are binary digits that denote the stats of $(i-1)^{th}$ and $i^{th}$ timing updates respectively. A status of $v=0$ indicates a timing violation while a $1$ denotes a successful timing update. 
% We initialize $r$ to 2 and incrementally update the value of $r$ depending on the $state$ of the timing update. We limit the maximum value of $r$ to $\frac{N}{2}$, where $N$ stands for the total number of gates in the design. For example, if there is a timing violation in iterations $(i-1)$ and $i$ then the value of $r$ is set to 1 and the $state$ is set to 00, and only one gate is updated in the next iteration $(i+1)$, and if in the $(i+1)^{th}$ iteration there is no timing violation then the $state$ variable is updated to 01 and the value of $r$ is set to $r(i)*2$ ( 2 in this case as only one gate was replaced in the $i^{th}$ iterataion) and $r(i)*2$ gates are analyzed in the current iteration. Thus, the algorithm adaptively varies the window size depending on the $state$ variable.
% We sum up each iteration of the algorithm in the following steps.
% \begin{itemize}

% \item For each gate in the list A sort the gates based on the TVLA scores.

% \item For the first $r$ choices of A\; perform the following steps\;
% 	\begin{itemize}
%       \item if the gate has sufficient positive slack, we then replace the gate with the next configuration.
%     \end{itemize}

% \item We then check for any timing violations by running Static Timing Analysis.

% \item If there is any delay violation, undo all reconfigurations.
% \begin{itemize}
% \item if $r$ is 1, then mark the corresponding gate as critical so that it cannot participate in any further timing optimizations.
% \item Update state and compute the new value of $r$.
% \end{itemize}
% \item  If timing evaluation is successful
% \begin{itemize}
% 	\item Run TVLA estimation, sort the gates based on updated TVLA values.
%     \item Update $state$ and compute the new value of $r$.
%     \item if value of $r$ is greater than A, the we resize $r$ to $\frac{A.size}{2}$.
% \end{itemize}

% \end{itemize}

%\item
%At the end of each iteration, {\sf Karna} checks the netlist for slew and capacitance violations. We incrementally upsize each gate in order to fix them. %Figure~\ref{fig:karna}
%shows the working of the {\sf Karna} module. 
%\end{itemize}

%Figure~\ref{fig:aesopt} showed that not all regions in the chip have a uniform TVLA value. In this step, we identify and optimize the gates in such vulnerable regions of the netlist. %It can be seen that for any given input, the amount of switching activity is different for different areas of the design. The side-channel leakage could be due to some areas of the design switching at a different rate for a specific input when compared to a random input.%Hence, in order to reduce the side-channel leakage  the gates belonging to these vulnerable areas need to be optimized. 
%In this step, we identify and optimize the gates in such vulnerable regions of the netlist.

% {\sf Karna} tries to achieve security without violating the design requirements. However, as mentioned earlier choosing gate configurations that favour security might violate the delay or area constraint. Hence, {\sf Karna} tries to balance between these two requirements.  It should be noted that the size of a region determines the nature of optimizations performed by {\sf Karna}. For example, consider the scenario where the value of $N$ is set such that there is only one gate per region. In this scenario {\sf Karna} would be able to identify uniquely the set of gates violating the secuirty constraints and change their configuration. This might cause the algorithm to select choices that are locally optimal i.e, they improve the overall security of the design but

% While a high value of $N$ aggressively optimizes the design for security even at the cost of area and delay, a very low value would perform a lazy security optimization. For instance, when $N_{grids}=1$, the entire design is considered as a whole during the optimization process. This means that the algorithm might select gates that

 %assessed for TVLA compliance. If it fails the TVLA test, all the gates belonging to the design are added to the working set of gates that needs to be optimized. This may lead to performance issues for designs that have a large number of gates. On the contrary, when $N_{grids}$ is equal to the number of gates in the design, each gate is checked for TVLA compliance and only the vulnerable gates are optimized. While this approach reduces the number of gates in the working set, this is also sub-optimal since the TVLA test has to be run for every gate in the design. More importantly, the algorithm may disregard placement dependencies between grids (i.e., delay and area budget of the design as a whole) since each grid is optimized in an isolated manner. Therefore, there is a need to select an optimal value of $N_{grids}$.

%A very high value of $N_{grids}$ will perform a fine-grained security analysis on the design while a low value of $N_{grids}$ will perform a coarse-grained analysis. For instance, setting $N_{grids}$ to the number of gates in the design will calculate the TVLA score for each gate in the netlist and identify if it is vulnerable, while a value of 1 will analyze the entire design as a whole and add all the gates to the vulnerable list. Thus the value of $N_{grids}$, much like the \texttt{-security\_level} option lets the designer specify the level of security expected from the design. A high value of $N_{grids}$ coupled together with a very low TVLA threshold would set extremely high security constraints on the design. Once the netlist is divided, the TVLA score is then calculated for each grid in the netlist. All the grids that do not comply with the TVLA score specified in the \texttt{-security\_level} option are marked as \textbf{unsafe} and the gates that belong to these grids are added to a working set. We then carefully tune the gate parameters of all the gates in this set in the next step, in order to improve the security of the design.

%{\flushleft \bf Reconfiguring the unsafe areas}

### 2019-05-30 Chapter4/related.tex
thesis initial draft

\section{Related Work}
\label{sec:related}
% \todo[inline]{
% Organize related work as follows:

% Side-channel countermeasures can be applied at either the algorithm level, system level, or device level.

% Algorithm level countermeasures include masking, threshold implementations, rekeying.

% System level countermeasures include all the power noise aspects.

% Ours is most close to 
% Device level include WDDL, SABL, etc.
% }
%\subsection{Related Work:}
Side-channel attack countermeasures can be categorized as algorithmic, physical, or system-level. Algorithmic countermeasures insert additional operations that mask~\cite{akkar:2001} or split~\cite{Bilgin:2014} the sensitive computation. System-level countermeasures, such as~\cite{Wang:2013,tokunaga:2009,singh:2015,mathew:2018}, use the device's power supply to  normalize or randomize the overall power consumption. Physical countermeasures like ~\cite{Kim2017,Tiri:2004} use custom gates that consume power independent of the gate's switching. While  algorithmic and system-level countermeasures require additional circuitry, {physical countermeasures} use custom logic design methodologies to tackle the leakage. {\sf Karna} on the other hand requires no additional circuitry nor custom logic therefore has much lower overheads.  
{\sf Karna} in principle, is similar to ~\cite{Tiri:2004}, where side-channel resistant gates are realized by combining multiple standard cell gates. However, the size of each compound gate is considerably larger, resulting in a 4$\times$ increase in area. {\sf Karna} on the other hand, simply reconfigures gates in the design. Thus the area is not affected. Gate reconfigurations during the EDA flow have been used in the past to ensure low-power design~\cite{hu:12,flach:2014} and high-performance~\cite{ozdal:2012}. To the best of our knowledge, {\sf Karna} is the first to use gate reconfiguration to address side-channel leakage.

%The EDA flow is responsible for translating the design specified in a high level language like Verilog into actual hardware. Gate sizing algorithms attempt to select the best possible configuration of the gate such that the objectives at the corresponding stage are achieved. Works like~\cite{hu:12, ozdal:2012,reimann:13,li:2012,flach:2014} propose a sizing algorithm that focuses on varying the threshold voltage $V_t$ and the size of the gate in order to reduce the power consumption of the design.  While~\cite{hu:12,reimann:13} use heuristics like simulated annealing to reconfigure the gates, \cite{ozdal:2012,li:2012,flach:2014} use analytical techniques to solve the problem. However, none of the prior works attempt to leverage the EDA flow in order to counter the power side-channel. To the best of our knowledge ours is the first work try and use the gate sizing techniques to mitigate power side-channels.
%\vspace{-3pt}
\section{Conclusion and Future Work}
\label{sec:conclusion}
{\sf Karna} demonstrates that side-channel security of a device can be improved by reconfiguring the vulnerable gates in the design. This allows security constraints to be elegantly integrated into any EDA flow permitting designers to achieve design security with minimal overheads. {\sf Karna} works on a post placed netlist and is tested successfully on three popular cipher implementations and meets the desired security level (4.5) with minimal impact on area,power and delay. Our current results show drastic increase in EDA design time, mainly due to power trace collection needed for TVLA computation. In the future we plan to optimize this step by parallelization and with better side-channel metrics. Another direction of work is to evaluate {\sf Karna} to address other side-channel attacks like fault injection and timing.

%In our proposed flow, we investigate the impact of various design optimizations on the security of the device using the metric proposed in~\cite{becker:2013}. We identify potential regions in the netlist that are vulnerable and use a gate sizing scheme to reconfigure the $V_{dd}$, $V_t$ and $size$ values in the netlist such that the overall t-score of the netlist falls under the prescribed limits.

% \begin{itemize}
% \item \textbf{Prior Survey}: \cite{Yang2017}:Hardware Designs for Security in Ultra-Low-Power IoT Systems: An Overview and Survey; \cite{Duarte2009}: A note on the security of M ST 3; \cite{Diehl2018}: Comparing the cost of protecting selected lightweight block ciphers against differential power analysis in low-cost FPGAs;

% \item \textbf{Attacks}: \cite{Moradi2014}:Side channel attack using static power;\cite{Alioto2010}: Leakage Power attacks; \cite{Wei2018}: I Know What You See: Power Side-Channel Attack on Convolutional Neural Network Accelerators
% \cite{Singh2017}: Improved power side channel attack resistance of a 128-bit AES engine with random fast voltage dithering.
% \item \textbf{Analysis on SideChannel Attacks}: \cite{Moos}:Static Power Side-Channel Analysis of a Threshold Implementation Prototype Chip;  \cite{Reparaz2017}: Dude, is my code constant time?; \cite{Goodwill2011}: A Testing Methodology for Side-Channel Resistance Validation;  \cite{Roy2015}:From theory to practice of private circuit: A cautionary note (This paper talks about leakage detection tests, more of an analysis than a metric, could be a section after discussing attacks); \cite{Moosa}: Glitch-Resistant Masking Revisited or Why Proofs in the Robust Probing Model are Needed; \cite{Zoni2018}: A Comprehensive Side-Channel Information Leakage Analysis of an In-Order RISC CPU Microarchitecture; \cite{Brier2004}: Correlation Power Analysis with a Leakage Model; \cite{Bache2018}: Confident Leakage Assessment -A Side-Channel Evaluation Framework based on Confidence Intervals

% \item \textbf{Metric}: \cite{Veyrat-charvillon2013}: Certify leakage of a chip; \cite{Schneider2016}:Leakage assessment methodology; \cite{Federal2017}: A Platform to Evaluate the Fault Sensitivity of Superscalar Processors; \cite{Standaert2017}: How (not) to Use Welch's T-test in Side-Channel Security Evaluations; \cite{Corre}: Micro-Architectural Power Simulator for Leakage Assessment of Cryptographic Software on ARM Cortex-M3 Processors
% \cite{Mather}: Does My Device Leak Information? An a priori Statistical Power Analysis of Leakage Detection Tests; \cite{Zhang}: Towards Sound and Optimal Leakage Detection Procedure; \cite{Reparaz}:Fast Leakage Assessment; \cite{Sadhukhan2017}: An Evaluation of Lightweight Block Ciphers for Resource-Constrained Applications: Area, Performance, and Security; \cite{Barenghi2018}: Side-channel security of superscalar CPUs Evaluating the Impact of Micro-architectural Features;

% \item \textbf{Model Using some metric to avoid attacks}: \cite{Leiserson2014}: Gate-Level Masking under a Path-Based Leakage Metric;

% \item \textbf{Models to provide security against attacks}: \cite{DeCnudde2016}: Masking AES with $d + 1$ shares in hardware; \cite{Ghoshal2017}: Several masked implementations of the boyar-peralta AES S-Box; \cite{DeCnudde2017}: Securing the PRESENT Block Cipher Against Combined Side-Channel Analysis and Fault Attacks; \cite{Kar2018}: Reducing Power Side-Channel Information Leakage of AES Engines Using Fully Integrated Inductive Voltage Regulator; \cite{Wegener}: A First-Order SCA Resistant AES without Fresh Randomness; \cite{DeCnudde2017}: Securing the PRESENT Block Cipher Against Combined Side-Channel Analysis and Fault Attacks; \cite{Seuschek2017}: Side-channel leakage aware instruction scheduling;  \cite{Kim2017}: STBC: Side Channel Attack Tolerant Balanced Circuit with Reduced Propagation Delay; \cite{Patranabis2016}: Shuffling across rounds: A lightweight strategy to counter side-channel attacks ; \cite{Judd2016}: Proteus; \cite{Gross2018}: Generic Low-Latency Masking in Hardware;\cite{Ghoshal2018}: Lightweight and Side-channel Secure 4 × 4 S-Boxes from 
% Cellular Automata Rules; \cite{Agosta2015}:The MEET Approach: Securing Cryptographic Embedded Software Against Side Channel Attacks;

% \item \textbf{Miscellaneous}: \cite{Levi2017}CPA Secured Data-Dependent Delay- Assignment Methodology;  \cite{Profile2014}: Optimum Leakage Recovery using Synopsys Primetime ECO Leakage Recovery Flow; \cite{Gross2018a}: Generic Low-Latency Masking in Hardware; \cite{Gierlichs2008}: Mutual Information Analysis; \cite{Peng2018}: Framework for efficient SCA resistance verification of IoT devices

% \end{itemize}

### 2019-05-30 abstract.tex
thesis initial draft

--- 2018-01-11 abstract.tex
@@
-This thesis studies the following topics in the area of Reinforcement Learning: Multi-armed bandits in stationary distribution with the goal of cumulative regret minimization and Thresholding bandits in pure exploration setting.
+Computers have evolved from being glorified calculators that occupied the space of a large building to small pervasive devices.
+This rapid growth, however, has increased the expectations that the end user places on today's digital devices which, in turn, has increased the number of constraints on the device.
+This thesis considers two such objectives viz, power and security and proposes design level techniques to address the same.
+
+Today's devices are expected to be extremely performance efficient with both servers and mobile phones expected to run the same workload, e.g., statistical inference algorithms, smaller in size and have a lower energy footprint to enable ubiquity in deployment.
+This creates challenges for digital designers as these constraints are orthogonal causing designers to sacrifice one or more of these objectives.
+The exponential growth in the number of EDGE devices has also impacted the device manufacturing time which creates a unique challenge for the digital designer as the design is now expected to meet three orthogonal constraints in a short amount of time.
+Our proposed MLTimer solution presented in this thesis addresses this problem that uses a novel data-driven algorithm which lets the designer re-use solutions from previously optimized circuits to meet the power constraints for  a given design.
+We show that the proposed solution outperforms the state-of-the-art solutions by evaluating it on the ISPD2012, ISPD2013 benchmark circuits.
+We compare the results with a commercial EDA flow by evaluating the proposed solution to optimize a state-of-the-art embedded processor running Linux.
+
+The recent Meltdown and Cambridge Analytica data leaks have sensitized the common man to the importance of a secure software and hardware computing platform.
+While software vulnerabilities can be fixed by implementing a patch with minimal overheads, hardware vulnerabilities, otherwise known as side-channels, are harder to detect and correct.
+In this thesis, we consider the problem of power side-channels on embedded devices and propose a gate-sizing based solution to reduce the risk of a digital device through the power side-channel.
+Our proposed solution, Karna, is the first design level solution.
+We quantify the effectiveness of Karna along with the area, delay and performance overheads by evaluating the proposed scheme on three different block ciphers.
+
+%This thesis studies the following topics in the area of Reinforcement Learning: classic Multi-armed bandits in stationary distribution with the goal of cumulative regret minimization using variance estimates and Thresholding bandits in pure exploration fixed-budget setting with the goal of instantaneous regret minimization also using variance estimates.
 The common underlying theme is the study of bandit theory and its application in various types of environments.
